### 2023-05-12 FoodWebsCheck.Rmd
First commit

---
title: "Check consistency"
author: "L.A.S."
output: html_document
editor_options: 
  chunk_output_type: console
---

## Setup

```{r setup, eval=T,echo=FALSE }
#load(".RData")
require(igraph)
require(stringr)
require(devtools)
if( require(meweasmo) == FALSE)
  install_github("lsaravia/meweasmo")
if( require(multiweb) == FALSE)
  install_github("lsaravia/multiweb")
require(tidyverse)

```

# Check Weddell Sea

```{r WeddellSea, eval=F,echo=F,message=T,warning=T}

#
dtot <- read_csv("Data/WeddellSea_links.csv")

# Check valid names 
#
#
require(taxize)
dfn <- unique(dtot$consumer)
con_names <- gnr_resolve(dfn, best_match_only = TRUE, canonical=TRUE)
# Species not found
anti_join(data.frame(user_supplied_name=dfn),con_names)
# 1 Cadulus dalli antarcticum

dfn <- unique(dtot$resource)
res_names <- gnr_resolve(dfn, best_match_only = TRUE, canonical=TRUE)
anti_join(data.frame(user_supplied_name=dfn),res_names)
# 1             Phytodetritus
# 2                  Sediment
# 3         Silicioflagellata
# 4 Cadulus dalli antarcticum
gM <- graph_from_edgelist(as.matrix(dtot), directed  = T)

# Basal species
#
basal_sp <- (V(gM)[ (degree(gM,mode="in")==0) ])$name

# CLasificación completa
clasall <- classification(basal_sp, db = 'itis') # 24 not found

# Solamente clase
class <- tax_name(basal_sp, get = "class", db = "itis")
class %>% count(is.na(class))                                # 27 NA

## class = Bacillariophyceae

```

### 2023-06-05 FoodWebsCheck.Rmd
Chequea red weddell y genera colapso de basales

@@
 # 4 Cadulus dalli antarcticum
+
 gM <- graph_from_edgelist(as.matrix(dtot), directed  = T)
@@
 # CLasificación completa
-clasall <- classification(basal_sp, db = 'itis') # 24 not found
+# clasall <- classification(basal_sp, db = 'itis') # 24 not found
 
@@
 class %>% count(is.na(class))                                # 27 NA
+class <- class%>% mutate(genera= stringr::word(query)) %>% rename( species = query ) %>% select(genera,species,class)
+# write_tsv(class,"Data/WeddellSea_basal.dat")
 
-## class = Bacillariophyceae
+# Genera tabla genero clase para reemplazar el nombre de la especie por la clase solo en el caso de Bacillariophyceae
+#
+gencla <- class %>% filter(!is.na(class)) %>%  distinct(genera,class) %>%  filter(class=="Bacillariophyceae")
+#
+gencla <- add_case(gencla, genera="Nitzschia", class="Bacillariophyceae" )
+gencla
+sapply( 1:nrow(dtot), function(i) {
+  res_gen <- stringr::word(dtot$resource[i]) 
+  rep_cla <- gencla %>% filter(genera == res_gen) 
+  if(nrow(rep_cla)==1)
+    dtot$resource[i] <<- rep_cla$class
+})
 
+#
+collapsed_w <- dtot %>% distinct()
+gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)
+
+# Basal species
+#
+new_basal_sp <- (V(gM)[ (degree(gM,mode="in")==0) ])$name
+new_basal_sp
+#
+#        Dictyocha     Chrysophyceae --> phytoplankton == silicioflagellata 
+#      Phaeocystis  Prymnesiophyceae --> phytoplankton
+#      
+#   Alcyonium antarcticum  --> Coral not basal
+#   Silicioflagellata     --> ??? Chrysophyceae? 
+#
+
+calc_topological_indices(gM)
+write_csv(collapsed_w,"Data/Weddell_collapsed_links.csv")
 ```

### 2023-06-05 R/Scotia_Sea_foodweb_subsampling.R
Scotia Sea methods

@@ -1,0 +1,61 @@
+###Scotia Sea food web###
+
+#working dir
+#C:\LocalData\susakort\GitHub\PIP\Rscripts
+setwd("C:/LocalData/susakort/GitHub/PIP/Rscripts")
+
+dirF<-"../Figures/"
+dirSoctia<-"../Data/Scotia_Sea/"
+
+#Scotia nodes info
+#metaweb_nodes.csv
+nodes_Scotia<-read.csv(paste0(dirSoctia,"metaweb_nodes.csv"), sep=",")
+dim(nodes_Scotia)
+nodes_Scotia<-nodes_Scotia[,-c(8,9)]
+head(nodes_Scotia)
+
+#southern_nodes
+ids_s<-sort(c(which(nodes_Scotia$Lat.distribution=="Both"), which(nodes_Scotia$Lat.distribution=="South")))
+SS_pw<-nodes_Scotia[ids_s,] 
+head(SS_pw)
+dim(SS_pw)
+
+#northern_nodes
+ids_n<-sort(c(which(nodes_Scotia$Lat.distribution=="Both"), which(nodes_Scotia$Lat.distribution=="North")))
+NS_pw<-nodes_Scotia[ids_n,] 
+head(NS_pw)
+dim(NS_pw)
+
+#Scotia links metaweb
+links_scotia<-read.csv(paste0(dirSoctia,"metaweb_links.csv"), sep=",")
+head(links_scotia)
+
+#Clean names of the pl, full species list
+#Select only interactions between species from species list
+links_scotia$consumer[links_scotia$consumer%in%SS_pw$node]
+links_scotia$resource[links_scotia$resource%in%SS_pw$node]
+
+#subset the pairwise list for Southern Scotia Sea
+pl_cons <- subset(links_scotia, links_scotia$consumer%in%SS_pw$node)
+pl_reso <- subset(links_scotia, links_scotia$resource%in%SS_pw$node)
+plA <- subset(links_scotia, links_scotia$consumer%in%SS_pw$node & links_scotia$resource%in%SS_pw$node)
+plA <- plA[!duplicated(plA),]
+dim(plA) # rows are identical to number of trophic links
+str(plA)
+SS_FW<-plA
+write.csv(SS_FW, "../Data/Scotia_Sea/SouthernScotia_FoodWeb.csv", row.names=T)
+
+#subset the pairwise list for Northern Scotia Sea
[…]

### 2023-06-06 R/Scotia_Sea_foodweb_subsampling.R
new files

@@ -1,17 +1,11 @@
 ###Scotia Sea food web###
 
-#working dir
-#C:\LocalData\susakort\GitHub\PIP\Rscripts
-setwd("C:/LocalData/susakort/GitHub/PIP/Rscripts")
-
-dirF<-"../Figures/"
-dirSoctia<-"../Data/Scotia_Sea/"
 
 #Scotia nodes info
 #metaweb_nodes.csv
-nodes_Scotia<-read.csv(paste0(dirSoctia,"metaweb_nodes.csv"), sep=",")
+nodes_Scotia<-read.csv("Data/metaweb_nodes.csv", sep=",")
 dim(nodes_Scotia)
-nodes_Scotia<-nodes_Scotia[,-c(8,9)]
+nodes_Scotia<-nodes_Scotia[,-c(8,9)]#remove these columns
 head(nodes_Scotia)
 
 #southern_nodes
@@ -27,7 +21,7 @@ head(NS_pw)
 dim(NS_pw)
 
 #Scotia links metaweb
-links_scotia<-read.csv(paste0(dirSoctia,"metaweb_links.csv"), sep=",")
+links_scotia<-read.csv("Data/metaweb_links.csv", sep=",")
 head(links_scotia)
 
 #Clean names of the pl, full species list
@@ -43,7 +37,7 @@ plA <- plA[!duplicated(plA),]
 dim(plA) # rows are identical to number of trophic links
 str(plA)
 SS_FW<-plA
-write.csv(SS_FW, "../Data/Scotia_Sea/SouthernScotia_FoodWeb.csv", row.names=T)
+write.csv(SS_FW, "Data/SouthernScotia_FoodWeb.csv", row.names=F)
 
 #subset the pairwise list for Northern Scotia Sea
 pl_cons2 <- subset(links_scotia, links_scotia$consumer%in%NS_pw$node)
@@ -54,7 +48,39 @@ dim(plA2) # rows are identical to number of trophic links
 str(plA2)
 NS_FW<-plA2
 head(NS_FW)
-write.csv(NS_FW, "../Data/Scotia_Sea/NorthernScotia_FoodWeb.csv", row.names=T)
+write.csv(NS_FW, "Data/NorthernScotia_FoodWeb.csv", row.names=F)
+
+
+#Extract taxonmic information for species
+
+library("taxize")
+library("tidyverse")
[…]

### 2023-06-06 R/Scotia_Sea_foodweb_subsampling.R
r script

@@ -64,7 +64,7 @@ colnames(scotia_tax_list)<-c("species", "genus", "family", "order", "class", "ph
 #head(scotia_tax_list)
 #unique(scotia_tax_list$order)
 
-#
+#Collapse basal species, code from Leo
 ss_fw<-read_csv("Data/SouthernScotia_FoodWeb.csv")
 head(ss_fw)
 dim(ss_fw)
@@ -79,8 +79,15 @@ res_names <- gnr_resolve(dfn_ss2, best_match_only = TRUE, canonical=TRUE)
 anti_join(data.frame(user_supplied_name=dfn_ss2),res_names)
 
 # pairwise interaction list for the Southern Scotia Sea food web
-gM <- graph_from_edgelist(as.matrix(ss_fw), directed  = T)
+gM_ss <- graph_from_edgelist(as.matrix(ss_fw), directed  = T)
 
+# identify basal species
+basal_sp_ss <- (V(gM)[ (degree(gM_ss,mode="in")==0) ])$name
+
+# Solamente clase
+class <- tax_name(basal_sp_ss, get = "class", db = "itis")
+class %>% count(is.na(class_ss))                                # 27 NA
+class <- class%>% mutate(genera= stringr::word(query)) %>% rename( species = query ) %>% select(genera,species,class)
 
 
 

### 2023-06-06 R/ScotiaSea_MM&SB.R
Add birds & mammals interactions

@@ -1,0 +1,54 @@
+##
+# Scotia Sea marine mammals & sea birds
+##
+
+# Packages
+library(tidyverse)
+
+# Species list ----
+sp_list <- read.csv("Data/SB&MM_list_ScotiaSea.csv", header = T)
+
+# Diet database ----
+# Import Southern Ocean dietary database from
+# https://esapubs.org/archive/ecol/E092/097/#data (diet.csv file)
+raymond_db <- read.csv("raymond_database.csv", header = T)
+
+# Get interactions ----
+# Select columns of interest
+inter_raw <- raymond_db %>% 
+  select(PREY_NAME, PREDATOR_NAME, LOCATION)
+# Tidy 'sp_list'
+sp_list_tidy <- sp_list %>% 
+  select(species) %>% 
+  rename(PREDATOR_NAME = species)
+# Get interactions for sea birds & marine mammals spp
+inter2add <- merge(x = inter_raw, y = sp_list_tidy, by = "PREDATOR_NAME")
+# Filter by prey from Scotia Sea FWs. First, load FWs
+nss_fw <- read.csv("Data/NorthernScotia_FoodWeb.csv", header = T, colClasses = c("NULL", NA, NA))
+nss_preylist <- nss_fw %>% 
+  select(resource) %>% 
+  rename(PREY_NAME = resource) %>% 
+  distinct()
+nss2add <- merge(x = inter2add, y = nss_preylist, by = "PREY_NAME") %>% 
+  select(PREY_NAME, PREDATOR_NAME) %>% 
+  rename(resource=PREY_NAME, consumer=PREDATOR_NAME) %>%
+  distinct()
+
+sss_fw <- read.csv("Data/SouthernScotia_FoodWeb.csv", header = T, colClasses = c("NULL", NA, NA))
+sss_preylist <- sss_fw %>% 
+  select(resource) %>% 
+  rename(PREY_NAME = resource) %>% 
+  distinct()
+sss2add <- merge(x = inter2add, y = sss_preylist, by = "PREY_NAME") %>% 
+  select(PREY_NAME, PREDATOR_NAME) %>% 
+  rename(resource=PREY_NAME, consumer=PREDATOR_NAME) %>% 
+  distinct()
+
+# Add interactions to FWs
+nss_fw_new <- bind_rows(nss_fw, nss2add)
+sss_fw_new <- bind_rows(sss_fw, sss2add)
+
+# New FWs ----
[…]

### 2023-06-06 R/Compare_FW_versions.R
Comparing FW versions

@@ -1,0 +1,39 @@
+##
+# Compare original & standardized FWs
+##
+
+library(tidyverse)
+library(igraph)
+library(multiweb)
+
+# Scotia Sea ----
+# Old
+nscotia_old <- read.csv("Data/NorthernScotia_FoodWeb.csv", header = T)
+sscotia_old <- read.csv("Data/SouthernScotia_FoodWeb.csv", header = T)
+# Standardized
+nscotia_std <- read.csv("Data/NorthernScotia_top.csv", header = T, colClasses = c("NULL",NA,NA))
+sscotia_std <- read.csv("Data/SouthernScotia_top.csv", header = T, colClasses = c("NULL",NA,NA))
+
+# Igraph objects
+nscotia_old_g <- graph_from_data_frame(nscotia_old, directed = T)
+sscotia_old_g <- graph_from_data_frame(sscotia_old, directed = T)
+nscotia_std_g <- graph_from_data_frame(nscotia_std, directed = T)
+sscotia_std_g <- graph_from_data_frame(sscotia_std, directed = T)
+
+# Properties
+nscotia_old_prop <- calc_topological_indices(nscotia_old_g) %>% mutate(Name="Old N Scotia")
+sscotia_old_prop <- calc_topological_indices(sscotia_old_g) %>% mutate(Name="Old S Scotia")
+nscotia_std_prop <- calc_topological_indices(nscotia_std_g) %>% mutate(Name="Std N Scotia")
+sscotia_std_prop <- calc_topological_indices(sscotia_std_g) %>% mutate(Name="Std S Scotia")
+
+scotia_prop <- bind_rows(nscotia_old_prop, sscotia_old_prop, nscotia_std_prop, sscotia_std_prop) %>% 
+  rename(Network=Name) %>% 
+  dplyr::select(Network, everything())
+
+# Plot
+par(mfrow = c(2,2))
+plot_troph_level(nscotia_old_g, main = "Old N Scotia")
+plot_troph_level(sscotia_old_g, main = "Old S Scotia")
+plot_troph_level(nscotia_std_g, main = "Std N Scotia")
+plot_troph_level(sscotia_std_g, main = "Std S Scotia")
+

### 2023-06-06 R/Scotia_Sea_foodweb_subsampling.R
new data

@@ -65,16 +65,16 @@ colnames(scotia_tax_list)<-c("species", "genus", "family", "order", "class", "ph
 #unique(scotia_tax_list$order)
 
 #Collapse basal species, code from Leo
-ss_fw<-read_csv("Data/SouthernScotia_FoodWeb.csv")
+ss_fw<-read_csv("Data/SouthernScotia_top.csv")
+ss_fw<-ss_fw[,-1]
 head(ss_fw)
 dim(ss_fw)
-dfn_ss <- unique(dtot$consumer)
+dfn_ss <- unique(ss_fw$consumer)
 con_names_ss <- gnr_resolve(dfn_ss, best_match_only = TRUE, canonical=TRUE)
 # Species not found
 anti_join(data.frame(user_supplied_name=dfn_ss),con_names_ss)
 
-
-dfn_ss2 <- unique(dtot$resource)
+dfn_ss2 <- unique(ss_fw$resource)
 res_names <- gnr_resolve(dfn_ss2, best_match_only = TRUE, canonical=TRUE)
 anti_join(data.frame(user_supplied_name=dfn_ss2),res_names)
 
@@ -82,12 +82,132 @@ anti_join(data.frame(user_supplied_name=dfn_ss2),res_names)
 gM_ss <- graph_from_edgelist(as.matrix(ss_fw), directed  = T)
 
 # identify basal species
-basal_sp_ss <- (V(gM)[ (degree(gM_ss,mode="in")==0) ])$name
-
+basal_sp_ss <- (V(gM_ss)[(degree(gM_ss,mode="in")==0) ])$name
+basal_sp_ss
 # Solamente clase
 class <- tax_name(basal_sp_ss, get = "class", db = "itis")
-class %>% count(is.na(class_ss))                                # 27 NA
+class %>% count(is.na(class))                                # 27 NA
 class <- class%>% mutate(genera= stringr::word(query)) %>% rename( species = query ) %>% select(genera,species,class)
+write_tsv(class,"Data/SoutherScotia_basal.dat")
+
+class<-read_tsv("Data/SoutherScotia_basal.dat")
+class2 <- class[-c(3,9,18),]#remove detritus, bacteria, and maxillopoda
+class2  <- class2 %>% 
+  mutate(class = case_when(class %in% c("Prymnesiophyceae",NA) ~ "Phytoplankton_other",TRUE ~ class))
[…]

### 2023-06-07 R/Scotia_Sea_foodweb_subsampling.R
new files

@@ -1,5 +1,7 @@
-###Scotia Sea food web###
+###Scotia Sea food webs###
 
+# Susanne Kortsch
+# 07.06.2023
 
 #Scotia nodes info
 #metaweb_nodes.csv
@@ -50,17 +52,20 @@ NS_FW<-plA2
 head(NS_FW)
 write.csv(NS_FW, "Data/NorthernScotia_FoodWeb.csv", row.names=F)
 
+##################################################################################
 
 #Extract taxonmic information for species
 
 library("taxize")
 library("tidyverse")
+library("igraph")
+
 #scotia_tax<-tax_name(nodes_Scotia$node, db = "itis", get = c("genus", "family", "order", "class", "phylum"))
 
 #Scotia Sea taxonmic info 
-scotia_tax_list<-read_csv("Data/scotia_taxonomic_list.csv")
-scotia_tax_list<-scotia_tax_list[, -c(1,2)]
-colnames(scotia_tax_list)<-c("species", "genus", "family", "order", "class", "phylum")
+#scotia_tax_list<-read_csv("Data/scotia_taxonomic_list.csv")
+#scotia_tax_list<-scotia_tax_list[, -c(1,2)]
+#colnames(scotia_tax_list)<-c("species", "genus", "family", "order", "class", "phylum")
 #head(scotia_tax_list)
 #unique(scotia_tax_list$order)
 
@@ -84,16 +89,19 @@ gM_ss <- graph_from_edgelist(as.matrix(ss_fw), directed  = T)
 # identify basal species
 basal_sp_ss <- (V(gM_ss)[(degree(gM_ss,mode="in")==0) ])$name
 basal_sp_ss
+
 # Solamente clase
-class <- tax_name(basal_sp_ss, get = "class", db = "itis")
-class %>% count(is.na(class))                                # 27 NA
-class <- class%>% mutate(genera= stringr::word(query)) %>% rename( species = query ) %>% select(genera,species,class)
-write_tsv(class,"Data/SoutherScotia_basal.dat")
+#class <- tax_name(basal_sp_ss, get = "class", db = "itis")
+#class %>% count(is.na(class))                                # 27 NA
+#class <- class%>% mutate(genera= stringr::word(query)) %>% rename( species = query ) %>% select(genera,species,class)
[…]

### 2023-06-07 R/Scotia_Sea_foodweb_subsampling.R
new file

@@ -156,7 +156,7 @@ ns_fw<-read_csv("Data/NorthernScotia_top.csv")
 ns_fw<-ns_fw[,-1]
 head(ns_fw)
 dim(ns_fw)
-dfn_ns <- unique(dtot$consumer)
+dfn_ns <- unique(ns_fw$consumer)
 con_names_ss <- gnr_resolve(dfn_ss, best_match_only = TRUE, canonical=TRUE)
 # Species not found
 anti_join(data.frame(user_supplied_name=dfn_ss),con_names_ss)

### 2023-06-07 R/Scotia_Sea_foodweb_subsampling.R
new files

@@ -3,6 +3,7 @@
 # Susanne Kortsch
 # 07.06.2023
 
+### Make the Southern and Northern Scotian Sea food webs
 #Scotia nodes info
 #metaweb_nodes.csv
 nodes_Scotia<-read.csv("Data/metaweb_nodes.csv", sep=",")
@@ -54,6 +55,9 @@ write.csv(NS_FW, "Data/NorthernScotia_FoodWeb.csv", row.names=F)
 
 ##################################################################################
 
+### Collapse the basal species into few phytoplankton nodes
+# code from Leo
+
 #Extract taxonmic information for species
 
 library("taxize")
@@ -98,7 +102,20 @@ basal_sp_ss
 
 class<-read_tsv("Data/SoutherScotia_basal.dat")
 class2 <- class[-c(3,9,18),]#remove detritus, bacteria, and maxillopoda nodes
-#NOTE! MAXILLOPODA IS MISSING RESOURCE ITEMS!
+
+#NOTE! Oncaea parila MAXILLOPODA IS MISSING RESOURCE ITEMS!
+#metaweb 
+#add Oncaea links from GENUS
+links_scotia<-read.csv("Data/metaweb_links.csv", sep=",")
+head(links_scotia)
+#Genus
+Oncacea_meta_con<-links_scotia[c(which(links_scotia$consumer=="Oncaea prolata"),which(links_scotia$consumer=="Oncaea curvata")),]
+Oncacea_meta_con[,2]<-"Oncaea parila"
+#duplicated(Oncacea_meta_con)
+#Oncacea_meta$resource%in%collapsed_ss_fw$resource
+
+ss_fw<-rbind(ss_fw, Oncacea_meta_con)
+
 #rename some plankton species to other for aggregation
 class2  <- class2 %>% 
 mutate(class = case_when(class %in% c("Prymnesiophyceae",NA) ~ "Phytoplankton_other",TRUE ~ class))
@@ -139,16 +156,14 @@ collapsed_ss_fw <- ss_fw2 %>% distinct()
 dim(collapsed_ss_fw)
 gM_ss2 <- graph_from_edgelist(as.matrix(collapsed_ss_fw), directed  = T)
 
-
 #check the basal species
 basal_sp_ss2 <- (V(gM_ss2)[ (degree(gM_ss2,mode="in")==0) ])$name
 basal_sp_ss2
 
-
[…]

### 2023-06-07 R/Scotia_Sea_foodweb_subsampling.R
files

@@ -226,35 +226,35 @@ gencla_dino <- class2 %>% filter(!is.na(class)) %>%  distinct(genera,class) %>% 
 gencla_other <- class2 %>% filter(!is.na(class)) %>%  distinct(genera,class) %>%  filter(class=="Phytoplankton_other")
 #
 
-sapply( 1:nrow(ss_fw), function(i) {
+sapply( 1:nrow(ns_fw), function(i) {
   #i<-5969
-  res_gen <- stringr::word(ss_fw$resource[i]) 
+  res_gen <- stringr::word(ns_fw$resource[i]) 
   
   rep_cla <- gencla %>% filter(genera == res_gen) 
   if(nrow(rep_cla)==1)
-    ss_fw$resource[i] <<- rep_cla$class
+    ns_fw$resource[i] <<- rep_cla$class
   
   rep_cla_dino <- gencla_dino %>% filter(genera == res_gen) 
   if(nrow(rep_cla_dino)==1)
-    ss_fw$resource[i] <<- rep_cla_dino$class
+    ns_fw$resource[i] <<- rep_cla_dino$class
   
   rep_cla_other <- gencla_other %>% filter(genera == res_gen) 
   if(nrow(rep_cla_other)==1)
-    ss_fw$resource[i] <<- rep_cla_other$class
+    ns_fw$resource[i] <<- rep_cla_other$class
 })
 
-unique(ss_fw$resource)
+unique(ns_fw$resource)
 
-collapsed_ss_fw <- ss_fw %>% distinct()
-dim(collapsed_ss_fw)
-gM_ss <- graph_from_edgelist(as.matrix(collapsed_ss_fw), directed  = T)
+collapsed_ns_fw <- ns_fw %>% distinct()
+dim(collapsed_ns_fw)
+gM_ns <- graph_from_edgelist(as.matrix(collapsed_ns_fw), directed  = T)
 
 
 #check the basal species
-basal_sp_ss <- (V(gM_ss)[ (degree(gM_ss,mode="in")==0) ])$name
-basal_sp_ss
+basal_sp_ns <- (V(gM_ns)[ (degree(gM_ns,mode="in")==0) ])$name
+basal_sp_ns
 
-write_csv(collapsed_ss_fw,"Data/Southern_Scotia_collapsed_basal_top.csv")
+write_csv(collapsed_ns_fw,"Data/Northern_Scotia_collapsed_basal_top.csv")
 
 
 

### 2023-06-07 FoodWebsCheck_SK.Rmd
new files

---
title: "Check consistency"
author: "L.A.S."
output: html_document
editor_options: 
  chunk_output_type: console
---

## Setup

```{r setup, eval=T,echo=FALSE }
#load(".RData")
require(igraph)
require(stringr)
require(devtools)
if( require(meweasmo) == FALSE)
  install_github("lsaravia/meweasmo")
if( require(multiweb) == FALSE)
  install_github("lsaravia/multiweb")
require(tidyverse)

```

# Check Weddell Sea

```{r WeddellSea, eval=F,echo=F,message=T,warning=T}

#
dtot <- read_csv("Data/WeddellSea_links.csv")

# Check valid names 
#
#
require(taxize)
dfn <- unique(dtot$consumer)
con_names <- gnr_resolve(dfn, best_match_only = TRUE, canonical=TRUE)
# Species not found
anti_join(data.frame(user_supplied_name=dfn),con_names)
# 1 Cadulus dalli antarcticum

dfn <- unique(dtot$resource)
res_names <- gnr_resolve(dfn, best_match_only = TRUE, canonical=TRUE)
anti_join(data.frame(user_supplied_name=dfn),res_names)
# 1             Phytodetritus
# 2                  Sediment
# 3         Silicioflagellata
# 4 Cadulus dalli antarcticum

gM <- graph_from_edgelist(as.matrix(dtot), directed  = T)

# Basal species
#
basal_sp <- (V(gM)[ (degree(gM,mode="in")==0) ])$name
basal_sp

# CLasificación completa
# clasall <- classification(basal_sp, db = 'itis') # 24 not found

# Solamente clase
class <- tax_name(basal_sp, get = "class", db = "itis")
class %>% count(is.na(class))                                # 27 NA
class <- class%>% mutate(genera= stringr::word(query)) %>% rename( species = query ) %>% select(genera,species,class)

unique(class$genera)

write_tsv(class,"Data/WeddellSea_basal.dat")
class<-read_tsv("Data/WeddellSea_basal.dat")

# Genera tabla genero clase para reemplazar el nombre de la especie por la clase solo en el caso de Bacillariophyceae

#remove "Phytodetritus" and "Sediment"
row_names_to_remove<-c("Phytodetritus","Sediment")
class<-class[!(class$genera %in% row_names_to_remove),]

class  <- class %>% 
mutate(class = case_when(class %in% c("Prymnesiophyceae", "Chrysophyceae") ~ "Phytoplankton_other",TRUE ~ class))

class  <- class %>% 
mutate(class = case_when(species %in% c("Silicioflagellata") ~ "Phytoplankton_other",TRUE ~ class))

#add a resource link to Alcyonium antarcticum
dtot<-rbind(dtot, c("Phytodetritus", "Alcyonium antarcticum"))

#
gencla <- class %>% filter(!is.na(class)) %>%  distinct(genera,class) %>%  filter(class=="Bacillariophyceae")
#
gencla <- add_case(gencla, genera="Nitzschia", class="Bacillariophyceae" )
dim(gencla)

gencla_other <- class %>% filter(!is.na(class)) %>%  distinct(genera,class) %>%  filter(class=="Phytoplankton_other")

sapply( 1:nrow(dtot), function(i) {
  res_gen <- stringr::word(dtot$resource[i]) 
  rep_cla <- gencla %>% filter(genera == res_gen) 
  if(nrow(rep_cla)==1)
    dtot$resource[i] <<- rep_cla$class

  rep_cla_other <- gencla_other %>% filter(genera == res_gen) 
  if(nrow(rep_cla_other)==1)
    dtot$resource[i] <<- rep_cla_other$class
})

#
collapsed_w <- dtot %>% distinct()
gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)

# Basal species
#
new_basal_sp <- (V(gM)[ (degree(gM,mode="in")==0) ])$name
new_basal_sp

#I FIXED THESE ISSUES!!! (Susanne)

#        Dictyocha     Chrysophyceae --> phytoplankton == silicioflagellata 
#      Phaeocystis  Prymnesiophyceae --> phytoplankton
#      
#   Alcyonium antarcticum  --> Coral not basal
#   Silicioflagellata     --> ??? Chrysophyceae? 
#

calc_topological_indices(gM)
write_csv(collapsed_w,"Data/Weddell_collapsed_links_2.csv")
```

### 2023-06-07 R/Compare_FW_versions.R
Compare FWs

@@ -11,8 +11,8 @@ library(multiweb)
 nscotia_old <- read.csv("Data/NorthernScotia_FoodWeb.csv", header = T)
 sscotia_old <- read.csv("Data/SouthernScotia_FoodWeb.csv", header = T)
 # Standardized
-nscotia_std <- read.csv("Data/NorthernScotia_top.csv", header = T, colClasses = c("NULL",NA,NA))
-sscotia_std <- read.csv("Data/SouthernScotia_top.csv", header = T, colClasses = c("NULL",NA,NA))
+nscotia_std <- read.csv("Data/Northern_Scotia_collapsed_basal_top.csv", header = T)
+sscotia_std <- read.csv("Data/Southern_Scotia_collapsed_basal_top.csv", header = T)
 
 # Igraph objects
 nscotia_old_g <- graph_from_data_frame(nscotia_old, directed = T)

### 2023-06-08 FoodWebsCheck.Rmd

--- 2023-05-12 FoodWebsCheck.Rmd
@@
 basal_sp <- (V(gM)[ (degree(gM,mode="in")==0) ])$name
+basal_sp
 
 # CLasificación completa
-clasall <- classification(basal_sp, db = 'itis') # 24 not found
+# clasall <- classification(basal_sp, db = 'itis') # 24 not found
 
@@
 class %>% count(is.na(class))                                # 27 NA
+class <- class%>% mutate(genera= stringr::word(query)) %>% rename( species = query ) %>% select(genera,species,class)
 
-## class = Bacillariophyceae
+unique(class$genera)
 
+#write_tsv(class,"Data/WeddellSea_basal.dat")
+class<-read_tsv("Data/WeddellSea_basal.dat")
+
+# Genera tabla genero clase para reemplazar el nombre de la especie por la clase solo en el caso de Bacillariophyceae
+
+#remove "Phytodetritus" and "Sediment"
+row_names_to_remove<-c("Phytodetritus","Sediment")
+class<-class[!(class$genera %in% row_names_to_remove),]
+
+class  <- class %>% 
+mutate(class = case_when(class %in% c("Prymnesiophyceae", "Chrysophyceae") ~ "Phytoplankton_other",TRUE ~ class))
+
+class  <- class %>% 
+mutate(class = case_when(species %in% c("Silicioflagellata") ~ "Phytoplankton_other",TRUE ~ class))
+
+#add a resource link to Alcyonium antarcticum
+dtot<-rbind(dtot, c("Phytodetritus", "Alcyonium antarcticum"))
+
+#
+gencla <- class %>% filter(!is.na(class)) %>%  distinct(genera,class) %>%  filter(class=="Bacillariophyceae")
+#
+gencla <- add_case(gencla, genera="Nitzschia", class="Bacillariophyceae" )
+dim(gencla)
+
+gencla_other <- class %>% filter(!is.na(class)) %>%  distinct(genera,class) %>%  filter(class=="Phytoplankton_other")
+
+sapply( 1:nrow(dtot), function(i) {
+  res_gen <- stringr::word(dtot$resource[i]) 
+  rep_cla <- gencla %>% filter(genera == res_gen) 
+  if(nrow(rep_cla)==1)
+    dtot$resource[i] <<- rep_cla$class
+
+  rep_cla_other <- gencla_other %>% filter(genera == res_gen) 
+  if(nrow(rep_cla_other)==1)
+    dtot$resource[i] <<- rep_cla_other$class
+})
+
+#
+collapsed_w <- dtot %>% distinct()
+gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)
+
+# Basal species
+#
+new_basal_sp <- (V(gM)[ (degree(gM,mode="in")==0) ])$name
+new_basal_sp
+
+#I FIXED THESE ISSUES!!! (Susanne)
+
+#        Dictyocha     Chrysophyceae --> phytoplankton == silicioflagellata 
+#      Phaeocystis  Prymnesiophyceae --> phytoplankton
+#      
+#   Alcyonium antarcticum  --> Coral not basal
+#   Silicioflagellata     --> ??? Chrysophyceae? 
+#
+
+calc_topological_indices(gM)
+write_csv(collapsed_w,"Data/Weddell_collapsed_links_2.csv")
 ```

### 2023-08-03 FoodWebsCheck.Rmd
Add manuscript en markdown

@@
 #
-dtot <- read_csv("Data/WeddellSea_links.csv")
+dtot <- read_csv("Data/WeddellSea_links_original.csv")
 
@@
 #
-#
+# Predators
 require(taxize)
@@
 
+# CLasificación completa
+clasall <- classification(dfn, db = 'itis') #
+
+# Preys
+#
 dfn <- unique(dtot$resource)
@@
 calc_topological_indices(gM)
-write_csv(collapsed_w,"Data/Weddell_collapsed_links_2.csv")
+write_csv(collapsed_w,"Data/Weddell_collapsed_links.csv")
 ```

### 2023-08-21 R/nodesMetrics.R
Node metrics with NetIndices

@@ -10,15 +10,20 @@ food.web.csv <- c("BeagleChannel_links_original.csv",
 
 library(igraph)
 library(multiweb)
+library(NetIndices)
 links <- list()
 dir.create("Output")
 for (i in 1:length(food.web.csv)){
   links[[i]] <- read.csv2 (paste("Data/",food.web.csv[i],sep=""), header = TRUE, sep = ",")
   #Compute node metrics
   fwgraph <- graph_from_data_frame(links[[i]], directed = T)
+  adjMat <- get.adjacency(fwgraph,sparse=F)
+  # nodesMetrics <- cbind.data.frame(data.frame(degree = degree(fwgraph)),
+  #                                  TrophInd(adjMat),
+  #                                  trophiclevels(fwgraph),
+  #                                  data.frame(omnivory = Level.omnivory(fwgraph)))
   nodesMetrics <- cbind.data.frame(data.frame(degree = degree(fwgraph)),
-                                   trophiclevels(fwgraph),
-                                   data.frame(omnivory = Level.omnivory(fwgraph)))
+                                   TrophInd(adjMat))
   nodesMetrics <- cbind.data.frame(data.frame(Nodes = rownames(nodesMetrics)),
                                    nodesMetrics)
   indexSorted <- sort(nodesMetrics$degree,decreasing = TRUE, index.return = TRUE)                     

### 2023-08-23 WeddellSea_collapse.Rmd
Change name of Rmd

--- 2023-08-03 FoodWebsCheck.Rmd
@@
 ---
-title: "Check consistency"
+title: "Collapse Weddell and Check consistency"
 author: "L.A.S."
@@
 write_csv(collapsed_w,"Data/Weddell_collapsed_links.csv")
+
+collapsed_w <- read_csv("Data/Weddell_collapsed_links.csv")
+
 ```
+
+# Weddell Sea get full classification
+
+```{r, WeddellSeaFullClass, eval=F,echo=F,message=T,warning=T}
+
+#
+dtot <- read_csv("Data/WeddellSea_links_original.csv")
+
+# Check valid names 
+#
+# Predators
+require(taxize)
+dfn <- unique(dtot$consumer)
+dfn <- c(dfn, unique(dtot$resource))
+dfn <- unique(dfn)
+
+# CLasificación completa
+
+clasall <- classification(dfn, db = 'gbif') #
+
+class_list <- class_to_df(clasall)
+
+classall_df <- class_list[[1]]
+
+#
+# Search in worms records Not found in gbif
+#
+
+dfn <- class_list[[2]]$Taxon
+
+clasall <- classification(dfn, db = 'worms') #
+
+class_list <- class_to_df(clasall)
+
+tmp_df <- class_list[[1]]
+names(tmp_df) <- tolower(names(tmp_df))
+names(tmp_df)[1] <- "Taxon"
+dfn <- class_list[[2]]$Taxon
+names(classall_df)
+classall_df <- bind_rows(classall_df,tmp_df)
+saveRDS(classall_df,file="Data/WeddellSea_clasification.rds")
+
+search_value <- "foram"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+
+search_value <- "Hexactinellida"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+
+search_value <- "Bacillariophyceae"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+
+dtot1 <- replace_nodes(dtot, result, "class")
+collapsed_w <- dtot1 %>% distinct()
+gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)
+
+degree(gM)["Bacillariophyceae"]
+degree(gM)["Pleuragramma antarcticum"]
+require(NetIndices)
+a <- get.adjacency(gM,sparse=F)
+tl <- TrophInd(a)
+tl[rownames(tl)=="Pleuragramma antarcticum",]
+tl[rownames(tl)=="Pygoscelis adeliae",]
+trophiclevels(gM)
+search_value <- "Chromista"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+
+search_value <- "Dictyocha"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+```

### 2023-08-23 R/functions.R
add functions.R

@@ -1,0 +1,51 @@
+
+class_to_df <- function(class_obj) {
+  # Create an empty data.frame
+  classall_df <- tibble()
+  not_found_df <- tibble()
+  # Iterate over the list of taxa
+  for (taxon in names(class_obj)) {
+    # Check if the taxon has classification information
+    if (!is.null(nrow(class_obj[[taxon]]))) {
+      # Extract the classification data.frame for the taxon
+      df <- class_obj[[taxon]]
+      
+      # Add a column to the data.frame indicating the taxon name
+      df$Taxon <- taxon
+      
+      # Bind the current data.frame to the overall data.frame
+      classall_df <- bind_rows(classall_df, df)
+    } else {
+      df <- tibble(Taxon = taxon)
+      not_found_df <- bind_rows(  not_found_df, df)
+    }
+  }
+  
+  # Pivot the data.frame to have unique 'rank' values as separate columns
+  classall_df <- classall_df %>% select(-id )%>%
+    pivot_wider(names_from = rank, values_from = name)
+  
+  return(list(classall_df,not_found_df))
+}
+
+#
+# Replace into dtot, the values of result$class
+#
+replace_nodes <- function(dtot,result,field){
+  sapply( 1:nrow(dtot), function(i) {
+    res_gen <- dtot$resource[i]
+    rep_cla <- result %>% filter(Taxon == res_gen) 
+    if(nrow(rep_cla)==1){
+      print(paste(dtot$resource[i],rep_cla[field] ))
+      dtot$resource[i] <<- unlist(rep_cla[field])
+    }
+    res_gen <- dtot$consumer[i]
+    rep_cla <- result %>% filter(Taxon == res_gen) 
+    if(nrow(rep_cla)==1){
+      print(paste(rep_cla[field], dtot$consumer[i] ))
+      dtot$consumer[i] <<- unlist(rep_cla[field])
+    }
+    
+  })
+  return(dtot)
+}

### 2023-08-25 WeddellSea_collapse.Rmd
Many changes

--- 2023-08-03 FoodWebsCheck.Rmd
@@
 write_csv(collapsed_w,"Data/Weddell_collapsed_links.csv")
+
+collapsed_w <- read_csv("Data/Weddell_collapsed_links.csv")
+
 ```
+
+# Weddell Sea get full classification
+
+```{r, WeddellSeaFullClass, eval=F,echo=F,message=T,warning=T}
+require(tidyverse)
+require(igraph)
+#
+# Auxiliary functions
+#
+source("R/functions.R")
+
+#
+# Food-web data 
+#
+dtot <- read_csv("Data/WeddellSea_links_original.csv")
+
+if( file.exists("Data/WeddellSea_clasification.rds")) {
+
+  classall_df <- readRDS("Data/WeddellSea_clasification.rds")
+
+} else {
+
+  # Read complete clasification from Taxonomic databases
+  #
+  require(taxize)
+  dfn <- unique(dtot$consumer)
+  dfn <- c(dfn, unique(dtot$resource))
+  dfn <- unique(dfn)
+
+  # CLasificación completa
+
+  clasall <- classification(dfn, db = 'gbif') #
+
+  class_list <- class_to_df(clasall)
+
+  classall_df <- class_list[[1]]
+
+  #
+  # Search in worms records Not found in gbif
+  #
+
+  dfn <- class_list[[2]]$Taxon
+
+  clasall <- classification(dfn, db = 'worms') #
+
+  class_list <- class_to_df(clasall)
+
+  tmp_df <- class_list[[1]]
+  names(tmp_df) <- tolower(names(tmp_df))
+  names(tmp_df)[1] <- "Taxon"
+  dfn <- class_list[[2]]$Taxon
+  names(classall_df)
+  classall_df <- bind_rows(classall_df,tmp_df)
+  saveRDS(classall_df,file="Data/WeddellSea_clasification.rds")
+}
+
+# Search in any field of the df
+#
+search_value <- "foram"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+
+# Replace the species nodes contained in `result` to the value of the field result$class 
+# to obtain the degree of the collapsed node
+#
+search_value <- "Hexactinellida"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+dtot1 <- replace_nodes(dtot, result, "class")
+collapsed_w <- dtot1 %>% distinct()
+gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)
+
+degree(gM)[search_value]
+
+# Replace the species nodes contained in `result` to the value of the field result$class 
+# to obtain the degree of the collapsed node
+#
+search_value <- "Bacillariophyceae"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+
+dtot1 <- replace_nodes(dtot, result, "class")
+collapsed_w <- dtot1 %>% distinct()
+gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)
+
+degree(gM)["Bacillariophyceae"]
+degree(gM)["Pleuragramma antarcticum"]
+require(NetIndices)
+a <- get.adjacency(gM,sparse=F)
+tl <- TrophInd(a)
+tl[rownames(tl)=="Pleuragramma antarcticum",]
+tl[rownames(tl)=="Pygoscelis adeliae",]
+trophiclevels(gM)
+
+search_value <- "Chromista"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+
+search_value <- "Dictyocha"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+```

### 2023-09-18 WeddellSea_collapse.Rmd
Changes

@@
 require(tidyverse)
+
+source("R/functions.R")
 
@@
 ```
+
+# Check Proportion of Stable Webs based on @Gross2009
+
+```{r}
+fwn <- c("BeagleChannel_links_original.csv",
+                  "BurdwoodBank_links_original.csv",
+                  "GulfSanJorge_links_original.csv",
+                  "NorthernScotia_links_original.csv",
+                  "SouthernScotia_links_original.csv",
+                  "WeddellSea_links_original.csv")
+fwn <- file.path("Data",fwn)
+fw <- multiweb::readNetwork(fwn)
+
+df_fw <- calc_topological_indices(fw)
+
+df_fw <- df_fw %>% mutate(PSW=calculate_psw(Connectance,Size)$PSW)
+
+ggplot(df_fw, aes(x = Connectance*Size, y = log(PSW))) +
+  geom_point() +
+  labs(x = "C * N", y = "PSW") +
+  theme_classic()
+
+node_to_remove <- "Euphausia superba"
+node_index <- which(V(fw[[6]])$name == node_to_remove)
+  food_web <- delete.vertices(fw[[6]], node_index)
+calc_topological_indices(list(food_web,fw[[6]])) %>% mutate(PSW=calculate_psw(Connectance,Size)$PSW)
+
+```

### 2023-09-18 R/functions.R

@@ -49,3 +49,19 @@ replace_nodes <- function(dtot,result,field){
   })
   return(dtot)
 }
+
+# Define a function to calculate PSW
+# the proportion of stable webs based on
+# @Gross2009
+calculate_psw <- function(C, N) {
+  a <- 0.2090
+  b <- -7.025
+  c_param <- 3.138
+  x <- log10(C * N)
+  psw <- 10^(b * x^c_param - a)
+
+    
+  df <- tibble(C = C, N = N, PSW = psw)
+  return(df)
+}
+

### 2023-09-28 WeddellSea_collapse.Rmd
Updated ms

@@
 
+require(NetIndices)
+a <- get.adjacency(gM,sparse=F)
+tl <- TrophInd(a)
+tl[rownames(tl)==search_value,]
+
 # Replace the species nodes contained in `result` to the value of the field result$class 
@@
 
-search_value <- "Dictyocha"
+search_value <- "Foraminifera"
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+dtot1 <- replace_nodes(dtot, result, "phylum")
+collapsed_w <- dtot1 %>% distinct()
+gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)
+degree(gM)[search_value]
+
+a <- get.adjacency(gM,sparse=F)
+tl <- TrophInd(a)
+tl[rownames(tl)==search_value,]
+
+search_value <- "Dictyocha" # Sillicoflagelados
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+degree(gM)[result$Taxon]
+tl[rownames(tl)==result$Taxon,]
+
+search_value <- "Silico" # Sillicoflagelados
+result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
+degree(gM)[result$Taxon]
+
+search_value <- "Cryptophy" # Cryptophyta -------------> NO HAY
 result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))

### 2023-09-29 manuscript.tex
Add manuscript Latex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[vmargin=1in,hmargin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}

\usepackage{pdflscape,booktabs}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage[running]{lineno}
\linenumbers
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\hypertarget{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}{%
\section{The response of trophic interaction networks to multiple
stressors in a marine latitudinal gradient of the Southern
Hemisphere}\label{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}}

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Ecological networks are increasingly used as conceptual frameworks for
  understanding ecological community structure, identifying key species,
  and for ecosystem management and biodiversity conservation. Nowadays,
  there is a growing interest in understanding how ecological networks
  respond to environmental and anthropogenic stressors along
  geographical gradients.
\item
  We review for the first time the state-of-the-art knowledge on
  stressor response of marine food webs along the southwest Atlantic to
  Antarctic gradient (45 - 78ºS), considering the following study areas:
  San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea, Potter Cove
  (Antarctica) and Weddell Sea (Antarctica). The aim of this review is
  threefold: 1) describe the complexity and structure of marine food
  webs along the southwest Atlantic to Antarctic axis from a network
  perspective; 2) identify the ongoing environmental and anthropogenic
  stressors for each marine ecosystem containing the food webs; and 3)
  resume proven food web changes and elaborate hypotheses on how the
  identified stressors might affect food web features, combining
  information on node- and network-level properties.
\item
  Environmental and anthropogenic stressor effects in the study gradient
  have been mostly assessed individually and at the organism and/or
  population, i.e., at the node level, with one exception: the effect of
  fisheries in the San Jorge Gulf food web. To address the most
  plausible stressors effects on the selected food webs, we built
  hypotheses for each study area considering the following: a)
  stressor(s), b) parameter(s) affected, c) node-level properties of the
  affected species, and d) network-level properties of the food web.
\item
  The most common stressor reported along the gradient is global
  warming, except for Beagle Channel and Burdwood Bank, which are more
  influenced by the introduction of an alien species and fisheries,
  respectively. We provide particular hypotheses on how warming might
  impact food webs.
\item
  We demonstrate the advantages of applying a network approach to better
  understand and predict the effect of stressors in marine ecosystems of
  the Southern Hemisphere.
\end{enumerate}

Keywords: anthropogenic stressors, environmental stressors, food webs,
latitudinal gradient, Southern Hemisphere

\hypertarget{introduction}{%
\subsection{1. Introduction}\label{introduction}}

The application of a network perspective has emerged as a powerful tool
to tackle the complexity of species interactions, facilitating a better
understanding of the structure and functioning of ecosystems (Belgrano,
Scharler, Scharler, Dunne, \& Ulanowicz, 2005; Thompson et al., 2012;
D'Alelio, Libralato, Wyatt, \& Ribera d'Alcalà, 2016). Trophic networks
(or food webs) allow identifying properties and key species that may be
crucial for ecosystem stability, and hence important for ecosystem
management and biodiversity conservation (Thompson et al., 2012). There
is a growing interest in understanding how ecological networks respond
to environmental and anthropogenic stressors along geographical
gradients (Baiser, Gotelli, Buckley, Miller, \& Ellison, 2012; Cirtwill,
Stouffer, \& Romanuk, 2015; Strydom et al., 2021; Bauer et al., 2022).
Yet, only a few studies have described variation in food web structure
along latitudinal gradients in marine ecosystems. The few that have come
from the Global North (Wood, Russell, Hanson, Williams, \& Dunne, 2015;
Kortsch et al., 2019; Frelat et al., 2022; Pecuchet et al., 2022),
whereas no studies, nor meta-analyses, on geographical variation in
marine food webs exist for the Global South (Southern Hemisphere).

Here we review for the first time the state-of-the-art knowledge on
stressor response of marine food webs along the southwest Atlantic to
Antarctic gradient (45 - 78ºS, Figure 1). We focus on proven and
expected changes in food webs driven by stressors in selected areas
along this large-scale latitudinal gradient. The aim of this review is
threefold: 1) describe the complexity and structure of marine food webs
along the southwest Atlantic to Antarctic axis from a network
perspective; 2) identify the ongoing environmental and anthropogenic
stressors for each marine ecosystem containing the food webs; and 3)
resume proven food web changes and elaborate hypotheses on how the
identified stressors might affect food web features (e.g.~energy flow,
stability), combining information on node- and network-level properties.
Finally, we suggest which additional data and analyses are needed to
gain insights into the stressors' effects on food web properties in the
southwest Atlantic to Antarctic region.

\hypertarget{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}{%
\subsection{2. The structure of marine food webs in the Southwest
Atlantic - Antarctic
region}\label{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}}

Together, the southwest and the Atlantic sector of the Southern Ocean
comprise one of the most biologically productive regions of the world's
oceans (Acha, Mianzan, Guerrero, Favero, \& Bava, 2004; Whitehouse et
al., 2008; Ballerini et al., 2014; Latorre et al., 2023). The referred
region extends from San Jorge Gulf (45ºS) in the Patagonian shelf to the
Weddell Sea (78ºS) in the Southern Ocean, and covers a well-connected
oceanic latitudinal gradient (R. P. Matano, Palma, \& Piola, 2010;
Steele, Thorpe, \& Turekian, 2010; Guihou, Piola, Palma, \& Chidichimo,
2020).

Throughout this latitudinal gradient, many investigations have been
carried out addressing the trophic ecology of specific species and
prey-predator relationships (Vinuesa \& Varisco, 2007; Sailley et al.,
2013; Pasotti et al., 2015; Riccialdelli, Newsome, Fogel, \& Fernández,
2017; Saunders, Hill, Tarling, \& Murphy, 2019; Riccialdelli et al.,
2020), but few studies have considered the complexity of the ecosystem
in terms of a high resolution of species and their prey-predator
interactions (but see Jacob et al. (2011), Marina et al. (2018), Funes,
Saravia, Cordone, Iribarne, \& Galván (2022), López-López, Genner,
Tarling, Saunders, \& O'Gorman (2022), Rodriguez, Marina, Schloss, \&
Saravia (2022), Marina et al. (in rev.)). Neglecting this complexity
might lead to a misunderstanding of the structure and functioning of the
ecosystems, and ultimately reduce the ability to predict ecosystem
responses to perturbations (Montoya, Woodward, Emmerson, \& Solé, 2009;
Woodward et al., 2010).

In this review, we consider marine areas in the Southern hemisphere for
which highly-resolved empirical food webs, in terms of species diversity
and trophic interactions, have been previously described. These areas
include: (1) San Jorge Gulf (45 - 47ºS, 65 - 68ºW), (2) Beagle Channel
(\textasciitilde54ºS, 68ºW), (3) Burdwood Bank (\textasciitilde54ºS,
59ºW), (4) Scotia Sea (48 - 58ºS, 50ºW), (5) Potter Cove (62ºS, 58ºW,
Antarctica), and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica) (Figure
1). The geographic locations of these marine biomes span from temperate
to Antarctic, and are exposed to both environmental (sea warming,
glacial retreat) and anthropogenic (fishery, pollution) stressors.

\begin{figure}
\centering
\includegraphics[width=6.27in,height=3.528in]{Figures/Map_final.jpg}
\caption{Map of the study areas along the southwest Atlantic - Antarctic
latitudinal gradient. The areas are marked with numbers from one to six.
Smaller areas (1. San Jorge Gulf, 2. Beagle Channel, 3. Burdwood Bank,
and 5. Potter Cove) are shown on the panels to the left, whereas the
larger areas (4. North and South Scotia Sea, and 6. Weddell Sea) are
marked with a red rectangle on the map. The map was drawn using the
`marmap' R package (Pante, Simon-Bouhet, \& Irisson, 2023). Continental
contour shapefiles were obtained from www.ign.gob.ar.}
\end{figure}

San Jorge Gulf is the northernmost study area considered in this review.
It is a partially enclosed basin spanning approximately 34,000 km2 and
\textasciitilde100 m of maximum depths, located from Cabo dos Bahias
(44°55'S) to Cabo tres Puntas (47°06'S) (Figure 1). The shallower
northern and southern ends of the Gulf (with depths \textasciitilde40 m)
present two prominent frontal systems. These systems are the areas of
highest productivity (Bogazzi et al., 2005; Glembocki, Williams,
Góngora, Gagliardini, \& Orensanz, 2015). The Gulf's productivity
supports large invertebrate and vertebrate fisheries (María Eva Góngora,
González-Zevallos, Pettovello, \& Mendía, 2012), as well as marine
mammal and seabird populations (Yorio, 2009). The San Jorge Gulf food
web comprises 165 nodes and 1015 trophic interactions with a connectance
of 0.04. The percentage of top predators is 16\%, 78\% of intermediate
nodes and 6\% of basal nodes; 60\% of predators are omnivorous (Table
1). The most connected nodes are: the Argentine red shrimp Pleoticus
muelleri, the squat lobster Gimothea gregaria, squids (Illex argentinus
as dominant species) and Amphipoda. Notably, these nodes present
mid-trophic positions in the food web (3.0, 2.5, 3.6 and 2,
respectively) (Funes et al., 2022).

At a southern latitude, the Beagle Channel (54°52'S, 68°8'W) is an
interoceanic passage located at the southernmost tip of South America,
spanning 240 km in length and 5 km in width (\textasciitilde1200 km2),
and a range depth of 0 - 140 m (Figure 1). It features complex
coastlines, varying bathymetry, a prevailing west-to-east circulation
pattern, and a significant longitudinal gradient of glacial freshwater
discharge (Schloss et al., 2023). Bruno, Riccialdelli, Acha, \&
Fernández (2023) suggests that locally produced suspended particulate
organic matter (mostly composed by phytoplankton) and organic matter
accumulated in the sediments (macroalgae-originated detritus) are the
primary food sources for the marine ecosystem, as opposed to
allochthonous materials. Beagle Channel food web includes 145 nodes and
1115 trophic interactions with a connectance of 0.05 (Table 1). The food
web is suggested to have a wasp-waist structure, where the following
species play a crucial role in the dynamics of the ecosystem: Fueguian
sprat Sprattus fuegensis, longtail southern cod Patagonotothen ramsayi,
black southern cod P. tessellata, frogmouth Cottoperca trigloides, and
squat lobster Grimothea gregaria (Riccialdelli et al., 2020). Moreover,
the squat lobster has been identified as a species responsible for
linking modules and connecting the entire food web (Rodriguez et al.,
2022).

The so-called Burdwood Bank ecosystem comprises Marine Protected Areas
Namuncurá - Burdwood Bank I and II, meaning the shallow submarine
plateau named Burdwood Bank with a 200 m isobath boundary, and a deep
slope that reaches 4000 m in depth, respectively (Tombesi, Rabufetti, \&
Lovrich, 2020; Administración de Parques Nacionales, 2022) (Figure 1).
Physical features in the plateau are fairly stable, with salinity
averaging 34 all year round and temperature ranging between 4 and 8ºC
(Acha et al., 2004; Piola \& Falabella, 2009). The plateau is surrounded
by steep flanks of up to 4000 m depth, protected by the Marine Protected
Area Namuncurá - Burdwood Bank II (32,000 km2; \textasciitilde55º -
56ºS, \textasciitilde58º - 62ºW). Intense upwelling and mixing occur in
relation to the slope, entraining deep nutrient-rich waters into the
photic layer (Piola \& Falabella, 2009; Ricardo P. Matano, Palma, \&
Combes, 2019), and resulting in a fairly homogeneous water column both
spatially and temporally (Glorioso \& Flather, 1995; Ricardo P. Matano
et al., 2019). The Burdwood Bank food web comprises 379 nodes and 1788
interactions, with a connectance of 0.01, and an asymmetric degree
distribution (i.e.~most of the species have a relatively low number of
interactions and few species concentrate most of them). Almost half of
the consumers are omnivores (0.48), and the network displays a
small-world pattern (Marina et al., in rev.) (Table 1).

The Scotia Sea is a deep-sea basin, delimited by the Drake Passage to
the West and by the island complex of the Scotia Arc to the North, East,
and South, with an approximate extension of 1.5 x 106 km2 and a depth
range of 0 - 3000 m (E. j. Murphy et al., 2006) (Figure 1). Its
oceanography is dominated by the Antarctic Circumpolar Current, which is
spatially structured by frontal systems (Whitworth, 1980). The South
Antarctic Circumpolar Current Front subdivides the Scotia Sea into two
biogeographic regions: the Northern Scotia Sea is characterized by
higher and more variable temperatures, and the Southern Scotia Sea by
lower and more stable temperatures and influenced by seasonal sea ice
(Raymond, 2011). The analysis of the Northern and Southern Scotia Sea
food webs shows that the former is relatively more complex than the
latter: with higher species richness (218 vs 192) and interactions
(10008 vs 7241) and a higher connection overall (0.21 vs 0.20). As
expected from a more complex network, the path length is shorter in the
Northern Scotia Sea food web. In the same sense, the Southern Scotia Sea
network displays a greater proportion of omnivores and a lower mean
trophic level (López-López et al., 2022) (Table 1).

In the Antarctic realm, Potter Cove is a \textasciitilde9 km2 fjord with
a depth range of 0 - 200 m located at 25 de Mayo/King George Island
(62°14'S, 58°38'W, South Shetland Islands) on the West Antarctic
Peninsula (Figure 1). The cove, bordered by the Fourcade Glacier, is
divided into three areas: a) the internal cove, a high
glacier-influenced, soft sediment zone with a 50 m maximum depth; b) the
central cove, a mixed substrate area with low meltwater influence and an
80 m maximum depth; and c) the external cove, ice-free for 60 years with
a 185 m maximum depth and rocky substrate (Jerosch et al., 2018; Neder
et al., 2022; Neder, 2023). Potter Cove's high-latitude location results
in variable environmental conditions due to photoperiod length
seasonality. Sea ice often covers this area in winter (Schloss et al.,
2012). With low phytoplankton biomass, macroalgae, and microphytobenthos
are likely the primary food sources for secondary benthic production (M.
L. Quartino \& Boraso de Zaixso, 2008). The Potter Cove food web
includes 110 nodes and 649 interactions, with an asymmetric degree
distribution, and a connectance value of 0.05 (Table 1). It presents a
modular structure (groups of species interact more strongly with each
other than with species belonging to other groups), that's positively
associated with stability, since perturbation can be retained within
modules (Rodriguez et al., 2022).

Located between 74 and 78ºS, the high Antarctic Weddell Sea shelf spans
approximately 450 km from East to West (Jacob et al., 2011) (Figure 1).
The water depth ranges from 200 to 500 m, with shallower regions being
covered by continental ice that forms the coastline along the eastern
and southern parts of the Weddell Sea. Within this shelf area, exists a
complex three-dimensional benthic habitat characterized by substantial
benthic biomasses and an intermediate to high diversity when compared to
benthic boreal communities (Dayton, 1990; Teixidó, Garrabou, \& Arntz,
2002). The Weddell Sea food web exhibits a high level of network
complexity, featuring the greatest number of nodes (490) and trophic
interactions (16041) among the analyzed food webs in this review (Table
1). Its connectance (0.07) and other structural properties are
intermediate compared to the other food webs. Recently, the interaction
strengths of this food web were estimated, revealing the presence of
numerous weak and few strong interactions, which is consistent with
findings in other complex food webs (McCann, Hastings, \& Huxel, 1998;
Nilsson \& McCann, 2016). Notably, this asymmetric distribution of
interaction strength is likely to promote community persistence.

\footnotesize

Table 1. Complexity and structure properties of the marine food webs
considered in the present review. Refer to Table 3 for definition of
properties. mean TL: mean trophic level. Food webs are ordered by
increasing latitude.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1538}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0839}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0839}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1259}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1259}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0979}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1049}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.2238}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Food web}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Nodes}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Links}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Connectance}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Path length}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{mean TL}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Omnivory}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Reference}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
San Jorge Gulf & 165 & 1015 & 0.04 & 2.17 & 3.02 & 0.63 & Funes et al.
(2022) \\
Beagle Channel & 145 & 1115 & 0.05 & 2.12 & 2.37 & 0.55 & Rodriguez et
al. (2022) \\
Burdwood Bank & 379 & 1788 & 0.01 & 2.99 & 2.52 & 0.49 & Marina et al.
(in rev.) \\
Potter Cove & 110 & 649 & 0.05 & 2.33 & 2.22 & 0.46 & Marina et al.
(2018); Rodriguez et al. (2022) \\
N Scotia Sea & 218 & 10008 & 0.21 & 1.87 & 3.29 & 0.73 & López-López et
al. (2022) \\
S Scotia Sea & 192 & 7241 & 0.20 & 1.90 & 3.21 & 0.71 & López-López et
al. (2022) \\
Weddell Sea & 490 & 16041 & 0.07 & 2.19 & 2.62 & 0.51 & Jacob et al.
(2011) \\
\end{longtable}

\normalsize

\hypertarget{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}{%
\subsection{3. Environmental and anthropogenic stressors in the
Southwest Atlantic - Antarctic
region}\label{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}}

A stressor is any environmental or anthropogenic variable that causes a
quantifiable change, irrespective of its direction (increase or
decrease), in a biological response (Côté, Darling, \& Brown, 2016; Orr
et al., 2020). In the light of this, the southwest Atlantic - Antarctic
marine biota has been and is currently subjected to a variety of
stressors (e.g.~sea warming, glacial retreat, ice changes,
acidification, species invasion, fisheries, and contamination). Although
it is well-known that multiple stressors act in concert at any given
time (e.g.~warming and fishery; acidification and contaminants) (Julian
Gutt et al., 2015, 2021), to date stressor assessments have been
performed individually. Moreover, the potential for interactive effects
of two or more stressors (synergy or antagonism) (Crain, Kroeker, \&
Halpern, 2008; Côté et al., 2016) is almost unknown for the region
(Rowlands et al., 2021).

In the following subsections, we describe the main environmental and
anthropogenic stressors, and the species (or trophic species) and
parameters affected reported for the marine ecosystems that contain the
food webs considered in this review. In Table 2 we provide an exhaustive
list of all stressors affecting species inhabiting each area,
considering: the type of stressor, species and parameter affected, and
locality.

\newpage
\begin{landscape}
\scriptsize

Table 2. Environmental and anthropogenic stressors reported for the
study areas: San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea
(North and South), Potter Cove, and Weddell Sea. Stressor categories:
sea warming; glacial retreat; sediment in the water column; iceberg
scouring; sea ice extent; ocean acidification; ocean acidification +
plastics; microplastics; mercury; urban \& industrial pollution;
fishery; alien species. The species affected were considered at the node
level, whereas effects were considered at the organism and population
levels. Categories of affected parameters and variables: metabolism;
biomass; distribution; diet (see text for explanation). ``Locality''
indicates whether a stressor for a given species was reported for the
study area (`In situ') or in another area (`Elsewhere').

\begin{longtable}{ L{2.1cm} L{2.5cm} L{4cm} L{2.5cm} L{2cm} L{3cm} }
\hline
\textbf{Study area} & \textbf{Stressor} & \textbf{Species affected} & \textbf{Parameter affected} & \textbf{Locality} & \textbf{Reference} \\
\hline
\endhead
\endfoot
\hline
\endlastfoot
\textbf{San Jorge Gulf} & & & & & \\
& Sea warming & Fish assemblage \& its prey & Distribution & In situ &
Galván et al. (2022) \\
& Fishery & Demersal fish community & Biomass & In situ & Galván et al.
(2022) \\
& Fishery & Macroinvertebrates, fishes and seabirds & Diet & In situ &
González-Zevallos \& Yorio (2006); González-Zevallos \& Yorio (2011);
Yorio, González-Zevallos, Gatto, Biagioni, \& Castillo (2017) \\
& Alien species & Fish assemblage \& its prey & Distribution & In situ &
Galván et al. (2022); J. Ciancio, Beauchamp, \& Pascual (2010) \\
& Urban \& industrial pollution & Seabirds \& benthic assemblage &
Biomass & Elsewhere & Moore \& Dwyer (1974); Buskey, White, \& Esbaugh
(2016) \\
\textbf{Beagle Channel} & & & & & \\
& Urban \& industrial pollution & Macroalgae; Mytilus edulis chilensis,
Patagonotothen tessellata & Metabolism & In situ & Giarratano \& Amin
(2010); Ferreira, Lo Nostro, Fernández, \& Genovese (2021); Kaminsky et
al. (in prep.) \\
& Mercury & Phytoplankton, Zooplankton, \emph{Grimothea gregaria} &
Metabolism & In situ & Fioramonti, Ribeiro Guevara, Becker, \&
Riccialdelli (2022) \\
& Microplastics & Mytilus edulis chilensis, Nacella magellanica &
Metabolism & In situ & Analía F. Pérez et al. (2020); Ojeda et al.
(2021) \\
& Alien species: Chinook salmon Oncorhynchus tshawytscha &
Patagonotothen tessellata, Sprattus fuegensis & Diet/Biomass & In situ
(the presence), Elsewhere (changes in prey biomass) & Fernández,
Ciancio, Ceballos, Riva-Rossi, \& Pascual (2010); J. E. Ciancio,
Pascual, Botto, Frere, \& Iribarne (2008) \\
\textbf{Burdwood Bank} & & & & & \\
& Mercury & Dissostichus eleginoides, Sprattus fuegensis, Patagonotothen
ramsayi, Cottoperca trigloides (fishes) \& squids & Metabolism & In situ
& Fioramonti et al. (2022) \\
& Microplastics & Henricia obesa \& Odontaster penicillatus (sea stars);
Patagonotothen guntheri \& P. ramsayi (fishes) & Metabolism & In situ &
Cossi et al. (2021); A. F. Pérez et al. (2021) \\
& Fishery & Target: Dissostichus eleginoides. Bycatch: Macrourus sp.,
Coelorinchus sp. (fishes), Daption capense, Thalassarche melanophris,
Macronectes giganteus, T. chrysostoma, Diomedea epomophora (seabirds),
30+ spp macrobenthos & Biomass & Elsewhere & Gaitán \& Marí (2016);
Patricia A. Martínez, Wöhler, Troccoli, Di Marco, \& Maydana (2022);
Administración de Parques Nacionales (2022); Tamini et al. (2023) \\
& Fishery & Thalassarche melanophris, Macronectes giganteus, Daption
capense, Diomedea epomophora, M. halli, Procellaria aequinoctialis
(seabirds) & Diet & Elsewhere & Tamini et al. (2023) \\
\textbf{Scotia Sea, North \& South} & & & & & \\
& Mercury & Krefftichthys anderssoni, Protomyctophum bolini, Electrona
antarctica, Gymnoscopelus nicholsi, Gymnoscopelus braueri, Dissostichus
eleginoides & Metabolism & In situ & Seco et al. (2021) \\
& Ocean acidification + plastics & Euphausia superba, Limacina
retroversa (Pteropoda) & Metabolism & In situ & Rowlands et al. (2021);
Manno, Peck, Corsi, \& Bergami (2022) \\
& Sea warming & Euphausia superba & Metabolism & In situ & E. J. Murphy
et al. (2007); Perry et al. (2020) \\
& Sea warming & Euphausia superba & Distribution & In situ & Atkinson et
al. (2019) \\
& Fishery & Euphausia superba & Biomass & In situ & P. N. Trathan et al.
(2021) \\
\textbf{Potter Cove (Antarctica)} & & & & & \\
& Sediment in water column & Microphytobenthos, macroalgae, benthic
filter feeders (ascidians), pelagic filter feeders (krill, salps) &
Metabolism & In situ & Sahade et al. (2015); D. Deregibus et al. (2016);
Fuentes et al. (2016); Hoffmann et al. (2019) \\
& Sea ice extent & Krill & Biomass & Elsewhere & Flores et al. (2012) \\
& Sea ice extent & Benthic community (macroalgae, invertebrates) &
Metabolism & Elsewhere & Clark et al. (2013); Campana et al. (2018) \\
& Glacial retreat & Benthic community (macroalgae, invertebrates) &
Biomass & In situ & María Liliana Quartino, Deregibus, Campana, Latorre,
\& Momo (2013); Lagger, Servetto, Torre, \& Sahade (2017); Lagger et al.
(2018) \\
& Iceberg scouring & Benthic community & Biomass & In situ & D.
Deregibus, Quartino, Zacher, Campana, \& Barnes (2017); Dolores
Deregibus et al. (2023) \\
& Sea warming & Phytoplankton & Metabolism, biomass & In situ & Antoni
et al. (2020); Latorre et al. (2023) \\
& Sea warming & Zooplankton & Metabolism, biomass, diet & In situ &
Garcia et al. (2016); Garcia et al. (2019) \\
& Sea warming & Fish & Metabolism & In situ, elsewhere & Strobel, Leo,
Pörtner, \& Mark (2013); Souza et al. (2018); Saravia et al. (2021) \\
\textbf{Weddell Sea (Antarctica)} & & & & & \\
& Iceberg scouring & Macrobentos & Biomass & In situ & Isla (2023);
Julian Gutt et al. (2015); Dan A. Smale, Brown, Barnes, Fraser, \&
Clarke (2008); J. Gutt, Starmans, \& Dieckmann (1996) \\
& Iceberg scouring & Hexactinellida sponges & Biomass & In situ & Julian
Gutt \& Starmans (2001); Pineda-Metz, Gerdes, \& Richter (2020); Julian
Gutt (2001); Julian Gutt \& Piepenburg (2003) \\
& Ocean acidification & Primary producers / krill / foraminifera /
flagellates & Metabolism & Elsewhere & Deppeler et al. (2020); Isla
(2023); Julian Gutt et al. (2015); Moy, Howard, Bray, \& Trull (2009) \\
& Ocean acidification & Euphausia superba, Pleuragramma antarcticum &
Metabolism & In situ & So Kawaguchi et al. (2010); S. Kawaguchi et al.
(2013); Piñones \& Fedorov (2016); Mintenbeck et al. (2012) \\
& Sea warming & Large (diatoms) \& small (cryptophytes) phytoplankton,
zooplankton (salps) & Metabolism & Elsewhere & Isla (2023); Julian Gutt
et al. (2015); Trebilco, Melbourne-Thomas, \& Constable (2020) \\
& Sea warming & Euphausia superba, Nototheniid fishes, Pleuragramma
antarcticum & Metabolism & In situ & Meyer et al. (2017); Hill,
Phillips, \& Atkinson (2013); Mintenbeck et al. (2012); Constable et al.
(2014); Mintenbeck et al. (2012) \\
& Sea ice extent & Phytoplankton, Lobodon carcinophaga, Hydrurga
leptonyx, Leptonychotes weddellii, Ommataphoca rossii, Mirounga leonina,
Arctocephalus gazella & Metabolism & In situ & Pineda-Metz et al.
(2020); Wege, Salas, \& LaRue (2021); Siniff, Garrott, Rotella, Fraser,
\& Ainley (2008) \\
& Sea ice extent & Euphausia superba, Pleuragramma antarcticum,
Pagodroma nivea, Thalassoica antarctica, Pygoscelis adeliae & Metabolism
& In situ & Orgeira, Alvarez, \& Salvó (2021); Braithwaite, Meeuwig,
Letessier, Jenner, \& Brierley (2015); Hill et al. (2013); Mintenbeck et
al. (2012) \\
& Sea ice extent & Megaptera novaeangliae & Metabolism & Elsewhere &
Pallin et al. (2023) \\
& Sea ice extent & Aptenodytes forsteri & Metabolism & Elsewhere &
Orgeira et al. (2021) \\
\end{longtable}

\end{landscape}
\normalsize

\hypertarget{san-jorge-gulf}{%
\subsubsection{3.1 San Jorge Gulf}\label{san-jorge-gulf}}

San Jorge Gulf experienced several environmental and anthropogenic
stressors (Table 2). Trawl fisheries discard several species and add new
trophic interactions to the food web which resulted in a decrease in
trait variability and the stability of the system (Rincón-Díaz, Bovcon,
Cochia, Góngora, \& Galván, 2021; Funes et al., 2022). Moreover, it
changed the availability of prey to several predators. For example,
Merluccius hubbsi one of the main bycatch species, became prey item to
non-diving seabirds, like the kelp gull Larus dominicanus
(González-Zevallos \& Yorio, 2006) and reef fishes (Funes, Marinao, \&
Galván, 2019). Although juveniles of M. hubbsi are largely the main
bycatch item, 29 other cartilaginous and 69 bony local fish species were
also registered as incidental catch between 2005 and 2014 (María E.
Góngora, Bovcon, \& Cochia, 2009; Bovcon, Góngora, Marinao, \&
González-Zevallos, 2013; Ruibal Nuñez, 2020). This level of impact
triggered a shift in the functional diversity of the assemblages
homogenizing the trophic function of fishes (Rincón-Díaz et al., 2021).
Other functional changes were a decrease in the maximum sizes of
individual fish, together with a drop in elasmobranchs biomass and an
increase in crustaceans biomass (Funes, 2020). The significant increase
in crustacean biomass was mostly due to the increase in Pleoticus
muelleri and Grimothea gregaria populations (Funes, 2020). These species
rapidly became the most important prey for the most abundant fishes in
the area: M. hubbsi and Mustelus schmitti (Belleggia, Giberto, \&
Bremec, 2017; Pasti et al., 2021). However, the above-mentioned effects
of trawl fisheries on the structure and function of the San Jorge Gulf
community may have changed again, since the fisheries ceased activity in
2015 (Annex I, Resolution CFP No 7/2018), remaining a minimum of
artisanal activity.

Sea warming is another important environmental stressor in the San Jorge
Gulf, because of the southward shifts of northern fish populations to
the Gulf (Galván et al., 2022). The San Jorge Gulf is especially prone
to be affected by climate-driven shifts in species ranges, because it is
located in the ecotone between two biogeographic provinces, the
Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) (Balech \&
Ehrlich, 2008). In addition to this tropicalization from northern fish
populations, alien species are also documented to affect the demersal
assemblage (fish and macroinvertebrates) in the Gulf (Vinuesa, 2005 ;
Galván et al., 2022). Finally, San Jorge Gulf is exposed to urban and
industrial pollution due to an oil monobuoy from which oil manipulation
and general oil transport along the Patagonian coast registered several
oil spills and chronic oil discharges (García-Borboroglu, Boersma,
Reyes, \& Skewgar, 2008). Other marine systems impacted by oil spill
showed an important decrease in marine bird populations (Irons, Kendall,
Erickson, McDonald, \& Lance, 2000), seals and macroalgae (e.g. Garrott,
Eberhardt, \& Burn (1993); Paine et al. (1996)), with examples of
cascading effects throughout the food web (Paine et al., 1996; Peterson,
2001).

\hypertarget{beagle-channel}{%
\subsubsection{3.2 Beagle Channel}\label{beagle-channel}}

A main anthropogenic stressor in the Beagle Channel is the introduction
of invasive species (Table 2). Salmonidae were introduced to Tierra del
Fuego in the 1930s. Especially Chinook salmon Oncorhynchus tshawytscha
causes concern. The detection of Chinook salmon in Tierra del Fuego
dates back to April 2006, and its population has been expanding since
then (Fernández et al., 2010; Nardi, Fernández, Vanella, \& Chalde,
2019). Being a top predator Chinook salmon can compete with several
native species in the Beagle Channel (Correa \& Gross, 2008), and prey
over native species such as Notothenioids (Eleginops maclovinus,
Patagonotothen tessellata, P. cornucola, P. sima, Paranotothenia
magellanica, Harpagifer bispinis), the Atherinidae Odontesthes smitti
and O. nigricans, the Fuegian sprat Sprattus fuegensis, and larvae of
king crabs (Lithodes antarcticus and Paralomis granulosa) (Fernández et
al., 2010). J. E. Ciancio et al. (2008) observed that Chinook salmon in
the Southern Patagonian Shelf Ecosystem Area primarily feed on sprats
and display trophic levels comparable to those of intermediate-sized
fish and cephalopod predators species, showing significant dietary
overlap with Magellanic penguins (Spheniscus magellanicus). Another
potential competitor for Chinook salmon in the Beagle Channel is the
Commerson's dolphin (Cephalorhynchus commersonii), which shares a
similar diet (Riccialdelli et al., 2013).

In the Beagle Channel, other anthropogenic stressors include
contaminants like metals, perfluorinated compounds, hydrocarbons, and
microplastics found in animal tissue and sediments. Some studies
reported varying heavy metal levels in sea mussel tissues and sediments,
indicating bioavailability differences (Duarte, Giarratano, Amin, \&
Comoglio, 2011). Other research found similar carbon and carbohydrate
levels in Ushuaia Bay's surface sediments to those in hypertrophic
ecosystems, along with hydrocarbons and heavy metals linked to port and
industrial activities (Gil, Torres, Amin, \& Esteves, 2011).
Commendatore, Nievas, Amin, \& Esteves (2012) identified three distinct
hydrocarbon accumulation zones in the Bay. Llorca et al. (2012) found
high levels of perfluorinated compounds in algae, fish, and guano.
Ferreira et al. (2021) showed that black southern cod in Ushuaia Bay may
be exposed to endocrine-disrupting compounds from urban and industrial
pollution. Analía F. Pérez et al. (2020) and Ojeda et al. (2021) found
microplastics in M. edulis chilensis and Nacella magellanica,
respectively. These studies link pollutants to Ushuaia (54°48′S 68°18′W)
and its port and industrial activities. We expect the Beagle Channel
area closest to the city to be most affected. Contaminants can spread
through the food web, magnifying the risk to higher-level organisms.
Fioramonti et al. (2022) studied mercury transfer in three southwest
Atlantic Ocean food webs and found biodilution in the Beagle Channel and
Atlantic coast of Tierra del Fuego webs. However, mercury concentrations
rose with benthivory in these webs, and higher mercury was found in
phytoplankton and Grimothea gregaria. Squat lobsters connect pelagic and
benthic habitats, so any disruption to them could disrupt the food web
(Rodriguez et al., 2022). Dodino et al. (2022) found the highest mercury
levels in Magellanic penguin feathers from offshore colonies in Tierra
del Fuego. Recently, Ushuaia's kelp forests have seen a decrease in
biodiversity and changes in macroalgae composition due to urban
pollution (Kaminsky et al., in prep.).

\hypertarget{burdwood-bank}{%
\subsubsection{3.3 Burdwood Bank}\label{burdwood-bank}}

The stressors reported for the ecosystem of the Marine Protected Areas
Namuncurá within Burdwood Bank I and II are mostly anthropogenic; there
is a lack of studies focusing on the environmental stressors that are
known to be occurring at a regional scale (e.g.~sea surface warming,
Franco, Combes, \& González Carman (2020)) (Table 2). Several fisheries
targeting demersal fishes operate in the vicinity and within the
ecosystem of the Marine Protected Areas (i.e.~Marine National Reserve
management category). The Patagonian fisheries on the toothfish
Dissostichus eleginoides has gained prominence in recent years (P. A.
Martínez, Wöhler, \& Troccoli, 2015; L. Allega et al., 2020; Gorini,
Lukaszewicz, \& Giussi, 2021; Administración de Parques Nacionales,
2022). Although these are regulated by the Argentinean government,
incidental catches do occur, where demersal fishes of the genera
Coelorinchus and Macrourus, seabirds and benthic invertebrates (30+
taxa) are the most common bycatches (Gaitán \& Marí, 2016; Patricia A.
Martínez et al., 2022). Noteworthy, among the invertebrates caught, 8
species are indicator taxa of vulnerable marine ecosystems (Gaitán \&
Marí, 2016; Schejter \& Albano, 2021). Independent assessments of these
bycatches suggest no significant impact on the communities (Gaitán \&
Marí, 2016; Patricia A. Martínez et al., 2022). Besides bycatch, species
of seabirds are being affected by the fishery due to discards, altering
its diet; the most frequently encountered species are Black-browed
albatross Thalassarche melanophris, Southern giant petrel Macronectes
giganteus, Cape petrel Daption capense, Southern royal albatross
Diomedea epomophora, Northern giant petrel M. halli, and White-chinned
petrel Procellaria aequinoctialis (Tamini et al., 2023). Nevertheless,
there is a lack of knowledge considering the species' role in the
ecosystem and the potential joint effect of both target fishes and
bycatch in a broader food web framework.

Anthropogenic contaminants such as microplastics and mercury are present
in the water column of the Burdwood Bank ecosystem (Cossi et al., 2021;
Di Mauro et al., 2022; Fioramonti et al., 2022). Microplastics are
distributed all along the water column, from surface to deep waters
(3-2450 m) (Di Mauro et al., 2022). More importantly, microplastics were
found in soft tissues of benthic macroinvertebrates (sea stars Henricia
obesa and Odontaster penicillatus) and benthopelagic fishes
(Patagonotothen guntheri and P. ramsayi), which not only incorporated
the contaminant from the environment through their filter-feeding system
but could also get it indirectly from prey organisms already containing
plastics in their tissues (Cossi et al., 2021). Notably, one of the
contaminated species, the long tail southern cod Patagonotothen ramsayi,
is part of the core group of species that drive the ecosystem through
the suggested wasp-waist control (Riccialdelli et al., 2020). Mercury
transfer and biomagnification are ongoing processes in the ecosystem,
which are occurring at a greater pace than near coastal areas (Beagle
Channel) (Fioramonti et al., 2022). It's important to note that the
Fuegian sprat Sprattus fuegensis, a pelagic fish with a mid-trophic
level in the food web, presented the highest levels of mercury
(Fioramonti et al., 2022). Considering the wasp-waist control of the
Fuegian sprat in the food web (Riccialdelli et al., 2020), a rapid and
widespread contamination to the top predators is expected (Fioramonti et
al., 2022).

In recent years, licenses for seismic studies and exploration of
hydrocarbon resources have been granted all along the northwestern limit
of the Marine Protected Areas (Secretaría de Gobierno de Energía Res. Nº
65/2018). Although effects from these types of surveys on marine mammals
and seabirds are well-known for other regions of the world (Nowacek et
al., 2015), there is no particular knowledge for this ecosystem.
However, several documents warn of the potential negative effects this
may have on the species inhabiting the Burdwood Bank area (Lucrecia
Allega et al., 2019; de Haro et al., 2022).

Despite evidence of warming at surface, mid-water and bottom layers (100
m) in Burdwood Bank (Franco et al., 2020), specific studies on the
oceanographic aspects of the system are lacking. In this sense, there is
a big question mark about the environmental stressors impact on the
species and trophic interactions in Burdwood Bank.

\hypertarget{scotia-sea}{%
\subsubsection{3.4 Scotia Sea}\label{scotia-sea}}

The Scotia Sea is a vast and heterogenous oceanic region, where
especially the areas around South Georgia island represents an area of
interest, here referred to as `Northern Scotia Sea'. The majority of
studies analyzing the stressors' effects come from this area.

The Scotia Sea has experienced one of the largest levels of warming
within the polar regions (Whitehouse et al., 2008). Together with the
Southern Annular Mode anomalies this has caused a long-term decrease in
krill abundance; more pronounced in the northern than in the southern
Scotia Sea (E. J. Murphy et al., 2007; Atkinson et al., 2019). Over the
past 90 years, the krill also showed an increase in mean body length
(Atkinson et al., 2019), which may also alter predator-prey interactions
and allow reaching cooler feeding grounds near the seabed, with the
potential to link krill to unexpected predators (Schmidt et al., 2011).
Another consequence of the mentioned environmental stressors, is a
change in krill distribution due to a southward contraction (Atkinson et
al., 2019). It is noteworthy here, that the distributional shift has not
affected all species inhabiting the Northern Scotia Sea, and most
abundant calanoid copepods have maintained their distribution (Tarling,
Ward, \& Thorpe, 2018). Considering the above, food web models of the
Northern Scotia Sea have suggested shifts in the structure and
functioning of the food web, from krill-based to non-krill-based, where
myctophid fishes and squid are playing important roles (Hill, Keeble,
Atkinson, \& Murphy, 2012; Saunders et al., 2019).

The principal anthropogenic stressor of the Scotia Sea is commercial
fisheries. Krill fishery not only stresses the targeted species, but
also the many predators that depend on it as a food source (Hilborn et
al., 2017). Yet, data currently available from monitoring of krill and
its predators remain insufficient, hence identifying the potential
fishery impacts on the ecosystem is difficult (P. N. Trathan et al.,
2021). Apart from krill fishery, two other commercial fisheries operate
in the Scotia Sea, targeting Patagonian toothfish species Dissostichus
eleginoides and D. mawsoni. The D. eleginoides stock is linked to the
stock at South Georgia (`Northern Scotia Sea') (Collins, Brickle, Brown,
\& Belchier, 2010), while the D. mawsoni stock is linked to the
Antarctic continental shelf (`Southern Scotia Sea') (Soeffker et al.,
2022). Despite the fact that the mentioned fisheries are certified by
the Marine Stewardship Council standards, Philip N. Trathan (2023)
identified several concerns regarding aspects of fisheries itself, other
species' population status (i.e.~recovery of baleen whales), and
environmental stressors (i.e.~sea warming), which could have synergistic
effects on the food web structure and functioning that are still
unknown.

Mercury transfer and biomagnification are current processes occurring in
the Scotia Sea, where the total concentration of contaminants increase
with trophic level and are highest in notothenioid and myctophid fishes
(e.g.~Dissostichus eleginoides, Gymnoscopelus nicholsi), and seabirds
(Seco et al., 2021). During years of low Antarctic krill abundance,
predators must deal with both the stress of reduced prey availability
and the concurrent rise in mercury exposure (Seco et al., 2021).

\hypertarget{potter-cove-antarctica}{%
\subsubsection{3.5 Potter Cove
(Antarctica)}\label{potter-cove-antarctica}}

Regional warming in the last half century has been one of the main
factors driving changes in Potter Cove (Western Antarctic Peninsula)
(Hendry, Meredith, \& Ducklow, 2018; Chown et al., 2022). Sudden
environmental changes have occurred, such as sea surface temperature
increase, salinity decrease, suspended particulate matter loading and
chlorophyll-a increase, all linked to climatic cycles (Southern Annular
Mode and El Niño Southern Oscillation) (Schloss et al., 2012; Bers,
Momo, Schloss, \& Abele, 2013). Particularly, sea warming has produced
drastic environmental and biological transformations (e.g.~shifts in
dominance of benthic community) in the Potter Cove ecosystem (Rückamp,
Braun, Suckro, \& Blindow, 2011; Schloss et al., 2012; María Liliana
Quartino et al., 2013; Sahade et al., 2015; Hernández, Lopez, Piquet,
Mac Cormack, \& Buma, 2019), a system highly dependent on sea-ice
dynamics (Table 2). In Potter Cove, total sea ice cover has decreased
since 1991 (Schloss et al., 2012). Changes in the annual timing of
landfast ice formation and breakup of the sea ice cover has multiple
effects on species in the food web (Michel et al., 2019; Rossi et al.,
2019). Warmer winters and springs result in earlier sea-ice melt,
causing an abrupt increase in the light available benthic primary
producers (Dolores Deregibus et al., 2020). Sea ice also mediates
physical disturbances to the benthos by influencing sedimentation and
iceberg scouring. These factors affect the production of macroalgae,
albeit in opposite ways (D. Deregibus et al., 2016, 2017), and
microphytobenthos (Hoffmann et al., 2019; Braeckman et al., 2021). On
the other hand, sea ice is an important habitat for diatoms and its
associated consumers, including copepods and krill (Flores et al.,
2012), and thus important for bentho-pelagic nutrient and carbon cycling
during winter. Additionally, a decrease in winter sea ice cover produces
an increase in physical perturbation on benthic shallow communities in
coastal shallows due to ice scouring (D. Deregibus et al., 2017). The
glacier surrounding Potter Cove has been receding at an increasing rate
since 1950 (Rückamp et al., 2011), which has caused a massive discharge
of sediment-laden meltwater (Meredith et al., 2018). Large quantities of
suspended particles affect growth, survival and reproduction of benthic
species. This had led to a major shift in the benthic community
structure, from a filter feeders--ascidian domination to a mixed
assemblage with scavengers and opportunistic species (Pasotti et al.,
2015; Sahade et al., 2015), and the metabolic balance in benthos went
from net autotrophy to heterotrophy (Hoffmann et al., 2019; Braeckman et
al., 2021). Additionally, massive stranding events of the tunicate Salpa
thompsoni and the euphausiid Euphausia superba (krill) linked to the
presence of glacial meltwater have been reported (Fuentes et al., 2016).
Rising temperatures leading to ice and glacial melting has also
substantial impacts on pelagic primary productivity, since it reduces
water salinity, affecting water column stratification, light penetration
and nutrient availability for photosynthesis (Schloss et al., 2012). In
Potter Cove, changes in biomass of most phytoplankton species have been
observed under heat wave conditions, resulting in a shift from a
microplankton to a nanoplankton dominated community (Antoni et al.,
2020; Latorre et al., 2023). This means that in areas strongly affected
by glacier melt, the planktonic food web is dominated by the microbial
loop (ciliates and heterotrophic dinoflagellates preys upon
nanophytoplankton, which are sequentially available prey for small
omnivorous copepods), instead of being predominantly herbivorous (Garcia
et al., 2016, 2019). In addition, phytoplankton species under these
warming conditions showed a decrease in metabolic rates and in the
quality of the fatty acids composition (Latorre et al., 2023).

\hypertarget{weddell-sea-antarctica}{%
\subsubsection{3.6 Weddell Sea
(Antarctica)}\label{weddell-sea-antarctica}}

In the Weddell Sea several stressors have already been triggered by
global warming effects (Table 2), from which spatial and temporal
reduction in sea ice is suggested to be driving changes in pelagic and
benthic communities (Constable et al., 2014; Julian Gutt et al., 2021).
Sea ice extent has reached new record lows since the satellite era began
in 1978. Sea warming has been substantial in recent years: in 2017 the
mean temperature for February reached 1.45°C, the highest monthly mean
ever recorded (0.56°C above the climatological mean) (Turner et al.,
2020). In this context, it has been suggested that Antarctic krill
Euphausia superba has already declined as a result of productivity
changes caused by sea ice declines (Atkinson, Siegel, Pakhomov, \&
Rothery, 2004). Declining sea ice cover allows increased access to krill
by predators (So Kawaguchi, Nicol, \& Press, 2009), which further
contributes to decreased krill abundances. This in turn can result in
reduced carbon export due to decreased fecal pellets from krill (Pauli
et al., 2021).

On the other hand, sea ice loss increases light availability, triggering
primary production by phytoplankton in the short-term (Pineda-Metz et
al., 2020; Dinniman, St-Laurent, Arrigo, Hofmann, \& van Dijken, 2023).
Furthermore, a warmer and more stable water column with a shallow upper
mixed layer, is expected to enhance the dominance of cryptophytes over
diatoms which may favor salp populations over krill populations; thereby
reducing the magnitude of energy transfer to higher trophic levels and
the seabed (Isla, 2023).

Higher trophic level species are expected to respond differently to
global warming in the Weddell Sea. In this regard, Notothenioid fishes
(e.g.~Pleuragramma antarcticum) face multiple stressors (sea warming,
sea ice decline, ocean acidification) that threaten their survival.
While some species exhibit physiological plasticity to compensate for
increased oxygen demand, most notothenioid fishes are stenothermal and
unable to adjust their metabolic functioning (Mintenbeck et al., 2012).
It is anticipated that the thermal habitat preferred by the Antarctic
toothfish Dissostichus mawsoni could undergo contraction in the coming
three decades (Constable et al., 2014), further emphasizing the
potential impact of global warming effects on these species. Marine
mammals, Weddell and crabeater seals (Leptonychotes weddellii and
Lobodon carcinophagus), exhibit varying levels of sensitivity. The
latter exhibits a preference for breeding in close proximity to krill
swarms, and thus is particularly susceptible to reductions in sea ice
concentrations and sea surface temperatures. Rescued sea ice can
significantly affect their post- and future breeding foraging success
(Siniff et al., 2008; Wege et al., 2021). In addition, the Antarctic
petrel Thalassoica antarctica, which is one of the most abundant
seabirds in the area, is a sea ice dependent forager and breeder
(Orgeira et al., 2021); therefore the loss of this habitat will degrade
its foraging success and reproductive output over time. The snow petrel
Pagodroma nivea also relies heavily on sea ice for foraging and its
colonies in the Weddell Sea may be affected. The emperor penguin
Aptenodytes forsteri uses sea ice for breeding; any reductions could
constrain its populations, as evidenced by recent observations in the
Bellingshausen Sea region (Fretwell, Boutet, \& Ratcliffe, 2023). The
Arctic tern Sterna paradisaea spends the summer in the Weddell Sea
exploiting krill swarms under receding ice edges, then declines in ice
cover may reduce prey availability and quality of molting habitats.
Continued warming is thus expected to gradually erode the abundance and
distribution of these `primary species' that dominate the avifauna of
the Weddell Sea through loss of critical sea ice habitat (Orgeira et
al., 2021). Variations in sea ice extent have implications for great
whales, such as the Humpback whale Megaptera novaeangliae, since their
primary prey resource is the Antarctic krill (Braithwaite et al., 2015).
Decreased winter ice coverage results in reduced suitable habitat and
lower krill abundance (Braithwaite et al., 2015), with flow-on effects
for whale body condition observed historically in harvest data. With
climate projections indicating ongoing sea ice losses, further threats
to critical krill populations pose risks to the energy intake and
reproductive success and long-term viability of humpback whale
populations dependent on consistent Antarctic feeding (Pallin et al.,
2023).

Iceberg scouring is a major factor in the high biodiversity of benthic
communities in the Weddell Sea (Julian Gutt \& Starmans, 2001). Even at
600 m depths, iceberg scouring has a strong effect on the benthic
environment, disrupting the upper layers of the seabed and removing
macrofauna. This patchy disturbance and distribution pattern occurs
roughly every 200 square meters on the Antarctic continental shelf.
Global warming is predicted to raise iceberg scouring frequency (J. Gutt
et al., 1996; Julian Gutt, 2001; Dan A. Smale et al., 2008), disrupting
the environment (J. Gutt et al., 1996; Dan A. Smale \& Barnes, 2008).
Julian Gutt et al. (2015) expects tipping points are significant due to
these effects and lack of knowledge.

\hypertarget{from-species-stressors-to-food-web-effects}{%
\subsection{4. From species' stressors to food web
effects}\label{from-species-stressors-to-food-web-effects}}

A major challenge in contemporary ecology lies in predicting the effects
of stressors on complex multispecies systems, such as food webs. Network
analysis has proved to be a powerful tool to tackle this issue, since it
can capture the effects of individual and multiple stressors on
communities and ecosystems (Montoya et al., 2009; O'Gorman, Fitch, \&
Crowe, 2012; Bruder, Frainer, Rota, \& Primicerio, 2019; Polazzo,
Marina, Crettaz-Minaglia, \& Rico, 2022). Environmental and
anthropogenic stressor effects in the southwest and the Atlantic sector
of the Southern Ocean have been mostly assessed individually and at the
organism and/or population, i.e., at the node level (Table 2), with one
exception: the effect of fisheries in the San Jorge Gulf food web (see
section below for more details). To address the most plausible stressors
effects on the selected food webs, given the current information, we
built hypotheses for each study area. To this aim, we developed a
theoretical framework considering the following: a) stressor(s), b)
parameter(s) affected, c) node-level properties of the affected species,
and d) network-level properties of the food web. We considered that a
stressor will affect one of the following species' characteristics or
parameters: metabolism, biomass, distribution, and diet (Figure 2).
`Metabolism' refers to any change related to metabolic rate, such as
reproduction, hatching, larval development, growth and mortality, and
contamination due to pollutants (e.g.~growth effect in filter-feeders
due to sediment in water column in Potter Cove; endocrine disruption in
fish due to urban pollutants in Beagle Channel). `Biomass' indicates an
effect at the population level, where the density/abundance is being
impacted (e.g.~abundance decreases in macrobenthos due to iceberg
scouring in Weddell Sea). `Distribution' entails a change at the
population level in the geographic space occupied by a species,
e.g.~southward contraction of Antarctic krill due to sea warming of the
Scotia Sea. `Diet' includes alterations in the prey items of a species
at the population level, e.g, due to prey switching, having a direct
effect on the structure of the food web, e.g.~new prey item (discards)
for seabirds due to fishery activities in Burdwood Bank. Next, we
considered node- and network-level properties relevant to the
hypothesized stressor effects on the food webs, and which have been
previously calculated for the studied food webs (Table 3). At the
node-level, we included: a) degree, b) trophic position, c) omnivory
index, and d) relative abundance (see Table S1 in Supporting Information
for properties of stressed nodes). At the network-level, we considered:
a) connectance, b) path length, c) mean trophic level, and d) omnivory
(Table 1).

\begin{figure}
\centering
\includegraphics[width=6.27in,height=3.528in]{Figures/Figure2_StressorDiagram.png}
\caption{Conceptual diagram: from species' stressors to food web
effects. See text for explanation.}
\end{figure}

\scriptsize

Table 3. Node and network-level properties used to build hypotheses on
the stressors' effects.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1963}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2617}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3925}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1495}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Property}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Definition}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Relevance for stressor effects}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Reference}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\emph{Node-level} & & & \\
Degre & Number of feeding interactions in which the species participates
as prey and/or predator. & Perturbations to high-degree species may have
more significant effects on the food web robustness to perturbations
than low-degree species. & Dunne, Williams, \& Martinez (2002a); Jordán,
Benedek, \& Podani (2007) \\
Trophic position & Place in the food web relative to the basal resources
that support the community. Classifies species in: basal, intermediate
and top. & Perturbations on basal resources, intermediate species and
top predators are expected to have large effects on the rest of their
communities if ecosystem control is bottom-up, wasp-waist or top-down,
respectively. & Williams \& Martinez (2000); Thompson, Hemberg,
Starzomski, \& Shurin (2007) \\
Omnivory & Consumer resource use across trophic levels. & High-omnivore
species (generalists) are more flexible than low-omnivore species to
diet changes. & Thompson et al. (2007) \\
Relative abundance & Species' density in proportion to the other species
of the food web. & Perturbations on abundant (dominant) species are
expected to have large effects on the stability and energy flux of the
food and ecosystem, respectively. & Nilsson \& McCann (2016) \\
\emph{Network-level} & & & \\
Conectance & Proportion of actual interactions among possible ones. &
Estimator of community sensitivity to stressors. High connectance gives
resistance and resilience to the food web. & Dunne, Williams, \&
Martinez (2002b) \\
Path length & Average distance, accounted by the number of interactions,
between any pair of species. & Short distances enhance rapid and broad
propagation of perturbations. & Albert \& Barabási (2002) \\
Mean TL & Average of all species' trophic position contained in the food
web. & Influences the magnitude and efficiency of trophic transfer. A
higher mean food chain length reflects increased energy availability and
productivity. & Duffy et al. (2007); Olivier et al. (2019) \\
Omnivory & Proportion of species that feed at different trophic levels.
& It provides trophic flexibility to an ecosystem. Reduces probability
of trophic cascades. & Kratina, LeCraw, Ingram, \& Anholt (2012) \\
\end{longtable}

\normalsize

\hypertarget{warming-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}{%
\subsubsection{4.1 Warming effects on food webs in a southwest Atlantic
- Antarctic
gradient}\label{warming-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}}

The most common stressor reported along the southwest Atlantic -
Antarctic gradient is global warming, except for Beagle Channel and
Burdwood Bank, which are more influenced by the introduction of an alien
species and fisheries, respectively (section 3). The main
characteristics of global warming in the region, and the most plausible
drivers of change, are: sea warming, glacial retreat, elevated sediment
input in the water column, and reduction of the sea ice extent. These
drivers act in different ways and magnitudes in the studied locations
along the latitudinal gradient. The above does not mean that there are
no other stressors interacting with global warming, potentially
buffering the overall effect on the food web (e.g.~sea warming and
fishery in San Jorge Gulf). Climate change has led to several
well-documented impacts on marine species regarding distributional
shifts induced by warming of marine currents (Wu et al., 2012;
Poloczanska et al., 2013; Vergés et al., 2014; Vergés et al., 2019).
Furthermore, warmer temperatures increase species metabolic rates
(Brown, Gillooly, Allen, Savage, \& West, 2004). Changes in metabolic
rates can subsequently translate into shifts in species traits (body
size, Vucic-Pestic, Ehnes, Rall, \& Brose (2011); Klein, Hill, Hinke,
Phillips, \& Watters (2018){]}, biomass (Perry et al., 2020) and
distribution (Kortsch, Primicerio, Fossheim, Dolgov, \& Aschan, 2015).
Alterations in the species body size and distributions have ripple
effects on feeding interactions, for example, it can introduce new
feeding interactions (Vergés et al., 2014; Pecuchet et al., 2020),
modify existing ones, and shorten energy pathways (Bartley et al., 2019;
O'Gorman et al., 2019), and reduce trophic efficiencies (Vucic-Pestic et
al., 2011).

In recent years, several new fish (Galván et al., 2022) and
macroinvertebrates species (Vinuesa, 2005; López-Gappa, 2022) were
registered in Patagonia, mostly in San Jorge Gulf in relation to the
southward range shift of warm-temperate species. This distributional
change is driven by the tropicalization of temperate waters caused by
sea warming (Vergés et al., 2014; Vergés et al., 2019). Because of its
location in the ecotone between two biogeographic provinces, the
Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) (Balech \&
Ehrlich, 2008), the San Jorge Gulf is prone to changes in species
composition. We hypothesize that sea warming will alter the food web
structure topologically, by increasing the number of species and
interactions. Newcomers are, in general, mid-trophic level species with
generalist diets, hence an increase in food web connectance may be
expected (Bartley et al., 2019). In another temperate ecosystem, an
increase in the number of fish species, led to an increase in functional
diversity and predation rate (Sgarlatta, 2023); consequences that may
also be expected in San Jorge Gulf. Given the short path length of the
San Jorge Gulf food web, the disturbances from the listed stressors are
expected to spread to many species of the food web. However, it has to
be acknowledged that the increase in functional diversity driven by the
range expansion of warm-temperate species is contrary to the process of
homogenization and loss of functional diversity in the area driven by
trawl fisheries (Rincón-Díaz et al., 2021).

In the middle of the latitudinal gradient (considered in this study),
the Scotia Sea has experienced one of the largest levels of sea warming
of any polar region (Whitehouse et al., 2008; Atkinson et al., 2019).
López-López et al. (2022) suggested that the southward distributional
change of generalist predators from the northern towards southern Scotia
Sea increases network connectance of the latter, while decreasing its
modularity. The lower modularity may increase the probability of
perturbations spreading through the network (Stouffer \& Bascompte,
2011), which may be offset by increased connectance enhancing robustness
to species loss (Dunne et al., 2002a). In the northern Scotia Sea around
South Georgia Island, we suggest that the declining krill biomass driven
by sea warming (Atkinson et al., 2019), and ocean acidification and
pollution synergy (Rowlands et al., 2021), will reduce the energy
transfer to top predators like seabirds and marine mammals. However,
this may be buffered since the dominant copepod species have maintained
its distribution (Tarling et al., 2018), but most importantly, showed an
abundance increase in recent decades likely due to reduced predation and
competition for food (Ward, Tarling, \& Thorpe, 2018). All this is
significant for the structure of the food web given the central role of
krill and copepods, characterized by high degree and mid-trophic
position (Table S1). Overall, the food web's inherent resilience, marked
by high connectance and omnivory, added to the potential compensation
for the krill decrease due to a copepod increase, may buffer against
structural changes.

In Potter Cove, a fjord-like Antarctic ecosystem, the impacts of climate
change affect many species within the food web. Potter Cove has recently
experienced frequent events of marine heatwaves, i.e.~prolonged periods
of anomalously high sea surface temperatures (Oliver et al., 2018;
Latorre et al., 2023). This has led to decreases in biomasses of
different planktonic functional groups (Garcia et al., 2019; Latorre et
al., 2023). Given the relatively low abundance of phytoplankton,
zooplankton's low degree, and the modular configuration of the food web,
we hypothesize that changes in these nodes, due to increased sea
temperatures, will be retained in the basal pelagic compartment of the
food web and will not expand to higher trophic levels. Benthic primary
producers in Potter Cove are being influence by the decrease in winter
sea ice cover (higher light availability), the increased levels of
sediments in the water column due to glacial melt run-off (lower light
penetration) and the newly free-ice areas available for colonization
associated to glacier retreat. The overall local effect of climate
change on macroalgae is a net increase in their production (Dolores
Deregibus et al., 2023). It has been proposed that larger diversity in
primary producers can support a more diverse food web with more
specialized consumers (Iken et al., 2023). We expect to see differential
effects of climate change on hard and soft bottom associated food webs
(Cordone et al., 2020). Given the high relative abundance and the high
degree of the macroalgae functional group (Table S1), we expect a longer
hard bottom food web, wider consumer trophic niches, and that it will
become more stable as sea ice cover decreases and the glacier retreats
due to global warming. In soft bottom areas of the Cove, multiple food
web nodes are being affected by ongoing warming effects: decrease in net
primary production of benthic microalgae (Hoffmann et al., 2019), and
changes in the benthic community biomass, distribution and composition
(Pasotti et al., 2015; Sahade et al., 2015). Given that the Potter Cove
food web's present low connectance and omnivory, we suggest fragility
and potential trophic cascade effects (Marina et al., 2018) with
pronounced changes in energy fluxes.

The southernmost location of the latitudinal gradient is the Weddell
Sea, where the main effect of global warming is the decrease in sea ice
extent, with reported anomalies in the past summer seasons (Fretwell et
al., 2023). Declining sea ice extent has reduced the abundance of krill
(Atkinson et al., 2004; Flores et al., 2012), and produced an increase
in phytoplankton productivity (Pinkerton et al., 2021; Isla, 2023),
altering the plankton community structure, and benefiting cryptophytes
over diatoms (Lin et al., 2021). Moreover, habitat loss from sea ice
decline will reduce the foraging success and breeding sites of seabirds
(e.g., snow petrel Pagodroma nivea and emperor penguin Aptenodytes
forsteri), decreasing their biomassess and modifying their
distributions. The projected rise in iceberg scouring is expected to
significantly alter the biomass and community structure of macrobenthos,
which in turn will impact mid-trophic level predators such as demersal
fish (Julian Gutt, 2001; Mintenbeck et al., 2012). While we do not
anticipate large-scale topological changes in the food web, local
extinctions could lead to such changes, particularly affecting benthic
species (Julian Gutt \& Piepenburg, 2003). Given that the impacted
species---whether individually like krill, or collectively like
macrobenthos---present a mid-trophic position, high biomass and high
degree (Table S1), we hypothesize that significant shifts in energy
fluxes will occur. Additionally, the food web's low proportion of
omnivores suggests reduced system resilience (Table 1), increasing the
likelihood of regime changes (Julian Gutt et al., 2015).

The two ecosystems in the subantarctic region, the Beagle Channel and
Burdwood Bank, are more affected by other anthropogenic stressors than
warming. Although these areas might be impacted by global warming
effects due to studies at a regional scale (Franco et al., 2020), to
date no studies exist for Beagle Channel and Burdwood Bank ecosystems.
In the Beagle Channel, the introduction of chinook salmon, a non-native
species, poses a significant risk to the existing food web (Fernández et
al., 2010). We hypothesize that chinook salmon's predation on Fuegian
sprat and black southern cod will disrupt the established patterns of
interaction within the food web. Both of these prey species are crucial
due to their mid-trophic positions and relatively high abundance (Table
S1). Moreover, we expect that changes in the black southern cod
population will have a more significant impact on the food web than
changes in the Fuegian sprat population, as the black southern cod has a
higher degree (Table S1). Overall, these disruptions could have
far-reaching effects on the ecosystem. This is particularly concerning
given the short path length of the food web, which means that changes
can quickly propagate through the system, affecting many species and
potentially destabilizing the entire network. This phenomenon is further
heightened by the ecosystem's inherent vulnerability to changes at
mid-trophic levels, often referred to as wasp-waist control. In the
Burdwood Bank region, fishing activities may be the main stressor
causing shifts in the food web (Table 2). We hypothesize that a
combination of factors will destabilize the already fragile ecosystem,
characterized by low connectance and low omnivory (Table 1). These
factors include a decline in the biomass of the Patagonian toothfish -a
key, highly-connected species (Table S1)- as well as smaller changes in
the biomass of four mid-level fish species, five top-level seabird
species, and over 30 types of benthic macroinvertebrates due to bycatch
(Gaitán \& Marí, 2016; Patricia A. Martínez et al., 2022; Tamini et al.,
2023). Additionally, alterations in the diets of six seabird species,
caused by discarded catch (Tamini et al., 2023), are expected to disrupt
the energy flow and further reduce the stability of the food web.

\hypertarget{gaps-and-future-perspectives}{%
\subsection{5. Gaps and future
perspectives}\label{gaps-and-future-perspectives}}

Since this review deals with qualitative data regarding, not only
prey-predator interactions but also the stressor effect, adding
quantitative data to the food webs (i.e.~interaction strength
estimations) and/or to the stressor effect (i.e.~magnitude) will provide
a better comprehension of how species' stressors might be translated
into food web effects. In this context, quantitative food webs will be
useful if they reflect energy fluxes among species (Nilsson \& McCann,
2016). Emerging methods have been proposed in this sense promising ways
to estimate shifts in species interactions within food webs (Gauzens et
al., 2019; Gellner, McCann, \& Hastings, 2023). These shifts, in turn,
could lead to changes in energy fluxes within the ecosystem.

As summarized in Table 2, in the selected study areas of the southwest
Atlantic - Antarctic latitudinal gradient several stressors might be
directly affecting consumer's diets, triggered by modified environmental
conditions (sea warming, reduced sea ice extent), new habitats (due to
distributional shifts) and/or new species (alien species). Moreover, the
population trend of important species is also changing (e.g., Funes
(2020), Constable et al. (2014), Pineda-Metz (2019), Hindell et al.
(2020), Woods et al. (2023)) driving changes in their roles as either
predators or prey (e.g. Belleggia et al. (2017), Pasti et al. (2021)).
These diet and biomass updates, either considered as a short or
long-term effect, should be contemplated in order to generate reliable
predictions of food web responses to multiple stressors in the southwest
Atlantic - Antarctic region. Examples of these interactions between
diet, relative biomass, and their effects on food webs at different
temporal scales include biological invasions and trawl fisheries. Both
stressors, in the short term, increase the complexity of food webs by
adding generalist predators and/or new prey (e.g., Cordone, Galván, \&
Momo (2023)) or by enabling discard consumption (e.g., Funes et al.
(2022)). However, in the long term, both stressors may lead to the
biological extinction of certain prey and competitors (e.g., Anton et
al. (2019)) or a significant reduction in target and incidental catch
species (e.g., Dulvy et al. (2014)), thereby promoting food web
simplification.

Regarding data gaps, we should mention the cases for Beagle Channel and
Burdwood Bank ecosystems, where almost no information exists for the
impact of global warming effects (sea warming, glacial retreat, ocean
acidification) in natural populations/communities, though warming
effects have been shown at a regional scale (Franco et al., 2020). It is
worth mentioning that in Beagle Channel recent experimental studies have
tested the tolerance of fishes to scenarios of sea warming and/or
acidification suggesting potential metabolic impacts (María Eugenia
Lattuca, Boy, Vanella, Barrantes, \& Fernández, 2018; María E. Lattuca
et al., 2023).

Analyzing the impact of multiple stressors through observational studies
can be challenging (Julian Gutt et al., 2021). This complexity arises
from the potential for antagonistic effects, where impacts cancel each
other out, or synergistic effects, where the combined impact is greater
than the sum of individual effects (Crain et al., 2008; Boyd, Lennartz,
Glover, \& Doney, 2015; Côté et al., 2016). These effects are further
complicated to handle in the framework of complex food webs. The number
of pathways of effect through which a species may affect or be affected
by other species, and through which stressors may permeate communities,
increases exponentially with the number of species and interactions in a
network (Menge, 1995). In this sense, Beauchesne, Cazelles, Archambault,
Dee, \& Gravel (2021) have developed a theory-grounded approach using
motifs (i.e.~groups of species that, when put together, construct whole
food webs) to simplify food webs; methodology that could be applied to
our food web study cases.

\hypertarget{conclusions}{%
\subsection{Conclusions}\label{conclusions}}

In the light of cumulative knowledge on how global warming and emerging
stressors are affecting species inhabiting marine ecosystems in the
Southern Hemisphere (e.g. Julian Gutt et al. (2021), Galván et al.
(2022)), there is a need to better understand these changes in a more
real framework where species interact and, consequently, might spread
the stressor effect to other species in complex ways. To this end, we
have reviewed the main environmental and anthropogenic stressors acting
in six different areas along a large-scale latitudinal gradient, from
temperate to Antarctic ecosystems. Using a theoretical framework that
combines node (species) and network (food web) level data, we show how
warming effects might affect food web structure and functioning. These
qualitative predictions are intended to serve as the basis to studies
that quantify how much the ongoing stressors are affecting food web
properties, such as energy fluxes and stability, in marine ecosystems of
the Southern Hemisphere.

\hypertarget{references}{%
\subsection*{References}\label{references}}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Acha2004}{}}%
Acha, E. M., Mianzan, H. W., Guerrero, R. A., Favero, M., \& Bava, J.
(2004). Marine fronts at the continental shelves of austral {South
America}: {Physical} and ecological processes. \emph{Journal of Marine
Systems}, \emph{44}(1), 83--105.
doi:\href{https://doi.org/10.1016/j.jmarsys.2003.09.005}{10.1016/j.jmarsys.2003.09.005}

\leavevmode\vadjust pre{\hypertarget{ref-APN2022}{}}%
Administración de Parques Nacionales. (2022). {Plan de gestión AMP
Namuncurá Banco Burdwood}. {Dirección Nacional de Áreas Marinas
Protegidas (DNAMP), Argentina}.

\leavevmode\vadjust pre{\hypertarget{ref-Albert2002}{}}%
Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex
networks. \emph{Reviews of Modern Physics}, \emph{74}(1), 47--97.
doi:\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}

\leavevmode\vadjust pre{\hypertarget{ref-Allega2019}{}}%
Allega, Lucrecia, Braverman, M. S., Cabreira, A. G., Campodónico, S.,
Colonello, J. H., Derisio, C. M., \ldots{} Verón, E. M. (2019).
\emph{{Estado del conocimiento biológico pesquero de los principales
recursos vivos y su ambiente, con relación a la exploración
hidrocarburífera en la Zona Económica Exclusiva Argentina y
adyacencias}}. {INIDEP}.

\leavevmode\vadjust pre{\hypertarget{ref-Allega2020}{}}%
Allega, L., Braverman, M., Campodónico, S., Carozza, C. R., Cepeda, G.
D., Colonello, J. H., \ldots{} Verón, E. (2020). \emph{{Estado del
conocimiento biológico pesquero de los principales recursos vivos y su
ambiente, con relación a la exploración hidrocarburífera en la Zona
Económica Exclusiva argentina y sus adyacencias}}. {Mar del Plata}:
{Instituto Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.

\leavevmode\vadjust pre{\hypertarget{ref-Anton2019}{}}%
Anton, A., Geraldi, N. R., Lovelock, C. E., Apostolaki, E. T., Bennett,
S., Cebrian, J., \ldots{} Duarte, C. M. (2019). Global ecological
impacts of marine exotic species. \emph{Nature Ecology \& Evolution},
\emph{3}(5), 787--800.
doi:\href{https://doi.org/10.1038/s41559-019-0851-0}{10.1038/s41559-019-0851-0}

\leavevmode\vadjust pre{\hypertarget{ref-Antoni2020}{}}%
Antoni, J. S., Almandoz, G. O., Ferrario, M. E., Hernando, M. P.,
Varela, D. E., Rozema, P. D., \ldots{} Schloss, I. R. (2020). Response
of a natural {Antarctic} phytoplankton assemblage to changes in
temperature and salinity. \emph{Journal of Experimental Marine Biology
and Ecology}, \emph{532}, 151444.
doi:\href{https://doi.org/10.1016/j.jembe.2020.151444}{10.1016/j.jembe.2020.151444}

\leavevmode\vadjust pre{\hypertarget{ref-Atkinson2019}{}}%
Atkinson, A., Hill, S. L., Pakhomov, E. A., Siegel, V., Reiss, C. S.,
Loeb, V. J., \ldots{} Sailley, S. F. (2019). Krill ({Euphausia} superba)
distribution contracts southward during rapid regional warming.
\emph{Nature Climate Change}, \emph{9}(2), 142--147.
doi:\href{https://doi.org/10.1038/s41558-018-0370-z}{10.1038/s41558-018-0370-z}

\leavevmode\vadjust pre{\hypertarget{ref-Atkinson2004}{}}%
Atkinson, A., Siegel, V., Pakhomov, E., \& Rothery, P. (2004). Long-term
decline in krill stock and increase in salps within the {Southern
Ocean}. \emph{Nature}, \emph{432}(7013), 100--103.
doi:\href{https://doi.org/10.1038/nature02996}{10.1038/nature02996}

\leavevmode\vadjust pre{\hypertarget{ref-Baiser2012}{}}%
Baiser, B., Gotelli, N. J., Buckley, H. L., Miller, T. E., \& Ellison,
A. M. (2012). Geographic variation in network structure of a nearctic
aquatic food web. \emph{Global Ecology and Biogeography}, \emph{21}(5),
579--591.
doi:\href{https://doi.org/10.1111/j.1466-8238.2011.00705.x}{10.1111/j.1466-8238.2011.00705.x}

\leavevmode\vadjust pre{\hypertarget{ref-Balech2008}{}}%
Balech, E., \& Ehrlich, M. D. (2008). {Esquema biogeográfico del Mar
Argentino}.

\leavevmode\vadjust pre{\hypertarget{ref-Ballerini2014}{}}%
Ballerini, T., Hofmann, E. E., Ainley, D. G., Daly, K., Marrari, M.,
Ribic, C. A., \ldots{} Steele, J. H. (2014). Productivity and linkages
of the food web of the southern region of the western {Antarctic
Peninsula} continental shelf. \emph{Progress in Oceanography},
\emph{122}, 10--29.
doi:\href{https://doi.org/10.1016/j.pocean.2013.11.007}{10.1016/j.pocean.2013.11.007}

\leavevmode\vadjust pre{\hypertarget{ref-Bartley2019}{}}%
Bartley, T. J., McCann, K. S., Bieg, C., Cazelles, K., Granados, M.,
Guzzo, M. M., \ldots{} McMeans, B. C. (2019). Food web rewiring in a
changing world. \emph{Nature Ecology \& Evolution}, \emph{3}(3),
345--354.
doi:\href{https://doi.org/10.1038/s41559-018-0772-3}{10.1038/s41559-018-0772-3}

\leavevmode\vadjust pre{\hypertarget{ref-Bauer2022}{}}%
Bauer, B., Berti, E., Ryser, R., Gauzens, B., Hirt, M. R., Rosenbaum,
B., \ldots{} Brose, U. (2022). Biotic filtering by species' interactions
constrains food-web variability across spatial and abiotic gradients.
\emph{Ecology Letters}, \emph{25}(5), 1225--1236.
doi:\href{https://doi.org/10.1111/ele.13995}{10.1111/ele.13995}

\leavevmode\vadjust pre{\hypertarget{ref-Beauchesne2021}{}}%
Beauchesne, D., Cazelles, K., Archambault, P., Dee, L. E., \& Gravel, D.
(2021). On the sensitivity of food webs to multiple stressors.
\emph{Ecology Letters}, \emph{24}(10), 2219--2237.
doi:\href{https://doi.org/10.1111/ele.13841}{10.1111/ele.13841}

\leavevmode\vadjust pre{\hypertarget{ref-Belgrano2005}{}}%
Belgrano, A., Scharler, S. E. R. C. U. M., Scharler, U. M., Dunne, J.,
\& Ulanowicz, R. E. (2005). \emph{Aquatic {Food Webs}: {An Ecosystem
Approach}}. {OUP Oxford}.

\leavevmode\vadjust pre{\hypertarget{ref-Belleggia2017}{}}%
Belleggia, M., Giberto, D., \& Bremec, C. (2017). Adaptation of diet in
a changed environment: {Increased} consumption of lobster krill {Munida}
gregaria ({Fabricius}, 1793) by {Argentine} hake. \emph{Marine Ecology},
\emph{38}(4), e12445.
doi:\href{https://doi.org/10.1111/maec.12445}{10.1111/maec.12445}

\leavevmode\vadjust pre{\hypertarget{ref-Bers2013}{}}%
Bers, A. V., Momo, F., Schloss, I. R., \& Abele, D. (2013). Analysis of
trends and sudden changes in long-term environmental data from {King
George Island} ({Antarctica}): Relationships between global climatic
oscillations and local system response. \emph{Climatic Change},
\emph{116}(3), 789--803.
doi:\href{https://doi.org/10.1007/s10584-012-0523-4}{10.1007/s10584-012-0523-4}

\leavevmode\vadjust pre{\hypertarget{ref-Bogazzi2005}{}}%
Bogazzi, E., Baldoni, A., Rivas, A., Martos, P., Reta, R., Orensanz, J.
M. (lobo)., \ldots{} Werner, F. (2005). Spatial correspondence between
areas of concentration of {Patagonian} scallop ({Zygochlamys}
patagonica) and frontal systems in the southwestern {Atlantic}.
\emph{Fisheries Oceanography}, \emph{14}(5), 359--376.
doi:\href{https://doi.org/10.1111/j.1365-2419.2005.00340.x}{10.1111/j.1365-2419.2005.00340.x}

\leavevmode\vadjust pre{\hypertarget{ref-Bovcon2013}{}}%
Bovcon, N. D., Góngora, M. E., Marinao, C., \& González-Zevallos, D.
(2013). Composición de las capturas y descartes generados en la pesca de
merluza común {Merluccius} hubbsi y langostino patagónico {Pleoticus}
muelleri: Un caso de estudio en la flota fresquera de altura del {Golfo
San Jorge}, {Chubut}, {Argentina}. \emph{Revista de Biología Marina y
Oceanografía}, \emph{48}(2), 303--319.
doi:\href{https://doi.org/10.4067/S0718-19572013000200010}{10.4067/S0718-19572013000200010}

\leavevmode\vadjust pre{\hypertarget{ref-Boyd2015}{}}%
Boyd, P. W., Lennartz, S. T., Glover, D. M., \& Doney, S. C. (2015).
Biological ramifications of climate-change-mediated oceanic
multi-stressors. \emph{Nature Climate Change}, \emph{5}(1), 71--79.
doi:\href{https://doi.org/10.1038/nclimate2441}{10.1038/nclimate2441}

\leavevmode\vadjust pre{\hypertarget{ref-Braeckman2021}{}}%
Braeckman, U., Pasotti, F., Hoffmann, R., Vázquez, S., Wulff, A.,
Schloss, I. R., \ldots{} Vanreusel, A. (2021). Glacial melt disturbance
shifts community metabolism of an {Antarctic} seafloor ecosystem from
net autotrophy to heterotrophy. \emph{Communications Biology},
\emph{4}(1), 148.
doi:\href{https://doi.org/10.1038/s42003-021-01673-6}{10.1038/s42003-021-01673-6}

\leavevmode\vadjust pre{\hypertarget{ref-Braithwaite2015}{}}%
Braithwaite, J. E., Meeuwig, J. J., Letessier, T. B., Jenner, K. C. S.,
\& Brierley, A. S. (2015). From sea ice to blubber: Linking whale
condition to krill abundance using historical whaling records.
\emph{Polar Biology}, \emph{38}(8), 1195--1202.
doi:\href{https://doi.org/10.1007/s00300-015-1685-0}{10.1007/s00300-015-1685-0}

\leavevmode\vadjust pre{\hypertarget{ref-Brown2004}{}}%
Brown, J. H., Gillooly, J. F., Allen, A. P., Savage, V. M., \& West, G.
B. (2004). Toward a {Metabolic Theory} of {Ecology}. \emph{Ecology},
\emph{85}(7), 1771--1789.
doi:\href{https://doi.org/10.1890/03-9000}{10.1890/03-9000}

\leavevmode\vadjust pre{\hypertarget{ref-Bruder2019}{}}%
Bruder, A., Frainer, A., Rota, T., \& Primicerio, R. (2019). The
{Importance} of {Ecological Networks} in {Multiple-Stressor Research}
and {Management}. \emph{Frontiers in Environmental Science}, \emph{7}.

\leavevmode\vadjust pre{\hypertarget{ref-Bruno2023}{}}%
Bruno, D. O., Riccialdelli, L., Acha, E. M., \& Fernández, D. A. (2023).
Seasonal variation of autochthonous and allochthonous carbon sources for
the first levels of the {Beagle Channel} food web. \emph{Journal of
Marine Systems}, \emph{239}, 103859.
doi:\href{https://doi.org/10.1016/j.jmarsys.2023.103859}{10.1016/j.jmarsys.2023.103859}

\leavevmode\vadjust pre{\hypertarget{ref-Buskey2016}{}}%
Buskey, E. J., White, H. K., \& Esbaugh, A. J. (2016). Impact of {Oil
Spills} on {Marine Life} in the {Gulf} of {Mexico}: {EFFECTS ON
PLANKTON}, {NEKTON}, {AND DEEP-SEA BENTHOS}. \emph{Oceanography},
\emph{29}(3), 174--181. Retrieved from
\url{https://www.jstor.org/stable/24862719}

\leavevmode\vadjust pre{\hypertarget{ref-Campana2018}{}}%
Campana, G. L., Zacher, K., Deregibus, D., Momo, F. R., Wiencke, C., \&
Quartino, M. L. (2018). Succession of {Antarctic} benthic algae ({Potter
Cove}, {South Shetland Islands}): Structural patterns and glacial impact
over a four-year period. \emph{Polar Biology}, \emph{41}(2), 377--396.
doi:\href{https://doi.org/10.1007/s00300-017-2197-x}{10.1007/s00300-017-2197-x}

\leavevmode\vadjust pre{\hypertarget{ref-Chown2022}{}}%
Chown, S. L., Leihy, R. I., Naish, T. R., Brooks, C. M., Convey, P.,
Henley, B. J., \ldots{} Grant, S. M. (2022). Antarctic climate change
and the environment: A decadal synopsis and recommendations for action.

\leavevmode\vadjust pre{\hypertarget{ref-Ciancio2008}{}}%
Ciancio, J. E., Pascual, M. A., Botto, F., Frere, E., \& Iribarne, O.
(2008). Trophic relationships of exotic anadromous salmonids in the
southern {Patagonian Shelf} as inferred from stable isotopes.
\emph{Limnology and Oceanography}, \emph{53}(2), 788--798.
doi:\href{https://doi.org/10.4319/lo.2008.53.2.0788}{10.4319/lo.2008.53.2.0788}

\leavevmode\vadjust pre{\hypertarget{ref-Ciancio2010}{}}%
Ciancio, J., Beauchamp, D. A., \& Pascual, M. (2010). Marine effect of
introduced salmonids: {Prey} consumption by exotic steelhead and
anadromous brown trout in the {Patagonian Continental Shelf}.
\emph{Limnology and Oceanography}, \emph{55}(5), 2181--2192.
doi:\href{https://doi.org/10.4319/lo.2010.55.5.2181}{10.4319/lo.2010.55.5.2181}

\leavevmode\vadjust pre{\hypertarget{ref-Cirtwill2015}{}}%
Cirtwill, A. R., Stouffer, D. B., \& Romanuk, T. N. (2015). Latitudinal
gradients in biotic niche breadth vary across ecosystem types.
\emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{282}(1819), 20151589.
doi:\href{https://doi.org/10.1098/rspb.2015.1589}{10.1098/rspb.2015.1589}

\leavevmode\vadjust pre{\hypertarget{ref-Clark2013}{}}%
Clark, G. F., Stark, J. S., Johnston, E. L., Runcie, J. W., Goldsworthy,
P. M., Raymond, B., \& Riddle, M. J. (2013). Light-driven tipping points
in polar ecosystems. \emph{Global Change Biology}, \emph{19}(12),
3749--3761.
doi:\href{https://doi.org/10.1111/gcb.12337}{10.1111/gcb.12337}

\leavevmode\vadjust pre{\hypertarget{ref-Collins2010}{}}%
Collins, M. A., Brickle, P., Brown, J., \& Belchier, M. (2010). Chapter
{Four} - {The Patagonian Toothfish}: {Biology}, {Ecology} and {Fishery}.
In M. Lesser (Ed.), \emph{Advances in {Marine Biology}} (Vol. 58, pp.
227--300). {Academic Press}.
doi:\href{https://doi.org/10.1016/B978-0-12-381015-1.00004-6}{10.1016/B978-0-12-381015-1.00004-6}

\leavevmode\vadjust pre{\hypertarget{ref-Commendatore2012}{}}%
Commendatore, M. G., Nievas, M. L., Amin, O., \& Esteves, J. L. (2012).
Sources and distribution of aliphatic and polyaromatic hydrocarbons in
coastal sediments from the {Ushuaia Bay} ({Tierra} del {Fuego},
{Patagonia}, {Argentina}). \emph{Marine Environmental Research},
\emph{74}, 20--31.
doi:\href{https://doi.org/10.1016/j.marenvres.2011.11.010}{10.1016/j.marenvres.2011.11.010}

\leavevmode\vadjust pre{\hypertarget{ref-Constable2014}{}}%
Constable, A. J., Melbourne-Thomas, J., Corney, S. P., Arrigo, K. R.,
Barbraud, C., Barnes, D. K. A., \ldots{} Ziegler, P. (2014). Climate
change and {Southern Ocean} ecosystems {I}: How changes in physical
habitats directly affect marine biota. \emph{Global Change Biology},
\emph{20}(10), 3004--3025.
doi:\href{https://doi.org/10.1111/gcb.12623}{10.1111/gcb.12623}

\leavevmode\vadjust pre{\hypertarget{ref-Cordone2023}{}}%
Cordone, G., Galván, D. E., \& Momo, F. R. (2023). Impacts of an
invasion by green crab {Carcinus} maenas on the intertidal food web of a
{Patagonian} rocky shore, {Argentina}. \emph{Marine Ecology Progress
Series}, \emph{713}, 97--115.
doi:\href{https://doi.org/10.3354/meps14336}{10.3354/meps14336}

\leavevmode\vadjust pre{\hypertarget{ref-Cordone2020}{}}%
Cordone, G., Salinas, V., Marina, T. I., Doyle, S. R., Pasotti, F.,
Saravia, L. A., \& Momo, F. R. (2020). Green vs brown food web:
{Effects} of habitat type on multidimensional stability proxies for a
highly-resolved {Antarctic} food web. \emph{Food Webs}, \emph{25},
e00166.
doi:\href{https://doi.org/10.1016/j.fooweb.2020.e00166}{10.1016/j.fooweb.2020.e00166}

\leavevmode\vadjust pre{\hypertarget{ref-Correa2008}{}}%
Correa, C., \& Gross, M. R. (2008). Chinook salmon invade southern
{South America}. \emph{Biological Invasions}, \emph{10}(5), 615--639.
doi:\href{https://doi.org/10.1007/s10530-007-9157-2}{10.1007/s10530-007-9157-2}

\leavevmode\vadjust pre{\hypertarget{ref-Cossi2021}{}}%
Cossi, P. F., Ojeda, M., Chiesa, I. L., Rimondino, G. N., Fraysse, C.,
Calcagno, J., \& Pérez, A. F. (2021). First evidence of microplastics in
the {Marine Protected Area Namuncurá} at {Burdwood Bank}, {Argentina}: A
study on {Henricia} obesa and {Odontaster} penicillatus
({Echinodermata}: {Asteroidea}). \emph{Polar Biology}, \emph{44}(12),
2277--2287.
doi:\href{https://doi.org/10.1007/s00300-021-02959-5}{10.1007/s00300-021-02959-5}

\leavevmode\vadjust pre{\hypertarget{ref-Cote2016}{}}%
Côté, I. M., Darling, E. S., \& Brown, C. J. (2016). Interactions among
ecosystem stressors and their importance in conservation.
\emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{283}(1824), 20152592.
doi:\href{https://doi.org/10.1098/rspb.2015.2592}{10.1098/rspb.2015.2592}

\leavevmode\vadjust pre{\hypertarget{ref-Crain2008}{}}%
Crain, C. M., Kroeker, K., \& Halpern, B. S. (2008). Interactive and
cumulative effects of multiple human stressors in marine systems.
\emph{Ecology Letters}, \emph{11}(12), 1304--1315.
doi:\href{https://doi.org/10.1111/j.1461-0248.2008.01253.x}{10.1111/j.1461-0248.2008.01253.x}

\leavevmode\vadjust pre{\hypertarget{ref-DAlelio2016}{}}%
D'Alelio, D., Libralato, S., Wyatt, T., \& Ribera d'Alcalà, M. (2016).
Ecological-network models link diversity, structure and function in the
plankton food-web. \emph{Scientific Reports}, \emph{6}(1), 21806.
doi:\href{https://doi.org/10.1038/srep21806}{10.1038/srep21806}

\leavevmode\vadjust pre{\hypertarget{ref-Dayton1990}{}}%
Dayton, P. K. (1990). Polar {Benthos}. In \emph{Polar {Oceanography Part
B}: {Chemistry}, {Biology} and {Geology}} (W.O. Smith, Jr., pp.
631--685). {London}: {Academic Press}.

\leavevmode\vadjust pre{\hypertarget{ref-deHaro2022}{}}%
de Haro, J. C., Perez Orsi, H., Cané, S., Di Pangracio, A., Falabella,
V., \& Sapoznikow, A. (2022). {Informe colaborativo sobre el Estado de
situación. Riesgos e impactos de la prospección sísmica en el Mar
Argentino}. {Foro para la Conservación del Mar Patagónico y Áreas de
Influencia}.

\leavevmode\vadjust pre{\hypertarget{ref-Deppeler2020}{}}%
Deppeler, S., Schulz, K. G., Hancock, A., Pascoe, P., McKinlay, J., \&
Davidson, A. (2020). Ocean acidification reduces growth and grazing
impact of {Antarctic} heterotrophic nanoflagellates.
\emph{Biogeosciences}, \emph{17}(16), 4153--4171.
doi:\href{https://doi.org/10.5194/bg-17-4153-2020}{10.5194/bg-17-4153-2020}

\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2023}{}}%
Deregibus, Dolores, Campana, G. L., Neder, C., Barnes, D. K. A., Zacher,
K., Piscicelli, J. M., \ldots{} Quartino, M. L. (2023). Potential
macroalgal expansion and blue carbon gains with northern {Antarctic
Peninsula} glacial retreat. \emph{Marine Environmental Research},
\emph{189}, 106056.
doi:\href{https://doi.org/10.1016/j.marenvres.2023.106056}{10.1016/j.marenvres.2023.106056}

\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2016}{}}%
Deregibus, D., Quartino, M. L., Campana, G. L., Momo, F. R., Wiencke,
C., \& Zacher, K. (2016). Photosynthetic light requirements and vertical
distribution of macroalgae in newly ice-free areas in {Potter Cove},
{South Shetland Islands}, {Antarctica}. \emph{Polar Biology},
\emph{39}(1), 153--166.
doi:\href{https://doi.org/10.1007/s00300-015-1679-y}{10.1007/s00300-015-1679-y}

\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2017}{}}%
Deregibus, D., Quartino, M. L., Zacher, K., Campana, G. L., \& Barnes,
D. K. A. (2017). Understanding the link between sea ice, ice scour and
{Antarctic} benthic biodiversity\textendash the need for cross-station
and international collaboration. \emph{Polar Record}, \emph{53}(2),
143--152.
doi:\href{https://doi.org/10.1017/S0032247416000875}{10.1017/S0032247416000875}

\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2020}{}}%
Deregibus, Dolores, Zacher, K., Bartsch, I., Campana, G. L., Momo, F.
R., Wiencke, C., \ldots{} Quartino, M. L. (2020). Carbon {Balance Under}
a {Changing Light Environment}. In I. Gómez \& P. Huovinen (Eds.),
\emph{Antarctic {Seaweeds}: {Diversity}, {Adaptation} and {Ecosystem
Services}} (pp. 173--191). {Cham}: {Springer International Publishing}.
doi:\href{https://doi.org/10.1007/978-3-030-39448-6_9}{10.1007/978-3-030-39448-6\_9}

\leavevmode\vadjust pre{\hypertarget{ref-DiMauro2022}{}}%
Di Mauro, R., Castillo, S., Pérez, A., Iachetti, C. M., Silva, L.,
Tomba, J. P., \& Chiesa, I. L. (2022). Anthropogenic microfibers are
highly abundant at the {Burdwood Bank} seamount, a protected
sub-{Antarctic} environment in the {Southwestern Atlantic Ocean}.
\emph{Environmental Pollution}, \emph{306}, 119364.
doi:\href{https://doi.org/10.1016/j.envpol.2022.119364}{10.1016/j.envpol.2022.119364}

\leavevmode\vadjust pre{\hypertarget{ref-Dinniman2023}{}}%
Dinniman, M. S., St-Laurent, P., Arrigo, K. R., Hofmann, E. E., \& van
Dijken, G. L. (2023). Sensitivity of the {Relationship Between Antarctic
Ice Shelves} and {Iron Supply} to {Projected Changes} in the
{Atmospheric Forcing}. \emph{Journal of Geophysical Research: Oceans},
\emph{128}(2), e2022JC019210.
doi:\href{https://doi.org/10.1029/2022JC019210}{10.1029/2022JC019210}

\leavevmode\vadjust pre{\hypertarget{ref-Dodino2022}{}}%
Dodino, S., Riccialdelli, L., Polito, M. J., Pütz, K., Brasso, R. L., \&
Raya Rey, A. (2022). Mercury exposure driven by geographic and trophic
factors in {Magellanic} penguins from {Tierra} del {Fuego}. \emph{Marine
Pollution Bulletin}, \emph{174}, 113184.
doi:\href{https://doi.org/10.1016/j.marpolbul.2021.113184}{10.1016/j.marpolbul.2021.113184}

\leavevmode\vadjust pre{\hypertarget{ref-Duarte2011}{}}%
Duarte, C. A., Giarratano, E., Amin, O. A., \& Comoglio, L. I. (2011).
Heavy metal concentrations and biomarkers of oxidative stress in native
mussels ({Mytilus} edulis chilensis) from {Beagle Channel} coast
({Tierra} del {Fuego}, {Argentina}). \emph{Marine Pollution Bulletin},
\emph{62}(8), 1895--1904.
doi:\href{https://doi.org/10.1016/j.marpolbul.2011.05.031}{10.1016/j.marpolbul.2011.05.031}

\leavevmode\vadjust pre{\hypertarget{ref-Duffy2007}{}}%
Duffy, J. E., Cardinale, B. J., France, K. E., McIntyre, P. B.,
Thébault, E., \& Loreau, M. (2007). The functional role of biodiversity
in ecosystems: Incorporating trophic complexity. \emph{Ecology Letters},
\emph{10}(6), 522--538.
doi:\href{https://doi.org/10.1111/j.1461-0248.2007.01037.x}{10.1111/j.1461-0248.2007.01037.x}

\leavevmode\vadjust pre{\hypertarget{ref-Dulvy2014}{}}%
Dulvy, N. K., Fowler, S. L., Musick, J. A., Cavanagh, R. D., Kyne, P.
M., Harrison, L. R., \ldots{} White, W. T. (2014). Extinction risk and
conservation of the world's sharks and rays. \emph{eLife}, \emph{3},
e00590.
doi:\href{https://doi.org/10.7554/eLife.00590}{10.7554/eLife.00590}

\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002a}{}}%
Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Food-web
structure and network theory: {The} role of connectance and size.
\emph{Proceedings of the National Academy of Sciences}, \emph{99}(20),
12917--12922.
doi:\href{https://doi.org/10.1073/pnas.192407699}{10.1073/pnas.192407699}

\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). Network
structure and biodiversity loss in food webs: Robustness increases with
connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
doi:\href{https://doi.org/10.1046/j.1461-0248.2002.00354.x}{10.1046/j.1461-0248.2002.00354.x}

\leavevmode\vadjust pre{\hypertarget{ref-Fernandez2010}{}}%
Fernández, D. A., Ciancio, J., Ceballos, S. G., Riva-Rossi, C., \&
Pascual, M. A. (2010). Chinook salmon ({Oncorhynchus} tshawytscha,
{Walbaum} 1792) in the {Beagle Channel}, {Tierra} del {Fuego}: The onset
of an invasion. \emph{Biological Invasions}, \emph{12}(9), 2991--2997.
doi:\href{https://doi.org/10.1007/s10530-010-9731-x}{10.1007/s10530-010-9731-x}

\leavevmode\vadjust pre{\hypertarget{ref-Ferreira2021}{}}%
Ferreira, M. F., Lo Nostro, F. L., Fernández, D. A., \& Genovese, G.
(2021). Endocrine disruption in the sub {Antarctic} fish
{Patagonotothen} tessellata ({Perciformes}, {Notothenidae}) from {Beagle
Channel} associated to anthropogenic impact. \emph{Marine Environmental
Research}, \emph{171}, 105478.
doi:\href{https://doi.org/10.1016/j.marenvres.2021.105478}{10.1016/j.marenvres.2021.105478}

\leavevmode\vadjust pre{\hypertarget{ref-Fioramonti2022}{}}%
Fioramonti, N. E., Ribeiro Guevara, S., Becker, Y. A., \& Riccialdelli,
L. (2022). Mercury transfer in coastal and oceanic food webs from the
{Southwest Atlantic Ocean}. \emph{Marine Pollution Bulletin},
\emph{175}, 113365.
doi:\href{https://doi.org/10.1016/j.marpolbul.2022.113365}{10.1016/j.marpolbul.2022.113365}

\leavevmode\vadjust pre{\hypertarget{ref-Flores2012}{}}%
Flores, H., Atkinson, A., Kawaguchi, S., Krafft, B., Milinevsky, G.,
Nicol, S., \ldots{} Werner, T. (2012). Impact of climate change on
{Antarctic} krill. \emph{Marine Ecology Progress Series}, \emph{458},
1--19. doi:\href{https://doi.org/10.3354/meps09831}{10.3354/meps09831}

\leavevmode\vadjust pre{\hypertarget{ref-Franco2020}{}}%
Franco, B. C., Combes, V., \& González Carman, V. (2020). Subsurface
{Ocean Warming Hotspots} and {Potential Impacts} on {Marine Species}:
{The Southwest South Atlantic Ocean Case Study}. \emph{Frontiers in
Marine Science}, \emph{7}.

\leavevmode\vadjust pre{\hypertarget{ref-Frelat2022}{}}%
Frelat, R., Kortsch, S., Kröncke, I., Neumann, H., Nordström, M. C.,
Olivier, P. E. N., \& Sell, A. F. (2022). Food web structure and
community composition: A comparison across space and time in the {North
Sea}. \emph{Ecography}, \emph{2022}(2), ecog.05945.
doi:\href{https://doi.org/10.1111/ecog.05945}{10.1111/ecog.05945}

\leavevmode\vadjust pre{\hypertarget{ref-Fretwell2023}{}}%
Fretwell, P. T., Boutet, A., \& Ratcliffe, N. (2023). Record low 2022
{Antarctic} sea ice led to catastrophic breeding failure of emperor
penguins. \emph{Communications Earth \& Environment}, \emph{4}(1), 1--6.
doi:\href{https://doi.org/10.1038/s43247-023-00927-x}{10.1038/s43247-023-00927-x}

\leavevmode\vadjust pre{\hypertarget{ref-Fuentes2016}{}}%
Fuentes, V., Alurralde, G., Meyer, B., Aguirre, G. E., Canepa, A.,
Wölfl, A.-C., \ldots{} Schloss, I. R. (2016). Glacial melting: An
overlooked threat to {Antarctic} krill. \emph{Scientific Reports},
\emph{6}(1), 27234.
doi:\href{https://doi.org/10.1038/srep27234}{10.1038/srep27234}

\leavevmode\vadjust pre{\hypertarget{ref-Funes2020}{}}%
Funes, M. (2020, March). \emph{Efectos de la pesca de arrastre sobre la
estructura trófica del norte del {Golfo San Jorge}} (PhD thesis).

\leavevmode\vadjust pre{\hypertarget{ref-Funes2019}{}}%
Funes, M., Marinao, C., \& Galván, D. E. (2019). Does trawl fisheries
affect the diet of fishes? {A} stable isotope analysis approach*.
\emph{Isotopes in Environmental and Health Studies}, \emph{55}(4),
327--343.
doi:\href{https://doi.org/10.1080/10256016.2019.1626381}{10.1080/10256016.2019.1626381}

\leavevmode\vadjust pre{\hypertarget{ref-Funes2022}{}}%
Funes, M., Saravia, L. A., Cordone, G., Iribarne, O. O., \& Galván, D.
E. (2022). Network analysis suggests changes in food web stability
produced by bottom trawl fishery in {Patagonia}. \emph{Scientific
Reports}, \emph{12}(1), 10876.
doi:\href{https://doi.org/10.1038/s41598-022-14363-y}{10.1038/s41598-022-14363-y}

\leavevmode\vadjust pre{\hypertarget{ref-Gaitan2016}{}}%
Gaitán, E., \& Marí, N. (2016). {Análisis de las comunidades bentónicas
asociadas a capturas de la flota comercial dirigida a Macruronus
magellanicus}. {Instituto Nacional de Investigación y Desarrollo
Pesquero (INIDEP)}.

\leavevmode\vadjust pre{\hypertarget{ref-Galvan2022}{}}%
Galván, D. E., Bovcon, N. D., Cochia, P. D., González, R. A., Lattuca,
M. E., Reinaldo, M. O., \ldots{} Svendsen, G. M. (2022). Changes in the
{Specific} and {Biogeographic Composition} of {Coastal Fish Assemblages}
in {Patagonia}, {Driven} by {Climate Change}, {Fishing}, and {Invasion}
by {Alien Species}. In E. W. Helbling, M. A. Narvarte, R. A. González,
\& V. E. Villafañe (Eds.), \emph{Global {Change} in {Atlantic Coastal
Patagonian Ecosystems}: {A Journey Through Time}} (pp. 205--231).
{Cham}: {Springer International Publishing}.
doi:\href{https://doi.org/10.1007/978-3-030-86676-1_9}{10.1007/978-3-030-86676-1\_9}

\leavevmode\vadjust pre{\hypertarget{ref-Garcia2019}{}}%
Garcia, M. D., Fernández Severini, M. D., Spetter, C., López Abbate, M.
C., Tartara, M. N., Nahuelhual, E. G., \ldots{} Hoffmeyer, M. S. (2019).
Effects of glacier melting on the planktonic communities of two
{Antarctic} coastal areas ({Potter Cove} and {Hope Bay}) in summer.
\emph{Regional Studies in Marine Science}, \emph{30}, 100731.
doi:\href{https://doi.org/10.1016/j.rsma.2019.100731}{10.1016/j.rsma.2019.100731}

\leavevmode\vadjust pre{\hypertarget{ref-Garcia2016}{}}%
Garcia, M. D., Hoffmeyer, M. S., Abbate, M. C. L., Barría De Cao, M. S.,
Pettigrosso, R. E., Almandoz, G. O., \ldots{} Schloss, I. R. (2016).
Micro- and mesozooplankton responses during two contrasting summers in a
coastal {Antarctic} environment. \emph{Polar Biology}, \emph{39}(1),
123--137.
doi:\href{https://doi.org/10.1007/s00300-015-1678-z}{10.1007/s00300-015-1678-z}

\leavevmode\vadjust pre{\hypertarget{ref-Garcia-Borboroglu2008}{}}%
García-Borboroglu, P., Boersma, P. D., Reyes, L., \& Skewgar, E. (2008).
Petroleum {Pollution} and {Penguins}: {Marine Conservation Tools} to
{Reduce} the {Problem}. In \emph{Marine {Pollution}: {New} research}
(Hofer, T.N., pp. 339--356). {New York, USA}: {Nova Science Publishers
Inc.}

\leavevmode\vadjust pre{\hypertarget{ref-Garrott1993}{}}%
Garrott, R. A., Eberhardt, L. L., \& Burn, D. M. (1993). Mortality of
{Sea Otters} in {Prince William Sound Following} the {Exxon Valdez Oil
Spill}. \emph{Marine Mammal Science}, \emph{9}(4), 343--359.
doi:\href{https://doi.org/10.1111/j.1748-7692.1993.tb00468.x}{10.1111/j.1748-7692.1993.tb00468.x}

\leavevmode\vadjust pre{\hypertarget{ref-Gauzens2019}{}}%
Gauzens, B., Barnes, A., Giling, D. P., Hines, J., Jochum, M., Lefcheck,
J. S., \ldots{} Brose, U. (2019). Fluxweb: {An R} package to easily
estimate energy fluxes in food webs. \emph{Methods in Ecology and
Evolution}, \emph{10}(2), 270--279.
doi:\href{https://doi.org/10.1111/2041-210X.13109}{10.1111/2041-210X.13109}

\leavevmode\vadjust pre{\hypertarget{ref-Gellner2023}{}}%
Gellner, G., McCann, K., \& Hastings, A. (2023). Stable diverse food
webs become more common when interactions are more biologically
constrained. \emph{Proceedings of the National Academy of Sciences},
\emph{120}(31), e2212061120.
doi:\href{https://doi.org/10.1073/pnas.2212061120}{10.1073/pnas.2212061120}

\leavevmode\vadjust pre{\hypertarget{ref-Giarratano2010}{}}%
Giarratano, E., \& Amin, O. A. (2010). Heavy metals monitoring in the
southernmost mussel farm of the world ({Beagle Channel}, {Argentina}).
\emph{Ecotoxicology and Environmental Safety}, \emph{73}(6), 1378--1384.
doi:\href{https://doi.org/10.1016/j.ecoenv.2010.06.023}{10.1016/j.ecoenv.2010.06.023}

\leavevmode\vadjust pre{\hypertarget{ref-Gil2011}{}}%
Gil, M. N., Torres, A. I., Amin, O., \& Esteves, J. L. (2011).
Assessment of recent sediment influence in an urban polluted
subantarctic coastal ecosystem. {Beagle Channel} ({Southern Argentina}).
\emph{Marine Pollution Bulletin}, \emph{62}(1), 201--207.
doi:\href{https://doi.org/10.1016/j.marpolbul.2010.10.004}{10.1016/j.marpolbul.2010.10.004}

\leavevmode\vadjust pre{\hypertarget{ref-Glembocki2015}{}}%
Glembocki, N. G., Williams, G. N., Góngora, M. E., Gagliardini, D. A.,
\& Orensanz, J. M. (Lobo). (2015). Synoptic oceanography of {San Jorge
Gulf} ({Argentina}): {A} template for {Patagonian} red shrimp
({Pleoticus} muelleri) spatial dynamics. \emph{Journal of Sea Research},
\emph{95}, 22--35.
doi:\href{https://doi.org/10.1016/j.seares.2014.10.011}{10.1016/j.seares.2014.10.011}

\leavevmode\vadjust pre{\hypertarget{ref-Glorioso1995}{}}%
Glorioso, P. D., \& Flather, R. A. (1995). A barotropic model of the
currents off {SE South America}. \emph{Journal of Geophysical Research:
Oceans}, \emph{100}(C7), 13427--13440.
doi:\href{https://doi.org/10.1029/95JC00942}{10.1029/95JC00942}

\leavevmode\vadjust pre{\hypertarget{ref-Gongora2009}{}}%
Góngora, María E., Bovcon, N. D., \& Cochia, P. D. (2009). Ictiofauna
capturada incidentalmente en la pesquería de langostino patagónico
{Pleoticus} muelleri {Bate}, 1888. \emph{Revista de Biología Marina y
Oceanografía}, \emph{44}(3), 583--593.
doi:\href{https://doi.org/10.4067/S0718-19572009000300006}{10.4067/S0718-19572009000300006}

\leavevmode\vadjust pre{\hypertarget{ref-Gongora2012}{}}%
Góngora, María Eva, González-Zevallos, D., Pettovello, A., \& Mendía, L.
(2012). Caracterización de las principales pesquerías del golfo {San
Jorge Patagonia}, {Argentina}. \emph{Latin American Journal of Aquatic
Research}, \emph{40}(1), 1--11.

\leavevmode\vadjust pre{\hypertarget{ref-Gonzalez-Zevallos2006}{}}%
González-Zevallos, D., \& Yorio, P. (2006). Seabird use of discards and
incidental captures at the {Argentine} hake trawl fishery in the {Golfo
San Jorge}, {Argentina}. \emph{Marine Ecology Progress Series},
\emph{316}, 175--183.
doi:\href{https://doi.org/10.3354/meps316175}{10.3354/meps316175}

\leavevmode\vadjust pre{\hypertarget{ref-Gonzalez-Zevallos2011}{}}%
González-Zevallos, D., \& Yorio, P. (2011). Consumption of discards and
interactions between {Black-browed Albatrosses} ({Thalassarche}
melanophrys) and {Kelp Gulls} ({Larus} dominicanus) at trawl fisheries
in {Golfo San Jorge}, {Argentina}. \emph{Journal of Ornithology},
\emph{152}(4), 827--838.
doi:\href{https://doi.org/10.1007/s10336-011-0657-6}{10.1007/s10336-011-0657-6}

\leavevmode\vadjust pre{\hypertarget{ref-Gorini2021}{}}%
Gorini, F. L., Lukaszewicz, G., \& Giussi, A. R. (2021).
\emph{{Actualización de la estadística pesquera de peces demersales
australes en el Atlántico Sudoccidental (período 2008-2020)}} (\{Informe
T\textbackslash\textquotesingle ecnico Oficial\}) (p. 64). {Mar del
Plata}: {Instituto Nacional de Investigación y Desarrollo Pesquero
(INIDEP)}.

\leavevmode\vadjust pre{\hypertarget{ref-Guihou2020}{}}%
Guihou, K., Piola, A. R., Palma, E. D., \& Chidichimo, M. P. (2020).
Dynamical connections between large marine ecosystems of austral {South
America} based on numerical simulations. \emph{Ocean Science},
\emph{16}(2), 271--290.
doi:\href{https://doi.org/10.5194/os-16-271-2020}{10.5194/os-16-271-2020}

\leavevmode\vadjust pre{\hypertarget{ref-Gutt2001a}{}}%
Gutt, Julian. (2001). On the direct impact of ice on marine benthic
communities, a review. \emph{Polar Biology}, \emph{24}(8), 553--564.
doi:\href{https://doi.org/10.1007/s003000100262}{10.1007/s003000100262}

\leavevmode\vadjust pre{\hypertarget{ref-Gutt2015}{}}%
Gutt, Julian, Bertler, N., Bracegirdle, T. J., Buschmann, A., Comiso,
J., Hosie, G., \ldots{} Xavier, J. C. (2015). The {Southern Ocean}
ecosystem under multiple climate change stresses - an integrated
circumpolar assessment. \emph{Global Change Biology}, \emph{21}(4),
1434--1453.
doi:\href{https://doi.org/10.1111/gcb.12794}{10.1111/gcb.12794}

\leavevmode\vadjust pre{\hypertarget{ref-Gutt2021}{}}%
Gutt, Julian, Isla, E., Xavier, J. C., Adams, B. J., Ahn, I.-Y., Cheng,
C.-H. C., \ldots{} Wall, D. H. (2021). Antarctic ecosystems in
transition \textendash{} life between stresses and opportunities.
\emph{Biological Reviews}, \emph{96}(3), 798--821.
doi:\href{https://doi.org/10.1111/brv.12679}{10.1111/brv.12679}

\leavevmode\vadjust pre{\hypertarget{ref-Gutt2003}{}}%
Gutt, Julian, \& Piepenburg, D. (2003). Scale-dependent impact on
diversity of {Antarctic} benthos caused by grounding of icebergs.
\emph{Marine Ecology Progress Series}, \emph{253}, 77--83.
doi:\href{https://doi.org/10.3354/meps253077}{10.3354/meps253077}

\leavevmode\vadjust pre{\hypertarget{ref-Gutt2001}{}}%
Gutt, Julian, \& Starmans, A. (2001). Quantification of iceberg impact
and benthic recolonisation patterns in the {Weddell Sea} ({Antarctica}).
\emph{Polar Biology}, \emph{24}(8), 615--619.
doi:\href{https://doi.org/10.1007/s003000100263}{10.1007/s003000100263}

\leavevmode\vadjust pre{\hypertarget{ref-Gutt1996}{}}%
Gutt, J., Starmans, A., \& Dieckmann, G. (1996). Impact of iceberg
scouring on polar benthic habitats. \emph{Marine Ecology Progress
Series}, \emph{137}, 311--316.
doi:\href{https://doi.org/10.3354/meps137311}{10.3354/meps137311}

\leavevmode\vadjust pre{\hypertarget{ref-Hendry2018}{}}%
Hendry, K. R., Meredith, M. P., \& Ducklow, H. W. (2018). The marine
system of the {West Antarctic Peninsula}: Status and strategy for
progress. \emph{Philosophical Transactions of the Royal Society A:
Mathematical, Physical and Engineering Sciences}, \emph{376}(2122),
20170179.
doi:\href{https://doi.org/10.1098/rsta.2017.0179}{10.1098/rsta.2017.0179}

\leavevmode\vadjust pre{\hypertarget{ref-Hernandez2019}{}}%
Hernández, E. A., Lopez, J. L., Piquet, A. M.-T., Mac Cormack, W. P., \&
Buma, A. G. J. (2019). Changes in salinity and temperature drive marine
bacterial communities' structure at {Potter Cove}, {Antarctica}.
\emph{Polar Biology}, \emph{42}(12), 2177--2191.
doi:\href{https://doi.org/10.1007/s00300-019-02590-5}{10.1007/s00300-019-02590-5}

\leavevmode\vadjust pre{\hypertarget{ref-Hilborn2017}{}}%
Hilborn, R., Amoroso, R. O., Bogazzi, E., Jensen, O. P., Parma, A. M.,
Szuwalski, C., \& Walters, C. J. (2017). When does fishing forage
species affect their predators? \emph{Fisheries Research}, \emph{191},
211--221.
doi:\href{https://doi.org/10.1016/j.fishres.2017.01.008}{10.1016/j.fishres.2017.01.008}

\leavevmode\vadjust pre{\hypertarget{ref-Hill2012}{}}%
Hill, S. L., Keeble, K., Atkinson, A., \& Murphy, E. J. (2012). A
foodweb model to explore uncertainties in the {South Georgia} shelf
pelagic ecosystem. \emph{Deep Sea Research Part II: Topical Studies in
Oceanography}, \emph{59--60}, 237--252.
doi:\href{https://doi.org/10.1016/j.dsr2.2011.09.001}{10.1016/j.dsr2.2011.09.001}

\leavevmode\vadjust pre{\hypertarget{ref-Hill2013}{}}%
Hill, S. L., Phillips, T., \& Atkinson, A. (2013). Potential {Climate
Change Effects} on the {Habitat} of {Antarctic Krill} in the {Weddell
Quadrant} of the {Southern Ocean}. \emph{PLOS ONE}, \emph{8}(8), e72246.
doi:\href{https://doi.org/10.1371/journal.pone.0072246}{10.1371/journal.pone.0072246}

\leavevmode\vadjust pre{\hypertarget{ref-Hindell2020}{}}%
Hindell, M. A., Reisinger, R. R., Ropert-Coudert, Y., Hückstädt, L. A.,
Trathan, P. N., Bornemann, H., \ldots{} Raymond, B. (2020). Tracking of
marine predators to protect {Southern Ocean} ecosystems. \emph{Nature},
\emph{580}(7801), 87--92.
doi:\href{https://doi.org/10.1038/s41586-020-2126-y}{10.1038/s41586-020-2126-y}

\leavevmode\vadjust pre{\hypertarget{ref-Hoffmann2019}{}}%
Hoffmann, R., Al-Handal, A. Y., Wulff, A., Deregibus, D., Zacher, K.,
Quartino, M. L., \ldots{} Braeckman, U. (2019). Implications of {Glacial
Melt-Related Processes} on the {Potential Primary Production} of a
{Microphytobenthic Community} in {Potter Cove} ({Antarctica}).
\emph{Frontiers in Marine Science}, \emph{6}, 655.
doi:\href{https://doi.org/10.3389/fmars.2019.00655}{10.3389/fmars.2019.00655}

\leavevmode\vadjust pre{\hypertarget{ref-Iken2023}{}}%
Iken, K., Amsler, C. D., Gorman, K. B., Klein, A. G., Galloway, A. W.
E., Amsler, M. O., \ldots{} McClintock, J. B. (2023). Macroalgal input
into the coastal food web along a gradient of seasonal sea ice cover
along the {Western Antarctic Peninsula}. \emph{Marine Ecology Progress
Series}, \emph{718}, 1--22.
doi:\href{https://doi.org/10.3354/meps14388}{10.3354/meps14388}

\leavevmode\vadjust pre{\hypertarget{ref-Irons2000}{}}%
Irons, D. B., Kendall, S. J., Erickson, W. P., McDonald, L. L., \&
Lance, B. K. (2000). Nine {Years After} the {Exxon Valdez Oil Spill}:
{Effects} on {Marine Bird Populations} in {Prince William Sound},
{Alaska}. \emph{The Condor}, \emph{102}(4), 723--737.
doi:\href{https://doi.org/10.1093/condor/102.4.723}{10.1093/condor/102.4.723}

\leavevmode\vadjust pre{\hypertarget{ref-Isla2023}{}}%
Isla, E. (2023). Animal\textendash{{Energy Relationships}} in a
{Changing Ocean}: {The Case} of {Continental Shelf Macrobenthic
Communities} on the {Weddell Sea} and the {Vicinity} of the {Antarctic
Peninsula}. \emph{Biology}, \emph{12}(5), 659.
doi:\href{https://doi.org/10.3390/biology12050659}{10.3390/biology12050659}

\leavevmode\vadjust pre{\hypertarget{ref-Jacob2011}{}}%
Jacob, U., Thierry, A., Brose, U., Arntz, W. E., Berg, S., Brey, T.,
\ldots{} Dunne, J. A. (2011). The {Role} of {Body Size} in {Complex Food
Webs}: {A Cold Case}. In A. Belgrano (Ed.), \emph{Advances in
{Ecological Research}} (Vol. 45, pp. 181--223). {Academic Press}.
doi:\href{https://doi.org/10.1016/B978-0-12-386475-8.00005-8}{10.1016/B978-0-12-386475-8.00005-8}

\leavevmode\vadjust pre{\hypertarget{ref-Jerosch2018}{}}%
Jerosch, K., Pehlke, H., Monien, P., Scharf, F., Weber, L., Kuhn, G.,
\ldots{} Abele, D. (2018). Benthic meltwater fjord habitats formed by
rapid glacier recession on {King George Island}, {Antarctica}.
\emph{Philosophical Transactions of the Royal Society A: Mathematical,
Physical and Engineering Sciences}, \emph{376}(2122), 20170178.
doi:\href{https://doi.org/10.1098/rsta.2017.0178}{10.1098/rsta.2017.0178}

\leavevmode\vadjust pre{\hypertarget{ref-Jordan2007}{}}%
Jordán, F., Benedek, Z., \& Podani, J. (2007). Quantifying positional
importance in food webs: {A} comparison of centrality indices.
\emph{Ecological Modelling}, \emph{205}(1), 270--275.
doi:\href{https://doi.org/10.1016/j.ecolmodel.2007.02.032}{10.1016/j.ecolmodel.2007.02.032}

\leavevmode\vadjust pre{\hypertarget{ref-Kaminskyinprep}{}}%
Kaminsky, J., Bagur, M., Boraso, A., Schloss, I. R., Buschmann, A. H.,
\& Quartino, M. L. (in prep.). Kelp recruitment declines in a
sub-{Antarctic} ecosystem with high sediment inputs and changes in the
understory algae.

\leavevmode\vadjust pre{\hypertarget{ref-Kawaguchi2013}{}}%
Kawaguchi, S., Ishida, A., King, R., Raymond, B., Waller, N., Constable,
A., \ldots{} Ishimatsu, A. (2013). Risk maps for {Antarctic} krill under
projected {Southern Ocean} acidification. \emph{Nature Climate Change},
\emph{3}(9), 843--847.
doi:\href{https://doi.org/10.1038/nclimate1937}{10.1038/nclimate1937}

\leavevmode\vadjust pre{\hypertarget{ref-Kawaguchi2010}{}}%
Kawaguchi, So, Kurihara, H., King, R., Hale, L., Berli, T., Robinson, J.
P., \ldots{} Ishimatsu, A. (2010). Will krill fare well under {Southern
Ocean} acidification? \emph{Biology Letters}, \emph{7}(2), 288--291.
doi:\href{https://doi.org/10.1098/rsbl.2010.0777}{10.1098/rsbl.2010.0777}

\leavevmode\vadjust pre{\hypertarget{ref-Kawaguchi2009}{}}%
Kawaguchi, So, Nicol, S., \& Press, A. (2009). Direct effects of climate
change on the {Antarctic} krill fishery.

\leavevmode\vadjust pre{\hypertarget{ref-Klein2018}{}}%
Klein, E. S., Hill, S. L., Hinke, J. T., Phillips, T., \& Watters, G. M.
(2018). Impacts of rising sea temperature on krill increase risks for
predators in the {Scotia Sea}. \emph{PLOS ONE}, \emph{13}(1), e0191011.
doi:\href{https://doi.org/10.1371/journal.pone.0191011}{10.1371/journal.pone.0191011}

\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2019}{}}%
Kortsch, S., Primicerio, R., Aschan, M., Lind, S., Dolgov, A. V., \&
Planque, B. (2019). Food-web structure varies along environmental
gradients in a high-latitude marine ecosystem. \emph{Ecography},
\emph{42}(2), 295--308.
doi:\href{https://doi.org/10.1111/ecog.03443}{10.1111/ecog.03443}

\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2015}{}}%
Kortsch, S., Primicerio, R., Fossheim, M., Dolgov, A. V., \& Aschan, M.
(2015). Climate change alters the structure of arctic marine food webs
due to poleward shifts of boreal generalists. \emph{Proceedings of the
Royal Society B: Biological Sciences}, \emph{282}(1814), 20151546.
doi:\href{https://doi.org/10.1098/rspb.2015.1546}{10.1098/rspb.2015.1546}

\leavevmode\vadjust pre{\hypertarget{ref-Kratina2012}{}}%
Kratina, P., LeCraw, R. M., Ingram, T., \& Anholt, B. R. (2012).
Stability and persistence of food webs with omnivory: {Is} there a
general pattern? \emph{Ecosphere}, \emph{3}(6), art50.
doi:\href{https://doi.org/10.1890/ES12-00121.1}{10.1890/ES12-00121.1}

\leavevmode\vadjust pre{\hypertarget{ref-Lagger2018}{}}%
Lagger, C., Nime, M., Torre, L., Servetto, N., Tatián, M., \& Sahade, R.
(2018). Climate change, glacier retreat and a new ice-free island offer
new insights on {Antarctic} benthic responses. \emph{Ecography},
\emph{41}(4), 579--591.
doi:\href{https://doi.org/10.1111/ecog.03018}{10.1111/ecog.03018}

\leavevmode\vadjust pre{\hypertarget{ref-Lagger2017}{}}%
Lagger, C., Servetto, N., Torre, L., \& Sahade, R. (2017). Benthic
colonization in newly ice-free soft-bottom areas in an {Antarctic}
fjord. \emph{PLOS ONE}, \emph{12}(11), e0186756.
doi:\href{https://doi.org/10.1371/journal.pone.0186756}{10.1371/journal.pone.0186756}

\leavevmode\vadjust pre{\hypertarget{ref-Latorre2023}{}}%
Latorre, M. P., Iachetti, C. M., Schloss, I. R., Antoni, J., Malits, A.,
De La Rosa, F., \ldots{} Hernando, M. (2023). Summer heatwaves affect
coastal {Antarctic} plankton metabolism and community structure.
\emph{Journal of Experimental Marine Biology and Ecology}, \emph{567},
151926.
doi:\href{https://doi.org/10.1016/j.jembe.2023.151926}{10.1016/j.jembe.2023.151926}

\leavevmode\vadjust pre{\hypertarget{ref-Lattuca2018}{}}%
Lattuca, María Eugenia, Boy, C. C., Vanella, F. A., Barrantes, M. E., \&
Fernández, D. A. (2018). Thermal responses of three native fishes from
estuarine areas of the {Beagle Channel}, and their implications for
climate change. \emph{Hydrobiologia}, \emph{808}(1), 235--249.
doi:\href{https://doi.org/10.1007/s10750-017-3424-8}{10.1007/s10750-017-3424-8}

\leavevmode\vadjust pre{\hypertarget{ref-Lattuca2023}{}}%
Lattuca, María E., Vanella, F. A., Malanga, G., Rubel, M. D., Manríquez,
P. H., Torres, R., \ldots{} Fernández, D. A. (2023). Ocean acidification
and seasonal temperature extremes combine to impair the thermal
physiology of a sub-{Antarctic} fish. \emph{Science of The Total
Environment}, \emph{856}, 159284.
doi:\href{https://doi.org/10.1016/j.scitotenv.2022.159284}{10.1016/j.scitotenv.2022.159284}

\leavevmode\vadjust pre{\hypertarget{ref-Lin2021}{}}%
Lin, Y., Moreno, C., Marchetti, A., Ducklow, H., Schofield, O., Delage,
E., \ldots{} Cassar, N. (2021). Decline in plankton diversity and carbon
flux with reduced sea ice extent along the {Western Antarctic
Peninsula}. \emph{Nature Communications}, \emph{12}(1), 4948.
doi:\href{https://doi.org/10.1038/s41467-021-25235-w}{10.1038/s41467-021-25235-w}

\leavevmode\vadjust pre{\hypertarget{ref-Llorca2012}{}}%
Llorca, M., Farré, M., Tavano, M. S., Alonso, B., Koremblit, G., \&
Barceló, D. (2012). Fate of a broad spectrum of perfluorinated compounds
in soils and biota from {Tierra} del {Fuego} and {Antarctica}.
\emph{Environmental Pollution}, \emph{163}, 158--166.
doi:\href{https://doi.org/10.1016/j.envpol.2011.10.027}{10.1016/j.envpol.2011.10.027}

\leavevmode\vadjust pre{\hypertarget{ref-Lopez-Gappa2022}{}}%
López-Gappa, J. (2022). The {Impact} of {Global Change} on {Marine
Benthic Invertebrates}. In E. W. Helbling, M. A. Narvarte, R. A.
González, \& V. E. Villafañe (Eds.), \emph{Global {Change} in {Atlantic
Coastal Patagonian Ecosystems}: {A Journey Through Time}} (pp.
177--204). {Cham}: {Springer International Publishing}.
doi:\href{https://doi.org/10.1007/978-3-030-86676-1_8}{10.1007/978-3-030-86676-1\_8}

\leavevmode\vadjust pre{\hypertarget{ref-Lopez-Lopez2022}{}}%
López-López, L., Genner, M. J., Tarling, G. A., Saunders, R. A., \&
O'Gorman, E. J. (2022). Ecological {Networks} in the {Scotia Sea}:
{Structural Changes Across Latitude} and {Depth}. \emph{Ecosystems},
\emph{25}(2), 457--470.
doi:\href{https://doi.org/10.1007/s10021-021-00665-1}{10.1007/s10021-021-00665-1}

\leavevmode\vadjust pre{\hypertarget{ref-Manno2022}{}}%
Manno, C., Peck, V. L., Corsi, I., \& Bergami, E. (2022). Under
pressure: {Nanoplastics} as a further stressor for sub-{Antarctic}
pteropods already tackling ocean acidification. \emph{Marine Pollution
Bulletin}, \emph{174}, 113176.
doi:\href{https://doi.org/10.1016/j.marpolbul.2021.113176}{10.1016/j.marpolbul.2021.113176}

\leavevmode\vadjust pre{\hypertarget{ref-Marina2018}{}}%
Marina, T. I., Salinas, V., Cordone, G., Campana, G., Moreira, E.,
Deregibus, D., \ldots{} Momo, F. R. (2018). The {Food Web} of {Potter
Cove} ({Antarctica}): Complexity, structure and function.
\emph{Estuarine, Coastal and Shelf Science}, \emph{200}, 141--151.
doi:\href{https://doi.org/10.1016/j.ecss.2017.10.015}{10.1016/j.ecss.2017.10.015}

\leavevmode\vadjust pre{\hypertarget{ref-Marinainrev}{}}%
Marina, T. I., Schloss, I. R., Lovrich, G. A., Boy, C. C., Bruno, D. O.,
Capitanio, F. L., \ldots{} Riccialdelli, L. (in rev.). The complex
network of trophic interactions in a {Subantarctic} oceanic {Marine
Protected Area}. \emph{Marine Ecology Progress Series}.

\leavevmode\vadjust pre{\hypertarget{ref-Martinez2022}{}}%
Martínez, Patricia A., Wöhler, O. C., Troccoli, G. H., Di Marco, E., \&
Maydana, L. (2022). \emph{{Descripción de las capturas incidentales de
granaderos presentes en los lances dirigidos a merluza negra en la
pesquería argentina de arrastre: período 2010-2019.}} {Instituto
Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.

\leavevmode\vadjust pre{\hypertarget{ref-Martinez2015}{}}%
Martínez, P. A., Wöhler, O. G., \& Troccoli, G. H. (2015). \emph{{La
evolución de la pesquería de merluza negra (Dissostichus eleginoides) en
el espacio marítimo argentino. Periodo 2003- 2014}} (\{Technical
report\} No. 11/15) (p. 12). {Instituto Nacional de Investigación y
Desarrollo Pesquero (INIDEP), Argentina}.

\leavevmode\vadjust pre{\hypertarget{ref-Matano2019}{}}%
Matano, Ricardo P., Palma, E. D., \& Combes, V. (2019). The {Burdwood
Bank Circulation}. \emph{Journal of Geophysical Research: Oceans},
\emph{124}(10), 6904--6926.
doi:\href{https://doi.org/10.1029/2019JC015001}{10.1029/2019JC015001}

\leavevmode\vadjust pre{\hypertarget{ref-Matano2010}{}}%
Matano, R. P., Palma, E. D., \& Piola, A. R. (2010). The influence of
the {Brazil} and {Malvinas Currents} on the {Southwestern Atlantic
Shelf} circulation. \emph{Ocean Science}, \emph{6}(4), 983--995.
doi:\href{https://doi.org/10.5194/os-6-983-2010}{10.5194/os-6-983-2010}

\leavevmode\vadjust pre{\hypertarget{ref-McCann1998}{}}%
McCann, K., Hastings, A., \& Huxel, G. R. (1998). Weak trophic
interactions and the balance of nature. \emph{Nature}, \emph{395}(6704),
794--798. doi:\href{https://doi.org/10.1038/27427}{10.1038/27427}

\leavevmode\vadjust pre{\hypertarget{ref-Menge1995}{}}%
Menge, B. A. (1995). Indirect {Effects} in {Marine Rocky Intertidal
Interaction Webs}: {Patterns} and {Importance}. \emph{Ecological
Monographs}, \emph{65}(1), 21--74.
doi:\href{https://doi.org/10.2307/2937158}{10.2307/2937158}

\leavevmode\vadjust pre{\hypertarget{ref-Meredith2018}{}}%
Meredith, M. P., Falk, U., Bers, A. V., Mackensen, A., Schloss, I. R.,
Ruiz Barlett, E., \ldots{} Abele, D. (2018). Anatomy of a glacial
meltwater discharge event in an {Antarctic} cove. \emph{Philosophical
Transactions of the Royal Society A: Mathematical, Physical and
Engineering Sciences}, \emph{376}(2122), 20170163.
doi:\href{https://doi.org/10.1098/rsta.2017.0163}{10.1098/rsta.2017.0163}

\leavevmode\vadjust pre{\hypertarget{ref-Meyer2017}{}}%
Meyer, B., Freier, U., Grimm, V., Groeneveld, J., Hunt, B. P. V.,
Kerwath, S., \ldots{} Yilmaz, N. I. (2017). The winter pack-ice zone
provides a sheltered but food-poor habitat for larval {Antarctic} krill.
\emph{Nature Ecology \& Evolution}, \emph{1}(12), 1853--1861.
doi:\href{https://doi.org/10.1038/s41559-017-0368-3}{10.1038/s41559-017-0368-3}

\leavevmode\vadjust pre{\hypertarget{ref-Michel2019}{}}%
Michel, L. N., Danis, B., Dubois, P., Eleaume, M., Fournier, J., Gallut,
C., \ldots{} Lepoint, G. (2019). Increased sea ice cover alters food web
structure in {East Antarctica}. \emph{Scientific Reports}, \emph{9}(1),
8062.
doi:\href{https://doi.org/10.1038/s41598-019-44605-5}{10.1038/s41598-019-44605-5}

\leavevmode\vadjust pre{\hypertarget{ref-Mintenbeck2012}{}}%
Mintenbeck, K., Barrera-Oro, E. R., Brey, T., Jacob, U., Knust, R.,
Mark, F. C., \ldots{} Arntz, W. E. (2012). Impact of {Climate Change} on
{Fishes} in {Complex Antarctic Ecosystems}. In U. Jacob \& G. Woodward
(Eds.), \emph{Advances in {Ecological Research}} (Vol. 46, pp.
361--426). {Burlington}: {Academic Press}.
doi:\href{https://doi.org/10.1016/B978-0-12-396992-7.00006-X}{10.1016/B978-0-12-396992-7.00006-X}

\leavevmode\vadjust pre{\hypertarget{ref-Montoya2009}{}}%
Montoya, JoséM., Woodward, G., Emmerson, M. C., \& Solé, R. V. (2009).
Press perturbations and indirect effects in real food webs.
\emph{Ecology}, \emph{90}(9), 2426--2433.
doi:\href{https://doi.org/10.1890/08-0657.1}{10.1890/08-0657.1}

\leavevmode\vadjust pre{\hypertarget{ref-Moore1974}{}}%
Moore, S. F., \& Dwyer, R. L. (1974). Effects of oil on marine
organisms: {A} critical assessment of published data. \emph{Water
Research}, \emph{8}(10), 819--827.
doi:\href{https://doi.org/10.1016/0043-1354(74)90028-1}{10.1016/0043-1354(74)90028-1}

\leavevmode\vadjust pre{\hypertarget{ref-Moy2009}{}}%
Moy, A. D., Howard, W. R., Bray, S. G., \& Trull, T. W. (2009). Reduced
calcification in modern {Southern Ocean} planktonic foraminifera.
\emph{Nature Geoscience}, \emph{2}(4), 276--280.
doi:\href{https://doi.org/10.1038/ngeo460}{10.1038/ngeo460}

\leavevmode\vadjust pre{\hypertarget{ref-Murphy2007}{}}%
Murphy, E. J., Trathan, P. N., Watkins, J. L., Reid, K., Meredith, M.
P., Forcada, J., \ldots{} Rothery, P. (2007). Climatically driven
fluctuations in {Southern Ocean} ecosystems. \emph{Proceedings of the
Royal Society B: Biological Sciences}, \emph{274}(1629), 3057--3067.
doi:\href{https://doi.org/10.1098/rspb.2007.1180}{10.1098/rspb.2007.1180}

\leavevmode\vadjust pre{\hypertarget{ref-Murphy2006}{}}%
Murphy, E. j., Watkins, J. l., Trathan, P. n., Reid, K., Meredith, M.
p., Thorpe, S. e., \ldots{} Fleming, A. h. (2006). Spatial and temporal
operation of the {Scotia Sea} ecosystem: A review of large-scale links
in a krill centred food web. \emph{Philosophical Transactions of the
Royal Society B: Biological Sciences}, \emph{362}(1477), 113--148.
doi:\href{https://doi.org/10.1098/rstb.2006.1957}{10.1098/rstb.2006.1957}

\leavevmode\vadjust pre{\hypertarget{ref-Nardi2019}{}}%
Nardi, C. F., Fernández, D. A., Vanella, F. A., \& Chalde, T. (2019).
The expansion of exotic {Chinook} salmon ({Oncorhynchus} tshawytscha) in
the extreme south of {Patagonia}: An environmental {DNA} approach.
\emph{Biological Invasions}, \emph{21}(4), 1415--1425.
doi:\href{https://doi.org/10.1007/s10530-018-1908-8}{10.1007/s10530-018-1908-8}

\leavevmode\vadjust pre{\hypertarget{ref-Neder2023}{}}%
Neder, C. (2023). \emph{{El bentos antártico y su respuesta al cambio
climático: una aproximación usando modelos de distribución de especies
como caso de estudio en caleta Potter}} (PhD thesis). Universidad
Nacional de Córdoba, {Córdoba, Argentina}.

\leavevmode\vadjust pre{\hypertarget{ref-Neder2022}{}}%
Neder, C., Fofonova, V., Androsov, A., Kuznetsov, I., Abele, D., Falk,
U., \ldots{} Jerosch, K. (2022). Modelling suspended particulate matter
dynamics at an {Antarctic} fjord impacted by glacier melt. \emph{Journal
of Marine Systems}, \emph{231}, 103734.
doi:\href{https://doi.org/10.1016/j.jmarsys.2022.103734}{10.1016/j.jmarsys.2022.103734}

\leavevmode\vadjust pre{\hypertarget{ref-Nilsson2016}{}}%
Nilsson, K. A., \& McCann, K. S. (2016). Interaction strength
revisited\textemdash clarifying the role of energy flux for food web
stability. \emph{Theoretical Ecology}, \emph{9}(1), 59--71.
doi:\href{https://doi.org/10.1007/s12080-015-0282-8}{10.1007/s12080-015-0282-8}

\leavevmode\vadjust pre{\hypertarget{ref-Nowacek2015}{}}%
Nowacek, D. P., Clark, C. W., Mann, D., Miller, P. J., Rosenbaum, H. C.,
Golden, J. S., \ldots{} Southall, B. L. (2015). Marine seismic surveys
and ocean noise: Time for coordinated and prudent planning.
\emph{Frontiers in Ecology and the Environment}, \emph{13}(7), 378--386.
doi:\href{https://doi.org/10.1890/130286}{10.1890/130286}

\leavevmode\vadjust pre{\hypertarget{ref-OGorman2012}{}}%
O'Gorman, E. J., Fitch, J. E., \& Crowe, T. P. (2012). Multiple
anthropogenic stressors and the structural properties of food webs.
\emph{Ecology}, \emph{93}(3), 441--448.
doi:\href{https://doi.org/10.1890/11-0982.1}{10.1890/11-0982.1}

\leavevmode\vadjust pre{\hypertarget{ref-OGorman2019}{}}%
O'Gorman, E. J., Petchey, O. L., Faulkner, K. J., Gallo, B., Gordon, T.
A. C., Neto-Cerejeira, J., \ldots{} Woodward, G. (2019). A simple model
predicts how warming simplifies wild food webs. \emph{Nature Climate
Change}, \emph{9}(8), 611--616.
doi:\href{https://doi.org/10.1038/s41558-019-0513-x}{10.1038/s41558-019-0513-x}

\leavevmode\vadjust pre{\hypertarget{ref-Ojeda2021}{}}%
Ojeda, M., Cossi, P. F., Rimondino, G. N., Chiesa, I. L., Boy, C. C., \&
Pérez, A. F. (2021). Microplastics pollution in the intertidal limpet,
{Nacella} magellanica, from {Beagle Channel} ({Argentina}).
\emph{Science of The Total Environment}, \emph{795}, 148866.
doi:\href{https://doi.org/10.1016/j.scitotenv.2021.148866}{10.1016/j.scitotenv.2021.148866}

\leavevmode\vadjust pre{\hypertarget{ref-Oliver2018}{}}%
Oliver, E. C. J., Donat, M. G., Burrows, M. T., Moore, P. J., Smale, D.
A., Alexander, L. V., \ldots{} Wernberg, T. (2018). Longer and more
frequent marine heatwaves over the past century. \emph{Nature
Communications}, \emph{9}(1), 1324.
doi:\href{https://doi.org/10.1038/s41467-018-03732-9}{10.1038/s41467-018-03732-9}

\leavevmode\vadjust pre{\hypertarget{ref-Olivier2019}{}}%
Olivier, P., Frelat, R., Bonsdorff, E., Kortsch, S., Kröncke, I.,
Möllmann, C., \ldots{} Nordström, M. C. (2019). Exploring the temporal
variability of a food web using long-term biomonitoring data.
\emph{Ecography}, \emph{42}(12), 2107--2121.
doi:\href{https://doi.org/10.1111/ecog.04461}{10.1111/ecog.04461}

\leavevmode\vadjust pre{\hypertarget{ref-Orgeira2021}{}}%
Orgeira, J. L., Alvarez, F., \& Salvó, C. S. (2021). The same pathway to
the {Weddell Sea} birdlife, after 65 years: Similarities in the species
composition, richness and abundances. \emph{Czech Polar Reports},
\emph{11}(2), 291--304.
doi:\href{https://doi.org/10.5817/CPR2021-2-20}{10.5817/CPR2021-2-20}

\leavevmode\vadjust pre{\hypertarget{ref-Orr2020}{}}%
Orr, J. A., Vinebrooke, R. D., Jackson, M. C., Kroeker, K. J., Kordas,
R. L., Mantyka-Pringle, C., \ldots{} Piggott, J. J. (2020). Towards a
unified study of multiple stressors: Divisions and common goals across
research disciplines. \emph{Proceedings of the Royal Society B:
Biological Sciences}, \emph{287}(1926), 20200421.
doi:\href{https://doi.org/10.1098/rspb.2020.0421}{10.1098/rspb.2020.0421}

\leavevmode\vadjust pre{\hypertarget{ref-Paine1996}{}}%
Paine, R. T., Ruesink, J. L., Sun, A., Soulanille, E. L., Wonham, M. J.,
Harley, C. D. G., \ldots{} Secord, D. L. (1996). {TROUBLE ON OILED
WATERS}: {Lessons} from the {\emph{Exxon Valdez}} {Oil Spill}.
\emph{Annual Review of Ecology and Systematics}, \emph{27}(1), 197--235.
doi:\href{https://doi.org/10.1146/annurev.ecolsys.27.1.197}{10.1146/annurev.ecolsys.27.1.197}

\leavevmode\vadjust pre{\hypertarget{ref-Pallin2023}{}}%
Pallin, L. J., Kellar, N. M., Steel, D., Botero-Acosta, N., Baker, C.
S., Conroy, J. A., \ldots{} Friedlaender, A. S. (2023). A surplus no
more? {Variation} in krill availability impacts reproductive rates of
{Antarctic} baleen whales. \emph{Global Change Biology}, \emph{29}(8),
2108--2121.
doi:\href{https://doi.org/10.1111/gcb.16559}{10.1111/gcb.16559}

\leavevmode\vadjust pre{\hypertarget{ref-Pante2023}{}}%
Pante, E., Simon-Bouhet, B., \& Irisson, J. (2023). Marmap: {Import},
{Plot} and {Analyze Bathymetric} and {Topographic Data}.

\leavevmode\vadjust pre{\hypertarget{ref-Pasotti2015}{}}%
Pasotti, F., Saravia, L. A., Troch, M. D., Tarantelli, M. S., Sahade,
R., \& Vanreusel, A. (2015). Benthic {Trophic Interactions} in an
{Antarctic Shallow Water Ecosystem Affected} by {Recent Glacier
Retreat}. \emph{PLOS ONE}, \emph{10}(11), e0141742.
doi:\href{https://doi.org/10.1371/journal.pone.0141742}{10.1371/journal.pone.0141742}

\leavevmode\vadjust pre{\hypertarget{ref-Pasti2021}{}}%
Pasti, A. T., Bovcon, N. D., Ruibal-Núñez, J., Navoa, X., Jacobi, K. J.,
\& Galván, D. E. (2021). The diet of {Mustelus} schmitti in areas with
and without commercial bottom trawling ({Central Patagonia},
{Southwestern Atlantic}): {Is} it evidence of trophic interaction with
the {Patagonian} shrimp fishery? \emph{Food Webs}, \emph{29}, e00214.
doi:\href{https://doi.org/10.1016/j.fooweb.2021.e00214}{10.1016/j.fooweb.2021.e00214}

\leavevmode\vadjust pre{\hypertarget{ref-Pauli2021}{}}%
Pauli, N.-C., Flintrop, C. M., Konrad, C., Pakhomov, E. A., Swoboda, S.,
Koch, F., \ldots{} Iversen, M. H. (2021). Krill and salp faecal pellets
contribute equally to the carbon flux at the {Antarctic Peninsula}.
\emph{Nature Communications}, \emph{12}(1), 7168.
doi:\href{https://doi.org/10.1038/s41467-021-27436-9}{10.1038/s41467-021-27436-9}

\leavevmode\vadjust pre{\hypertarget{ref-Pecuchet2022}{}}%
Pecuchet, L., Jørgensen, L. L., Dolgov, A. V., Eriksen, E., Husson, B.,
Skern-Mauritzen, M., \& Primicerio, R. (2022). Spatio-temporal turnover
and drivers of bentho-demersal community and food web structure in a
high-latitude marine ecosystem. \emph{Diversity and Distributions},
\emph{28}(12), 2503--2520.
doi:\href{https://doi.org/10.1111/ddi.13580}{10.1111/ddi.13580}

\leavevmode\vadjust pre{\hypertarget{ref-Pecuchet2020}{}}%
Pecuchet, L., Lindegren, M., Kortsch, S., Całkiewicz, J., Jurgensone,
I., Margonski, P., \ldots{} Nordström, M. C. (2020). Spatio-temporal
dynamics of multi-trophic communities reveal ecosystem-wide functional
reorganization. \emph{Ecography}, \emph{43}(2), 197--208.
doi:\href{https://doi.org/10.1111/ecog.04643}{10.1111/ecog.04643}

\leavevmode\vadjust pre{\hypertarget{ref-Perez2021}{}}%
Pérez, A. F., Ojeda, M., Cossi, P. F., Rimondino, G. N., Chiesa, I. L.,
Fraysse, C., \& Calcagno, J. (2021). {Microplásticos en organismos
marinos de altas latitudes}. In \emph{{I Jornadas de la Red Científica
Argentina para el estudio de los plásticos y sus impactos en el ambiente
(SEPIA)}}.

\leavevmode\vadjust pre{\hypertarget{ref-Perez2020}{}}%
Pérez, Analía F., Ojeda, M., Rimondino, G. N., Chiesa, I. L., Di Mauro,
R., Boy, C. C., \& Calcagno, J. A. (2020). First report of microplastics
presence in the mussel {Mytilus} chilensis from {Ushuaia Bay} ({Beagle
Channel}, {Tierra} del {Fuego}, {Argentina}). \emph{Marine Pollution
Bulletin}, \emph{161}, 111753.
doi:\href{https://doi.org/10.1016/j.marpolbul.2020.111753}{10.1016/j.marpolbul.2020.111753}

\leavevmode\vadjust pre{\hypertarget{ref-Perry2020}{}}%
Perry, F. A., Kawaguchi, S., Atkinson, A., Sailley, S. F., Tarling, G.
A., Mayor, D. J., \ldots{} Cooper, A. (2020).
Temperature\textendash{{Induced Hatch Failure}} and {Nauplii
Malformation} in {Antarctic Krill}. \emph{Frontiers in Marine Science},
\emph{7}.

\leavevmode\vadjust pre{\hypertarget{ref-Peterson2001}{}}%
Peterson, C. H. (2001). The {`{Exxon Valdez}'} oil spill in {Alaska}:
{Acute}, indirect and chronic effects on the ecosystem. In
\emph{Advances in {Marine Biology}} (Vol. 39, pp. 1--103). {Academic
Press}.
doi:\href{https://doi.org/10.1016/S0065-2881(01)39008-9}{10.1016/S0065-2881(01)39008-9}

\leavevmode\vadjust pre{\hypertarget{ref-Pineda-Metz2019a}{}}%
Pineda-Metz, S. E. A. (2019). \emph{Benthic communities of the {Weddell
Sea}: Past, present and future} (PhD thesis). University of Bremen,
{Germany}.

\leavevmode\vadjust pre{\hypertarget{ref-Pineda-Metz2020}{}}%
Pineda-Metz, S. E. A., Gerdes, D., \& Richter, C. (2020). Benthic fauna
declined on a whitening {Antarctic} continental shelf. \emph{Nature
Communications}, \emph{11}(1), 2226.
doi:\href{https://doi.org/10.1038/s41467-020-16093-z}{10.1038/s41467-020-16093-z}

\leavevmode\vadjust pre{\hypertarget{ref-Pinkerton2021}{}}%
Pinkerton, M. H., Boyd, P. W., Deppeler, S., Hayward, A., Höfer, J., \&
Moreau, S. (2021). Evidence for the {Impact} of {Climate Change} on
{Primary Producers} in the {Southern Ocean}. \emph{Frontiers in Ecology
and Evolution}, \emph{9}.

\leavevmode\vadjust pre{\hypertarget{ref-Pinones2016}{}}%
Piñones, A., \& Fedorov, A. V. (2016). Projected changes of {Antarctic}
krill habitat by the end of the 21st century. \emph{Geophysical Research
Letters}, \emph{43}(16), 8580--8589.
doi:\href{https://doi.org/10.1002/2016GL069656}{10.1002/2016GL069656}

\leavevmode\vadjust pre{\hypertarget{ref-Piola2009}{}}%
Piola, A. R., \& Falabella, V. (2009). {El mar Patagónico}. In
\emph{{Atlas del Mar Patagónico. Especies y Espacios}} (Falabella, V.,
Campagna, C. y Croxall, J. Ed., pp. 54--75). {Buenos Aires, Argentina}:
{Wildlife Conservation Society y Birdlife Internacional}.

\leavevmode\vadjust pre{\hypertarget{ref-Polazzo2022}{}}%
Polazzo, F., Marina, T. I., Crettaz-Minaglia, M., \& Rico, A. (2022).
Food web rewiring drives long-term compositional differences and
late-disturbance interactions at the community level. \emph{Proceedings
of the National Academy of Sciences}, \emph{119}(17), e2117364119.
doi:\href{https://doi.org/10.1073/pnas.2117364119}{10.1073/pnas.2117364119}

\leavevmode\vadjust pre{\hypertarget{ref-Poloczanska2013}{}}%
Poloczanska, E. S., Brown, C. J., Sydeman, W. J., Kiessling, W.,
Schoeman, D. S., Moore, P. J., \ldots{} Richardson, A. J. (2013). Global
imprint of climate change on marine life. \emph{Nature Climate Change},
\emph{3}(10), 919--925.
doi:\href{https://doi.org/10.1038/nclimate1958}{10.1038/nclimate1958}

\leavevmode\vadjust pre{\hypertarget{ref-Quartino2008}{}}%
Quartino, M. L., \& Boraso de Zaixso, A. L. (2008). Summer macroalgal
biomass in {Potter Cove}, {South Shetland Islands}, {Antarctica}: Its
production and flux to the ecosystem. \emph{Polar Biology},
\emph{31}(3), 281--294.
doi:\href{https://doi.org/10.1007/s00300-007-0356-1}{10.1007/s00300-007-0356-1}

\leavevmode\vadjust pre{\hypertarget{ref-Quartino2013}{}}%
Quartino, María Liliana, Deregibus, D., Campana, G. L., Latorre, G. E.
J., \& Momo, F. R. (2013). Evidence of {Macroalgal Colonization} on
{Newly Ice-Free Areas} following {Glacial Retreat} in {Potter Cove}
({South Shetland Islands}), {Antarctica}. \emph{PLoS ONE}, \emph{8}(3),
e58223.
doi:\href{https://doi.org/10.1371/journal.pone.0058223}{10.1371/journal.pone.0058223}

\leavevmode\vadjust pre{\hypertarget{ref-Raymond2011}{}}%
Raymond, B. (2011). \emph{A circumpolar pelagic regionalisation of the
{Southern Ocean}. {CCAMLR WS-MPA}, {Brest}, {France}, 29
{Aug}\textendash 2 {Sep} 2011. {Document WS-MPA-11}/6.
{http://data.aad.gov.au/regionalisation}}.

\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2020}{}}%
Riccialdelli, L., Becker, Y. A., Fioramonti, N. E., Torres, M., Bruno,
D. O., Rey, A. R., \& Fernández, D. A. (2020). Trophic structure of
southern marine ecosystems: A comparative isotopic analysis from the
{Beagle Channel} to the oceanic {Burdwood Bank} area under a wasp-waist
assumption. \emph{Marine Ecology Progress Series}, \emph{655}, 1--27.
doi:\href{https://doi.org/10.3354/meps13524}{10.3354/meps13524}

\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2013}{}}%
Riccialdelli, L., Newsome, S. D., Dellabianca, N. A., Bastida, R.,
Fogel, M. L., \& Goodall, R. N. P. (2013). Ontogenetic diet shift in
{Commerson}'s dolphin ({Cephalorhynchus} commersonii commersonii) off
{Tierra} del {Fuego}. \emph{Polar Biology}, \emph{36}(5), 617--627.
doi:\href{https://doi.org/10.1007/s00300-013-1289-5}{10.1007/s00300-013-1289-5}

\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2017}{}}%
Riccialdelli, L., Newsome, S. D., Fogel, M. L., \& Fernández, D. A.
(2017). Trophic interactions and food web structure of a subantarctic
marine food web in the {Beagle Channel}: {Bahía Lapataia}, {Argentina}.
\emph{Polar Biology}, \emph{40}(4), 807--821.
doi:\href{https://doi.org/10.1007/s00300-016-2007-x}{10.1007/s00300-016-2007-x}

\leavevmode\vadjust pre{\hypertarget{ref-Rincon-Diaz2021}{}}%
Rincón-Díaz, M. P., Bovcon, N. D., Cochia, P. D., Góngora, M. E., \&
Galván, D. E. (2021). Fish functional diversity as an indicator of
resilience to industrial fishing in {Patagonia Argentina}. \emph{Journal
of Fish Biology}, \emph{99}(5), 1650--1667.
doi:\href{https://doi.org/10.1111/jfb.14873}{10.1111/jfb.14873}

\leavevmode\vadjust pre{\hypertarget{ref-Rodriguez2022}{}}%
Rodriguez, I. D., Marina, T. I., Schloss, I. R., \& Saravia, L. A.
(2022). Marine food webs are more complex but less stable in
sub-{Antarctic} ({Beagle Channel}, {Argentina}) than in {Antarctic}
({Potter Cove}, {Antarctic Peninsula}) regions. \emph{Marine
Environmental Research}, \emph{174}, 105561.
doi:\href{https://doi.org/10.1016/j.marenvres.2022.105561}{10.1016/j.marenvres.2022.105561}

\leavevmode\vadjust pre{\hypertarget{ref-Rossi2019}{}}%
Rossi, L., Sporta Caputi, S., Calizza, E., Careddu, G., Oliverio, M.,
Schiaparelli, S., \& Costantini, M. L. (2019). Antarctic food web
architecture under varying dynamics of sea ice cover. \emph{Scientific
Reports}, \emph{9}(1), 12454.
doi:\href{https://doi.org/10.1038/s41598-019-48245-7}{10.1038/s41598-019-48245-7}

\leavevmode\vadjust pre{\hypertarget{ref-Rowlands2021}{}}%
Rowlands, E., Galloway, T., Cole, M., Lewis, C., Peck, V., Thorpe, S.,
\& Manno, C. (2021). The {Effects} of {Combined Ocean Acidification} and
{Nanoplastic Exposures} on the {Embryonic Development} of {Antarctic
Krill}. \emph{Frontiers in Marine Science}, \emph{8}.

\leavevmode\vadjust pre{\hypertarget{ref-Ruckamp2011}{}}%
Rückamp, M., Braun, M., Suckro, S., \& Blindow, N. (2011). Observed
glacial changes on the {King George Island} ice cap, {Antarctica}, in
the last decade. \emph{Global and Planetary Change}, \emph{79}(1-2),
99--109.
doi:\href{https://doi.org/10.1016/j.gloplacha.2011.06.009}{10.1016/j.gloplacha.2011.06.009}

\leavevmode\vadjust pre{\hypertarget{ref-RuibalNunez2020}{}}%
Ruibal Nuñez, J. (2020). \emph{{Impacto ecológico de la actividad
pesquera en las poblaciones de condrictios en el litoral de la Provincia
de Chubut y Golfo San Jorge}} (PhD thesis). Universidad Nacional de Mar
del Plata (UNMdP), {Argentina}.

\leavevmode\vadjust pre{\hypertarget{ref-Sahade2015}{}}%
Sahade, R., Lagger, C., Torre, L., Momo, F., Monien, P., Schloss, I.,
\ldots{} Abele, D. (2015). Climate change and glacier retreat drive
shifts in an {Antarctic} benthic ecosystem. \emph{Science Advances},
\emph{1}(10), e1500050.
doi:\href{https://doi.org/10.1126/sciadv.1500050}{10.1126/sciadv.1500050}

\leavevmode\vadjust pre{\hypertarget{ref-Sailley2013}{}}%
Sailley, S. F., Ducklow, H. W., Moeller, H. V., Fraser, W. R.,
Schofield, O. M., Steinberg, D. K., \ldots{} Doney, S. C. (2013). Carbon
fluxes and pelagic ecosystem dynamics near two western {Antarctic
Peninsula Adélie} penguin colonies: An inverse model approach.
\emph{Marine Ecology Progress Series}, \emph{492}, 253--272.
doi:\href{https://doi.org/10.3354/meps10534}{10.3354/meps10534}

\leavevmode\vadjust pre{\hypertarget{ref-Saravia2021}{}}%
Saravia, J., Paschke, K., Oyarzún-Salazar, R., Cheng, C.-H. C., Navarro,
J. M., \& Vargas-Chacoff, L. (2021). Effects of warming rates on
physiological and molecular components of response to {CTMax} heat
stress in the {Antarctic} fish {Harpagifer} antarcticus. \emph{Journal
of Thermal Biology}, \emph{99}, 103021.
doi:\href{https://doi.org/10.1016/j.jtherbio.2021.103021}{10.1016/j.jtherbio.2021.103021}

\leavevmode\vadjust pre{\hypertarget{ref-Saunders2019}{}}%
Saunders, R. A., Hill, S. L., Tarling, G. A., \& Murphy, E. J. (2019).
Myctophid {Fish} ({Family Myctophidae}) {Are Central Consumers} in the
{Food Web} of the {Scotia Sea} ({Southern Ocean}). \emph{Frontiers in
Marine Science}, \emph{6}.

\leavevmode\vadjust pre{\hypertarget{ref-Schejter2021}{}}%
Schejter, L., \& Albano, M. (2021). Benthic communities at the marine
protected area {Namuncurá}/{Burdwood} bank, {SW Atlantic Ocean}:
Detection of vulnerable marine ecosystems and contributions to the
assessment of the rezoning process. \emph{Polar Biology}, \emph{44}(10),
2023--2037.
doi:\href{https://doi.org/10.1007/s00300-021-02936-y}{10.1007/s00300-021-02936-y}

\leavevmode\vadjust pre{\hypertarget{ref-Schloss2012}{}}%
Schloss, I. R., Abele, D., Moreau, S., Demers, S., Bers, A. V.,
González, O., \& Ferreyra, G. A. (2012). Response of phytoplankton
dynamics to 19-year (1991\textendash 2009) climate trends in {Potter
Cove} ({Antarctica}). \emph{Journal of Marine Systems}, \emph{92}(1),
53--66.
doi:\href{https://doi.org/10.1016/j.jmarsys.2011.10.006}{10.1016/j.jmarsys.2011.10.006}

\leavevmode\vadjust pre{\hypertarget{ref-Schloss2023}{}}%
Schloss, I. R., Pizarro, G., Cadaillon, A. M., Giesecke, R., Hernando,
M. P., Almandoz, G. O., \ldots{} Ruiz, C. (2023). Alexandrium catenella
dynamics and paralytic shellfish toxins distribution along the {Beagle
Channel} (southern {Patagonia}). \emph{Journal of Marine Systems},
\emph{239}, 103856.
doi:\href{https://doi.org/10.1016/j.jmarsys.2022.103856}{10.1016/j.jmarsys.2022.103856}

\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2011}{}}%
Schmidt, K., Atkinson, A., Steigenberger, S., Fielding, S., Lindsay, M.
C. M., Pond, D. W., \ldots{} Achterberg, E. P. (2011). Seabed foraging
by {Antarctic} krill: {Implications} for stock assessment,
bentho-pelagic coupling, and the vertical transfer of iron.
\emph{Limnology and Oceanography}, \emph{56}(4), 1411--1428.
doi:\href{https://doi.org/10.4319/lo.2011.56.4.1411}{10.4319/lo.2011.56.4.1411}

\leavevmode\vadjust pre{\hypertarget{ref-Seco2021}{}}%
Seco, J., Aparício, S., Brierley, A. S., Bustamante, P., Ceia, F. R.,
Coelho, J. P., \ldots{} Xavier, J. C. (2021). Mercury biomagnification
in a {Southern Ocean} food web. \emph{Environmental Pollution},
\emph{275}, 116620.
doi:\href{https://doi.org/10.1016/j.envpol.2021.116620}{10.1016/j.envpol.2021.116620}

\leavevmode\vadjust pre{\hypertarget{ref-Sgarlatta2023}{}}%
Sgarlatta, M. (2023). \emph{Mechanisms driving tropicalization of
temperate reef fish assemblages} (Thesis). UNSW Sydney.
doi:/\href{https://doi.org/10.26190/unsworks/25104}{10.26190/unsworks/25104}

\leavevmode\vadjust pre{\hypertarget{ref-Siniff2008}{}}%
Siniff, D. B., Garrott, R. A., Rotella, J. J., Fraser, W. R., \& Ainley,
D. G. (2008). Opinion: {Projecting} the effects of environmental change
on {Antarctic} seals. \emph{Antarctic Science}, \emph{20}(5), 425--435.
doi:\href{https://doi.org/10.1017/S0954102008001351}{10.1017/S0954102008001351}

\leavevmode\vadjust pre{\hypertarget{ref-Smale2008}{}}%
Smale, Dan A., \& Barnes, D. K. A. (2008). Likely responses of the
{Antarctic} benthos to climate-related changes in physical disturbance
during the 21st century, based primarily on evidence from the {West
Antarctic Peninsula} region. \emph{Ecography}, \emph{31}(3), 289--305.
doi:\href{https://doi.org/10.1111/j.0906-7590.2008.05456.x}{10.1111/j.0906-7590.2008.05456.x}

\leavevmode\vadjust pre{\hypertarget{ref-Smale2008a}{}}%
Smale, Dan A., Brown, K. M., Barnes, D. K. A., Fraser, K. P. P., \&
Clarke, A. (2008). Ice {Scour Disturbance} in {Antarctic Waters}.
\emph{Science}, \emph{321}(5887), 371--371.
doi:\href{https://doi.org/10.1126/science.1158647}{10.1126/science.1158647}

\leavevmode\vadjust pre{\hypertarget{ref-Soeffker2022}{}}%
Soeffker, M., Hollyman, P. R., Collins, M. A., Hogg, O. T., Riley, A.,
Laptikhovsky, V., \ldots{} Darby, C. (2022). Contrasting life-history
traits of two toothfish ({Dissostichus} spp.) species at their range
edge around the {South Sandwich Islands}. \emph{Deep Sea Research Part
II: Topical Studies in Oceanography}, \emph{201}, 105098.
doi:\href{https://doi.org/10.1016/j.dsr2.2022.105098}{10.1016/j.dsr2.2022.105098}

\leavevmode\vadjust pre{\hypertarget{ref-Souza2018}{}}%
Souza, M. R. D. P. de, Herrerias, T., Zaleski, T., Forgati, M.,
Kandalski, P. K., Machado, C., \ldots{} Donatti, L. (2018). Heat stress
in the heart and muscle of the {Antarctic} fishes {Notothenia} rossii
and {Notothenia} coriiceps: {Carbohydrate} metabolism and antioxidant
defence. \emph{Biochimie}, \emph{146}, 43--55.
doi:\href{https://doi.org/10.1016/j.biochi.2017.11.010}{10.1016/j.biochi.2017.11.010}

\leavevmode\vadjust pre{\hypertarget{ref-Steele2010}{}}%
Steele, J. H., Thorpe, S. A., \& Turekian, K. K. (2010). \emph{Ocean
{Currents}}. {Academic Press}.

\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2011}{}}%
Stouffer, D. B., \& Bascompte, J. (2011). Compartmentalization increases
food-web persistence. \emph{Proceedings of the National Academy of
Sciences}, \emph{108}(9), 3648--3652.
doi:\href{https://doi.org/10.1073/pnas.1014353108}{10.1073/pnas.1014353108}

\leavevmode\vadjust pre{\hypertarget{ref-Strobel2013}{}}%
Strobel, A., Leo, E., Pörtner, H. O., \& Mark, F. C. (2013). Elevated
temperature and {PCO2} shift metabolic pathways in differentially
oxidative tissues of {Notothenia} rossii. \emph{Comparative Biochemistry
and Physiology Part B: Biochemistry and Molecular Biology},
\emph{166}(1), 48--57.
doi:\href{https://doi.org/10.1016/j.cbpb.2013.06.006}{10.1016/j.cbpb.2013.06.006}

\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021}{}}%
Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
Desjardins-Proulx, P., \ldots{} Poisot, T. (2021). A roadmap towards
predicting species interaction networks (across space and time).
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences}, \emph{376}(1837), 20210063.
doi:\href{https://doi.org/10.1098/rstb.2021.0063}{10.1098/rstb.2021.0063}

\leavevmode\vadjust pre{\hypertarget{ref-Tamini2023}{}}%
Tamini, L. L., Dellacasa, R. F., Chavez, L. N., Marinao, C. J., Góngora,
M. E., Crawford, R., \& Frere, E. (2023). Bird scaring lines reduce
seabird mortality in mid-water and bottom trawlers in {Argentina}.
\emph{ICES Journal of Marine Science}, fsad109.
doi:\href{https://doi.org/10.1093/icesjms/fsad109}{10.1093/icesjms/fsad109}

\leavevmode\vadjust pre{\hypertarget{ref-Tarling2018}{}}%
Tarling, G. A., Ward, P., \& Thorpe, S. E. (2018). Spatial distributions
of {Southern Ocean} mesozooplankton communities have been resilient to
long-term surface warming. \emph{Global Change Biology}, \emph{24}(1),
132--142.
doi:\href{https://doi.org/10.1111/gcb.13834}{10.1111/gcb.13834}

\leavevmode\vadjust pre{\hypertarget{ref-Teixido2002}{}}%
Teixidó, N., Garrabou, J., \& Arntz, W. E. (2002). Spatial pattern
quantification of {Antarctic} benthic communities using landscape
indices. \emph{Marine Ecology Progress Series}, \emph{242}, 1--14.
doi:\href{https://doi.org/10.3354/meps242001}{10.3354/meps242001}

\leavevmode\vadjust pre{\hypertarget{ref-Thompson2012}{}}%
Thompson, R. M., Brose, U., Dunne, J. A., Hall, R. O., Hladyz, S.,
Kitching, R. L., \ldots{} Tylianakis, J. M. (2012). Food webs:
Reconciling the structure and function of biodiversity. \emph{Trends in
Ecology \& Evolution}, \emph{27}(12), 689--697.
doi:\href{https://doi.org/10.1016/j.tree.2012.08.005}{10.1016/j.tree.2012.08.005}

\leavevmode\vadjust pre{\hypertarget{ref-Thompson2007}{}}%
Thompson, R. M., Hemberg, M., Starzomski, B. M., \& Shurin, J. B.
(2007). Trophic {Levels} and {Trophic Tangles}: {The Prevalence} of
{Omnivory} in {Real Food Webs}. \emph{Ecology}, \emph{88}(3), 612--617.
doi:\href{https://doi.org/10.1890/05-1454}{10.1890/05-1454}

\leavevmode\vadjust pre{\hypertarget{ref-Tombesi2020}{}}%
Tombesi, M. L., Rabufetti, F., \& Lovrich, G. A. (2020). Las áreas
marinas protegidas en la {Argentina}. \emph{La Lupa. Colección Fueguina
De Divulgación Científica}, \emph{16}, 2--7.
doi:\url{https://www.coleccionlalupa.com.ar/index.php/lalupa/article/view/79}

\leavevmode\vadjust pre{\hypertarget{ref-Trathan2023}{}}%
Trathan, Philip N. (2023). The future of the {South Georgia} and {South
Sandwich Islands} marine protected area in a changing environment: {The}
choice between industrial fisheries, or ecosystem protection.
\emph{Marine Policy}, \emph{155}, 105773.
doi:\href{https://doi.org/10.1016/j.marpol.2023.105773}{10.1016/j.marpol.2023.105773}

\leavevmode\vadjust pre{\hypertarget{ref-Trathan2021}{}}%
Trathan, P. N., Fielding, S., Hollyman, P. R., Murphy, E. J.,
Warwick-Evans, V., \& Collins, M. A. (2021). Enhancing the ecosystem
approach for the fishery for {Antarctic} krill within the complex,
variable, and changing ecosystem at {South Georgia}. \emph{ICES Journal
of Marine Science}, \emph{78}(6), 2065--2081.
doi:\href{https://doi.org/10.1093/icesjms/fsab092}{10.1093/icesjms/fsab092}

\leavevmode\vadjust pre{\hypertarget{ref-Trebilco2020}{}}%
Trebilco, R., Melbourne-Thomas, J., \& Constable, A. J. (2020). The
policy relevance of {Southern Ocean} food web structure: {Implications}
of food web change for fisheries, conservation and carbon sequestration.
\emph{Marine Policy}, \emph{115}, 103832.
doi:\href{https://doi.org/10.1016/j.marpol.2020.103832}{10.1016/j.marpol.2020.103832}

\leavevmode\vadjust pre{\hypertarget{ref-Turner2020}{}}%
Turner, J., Guarino, M. V., Arnatt, J., Jena, B., Marshall, G. J.,
Phillips, T., \ldots{} Cavanagh, R. (2020). Recent {Decrease} of {Summer
Sea Ice} in the {Weddell Sea}, {Antarctica}. \emph{Geophysical Research
Letters}, \emph{47}(11), e2020GL087127.
doi:\href{https://doi.org/10.1029/2020GL087127}{10.1029/2020GL087127}

\leavevmode\vadjust pre{\hypertarget{ref-Verges2019}{}}%
Vergés, A., McCosker, E., Mayer-Pinto, M., Coleman, M. A., Wernberg, T.,
Ainsworth, T., \& Steinberg, P. D. (2019). Tropicalisation of temperate
reefs: {Implications} for ecosystem functions and management actions.
\emph{Functional Ecology}, \emph{33}(6), 1000--1013.
doi:\href{https://doi.org/10.1111/1365-2435.13310}{10.1111/1365-2435.13310}

\leavevmode\vadjust pre{\hypertarget{ref-Verges2014}{}}%
Vergés, A., Steinberg, P. D., Hay, M. E., Poore, A. G. B., Campbell, A.
H., Ballesteros, E., \ldots{} Wilson, S. K. (2014). The tropicalization
of temperate marine ecosystems: Climate-mediated changes in herbivory
and community phase shifts. \emph{Proceedings of the Royal Society B:
Biological Sciences}, \emph{281}(1789), 20140846.
doi:\href{https://doi.org/10.1098/rspb.2014.0846}{10.1098/rspb.2014.0846}

\leavevmode\vadjust pre{\hypertarget{ref-Vinuesa2005}{}}%
Vinuesa, J. H. (2005). Distribución de crustáceos decápodos y
estomatópodos del golfo {San Jorge}, {Argentina}. \emph{Revista de
Biología Marina y Oceanografía}, \emph{40}(1), 7--21.
doi:\href{https://doi.org/10.4067/S0718-19572005000100002}{10.4067/S0718-19572005000100002}

\leavevmode\vadjust pre{\hypertarget{ref-Vinuesa2007}{}}%
Vinuesa, J. H., \& Varisco, M. (2007). Trophic ecology of the lobster
krill {Munida} gregaria in {San Jorge Gulf}, {Argentina}.
\emph{Investigaciones Marinas}, \emph{35}(2), 25--34.
doi:\href{https://doi.org/10.4067/S0717-71782007000200003}{10.4067/S0717-71782007000200003}

\leavevmode\vadjust pre{\hypertarget{ref-Vucic-Pestic2011}{}}%
Vucic-Pestic, O., Ehnes, R. B., Rall, B. C., \& Brose, U. (2011).
Warming up the system: Higher predator feeding rates but lower energetic
efficiencies. \emph{Global Change Biology}, \emph{17}(3), 1301--1310.
doi:\href{https://doi.org/10.1111/j.1365-2486.2010.02329.x}{10.1111/j.1365-2486.2010.02329.x}

\leavevmode\vadjust pre{\hypertarget{ref-Ward2018}{}}%
Ward, P., Tarling, G. A., \& Thorpe, S. E. (2018). Temporal changes in
abundances of large calanoid copepods in the {Scotia Sea}: Comparing the
1930s with contemporary times. \emph{Polar Biology}, \emph{41}(11),
2297--2310.
doi:\href{https://doi.org/10.1007/s00300-018-2369-3}{10.1007/s00300-018-2369-3}

\leavevmode\vadjust pre{\hypertarget{ref-Wege2021}{}}%
Wege, M., Salas, L., \& LaRue, M. (2021). Ice matters: {Life-history}
strategies of two {Antarctic} seals dictate climate change eventualities
in the {Weddell Sea}. \emph{Global Change Biology}, \emph{27}(23),
6252--6262.
doi:\href{https://doi.org/10.1111/gcb.15828}{10.1111/gcb.15828}

\leavevmode\vadjust pre{\hypertarget{ref-Whitehouse2008}{}}%
Whitehouse, M. J., Meredith, M. P., Rothery, P., Atkinson, A., Ward, P.,
\& Korb, R. E. (2008). Rapid warming of the ocean around {South
Georgia}, {Southern Ocean}, during the 20th century: {Forcings},
characteristics and implications for lower trophic levels. \emph{Deep
Sea Research Part I: Oceanographic Research Papers}, \emph{55}(10),
1218--1228.
doi:\href{https://doi.org/10.1016/j.dsr.2008.06.002}{10.1016/j.dsr.2008.06.002}

\leavevmode\vadjust pre{\hypertarget{ref-Whitworth1980}{}}%
Whitworth, T. (1980). Zonation and geostrophic flow of the {Antarctic}
circumpolar current at {Drake Passage}. \emph{Deep Sea Research Part A.
Oceanographic Research Papers}, \emph{27}(7), 497--507.
doi:\href{https://doi.org/10.1016/0198-0149(80)90036-9}{10.1016/0198-0149(80)90036-9}

\leavevmode\vadjust pre{\hypertarget{ref-Williams2000}{}}%
Williams, R. J., \& Martinez, N. D. (2000). Simple rules yield complex
food webs. \emph{Nature}, \emph{404}(6774), 180--183.
doi:\href{https://doi.org/10.1038/35004572}{10.1038/35004572}

\leavevmode\vadjust pre{\hypertarget{ref-Wood2015}{}}%
Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
(2015). Effects of spatial scale of sampling on food web structure.
\emph{Ecology and Evolution}, \emph{5}(17), 3769--3782.
doi:\href{https://doi.org/10.1002/ece3.1640}{10.1002/ece3.1640}

\leavevmode\vadjust pre{\hypertarget{ref-Woods2023}{}}%
Woods, B. L., Van de Putte, A. P., Hindell, M. A., Raymond, B.,
Saunders, R. A., Walters, A., \& Trebilco, R. (2023). Species
distribution models describe spatial variability in mesopelagic fish
abundance in the {Southern Ocean}. \emph{Frontiers in Marine Science},
\emph{9}.

\leavevmode\vadjust pre{\hypertarget{ref-Woodward2010}{}}%
Woodward, G., Benstead, J. P., Beveridge, O. S., Blanchard, J., Brey,
T., Brown, L. E., \ldots{} Yvon-Durocher, G. (2010). Ecological
{Networks} in a {Changing Climate}. In G. Woodward (Ed.), \emph{Advances
in {Ecological Research}} (Vol. 42, pp. 71--138). {Academic Press}.
doi:\href{https://doi.org/10.1016/B978-0-12-381363-3.00002-2}{10.1016/B978-0-12-381363-3.00002-2}

\leavevmode\vadjust pre{\hypertarget{ref-Wu2012}{}}%
Wu, L., Cai, W., Zhang, L., Nakamura, H., Timmermann, A., Joyce, T.,
\ldots{} Giese, B. (2012). Enhanced warming over the global subtropical
western boundary currents. \emph{Nature Climate Change}, \emph{2}(3),
161--166.
doi:\href{https://doi.org/10.1038/nclimate1353}{10.1038/nclimate1353}

\leavevmode\vadjust pre{\hypertarget{ref-Yorio2009}{}}%
Yorio, P. (2009). Marine protected areas, spatial scales, and
governance: Implications for the conservation of breeding seabirds.
\emph{Conservation Letters}, \emph{2}(4), 171--178.
doi:\href{https://doi.org/10.1111/j.1755-263X.2009.00062.x}{10.1111/j.1755-263X.2009.00062.x}

\leavevmode\vadjust pre{\hypertarget{ref-Yorio2017}{}}%
Yorio, P., González-Zevallos, D., Gatto, A., Biagioni, O., \& Castillo,
J. (2017). Relevance of forage fish in the diet of {Magellanic} penguins
breeding in northern {Patagonia}, {Argentina}. \emph{Marine Biology
Research}, \emph{13}(6), 603--617.
doi:\href{https://doi.org/10.1080/17451000.2016.1273529}{10.1080/17451000.2016.1273529}

\end{CSLReferences}

\end{document}

### 2023-11-21 SupportingInformation.tex
New version to submit to GCB

--- 2023-09-29 manuscript.tex
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{pdflscape,booktabs}
+\newcommand{\blandscape}{\begin{landscape}}
+\newcommand{\elandscape}{\end{landscape}}
 \newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
@@
 \newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
-
-\usepackage{pdflscape,booktabs}
-\newcommand{\blandscape}{\begin{landscape}}
-\newcommand{\elandscape}{\end{landscape}}
-\usepackage[running]{lineno}
-\linenumbers
 \ifLuaTeX
@@
 \hypersetup{
+  pdftitle={Supplementary Material for `The response of trophic interaction networks to multiple stressors in a marine latitudinal gradient of the Southern Hemisphere'},
   hidelinks,
@@
 
+\title{Supplementary Material for `The response of trophic interaction
+networks to multiple stressors in a marine latitudinal gradient of the
+Southern Hemisphere'}
 \author{}
@@
 \begin{document}
-
-\hypertarget{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}{%
-\section{The response of trophic interaction networks to multiple
-stressors in a marine latitudinal gradient of the Southern
-Hemisphere}\label{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}}
-
-\hypertarget{abstract}{%
-\subsection{Abstract}\label{abstract}}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  Ecological networks are increasingly used as conceptual frameworks for
-  understanding ecological community structure, identifying key species,
-  and for ecosystem management and biodiversity conservation. Nowadays,
-  there is a growing interest in understanding how ecological networks
-  respond to environmental and anthropogenic stressors along
-  geographical gradients.
-\item
-  We review for the first time the state-of-the-art knowledge on
-  stressor response of marine food webs along the southwest Atlantic to
-  Antarctic gradient (45 - 78ºS), considering the following study areas:
-  San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea, Potter Cove
-  (Antarctica) and Weddell Sea (Antarctica). The aim of this review is
-  threefold: 1) describe the complexity and structure of marine food
-  webs along the southwest Atlantic to Antarctic axis from a network
-  perspective; 2) identify the ongoing environmental and anthropogenic
-  stressors for each marine ecosystem containing the food webs; and 3)
-  resume proven food web changes and elaborate hypotheses on how the
-  identified stressors might affect food web features, combining
-  information on node- and network-level properties.
-\item
-  Environmental and anthropogenic stressor effects in the study gradient
-  have been mostly assessed individually and at the organism and/or
-  population, i.e., at the node level, with one exception: the effect of
-  fisheries in the San Jorge Gulf food web. To address the most
-  plausible stressors effects on the selected food webs, we built
-  hypotheses for each study area considering the following: a)
-  stressor(s), b) parameter(s) affected, c) node-level properties of the
-  affected species, and d) network-level properties of the food web.
-\item
-  The most common stressor reported along the gradient is global
-  warming, except for Beagle Channel and Burdwood Bank, which are more
-  influenced by the introduction of an alien species and fisheries,
-  respectively. We provide particular hypotheses on how warming might
-  impact food webs.
-\item
-  We demonstrate the advantages of applying a network approach to better
-  understand and predict the effect of stressors in marine ecosystems of
-  the Southern Hemisphere.
-\end{enumerate}
-
-Keywords: anthropogenic stressors, environmental stressors, food webs,
-latitudinal gradient, Southern Hemisphere
-
-\hypertarget{introduction}{%
-\subsection{1. Introduction}\label{introduction}}
-
-The application of a network perspective has emerged as a powerful tool
-to tackle the complexity of species interactions, facilitating a better
-understanding of the structure and functioning of ecosystems (Belgrano,
-Scharler, Scharler, Dunne, \& Ulanowicz, 2005; Thompson et al., 2012;
-D'Alelio, Libralato, Wyatt, \& Ribera d'Alcalà, 2016). Trophic networks
-(or food webs) allow identifying properties and key species that may be
-crucial for ecosystem stability, and hence important for ecosystem
-management and biodiversity conservation (Thompson et al., 2012). There
-is a growing interest in understanding how ecological networks respond
-to environmental and anthropogenic stressors along geographical
-gradients (Baiser, Gotelli, Buckley, Miller, \& Ellison, 2012; Cirtwill,
-Stouffer, \& Romanuk, 2015; Strydom et al., 2021; Bauer et al., 2022).
-Yet, only a few studies have described variation in food web structure
-along latitudinal gradients in marine ecosystems. The few that have come
-from the Global North (Wood, Russell, Hanson, Williams, \& Dunne, 2015;
-Kortsch et al., 2019; Frelat et al., 2022; Pecuchet et al., 2022),
-whereas no studies, nor meta-analyses, on geographical variation in
-marine food webs exist for the Global South (Southern Hemisphere).
-
-Here we review for the first time the state-of-the-art knowledge on
-stressor response of marine food webs along the southwest Atlantic to
-Antarctic gradient (45 - 78ºS, Figure 1). We focus on proven and
-expected changes in food webs driven by stressors in selected areas
-along this large-scale latitudinal gradient. The aim of this review is
-threefold: 1) describe the complexity and structure of marine food webs
-along the southwest Atlantic to Antarctic axis from a network
-perspective; 2) identify the ongoing environmental and anthropogenic
-stressors for each marine ecosystem containing the food webs; and 3)
-resume proven food web changes and elaborate hypotheses on how the
-identified stressors might affect food web features (e.g.~energy flow,
-stability), combining information on node- and network-level properties.
-Finally, we suggest which additional data and analyses are needed to
-gain insights into the stressors' effects on food web properties in the
-southwest Atlantic to Antarctic region.
-
-\hypertarget{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}{%
-\subsection{2. The structure of marine food webs in the Southwest
-Atlantic - Antarctic
-region}\label{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}}
-
-Together, the southwest and the Atlantic sector of the Southern Ocean
-comprise one of the most biologically productive regions of the world's
-oceans (Acha, Mianzan, Guerrero, Favero, \& Bava, 2004; Whitehouse et
-al., 2008; Ballerini et al., 2014; Latorre et al., 2023). The referred
-region extends from San Jorge Gulf (45ºS) in the Patagonian shelf to the
-Weddell Sea (78ºS) in the Southern Ocean, and covers a well-connected
-oceanic latitudinal gradient (R. P. Matano, Palma, \& Piola, 2010;
-Steele, Thorpe, \& Turekian, 2010; Guihou, Piola, Palma, \& Chidichimo,
-2020).
-
-Throughout this latitudinal gradient, many investigations have been
-carried out addressing the trophic ecology of specific species and
-prey-predator relationships (Vinuesa \& Varisco, 2007; Sailley et al.,
-2013; Pasotti et al., 2015; Riccialdelli, Newsome, Fogel, \& Fernández,
-2017; Saunders, Hill, Tarling, \& Murphy, 2019; Riccialdelli et al.,
-2020), but few studies have considered the complexity of the ecosystem
-in terms of a high resolution of species and their prey-predator
-interactions (but see Jacob et al. (2011), Marina et al. (2018), Funes,
-Saravia, Cordone, Iribarne, \& Galván (2022), López-López, Genner,
-Tarling, Saunders, \& O'Gorman (2022), Rodriguez, Marina, Schloss, \&
-Saravia (2022), Marina et al. (in rev.)). Neglecting this complexity
-might lead to a misunderstanding of the structure and functioning of the
-ecosystems, and ultimately reduce the ability to predict ecosystem
-responses to perturbations (Montoya, Woodward, Emmerson, \& Solé, 2009;
-Woodward et al., 2010).
-
-In this review, we consider marine areas in the Southern hemisphere for
-which highly-resolved empirical food webs, in terms of species diversity
-and trophic interactions, have been previously described. These areas
-include: (1) San Jorge Gulf (45 - 47ºS, 65 - 68ºW), (2) Beagle Channel
-(\textasciitilde54ºS, 68ºW), (3) Burdwood Bank (\textasciitilde54ºS,
-59ºW), (4) Scotia Sea (48 - 58ºS, 50ºW), (5) Potter Cove (62ºS, 58ºW,
-Antarctica), and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica) (Figure
-1). The geographic locations of these marine biomes span from temperate
-to Antarctic, and are exposed to both environmental (sea warming,
-glacial retreat) and anthropogenic (fishery, pollution) stressors.
-
-\begin{figure}
-\centering
-\includegraphics[width=6.27in,height=3.528in]{Figures/Map_final.jpg}
-\caption{Map of the study areas along the southwest Atlantic - Antarctic
-latitudinal gradient. The areas are marked with numbers from one to six.
-Smaller areas (1. San Jorge Gulf, 2. Beagle Channel, 3. Burdwood Bank,
-and 5. Potter Cove) are shown on the panels to the left, whereas the
-larger areas (4. North and South Scotia Sea, and 6. Weddell Sea) are
-marked with a red rectangle on the map. The map was drawn using the
-`marmap' R package (Pante, Simon-Bouhet, \& Irisson, 2023). Continental
-contour shapefiles were obtained from www.ign.gob.ar.}
-\end{figure}
-
-San Jorge Gulf is the northernmost study area considered in this review.
-It is a partially enclosed basin spanning approximately 34,000 km2 and
-\textasciitilde100 m of maximum depths, located from Cabo dos Bahias
-(44°55'S) to Cabo tres Puntas (47°06'S) (Figure 1). The shallower
-northern and southern ends of the Gulf (with depths \textasciitilde40 m)
-present two prominent frontal systems. These systems are the areas of
-highest productivity (Bogazzi et al., 2005; Glembocki, Williams,
-Góngora, Gagliardini, \& Orensanz, 2015). The Gulf's productivity
-supports large invertebrate and vertebrate fisheries (María Eva Góngora,
-González-Zevallos, Pettovello, \& Mendía, 2012), as well as marine
-mammal and seabird populations (Yorio, 2009). The San Jorge Gulf food
-web comprises 165 nodes and 1015 trophic interactions with a connectance
-of 0.04. The percentage of top predators is 16\%, 78\% of intermediate
-nodes and 6\% of basal nodes; 60\% of predators are omnivorous (Table
-1). The most connected nodes are: the Argentine red shrimp Pleoticus
-muelleri, the squat lobster Gimothea gregaria, squids (Illex argentinus
-as dominant species) and Amphipoda. Notably, these nodes present
-mid-trophic positions in the food web (3.0, 2.5, 3.6 and 2,
-respectively) (Funes et al., 2022).
-
-At a southern latitude, the Beagle Channel (54°52'S, 68°8'W) is an
-interoceanic passage located at the southernmost tip of South America,
-spanning 240 km in length and 5 km in width (\textasciitilde1200 km2),
-and a range depth of 0 - 140 m (Figure 1). It features complex
-coastlines, varying bathymetry, a prevailing west-to-east circulation
-pattern, and a significant longitudinal gradient of glacial freshwater
-discharge (Schloss et al., 2023). Bruno, Riccialdelli, Acha, \&
-Fernández (2023) suggests that locally produced suspended particulate
-organic matter (mostly composed by phytoplankton) and organic matter
-accumulated in the sediments (macroalgae-originated detritus) are the
-primary food sources for the marine ecosystem, as opposed to
-allochthonous materials. Beagle Channel food web includes 145 nodes and
-1115 trophic interactions with a connectance of 0.05 (Table 1). The food
-web is suggested to have a wasp-waist structure, where the following
-species play a crucial role in the dynamics of the ecosystem: Fueguian
-sprat Sprattus fuegensis, longtail southern cod Patagonotothen ramsayi,
-black southern cod P. tessellata, frogmouth Cottoperca trigloides, and
-squat lobster Grimothea gregaria (Riccialdelli et al., 2020). Moreover,
-the squat lobster has been identified as a species responsible for
-linking modules and connecting the entire food web (Rodriguez et al.,
-2022).
-
-The so-called Burdwood Bank ecosystem comprises Marine Protected Areas
-Namuncurá - Burdwood Bank I and II, meaning the shallow submarine
-plateau named Burdwood Bank with a 200 m isobath boundary, and a deep
-slope that reaches 4000 m in depth, respectively (Tombesi, Rabufetti, \&
-Lovrich, 2020; Administración de Parques Nacionales, 2022) (Figure 1).
-Physical features in the plateau are fairly stable, with salinity
-averaging 34 all year round and temperature ranging between 4 and 8ºC
-(Acha et al., 2004; Piola \& Falabella, 2009). The plateau is surrounded
-by steep flanks of up to 4000 m depth, protected by the Marine Protected
-Area Namuncurá - Burdwood Bank II (32,000 km2; \textasciitilde55º -
-56ºS, \textasciitilde58º - 62ºW). Intense upwelling and mixing occur in
-relation to the slope, entraining deep nutrient-rich waters into the
-photic layer (Piola \& Falabella, 2009; Ricardo P. Matano, Palma, \&
-Combes, 2019), and resulting in a fairly homogeneous water column both
-spatially and temporally (Glorioso \& Flather, 1995; Ricardo P. Matano
-et al., 2019). The Burdwood Bank food web comprises 379 nodes and 1788
-interactions, with a connectance of 0.01, and an asymmetric degree
-distribution (i.e.~most of the species have a relatively low number of
-interactions and few species concentrate most of them). Almost half of
-the consumers are omnivores (0.48), and the network displays a
-small-world pattern (Marina et al., in rev.) (Table 1).
-
-The Scotia Sea is a deep-sea basin, delimited by the Drake Passage to
-the West and by the island complex of the Scotia Arc to the North, East,
-and South, with an approximate extension of 1.5 x 106 km2 and a depth
-range of 0 - 3000 m (E. j. Murphy et al., 2006) (Figure 1). Its
-oceanography is dominated by the Antarctic Circumpolar Current, which is
-spatially structured by frontal systems (Whitworth, 1980). The South
-Antarctic Circumpolar Current Front subdivides the Scotia Sea into two
-biogeographic regions: the Northern Scotia Sea is characterized by
-higher and more variable temperatures, and the Southern Scotia Sea by
-lower and more stable temperatures and influenced by seasonal sea ice
-(Raymond, 2011). The analysis of the Northern and Southern Scotia Sea
-food webs shows that the former is relatively more complex than the
-latter: with higher species richness (218 vs 192) and interactions
-(10008 vs 7241) and a higher connection overall (0.21 vs 0.20). As
-expected from a more complex network, the path length is shorter in the
-Northern Scotia Sea food web. In the same sense, the Southern Scotia Sea
-network displays a greater proportion of omnivores and a lower mean
-trophic level (López-López et al., 2022) (Table 1).
-
-In the Antarctic realm, Potter Cove is a \textasciitilde9 km2 fjord with
-a depth range of 0 - 200 m located at 25 de Mayo/King George Island
-(62°14'S, 58°38'W, South Shetland Islands) on the West Antarctic
-Peninsula (Figure 1). The cove, bordered by the Fourcade Glacier, is
-divided into three areas: a) the internal cove, a high
-glacier-influenced, soft sediment zone with a 50 m maximum depth; b) the
-central cove, a mixed substrate area with low meltwater influence and an
-80 m maximum depth; and c) the external cove, ice-free for 60 years with
-a 185 m maximum depth and rocky substrate (Jerosch et al., 2018; Neder
-et al., 2022; Neder, 2023). Potter Cove's high-latitude location results
-in variable environmental conditions due to photoperiod length
-seasonality. Sea ice often covers this area in winter (Schloss et al.,
-2012). With low phytoplankton biomass, macroalgae, and microphytobenthos
-are likely the primary food sources for secondary benthic production (M.
-L. Quartino \& Boraso de Zaixso, 2008). The Potter Cove food web
-includes 110 nodes and 649 interactions, with an asymmetric degree
-distribution, and a connectance value of 0.05 (Table 1). It presents a
-modular structure (groups of species interact more strongly with each
-other than with species belonging to other groups), that's positively
-associated with stability, since perturbation can be retained within
-modules (Rodriguez et al., 2022).
-
-Located between 74 and 78ºS, the high Antarctic Weddell Sea shelf spans
-approximately 450 km from East to West (Jacob et al., 2011) (Figure 1).
-The water depth ranges from 200 to 500 m, with shallower regions being
-covered by continental ice that forms the coastline along the eastern
-and southern parts of the Weddell Sea. Within this shelf area, exists a
-complex three-dimensional benthic habitat characterized by substantial
-benthic biomasses and an intermediate to high diversity when compared to
-benthic boreal communities (Dayton, 1990; Teixidó, Garrabou, \& Arntz,
-2002). The Weddell Sea food web exhibits a high level of network
-complexity, featuring the greatest number of nodes (490) and trophic
-interactions (16041) among the analyzed food webs in this review (Table
-1). Its connectance (0.07) and other structural properties are
-intermediate compared to the other food webs. Recently, the interaction
-strengths of this food web were estimated, revealing the presence of
-numerous weak and few strong interactions, which is consistent with
-findings in other complex food webs (McCann, Hastings, \& Huxel, 1998;
-Nilsson \& McCann, 2016). Notably, this asymmetric distribution of
-interaction strength is likely to promote community persistence.
-
-\footnotesize
-
-Table 1. Complexity and structure properties of the marine food webs
-considered in the present review. Refer to Table 3 for definition of
-properties. mean TL: mean trophic level. Food webs are ordered by
-increasing latitude.
+\maketitle
+
+Table S1. Node-level properties for species being impacted by
+environmental and/or anthropogenic stressors (see Table 2 in the article
+for details) in six study areas along the southwest Atlantic to
+Antarctic gradient (45 - 78ºS). Degree: total number of interactions;
+relative abundance: high (+++), medium (+), low (-), unknown (?).
 
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1538}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0839}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0839}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1259}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1259}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0979}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1049}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.2238}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1809}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2340}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1383}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1277}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1383}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1596}}@{}}
 \toprule\noalign{}
@@
 \textbf{Food web}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Nodes}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Links}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Connectance}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Path length}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{mean TL}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Omnivory}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Reference}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Node / trophic species}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Degree}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Trophic level}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Omnivory level}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Relative abundance}
 \end{minipage} \\
@@
 \endlastfoot
-San Jorge Gulf & 165 & 1015 & 0.04 & 2.17 & 3.02 & 0.63 & Funes et al.
-(2022) \\
-Beagle Channel & 145 & 1115 & 0.05 & 2.12 & 2.37 & 0.55 & Rodriguez et
-al. (2022) \\
-Burdwood Bank & 379 & 1788 & 0.01 & 2.99 & 2.52 & 0.49 & Marina et al.
-(in rev.) \\
-Potter Cove & 110 & 649 & 0.05 & 2.33 & 2.22 & 0.46 & Marina et al.
-(2018); Rodriguez et al. (2022) \\
-N Scotia Sea & 218 & 10008 & 0.21 & 1.87 & 3.29 & 0.73 & López-López et
-al. (2022) \\
-S Scotia Sea & 192 & 7241 & 0.20 & 1.90 & 3.21 & 0.71 & López-López et
-al. (2022) \\
-Weddell Sea & 490 & 16041 & 0.07 & 2.19 & 2.62 & 0.51 & Jacob et al.
-(2011) \\
+\textbf{Beagle Channel} & & & & & \\
+& \emph{Eleginops maclovinus} & 42 & 3.11 & 0.752 & ? \\
+& \emph{Patagonotothen tessellata} & 35 & 3.29 & 0.721 & ++ \\
+& \emph{Paralomis granulosa} & 26 & 3.28 & 0.277 & ? \\
+& \emph{Patagonotothen cornucola} & 23 & 3.23 & 0.495 & +++ \\
+& \emph{Nacella magellanica} & 22 & 2.46 & 0.397 & ? \\
+& \emph{Mytilus edulis chilensis} & 21 & 2.42 & 0.368 & ? \\
+& \emph{Sprattus fuegensis} & 17 & 3.05 & 0.422 & ++++ \\
+& \emph{Harpagifer bispinis} & 15 & 3.51 & 0.145 & ? \\
+& \emph{Paranotothenia magellanica} & 14 & 3.42 & 0.450 & +++ \\
+& \emph{Odontesthes nigricans} & 11 & 3.50 & 0.428 & ? \\
+& \emph{Patagonotothen sima} & 7 & 3.44 & 0.115 & ++ \\
+& \emph{Grimothea gregaria} & 71 & 2.41 & 0.434 & ++ \\
+\textbf{Burdwood Bank} & & & & & \\
+& \emph{Sprattus fuegensis} & 42 & 3.45 & 0.688 & ++ \\
+& \emph{Patagonotothen ramsayi} & 68 & 3.48 & 0.492 & +++ \\
+& \emph{Cottoperca trigloides} & 20 & 4.16 & 0.742 & ++ \\
+& \emph{Dissostichus eleginoides} & 49 & 4.01 & 0.797 & + \\
+& \emph{Dorytheuthis gahi} & 38 & 3.45 & 0.896 & ? \\
+& \emph{Henricia obesa} & 5 & 2.19 & 0.160 & ? \\
+& \emph{Odontaster penicillatus} & 7 & 2.94 & 0.148 & ? \\
+& \emph{Patagonotothen guntheri} & 63 & 3.39 & 0.390 & ++ \\
+& \emph{Coelorinchus fasciatus} & 16 & 3.48 & 0.446 & ++ \\
+& \emph{Coelorinchus marinii} & 8 & 3.32 & 0.658 & + \\
+& \emph{Macrourus carinatus} & 17 & 4.13 & 0.455 & +++ \\
+& \emph{Macrourus holotrachys} & 16 & 3.79 & 0.528 & +++ \\
+& \emph{Tedania sp} & 2 & 2.00 & 0.000 & +++ \\
+& \emph{Fusitriton magellanicus} & 8 & 3.11 & 0.017 & ++ \\
+& \emph{Adelomelon ancilla} & 5 & 3.46 & 0.220 & + \\
+& \emph{Zygochlamys patagonica} & 18 & 2.28 & 0.250 & ++ \\
+& \emph{Hiatella sp} & 7 & 2.00 & 0.000 & ? \\
+& \emph{Eurypodius latreillii} & 2 & 3.00 & 0.000 & + \\
+& \emph{Sympagurus dimorphus} & 4 & 2.00 & 0.000 & ? \\
+& \emph{Grimothea gregaria} & 32 & 2.50 & 0.250 & ? \\
+& \emph{Libidoclaea granaria} & 7 & 2.00 & 0.000 & ? \\
+& \emph{Alcyonium antarcticum} & 5 & 2.00 & 0.000 & ? \\
+& \emph{Convexella magelhaenica} & 14 & 2.70 & 0.410 & ? \\
+& \emph{Anthoptilum grandiflorum} & 9 & 2.78 & 0.395 & ? \\
+& \emph{Primnoella scotiae} & 13 & 2.78 & 0.395 & ? \\
+& \emph{Primnoisis antarctica} & 14 & 2.64 & 0.413 & ? \\
+& \emph{Actinostola crassicornis} & 7 & 2.83 & 0.138 & + \\
+& \emph{Brachiopoda spp} & 24 & 2.00 & 0.000 & ? \\
+& \emph{Acodontaster sp} & 2 & 2.00 & 0.000 & ? \\
+& \emph{Anasterias antarctica} & 2 & 3.57 & 0.000 & ++ \\
+& \emph{Ceramaster patagonicus} & 4 & 3.53 & 0.096 & ? \\
+& \emph{Henricia obesa} & 5 & 2.20 & 0.160 & ? \\
+& \emph{Cosmasterias lurida} & 12 & 3.24 & 0.418 & ? \\
+& \emph{Glabraster antarctica} & 4 & 2.00 & 0.000 & - \\
+& \emph{Pteraster affinis} & 3 & 3.00 & 0.000 & ? \\
+& \emph{Perknaster sp} & 2 & 3.08 & 0.000 & ? \\
+& \emph{Ctenodiscus australis} & 2 & 2.00 & 0.000 & ? \\
+& \emph{Odontaster sp} & 12 & 2.98 & 0.279 & ? \\
+& \emph{Gorgonocephalus chilensis} & 4 & 3.59 & 0.009 & ? \\
+& \emph{Ophiacantha vivipara} & 7 & 3.44 & 0.052 & ? \\
+& \emph{Pseudechinus magellanicus} & 9 & 2.50 & 0.250 & ? \\
+& \emph{Sterechinus agassizii} & 6 & 3.19 & 0.009 & ? \\
+& \emph{Austrocidaris canaliculata} & 7 & 3.17 & 0.028 & - \\
+& \emph{Chaetopterus antarcticus} & 1 & 2.00 & 0.000 & - \\
+& \emph{Cnemidocarpa spp} & 12 & 2.10 & 0.090 & ? \\
+& \emph{Daption capense} & 11 & 3.55 & 0.510 & ? \\
+& \emph{Thalassarche melanophris} & 22 & 3.83 & 0.983 & ? \\
+& \emph{Macronectes giganteus} & 7 & 3.93 & 0.903 & ? \\
+& \emph{Thalassarche chrysostoma} & 16 & 4.06 & 0.906 & ? \\
+& \emph{Diomedea epomophora} & 6 & 3.97 & 1.022 & ? \\
+& \emph{Macronectes halli} & 6 & 4.00 & 1.017 & ? \\
+& \emph{Procellaria aequinoctialis} & 8 & 4.06 & 0.782 & ? \\
+\textbf{Scotia Sea, North \& South} & & & & & \\
+& \emph{Euphausia superba} & 146 & 3.12 & 0.928 & +++ \\
+& \emph{Dissostichus eleginoides} & 29 & 5.99 & 0.249 & +++ \\
+& \emph{Krefftichthys anderssoni} & 157 & 4.50 & 1.010 & ++ \\
+& \emph{Protomyctophum bolini} & 135 & 4.09 & 0.773 & + \\
+& \emph{Electrona antarctica} & 192 & 4.50 & 1.000 & +++ \\
+& \emph{Gymnoscopelus nicholsi} & 134 & 4.07 & 0.781 & - \\
+& \emph{Gymnoscopelus braueri} & 185 & 4.53 & 0.978 & ++ \\
+& \emph{Limacina retroversa} & 35 & 2.00 & 0.000 & +++ \\
+\textbf{Potter Cove (Antarctica)} & & & & & \\
+& Benthic Diatomea & 36 & 1.00 & 0.000 & - \\
+& Copepoda & 27 & 2.60 & 0.720 & - \\
+& Phytoplankton & 23 & 1.00 & 0.000 & - \\
+& Zooplankton & 17 & 2.80 & 0.640 & - \\
+& Porifera & 18 & 2.00 & 8.043 & - \\
+& \emph{Euphausia superba} & 17 & 3.42 & 0.734 & + \\
+& Salpidae & 13 & 3.28 & 1.198 & - \\
+& Ascidiacea & 9 & 2.45 & 0.607 & +++ \\
+& \emph{Malacobelemnon daytoni} & 2 & 2.90 & 0.810 & + \\
+Macroalgae & \emph{Palmaria decipiens} & 11 & 1.00 & 0.000 & + \\
+& \emph{Gigartina skottsbergii} & 8 & 1.00 & 0.000 & + \\
+& \emph{Desmarestia menziesii} & 7 & 1.00 & 0.000 & +++ \\
+& \emph{Desmarestia anceps} & 6 & 1.00 & 0.000 & +++ \\
+& \emph{Desmarestia antarctica} & 6 & 1.00 & 0.000 & + \\
+& \emph{Iridaea cordata} & 6 & 1.00 & 0.000 & + \\
+& \emph{Plocamium cartilagineum} & 6 & 1.00 & 0.000 & - \\
+& \emph{Myriogramme manginii} & 4 & 1.00 & 0.000 & - \\
+& \emph{Adenocystis utricularis} & 3 & 1.00 & 0.000 & + \\
+& \emph{Georgiella confluens} & 3 & 1.00 & 0.000 & - \\
+& \emph{Ascoseira mirabilis} & 2 & 1.00 & 0.000 & + \\
+& \emph{Phaeurus antarcticus} & 2 & 1.00 & 0.000 & - \\
+& \emph{Curdiea racovitzae} & 2 & 1.00 & 0.000 & - \\
+& \emph{Callophyllis atrosanguinea} & 1 & 1.00 & 0.000 & - \\
+& \emph{Neuroglossum delesseriae} & 1 & 1.00 & 0.000 & - \\
+& \emph{Pantoneura plocamioides} & 1 & 1.00 & 0.000 & - \\
+& \emph{Picconiella plumosa} & 1 & 1.00 & 0.000 & - \\
+\textbf{Weddell Sea (Antarctica)} & & & & & \\
+& \emph{Pleuragramma antarcticum} & 69 & 3.58 & 0.440 & +++ \\
+& \emph{Chionodraco myersi} & 37 & 4.09 & 0.356 & ++ \\
+& \emph{Pagetopsis maculatus} & 37 & 4.09 & 0.356 & + \\
+& \emph{Gymnoscopelus braueri} & 62 & 3.53 & 0.274 & ? \\
+& \emph{Dissostichus mawsoni} & 87 & 4.12 & 0.560 & ? \\
+& Bacillariophyceae & 81 & 1.00 & 0.000 & +++ \\
+& Silicoflagellates & 30 & 1.00 & 0.000 & ++ \\
+& Foraminifera & 93 & 2.00 & 0.000 & ++ \\
+& \emph{Euphausia superba} & 163 & 2.27 & 0.385 & +++ \\
+& \emph{Salpa thompsoni} & 108 & 2.28 & 0.347 & ++ \\
+& \emph{Leptonychotes weddellii} & 59 & 4.86 & 0.204 & ? \\
+& \emph{Lobodon carcinophagus} & 28 & 4.24 & 0.553 & +++ \\
+& \emph{Hydrurga leptonyx} & 67 & 4.72 & 0.346 & ? \\
+& \emph{Arctocephalus gazella} & 61 & 4.67 & 0.331 & ? \\
+& \emph{Thalassoica antarctica} & 19 & 4.32 & 0.429 & +++ \\
+& \emph{Pagodroma nivea} & 11 & 4.21 & 0.209 & ++ \\
+& \emph{Sterna paradisaea} & 7 & 4.04 & 0.347 & ++ \\
+& \emph{Aptenodytes forsteri} & 53 & 4.78 & 0.211 & ++ \\
+& \emph{Pygoscelis adeliae} & 7 & 3.78 & 0.282 & +++ \\
+& \emph{Megaptera novaeangliae} & 4 & 3.26 & 0.014 & ? \\
+& Hexactinellida & 49 & 2.00 & 0.000 & +++ \\
+\textbf{San Jorge Gulf} & & & & & \\
+& The species of the San Jorge Gulf are not listed because the number of
+stressed species reported is too high. At a functional group level of
+resolution, the main impacted groups are: macroinvertebrates, fish, and
+seabirds. & & & & \\
 \end{longtable}
-
-\normalsize
-
-\hypertarget{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}{%
-\subsection{3. Environmental and anthropogenic stressors in the
-Southwest Atlantic - Antarctic
-region}\label{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}}
-
-A stressor is any environmental or anthropogenic variable that causes a
-quantifiable change, irrespective of its direction (increase or
-decrease), in a biological response (Côté, Darling, \& Brown, 2016; Orr
-et al., 2020). In the light of this, the southwest Atlantic - Antarctic
-marine biota has been and is currently subjected to a variety of
-stressors (e.g.~sea warming, glacial retreat, ice changes,
-acidification, species invasion, fisheries, and contamination). Although
-it is well-known that multiple stressors act in concert at any given
-time (e.g.~warming and fishery; acidification and contaminants) (Julian
-Gutt et al., 2015, 2021), to date stressor assessments have been
-performed individually. Moreover, the potential for interactive effects
-of two or more stressors (synergy or antagonism) (Crain, Kroeker, \&
-Halpern, 2008; Côté et al., 2016) is almost unknown for the region
-(Rowlands et al., 2021).
-
-In the following subsections, we describe the main environmental and
-anthropogenic stressors, and the species (or trophic species) and
-parameters affected reported for the marine ecosystems that contain the
-food webs considered in this review. In Table 2 we provide an exhaustive
-list of all stressors affecting species inhabiting each area,
-considering: the type of stressor, species and parameter affected, and
-locality.
 
@@
 
-Table 2. Environmental and anthropogenic stressors reported for the
+Table S2. Environmental and anthropogenic stressors reported for the
 study areas: San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea
@@
 \endlastfoot
+
 \textbf{San Jorge Gulf} & & & & & \\
@@
 30+ spp macrobenthos & Biomass & Elsewhere & Gaitán \& Marí (2016);
-Patricia A. Martínez, Wöhler, Troccoli, Di Marco, \& Maydana (2022);
-Administración de Parques Nacionales (2022); Tamini et al. (2023) \\
+Martínez, Wöhler, Troccoli, Di Marco, \& Maydana (2022); Administración
+de Parques Nacionales (2022); Tamini et al. (2023) \\
 & Fishery & Thalassarche melanophris, Macronectes giganteus, Daption
@@
 Manno, Peck, Corsi, \& Bergami (2022) \\
-& Sea warming & Euphausia superba & Metabolism & In situ & E. J. Murphy
-et al. (2007); Perry et al. (2020) \\
+& Sea warming & Euphausia superba & Metabolism & In situ & Murphy et al.
+(2007); Perry et al. (2020) \\
 & Sea warming & Euphausia superba & Distribution & In situ & Atkinson et
 al. (2019) \\
-& Fishery & Euphausia superba & Biomass & In situ & P. N. Trathan et al.
+& Fishery & Euphausia superba & Biomass & In situ & Trathan et al.
 (2021) \\
@@
 & Glacial retreat & Benthic community (macroalgae, invertebrates) &
-Biomass & In situ & María Liliana Quartino, Deregibus, Campana, Latorre,
-\& Momo (2013); Lagger, Servetto, Torre, \& Sahade (2017); Lagger et al.
+Biomass & In situ & Quartino, Deregibus, Campana, Latorre, \& Momo
+(2013); Lagger, Servetto, Torre, \& Sahade (2017); Lagger et al.
 (2018) \\
@@
 & Iceberg scouring & Macrobentos & Biomass & In situ & Isla (2023);
-Julian Gutt et al. (2015); Dan A. Smale, Brown, Barnes, Fraser, \&
-Clarke (2008); J. Gutt, Starmans, \& Dieckmann (1996) \\
+Julian Gutt et al. (2015); Smale, Brown, Barnes, Fraser, \& Clarke
+(2008); J. Gutt, Starmans, \& Dieckmann (1996) \\
 & Iceberg scouring & Hexactinellida sponges & Biomass & In situ & Julian
@@
 \end{landscape}
+
 \normalsize
 
-\hypertarget{san-jorge-gulf}{%
-\subsubsection{3.1 San Jorge Gulf}\label{san-jorge-gulf}}
-
-San Jorge Gulf experienced several environmental and anthropogenic
-stressors (Table 2). Trawl fisheries discard several species and add new
-trophic interactions to the food web which resulted in a decrease in
-trait variability and the stability of the system (Rincón-Díaz, Bovcon,
-Cochia, Góngora, \& Galván, 2021; Funes et al., 2022). Moreover, it
-changed the availability of prey to several predators. For example,
-Merluccius hubbsi one of the main bycatch species, became prey item to
-non-diving seabirds, like the kelp gull Larus dominicanus
-(González-Zevallos \& Yorio, 2006) and reef fishes (Funes, Marinao, \&
-Galván, 2019). Although juveniles of M. hubbsi are largely the main
-bycatch item, 29 other cartilaginous and 69 bony local fish species were
-also registered as incidental catch between 2005 and 2014 (María E.
-Góngora, Bovcon, \& Cochia, 2009; Bovcon, Góngora, Marinao, \&
-González-Zevallos, 2013; Ruibal Nuñez, 2020). This level of impact
-triggered a shift in the functional diversity of the assemblages
-homogenizing the trophic function of fishes (Rincón-Díaz et al., 2021).
-Other functional changes were a decrease in the maximum sizes of
-individual fish, together with a drop in elasmobranchs biomass and an
-increase in crustaceans biomass (Funes, 2020). The significant increase
-in crustacean biomass was mostly due to the increase in Pleoticus
-muelleri and Grimothea gregaria populations (Funes, 2020). These species
-rapidly became the most important prey for the most abundant fishes in
-the area: M. hubbsi and Mustelus schmitti (Belleggia, Giberto, \&
-Bremec, 2017; Pasti et al., 2021). However, the above-mentioned effects
-of trawl fisheries on the structure and function of the San Jorge Gulf
-community may have changed again, since the fisheries ceased activity in
-2015 (Annex I, Resolution CFP No 7/2018), remaining a minimum of
-artisanal activity.
-
-Sea warming is another important environmental stressor in the San Jorge
-Gulf, because of the southward shifts of northern fish populations to
-the Gulf (Galván et al., 2022). The San Jorge Gulf is especially prone
-to be affected by climate-driven shifts in species ranges, because it is
-located in the ecotone between two biogeographic provinces, the
-Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) (Balech \&
-Ehrlich, 2008). In addition to this tropicalization from northern fish
-populations, alien species are also documented to affect the demersal
-assemblage (fish and macroinvertebrates) in the Gulf (Vinuesa, 2005 ;
-Galván et al., 2022). Finally, San Jorge Gulf is exposed to urban and
-industrial pollution due to an oil monobuoy from which oil manipulation
-and general oil transport along the Patagonian coast registered several
-oil spills and chronic oil discharges (García-Borboroglu, Boersma,
-Reyes, \& Skewgar, 2008). Other marine systems impacted by oil spill
-showed an important decrease in marine bird populations (Irons, Kendall,
-Erickson, McDonald, \& Lance, 2000), seals and macroalgae (e.g. Garrott,
-Eberhardt, \& Burn (1993); Paine et al. (1996)), with examples of
-cascading effects throughout the food web (Paine et al., 1996; Peterson,
-2001).
-
-\hypertarget{beagle-channel}{%
-\subsubsection{3.2 Beagle Channel}\label{beagle-channel}}
-
-A main anthropogenic stressor in the Beagle Channel is the introduction
-of invasive species (Table 2). Salmonidae were introduced to Tierra del
-Fuego in the 1930s. Especially Chinook salmon Oncorhynchus tshawytscha
-causes concern. The detection of Chinook salmon in Tierra del Fuego
-dates back to April 2006, and its population has been expanding since
-then (Fernández et al., 2010; Nardi, Fernández, Vanella, \& Chalde,
-2019). Being a top predator Chinook salmon can compete with several
-native species in the Beagle Channel (Correa \& Gross, 2008), and prey
-over native species such as Notothenioids (Eleginops maclovinus,
-Patagonotothen tessellata, P. cornucola, P. sima, Paranotothenia
-magellanica, Harpagifer bispinis), the Atherinidae Odontesthes smitti
-and O. nigricans, the Fuegian sprat Sprattus fuegensis, and larvae of
-king crabs (Lithodes antarcticus and Paralomis granulosa) (Fernández et
-al., 2010). J. E. Ciancio et al. (2008) observed that Chinook salmon in
-the Southern Patagonian Shelf Ecosystem Area primarily feed on sprats
-and display trophic levels comparable to those of intermediate-sized
-fish and cephalopod predators species, showing significant dietary
-overlap with Magellanic penguins (Spheniscus magellanicus). Another
-potential competitor for Chinook salmon in the Beagle Channel is the
-Commerson's dolphin (Cephalorhynchus commersonii), which shares a
-similar diet (Riccialdelli et al., 2013).
-
-In the Beagle Channel, other anthropogenic stressors include
-contaminants like metals, perfluorinated compounds, hydrocarbons, and
-microplastics found in animal tissue and sediments. Some studies
-reported varying heavy metal levels in sea mussel tissues and sediments,
-indicating bioavailability differences (Duarte, Giarratano, Amin, \&
-Comoglio, 2011). Other research found similar carbon and carbohydrate
-levels in Ushuaia Bay's surface sediments to those in hypertrophic
-ecosystems, along with hydrocarbons and heavy metals linked to port and
-industrial activities (Gil, Torres, Amin, \& Esteves, 2011).
-Commendatore, Nievas, Amin, \& Esteves (2012) identified three distinct
-hydrocarbon accumulation zones in the Bay. Llorca et al. (2012) found
-high levels of perfluorinated compounds in algae, fish, and guano.
-Ferreira et al. (2021) showed that black southern cod in Ushuaia Bay may
-be exposed to endocrine-disrupting compounds from urban and industrial
-pollution. Analía F. Pérez et al. (2020) and Ojeda et al. (2021) found
-microplastics in M. edulis chilensis and Nacella magellanica,
-respectively. These studies link pollutants to Ushuaia (54°48′S 68°18′W)
-and its port and industrial activities. We expect the Beagle Channel
-area closest to the city to be most affected. Contaminants can spread
-through the food web, magnifying the risk to higher-level organisms.
-Fioramonti et al. (2022) studied mercury transfer in three southwest
-Atlantic Ocean food webs and found biodilution in the Beagle Channel and
-Atlantic coast of Tierra del Fuego webs. However, mercury concentrations
-rose with benthivory in these webs, and higher mercury was found in
-phytoplankton and Grimothea gregaria. Squat lobsters connect pelagic and
-benthic habitats, so any disruption to them could disrupt the food web
-(Rodriguez et al., 2022). Dodino et al. (2022) found the highest mercury
-levels in Magellanic penguin feathers from offshore colonies in Tierra
-del Fuego. Recently, Ushuaia's kelp forests have seen a decrease in
-biodiversity and changes in macroalgae composition due to urban
-pollution (Kaminsky et al., in prep.).
-
-\hypertarget{burdwood-bank}{%
-\subsubsection{3.3 Burdwood Bank}\label{burdwood-bank}}
-
-The stressors reported for the ecosystem of the Marine Protected Areas
-Namuncurá within Burdwood Bank I and II are mostly anthropogenic; there
-is a lack of studies focusing on the environmental stressors that are
-known to be occurring at a regional scale (e.g.~sea surface warming,
-Franco, Combes, \& González Carman (2020)) (Table 2). Several fisheries
-targeting demersal fishes operate in the vicinity and within the
-ecosystem of the Marine Protected Areas (i.e.~Marine National Reserve
-management category). The Patagonian fisheries on the toothfish
-Dissostichus eleginoides has gained prominence in recent years (P. A.
-Martínez, Wöhler, \& Troccoli, 2015; L. Allega et al., 2020; Gorini,
-Lukaszewicz, \& Giussi, 2021; Administración de Parques Nacionales,
-2022). Although these are regulated by the Argentinean government,
-incidental catches do occur, where demersal fishes of the genera
-Coelorinchus and Macrourus, seabirds and benthic invertebrates (30+
-taxa) are the most common bycatches (Gaitán \& Marí, 2016; Patricia A.
-Martínez et al., 2022). Noteworthy, among the invertebrates caught, 8
-species are indicator taxa of vulnerable marine ecosystems (Gaitán \&
-Marí, 2016; Schejter \& Albano, 2021). Independent assessments of these
-bycatches suggest no significant impact on the communities (Gaitán \&
-Marí, 2016; Patricia A. Martínez et al., 2022). Besides bycatch, species
-of seabirds are being affected by the fishery due to discards, altering
-its diet; the most frequently encountered species are Black-browed
-albatross Thalassarche melanophris, Southern giant petrel Macronectes
-giganteus, Cape petrel Daption capense, Southern royal albatross
-Diomedea epomophora, Northern giant petrel M. halli, and White-chinned
-petrel Procellaria aequinoctialis (Tamini et al., 2023). Nevertheless,
-there is a lack of knowledge considering the species' role in the
-ecosystem and the potential joint effect of both target fishes and
-bycatch in a broader food web framework.
-
-Anthropogenic contaminants such as microplastics and mercury are present
-in the water column of the Burdwood Bank ecosystem (Cossi et al., 2021;
-Di Mauro et al., 2022; Fioramonti et al., 2022). Microplastics are
-distributed all along the water column, from surface to deep waters
-(3-2450 m) (Di Mauro et al., 2022). More importantly, microplastics were
-found in soft tissues of benthic macroinvertebrates (sea stars Henricia
-obesa and Odontaster penicillatus) and benthopelagic fishes
-(Patagonotothen guntheri and P. ramsayi), which not only incorporated
-the contaminant from the environment through their filter-feeding system
-but could also get it indirectly from prey organisms already containing
-plastics in their tissues (Cossi et al., 2021). Notably, one of the
-contaminated species, the long tail southern cod Patagonotothen ramsayi,
-is part of the core group of species that drive the ecosystem through
-the suggested wasp-waist control (Riccialdelli et al., 2020). Mercury
-transfer and biomagnification are ongoing processes in the ecosystem,
-which are occurring at a greater pace than near coastal areas (Beagle
-Channel) (Fioramonti et al., 2022). It's important to note that the
-Fuegian sprat Sprattus fuegensis, a pelagic fish with a mid-trophic
-level in the food web, presented the highest levels of mercury
-(Fioramonti et al., 2022). Considering the wasp-waist control of the
-Fuegian sprat in the food web (Riccialdelli et al., 2020), a rapid and
-widespread contamination to the top predators is expected (Fioramonti et
-al., 2022).
-
-In recent years, licenses for seismic studies and exploration of
-hydrocarbon resources have been granted all along the northwestern limit
-of the Marine Protected Areas (Secretaría de Gobierno de Energía Res. Nº
-65/2018). Although effects from these types of surveys on marine mammals
-and seabirds are well-known for other regions of the world (Nowacek et
-al., 2015), there is no particular knowledge for this ecosystem.
-However, several documents warn of the potential negative effects this
-may have on the species inhabiting the Burdwood Bank area (Lucrecia
-Allega et al., 2019; de Haro et al., 2022).
-
-Despite evidence of warming at surface, mid-water and bottom layers (100
-m) in Burdwood Bank (Franco et al., 2020), specific studies on the
-oceanographic aspects of the system are lacking. In this sense, there is
-a big question mark about the environmental stressors impact on the
-species and trophic interactions in Burdwood Bank.
-
-\hypertarget{scotia-sea}{%
-\subsubsection{3.4 Scotia Sea}\label{scotia-sea}}
-
-The Scotia Sea is a vast and heterogenous oceanic region, where
-especially the areas around South Georgia island represents an area of
-interest, here referred to as `Northern Scotia Sea'. The majority of
-studies analyzing the stressors' effects come from this area.
-
-The Scotia Sea has experienced one of the largest levels of warming
-within the polar regions (Whitehouse et al., 2008). Together with the
-Southern Annular Mode anomalies this has caused a long-term decrease in
-krill abundance; more pronounced in the northern than in the southern
-Scotia Sea (E. J. Murphy et al., 2007; Atkinson et al., 2019). Over the
-past 90 years, the krill also showed an increase in mean body length
-(Atkinson et al., 2019), which may also alter predator-prey interactions
-and allow reaching cooler feeding grounds near the seabed, with the
-potential to link krill to unexpected predators (Schmidt et al., 2011).
-Another consequence of the mentioned environmental stressors, is a
-change in krill distribution due to a southward contraction (Atkinson et
-al., 2019). It is noteworthy here, that the distributional shift has not
-affected all species inhabiting the Northern Scotia Sea, and most
-abundant calanoid copepods have maintained their distribution (Tarling,
-Ward, \& Thorpe, 2018). Considering the above, food web models of the
-Northern Scotia Sea have suggested shifts in the structure and
-functioning of the food web, from krill-based to non-krill-based, where
-myctophid fishes and squid are playing important roles (Hill, Keeble,
-Atkinson, \& Murphy, 2012; Saunders et al., 2019).
-
-The principal anthropogenic stressor of the Scotia Sea is commercial
-fisheries. Krill fishery not only stresses the targeted species, but
-also the many predators that depend on it as a food source (Hilborn et
-al., 2017). Yet, data currently available from monitoring of krill and
-its predators remain insufficient, hence identifying the potential
-fishery impacts on the ecosystem is difficult (P. N. Trathan et al.,
-2021). Apart from krill fishery, two other commercial fisheries operate
-in the Scotia Sea, targeting Patagonian toothfish species Dissostichus
-eleginoides and D. mawsoni. The D. eleginoides stock is linked to the
-stock at South Georgia (`Northern Scotia Sea') (Collins, Brickle, Brown,
-\& Belchier, 2010), while the D. mawsoni stock is linked to the
-Antarctic continental shelf (`Southern Scotia Sea') (Soeffker et al.,
-2022). Despite the fact that the mentioned fisheries are certified by
-the Marine Stewardship Council standards, Philip N. Trathan (2023)
-identified several concerns regarding aspects of fisheries itself, other
-species' population status (i.e.~recovery of baleen whales), and
-environmental stressors (i.e.~sea warming), which could have synergistic
-effects on the food web structure and functioning that are still
-unknown.
-
-Mercury transfer and biomagnification are current processes occurring in
-the Scotia Sea, where the total concentration of contaminants increase
-with trophic level and are highest in notothenioid and myctophid fishes
-(e.g.~Dissostichus eleginoides, Gymnoscopelus nicholsi), and seabirds
-(Seco et al., 2021). During years of low Antarctic krill abundance,
-predators must deal with both the stress of reduced prey availability
-and the concurrent rise in mercury exposure (Seco et al., 2021).
-
-\hypertarget{potter-cove-antarctica}{%
-\subsubsection{3.5 Potter Cove
-(Antarctica)}\label{potter-cove-antarctica}}
-
-Regional warming in the last half century has been one of the main
-factors driving changes in Potter Cove (Western Antarctic Peninsula)
-(Hendry, Meredith, \& Ducklow, 2018; Chown et al., 2022). Sudden
-environmental changes have occurred, such as sea surface temperature
-increase, salinity decrease, suspended particulate matter loading and
-chlorophyll-a increase, all linked to climatic cycles (Southern Annular
-Mode and El Niño Southern Oscillation) (Schloss et al., 2012; Bers,
-Momo, Schloss, \& Abele, 2013). Particularly, sea warming has produced
-drastic environmental and biological transformations (e.g.~shifts in
-dominance of benthic community) in the Potter Cove ecosystem (Rückamp,
-Braun, Suckro, \& Blindow, 2011; Schloss et al., 2012; María Liliana
-Quartino et al., 2013; Sahade et al., 2015; Hernández, Lopez, Piquet,
-Mac Cormack, \& Buma, 2019), a system highly dependent on sea-ice
-dynamics (Table 2). In Potter Cove, total sea ice cover has decreased
-since 1991 (Schloss et al., 2012). Changes in the annual timing of
-landfast ice formation and breakup of the sea ice cover has multiple
-effects on species in the food web (Michel et al., 2019; Rossi et al.,
-2019). Warmer winters and springs result in earlier sea-ice melt,
-causing an abrupt increase in the light available benthic primary
-producers (Dolores Deregibus et al., 2020). Sea ice also mediates
-physical disturbances to the benthos by influencing sedimentation and
-iceberg scouring. These factors affect the production of macroalgae,
-albeit in opposite ways (D. Deregibus et al., 2016, 2017), and
-microphytobenthos (Hoffmann et al., 2019; Braeckman et al., 2021). On
-the other hand, sea ice is an important habitat for diatoms and its
-associated consumers, including copepods and krill (Flores et al.,
-2012), and thus important for bentho-pelagic nutrient and carbon cycling
-during winter. Additionally, a decrease in winter sea ice cover produces
-an increase in physical perturbation on benthic shallow communities in
-coastal shallows due to ice scouring (D. Deregibus et al., 2017). The
-glacier surrounding Potter Cove has been receding at an increasing rate
-since 1950 (Rückamp et al., 2011), which has caused a massive discharge
-of sediment-laden meltwater (Meredith et al., 2018). Large quantities of
-suspended particles affect growth, survival and reproduction of benthic
-species. This had led to a major shift in the benthic community
-structure, from a filter feeders--ascidian domination to a mixed
-assemblage with scavengers and opportunistic species (Pasotti et al.,
-2015; Sahade et al., 2015), and the metabolic balance in benthos went
-from net autotrophy to heterotrophy (Hoffmann et al., 2019; Braeckman et
-al., 2021). Additionally, massive stranding events of the tunicate Salpa
-thompsoni and the euphausiid Euphausia superba (krill) linked to the
-presence of glacial meltwater have been reported (Fuentes et al., 2016).
-Rising temperatures leading to ice and glacial melting has also
-substantial impacts on pelagic primary productivity, since it reduces
-water salinity, affecting water column stratification, light penetration
-and nutrient availability for photosynthesis (Schloss et al., 2012). In
-Potter Cove, changes in biomass of most phytoplankton species have been
-observed under heat wave conditions, resulting in a shift from a
-microplankton to a nanoplankton dominated community (Antoni et al.,
-2020; Latorre et al., 2023). This means that in areas strongly affected
-by glacier melt, the planktonic food web is dominated by the microbial
-loop (ciliates and heterotrophic dinoflagellates preys upon
-nanophytoplankton, which are sequentially available prey for small
-omnivorous copepods), instead of being predominantly herbivorous (Garcia
-et al., 2016, 2019). In addition, phytoplankton species under these
-warming conditions showed a decrease in metabolic rates and in the
-quality of the fatty acids composition (Latorre et al., 2023).
-
-\hypertarget{weddell-sea-antarctica}{%
-\subsubsection{3.6 Weddell Sea
-(Antarctica)}\label{weddell-sea-antarctica}}
-
-In the Weddell Sea several stressors have already been triggered by
-global warming effects (Table 2), from which spatial and temporal
-reduction in sea ice is suggested to be driving changes in pelagic and
-benthic communities (Constable et al., 2014; Julian Gutt et al., 2021).
-Sea ice extent has reached new record lows since the satellite era began
-in 1978. Sea warming has been substantial in recent years: in 2017 the
-mean temperature for February reached 1.45°C, the highest monthly mean
-ever recorded (0.56°C above the climatological mean) (Turner et al.,
-2020). In this context, it has been suggested that Antarctic krill
-Euphausia superba has already declined as a result of productivity
-changes caused by sea ice declines (Atkinson, Siegel, Pakhomov, \&
-Rothery, 2004). Declining sea ice cover allows increased access to krill
-by predators (So Kawaguchi, Nicol, \& Press, 2009), which further
-contributes to decreased krill abundances. This in turn can result in
-reduced carbon export due to decreased fecal pellets from krill (Pauli
-et al., 2021).
-
-On the other hand, sea ice loss increases light availability, triggering
-primary production by phytoplankton in the short-term (Pineda-Metz et
-al., 2020; Dinniman, St-Laurent, Arrigo, Hofmann, \& van Dijken, 2023).
-Furthermore, a warmer and more stable water column with a shallow upper
-mixed layer, is expected to enhance the dominance of cryptophytes over
-diatoms which may favor salp populations over krill populations; thereby
-reducing the magnitude of energy transfer to higher trophic levels and
-the seabed (Isla, 2023).
-
-Higher trophic level species are expected to respond differently to
-global warming in the Weddell Sea. In this regard, Notothenioid fishes
-(e.g.~Pleuragramma antarcticum) face multiple stressors (sea warming,
-sea ice decline, ocean acidification) that threaten their survival.
-While some species exhibit physiological plasticity to compensate for
-increased oxygen demand, most notothenioid fishes are stenothermal and
-unable to adjust their metabolic functioning (Mintenbeck et al., 2012).
-It is anticipated that the thermal habitat preferred by the Antarctic
-toothfish Dissostichus mawsoni could undergo contraction in the coming
-three decades (Constable et al., 2014), further emphasizing the
-potential impact of global warming effects on these species. Marine
-mammals, Weddell and crabeater seals (Leptonychotes weddellii and
-Lobodon carcinophagus), exhibit varying levels of sensitivity. The
-latter exhibits a preference for breeding in close proximity to krill
-swarms, and thus is particularly susceptible to reductions in sea ice
-concentrations and sea surface temperatures. Rescued sea ice can
-significantly affect their post- and future breeding foraging success
-(Siniff et al., 2008; Wege et al., 2021). In addition, the Antarctic
-petrel Thalassoica antarctica, which is one of the most abundant
-seabirds in the area, is a sea ice dependent forager and breeder
-(Orgeira et al., 2021); therefore the loss of this habitat will degrade
-its foraging success and reproductive output over time. The snow petrel
-Pagodroma nivea also relies heavily on sea ice for foraging and its
-colonies in the Weddell Sea may be affected. The emperor penguin
-Aptenodytes forsteri uses sea ice for breeding; any reductions could
-constrain its populations, as evidenced by recent observations in the
-Bellingshausen Sea region (Fretwell, Boutet, \& Ratcliffe, 2023). The
-Arctic tern Sterna paradisaea spends the summer in the Weddell Sea
-exploiting krill swarms under receding ice edges, then declines in ice
-cover may reduce prey availability and quality of molting habitats.
-Continued warming is thus expected to gradually erode the abundance and
-distribution of these `primary species' that dominate the avifauna of
-the Weddell Sea through loss of critical sea ice habitat (Orgeira et
-al., 2021). Variations in sea ice extent have implications for great
-whales, such as the Humpback whale Megaptera novaeangliae, since their
-primary prey resource is the Antarctic krill (Braithwaite et al., 2015).
-Decreased winter ice coverage results in reduced suitable habitat and
-lower krill abundance (Braithwaite et al., 2015), with flow-on effects
-for whale body condition observed historically in harvest data. With
-climate projections indicating ongoing sea ice losses, further threats
-to critical krill populations pose risks to the energy intake and
-reproductive success and long-term viability of humpback whale
-populations dependent on consistent Antarctic feeding (Pallin et al.,
-2023).
-
-Iceberg scouring is a major factor in the high biodiversity of benthic
-communities in the Weddell Sea (Julian Gutt \& Starmans, 2001). Even at
-600 m depths, iceberg scouring has a strong effect on the benthic
-environment, disrupting the upper layers of the seabed and removing
-macrofauna. This patchy disturbance and distribution pattern occurs
-roughly every 200 square meters on the Antarctic continental shelf.
-Global warming is predicted to raise iceberg scouring frequency (J. Gutt
-et al., 1996; Julian Gutt, 2001; Dan A. Smale et al., 2008), disrupting
-the environment (J. Gutt et al., 1996; Dan A. Smale \& Barnes, 2008).
-Julian Gutt et al. (2015) expects tipping points are significant due to
-these effects and lack of knowledge.
-
-\hypertarget{from-species-stressors-to-food-web-effects}{%
-\subsection{4. From species' stressors to food web
-effects}\label{from-species-stressors-to-food-web-effects}}
-
-A major challenge in contemporary ecology lies in predicting the effects
-of stressors on complex multispecies systems, such as food webs. Network
-analysis has proved to be a powerful tool to tackle this issue, since it
-can capture the effects of individual and multiple stressors on
-communities and ecosystems (Montoya et al., 2009; O'Gorman, Fitch, \&
-Crowe, 2012; Bruder, Frainer, Rota, \& Primicerio, 2019; Polazzo,
-Marina, Crettaz-Minaglia, \& Rico, 2022). Environmental and
-anthropogenic stressor effects in the southwest and the Atlantic sector
-of the Southern Ocean have been mostly assessed individually and at the
-organism and/or population, i.e., at the node level (Table 2), with one
-exception: the effect of fisheries in the San Jorge Gulf food web (see
-section below for more details). To address the most plausible stressors
-effects on the selected food webs, given the current information, we
-built hypotheses for each study area. To this aim, we developed a
-theoretical framework considering the following: a) stressor(s), b)
-parameter(s) affected, c) node-level properties of the affected species,
-and d) network-level properties of the food web. We considered that a
-stressor will affect one of the following species' characteristics or
-parameters: metabolism, biomass, distribution, and diet (Figure 2).
-`Metabolism' refers to any change related to metabolic rate, such as
-reproduction, hatching, larval development, growth and mortality, and
-contamination due to pollutants (e.g.~growth effect in filter-feeders
-due to sediment in water column in Potter Cove; endocrine disruption in
-fish due to urban pollutants in Beagle Channel). `Biomass' indicates an
-effect at the population level, where the density/abundance is being
-impacted (e.g.~abundance decreases in macrobenthos due to iceberg
-scouring in Weddell Sea). `Distribution' entails a change at the
-population level in the geographic space occupied by a species,
-e.g.~southward contraction of Antarctic krill due to sea warming of the
-Scotia Sea. `Diet' includes alterations in the prey items of a species
-at the population level, e.g, due to prey switching, having a direct
-effect on the structure of the food web, e.g.~new prey item (discards)
-for seabirds due to fishery activities in Burdwood Bank. Next, we
-considered node- and network-level properties relevant to the
-hypothesized stressor effects on the food webs, and which have been
-previously calculated for the studied food webs (Table 3). At the
-node-level, we included: a) degree, b) trophic position, c) omnivory
-index, and d) relative abundance (see Table S1 in Supporting Information
-for properties of stressed nodes). At the network-level, we considered:
-a) connectance, b) path length, c) mean trophic level, and d) omnivory
-(Table 1).
-
-\begin{figure}
-\centering
-\includegraphics[width=6.27in,height=3.528in]{Figures/Figure2_StressorDiagram.png}
-\caption{Conceptual diagram: from species' stressors to food web
-effects. See text for explanation.}
-\end{figure}
-
-\scriptsize
-
-Table 3. Node and network-level properties used to build hypotheses on
-the stressors' effects.
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1963}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2617}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3925}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1495}}@{}}
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Property}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Definition}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Relevance for stressor effects}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Reference}
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-\emph{Node-level} & & & \\
-Degre & Number of feeding interactions in which the species participates
-as prey and/or predator. & Perturbations to high-degree species may have
-more significant effects on the food web robustness to perturbations
-than low-degree species. & Dunne, Williams, \& Martinez (2002a); Jordán,
-Benedek, \& Podani (2007) \\
-Trophic position & Place in the food web relative to the basal resources
-that support the community. Classifies species in: basal, intermediate
-and top. & Perturbations on basal resources, intermediate species and
-top predators are expected to have large effects on the rest of their
-communities if ecosystem control is bottom-up, wasp-waist or top-down,
-respectively. & Williams \& Martinez (2000); Thompson, Hemberg,
-Starzomski, \& Shurin (2007) \\
-Omnivory & Consumer resource use across trophic levels. & High-omnivore
-species (generalists) are more flexible than low-omnivore species to
-diet changes. & Thompson et al. (2007) \\
-Relative abundance & Species' density in proportion to the other species
-of the food web. & Perturbations on abundant (dominant) species are
-expected to have large effects on the stability and energy flux of the
-food and ecosystem, respectively. & Nilsson \& McCann (2016) \\
-\emph{Network-level} & & & \\
-Conectance & Proportion of actual interactions among possible ones. &
-Estimator of community sensitivity to stressors. High connectance gives
-resistance and resilience to the food web. & Dunne, Williams, \&
-Martinez (2002b) \\
-Path length & Average distance, accounted by the number of interactions,
-between any pair of species. & Short distances enhance rapid and broad
-propagation of perturbations. & Albert \& Barabási (2002) \\
-Mean TL & Average of all species' trophic position contained in the food
-web. & Influences the magnitude and efficiency of trophic transfer. A
-higher mean food chain length reflects increased energy availability and
-productivity. & Duffy et al. (2007); Olivier et al. (2019) \\
-Omnivory & Proportion of species that feed at different trophic levels.
-& It provides trophic flexibility to an ecosystem. Reduces probability
-of trophic cascades. & Kratina, LeCraw, Ingram, \& Anholt (2012) \\
-\end{longtable}
-
-\normalsize
-
-\hypertarget{warming-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}{%
-\subsubsection{4.1 Warming effects on food webs in a southwest Atlantic
-- Antarctic
-gradient}\label{warming-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}}
-
-The most common stressor reported along the southwest Atlantic -
-Antarctic gradient is global warming, except for Beagle Channel and
-Burdwood Bank, which are more influenced by the introduction of an alien
-species and fisheries, respectively (section 3). The main
-characteristics of global warming in the region, and the most plausible
-drivers of change, are: sea warming, glacial retreat, elevated sediment
-input in the water column, and reduction of the sea ice extent. These
-drivers act in different ways and magnitudes in the studied locations
-along the latitudinal gradient. The above does not mean that there are
-no other stressors interacting with global warming, potentially
-buffering the overall effect on the food web (e.g.~sea warming and
-fishery in San Jorge Gulf). Climate change has led to several
-well-documented impacts on marine species regarding distributional
-shifts induced by warming of marine currents (Wu et al., 2012;
-Poloczanska et al., 2013; Vergés et al., 2014; Vergés et al., 2019).
-Furthermore, warmer temperatures increase species metabolic rates
-(Brown, Gillooly, Allen, Savage, \& West, 2004). Changes in metabolic
-rates can subsequently translate into shifts in species traits (body
-size, Vucic-Pestic, Ehnes, Rall, \& Brose (2011); Klein, Hill, Hinke,
-Phillips, \& Watters (2018){]}, biomass (Perry et al., 2020) and
-distribution (Kortsch, Primicerio, Fossheim, Dolgov, \& Aschan, 2015).
-Alterations in the species body size and distributions have ripple
-effects on feeding interactions, for example, it can introduce new
-feeding interactions (Vergés et al., 2014; Pecuchet et al., 2020),
-modify existing ones, and shorten energy pathways (Bartley et al., 2019;
-O'Gorman et al., 2019), and reduce trophic efficiencies (Vucic-Pestic et
-al., 2011).
-
-In recent years, several new fish (Galván et al., 2022) and
-macroinvertebrates species (Vinuesa, 2005; López-Gappa, 2022) were
-registered in Patagonia, mostly in San Jorge Gulf in relation to the
-southward range shift of warm-temperate species. This distributional
-change is driven by the tropicalization of temperate waters caused by
-sea warming (Vergés et al., 2014; Vergés et al., 2019). Because of its
-location in the ecotone between two biogeographic provinces, the
-Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) (Balech \&
-Ehrlich, 2008), the San Jorge Gulf is prone to changes in species
-composition. We hypothesize that sea warming will alter the food web
-structure topologically, by increasing the number of species and
-interactions. Newcomers are, in general, mid-trophic level species with
-generalist diets, hence an increase in food web connectance may be
-expected (Bartley et al., 2019). In another temperate ecosystem, an
-increase in the number of fish species, led to an increase in functional
-diversity and predation rate (Sgarlatta, 2023); consequences that may
-also be expected in San Jorge Gulf. Given the short path length of the
-San Jorge Gulf food web, the disturbances from the listed stressors are
-expected to spread to many species of the food web. However, it has to
-be acknowledged that the increase in functional diversity driven by the
-range expansion of warm-temperate species is contrary to the process of
-homogenization and loss of functional diversity in the area driven by
-trawl fisheries (Rincón-Díaz et al., 2021).
-
-In the middle of the latitudinal gradient (considered in this study),
-the Scotia Sea has experienced one of the largest levels of sea warming
-of any polar region (Whitehouse et al., 2008; Atkinson et al., 2019).
-López-López et al. (2022) suggested that the southward distributional
-change of generalist predators from the northern towards southern Scotia
-Sea increases network connectance of the latter, while decreasing its
-modularity. The lower modularity may increase the probability of
-perturbations spreading through the network (Stouffer \& Bascompte,
-2011), which may be offset by increased connectance enhancing robustness
-to species loss (Dunne et al., 2002a). In the northern Scotia Sea around
-South Georgia Island, we suggest that the declining krill biomass driven
-by sea warming (Atkinson et al., 2019), and ocean acidification and
-pollution synergy (Rowlands et al., 2021), will reduce the energy
-transfer to top predators like seabirds and marine mammals. However,
-this may be buffered since the dominant copepod species have maintained
-its distribution (Tarling et al., 2018), but most importantly, showed an
-abundance increase in recent decades likely due to reduced predation and
-competition for food (Ward, Tarling, \& Thorpe, 2018). All this is
-significant for the structure of the food web given the central role of
-krill and copepods, characterized by high degree and mid-trophic
-position (Table S1). Overall, the food web's inherent resilience, marked
-by high connectance and omnivory, added to the potential compensation
-for the krill decrease due to a copepod increase, may buffer against
-structural changes.
-
-In Potter Cove, a fjord-like Antarctic ecosystem, the impacts of climate
-change affect many species within the food web. Potter Cove has recently
-experienced frequent events of marine heatwaves, i.e.~prolonged periods
-of anomalously high sea surface temperatures (Oliver et al., 2018;
-Latorre et al., 2023). This has led to decreases in biomasses of
-different planktonic functional groups (Garcia et al., 2019; Latorre et
-al., 2023). Given the relatively low abundance of phytoplankton,
-zooplankton's low degree, and the modular configuration of the food web,
-we hypothesize that changes in these nodes, due to increased sea
-temperatures, will be retained in the basal pelagic compartment of the
-food web and will not expand to higher trophic levels. Benthic primary
-producers in Potter Cove are being influence by the decrease in winter
-sea ice cover (higher light availability), the increased levels of
-sediments in the water column due to glacial melt run-off (lower light
-penetration) and the newly free-ice areas available for colonization
-associated to glacier retreat. The overall local effect of climate
-change on macroalgae is a net increase in their production (Dolores
-Deregibus et al., 2023). It has been proposed that larger diversity in
-primary producers can support a more diverse food web with more
-specialized consumers (Iken et al., 2023). We expect to see differential
-effects of climate change on hard and soft bottom associated food webs
-(Cordone et al., 2020). Given the high relative abundance and the high
-degree of the macroalgae functional group (Table S1), we expect a longer
-hard bottom food web, wider consumer trophic niches, and that it will
-become more stable as sea ice cover decreases and the glacier retreats
-due to global warming. In soft bottom areas of the Cove, multiple food
-web nodes are being affected by ongoing warming effects: decrease in net
-primary production of benthic microalgae (Hoffmann et al., 2019), and
-changes in the benthic community biomass, distribution and composition
-(Pasotti et al., 2015; Sahade et al., 2015). Given that the Potter Cove
-food web's present low connectance and omnivory, we suggest fragility
-and potential trophic cascade effects (Marina et al., 2018) with
-pronounced changes in energy fluxes.
-
-The southernmost location of the latitudinal gradient is the Weddell
-Sea, where the main effect of global warming is the decrease in sea ice
-extent, with reported anomalies in the past summer seasons (Fretwell et
-al., 2023). Declining sea ice extent has reduced the abundance of krill
-(Atkinson et al., 2004; Flores et al., 2012), and produced an increase
-in phytoplankton productivity (Pinkerton et al., 2021; Isla, 2023),
-altering the plankton community structure, and benefiting cryptophytes
-over diatoms (Lin et al., 2021). Moreover, habitat loss from sea ice
-decline will reduce the foraging success and breeding sites of seabirds
-(e.g., snow petrel Pagodroma nivea and emperor penguin Aptenodytes
-forsteri), decreasing their biomassess and modifying their
-distributions. The projected rise in iceberg scouring is expected to
-significantly alter the biomass and community structure of macrobenthos,
-which in turn will impact mid-trophic level predators such as demersal
-fish (Julian Gutt, 2001; Mintenbeck et al., 2012). While we do not
-anticipate large-scale topological changes in the food web, local
-extinctions could lead to such changes, particularly affecting benthic
-species (Julian Gutt \& Piepenburg, 2003). Given that the impacted
-species---whether individually like krill, or collectively like
-macrobenthos---present a mid-trophic position, high biomass and high
-degree (Table S1), we hypothesize that significant shifts in energy
-fluxes will occur. Additionally, the food web's low proportion of
-omnivores suggests reduced system resilience (Table 1), increasing the
-likelihood of regime changes (Julian Gutt et al., 2015).
-
-The two ecosystems in the subantarctic region, the Beagle Channel and
-Burdwood Bank, are more affected by other anthropogenic stressors than
-warming. Although these areas might be impacted by global warming
-effects due to studies at a regional scale (Franco et al., 2020), to
-date no studies exist for Beagle Channel and Burdwood Bank ecosystems.
-In the Beagle Channel, the introduction of chinook salmon, a non-native
-species, poses a significant risk to the existing food web (Fernández et
-al., 2010). We hypothesize that chinook salmon's predation on Fuegian
-sprat and black southern cod will disrupt the established patterns of
-interaction within the food web. Both of these prey species are crucial
-due to their mid-trophic positions and relatively high abundance (Table
-S1). Moreover, we expect that changes in the black southern cod
-population will have a more significant impact on the food web than
-changes in the Fuegian sprat population, as the black southern cod has a
-higher degree (Table S1). Overall, these disruptions could have
-far-reaching effects on the ecosystem. This is particularly concerning
-given the short path length of the food web, which means that changes
-can quickly propagate through the system, affecting many species and
-potentially destabilizing the entire network. This phenomenon is further
-heightened by the ecosystem's inherent vulnerability to changes at
-mid-trophic levels, often referred to as wasp-waist control. In the
-Burdwood Bank region, fishing activities may be the main stressor
-causing shifts in the food web (Table 2). We hypothesize that a
-combination of factors will destabilize the already fragile ecosystem,
-characterized by low connectance and low omnivory (Table 1). These
-factors include a decline in the biomass of the Patagonian toothfish -a
-key, highly-connected species (Table S1)- as well as smaller changes in
-the biomass of four mid-level fish species, five top-level seabird
-species, and over 30 types of benthic macroinvertebrates due to bycatch
-(Gaitán \& Marí, 2016; Patricia A. Martínez et al., 2022; Tamini et al.,
-2023). Additionally, alterations in the diets of six seabird species,
-caused by discarded catch (Tamini et al., 2023), are expected to disrupt
-the energy flow and further reduce the stability of the food web.
-
-\hypertarget{gaps-and-future-perspectives}{%
-\subsection{5. Gaps and future
-perspectives}\label{gaps-and-future-perspectives}}
-
-Since this review deals with qualitative data regarding, not only
-prey-predator interactions but also the stressor effect, adding
-quantitative data to the food webs (i.e.~interaction strength
-estimations) and/or to the stressor effect (i.e.~magnitude) will provide
-a better comprehension of how species' stressors might be translated
-into food web effects. In this context, quantitative food webs will be
-useful if they reflect energy fluxes among species (Nilsson \& McCann,
-2016). Emerging methods have been proposed in this sense promising ways
-to estimate shifts in species interactions within food webs (Gauzens et
-al., 2019; Gellner, McCann, \& Hastings, 2023). These shifts, in turn,
-could lead to changes in energy fluxes within the ecosystem.
-
-As summarized in Table 2, in the selected study areas of the southwest
-Atlantic - Antarctic latitudinal gradient several stressors might be
-directly affecting consumer's diets, triggered by modified environmental
-conditions (sea warming, reduced sea ice extent), new habitats (due to
-distributional shifts) and/or new species (alien species). Moreover, the
-population trend of important species is also changing (e.g., Funes
-(2020), Constable et al. (2014), Pineda-Metz (2019), Hindell et al.
-(2020), Woods et al. (2023)) driving changes in their roles as either
-predators or prey (e.g. Belleggia et al. (2017), Pasti et al. (2021)).
-These diet and biomass updates, either considered as a short or
-long-term effect, should be contemplated in order to generate reliable
-predictions of food web responses to multiple stressors in the southwest
-Atlantic - Antarctic region. Examples of these interactions between
-diet, relative biomass, and their effects on food webs at different
-temporal scales include biological invasions and trawl fisheries. Both
-stressors, in the short term, increase the complexity of food webs by
-adding generalist predators and/or new prey (e.g., Cordone, Galván, \&
-Momo (2023)) or by enabling discard consumption (e.g., Funes et al.
-(2022)). However, in the long term, both stressors may lead to the
-biological extinction of certain prey and competitors (e.g., Anton et
-al. (2019)) or a significant reduction in target and incidental catch
-species (e.g., Dulvy et al. (2014)), thereby promoting food web
-simplification.
-
-Regarding data gaps, we should mention the cases for Beagle Channel and
-Burdwood Bank ecosystems, where almost no information exists for the
-impact of global warming effects (sea warming, glacial retreat, ocean
-acidification) in natural populations/communities, though warming
-effects have been shown at a regional scale (Franco et al., 2020). It is
-worth mentioning that in Beagle Channel recent experimental studies have
-tested the tolerance of fishes to scenarios of sea warming and/or
-acidification suggesting potential metabolic impacts (María Eugenia
-Lattuca, Boy, Vanella, Barrantes, \& Fernández, 2018; María E. Lattuca
-et al., 2023).
-
-Analyzing the impact of multiple stressors through observational studies
-can be challenging (Julian Gutt et al., 2021). This complexity arises
-from the potential for antagonistic effects, where impacts cancel each
-other out, or synergistic effects, where the combined impact is greater
-than the sum of individual effects (Crain et al., 2008; Boyd, Lennartz,
-Glover, \& Doney, 2015; Côté et al., 2016). These effects are further
-complicated to handle in the framework of complex food webs. The number
-of pathways of effect through which a species may affect or be affected
-by other species, and through which stressors may permeate communities,
-increases exponentially with the number of species and interactions in a
-network (Menge, 1995). In this sense, Beauchesne, Cazelles, Archambault,
-Dee, \& Gravel (2021) have developed a theory-grounded approach using
-motifs (i.e.~groups of species that, when put together, construct whole
-food webs) to simplify food webs; methodology that could be applied to
-our food web study cases.
-
-\hypertarget{conclusions}{%
-\subsection{Conclusions}\label{conclusions}}
-
-In the light of cumulative knowledge on how global warming and emerging
-stressors are affecting species inhabiting marine ecosystems in the
-Southern Hemisphere (e.g. Julian Gutt et al. (2021), Galván et al.
-(2022)), there is a need to better understand these changes in a more
-real framework where species interact and, consequently, might spread
-the stressor effect to other species in complex ways. To this end, we
-have reviewed the main environmental and anthropogenic stressors acting
-in six different areas along a large-scale latitudinal gradient, from
-temperate to Antarctic ecosystems. Using a theoretical framework that
-combines node (species) and network (food web) level data, we show how
-warming effects might affect food web structure and functioning. These
-qualitative predictions are intended to serve as the basis to studies
-that quantify how much the ongoing stressors are affecting food web
-properties, such as energy fluxes and stability, in marine ecosystems of
-the Southern Hemisphere.
-
-\hypertarget{references}{%
-\subsection*{References}\label{references}}
-\addcontentsline{toc}{subsection}{References}
-
-\hypertarget{refs}{}
+\subsection*{References}\label{references}
+
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Acha2004}{}}%
-Acha, E. M., Mianzan, H. W., Guerrero, R. A., Favero, M., \& Bava, J.
-(2004). Marine fronts at the continental shelves of austral {South
-America}: {Physical} and ecological processes. \emph{Journal of Marine
-Systems}, \emph{44}(1), 83--105.
-doi:\href{https://doi.org/10.1016/j.jmarsys.2003.09.005}{10.1016/j.jmarsys.2003.09.005}
-
-\leavevmode\vadjust pre{\hypertarget{ref-APN2022}{}}%
+\bibitem[\citeproctext]{ref-APN2022}
 Administración de Parques Nacionales. (2022). {Plan de gestión AMP
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Albert2002}{}}%
-Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex
-networks. \emph{Reviews of Modern Physics}, \emph{74}(1), 47--97.
-doi:\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Allega2019}{}}%
-Allega, Lucrecia, Braverman, M. S., Cabreira, A. G., Campodónico, S.,
-Colonello, J. H., Derisio, C. M., \ldots{} Verón, E. M. (2019).
-\emph{{Estado del conocimiento biológico pesquero de los principales
-recursos vivos y su ambiente, con relación a la exploración
-hidrocarburífera en la Zona Económica Exclusiva Argentina y
-adyacencias}}. {INIDEP}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Allega2020}{}}%
-Allega, L., Braverman, M., Campodónico, S., Carozza, C. R., Cepeda, G.
-D., Colonello, J. H., \ldots{} Verón, E. (2020). \emph{{Estado del
-conocimiento biológico pesquero de los principales recursos vivos y su
-ambiente, con relación a la exploración hidrocarburífera en la Zona
-Económica Exclusiva argentina y sus adyacencias}}. {Mar del Plata}:
-{Instituto Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Anton2019}{}}%
-Anton, A., Geraldi, N. R., Lovelock, C. E., Apostolaki, E. T., Bennett,
-S., Cebrian, J., \ldots{} Duarte, C. M. (2019). Global ecological
-impacts of marine exotic species. \emph{Nature Ecology \& Evolution},
-\emph{3}(5), 787--800.
-doi:\href{https://doi.org/10.1038/s41559-019-0851-0}{10.1038/s41559-019-0851-0}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Antoni2020}{}}%
+\bibitem[\citeproctext]{ref-Antoni2020}
 Antoni, J. S., Almandoz, G. O., Ferrario, M. E., Hernando, M. P.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Atkinson2019}{}}%
+\bibitem[\citeproctext]{ref-Atkinson2019}
 Atkinson, A., Hill, S. L., Pakhomov, E. A., Siegel, V., Reiss, C. S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Atkinson2004}{}}%
-Atkinson, A., Siegel, V., Pakhomov, E., \& Rothery, P. (2004). Long-term
-decline in krill stock and increase in salps within the {Southern
-Ocean}. \emph{Nature}, \emph{432}(7013), 100--103.
-doi:\href{https://doi.org/10.1038/nature02996}{10.1038/nature02996}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Baiser2012}{}}%
-Baiser, B., Gotelli, N. J., Buckley, H. L., Miller, T. E., \& Ellison,
-A. M. (2012). Geographic variation in network structure of a nearctic
-aquatic food web. \emph{Global Ecology and Biogeography}, \emph{21}(5),
-579--591.
-doi:\href{https://doi.org/10.1111/j.1466-8238.2011.00705.x}{10.1111/j.1466-8238.2011.00705.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Balech2008}{}}%
-Balech, E., \& Ehrlich, M. D. (2008). {Esquema biogeográfico del Mar
-Argentino}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ballerini2014}{}}%
-Ballerini, T., Hofmann, E. E., Ainley, D. G., Daly, K., Marrari, M.,
-Ribic, C. A., \ldots{} Steele, J. H. (2014). Productivity and linkages
-of the food web of the southern region of the western {Antarctic
-Peninsula} continental shelf. \emph{Progress in Oceanography},
-\emph{122}, 10--29.
-doi:\href{https://doi.org/10.1016/j.pocean.2013.11.007}{10.1016/j.pocean.2013.11.007}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bartley2019}{}}%
-Bartley, T. J., McCann, K. S., Bieg, C., Cazelles, K., Granados, M.,
-Guzzo, M. M., \ldots{} McMeans, B. C. (2019). Food web rewiring in a
-changing world. \emph{Nature Ecology \& Evolution}, \emph{3}(3),
-345--354.
-doi:\href{https://doi.org/10.1038/s41559-018-0772-3}{10.1038/s41559-018-0772-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bauer2022}{}}%
-Bauer, B., Berti, E., Ryser, R., Gauzens, B., Hirt, M. R., Rosenbaum,
-B., \ldots{} Brose, U. (2022). Biotic filtering by species' interactions
-constrains food-web variability across spatial and abiotic gradients.
-\emph{Ecology Letters}, \emph{25}(5), 1225--1236.
-doi:\href{https://doi.org/10.1111/ele.13995}{10.1111/ele.13995}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Beauchesne2021}{}}%
-Beauchesne, D., Cazelles, K., Archambault, P., Dee, L. E., \& Gravel, D.
-(2021). On the sensitivity of food webs to multiple stressors.
-\emph{Ecology Letters}, \emph{24}(10), 2219--2237.
-doi:\href{https://doi.org/10.1111/ele.13841}{10.1111/ele.13841}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Belgrano2005}{}}%
-Belgrano, A., Scharler, S. E. R. C. U. M., Scharler, U. M., Dunne, J.,
-\& Ulanowicz, R. E. (2005). \emph{Aquatic {Food Webs}: {An Ecosystem
-Approach}}. {OUP Oxford}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Belleggia2017}{}}%
-Belleggia, M., Giberto, D., \& Bremec, C. (2017). Adaptation of diet in
-a changed environment: {Increased} consumption of lobster krill {Munida}
-gregaria ({Fabricius}, 1793) by {Argentine} hake. \emph{Marine Ecology},
-\emph{38}(4), e12445.
-doi:\href{https://doi.org/10.1111/maec.12445}{10.1111/maec.12445}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bers2013}{}}%
-Bers, A. V., Momo, F., Schloss, I. R., \& Abele, D. (2013). Analysis of
-trends and sudden changes in long-term environmental data from {King
-George Island} ({Antarctica}): Relationships between global climatic
-oscillations and local system response. \emph{Climatic Change},
-\emph{116}(3), 789--803.
-doi:\href{https://doi.org/10.1007/s10584-012-0523-4}{10.1007/s10584-012-0523-4}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bogazzi2005}{}}%
-Bogazzi, E., Baldoni, A., Rivas, A., Martos, P., Reta, R., Orensanz, J.
-M. (lobo)., \ldots{} Werner, F. (2005). Spatial correspondence between
-areas of concentration of {Patagonian} scallop ({Zygochlamys}
-patagonica) and frontal systems in the southwestern {Atlantic}.
-\emph{Fisheries Oceanography}, \emph{14}(5), 359--376.
-doi:\href{https://doi.org/10.1111/j.1365-2419.2005.00340.x}{10.1111/j.1365-2419.2005.00340.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bovcon2013}{}}%
-Bovcon, N. D., Góngora, M. E., Marinao, C., \& González-Zevallos, D.
-(2013). Composición de las capturas y descartes generados en la pesca de
-merluza común {Merluccius} hubbsi y langostino patagónico {Pleoticus}
-muelleri: Un caso de estudio en la flota fresquera de altura del {Golfo
-San Jorge}, {Chubut}, {Argentina}. \emph{Revista de Biología Marina y
-Oceanografía}, \emph{48}(2), 303--319.
-doi:\href{https://doi.org/10.4067/S0718-19572013000200010}{10.4067/S0718-19572013000200010}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Boyd2015}{}}%
-Boyd, P. W., Lennartz, S. T., Glover, D. M., \& Doney, S. C. (2015).
-Biological ramifications of climate-change-mediated oceanic
-multi-stressors. \emph{Nature Climate Change}, \emph{5}(1), 71--79.
-doi:\href{https://doi.org/10.1038/nclimate2441}{10.1038/nclimate2441}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Braeckman2021}{}}%
-Braeckman, U., Pasotti, F., Hoffmann, R., Vázquez, S., Wulff, A.,
-Schloss, I. R., \ldots{} Vanreusel, A. (2021). Glacial melt disturbance
-shifts community metabolism of an {Antarctic} seafloor ecosystem from
-net autotrophy to heterotrophy. \emph{Communications Biology},
-\emph{4}(1), 148.
-doi:\href{https://doi.org/10.1038/s42003-021-01673-6}{10.1038/s42003-021-01673-6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Braithwaite2015}{}}%
+\bibitem[\citeproctext]{ref-Braithwaite2015}
 Braithwaite, J. E., Meeuwig, J. J., Letessier, T. B., Jenner, K. C. S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Brown2004}{}}%
-Brown, J. H., Gillooly, J. F., Allen, A. P., Savage, V. M., \& West, G.
-B. (2004). Toward a {Metabolic Theory} of {Ecology}. \emph{Ecology},
-\emph{85}(7), 1771--1789.
-doi:\href{https://doi.org/10.1890/03-9000}{10.1890/03-9000}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bruder2019}{}}%
-Bruder, A., Frainer, A., Rota, T., \& Primicerio, R. (2019). The
-{Importance} of {Ecological Networks} in {Multiple-Stressor Research}
-and {Management}. \emph{Frontiers in Environmental Science}, \emph{7}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bruno2023}{}}%
-Bruno, D. O., Riccialdelli, L., Acha, E. M., \& Fernández, D. A. (2023).
-Seasonal variation of autochthonous and allochthonous carbon sources for
-the first levels of the {Beagle Channel} food web. \emph{Journal of
-Marine Systems}, \emph{239}, 103859.
-doi:\href{https://doi.org/10.1016/j.jmarsys.2023.103859}{10.1016/j.jmarsys.2023.103859}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Buskey2016}{}}%
+\bibitem[\citeproctext]{ref-Buskey2016}
 Buskey, E. J., White, H. K., \& Esbaugh, A. J. (2016). Impact of {Oil
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Campana2018}{}}%
+\bibitem[\citeproctext]{ref-Campana2018}
 Campana, G. L., Zacher, K., Deregibus, D., Momo, F. R., Wiencke, C., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Chown2022}{}}%
-Chown, S. L., Leihy, R. I., Naish, T. R., Brooks, C. M., Convey, P.,
-Henley, B. J., \ldots{} Grant, S. M. (2022). Antarctic climate change
-and the environment: A decadal synopsis and recommendations for action.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ciancio2008}{}}%
+\bibitem[\citeproctext]{ref-Ciancio2008}
 Ciancio, J. E., Pascual, M. A., Botto, F., Frere, E., \& Iribarne, O.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ciancio2010}{}}%
+\bibitem[\citeproctext]{ref-Ciancio2010}
 Ciancio, J., Beauchamp, D. A., \& Pascual, M. (2010). Marine effect of
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cirtwill2015}{}}%
-Cirtwill, A. R., Stouffer, D. B., \& Romanuk, T. N. (2015). Latitudinal
-gradients in biotic niche breadth vary across ecosystem types.
-\emph{Proceedings of the Royal Society B: Biological Sciences},
-\emph{282}(1819), 20151589.
-doi:\href{https://doi.org/10.1098/rspb.2015.1589}{10.1098/rspb.2015.1589}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Clark2013}{}}%
+\bibitem[\citeproctext]{ref-Clark2013}
 Clark, G. F., Stark, J. S., Johnston, E. L., Runcie, J. W., Goldsworthy,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Collins2010}{}}%
-Collins, M. A., Brickle, P., Brown, J., \& Belchier, M. (2010). Chapter
-{Four} - {The Patagonian Toothfish}: {Biology}, {Ecology} and {Fishery}.
-In M. Lesser (Ed.), \emph{Advances in {Marine Biology}} (Vol. 58, pp.
-227--300). {Academic Press}.
-doi:\href{https://doi.org/10.1016/B978-0-12-381015-1.00004-6}{10.1016/B978-0-12-381015-1.00004-6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Commendatore2012}{}}%
-Commendatore, M. G., Nievas, M. L., Amin, O., \& Esteves, J. L. (2012).
-Sources and distribution of aliphatic and polyaromatic hydrocarbons in
-coastal sediments from the {Ushuaia Bay} ({Tierra} del {Fuego},
-{Patagonia}, {Argentina}). \emph{Marine Environmental Research},
-\emph{74}, 20--31.
-doi:\href{https://doi.org/10.1016/j.marenvres.2011.11.010}{10.1016/j.marenvres.2011.11.010}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Constable2014}{}}%
+\bibitem[\citeproctext]{ref-Constable2014}
 Constable, A. J., Melbourne-Thomas, J., Corney, S. P., Arrigo, K. R.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cordone2023}{}}%
-Cordone, G., Galván, D. E., \& Momo, F. R. (2023). Impacts of an
-invasion by green crab {Carcinus} maenas on the intertidal food web of a
-{Patagonian} rocky shore, {Argentina}. \emph{Marine Ecology Progress
-Series}, \emph{713}, 97--115.
-doi:\href{https://doi.org/10.3354/meps14336}{10.3354/meps14336}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Cordone2020}{}}%
-Cordone, G., Salinas, V., Marina, T. I., Doyle, S. R., Pasotti, F.,
-Saravia, L. A., \& Momo, F. R. (2020). Green vs brown food web:
-{Effects} of habitat type on multidimensional stability proxies for a
-highly-resolved {Antarctic} food web. \emph{Food Webs}, \emph{25},
-e00166.
-doi:\href{https://doi.org/10.1016/j.fooweb.2020.e00166}{10.1016/j.fooweb.2020.e00166}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Correa2008}{}}%
-Correa, C., \& Gross, M. R. (2008). Chinook salmon invade southern
-{South America}. \emph{Biological Invasions}, \emph{10}(5), 615--639.
-doi:\href{https://doi.org/10.1007/s10530-007-9157-2}{10.1007/s10530-007-9157-2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Cossi2021}{}}%
+\bibitem[\citeproctext]{ref-Cossi2021}
 Cossi, P. F., Ojeda, M., Chiesa, I. L., Rimondino, G. N., Fraysse, C.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cote2016}{}}%
-Côté, I. M., Darling, E. S., \& Brown, C. J. (2016). Interactions among
-ecosystem stressors and their importance in conservation.
-\emph{Proceedings of the Royal Society B: Biological Sciences},
-\emph{283}(1824), 20152592.
-doi:\href{https://doi.org/10.1098/rspb.2015.2592}{10.1098/rspb.2015.2592}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Crain2008}{}}%
-Crain, C. M., Kroeker, K., \& Halpern, B. S. (2008). Interactive and
-cumulative effects of multiple human stressors in marine systems.
-\emph{Ecology Letters}, \emph{11}(12), 1304--1315.
-doi:\href{https://doi.org/10.1111/j.1461-0248.2008.01253.x}{10.1111/j.1461-0248.2008.01253.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-DAlelio2016}{}}%
-D'Alelio, D., Libralato, S., Wyatt, T., \& Ribera d'Alcalà, M. (2016).
-Ecological-network models link diversity, structure and function in the
-plankton food-web. \emph{Scientific Reports}, \emph{6}(1), 21806.
-doi:\href{https://doi.org/10.1038/srep21806}{10.1038/srep21806}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dayton1990}{}}%
-Dayton, P. K. (1990). Polar {Benthos}. In \emph{Polar {Oceanography Part
-B}: {Chemistry}, {Biology} and {Geology}} (W.O. Smith, Jr., pp.
-631--685). {London}: {Academic Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-deHaro2022}{}}%
-de Haro, J. C., Perez Orsi, H., Cané, S., Di Pangracio, A., Falabella,
-V., \& Sapoznikow, A. (2022). {Informe colaborativo sobre el Estado de
-situación. Riesgos e impactos de la prospección sísmica en el Mar
-Argentino}. {Foro para la Conservación del Mar Patagónico y Áreas de
-Influencia}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Deppeler2020}{}}%
+\bibitem[\citeproctext]{ref-Deppeler2020}
 Deppeler, S., Schulz, K. G., Hancock, A., Pascoe, P., McKinlay, J., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2023}{}}%
+\bibitem[\citeproctext]{ref-Deregibus2023}
 Deregibus, Dolores, Campana, G. L., Neder, C., Barnes, D. K. A., Zacher,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2016}{}}%
+\bibitem[\citeproctext]{ref-Deregibus2016}
 Deregibus, D., Quartino, M. L., Campana, G. L., Momo, F. R., Wiencke,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2017}{}}%
+\bibitem[\citeproctext]{ref-Deregibus2017}
 Deregibus, D., Quartino, M. L., Zacher, K., Campana, G. L., \& Barnes,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2020}{}}%
-Deregibus, Dolores, Zacher, K., Bartsch, I., Campana, G. L., Momo, F.
-R., Wiencke, C., \ldots{} Quartino, M. L. (2020). Carbon {Balance Under}
-a {Changing Light Environment}. In I. Gómez \& P. Huovinen (Eds.),
-\emph{Antarctic {Seaweeds}: {Diversity}, {Adaptation} and {Ecosystem
-Services}} (pp. 173--191). {Cham}: {Springer International Publishing}.
-doi:\href{https://doi.org/10.1007/978-3-030-39448-6_9}{10.1007/978-3-030-39448-6\_9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-DiMauro2022}{}}%
-Di Mauro, R., Castillo, S., Pérez, A., Iachetti, C. M., Silva, L.,
-Tomba, J. P., \& Chiesa, I. L. (2022). Anthropogenic microfibers are
-highly abundant at the {Burdwood Bank} seamount, a protected
-sub-{Antarctic} environment in the {Southwestern Atlantic Ocean}.
-\emph{Environmental Pollution}, \emph{306}, 119364.
-doi:\href{https://doi.org/10.1016/j.envpol.2022.119364}{10.1016/j.envpol.2022.119364}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dinniman2023}{}}%
-Dinniman, M. S., St-Laurent, P., Arrigo, K. R., Hofmann, E. E., \& van
-Dijken, G. L. (2023). Sensitivity of the {Relationship Between Antarctic
-Ice Shelves} and {Iron Supply} to {Projected Changes} in the
-{Atmospheric Forcing}. \emph{Journal of Geophysical Research: Oceans},
-\emph{128}(2), e2022JC019210.
-doi:\href{https://doi.org/10.1029/2022JC019210}{10.1029/2022JC019210}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dodino2022}{}}%
-Dodino, S., Riccialdelli, L., Polito, M. J., Pütz, K., Brasso, R. L., \&
-Raya Rey, A. (2022). Mercury exposure driven by geographic and trophic
-factors in {Magellanic} penguins from {Tierra} del {Fuego}. \emph{Marine
-Pollution Bulletin}, \emph{174}, 113184.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2021.113184}{10.1016/j.marpolbul.2021.113184}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Duarte2011}{}}%
-Duarte, C. A., Giarratano, E., Amin, O. A., \& Comoglio, L. I. (2011).
-Heavy metal concentrations and biomarkers of oxidative stress in native
-mussels ({Mytilus} edulis chilensis) from {Beagle Channel} coast
-({Tierra} del {Fuego}, {Argentina}). \emph{Marine Pollution Bulletin},
-\emph{62}(8), 1895--1904.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2011.05.031}{10.1016/j.marpolbul.2011.05.031}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Duffy2007}{}}%
-Duffy, J. E., Cardinale, B. J., France, K. E., McIntyre, P. B.,
-Thébault, E., \& Loreau, M. (2007). The functional role of biodiversity
-in ecosystems: Incorporating trophic complexity. \emph{Ecology Letters},
-\emph{10}(6), 522--538.
-doi:\href{https://doi.org/10.1111/j.1461-0248.2007.01037.x}{10.1111/j.1461-0248.2007.01037.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dulvy2014}{}}%
-Dulvy, N. K., Fowler, S. L., Musick, J. A., Cavanagh, R. D., Kyne, P.
-M., Harrison, L. R., \ldots{} White, W. T. (2014). Extinction risk and
-conservation of the world's sharks and rays. \emph{eLife}, \emph{3},
-e00590.
-doi:\href{https://doi.org/10.7554/eLife.00590}{10.7554/eLife.00590}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002a}{}}%
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Food-web
-structure and network theory: {The} role of connectance and size.
-\emph{Proceedings of the National Academy of Sciences}, \emph{99}(20),
-12917--12922.
-doi:\href{https://doi.org/10.1073/pnas.192407699}{10.1073/pnas.192407699}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). Network
-structure and biodiversity loss in food webs: Robustness increases with
-connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
-doi:\href{https://doi.org/10.1046/j.1461-0248.2002.00354.x}{10.1046/j.1461-0248.2002.00354.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fernandez2010}{}}%
+\bibitem[\citeproctext]{ref-Fernandez2010}
 Fernández, D. A., Ciancio, J., Ceballos, S. G., Riva-Rossi, C., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ferreira2021}{}}%
+\bibitem[\citeproctext]{ref-Ferreira2021}
 Ferreira, M. F., Lo Nostro, F. L., Fernández, D. A., \& Genovese, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Fioramonti2022}{}}%
+\bibitem[\citeproctext]{ref-Fioramonti2022}
 Fioramonti, N. E., Ribeiro Guevara, S., Becker, Y. A., \& Riccialdelli,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Flores2012}{}}%
+\bibitem[\citeproctext]{ref-Flores2012}
 Flores, H., Atkinson, A., Kawaguchi, S., Krafft, B., Milinevsky, G.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Franco2020}{}}%
-Franco, B. C., Combes, V., \& González Carman, V. (2020). Subsurface
-{Ocean Warming Hotspots} and {Potential Impacts} on {Marine Species}:
-{The Southwest South Atlantic Ocean Case Study}. \emph{Frontiers in
-Marine Science}, \emph{7}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Frelat2022}{}}%
-Frelat, R., Kortsch, S., Kröncke, I., Neumann, H., Nordström, M. C.,
-Olivier, P. E. N., \& Sell, A. F. (2022). Food web structure and
-community composition: A comparison across space and time in the {North
-Sea}. \emph{Ecography}, \emph{2022}(2), ecog.05945.
-doi:\href{https://doi.org/10.1111/ecog.05945}{10.1111/ecog.05945}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fretwell2023}{}}%
-Fretwell, P. T., Boutet, A., \& Ratcliffe, N. (2023). Record low 2022
-{Antarctic} sea ice led to catastrophic breeding failure of emperor
-penguins. \emph{Communications Earth \& Environment}, \emph{4}(1), 1--6.
-doi:\href{https://doi.org/10.1038/s43247-023-00927-x}{10.1038/s43247-023-00927-x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fuentes2016}{}}%
+\bibitem[\citeproctext]{ref-Fuentes2016}
 Fuentes, V., Alurralde, G., Meyer, B., Aguirre, G. E., Canepa, A.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Funes2020}{}}%
-Funes, M. (2020, March). \emph{Efectos de la pesca de arrastre sobre la
-estructura trófica del norte del {Golfo San Jorge}} (PhD thesis).
-
-\leavevmode\vadjust pre{\hypertarget{ref-Funes2019}{}}%
-Funes, M., Marinao, C., \& Galván, D. E. (2019). Does trawl fisheries
-affect the diet of fishes? {A} stable isotope analysis approach*.
-\emph{Isotopes in Environmental and Health Studies}, \emph{55}(4),
-327--343.
-doi:\href{https://doi.org/10.1080/10256016.2019.1626381}{10.1080/10256016.2019.1626381}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Funes2022}{}}%
-Funes, M., Saravia, L. A., Cordone, G., Iribarne, O. O., \& Galván, D.
-E. (2022). Network analysis suggests changes in food web stability
-produced by bottom trawl fishery in {Patagonia}. \emph{Scientific
-Reports}, \emph{12}(1), 10876.
-doi:\href{https://doi.org/10.1038/s41598-022-14363-y}{10.1038/s41598-022-14363-y}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gaitan2016}{}}%
+\bibitem[\citeproctext]{ref-Gaitan2016}
 Gaitán, E., \& Marí, N. (2016). {Análisis de las comunidades bentónicas
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Galvan2022}{}}%
+\bibitem[\citeproctext]{ref-Galvan2022}
 Galván, D. E., Bovcon, N. D., Cochia, P. D., González, R. A., Lattuca,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Garcia2019}{}}%
+\bibitem[\citeproctext]{ref-Garcia2019}
 Garcia, M. D., Fernández Severini, M. D., Spetter, C., López Abbate, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Garcia2016}{}}%
+\bibitem[\citeproctext]{ref-Garcia2016}
 Garcia, M. D., Hoffmeyer, M. S., Abbate, M. C. L., Barría De Cao, M. S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Garcia-Borboroglu2008}{}}%
-García-Borboroglu, P., Boersma, P. D., Reyes, L., \& Skewgar, E. (2008).
-Petroleum {Pollution} and {Penguins}: {Marine Conservation Tools} to
-{Reduce} the {Problem}. In \emph{Marine {Pollution}: {New} research}
-(Hofer, T.N., pp. 339--356). {New York, USA}: {Nova Science Publishers
-Inc.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Garrott1993}{}}%
-Garrott, R. A., Eberhardt, L. L., \& Burn, D. M. (1993). Mortality of
-{Sea Otters} in {Prince William Sound Following} the {Exxon Valdez Oil
-Spill}. \emph{Marine Mammal Science}, \emph{9}(4), 343--359.
-doi:\href{https://doi.org/10.1111/j.1748-7692.1993.tb00468.x}{10.1111/j.1748-7692.1993.tb00468.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gauzens2019}{}}%
-Gauzens, B., Barnes, A., Giling, D. P., Hines, J., Jochum, M., Lefcheck,
-J. S., \ldots{} Brose, U. (2019). Fluxweb: {An R} package to easily
-estimate energy fluxes in food webs. \emph{Methods in Ecology and
-Evolution}, \emph{10}(2), 270--279.
-doi:\href{https://doi.org/10.1111/2041-210X.13109}{10.1111/2041-210X.13109}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gellner2023}{}}%
-Gellner, G., McCann, K., \& Hastings, A. (2023). Stable diverse food
-webs become more common when interactions are more biologically
-constrained. \emph{Proceedings of the National Academy of Sciences},
-\emph{120}(31), e2212061120.
-doi:\href{https://doi.org/10.1073/pnas.2212061120}{10.1073/pnas.2212061120}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Giarratano2010}{}}%
+\bibitem[\citeproctext]{ref-Giarratano2010}
 Giarratano, E., \& Amin, O. A. (2010). Heavy metals monitoring in the
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gil2011}{}}%
-Gil, M. N., Torres, A. I., Amin, O., \& Esteves, J. L. (2011).
-Assessment of recent sediment influence in an urban polluted
-subantarctic coastal ecosystem. {Beagle Channel} ({Southern Argentina}).
-\emph{Marine Pollution Bulletin}, \emph{62}(1), 201--207.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2010.10.004}{10.1016/j.marpolbul.2010.10.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Glembocki2015}{}}%
-Glembocki, N. G., Williams, G. N., Góngora, M. E., Gagliardini, D. A.,
-\& Orensanz, J. M. (Lobo). (2015). Synoptic oceanography of {San Jorge
-Gulf} ({Argentina}): {A} template for {Patagonian} red shrimp
-({Pleoticus} muelleri) spatial dynamics. \emph{Journal of Sea Research},
-\emph{95}, 22--35.
-doi:\href{https://doi.org/10.1016/j.seares.2014.10.011}{10.1016/j.seares.2014.10.011}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Glorioso1995}{}}%
-Glorioso, P. D., \& Flather, R. A. (1995). A barotropic model of the
-currents off {SE South America}. \emph{Journal of Geophysical Research:
-Oceans}, \emph{100}(C7), 13427--13440.
-doi:\href{https://doi.org/10.1029/95JC00942}{10.1029/95JC00942}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gongora2009}{}}%
-Góngora, María E., Bovcon, N. D., \& Cochia, P. D. (2009). Ictiofauna
-capturada incidentalmente en la pesquería de langostino patagónico
-{Pleoticus} muelleri {Bate}, 1888. \emph{Revista de Biología Marina y
-Oceanografía}, \emph{44}(3), 583--593.
-doi:\href{https://doi.org/10.4067/S0718-19572009000300006}{10.4067/S0718-19572009000300006}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gongora2012}{}}%
-Góngora, María Eva, González-Zevallos, D., Pettovello, A., \& Mendía, L.
-(2012). Caracterización de las principales pesquerías del golfo {San
-Jorge Patagonia}, {Argentina}. \emph{Latin American Journal of Aquatic
-Research}, \emph{40}(1), 1--11.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gonzalez-Zevallos2006}{}}%
+\bibitem[\citeproctext]{ref-Gonzalez-Zevallos2006}
 González-Zevallos, D., \& Yorio, P. (2006). Seabird use of discards and
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gonzalez-Zevallos2011}{}}%
+\bibitem[\citeproctext]{ref-Gonzalez-Zevallos2011}
 González-Zevallos, D., \& Yorio, P. (2011). Consumption of discards and
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gorini2021}{}}%
-Gorini, F. L., Lukaszewicz, G., \& Giussi, A. R. (2021).
-\emph{{Actualización de la estadística pesquera de peces demersales
-australes en el Atlántico Sudoccidental (período 2008-2020)}} (\{Informe
-T\textbackslash\textquotesingle ecnico Oficial\}) (p. 64). {Mar del
-Plata}: {Instituto Nacional de Investigación y Desarrollo Pesquero
-(INIDEP)}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Guihou2020}{}}%
-Guihou, K., Piola, A. R., Palma, E. D., \& Chidichimo, M. P. (2020).
-Dynamical connections between large marine ecosystems of austral {South
-America} based on numerical simulations. \emph{Ocean Science},
-\emph{16}(2), 271--290.
-doi:\href{https://doi.org/10.5194/os-16-271-2020}{10.5194/os-16-271-2020}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt2001a}{}}%
+\bibitem[\citeproctext]{ref-Gutt2001a}
 Gutt, Julian. (2001). On the direct impact of ice on marine benthic
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt2015}{}}%
+\bibitem[\citeproctext]{ref-Gutt2015}
 Gutt, Julian, Bertler, N., Bracegirdle, T. J., Buschmann, A., Comiso,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt2021}{}}%
-Gutt, Julian, Isla, E., Xavier, J. C., Adams, B. J., Ahn, I.-Y., Cheng,
-C.-H. C., \ldots{} Wall, D. H. (2021). Antarctic ecosystems in
-transition \textendash{} life between stresses and opportunities.
-\emph{Biological Reviews}, \emph{96}(3), 798--821.
-doi:\href{https://doi.org/10.1111/brv.12679}{10.1111/brv.12679}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt2003}{}}%
+\bibitem[\citeproctext]{ref-Gutt2003}
 Gutt, Julian, \& Piepenburg, D. (2003). Scale-dependent impact on
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt2001}{}}%
+\bibitem[\citeproctext]{ref-Gutt2001}
 Gutt, Julian, \& Starmans, A. (2001). Quantification of iceberg impact
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt1996}{}}%
+\bibitem[\citeproctext]{ref-Gutt1996}
 Gutt, J., Starmans, A., \& Dieckmann, G. (1996). Impact of iceberg
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hendry2018}{}}%
-Hendry, K. R., Meredith, M. P., \& Ducklow, H. W. (2018). The marine
-system of the {West Antarctic Peninsula}: Status and strategy for
-progress. \emph{Philosophical Transactions of the Royal Society A:
-Mathematical, Physical and Engineering Sciences}, \emph{376}(2122),
-20170179.
-doi:\href{https://doi.org/10.1098/rsta.2017.0179}{10.1098/rsta.2017.0179}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hernandez2019}{}}%
-Hernández, E. A., Lopez, J. L., Piquet, A. M.-T., Mac Cormack, W. P., \&
-Buma, A. G. J. (2019). Changes in salinity and temperature drive marine
-bacterial communities' structure at {Potter Cove}, {Antarctica}.
-\emph{Polar Biology}, \emph{42}(12), 2177--2191.
-doi:\href{https://doi.org/10.1007/s00300-019-02590-5}{10.1007/s00300-019-02590-5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hilborn2017}{}}%
-Hilborn, R., Amoroso, R. O., Bogazzi, E., Jensen, O. P., Parma, A. M.,
-Szuwalski, C., \& Walters, C. J. (2017). When does fishing forage
-species affect their predators? \emph{Fisheries Research}, \emph{191},
-211--221.
-doi:\href{https://doi.org/10.1016/j.fishres.2017.01.008}{10.1016/j.fishres.2017.01.008}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hill2012}{}}%
-Hill, S. L., Keeble, K., Atkinson, A., \& Murphy, E. J. (2012). A
-foodweb model to explore uncertainties in the {South Georgia} shelf
-pelagic ecosystem. \emph{Deep Sea Research Part II: Topical Studies in
-Oceanography}, \emph{59--60}, 237--252.
-doi:\href{https://doi.org/10.1016/j.dsr2.2011.09.001}{10.1016/j.dsr2.2011.09.001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hill2013}{}}%
+\bibitem[\citeproctext]{ref-Hill2013}
 Hill, S. L., Phillips, T., \& Atkinson, A. (2013). Potential {Climate
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hindell2020}{}}%
-Hindell, M. A., Reisinger, R. R., Ropert-Coudert, Y., Hückstädt, L. A.,
-Trathan, P. N., Bornemann, H., \ldots{} Raymond, B. (2020). Tracking of
-marine predators to protect {Southern Ocean} ecosystems. \emph{Nature},
-\emph{580}(7801), 87--92.
-doi:\href{https://doi.org/10.1038/s41586-020-2126-y}{10.1038/s41586-020-2126-y}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hoffmann2019}{}}%
+\bibitem[\citeproctext]{ref-Hoffmann2019}
 Hoffmann, R., Al-Handal, A. Y., Wulff, A., Deregibus, D., Zacher, K.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Iken2023}{}}%
-Iken, K., Amsler, C. D., Gorman, K. B., Klein, A. G., Galloway, A. W.
-E., Amsler, M. O., \ldots{} McClintock, J. B. (2023). Macroalgal input
-into the coastal food web along a gradient of seasonal sea ice cover
-along the {Western Antarctic Peninsula}. \emph{Marine Ecology Progress
-Series}, \emph{718}, 1--22.
-doi:\href{https://doi.org/10.3354/meps14388}{10.3354/meps14388}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Irons2000}{}}%
-Irons, D. B., Kendall, S. J., Erickson, W. P., McDonald, L. L., \&
-Lance, B. K. (2000). Nine {Years After} the {Exxon Valdez Oil Spill}:
-{Effects} on {Marine Bird Populations} in {Prince William Sound},
-{Alaska}. \emph{The Condor}, \emph{102}(4), 723--737.
-doi:\href{https://doi.org/10.1093/condor/102.4.723}{10.1093/condor/102.4.723}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Isla2023}{}}%
+\bibitem[\citeproctext]{ref-Isla2023}
 Isla, E. (2023). Animal\textendash{{Energy Relationships}} in a
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Jacob2011}{}}%
-Jacob, U., Thierry, A., Brose, U., Arntz, W. E., Berg, S., Brey, T.,
-\ldots{} Dunne, J. A. (2011). The {Role} of {Body Size} in {Complex Food
-Webs}: {A Cold Case}. In A. Belgrano (Ed.), \emph{Advances in
-{Ecological Research}} (Vol. 45, pp. 181--223). {Academic Press}.
-doi:\href{https://doi.org/10.1016/B978-0-12-386475-8.00005-8}{10.1016/B978-0-12-386475-8.00005-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jerosch2018}{}}%
-Jerosch, K., Pehlke, H., Monien, P., Scharf, F., Weber, L., Kuhn, G.,
-\ldots{} Abele, D. (2018). Benthic meltwater fjord habitats formed by
-rapid glacier recession on {King George Island}, {Antarctica}.
-\emph{Philosophical Transactions of the Royal Society A: Mathematical,
-Physical and Engineering Sciences}, \emph{376}(2122), 20170178.
-doi:\href{https://doi.org/10.1098/rsta.2017.0178}{10.1098/rsta.2017.0178}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jordan2007}{}}%
-Jordán, F., Benedek, Z., \& Podani, J. (2007). Quantifying positional
-importance in food webs: {A} comparison of centrality indices.
-\emph{Ecological Modelling}, \emph{205}(1), 270--275.
-doi:\href{https://doi.org/10.1016/j.ecolmodel.2007.02.032}{10.1016/j.ecolmodel.2007.02.032}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kaminskyinprep}{}}%
+\bibitem[\citeproctext]{ref-Kaminskyinprep}
 Kaminsky, J., Bagur, M., Boraso, A., Schloss, I. R., Buschmann, A. H.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kawaguchi2013}{}}%
+\bibitem[\citeproctext]{ref-Kawaguchi2013}
 Kawaguchi, S., Ishida, A., King, R., Raymond, B., Waller, N., Constable,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kawaguchi2010}{}}%
+\bibitem[\citeproctext]{ref-Kawaguchi2010}
 Kawaguchi, So, Kurihara, H., King, R., Hale, L., Berli, T., Robinson, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kawaguchi2009}{}}%
-Kawaguchi, So, Nicol, S., \& Press, A. (2009). Direct effects of climate
-change on the {Antarctic} krill fishery.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Klein2018}{}}%
-Klein, E. S., Hill, S. L., Hinke, J. T., Phillips, T., \& Watters, G. M.
-(2018). Impacts of rising sea temperature on krill increase risks for
-predators in the {Scotia Sea}. \emph{PLOS ONE}, \emph{13}(1), e0191011.
-doi:\href{https://doi.org/10.1371/journal.pone.0191011}{10.1371/journal.pone.0191011}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2019}{}}%
-Kortsch, S., Primicerio, R., Aschan, M., Lind, S., Dolgov, A. V., \&
-Planque, B. (2019). Food-web structure varies along environmental
-gradients in a high-latitude marine ecosystem. \emph{Ecography},
-\emph{42}(2), 295--308.
-doi:\href{https://doi.org/10.1111/ecog.03443}{10.1111/ecog.03443}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2015}{}}%
-Kortsch, S., Primicerio, R., Fossheim, M., Dolgov, A. V., \& Aschan, M.
-(2015). Climate change alters the structure of arctic marine food webs
-due to poleward shifts of boreal generalists. \emph{Proceedings of the
-Royal Society B: Biological Sciences}, \emph{282}(1814), 20151546.
-doi:\href{https://doi.org/10.1098/rspb.2015.1546}{10.1098/rspb.2015.1546}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kratina2012}{}}%
-Kratina, P., LeCraw, R. M., Ingram, T., \& Anholt, B. R. (2012).
-Stability and persistence of food webs with omnivory: {Is} there a
-general pattern? \emph{Ecosphere}, \emph{3}(6), art50.
-doi:\href{https://doi.org/10.1890/ES12-00121.1}{10.1890/ES12-00121.1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lagger2018}{}}%
+\bibitem[\citeproctext]{ref-Lagger2018}
 Lagger, C., Nime, M., Torre, L., Servetto, N., Tatián, M., \& Sahade, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lagger2017}{}}%
+\bibitem[\citeproctext]{ref-Lagger2017}
 Lagger, C., Servetto, N., Torre, L., \& Sahade, R. (2017). Benthic
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Latorre2023}{}}%
+\bibitem[\citeproctext]{ref-Latorre2023}
 Latorre, M. P., Iachetti, C. M., Schloss, I. R., Antoni, J., Malits, A.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lattuca2018}{}}%
-Lattuca, María Eugenia, Boy, C. C., Vanella, F. A., Barrantes, M. E., \&
-Fernández, D. A. (2018). Thermal responses of three native fishes from
-estuarine areas of the {Beagle Channel}, and their implications for
-climate change. \emph{Hydrobiologia}, \emph{808}(1), 235--249.
-doi:\href{https://doi.org/10.1007/s10750-017-3424-8}{10.1007/s10750-017-3424-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lattuca2023}{}}%
-Lattuca, María E., Vanella, F. A., Malanga, G., Rubel, M. D., Manríquez,
-P. H., Torres, R., \ldots{} Fernández, D. A. (2023). Ocean acidification
-and seasonal temperature extremes combine to impair the thermal
-physiology of a sub-{Antarctic} fish. \emph{Science of The Total
-Environment}, \emph{856}, 159284.
-doi:\href{https://doi.org/10.1016/j.scitotenv.2022.159284}{10.1016/j.scitotenv.2022.159284}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lin2021}{}}%
-Lin, Y., Moreno, C., Marchetti, A., Ducklow, H., Schofield, O., Delage,
-E., \ldots{} Cassar, N. (2021). Decline in plankton diversity and carbon
-flux with reduced sea ice extent along the {Western Antarctic
-Peninsula}. \emph{Nature Communications}, \emph{12}(1), 4948.
-doi:\href{https://doi.org/10.1038/s41467-021-25235-w}{10.1038/s41467-021-25235-w}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Llorca2012}{}}%
-Llorca, M., Farré, M., Tavano, M. S., Alonso, B., Koremblit, G., \&
-Barceló, D. (2012). Fate of a broad spectrum of perfluorinated compounds
-in soils and biota from {Tierra} del {Fuego} and {Antarctica}.
-\emph{Environmental Pollution}, \emph{163}, 158--166.
-doi:\href{https://doi.org/10.1016/j.envpol.2011.10.027}{10.1016/j.envpol.2011.10.027}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lopez-Gappa2022}{}}%
-López-Gappa, J. (2022). The {Impact} of {Global Change} on {Marine
-Benthic Invertebrates}. In E. W. Helbling, M. A. Narvarte, R. A.
-González, \& V. E. Villafañe (Eds.), \emph{Global {Change} in {Atlantic
-Coastal Patagonian Ecosystems}: {A Journey Through Time}} (pp.
-177--204). {Cham}: {Springer International Publishing}.
-doi:\href{https://doi.org/10.1007/978-3-030-86676-1_8}{10.1007/978-3-030-86676-1\_8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lopez-Lopez2022}{}}%
-López-López, L., Genner, M. J., Tarling, G. A., Saunders, R. A., \&
-O'Gorman, E. J. (2022). Ecological {Networks} in the {Scotia Sea}:
-{Structural Changes Across Latitude} and {Depth}. \emph{Ecosystems},
-\emph{25}(2), 457--470.
-doi:\href{https://doi.org/10.1007/s10021-021-00665-1}{10.1007/s10021-021-00665-1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Manno2022}{}}%
+\bibitem[\citeproctext]{ref-Manno2022}
 Manno, C., Peck, V. L., Corsi, I., \& Bergami, E. (2022). Under
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Marina2018}{}}%
-Marina, T. I., Salinas, V., Cordone, G., Campana, G., Moreira, E.,
-Deregibus, D., \ldots{} Momo, F. R. (2018). The {Food Web} of {Potter
-Cove} ({Antarctica}): Complexity, structure and function.
-\emph{Estuarine, Coastal and Shelf Science}, \emph{200}, 141--151.
-doi:\href{https://doi.org/10.1016/j.ecss.2017.10.015}{10.1016/j.ecss.2017.10.015}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Marinainrev}{}}%
-Marina, T. I., Schloss, I. R., Lovrich, G. A., Boy, C. C., Bruno, D. O.,
-Capitanio, F. L., \ldots{} Riccialdelli, L. (in rev.). The complex
-network of trophic interactions in a {Subantarctic} oceanic {Marine
-Protected Area}. \emph{Marine Ecology Progress Series}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Martinez2022}{}}%
-Martínez, Patricia A., Wöhler, O. C., Troccoli, G. H., Di Marco, E., \&
+\bibitem[\citeproctext]{ref-Martinez2022}
+Martínez, P. A., Wöhler, O. C., Troccoli, G. H., Di Marco, E., \&
 Maydana, L. (2022). \emph{{Descripción de las capturas incidentales de
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martinez2015}{}}%
-Martínez, P. A., Wöhler, O. G., \& Troccoli, G. H. (2015). \emph{{La
-evolución de la pesquería de merluza negra (Dissostichus eleginoides) en
-el espacio marítimo argentino. Periodo 2003- 2014}} (\{Technical
-report\} No. 11/15) (p. 12). {Instituto Nacional de Investigación y
-Desarrollo Pesquero (INIDEP), Argentina}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Matano2019}{}}%
-Matano, Ricardo P., Palma, E. D., \& Combes, V. (2019). The {Burdwood
-Bank Circulation}. \emph{Journal of Geophysical Research: Oceans},
-\emph{124}(10), 6904--6926.
-doi:\href{https://doi.org/10.1029/2019JC015001}{10.1029/2019JC015001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Matano2010}{}}%
-Matano, R. P., Palma, E. D., \& Piola, A. R. (2010). The influence of
-the {Brazil} and {Malvinas Currents} on the {Southwestern Atlantic
-Shelf} circulation. \emph{Ocean Science}, \emph{6}(4), 983--995.
-doi:\href{https://doi.org/10.5194/os-6-983-2010}{10.5194/os-6-983-2010}
-
-\leavevmode\vadjust pre{\hypertarget{ref-McCann1998}{}}%
-McCann, K., Hastings, A., \& Huxel, G. R. (1998). Weak trophic
-interactions and the balance of nature. \emph{Nature}, \emph{395}(6704),
-794--798. doi:\href{https://doi.org/10.1038/27427}{10.1038/27427}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Menge1995}{}}%
-Menge, B. A. (1995). Indirect {Effects} in {Marine Rocky Intertidal
-Interaction Webs}: {Patterns} and {Importance}. \emph{Ecological
-Monographs}, \emph{65}(1), 21--74.
-doi:\href{https://doi.org/10.2307/2937158}{10.2307/2937158}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Meredith2018}{}}%
-Meredith, M. P., Falk, U., Bers, A. V., Mackensen, A., Schloss, I. R.,
-Ruiz Barlett, E., \ldots{} Abele, D. (2018). Anatomy of a glacial
-meltwater discharge event in an {Antarctic} cove. \emph{Philosophical
-Transactions of the Royal Society A: Mathematical, Physical and
-Engineering Sciences}, \emph{376}(2122), 20170163.
-doi:\href{https://doi.org/10.1098/rsta.2017.0163}{10.1098/rsta.2017.0163}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Meyer2017}{}}%
+\bibitem[\citeproctext]{ref-Meyer2017}
 Meyer, B., Freier, U., Grimm, V., Groeneveld, J., Hunt, B. P. V.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Michel2019}{}}%
-Michel, L. N., Danis, B., Dubois, P., Eleaume, M., Fournier, J., Gallut,
-C., \ldots{} Lepoint, G. (2019). Increased sea ice cover alters food web
-structure in {East Antarctica}. \emph{Scientific Reports}, \emph{9}(1),
-8062.
-doi:\href{https://doi.org/10.1038/s41598-019-44605-5}{10.1038/s41598-019-44605-5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mintenbeck2012}{}}%
+\bibitem[\citeproctext]{ref-Mintenbeck2012}
 Mintenbeck, K., Barrera-Oro, E. R., Brey, T., Jacob, U., Knust, R.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Montoya2009}{}}%
-Montoya, JoséM., Woodward, G., Emmerson, M. C., \& Solé, R. V. (2009).
-Press perturbations and indirect effects in real food webs.
-\emph{Ecology}, \emph{90}(9), 2426--2433.
-doi:\href{https://doi.org/10.1890/08-0657.1}{10.1890/08-0657.1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Moore1974}{}}%
+\bibitem[\citeproctext]{ref-Moore1974}
 Moore, S. F., \& Dwyer, R. L. (1974). Effects of oil on marine
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Moy2009}{}}%
+\bibitem[\citeproctext]{ref-Moy2009}
 Moy, A. D., Howard, W. R., Bray, S. G., \& Trull, T. W. (2009). Reduced
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Murphy2007}{}}%
+\bibitem[\citeproctext]{ref-Murphy2007}
 Murphy, E. J., Trathan, P. N., Watkins, J. L., Reid, K., Meredith, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Murphy2006}{}}%
-Murphy, E. j., Watkins, J. l., Trathan, P. n., Reid, K., Meredith, M.
-p., Thorpe, S. e., \ldots{} Fleming, A. h. (2006). Spatial and temporal
-operation of the {Scotia Sea} ecosystem: A review of large-scale links
-in a krill centred food web. \emph{Philosophical Transactions of the
-Royal Society B: Biological Sciences}, \emph{362}(1477), 113--148.
-doi:\href{https://doi.org/10.1098/rstb.2006.1957}{10.1098/rstb.2006.1957}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Nardi2019}{}}%
-Nardi, C. F., Fernández, D. A., Vanella, F. A., \& Chalde, T. (2019).
-The expansion of exotic {Chinook} salmon ({Oncorhynchus} tshawytscha) in
-the extreme south of {Patagonia}: An environmental {DNA} approach.
-\emph{Biological Invasions}, \emph{21}(4), 1415--1425.
-doi:\href{https://doi.org/10.1007/s10530-018-1908-8}{10.1007/s10530-018-1908-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Neder2023}{}}%
-Neder, C. (2023). \emph{{El bentos antártico y su respuesta al cambio
-climático: una aproximación usando modelos de distribución de especies
-como caso de estudio en caleta Potter}} (PhD thesis). Universidad
-Nacional de Córdoba, {Córdoba, Argentina}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Neder2022}{}}%
-Neder, C., Fofonova, V., Androsov, A., Kuznetsov, I., Abele, D., Falk,
-U., \ldots{} Jerosch, K. (2022). Modelling suspended particulate matter
-dynamics at an {Antarctic} fjord impacted by glacier melt. \emph{Journal
-of Marine Systems}, \emph{231}, 103734.
-doi:\href{https://doi.org/10.1016/j.jmarsys.2022.103734}{10.1016/j.jmarsys.2022.103734}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Nilsson2016}{}}%
-Nilsson, K. A., \& McCann, K. S. (2016). Interaction strength
-revisited\textemdash clarifying the role of energy flux for food web
-stability. \emph{Theoretical Ecology}, \emph{9}(1), 59--71.
-doi:\href{https://doi.org/10.1007/s12080-015-0282-8}{10.1007/s12080-015-0282-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Nowacek2015}{}}%
-Nowacek, D. P., Clark, C. W., Mann, D., Miller, P. J., Rosenbaum, H. C.,
-Golden, J. S., \ldots{} Southall, B. L. (2015). Marine seismic surveys
-and ocean noise: Time for coordinated and prudent planning.
-\emph{Frontiers in Ecology and the Environment}, \emph{13}(7), 378--386.
-doi:\href{https://doi.org/10.1890/130286}{10.1890/130286}
-
-\leavevmode\vadjust pre{\hypertarget{ref-OGorman2012}{}}%
-O'Gorman, E. J., Fitch, J. E., \& Crowe, T. P. (2012). Multiple
-anthropogenic stressors and the structural properties of food webs.
-\emph{Ecology}, \emph{93}(3), 441--448.
-doi:\href{https://doi.org/10.1890/11-0982.1}{10.1890/11-0982.1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-OGorman2019}{}}%
-O'Gorman, E. J., Petchey, O. L., Faulkner, K. J., Gallo, B., Gordon, T.
-A. C., Neto-Cerejeira, J., \ldots{} Woodward, G. (2019). A simple model
-predicts how warming simplifies wild food webs. \emph{Nature Climate
-Change}, \emph{9}(8), 611--616.
-doi:\href{https://doi.org/10.1038/s41558-019-0513-x}{10.1038/s41558-019-0513-x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ojeda2021}{}}%
+\bibitem[\citeproctext]{ref-Ojeda2021}
 Ojeda, M., Cossi, P. F., Rimondino, G. N., Chiesa, I. L., Boy, C. C., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Oliver2018}{}}%
-Oliver, E. C. J., Donat, M. G., Burrows, M. T., Moore, P. J., Smale, D.
-A., Alexander, L. V., \ldots{} Wernberg, T. (2018). Longer and more
-frequent marine heatwaves over the past century. \emph{Nature
-Communications}, \emph{9}(1), 1324.
-doi:\href{https://doi.org/10.1038/s41467-018-03732-9}{10.1038/s41467-018-03732-9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Olivier2019}{}}%
-Olivier, P., Frelat, R., Bonsdorff, E., Kortsch, S., Kröncke, I.,
-Möllmann, C., \ldots{} Nordström, M. C. (2019). Exploring the temporal
-variability of a food web using long-term biomonitoring data.
-\emph{Ecography}, \emph{42}(12), 2107--2121.
-doi:\href{https://doi.org/10.1111/ecog.04461}{10.1111/ecog.04461}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Orgeira2021}{}}%
+\bibitem[\citeproctext]{ref-Orgeira2021}
 Orgeira, J. L., Alvarez, F., \& Salvó, C. S. (2021). The same pathway to
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Orr2020}{}}%
-Orr, J. A., Vinebrooke, R. D., Jackson, M. C., Kroeker, K. J., Kordas,
-R. L., Mantyka-Pringle, C., \ldots{} Piggott, J. J. (2020). Towards a
-unified study of multiple stressors: Divisions and common goals across
-research disciplines. \emph{Proceedings of the Royal Society B:
-Biological Sciences}, \emph{287}(1926), 20200421.
-doi:\href{https://doi.org/10.1098/rspb.2020.0421}{10.1098/rspb.2020.0421}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Paine1996}{}}%
-Paine, R. T., Ruesink, J. L., Sun, A., Soulanille, E. L., Wonham, M. J.,
-Harley, C. D. G., \ldots{} Secord, D. L. (1996). {TROUBLE ON OILED
-WATERS}: {Lessons} from the {\emph{Exxon Valdez}} {Oil Spill}.
-\emph{Annual Review of Ecology and Systematics}, \emph{27}(1), 197--235.
-doi:\href{https://doi.org/10.1146/annurev.ecolsys.27.1.197}{10.1146/annurev.ecolsys.27.1.197}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pallin2023}{}}%
+\bibitem[\citeproctext]{ref-Pallin2023}
 Pallin, L. J., Kellar, N. M., Steel, D., Botero-Acosta, N., Baker, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pante2023}{}}%
-Pante, E., Simon-Bouhet, B., \& Irisson, J. (2023). Marmap: {Import},
-{Plot} and {Analyze Bathymetric} and {Topographic Data}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pasotti2015}{}}%
-Pasotti, F., Saravia, L. A., Troch, M. D., Tarantelli, M. S., Sahade,
-R., \& Vanreusel, A. (2015). Benthic {Trophic Interactions} in an
-{Antarctic Shallow Water Ecosystem Affected} by {Recent Glacier
-Retreat}. \emph{PLOS ONE}, \emph{10}(11), e0141742.
-doi:\href{https://doi.org/10.1371/journal.pone.0141742}{10.1371/journal.pone.0141742}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pasti2021}{}}%
-Pasti, A. T., Bovcon, N. D., Ruibal-Núñez, J., Navoa, X., Jacobi, K. J.,
-\& Galván, D. E. (2021). The diet of {Mustelus} schmitti in areas with
-and without commercial bottom trawling ({Central Patagonia},
-{Southwestern Atlantic}): {Is} it evidence of trophic interaction with
-the {Patagonian} shrimp fishery? \emph{Food Webs}, \emph{29}, e00214.
-doi:\href{https://doi.org/10.1016/j.fooweb.2021.e00214}{10.1016/j.fooweb.2021.e00214}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pauli2021}{}}%
-Pauli, N.-C., Flintrop, C. M., Konrad, C., Pakhomov, E. A., Swoboda, S.,
-Koch, F., \ldots{} Iversen, M. H. (2021). Krill and salp faecal pellets
-contribute equally to the carbon flux at the {Antarctic Peninsula}.
-\emph{Nature Communications}, \emph{12}(1), 7168.
-doi:\href{https://doi.org/10.1038/s41467-021-27436-9}{10.1038/s41467-021-27436-9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pecuchet2022}{}}%
-Pecuchet, L., Jørgensen, L. L., Dolgov, A. V., Eriksen, E., Husson, B.,
-Skern-Mauritzen, M., \& Primicerio, R. (2022). Spatio-temporal turnover
-and drivers of bentho-demersal community and food web structure in a
-high-latitude marine ecosystem. \emph{Diversity and Distributions},
-\emph{28}(12), 2503--2520.
-doi:\href{https://doi.org/10.1111/ddi.13580}{10.1111/ddi.13580}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pecuchet2020}{}}%
-Pecuchet, L., Lindegren, M., Kortsch, S., Całkiewicz, J., Jurgensone,
-I., Margonski, P., \ldots{} Nordström, M. C. (2020). Spatio-temporal
-dynamics of multi-trophic communities reveal ecosystem-wide functional
-reorganization. \emph{Ecography}, \emph{43}(2), 197--208.
-doi:\href{https://doi.org/10.1111/ecog.04643}{10.1111/ecog.04643}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Perez2021}{}}%
+\bibitem[\citeproctext]{ref-Perez2021}
 Pérez, A. F., Ojeda, M., Cossi, P. F., Rimondino, G. N., Chiesa, I. L.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Perez2020}{}}%
+\bibitem[\citeproctext]{ref-Perez2020}
 Pérez, Analía F., Ojeda, M., Rimondino, G. N., Chiesa, I. L., Di Mauro,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Perry2020}{}}%
+\bibitem[\citeproctext]{ref-Perry2020}
 Perry, F. A., Kawaguchi, S., Atkinson, A., Sailley, S. F., Tarling, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Peterson2001}{}}%
-Peterson, C. H. (2001). The {`{Exxon Valdez}'} oil spill in {Alaska}:
-{Acute}, indirect and chronic effects on the ecosystem. In
-\emph{Advances in {Marine Biology}} (Vol. 39, pp. 1--103). {Academic
-Press}.
-doi:\href{https://doi.org/10.1016/S0065-2881(01)39008-9}{10.1016/S0065-2881(01)39008-9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pineda-Metz2019a}{}}%
-Pineda-Metz, S. E. A. (2019). \emph{Benthic communities of the {Weddell
-Sea}: Past, present and future} (PhD thesis). University of Bremen,
-{Germany}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pineda-Metz2020}{}}%
+\bibitem[\citeproctext]{ref-Pineda-Metz2020}
 Pineda-Metz, S. E. A., Gerdes, D., \& Richter, C. (2020). Benthic fauna
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pinkerton2021}{}}%
-Pinkerton, M. H., Boyd, P. W., Deppeler, S., Hayward, A., Höfer, J., \&
-Moreau, S. (2021). Evidence for the {Impact} of {Climate Change} on
-{Primary Producers} in the {Southern Ocean}. \emph{Frontiers in Ecology
-and Evolution}, \emph{9}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pinones2016}{}}%
+\bibitem[\citeproctext]{ref-Pinones2016}
 Piñones, A., \& Fedorov, A. V. (2016). Projected changes of {Antarctic}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Piola2009}{}}%
-Piola, A. R., \& Falabella, V. (2009). {El mar Patagónico}. In
-\emph{{Atlas del Mar Patagónico. Especies y Espacios}} (Falabella, V.,
-Campagna, C. y Croxall, J. Ed., pp. 54--75). {Buenos Aires, Argentina}:
-{Wildlife Conservation Society y Birdlife Internacional}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Polazzo2022}{}}%
-Polazzo, F., Marina, T. I., Crettaz-Minaglia, M., \& Rico, A. (2022).
-Food web rewiring drives long-term compositional differences and
-late-disturbance interactions at the community level. \emph{Proceedings
-of the National Academy of Sciences}, \emph{119}(17), e2117364119.
-doi:\href{https://doi.org/10.1073/pnas.2117364119}{10.1073/pnas.2117364119}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Poloczanska2013}{}}%
-Poloczanska, E. S., Brown, C. J., Sydeman, W. J., Kiessling, W.,
-Schoeman, D. S., Moore, P. J., \ldots{} Richardson, A. J. (2013). Global
-imprint of climate change on marine life. \emph{Nature Climate Change},
-\emph{3}(10), 919--925.
-doi:\href{https://doi.org/10.1038/nclimate1958}{10.1038/nclimate1958}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Quartino2008}{}}%
-Quartino, M. L., \& Boraso de Zaixso, A. L. (2008). Summer macroalgal
-biomass in {Potter Cove}, {South Shetland Islands}, {Antarctica}: Its
-production and flux to the ecosystem. \emph{Polar Biology},
-\emph{31}(3), 281--294.
-doi:\href{https://doi.org/10.1007/s00300-007-0356-1}{10.1007/s00300-007-0356-1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Quartino2013}{}}%
-Quartino, María Liliana, Deregibus, D., Campana, G. L., Latorre, G. E.
-J., \& Momo, F. R. (2013). Evidence of {Macroalgal Colonization} on
-{Newly Ice-Free Areas} following {Glacial Retreat} in {Potter Cove}
-({South Shetland Islands}), {Antarctica}. \emph{PLoS ONE}, \emph{8}(3),
-e58223.
+\bibitem[\citeproctext]{ref-Quartino2013}
+Quartino, M. L., Deregibus, D., Campana, G. L., Latorre, G. E. J., \&
+Momo, F. R. (2013). Evidence of {Macroalgal Colonization} on {Newly
+Ice-Free Areas} following {Glacial Retreat} in {Potter Cove} ({South
+Shetland Islands}), {Antarctica}. \emph{PLoS ONE}, \emph{8}(3), e58223.
 doi:\href{https://doi.org/10.1371/journal.pone.0058223}{10.1371/journal.pone.0058223}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Raymond2011}{}}%
-Raymond, B. (2011). \emph{A circumpolar pelagic regionalisation of the
-{Southern Ocean}. {CCAMLR WS-MPA}, {Brest}, {France}, 29
-{Aug}\textendash 2 {Sep} 2011. {Document WS-MPA-11}/6.
-{http://data.aad.gov.au/regionalisation}}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2020}{}}%
-Riccialdelli, L., Becker, Y. A., Fioramonti, N. E., Torres, M., Bruno,
-D. O., Rey, A. R., \& Fernández, D. A. (2020). Trophic structure of
-southern marine ecosystems: A comparative isotopic analysis from the
-{Beagle Channel} to the oceanic {Burdwood Bank} area under a wasp-waist
-assumption. \emph{Marine Ecology Progress Series}, \emph{655}, 1--27.
-doi:\href{https://doi.org/10.3354/meps13524}{10.3354/meps13524}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2013}{}}%
-Riccialdelli, L., Newsome, S. D., Dellabianca, N. A., Bastida, R.,
-Fogel, M. L., \& Goodall, R. N. P. (2013). Ontogenetic diet shift in
-{Commerson}'s dolphin ({Cephalorhynchus} commersonii commersonii) off
-{Tierra} del {Fuego}. \emph{Polar Biology}, \emph{36}(5), 617--627.
-doi:\href{https://doi.org/10.1007/s00300-013-1289-5}{10.1007/s00300-013-1289-5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2017}{}}%
-Riccialdelli, L., Newsome, S. D., Fogel, M. L., \& Fernández, D. A.
-(2017). Trophic interactions and food web structure of a subantarctic
-marine food web in the {Beagle Channel}: {Bahía Lapataia}, {Argentina}.
-\emph{Polar Biology}, \emph{40}(4), 807--821.
-doi:\href{https://doi.org/10.1007/s00300-016-2007-x}{10.1007/s00300-016-2007-x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Rincon-Diaz2021}{}}%
-Rincón-Díaz, M. P., Bovcon, N. D., Cochia, P. D., Góngora, M. E., \&
-Galván, D. E. (2021). Fish functional diversity as an indicator of
-resilience to industrial fishing in {Patagonia Argentina}. \emph{Journal
-of Fish Biology}, \emph{99}(5), 1650--1667.
-doi:\href{https://doi.org/10.1111/jfb.14873}{10.1111/jfb.14873}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Rodriguez2022}{}}%
-Rodriguez, I. D., Marina, T. I., Schloss, I. R., \& Saravia, L. A.
-(2022). Marine food webs are more complex but less stable in
-sub-{Antarctic} ({Beagle Channel}, {Argentina}) than in {Antarctic}
-({Potter Cove}, {Antarctic Peninsula}) regions. \emph{Marine
-Environmental Research}, \emph{174}, 105561.
-doi:\href{https://doi.org/10.1016/j.marenvres.2022.105561}{10.1016/j.marenvres.2022.105561}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Rossi2019}{}}%
-Rossi, L., Sporta Caputi, S., Calizza, E., Careddu, G., Oliverio, M.,
-Schiaparelli, S., \& Costantini, M. L. (2019). Antarctic food web
-architecture under varying dynamics of sea ice cover. \emph{Scientific
-Reports}, \emph{9}(1), 12454.
-doi:\href{https://doi.org/10.1038/s41598-019-48245-7}{10.1038/s41598-019-48245-7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Rowlands2021}{}}%
+\bibitem[\citeproctext]{ref-Rowlands2021}
 Rowlands, E., Galloway, T., Cole, M., Lewis, C., Peck, V., Thorpe, S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ruckamp2011}{}}%
-Rückamp, M., Braun, M., Suckro, S., \& Blindow, N. (2011). Observed
-glacial changes on the {King George Island} ice cap, {Antarctica}, in
-the last decade. \emph{Global and Planetary Change}, \emph{79}(1-2),
-99--109.
-doi:\href{https://doi.org/10.1016/j.gloplacha.2011.06.009}{10.1016/j.gloplacha.2011.06.009}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RuibalNunez2020}{}}%
-Ruibal Nuñez, J. (2020). \emph{{Impacto ecológico de la actividad
-pesquera en las poblaciones de condrictios en el litoral de la Provincia
-de Chubut y Golfo San Jorge}} (PhD thesis). Universidad Nacional de Mar
-del Plata (UNMdP), {Argentina}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sahade2015}{}}%
+\bibitem[\citeproctext]{ref-Sahade2015}
 Sahade, R., Lagger, C., Torre, L., Momo, F., Monien, P., Schloss, I.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sailley2013}{}}%
-Sailley, S. F., Ducklow, H. W., Moeller, H. V., Fraser, W. R.,
-Schofield, O. M., Steinberg, D. K., \ldots{} Doney, S. C. (2013). Carbon
-fluxes and pelagic ecosystem dynamics near two western {Antarctic
-Peninsula Adélie} penguin colonies: An inverse model approach.
-\emph{Marine Ecology Progress Series}, \emph{492}, 253--272.
-doi:\href{https://doi.org/10.3354/meps10534}{10.3354/meps10534}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Saravia2021}{}}%
+\bibitem[\citeproctext]{ref-Saravia2021}
 Saravia, J., Paschke, K., Oyarzún-Salazar, R., Cheng, C.-H. C., Navarro,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Saunders2019}{}}%
-Saunders, R. A., Hill, S. L., Tarling, G. A., \& Murphy, E. J. (2019).
-Myctophid {Fish} ({Family Myctophidae}) {Are Central Consumers} in the
-{Food Web} of the {Scotia Sea} ({Southern Ocean}). \emph{Frontiers in
-Marine Science}, \emph{6}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schejter2021}{}}%
-Schejter, L., \& Albano, M. (2021). Benthic communities at the marine
-protected area {Namuncurá}/{Burdwood} bank, {SW Atlantic Ocean}:
-Detection of vulnerable marine ecosystems and contributions to the
-assessment of the rezoning process. \emph{Polar Biology}, \emph{44}(10),
-2023--2037.
-doi:\href{https://doi.org/10.1007/s00300-021-02936-y}{10.1007/s00300-021-02936-y}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schloss2012}{}}%
-Schloss, I. R., Abele, D., Moreau, S., Demers, S., Bers, A. V.,
-González, O., \& Ferreyra, G. A. (2012). Response of phytoplankton
-dynamics to 19-year (1991\textendash 2009) climate trends in {Potter
-Cove} ({Antarctica}). \emph{Journal of Marine Systems}, \emph{92}(1),
-53--66.
-doi:\href{https://doi.org/10.1016/j.jmarsys.2011.10.006}{10.1016/j.jmarsys.2011.10.006}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schloss2023}{}}%
-Schloss, I. R., Pizarro, G., Cadaillon, A. M., Giesecke, R., Hernando,
-M. P., Almandoz, G. O., \ldots{} Ruiz, C. (2023). Alexandrium catenella
-dynamics and paralytic shellfish toxins distribution along the {Beagle
-Channel} (southern {Patagonia}). \emph{Journal of Marine Systems},
-\emph{239}, 103856.
-doi:\href{https://doi.org/10.1016/j.jmarsys.2022.103856}{10.1016/j.jmarsys.2022.103856}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2011}{}}%
-Schmidt, K., Atkinson, A., Steigenberger, S., Fielding, S., Lindsay, M.
-C. M., Pond, D. W., \ldots{} Achterberg, E. P. (2011). Seabed foraging
-by {Antarctic} krill: {Implications} for stock assessment,
-bentho-pelagic coupling, and the vertical transfer of iron.
-\emph{Limnology and Oceanography}, \emph{56}(4), 1411--1428.
-doi:\href{https://doi.org/10.4319/lo.2011.56.4.1411}{10.4319/lo.2011.56.4.1411}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Seco2021}{}}%
+\bibitem[\citeproctext]{ref-Seco2021}
 Seco, J., Aparício, S., Brierley, A. S., Bustamante, P., Ceia, F. R.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sgarlatta2023}{}}%
-Sgarlatta, M. (2023). \emph{Mechanisms driving tropicalization of
-temperate reef fish assemblages} (Thesis). UNSW Sydney.
-doi:/\href{https://doi.org/10.26190/unsworks/25104}{10.26190/unsworks/25104}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Siniff2008}{}}%
+\bibitem[\citeproctext]{ref-Siniff2008}
 Siniff, D. B., Garrott, R. A., Rotella, J. J., Fraser, W. R., \& Ainley,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Smale2008}{}}%
-Smale, Dan A., \& Barnes, D. K. A. (2008). Likely responses of the
-{Antarctic} benthos to climate-related changes in physical disturbance
-during the 21st century, based primarily on evidence from the {West
-Antarctic Peninsula} region. \emph{Ecography}, \emph{31}(3), 289--305.
-doi:\href{https://doi.org/10.1111/j.0906-7590.2008.05456.x}{10.1111/j.0906-7590.2008.05456.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Smale2008a}{}}%
-Smale, Dan A., Brown, K. M., Barnes, D. K. A., Fraser, K. P. P., \&
+\bibitem[\citeproctext]{ref-Smale2008a}
+Smale, D. A., Brown, K. M., Barnes, D. K. A., Fraser, K. P. P., \&
 Clarke, A. (2008). Ice {Scour Disturbance} in {Antarctic Waters}.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Soeffker2022}{}}%
-Soeffker, M., Hollyman, P. R., Collins, M. A., Hogg, O. T., Riley, A.,
-Laptikhovsky, V., \ldots{} Darby, C. (2022). Contrasting life-history
-traits of two toothfish ({Dissostichus} spp.) species at their range
-edge around the {South Sandwich Islands}. \emph{Deep Sea Research Part
-II: Topical Studies in Oceanography}, \emph{201}, 105098.
-doi:\href{https://doi.org/10.1016/j.dsr2.2022.105098}{10.1016/j.dsr2.2022.105098}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Souza2018}{}}%
+\bibitem[\citeproctext]{ref-Souza2018}
 Souza, M. R. D. P. de, Herrerias, T., Zaleski, T., Forgati, M.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Steele2010}{}}%
-Steele, J. H., Thorpe, S. A., \& Turekian, K. K. (2010). \emph{Ocean
-{Currents}}. {Academic Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2011}{}}%
-Stouffer, D. B., \& Bascompte, J. (2011). Compartmentalization increases
-food-web persistence. \emph{Proceedings of the National Academy of
-Sciences}, \emph{108}(9), 3648--3652.
-doi:\href{https://doi.org/10.1073/pnas.1014353108}{10.1073/pnas.1014353108}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Strobel2013}{}}%
+\bibitem[\citeproctext]{ref-Strobel2013}
 Strobel, A., Leo, E., Pörtner, H. O., \& Mark, F. C. (2013). Elevated
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021}{}}%
-Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
-Desjardins-Proulx, P., \ldots{} Poisot, T. (2021). A roadmap towards
-predicting species interaction networks (across space and time).
-\emph{Philosophical Transactions of the Royal Society B: Biological
-Sciences}, \emph{376}(1837), 20210063.
-doi:\href{https://doi.org/10.1098/rstb.2021.0063}{10.1098/rstb.2021.0063}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Tamini2023}{}}%
+\bibitem[\citeproctext]{ref-Tamini2023}
 Tamini, L. L., Dellacasa, R. F., Chavez, L. N., Marinao, C. J., Góngora,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Tarling2018}{}}%
-Tarling, G. A., Ward, P., \& Thorpe, S. E. (2018). Spatial distributions
-of {Southern Ocean} mesozooplankton communities have been resilient to
-long-term surface warming. \emph{Global Change Biology}, \emph{24}(1),
-132--142.
-doi:\href{https://doi.org/10.1111/gcb.13834}{10.1111/gcb.13834}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Teixido2002}{}}%
-Teixidó, N., Garrabou, J., \& Arntz, W. E. (2002). Spatial pattern
-quantification of {Antarctic} benthic communities using landscape
-indices. \emph{Marine Ecology Progress Series}, \emph{242}, 1--14.
-doi:\href{https://doi.org/10.3354/meps242001}{10.3354/meps242001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Thompson2012}{}}%
-Thompson, R. M., Brose, U., Dunne, J. A., Hall, R. O., Hladyz, S.,
-Kitching, R. L., \ldots{} Tylianakis, J. M. (2012). Food webs:
-Reconciling the structure and function of biodiversity. \emph{Trends in
-Ecology \& Evolution}, \emph{27}(12), 689--697.
-doi:\href{https://doi.org/10.1016/j.tree.2012.08.005}{10.1016/j.tree.2012.08.005}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Thompson2007}{}}%
-Thompson, R. M., Hemberg, M., Starzomski, B. M., \& Shurin, J. B.
-(2007). Trophic {Levels} and {Trophic Tangles}: {The Prevalence} of
-{Omnivory} in {Real Food Webs}. \emph{Ecology}, \emph{88}(3), 612--617.
-doi:\href{https://doi.org/10.1890/05-1454}{10.1890/05-1454}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Tombesi2020}{}}%
-Tombesi, M. L., Rabufetti, F., \& Lovrich, G. A. (2020). Las áreas
-marinas protegidas en la {Argentina}. \emph{La Lupa. Colección Fueguina
-De Divulgación Científica}, \emph{16}, 2--7.
-doi:\url{https://www.coleccionlalupa.com.ar/index.php/lalupa/article/view/79}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Trathan2023}{}}%
-Trathan, Philip N. (2023). The future of the {South Georgia} and {South
-Sandwich Islands} marine protected area in a changing environment: {The}
-choice between industrial fisheries, or ecosystem protection.
-\emph{Marine Policy}, \emph{155}, 105773.
-doi:\href{https://doi.org/10.1016/j.marpol.2023.105773}{10.1016/j.marpol.2023.105773}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Trathan2021}{}}%
+\bibitem[\citeproctext]{ref-Trathan2021}
 Trathan, P. N., Fielding, S., Hollyman, P. R., Murphy, E. J.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Trebilco2020}{}}%
+\bibitem[\citeproctext]{ref-Trebilco2020}
 Trebilco, R., Melbourne-Thomas, J., \& Constable, A. J. (2020). The
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Turner2020}{}}%
-Turner, J., Guarino, M. V., Arnatt, J., Jena, B., Marshall, G. J.,
-Phillips, T., \ldots{} Cavanagh, R. (2020). Recent {Decrease} of {Summer
-Sea Ice} in the {Weddell Sea}, {Antarctica}. \emph{Geophysical Research
-Letters}, \emph{47}(11), e2020GL087127.
-doi:\href{https://doi.org/10.1029/2020GL087127}{10.1029/2020GL087127}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Verges2019}{}}%
-Vergés, A., McCosker, E., Mayer-Pinto, M., Coleman, M. A., Wernberg, T.,
-Ainsworth, T., \& Steinberg, P. D. (2019). Tropicalisation of temperate
-reefs: {Implications} for ecosystem functions and management actions.
-\emph{Functional Ecology}, \emph{33}(6), 1000--1013.
-doi:\href{https://doi.org/10.1111/1365-2435.13310}{10.1111/1365-2435.13310}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Verges2014}{}}%
-Vergés, A., Steinberg, P. D., Hay, M. E., Poore, A. G. B., Campbell, A.
-H., Ballesteros, E., \ldots{} Wilson, S. K. (2014). The tropicalization
-of temperate marine ecosystems: Climate-mediated changes in herbivory
-and community phase shifts. \emph{Proceedings of the Royal Society B:
-Biological Sciences}, \emph{281}(1789), 20140846.
-doi:\href{https://doi.org/10.1098/rspb.2014.0846}{10.1098/rspb.2014.0846}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Vinuesa2005}{}}%
-Vinuesa, J. H. (2005). Distribución de crustáceos decápodos y
-estomatópodos del golfo {San Jorge}, {Argentina}. \emph{Revista de
-Biología Marina y Oceanografía}, \emph{40}(1), 7--21.
-doi:\href{https://doi.org/10.4067/S0718-19572005000100002}{10.4067/S0718-19572005000100002}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Vinuesa2007}{}}%
-Vinuesa, J. H., \& Varisco, M. (2007). Trophic ecology of the lobster
-krill {Munida} gregaria in {San Jorge Gulf}, {Argentina}.
-\emph{Investigaciones Marinas}, \emph{35}(2), 25--34.
-doi:\href{https://doi.org/10.4067/S0717-71782007000200003}{10.4067/S0717-71782007000200003}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Vucic-Pestic2011}{}}%
-Vucic-Pestic, O., Ehnes, R. B., Rall, B. C., \& Brose, U. (2011).
-Warming up the system: Higher predator feeding rates but lower energetic
-efficiencies. \emph{Global Change Biology}, \emph{17}(3), 1301--1310.
-doi:\href{https://doi.org/10.1111/j.1365-2486.2010.02329.x}{10.1111/j.1365-2486.2010.02329.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ward2018}{}}%
-Ward, P., Tarling, G. A., \& Thorpe, S. E. (2018). Temporal changes in
-abundances of large calanoid copepods in the {Scotia Sea}: Comparing the
-1930s with contemporary times. \emph{Polar Biology}, \emph{41}(11),
-2297--2310.
-doi:\href{https://doi.org/10.1007/s00300-018-2369-3}{10.1007/s00300-018-2369-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wege2021}{}}%
+\bibitem[\citeproctext]{ref-Wege2021}
 Wege, M., Salas, L., \& LaRue, M. (2021). Ice matters: {Life-history}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Whitehouse2008}{}}%
-Whitehouse, M. J., Meredith, M. P., Rothery, P., Atkinson, A., Ward, P.,
-\& Korb, R. E. (2008). Rapid warming of the ocean around {South
-Georgia}, {Southern Ocean}, during the 20th century: {Forcings},
-characteristics and implications for lower trophic levels. \emph{Deep
-Sea Research Part I: Oceanographic Research Papers}, \emph{55}(10),
-1218--1228.
-doi:\href{https://doi.org/10.1016/j.dsr.2008.06.002}{10.1016/j.dsr.2008.06.002}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Whitworth1980}{}}%
-Whitworth, T. (1980). Zonation and geostrophic flow of the {Antarctic}
-circumpolar current at {Drake Passage}. \emph{Deep Sea Research Part A.
-Oceanographic Research Papers}, \emph{27}(7), 497--507.
-doi:\href{https://doi.org/10.1016/0198-0149(80)90036-9}{10.1016/0198-0149(80)90036-9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Williams2000}{}}%
-Williams, R. J., \& Martinez, N. D. (2000). Simple rules yield complex
-food webs. \emph{Nature}, \emph{404}(6774), 180--183.
-doi:\href{https://doi.org/10.1038/35004572}{10.1038/35004572}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wood2015}{}}%
-Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
-(2015). Effects of spatial scale of sampling on food web structure.
-\emph{Ecology and Evolution}, \emph{5}(17), 3769--3782.
-doi:\href{https://doi.org/10.1002/ece3.1640}{10.1002/ece3.1640}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Woods2023}{}}%
-Woods, B. L., Van de Putte, A. P., Hindell, M. A., Raymond, B.,
-Saunders, R. A., Walters, A., \& Trebilco, R. (2023). Species
-distribution models describe spatial variability in mesopelagic fish
-abundance in the {Southern Ocean}. \emph{Frontiers in Marine Science},
-\emph{9}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Woodward2010}{}}%
-Woodward, G., Benstead, J. P., Beveridge, O. S., Blanchard, J., Brey,
-T., Brown, L. E., \ldots{} Yvon-Durocher, G. (2010). Ecological
-{Networks} in a {Changing Climate}. In G. Woodward (Ed.), \emph{Advances
-in {Ecological Research}} (Vol. 42, pp. 71--138). {Academic Press}.
-doi:\href{https://doi.org/10.1016/B978-0-12-381363-3.00002-2}{10.1016/B978-0-12-381363-3.00002-2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wu2012}{}}%
-Wu, L., Cai, W., Zhang, L., Nakamura, H., Timmermann, A., Joyce, T.,
-\ldots{} Giese, B. (2012). Enhanced warming over the global subtropical
-western boundary currents. \emph{Nature Climate Change}, \emph{2}(3),
-161--166.
-doi:\href{https://doi.org/10.1038/nclimate1353}{10.1038/nclimate1353}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Yorio2009}{}}%
-Yorio, P. (2009). Marine protected areas, spatial scales, and
-governance: Implications for the conservation of breeding seabirds.
-\emph{Conservation Letters}, \emph{2}(4), 171--178.
-doi:\href{https://doi.org/10.1111/j.1755-263X.2009.00062.x}{10.1111/j.1755-263X.2009.00062.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Yorio2017}{}}%
+\bibitem[\citeproctext]{ref-Yorio2017}
 Yorio, P., González-Zevallos, D., Gatto, A., Biagioni, O., \& Castillo,

### 2023-11-21 manuscript.tex
New version to submit to GCB

@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
-\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
-
 \usepackage{pdflscape,booktabs}
@@
 
-\hypertarget{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}{%
 \section{The response of trophic interaction networks to multiple
 stressors in a marine latitudinal gradient of the Southern
-Hemisphere}\label{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}}
-
-\hypertarget{abstract}{%
-\subsection{Abstract}\label{abstract}}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  Ecological networks are increasingly used as conceptual frameworks for
-  understanding ecological community structure, identifying key species,
-  and for ecosystem management and biodiversity conservation. Nowadays,
-  there is a growing interest in understanding how ecological networks
-  respond to environmental and anthropogenic stressors along
-  geographical gradients.
-\item
-  We review for the first time the state-of-the-art knowledge on
-  stressor response of marine food webs along the southwest Atlantic to
-  Antarctic gradient (45 - 78ºS), considering the following study areas:
-  San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea, Potter Cove
-  (Antarctica) and Weddell Sea (Antarctica). The aim of this review is
-  threefold: 1) describe the complexity and structure of marine food
-  webs along the southwest Atlantic to Antarctic axis from a network
-  perspective; 2) identify the ongoing environmental and anthropogenic
-  stressors for each marine ecosystem containing the food webs; and 3)
-  resume proven food web changes and elaborate hypotheses on how the
-  identified stressors might affect food web features, combining
-  information on node- and network-level properties.
-\item
-  Environmental and anthropogenic stressor effects in the study gradient
-  have been mostly assessed individually and at the organism and/or
-  population, i.e., at the node level, with one exception: the effect of
-  fisheries in the San Jorge Gulf food web. To address the most
-  plausible stressors effects on the selected food webs, we built
-  hypotheses for each study area considering the following: a)
-  stressor(s), b) parameter(s) affected, c) node-level properties of the
-  affected species, and d) network-level properties of the food web.
-\item
-  The most common stressor reported along the gradient is global
-  warming, except for Beagle Channel and Burdwood Bank, which are more
-  influenced by the introduction of an alien species and fisheries,
-  respectively. We provide particular hypotheses on how warming might
-  impact food webs.
-\item
-  We demonstrate the advantages of applying a network approach to better
-  understand and predict the effect of stressors in marine ecosystems of
-  the Southern Hemisphere.
-\end{enumerate}
+Hemisphere}\label{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}
+
+Tomás I. Marina\textsuperscript{1}, Leonardo A.
+Saravia\textsuperscript{1,2,*}, Iara D. Rodriguez\textsuperscript{3},
+Manuela Funes\textsuperscript{4}, Georgina Cordone\textsuperscript{5},
+Santiago R. Doyle\textsuperscript{3,6}, Anahí
+Silvestro\textsuperscript{6}, David E. Galván\textsuperscript{5},
+Susanne Kortsch\textsuperscript{7} \& Fernando Momo\textsuperscript{3,6}
+
+\textsuperscript{1} Centro Austral de Investigaciones Científicas
+(CADIC-CONICET), Ushuaia, Argentina;
+
+\textsuperscript{2} Instituto de Ciencias Polares, Ambiente y Recursos
+Naturales, Universidad Nacional de Tierra del Fuego (UNTdF), Ushuaia,
+Argentina;
+
+\textsuperscript{3} Instituto de Ciencias, Universidad Nacional de
+General Sarmiento (UNGS), Los Polvorines, Argentina;
+
+\textsuperscript{4} Instituto de Investigaciones Marinas y Costeras
+(IIMyC-CONICET), Mar del Plata, Argentina;
+
+\textsuperscript{5} Centro Para el Estudio de Sistemas Marinos
+(CESIMAR-CONICET), Puerto Madryn, Argentina;
+
+\textsuperscript{6} Instituto de Ecología y Desarrollo Sustentable
+(INEDES-CONICET-UNLu), Luján, Argentina;
+
+\textsuperscript{7} Tvärminne Zoological Station, University of
+Helsinki, Hanko, Finland.
+
+* corresponding author: Leonardo A. Saravia. Centro Austral de
+Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina.
+\href{mailto:lasaravia@untdf.edu.ar}{\nolinkurl{lasaravia@untdf.edu.ar}}
+
+\subsection{Abstract}\label{abstract}
+
+Ecological networks offer valuable insights into community structure,
+key species identification, and ecosystem management for biodiversity
+conservation. Understanding how these networks react to environmental
+and anthropogenic stressors, especially along geographical gradients, is
+of increasing interest. This review presents a pioneering analysis of
+stressor responses in marine food webs from the southwest Atlantic to
+the Antarctic (45 - 78ºS), encompassing areas such as San Jorge Gulf,
+Beagle Channel, Burdwood Bank, Scotia Sea, Potter Cove, and the Weddell
+Sea in Antarctica. Our objectives are to: 1) describe the structure of
+marine food webs along this axis using a network approach; 2) identify
+predominant environmental and anthropogenic stressors affecting each
+ecosystem; and 3) summarize observed food web changes and hypothesize on
+stressor impacts. Our collaborative team, comprising regional experts
+and global authorities on high-latitude marine food webs and stressor
+effects, ensures a comprehensive and credible literature review. We
+assessed the effects of stressors primarily at the species level, with
+notable exceptions like fisheries in San Jorge Gulf. Hypotheses for each
+study area were formulated considering: a) stressors; b) impacted
+parameters; c) node-level species properties; and d) network-level food
+web properties. Global warming emerges as the most common stressor
+across the gradient, except in the Beagle Channel and Burdwood Bank,
+where alien species introduction and fisheries are more influential,
+respectively. We offer specific hypotheses on how warming may affect
+food webs. Our findings highlight the benefits of a network approach in
+understanding and predicting stressor effects in Southern Hemisphere
+marine ecosystems. This approach provides a holistic understanding of
+ecological networks, enhances our ability to identify key species and
+interactions, and offers insights for ecosystem management and
+conservation in the face of various stressors.
 
@@
 
-\hypertarget{introduction}{%
-\subsection{1. Introduction}\label{introduction}}
+\subsection{1. Introduction}\label{introduction}
 
@@
 understanding of the structure and functioning of ecosystems (Belgrano,
-Scharler, Scharler, Dunne, \& Ulanowicz, 2005; Thompson et al., 2012;
-D'Alelio, Libralato, Wyatt, \& Ribera d'Alcalà, 2016). Trophic networks
-(or food webs) allow identifying properties and key species that may be
-crucial for ecosystem stability, and hence important for ecosystem
-management and biodiversity conservation (Thompson et al., 2012). There
-is a growing interest in understanding how ecological networks respond
-to environmental and anthropogenic stressors along geographical
-gradients (Baiser, Gotelli, Buckley, Miller, \& Ellison, 2012; Cirtwill,
-Stouffer, \& Romanuk, 2015; Strydom et al., 2021; Bauer et al., 2022).
-Yet, only a few studies have described variation in food web structure
-along latitudinal gradients in marine ecosystems. The few that have come
-from the Global North (Wood, Russell, Hanson, Williams, \& Dunne, 2015;
-Kortsch et al., 2019; Frelat et al., 2022; Pecuchet et al., 2022),
-whereas no studies, nor meta-analyses, on geographical variation in
-marine food webs exist for the Global South (Southern Hemisphere).
+Scharler, Scharler, Dunne, \& Ulanowicz, 2005; Thompson et al., 2012).
+Trophic networks (or food webs) allow identifying properties and key
+species that may be crucial for ecosystem stability, and hence important
+for ecosystem management and biodiversity conservation (Thompson et al.,
+2012). There is a growing interest in understanding how ecological
+networks respond to environmental and anthropogenic stressors along
+geographical gradients (Cirtwill, Stouffer, \& Romanuk, 2015; Bauer et
+al., 2022). Yet, only a few studies have described variation in food web
+structure along latitudinal gradients in marine ecosystems. The few that
+have come from the Global North (Wood, Russell, Hanson, Williams, \&
+Dunne, 2015; Kortsch et al., 2019; Pecuchet et al., 2022), whereas no
+studies, nor meta-analyses, on geographical variation in marine food
+webs exist for the Global South (Southern Hemisphere).
 
@@
 expected changes in food webs driven by stressors in selected areas
-along this large-scale latitudinal gradient. The aim of this review is
-threefold: 1) describe the complexity and structure of marine food webs
-along the southwest Atlantic to Antarctic axis from a network
-perspective; 2) identify the ongoing environmental and anthropogenic
-stressors for each marine ecosystem containing the food webs; and 3)
-resume proven food web changes and elaborate hypotheses on how the
-identified stressors might affect food web features (e.g.~energy flow,
-stability), combining information on node- and network-level properties.
-Finally, we suggest which additional data and analyses are needed to
-gain insights into the stressors' effects on food web properties in the
-southwest Atlantic to Antarctic region.
-
-\hypertarget{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}{%
+along this large-scale latitudinal gradient. We recruited food web
+experts from different marine systems of Argentina and the world (see
+co-authors' list). Throughout the year 2023 we maintained regular
+discussion meetings, typically held every two or three weeks. The aim of
+this review is threefold: 1) describe the complexity and structure of
+marine food webs along the southwest Atlantic to Antarctic axis from a
+network perspective; 2) identify the ongoing environmental and
+anthropogenic stressors for each marine ecosystem containing the food
+webs; and 3) resume proven food web changes and elaborate hypotheses on
+how the identified stressors might affect food web features (e.g.~energy
+flow, stability), combining information on node- and network-level
+properties. Finally, we suggest which additional data and analyses are
+needed to gain insights into the stressors' effects on food web
+properties in the southwest Atlantic to Antarctic region.
+
 \subsection{2. The structure of marine food webs in the Southwest
 Atlantic - Antarctic
-region}\label{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}}
+region}\label{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}
 
@@
 comprise one of the most biologically productive regions of the world's
-oceans (Acha, Mianzan, Guerrero, Favero, \& Bava, 2004; Whitehouse et
-al., 2008; Ballerini et al., 2014; Latorre et al., 2023). The referred
-region extends from San Jorge Gulf (45ºS) in the Patagonian shelf to the
-Weddell Sea (78ºS) in the Southern Ocean, and covers a well-connected
-oceanic latitudinal gradient (R. P. Matano, Palma, \& Piola, 2010;
-Steele, Thorpe, \& Turekian, 2010; Guihou, Piola, Palma, \& Chidichimo,
-2020).
+oceans (Acha, Mianzan, Guerrero, Favero, \& Bava, 2004; Latorre et al.,
+2023). The referred region extends from San Jorge Gulf (45ºS) in the
+Patagonian shelf to the Weddell Sea (78ºS) in the Southern Ocean, and
+covers a well-connected oceanic latitudinal gradient (R. P. Matano,
+Palma, \& Piola, 2010; Guihou, Piola, Palma, \& Chidichimo, 2020).
 
@@
 carried out addressing the trophic ecology of specific species and
-prey-predator relationships (Vinuesa \& Varisco, 2007; Sailley et al.,
-2013; Pasotti et al., 2015; Riccialdelli, Newsome, Fogel, \& Fernández,
-2017; Saunders, Hill, Tarling, \& Murphy, 2019; Riccialdelli et al.,
+prey-predator relationships (Vinuesa \& Varisco, 2007; Pasotti et al.,
+2015; Saunders, Hill, Tarling, \& Murphy, 2019; Riccialdelli et al.,
 2020), but few studies have considered the complexity of the ecosystem
@@
 ecosystems, and ultimately reduce the ability to predict ecosystem
-responses to perturbations (Montoya, Woodward, Emmerson, \& Solé, 2009;
-Woodward et al., 2010).
+responses to perturbations (Montoya, Woodward, Emmerson, \& Solé, 2009).
 
@@
 present two prominent frontal systems. These systems are the areas of
-highest productivity (Bogazzi et al., 2005; Glembocki, Williams,
-Góngora, Gagliardini, \& Orensanz, 2015). The Gulf's productivity
-supports large invertebrate and vertebrate fisheries (María Eva Góngora,
-González-Zevallos, Pettovello, \& Mendía, 2012), as well as marine
-mammal and seabird populations (Yorio, 2009). The San Jorge Gulf food
-web comprises 165 nodes and 1015 trophic interactions with a connectance
-of 0.04. The percentage of top predators is 16\%, 78\% of intermediate
-nodes and 6\% of basal nodes; 60\% of predators are omnivorous (Table
-1). The most connected nodes are: the Argentine red shrimp Pleoticus
-muelleri, the squat lobster Gimothea gregaria, squids (Illex argentinus
-as dominant species) and Amphipoda. Notably, these nodes present
-mid-trophic positions in the food web (3.0, 2.5, 3.6 and 2,
-respectively) (Funes et al., 2022).
+highest productivity (Glembocki, Williams, Góngora, Gagliardini, \&
+Orensanz, 2015). The Gulf's productivity supports large invertebrate and
+vertebrate fisheries (Góngora, González-Zevallos, Pettovello, \& Mendía,
+2012), as well as marine mammal and seabird populations (Yorio, 2009).
+The San Jorge Gulf food web comprises 165 nodes and 1015 trophic
+interactions with a connectance of 0.04. The percentage of top predators
+is 16\%, 78\% of intermediate nodes and 6\% of basal nodes; 60\% of
+predators are omnivorous (Table 1). The most connected nodes are: the
+Argentine red shrimp Pleoticus muelleri, the squat lobster Gimothea
+gregaria, squids (Illex argentinus as dominant species) and Amphipoda.
+Notably, these nodes present mid-trophic positions in the food web (3.0,
+2.5, 3.6 and 2, respectively) (Funes et al., 2022).
 
@@
 plateau named Burdwood Bank with a 200 m isobath boundary, and a deep
-slope that reaches 4000 m in depth, respectively (Tombesi, Rabufetti, \&
-Lovrich, 2020; Administración de Parques Nacionales, 2022) (Figure 1).
-Physical features in the plateau are fairly stable, with salinity
-averaging 34 all year round and temperature ranging between 4 and 8ºC
-(Acha et al., 2004; Piola \& Falabella, 2009). The plateau is surrounded
-by steep flanks of up to 4000 m depth, protected by the Marine Protected
-Area Namuncurá - Burdwood Bank II (32,000 km2; \textasciitilde55º -
-56ºS, \textasciitilde58º - 62ºW). Intense upwelling and mixing occur in
-relation to the slope, entraining deep nutrient-rich waters into the
-photic layer (Piola \& Falabella, 2009; Ricardo P. Matano, Palma, \&
-Combes, 2019), and resulting in a fairly homogeneous water column both
-spatially and temporally (Glorioso \& Flather, 1995; Ricardo P. Matano
-et al., 2019). The Burdwood Bank food web comprises 379 nodes and 1788
-interactions, with a connectance of 0.01, and an asymmetric degree
-distribution (i.e.~most of the species have a relatively low number of
-interactions and few species concentrate most of them). Almost half of
-the consumers are omnivores (0.48), and the network displays a
-small-world pattern (Marina et al., in rev.) (Table 1).
+slope that reaches 4000 m in depth, respectively (Administración de
+Parques Nacionales, 2022) (Figure 1). Physical features in the plateau
+are fairly stable, with salinity averaging 34 all year round and
+temperature ranging between 4 and 8ºC (Acha et al., 2004). The plateau
+is surrounded by steep flanks of up to 4000 m depth, protected by the
+Marine Protected Area Namuncurá - Burdwood Bank II (32,000 km2;
+\textasciitilde55º - 56ºS, \textasciitilde58º - 62ºW). Intense upwelling
+and mixing occur in relation to the slope, entraining deep nutrient-rich
+waters into the photic layer (Ricardo P. Matano, Palma, \& Combes,
+2019), and resulting in a fairly homogeneous water column both spatially
+and temporally (Ricardo P. Matano et al., 2019). The Burdwood Bank food
+web comprises 379 nodes and 1788 interactions, with a connectance of
+0.01, and an asymmetric degree distribution (i.e.~most of the species
+have a relatively low number of interactions and few species concentrate
+most of them). Almost half of the consumers are omnivores (0.48), and
+the network displays a small-world pattern (Marina et al., in rev.)
+(Table 1).
 
@@
 80 m maximum depth; and c) the external cove, ice-free for 60 years with
-a 185 m maximum depth and rocky substrate (Jerosch et al., 2018; Neder
-et al., 2022; Neder, 2023). Potter Cove's high-latitude location results
-in variable environmental conditions due to photoperiod length
-seasonality. Sea ice often covers this area in winter (Schloss et al.,
-2012). With low phytoplankton biomass, macroalgae, and microphytobenthos
-are likely the primary food sources for secondary benthic production (M.
-L. Quartino \& Boraso de Zaixso, 2008). The Potter Cove food web
-includes 110 nodes and 649 interactions, with an asymmetric degree
-distribution, and a connectance value of 0.05 (Table 1). It presents a
-modular structure (groups of species interact more strongly with each
-other than with species belonging to other groups), that's positively
-associated with stability, since perturbation can be retained within
-modules (Rodriguez et al., 2022).
+a 185 m maximum depth and rocky substrate (Jerosch et al., 2018). Potter
+Cove's high-latitude location results in variable environmental
+conditions due to photoperiod length seasonality. Sea ice often covers
+this area in winter (Schloss et al., 2012). With low phytoplankton
+biomass, macroalgae, and microphytobenthos are likely the primary food
+sources for secondary benthic production (M. L. Quartino \& Boraso de
+Zaixso, 2008). The Potter Cove food web includes 110 nodes and 649
+interactions, with an asymmetric degree distribution, and a connectance
+value of 0.05 (Table 1). It presents a modular structure (groups of
+species interact more strongly with each other than with species
+belonging to other groups), that's positively associated with stability,
+since perturbation can be retained within modules (Rodriguez et al.,
+2022).
 
@@
 benthic biomasses and an intermediate to high diversity when compared to
-benthic boreal communities (Dayton, 1990; Teixidó, Garrabou, \& Arntz,
-2002). The Weddell Sea food web exhibits a high level of network
-complexity, featuring the greatest number of nodes (490) and trophic
-interactions (16041) among the analyzed food webs in this review (Table
-1). Its connectance (0.07) and other structural properties are
-intermediate compared to the other food webs. Recently, the interaction
-strengths of this food web were estimated, revealing the presence of
-numerous weak and few strong interactions, which is consistent with
-findings in other complex food webs (McCann, Hastings, \& Huxel, 1998;
-Nilsson \& McCann, 2016). Notably, this asymmetric distribution of
-interaction strength is likely to promote community persistence.
-
+benthic boreal communities (Teixidó, Garrabou, \& Arntz, 2002). The
+Weddell Sea food web exhibits a high level of network complexity,
+featuring the greatest number of nodes (490) and trophic interactions
+(16041) among the analyzed food webs in this review (Table 1). Its
+connectance (0.07) and other structural properties are intermediate
+compared to the other food webs. Recently, the interaction strengths of
+this food web were estimated, revealing the presence of numerous weak
+and few strong interactions, which is consistent with findings in other
+complex food webs (Nilsson \& McCann, 2016). Notably, this asymmetric
+distribution of interaction strength is likely to promote community
+persistence.
+
+\newpage
 \footnotesize
@@
 Table 1. Complexity and structure properties of the marine food webs
-considered in the present review. Refer to Table 3 for definition of
+considered in the present review. Refer to Table 2 for definition of
 properties. mean TL: mean trophic level. Food webs are ordered by
@@
 
-\hypertarget{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}{%
 \subsection{3. Environmental and anthropogenic stressors in the
 Southwest Atlantic - Antarctic
-region}\label{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}}
+region}\label{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}
 
@@
 quantifiable change, irrespective of its direction (increase or
-decrease), in a biological response (Côté, Darling, \& Brown, 2016; Orr
-et al., 2020). In the light of this, the southwest Atlantic - Antarctic
-marine biota has been and is currently subjected to a variety of
-stressors (e.g.~sea warming, glacial retreat, ice changes,
-acidification, species invasion, fisheries, and contamination). Although
-it is well-known that multiple stressors act in concert at any given
-time (e.g.~warming and fishery; acidification and contaminants) (Julian
-Gutt et al., 2015, 2021), to date stressor assessments have been
-performed individually. Moreover, the potential for interactive effects
-of two or more stressors (synergy or antagonism) (Crain, Kroeker, \&
-Halpern, 2008; Côté et al., 2016) is almost unknown for the region
-(Rowlands et al., 2021).
+decrease), in a biological response (Orr et al., 2020). In the light of
+this, the southwest Atlantic - Antarctic marine biota has been and is
+currently subjected to a variety of stressors (e.g.~sea warming, glacial
+retreat, ice changes, acidification, species invasion, fisheries, and
+contamination). Although it is well-known that multiple stressors act in
+concert at any given time (e.g.~warming and fishery; acidification and
+contaminants) (Gutt et al., 2021), to date stressor assessments have
+been performed individually. Moreover, the potential for interactive
+effects of two or more stressors (synergy or antagonism) (Côté, Darling,
+\& Brown, 2016) is almost unknown for the region (Rowlands et al.,
+2021).
 
@@
 parameters affected reported for the marine ecosystems that contain the
-food webs considered in this review. In Table 2 we provide an exhaustive
-list of all stressors affecting species inhabiting each area,
+food webs considered in this review. In Table S2 we provide an
+exhaustive list of all stressors affecting species inhabiting each area,
 considering: the type of stressor, species and parameter affected, and
@@
 
-\newpage
-\begin{landscape}
-\scriptsize
-
-Table 2. Environmental and anthropogenic stressors reported for the
-study areas: San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea
-(North and South), Potter Cove, and Weddell Sea. Stressor categories:
-sea warming; glacial retreat; sediment in the water column; iceberg
-scouring; sea ice extent; ocean acidification; ocean acidification +
-plastics; microplastics; mercury; urban \& industrial pollution;
-fishery; alien species. The species affected were considered at the node
-level, whereas effects were considered at the organism and population
-levels. Categories of affected parameters and variables: metabolism;
-biomass; distribution; diet (see text for explanation). ``Locality''
-indicates whether a stressor for a given species was reported for the
-study area (`In situ') or in another area (`Elsewhere').
-
-\begin{longtable}{ L{2.1cm} L{2.5cm} L{4cm} L{2.5cm} L{2cm} L{3cm} }
-\hline
-\textbf{Study area} & \textbf{Stressor} & \textbf{Species affected} & \textbf{Parameter affected} & \textbf{Locality} & \textbf{Reference} \\
-\hline
-\endhead
-\endfoot
-\hline
-\endlastfoot
-\textbf{San Jorge Gulf} & & & & & \\
-& Sea warming & Fish assemblage \& its prey & Distribution & In situ &
-Galván et al. (2022) \\
-& Fishery & Demersal fish community & Biomass & In situ & Galván et al.
-(2022) \\
-& Fishery & Macroinvertebrates, fishes and seabirds & Diet & In situ &
-González-Zevallos \& Yorio (2006); González-Zevallos \& Yorio (2011);
-Yorio, González-Zevallos, Gatto, Biagioni, \& Castillo (2017) \\
-& Alien species & Fish assemblage \& its prey & Distribution & In situ &
-Galván et al. (2022); J. Ciancio, Beauchamp, \& Pascual (2010) \\
-& Urban \& industrial pollution & Seabirds \& benthic assemblage &
-Biomass & Elsewhere & Moore \& Dwyer (1974); Buskey, White, \& Esbaugh
-(2016) \\
-\textbf{Beagle Channel} & & & & & \\
-& Urban \& industrial pollution & Macroalgae; Mytilus edulis chilensis,
-Patagonotothen tessellata & Metabolism & In situ & Giarratano \& Amin
-(2010); Ferreira, Lo Nostro, Fernández, \& Genovese (2021); Kaminsky et
-al. (in prep.) \\
-& Mercury & Phytoplankton, Zooplankton, \emph{Grimothea gregaria} &
-Metabolism & In situ & Fioramonti, Ribeiro Guevara, Becker, \&
-Riccialdelli (2022) \\
-& Microplastics & Mytilus edulis chilensis, Nacella magellanica &
-Metabolism & In situ & Analía F. Pérez et al. (2020); Ojeda et al.
-(2021) \\
-& Alien species: Chinook salmon Oncorhynchus tshawytscha &
-Patagonotothen tessellata, Sprattus fuegensis & Diet/Biomass & In situ
-(the presence), Elsewhere (changes in prey biomass) & Fernández,
-Ciancio, Ceballos, Riva-Rossi, \& Pascual (2010); J. E. Ciancio,
-Pascual, Botto, Frere, \& Iribarne (2008) \\
-\textbf{Burdwood Bank} & & & & & \\
-& Mercury & Dissostichus eleginoides, Sprattus fuegensis, Patagonotothen
-ramsayi, Cottoperca trigloides (fishes) \& squids & Metabolism & In situ
-& Fioramonti et al. (2022) \\
-& Microplastics & Henricia obesa \& Odontaster penicillatus (sea stars);
-Patagonotothen guntheri \& P. ramsayi (fishes) & Metabolism & In situ &
-Cossi et al. (2021); A. F. Pérez et al. (2021) \\
-& Fishery & Target: Dissostichus eleginoides. Bycatch: Macrourus sp.,
-Coelorinchus sp. (fishes), Daption capense, Thalassarche melanophris,
-Macronectes giganteus, T. chrysostoma, Diomedea epomophora (seabirds),
-30+ spp macrobenthos & Biomass & Elsewhere & Gaitán \& Marí (2016);
-Patricia A. Martínez, Wöhler, Troccoli, Di Marco, \& Maydana (2022);
-Administración de Parques Nacionales (2022); Tamini et al. (2023) \\
-& Fishery & Thalassarche melanophris, Macronectes giganteus, Daption
-capense, Diomedea epomophora, M. halli, Procellaria aequinoctialis
-(seabirds) & Diet & Elsewhere & Tamini et al. (2023) \\
-\textbf{Scotia Sea, North \& South} & & & & & \\
-& Mercury & Krefftichthys anderssoni, Protomyctophum bolini, Electrona
-antarctica, Gymnoscopelus nicholsi, Gymnoscopelus braueri, Dissostichus
-eleginoides & Metabolism & In situ & Seco et al. (2021) \\
-& Ocean acidification + plastics & Euphausia superba, Limacina
-retroversa (Pteropoda) & Metabolism & In situ & Rowlands et al. (2021);
-Manno, Peck, Corsi, \& Bergami (2022) \\
-& Sea warming & Euphausia superba & Metabolism & In situ & E. J. Murphy
-et al. (2007); Perry et al. (2020) \\
-& Sea warming & Euphausia superba & Distribution & In situ & Atkinson et
-al. (2019) \\
-& Fishery & Euphausia superba & Biomass & In situ & P. N. Trathan et al.
-(2021) \\
-\textbf{Potter Cove (Antarctica)} & & & & & \\
-& Sediment in water column & Microphytobenthos, macroalgae, benthic
-filter feeders (ascidians), pelagic filter feeders (krill, salps) &
-Metabolism & In situ & Sahade et al. (2015); D. Deregibus et al. (2016);
-Fuentes et al. (2016); Hoffmann et al. (2019) \\
-& Sea ice extent & Krill & Biomass & Elsewhere & Flores et al. (2012) \\
-& Sea ice extent & Benthic community (macroalgae, invertebrates) &
-Metabolism & Elsewhere & Clark et al. (2013); Campana et al. (2018) \\
-& Glacial retreat & Benthic community (macroalgae, invertebrates) &
-Biomass & In situ & María Liliana Quartino, Deregibus, Campana, Latorre,
-\& Momo (2013); Lagger, Servetto, Torre, \& Sahade (2017); Lagger et al.
-(2018) \\
-& Iceberg scouring & Benthic community & Biomass & In situ & D.
-Deregibus, Quartino, Zacher, Campana, \& Barnes (2017); Dolores
-Deregibus et al. (2023) \\
-& Sea warming & Phytoplankton & Metabolism, biomass & In situ & Antoni
-et al. (2020); Latorre et al. (2023) \\
-& Sea warming & Zooplankton & Metabolism, biomass, diet & In situ &
-Garcia et al. (2016); Garcia et al. (2019) \\
-& Sea warming & Fish & Metabolism & In situ, elsewhere & Strobel, Leo,
-Pörtner, \& Mark (2013); Souza et al. (2018); Saravia et al. (2021) \\
-\textbf{Weddell Sea (Antarctica)} & & & & & \\
-& Iceberg scouring & Macrobentos & Biomass & In situ & Isla (2023);
-Julian Gutt et al. (2015); Dan A. Smale, Brown, Barnes, Fraser, \&
-Clarke (2008); J. Gutt, Starmans, \& Dieckmann (1996) \\
-& Iceberg scouring & Hexactinellida sponges & Biomass & In situ & Julian
-Gutt \& Starmans (2001); Pineda-Metz, Gerdes, \& Richter (2020); Julian
-Gutt (2001); Julian Gutt \& Piepenburg (2003) \\
-& Ocean acidification & Primary producers / krill / foraminifera /
-flagellates & Metabolism & Elsewhere & Deppeler et al. (2020); Isla
-(2023); Julian Gutt et al. (2015); Moy, Howard, Bray, \& Trull (2009) \\
-& Ocean acidification & Euphausia superba, Pleuragramma antarcticum &
-Metabolism & In situ & So Kawaguchi et al. (2010); S. Kawaguchi et al.
-(2013); Piñones \& Fedorov (2016); Mintenbeck et al. (2012) \\
-& Sea warming & Large (diatoms) \& small (cryptophytes) phytoplankton,
-zooplankton (salps) & Metabolism & Elsewhere & Isla (2023); Julian Gutt
-et al. (2015); Trebilco, Melbourne-Thomas, \& Constable (2020) \\
-& Sea warming & Euphausia superba, Nototheniid fishes, Pleuragramma
-antarcticum & Metabolism & In situ & Meyer et al. (2017); Hill,
-Phillips, \& Atkinson (2013); Mintenbeck et al. (2012); Constable et al.
-(2014); Mintenbeck et al. (2012) \\
-& Sea ice extent & Phytoplankton, Lobodon carcinophaga, Hydrurga
-leptonyx, Leptonychotes weddellii, Ommataphoca rossii, Mirounga leonina,
-Arctocephalus gazella & Metabolism & In situ & Pineda-Metz et al.
-(2020); Wege, Salas, \& LaRue (2021); Siniff, Garrott, Rotella, Fraser,
-\& Ainley (2008) \\
-& Sea ice extent & Euphausia superba, Pleuragramma antarcticum,
-Pagodroma nivea, Thalassoica antarctica, Pygoscelis adeliae & Metabolism
-& In situ & Orgeira, Alvarez, \& Salvó (2021); Braithwaite, Meeuwig,
-Letessier, Jenner, \& Brierley (2015); Hill et al. (2013); Mintenbeck et
-al. (2012) \\
-& Sea ice extent & Megaptera novaeangliae & Metabolism & Elsewhere &
-Pallin et al. (2023) \\
-& Sea ice extent & Aptenodytes forsteri & Metabolism & Elsewhere &
-Orgeira et al. (2021) \\
-\end{longtable}
-
-\end{landscape}
-\normalsize
-
-\hypertarget{san-jorge-gulf}{%
-\subsubsection{3.1 San Jorge Gulf}\label{san-jorge-gulf}}
+\subsubsection{3.1 San Jorge Gulf}\label{san-jorge-gulf}
 
 San Jorge Gulf experienced several environmental and anthropogenic
-stressors (Table 2). Trawl fisheries discard several species and add new
-trophic interactions to the food web which resulted in a decrease in
+stressors (Table S2). Trawl fisheries discard several species and add
+new trophic interactions to the food web which resulted in a decrease in
 trait variability and the stability of the system (Rincón-Díaz, Bovcon,
@@
 bycatch item, 29 other cartilaginous and 69 bony local fish species were
-also registered as incidental catch between 2005 and 2014 (María E.
-Góngora, Bovcon, \& Cochia, 2009; Bovcon, Góngora, Marinao, \&
-González-Zevallos, 2013; Ruibal Nuñez, 2020). This level of impact
-triggered a shift in the functional diversity of the assemblages
-homogenizing the trophic function of fishes (Rincón-Díaz et al., 2021).
-Other functional changes were a decrease in the maximum sizes of
-individual fish, together with a drop in elasmobranchs biomass and an
-increase in crustaceans biomass (Funes, 2020). The significant increase
-in crustacean biomass was mostly due to the increase in Pleoticus
-muelleri and Grimothea gregaria populations (Funes, 2020). These species
-rapidly became the most important prey for the most abundant fishes in
-the area: M. hubbsi and Mustelus schmitti (Belleggia, Giberto, \&
-Bremec, 2017; Pasti et al., 2021). However, the above-mentioned effects
-of trawl fisheries on the structure and function of the San Jorge Gulf
-community may have changed again, since the fisheries ceased activity in
-2015 (Annex I, Resolution CFP No 7/2018), remaining a minimum of
-artisanal activity.
+also registered as incidental catch between 2005 and 2014 (Bovcon,
+Góngora, Marinao, \& González-Zevallos, 2013; Ruibal Nuñez, 2020). This
+level of impact triggered a shift in the functional diversity of the
+assemblages homogenizing the trophic function of fishes (Rincón-Díaz et
+al., 2021). Other functional changes were a decrease in the maximum
+sizes of individual fish, together with a drop in elasmobranchs biomass
+and an increase in crustaceans biomass (Funes, 2020). The significant
+increase in crustacean biomass was mostly due to the increase in
+Pleoticus muelleri and Grimothea gregaria populations (Funes, 2020).
+These species rapidly became the most important prey for the most
+abundant fishes in the area: M. hubbsi and Mustelus schmitti (Pasti et
+al., 2021). However, the above-mentioned effects of trawl fisheries on
+the structure and function of the San Jorge Gulf community may have
+changed again, since the fisheries ceased activity in 2015 (Annex I,
+Resolution CFP No 7/2018), remaining a small trawling artisanal fishery.
 
@@
 populations, alien species are also documented to affect the demersal
-assemblage (fish and macroinvertebrates) in the Gulf (Vinuesa, 2005 ;
-Galván et al., 2022). Finally, San Jorge Gulf is exposed to urban and
-industrial pollution due to an oil monobuoy from which oil manipulation
-and general oil transport along the Patagonian coast registered several
-oil spills and chronic oil discharges (García-Borboroglu, Boersma,
-Reyes, \& Skewgar, 2008). Other marine systems impacted by oil spill
-showed an important decrease in marine bird populations (Irons, Kendall,
-Erickson, McDonald, \& Lance, 2000), seals and macroalgae (e.g. Garrott,
-Eberhardt, \& Burn (1993); Paine et al. (1996)), with examples of
-cascading effects throughout the food web (Paine et al., 1996; Peterson,
-2001).
-
-\hypertarget{beagle-channel}{%
-\subsubsection{3.2 Beagle Channel}\label{beagle-channel}}
+assemblage (fish and macroinvertebrates) in the Gulf (Galván et al.,
+2022). Finally, San Jorge Gulf is exposed to urban and industrial
+pollution due to an oil monobuoy from which oil manipulation and general
+oil transport along the Patagonian coast registered several oil spills
+and chronic oil discharges (García-Borboroglu, Boersma, Reyes, \&
+Skewgar, 2008). Other marine systems impacted by oil spill showed an
+important decrease in marine bird populations (Irons, Kendall, Erickson,
+McDonald, \& Lance, 2000), seals and macroalgae (e.g. Paine et al.
+(1996)), with examples of cascading effects throughout the food web
+(Peterson, 2001).
+
+\subsubsection{3.2 Beagle Channel}\label{beagle-channel}
 
 A main anthropogenic stressor in the Beagle Channel is the introduction
-of invasive species (Table 2). Salmonidae were introduced to Tierra del
+of invasive species (Table S2). Salmonidae were introduced to Tierra del
 Fuego in the 1930s. Especially Chinook salmon Oncorhynchus tshawytscha
@@
 dates back to April 2006, and its population has been expanding since
-then (Fernández et al., 2010; Nardi, Fernández, Vanella, \& Chalde,
-2019). Being a top predator Chinook salmon can compete with several
-native species in the Beagle Channel (Correa \& Gross, 2008), and prey
-over native species such as Notothenioids (Eleginops maclovinus,
-Patagonotothen tessellata, P. cornucola, P. sima, Paranotothenia
-magellanica, Harpagifer bispinis), the Atherinidae Odontesthes smitti
-and O. nigricans, the Fuegian sprat Sprattus fuegensis, and larvae of
-king crabs (Lithodes antarcticus and Paralomis granulosa) (Fernández et
-al., 2010). J. E. Ciancio et al. (2008) observed that Chinook salmon in
-the Southern Patagonian Shelf Ecosystem Area primarily feed on sprats
-and display trophic levels comparable to those of intermediate-sized
-fish and cephalopod predators species, showing significant dietary
-overlap with Magellanic penguins (Spheniscus magellanicus). Another
-potential competitor for Chinook salmon in the Beagle Channel is the
-Commerson's dolphin (Cephalorhynchus commersonii), which shares a
-similar diet (Riccialdelli et al., 2013).
+then (Nardi, Fernández, Vanella, \& Chalde, 2019). Being a top predator
+Chinook salmon can compete with several native species in the Beagle
+Channel (Correa \& Gross, 2008), and prey over native species such as
+Notothenioids (Eleginops maclovinus, Patagonotothen tessellata, P.
+cornucola, P. sima, Paranotothenia magellanica, Harpagifer bispinis),
+the Atherinidae Odontesthes smitti and O. nigricans, the Fuegian sprat
+Sprattus fuegensis, and larvae of king crabs (Lithodes antarcticus and
+Paralomis granulosa) (Fernández, Ciancio, Ceballos, Riva-Rossi, \&
+Pascual, 2010). Ciancio, Pascual, Botto, Frere, \& Iribarne (2008)
+observed that Chinook salmon in the Southern Patagonian Shelf Ecosystem
+Area primarily feed on sprats and display trophic levels comparable to
+those of intermediate-sized fish and cephalopod predators species,
+showing significant dietary overlap with Magellanic penguins (Spheniscus
+magellanicus). Another potential competitor for Chinook salmon in the
+Beagle Channel is the Commerson's dolphin (Cephalorhynchus commersonii),
+which shares a similar diet (Riccialdelli et al., 2013).
 
@@
 high levels of perfluorinated compounds in algae, fish, and guano.
-Ferreira et al. (2021) showed that black southern cod in Ushuaia Bay may
-be exposed to endocrine-disrupting compounds from urban and industrial
-pollution. Analía F. Pérez et al. (2020) and Ojeda et al. (2021) found
-microplastics in M. edulis chilensis and Nacella magellanica,
-respectively. These studies link pollutants to Ushuaia (54°48′S 68°18′W)
-and its port and industrial activities. We expect the Beagle Channel
-area closest to the city to be most affected. Contaminants can spread
-through the food web, magnifying the risk to higher-level organisms.
-Fioramonti et al. (2022) studied mercury transfer in three southwest
-Atlantic Ocean food webs and found biodilution in the Beagle Channel and
-Atlantic coast of Tierra del Fuego webs. However, mercury concentrations
-rose with benthivory in these webs, and higher mercury was found in
+Ferreira, Lo Nostro, Fernández, \& Genovese (2021) showed that black
+southern cod in Ushuaia Bay may be exposed to endocrine-disrupting
+compounds from urban and industrial pollution. Pérez et al. (2020) and
+Ojeda et al. (2021) found microplastics in M. edulis chilensis and
+Nacella magellanica, respectively. These studies link pollutants to
+Ushuaia (54°48′S 68°18′W) and its port and industrial activities. We
+expect the Beagle Channel area closest to the city to be most affected.
+Contaminants can spread through the food web, magnifying the risk to
+higher-level organisms. Fioramonti, Ribeiro Guevara, Becker, \&
+Riccialdelli (2022) studied mercury transfer in three southwest Atlantic
+Ocean food webs and found biodilution in the Beagle Channel and Atlantic
+coast of Tierra del Fuego webs. However, mercury concentrations rose
+with benthivory in these webs, and higher mercury was found in
 phytoplankton and Grimothea gregaria. Squat lobsters connect pelagic and
@@
 
-\hypertarget{burdwood-bank}{%
-\subsubsection{3.3 Burdwood Bank}\label{burdwood-bank}}
+\subsubsection{3.3 Burdwood Bank}\label{burdwood-bank}
 
@@
 known to be occurring at a regional scale (e.g.~sea surface warming,
-Franco, Combes, \& González Carman (2020)) (Table 2). Several fisheries
+Franco, Combes, \& González Carman (2020)) (Table S2). Several fisheries
 targeting demersal fishes operate in the vicinity and within the
@@
 management category). The Patagonian fisheries on the toothfish
-Dissostichus eleginoides has gained prominence in recent years (P. A.
-Martínez, Wöhler, \& Troccoli, 2015; L. Allega et al., 2020; Gorini,
-Lukaszewicz, \& Giussi, 2021; Administración de Parques Nacionales,
-2022). Although these are regulated by the Argentinean government,
-incidental catches do occur, where demersal fishes of the genera
-Coelorinchus and Macrourus, seabirds and benthic invertebrates (30+
-taxa) are the most common bycatches (Gaitán \& Marí, 2016; Patricia A.
-Martínez et al., 2022). Noteworthy, among the invertebrates caught, 8
-species are indicator taxa of vulnerable marine ecosystems (Gaitán \&
-Marí, 2016; Schejter \& Albano, 2021). Independent assessments of these
+Dissostichus eleginoides has gained prominence in recent years (L.
+Allega et al., 2020; Gorini, Lukaszewicz, \& Giussi, 2021). Although
+these are regulated by the Argentinean government, incidental catches do
+occur, where demersal fishes of the genera Coelorinchus and Macrourus,
+seabirds and benthic invertebrates (30+ taxa) are the most common
+bycatches (Gaitán \& Marí, 2016; Martínez, Wöhler, Troccoli, Di Marco,
+\& Maydana, 2022). Noteworthy, among the invertebrates caught, 8 species
+are indicator taxa of vulnerable marine ecosystems (Gaitán \& Marí,
+2016; Schejter \& Albano, 2021). Independent assessments of these
 bycatches suggest no significant impact on the communities (Gaitán \&
-Marí, 2016; Patricia A. Martínez et al., 2022). Besides bycatch, species
-of seabirds are being affected by the fishery due to discards, altering
-its diet; the most frequently encountered species are Black-browed
-albatross Thalassarche melanophris, Southern giant petrel Macronectes
-giganteus, Cape petrel Daption capense, Southern royal albatross
-Diomedea epomophora, Northern giant petrel M. halli, and White-chinned
-petrel Procellaria aequinoctialis (Tamini et al., 2023). Nevertheless,
-there is a lack of knowledge considering the species' role in the
-ecosystem and the potential joint effect of both target fishes and
-bycatch in a broader food web framework.
+Marí, 2016; Martínez et al., 2022). Besides bycatch, species of seabirds
+are being affected by the fishery due to discards, altering its diet;
+the most frequently encountered species are Black-browed albatross
+Thalassarche melanophris, Southern giant petrel Macronectes giganteus,
+Cape petrel Daption capense, Southern royal albatross Diomedea
+epomophora, Northern giant petrel M. halli, and White-chinned petrel
+Procellaria aequinoctialis (Tamini et al., 2023). Nevertheless, there is
+a lack of knowledge considering the species' role in the ecosystem and
+the potential joint effect of both target fishes and bycatch in a
+broader food web framework.
 
@@
 
-\hypertarget{scotia-sea}{%
-\subsubsection{3.4 Scotia Sea}\label{scotia-sea}}
+\subsubsection{3.4 Scotia Sea}\label{scotia-sea}
 
@@
 krill abundance; more pronounced in the northern than in the southern
-Scotia Sea (E. J. Murphy et al., 2007; Atkinson et al., 2019). Over the
-past 90 years, the krill also showed an increase in mean body length
-(Atkinson et al., 2019), which may also alter predator-prey interactions
-and allow reaching cooler feeding grounds near the seabed, with the
-potential to link krill to unexpected predators (Schmidt et al., 2011).
-Another consequence of the mentioned environmental stressors, is a
-change in krill distribution due to a southward contraction (Atkinson et
-al., 2019). It is noteworthy here, that the distributional shift has not
+Scotia Sea (E. J. Murphy et al., 2007). Over the past 90 years, the
+krill also showed an increase in mean body length (Atkinson et al.,
+2019), which may also alter predator-prey interactions and allow
+reaching cooler feeding grounds near the seabed, with the potential to
+link krill to unexpected predators (Schmidt et al., 2011). Another
+consequence of the mentioned environmental stressors, is a change in
+krill distribution due to a southward contraction (Atkinson et al.,
+2019). It is noteworthy here, that the distributional shift has not
 affected all species inhabiting the Northern Scotia Sea, and most
@@
 functioning of the food web, from krill-based to non-krill-based, where
-myctophid fishes and squid are playing important roles (Hill, Keeble,
-Atkinson, \& Murphy, 2012; Saunders et al., 2019).
+myctophid fishes and squid are playing important roles (Saunders et al.,
+2019).
 
@@
 
-\hypertarget{potter-cove-antarctica}{%
 \subsubsection{3.5 Potter Cove
-(Antarctica)}\label{potter-cove-antarctica}}
+(Antarctica)}\label{potter-cove-antarctica}
 
@@
 factors driving changes in Potter Cove (Western Antarctic Peninsula)
-(Hendry, Meredith, \& Ducklow, 2018; Chown et al., 2022). Sudden
-environmental changes have occurred, such as sea surface temperature
-increase, salinity decrease, suspended particulate matter loading and
-chlorophyll-a increase, all linked to climatic cycles (Southern Annular
-Mode and El Niño Southern Oscillation) (Schloss et al., 2012; Bers,
-Momo, Schloss, \& Abele, 2013). Particularly, sea warming has produced
-drastic environmental and biological transformations (e.g.~shifts in
-dominance of benthic community) in the Potter Cove ecosystem (Rückamp,
-Braun, Suckro, \& Blindow, 2011; Schloss et al., 2012; María Liliana
-Quartino et al., 2013; Sahade et al., 2015; Hernández, Lopez, Piquet,
-Mac Cormack, \& Buma, 2019), a system highly dependent on sea-ice
-dynamics (Table 2). In Potter Cove, total sea ice cover has decreased
+(Chown et al., 2022). Sudden environmental changes have occurred, such
+as sea surface temperature increase, salinity decrease, suspended
+particulate matter loading and chlorophyll-a increase, all linked to
+climatic cycles (Southern Annular Mode and El Niño Southern Oscillation)
+(Schloss et al., 2012). Particularly, sea warming has produced drastic
+environmental and biological transformations (e.g.~shifts in dominance
+of benthic community) in the Potter Cove ecosystem (Schloss et al.,
+2012; María Liliana Quartino, Deregibus, Campana, Latorre, \& Momo,
+2013; Sahade et al., 2015), a system highly dependent on sea-ice
+dynamics (Table S2). In Potter Cove, total sea ice cover has decreased
 since 1991 (Schloss et al., 2012). Changes in the annual timing of
 landfast ice formation and breakup of the sea ice cover has multiple
-effects on species in the food web (Michel et al., 2019; Rossi et al.,
-2019). Warmer winters and springs result in earlier sea-ice melt,
-causing an abrupt increase in the light available benthic primary
-producers (Dolores Deregibus et al., 2020). Sea ice also mediates
-physical disturbances to the benthos by influencing sedimentation and
-iceberg scouring. These factors affect the production of macroalgae,
-albeit in opposite ways (D. Deregibus et al., 2016, 2017), and
-microphytobenthos (Hoffmann et al., 2019; Braeckman et al., 2021). On
-the other hand, sea ice is an important habitat for diatoms and its
-associated consumers, including copepods and krill (Flores et al.,
-2012), and thus important for bentho-pelagic nutrient and carbon cycling
-during winter. Additionally, a decrease in winter sea ice cover produces
-an increase in physical perturbation on benthic shallow communities in
-coastal shallows due to ice scouring (D. Deregibus et al., 2017). The
-glacier surrounding Potter Cove has been receding at an increasing rate
-since 1950 (Rückamp et al., 2011), which has caused a massive discharge
-of sediment-laden meltwater (Meredith et al., 2018). Large quantities of
-suspended particles affect growth, survival and reproduction of benthic
-species. This had led to a major shift in the benthic community
-structure, from a filter feeders--ascidian domination to a mixed
-assemblage with scavengers and opportunistic species (Pasotti et al.,
-2015; Sahade et al., 2015), and the metabolic balance in benthos went
-from net autotrophy to heterotrophy (Hoffmann et al., 2019; Braeckman et
-al., 2021). Additionally, massive stranding events of the tunicate Salpa
-thompsoni and the euphausiid Euphausia superba (krill) linked to the
-presence of glacial meltwater have been reported (Fuentes et al., 2016).
-Rising temperatures leading to ice and glacial melting has also
-substantial impacts on pelagic primary productivity, since it reduces
-water salinity, affecting water column stratification, light penetration
-and nutrient availability for photosynthesis (Schloss et al., 2012). In
-Potter Cove, changes in biomass of most phytoplankton species have been
-observed under heat wave conditions, resulting in a shift from a
-microplankton to a nanoplankton dominated community (Antoni et al.,
-2020; Latorre et al., 2023). This means that in areas strongly affected
-by glacier melt, the planktonic food web is dominated by the microbial
-loop (ciliates and heterotrophic dinoflagellates preys upon
+effects on species in the food web (Michel et al., 2019). Warmer winters
+and springs result in earlier sea-ice melt, causing an abrupt increase
+in the light available benthic primary producers (Dolores Deregibus et
+al., 2020). Sea ice also mediates physical disturbances to the benthos
+by influencing sedimentation and iceberg scouring. These factors affect
+the production of macroalgae, albeit in opposite ways (D. Deregibus,
+Quartino, Zacher, Campana, \& Barnes, 2017), and microphytobenthos
+(Hoffmann et al., 2019). On the other hand, sea ice is an important
+habitat for diatoms and its associated consumers, including copepods and
+krill (Flores et al., 2012), and thus important for bentho-pelagic
+nutrient and carbon cycling during winter. Additionally, a decrease in
+winter sea ice cover produces an increase in physical perturbation on
+benthic shallow communities in coastal shallows due to ice scouring (D.
+Deregibus et al., 2017). The glacier surrounding Potter Cove has been
+receding at an increasing rate since 1950 (Rückamp, Braun, Suckro, \&
+Blindow, 2011), which has caused a massive discharge of sediment-laden
+meltwater (Meredith et al., 2018). Large quantities of suspended
+particles affect growth, survival and reproduction of benthic species.
+This had led to a major shift in the benthic community structure, from a
+filter feeders--ascidian domination to a mixed assemblage with
+scavengers and opportunistic species (Sahade et al., 2015), and the
+metabolic balance in benthos went from net autotrophy to heterotrophy
+(Braeckman et al., 2021). Additionally, massive stranding events of the
+tunicate Salpa thompsoni and the euphausiid Euphausia superba (krill)
+linked to the presence of glacial meltwater have been reported (Fuentes
+et al., 2016). Rising temperatures leading to ice and glacial melting
+has also substantial impacts on pelagic primary productivity, since it
+reduces water salinity, affecting water column stratification, light
+penetration and nutrient availability for photosynthesis (Schloss et
+al., 2012). In Potter Cove, changes in biomass of most phytoplankton
+species have been observed under heat wave conditions, resulting in a
+shift from a microplankton to a nanoplankton dominated community (Antoni
+et al., 2020; Latorre et al., 2023). This means that in areas strongly
+affected by glacier melt, the planktonic food web is dominated by the
+microbial loop (ciliates and heterotrophic dinoflagellates preys upon
 nanophytoplankton, which are sequentially available prey for small
@@
 
-\hypertarget{weddell-sea-antarctica}{%
 \subsubsection{3.6 Weddell Sea
-(Antarctica)}\label{weddell-sea-antarctica}}
+(Antarctica)}\label{weddell-sea-antarctica}
 
 In the Weddell Sea several stressors have already been triggered by
-global warming effects (Table 2), from which spatial and temporal
+global warming effects (Table S2), from which spatial and temporal
 reduction in sea ice is suggested to be driving changes in pelagic and
-benthic communities (Constable et al., 2014; Julian Gutt et al., 2021).
-Sea ice extent has reached new record lows since the satellite era began
-in 1978. Sea warming has been substantial in recent years: in 2017 the
-mean temperature for February reached 1.45°C, the highest monthly mean
-ever recorded (0.56°C above the climatological mean) (Turner et al.,
-2020). In this context, it has been suggested that Antarctic krill
-Euphausia superba has already declined as a result of productivity
-changes caused by sea ice declines (Atkinson, Siegel, Pakhomov, \&
-Rothery, 2004). Declining sea ice cover allows increased access to krill
-by predators (So Kawaguchi, Nicol, \& Press, 2009), which further
-contributes to decreased krill abundances. This in turn can result in
-reduced carbon export due to decreased fecal pellets from krill (Pauli
-et al., 2021).
+benthic communities (Constable et al., 2014; Gutt et al., 2021). Sea ice
+extent has reached new record lows since the satellite era began in
+1978. Sea warming has been substantial in recent years: in 2017 the mean
+temperature for February reached 1.45°C, the highest monthly mean ever
+recorded (0.56°C above the climatological mean) (Turner et al., 2020).
+In this context, it has been suggested that Antarctic krill Euphausia
+superba has already declined as a result of productivity changes caused
+by sea ice declines (Atkinson, Siegel, Pakhomov, \& Rothery, 2004).
+Declining sea ice cover allows increased access to krill by predators
+(Kawaguchi, Nicol, \& Press, 2009), which further contributes to
+decreased krill abundances. This in turn can result in reduced carbon
+export due to decreased fecal pellets from krill (Pauli et al., 2021).
 
 On the other hand, sea ice loss increases light availability, triggering
-primary production by phytoplankton in the short-term (Pineda-Metz et
-al., 2020; Dinniman, St-Laurent, Arrigo, Hofmann, \& van Dijken, 2023).
-Furthermore, a warmer and more stable water column with a shallow upper
-mixed layer, is expected to enhance the dominance of cryptophytes over
-diatoms which may favor salp populations over krill populations; thereby
-reducing the magnitude of energy transfer to higher trophic levels and
-the seabed (Isla, 2023).
+primary production by phytoplankton in the short-term (Pineda-Metz,
+Gerdes, \& Richter, 2020). Furthermore, a warmer and more stable water
+column with a shallow upper mixed layer, is expected to enhance the
+dominance of cryptophytes over diatoms which may favor salp populations
+over krill populations; thereby reducing the magnitude of energy
+transfer to higher trophic levels and the seabed (Isla, 2023).
 
@@
 significantly affect their post- and future breeding foraging success
-(Siniff et al., 2008; Wege et al., 2021). In addition, the Antarctic
-petrel Thalassoica antarctica, which is one of the most abundant
-seabirds in the area, is a sea ice dependent forager and breeder
-(Orgeira et al., 2021); therefore the loss of this habitat will degrade
-its foraging success and reproductive output over time. The snow petrel
+(Wege, Salas, \& LaRue, 2021). In addition, the Antarctic petrel
+Thalassoica antarctica, which is one of the most abundant seabirds in
+the area, is a sea ice dependent forager and breeder (Orgeira, Alvarez,
+\& Salvó, 2021); therefore the loss of this habitat will degrade its
+foraging success and reproductive output over time. The snow petrel
 Pagodroma nivea also relies heavily on sea ice for foraging and its
@@
 whales, such as the Humpback whale Megaptera novaeangliae, since their
-primary prey resource is the Antarctic krill (Braithwaite et al., 2015).
-Decreased winter ice coverage results in reduced suitable habitat and
-lower krill abundance (Braithwaite et al., 2015), with flow-on effects
-for whale body condition observed historically in harvest data. With
-climate projections indicating ongoing sea ice losses, further threats
-to critical krill populations pose risks to the energy intake and
+primary prey resource is the Antarctic krill (Braithwaite, Meeuwig,
+Letessier, Jenner, \& Brierley, 2015). Decreased winter ice coverage
+results in reduced suitable habitat and lower krill abundance
+(Braithwaite et al., 2015), with flow-on effects for whale body
+condition observed historically in harvest data. With climate
+projections indicating ongoing sea ice losses, further threats to
+critical krill populations pose risks to the energy intake and
 reproductive success and long-term viability of humpback whale
@@
 Iceberg scouring is a major factor in the high biodiversity of benthic
-communities in the Weddell Sea (Julian Gutt \& Starmans, 2001). Even at
-600 m depths, iceberg scouring has a strong effect on the benthic
-environment, disrupting the upper layers of the seabed and removing
-macrofauna. This patchy disturbance and distribution pattern occurs
-roughly every 200 square meters on the Antarctic continental shelf.
-Global warming is predicted to raise iceberg scouring frequency (J. Gutt
-et al., 1996; Julian Gutt, 2001; Dan A. Smale et al., 2008), disrupting
-the environment (J. Gutt et al., 1996; Dan A. Smale \& Barnes, 2008).
-Julian Gutt et al. (2015) expects tipping points are significant due to
-these effects and lack of knowledge.
-
-\hypertarget{from-species-stressors-to-food-web-effects}{%
+communities in the Weddell Sea (Gutt \& Starmans, 2001). Even at 600 m
+depths, iceberg scouring has a strong effect on the benthic environment,
+disrupting the upper layers of the seabed and removing macrofauna. This
+patchy disturbance and distribution pattern occurs roughly every 200
+square meters on the Antarctic continental shelf. Global warming is
+predicted to raise iceberg scouring frequency (Gutt, 2001; Dan A. Smale,
+Brown, Barnes, Fraser, \& Clarke, 2008), disrupting the environment (Dan
+A. Smale \& Barnes, 2008). Gutt et al. (2015) expects tipping points are
+significant due to these effects and lack of knowledge.
+
 \subsection{4. From species' stressors to food web
-effects}\label{from-species-stressors-to-food-web-effects}}
+effects}\label{from-species-stressors-to-food-web-effects}
 
@@
 communities and ecosystems (Montoya et al., 2009; O'Gorman, Fitch, \&
-Crowe, 2012; Bruder, Frainer, Rota, \& Primicerio, 2019; Polazzo,
-Marina, Crettaz-Minaglia, \& Rico, 2022). Environmental and
-anthropogenic stressor effects in the southwest and the Atlantic sector
-of the Southern Ocean have been mostly assessed individually and at the
-organism and/or population, i.e., at the node level (Table 2), with one
-exception: the effect of fisheries in the San Jorge Gulf food web (see
-section below for more details). To address the most plausible stressors
-effects on the selected food webs, given the current information, we
-built hypotheses for each study area. To this aim, we developed a
-theoretical framework considering the following: a) stressor(s), b)
-parameter(s) affected, c) node-level properties of the affected species,
-and d) network-level properties of the food web. We considered that a
-stressor will affect one of the following species' characteristics or
-parameters: metabolism, biomass, distribution, and diet (Figure 2).
-`Metabolism' refers to any change related to metabolic rate, such as
-reproduction, hatching, larval development, growth and mortality, and
-contamination due to pollutants (e.g.~growth effect in filter-feeders
-due to sediment in water column in Potter Cove; endocrine disruption in
-fish due to urban pollutants in Beagle Channel). `Biomass' indicates an
-effect at the population level, where the density/abundance is being
-impacted (e.g.~abundance decreases in macrobenthos due to iceberg
-scouring in Weddell Sea). `Distribution' entails a change at the
+Crowe, 2012; Bruder, Frainer, Rota, \& Primicerio, 2019).
+
+Environmental and anthropogenic stressor effects in the southwest and
+the Atlantic sector of the Southern Ocean have been mostly assessed
+individually and at the organism and/or population, i.e., at the node
+level (Table S2), with one exception: the effect of fisheries in the San
+Jorge Gulf food web (see section below for more details). To address the
+most plausible stressors effects on the selected food webs, given the
+current information, we built hypotheses for each study area. To this
+aim, we developed a theoretical framework considering the following: a)
+stressor(s), b) parameter(s) affected, c) node-level properties of the
+affected species, and d) network-level properties of the food web.
+
+We considered that a stressor will affect one of the following species'
+characteristics or parameters: metabolism, biomass, distribution, and
+diet (Figure 2). `Metabolism' refers to any change related to metabolic
+rate, such as reproduction, hatching, larval development, growth and
+mortality, and contamination due to pollutants (e.g.~growth effect in
+filter-feeders due to sediment in water column in Potter Cove; endocrine
+disruption in fish due to urban pollutants in Beagle Channel). `Biomass'
+indicates an effect at the population level, where the density/abundance
+is being impacted (e.g.~abundance decreases in macrobenthos due to
+iceberg scouring in Weddell Sea). `Distribution' entails a change at the
 population level in the geographic space occupied by a species,
@@
 hypothesized stressor effects on the food webs, and which have been
-previously calculated for the studied food webs (Table 3). At the
+previously calculated for the studied food webs (Table 2). At the
 node-level, we included: a) degree, b) trophic position, c) omnivory
@@
 
+\newpage
 \scriptsize
 
-Table 3. Node and network-level properties used to build hypotheses on
+Table 2. Node and network-level properties used to build hypotheses on
 the stressors' effects.
@@
 \emph{Node-level} & & & \\
-Degre & Number of feeding interactions in which the species participates
-as prey and/or predator. & Perturbations to high-degree species may have
-more significant effects on the food web robustness to perturbations
-than low-degree species. & Dunne, Williams, \& Martinez (2002a); Jordán,
-Benedek, \& Podani (2007) \\
+Degree & Number of feeding interactions in which the species
+participates as prey and/or predator. & Perturbations to high-degree
+species may have more significant effects on the food web robustness to
+perturbations than low-degree species. & Dunne, Williams, \& Martinez
+(2002a); Jordán, Benedek, \& Podani (2007) \\
 Trophic position & Place in the food web relative to the basal resources
@@
 
-\hypertarget{warming-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}{%
-\subsubsection{4.1 Warming effects on food webs in a southwest Atlantic
-- Antarctic
-gradient}\label{warming-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}}
+\subsubsection{4.1 Main stressors effects on food webs in a southwest
+Atlantic - Antarctic
+gradient}\label{main-stressors-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}
 
@@
 Burdwood Bank, which are more influenced by the introduction of an alien
-species and fisheries, respectively (section 3). The main
+species and fisheries, respectively (section 3, Table 3). The main
 characteristics of global warming in the region, and the most plausible
@@
 drivers act in different ways and magnitudes in the studied locations
-along the latitudinal gradient. The above does not mean that there are
-no other stressors interacting with global warming, potentially
-buffering the overall effect on the food web (e.g.~sea warming and
-fishery in San Jorge Gulf). Climate change has led to several
-well-documented impacts on marine species regarding distributional
-shifts induced by warming of marine currents (Wu et al., 2012;
-Poloczanska et al., 2013; Vergés et al., 2014; Vergés et al., 2019).
-Furthermore, warmer temperatures increase species metabolic rates
-(Brown, Gillooly, Allen, Savage, \& West, 2004). Changes in metabolic
-rates can subsequently translate into shifts in species traits (body
-size, Vucic-Pestic, Ehnes, Rall, \& Brose (2011); Klein, Hill, Hinke,
-Phillips, \& Watters (2018){]}, biomass (Perry et al., 2020) and
+along the latitudinal gradient. Despite emphasizing global warming in
+this section, this does not mean that no other stressors act or interact
+with global warming in the study systems, potentially buffering the
+overall effect on the food web (e.g.~sea warming and fishery in San
+Jorge Gulf). Climate change has led to several well-documented impacts
+on marine species regarding distributional shifts induced by warming of
+marine currents (Wu et al., 2012; Poloczanska et al., 2013; Vergés et
+al., 2019). Furthermore, warmer temperatures increase species metabolic
+rates (Brown, Gillooly, Allen, Savage, \& West, 2004). Changes in
+metabolic rates can subsequently translate into shifts in species traits
+(body size, Vucic-Pestic, Ehnes, Rall, \& Brose (2011); Klein, Hill,
+Hinke, Phillips, \& Watters (2018){]}, biomass (Perry et al., 2020) and
 distribution (Kortsch, Primicerio, Fossheim, Dolgov, \& Aschan, 2015).
@@
 San Jorge Gulf food web, the disturbances from the listed stressors are
-expected to spread to many species of the food web. However, it has to
-be acknowledged that the increase in functional diversity driven by the
-range expansion of warm-temperate species is contrary to the process of
-homogenization and loss of functional diversity in the area driven by
-trawl fisheries (Rincón-Díaz et al., 2021).
+expected to spread to many species of the food web (Table 3). However,
+it has to be acknowledged that the increase in functional diversity
+driven by the range expansion of warm-temperate species is contrary to
+the process of homogenization and loss of functional diversity in the
+area driven by trawl fisheries (Rincón-Díaz et al., 2021).
 
@@
 López-López et al. (2022) suggested that the southward distributional
-change of generalist predators from the northern towards southern Scotia
+shift of generalist predators from the northern towards southern Scotia
 Sea increases network connectance of the latter, while decreasing its
@@
 South Georgia Island, we suggest that the declining krill biomass driven
-by sea warming (Atkinson et al., 2019), and ocean acidification and
+by sea warming (Atkinson et al., 2019), ocean acidification and
 pollution synergy (Rowlands et al., 2021), will reduce the energy
@@
 this may be buffered since the dominant copepod species have maintained
-its distribution (Tarling et al., 2018), but most importantly, showed an
-abundance increase in recent decades likely due to reduced predation and
-competition for food (Ward, Tarling, \& Thorpe, 2018). All this is
+their distribution (Tarling et al., 2018), but most importantly, showed
+an abundance increase in recent decades likely due to reduced predation
+and competition for food (Ward, Tarling, \& Thorpe, 2018). All this is
 significant for the structure of the food web given the central role of
@@
 for the krill decrease due to a copepod increase, may buffer against
-structural changes.
+structural changes (Table 3).
 
@@
 and potential trophic cascade effects (Marina et al., 2018) with
-pronounced changes in energy fluxes.
+pronounced changes in energy fluxes (Table 3).
 
@@
 which in turn will impact mid-trophic level predators such as demersal
-fish (Julian Gutt, 2001; Mintenbeck et al., 2012). While we do not
-anticipate large-scale topological changes in the food web, local
-extinctions could lead to such changes, particularly affecting benthic
-species (Julian Gutt \& Piepenburg, 2003). Given that the impacted
-species---whether individually like krill, or collectively like
-macrobenthos---present a mid-trophic position, high biomass and high
-degree (Table S1), we hypothesize that significant shifts in energy
-fluxes will occur. Additionally, the food web's low proportion of
-omnivores suggests reduced system resilience (Table 1), increasing the
-likelihood of regime changes (Julian Gutt et al., 2015).
+fish (Gutt, 2001; Mintenbeck et al., 2012). While we do not anticipate
+large-scale topological changes in the food web, local extinctions could
+lead to such changes, particularly affecting benthic species (Gutt \&
+Piepenburg, 2003). Given that the impacted species---whether
+individually like krill, or collectively like macrobenthos---present a
+mid-trophic position, high biomass and high degree (Table S1), we
+hypothesize that significant shifts in energy fluxes will occur (Table
+3). Additionally, the food web's low proportion of omnivores suggests
+reduced system resilience (Table 1), increasing the likelihood of regime
+changes (Gutt et al., 2015).
 
@@
 Burdwood Bank, are more affected by other anthropogenic stressors than
-warming. Although these areas might be impacted by global warming
-effects due to studies at a regional scale (Franco et al., 2020), to
-date no studies exist for Beagle Channel and Burdwood Bank ecosystems.
-In the Beagle Channel, the introduction of chinook salmon, a non-native
-species, poses a significant risk to the existing food web (Fernández et
-al., 2010). We hypothesize that chinook salmon's predation on Fuegian
-sprat and black southern cod will disrupt the established patterns of
-interaction within the food web. Both of these prey species are crucial
-due to their mid-trophic positions and relatively high abundance (Table
-S1). Moreover, we expect that changes in the black southern cod
-population will have a more significant impact on the food web than
-changes in the Fuegian sprat population, as the black southern cod has a
-higher degree (Table S1). Overall, these disruptions could have
-far-reaching effects on the ecosystem. This is particularly concerning
-given the short path length of the food web, which means that changes
-can quickly propagate through the system, affecting many species and
-potentially destabilizing the entire network. This phenomenon is further
-heightened by the ecosystem's inherent vulnerability to changes at
-mid-trophic levels, often referred to as wasp-waist control. In the
-Burdwood Bank region, fishing activities may be the main stressor
-causing shifts in the food web (Table 2). We hypothesize that a
-combination of factors will destabilize the already fragile ecosystem,
-characterized by low connectance and low omnivory (Table 1). These
-factors include a decline in the biomass of the Patagonian toothfish -a
-key, highly-connected species (Table S1)- as well as smaller changes in
-the biomass of four mid-level fish species, five top-level seabird
-species, and over 30 types of benthic macroinvertebrates due to bycatch
-(Gaitán \& Marí, 2016; Patricia A. Martínez et al., 2022; Tamini et al.,
-2023). Additionally, alterations in the diets of six seabird species,
-caused by discarded catch (Tamini et al., 2023), are expected to disrupt
-the energy flow and further reduce the stability of the food web.
-
-\hypertarget{gaps-and-future-perspectives}{%
+warming. Although these areas are being impacted by sea warming,
+potentially affecting vertebrate and invertebrate species (Franco et
+al., 2020), to date no studies exist for Beagle Channel and Burdwood
+Bank ecosystems. In the Beagle Channel, the introduction of chinook
+salmon, a non-native species, poses a significant risk to the existing
+food web (Fernández et al., 2010). We hypothesize that chinook salmon's
+predation on Fuegian sprat and black southern cod will disrupt the
+established patterns of interaction within the food web. Both of these
+prey species are crucial for food web dynamics due to their mid-trophic
+positions and relatively high abundance (Table S1). Moreover, we expect
+that changes in the black southern cod population will have a more
+significant impact on the food web than changes in the Fuegian sprat
+population, as the black southern cod has a higher degree (Table S1).
+Overall, these disruptions could have far-reaching effects on the
+ecosystem. This is particularly concerning given the short path length
+of the food web, which means that changes can quickly propagate through
+the system, affecting many species and potentially destabilizing the
+entire network. This phenomenon is further heightened by the ecosystem's
+inherent vulnerability to changes at mid-trophic levels, often referred
+to as wasp-waist control (Table 3). In the Burdwood Bank region, fishing
+activities may be the main stressor causing shifts in the food web
+(Table S2). We hypothesize that a combination of factors will
+destabilize the already fragile ecosystem, characterized by low
+connectance and low omnivory (Table 1). These factors include a decline
+in the biomass of the Patagonian toothfish -a key, highly-connected
+species (Table S1)- as well as smaller changes in the biomass of four
+mid-level fish species, five top-level seabird species, and over 30
+types of benthic macroinvertebrates due to bycatch (Gaitán \& Marí,
+2016; Martínez et al., 2022; Tamini et al., 2023). Additionally,
+alterations in the diets of six seabird species, caused by discarded
+catch (Tamini et al., 2023), are expected to disrupt the energy flow and
+further reduce the stability of the food web (Table 3).
+
+\scriptsize
+
+Table 3. Summary of food web (FW) effects according to the main
+stressors reported for each study area. *Industrial trawl fishery ceased
+in 2015 remaining artisanal trawling activity.
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3194}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Study area}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Stressor}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Food web effects}
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+\textbf{San Jorge Gulf} & & \\
+& Fishery* & ↑ FW connectance
+
+↓ FW stability
+
+↓ functional diversity \\
+& Sea warming & Shifts in FW topology
+
+↑ FW connectance
+
+↑ functional diversity \\
+\textbf{Beagle Channel} & & \\
+& Alien species & Shifts in FW topology
+
+↑ spread of perturbations \\
+\textbf{Burdwood Bank} & & \\
+& Fishery & Shifts in main energy fluxes
+
+↓ FW stability \\
+\textbf{Scotia Sea} & & \\
+& Sea warming & ↑ FW connectance
+
+↓ FW modularity
+
+↓ energy transfer to high TLs
+
+↑ spread of perturbation \\
+\textbf{Potter Cove (Antarctica)} & & \\
+& Sea warming & ↓ perturbation spreading \\
+& Sea ice decline + glacial retreat & Differential impacts, by
+substrate: hard (HS) or soft (SS)
+
+↑ FW chain length \& ↑ trophic niches (HS)
+
+↑ FW fragility \& trophic cascades (SS) \\
+\textbf{Weddell Sea (Antarctica)} & & \\
+& Sea ice decline + iceberg scouring & Shifts in main energy fluxes
+
+↑ likelihood of regime shifts
+
+↓ resilience \\
+\end{longtable}
+
+\normalsize
+
 \subsection{5. Gaps and future
-perspectives}\label{gaps-and-future-perspectives}}
-
-Since this review deals with qualitative data regarding, not only
-prey-predator interactions but also the stressor effect, adding
-quantitative data to the food webs (i.e.~interaction strength
-estimations) and/or to the stressor effect (i.e.~magnitude) will provide
-a better comprehension of how species' stressors might be translated
-into food web effects. In this context, quantitative food webs will be
-useful if they reflect energy fluxes among species (Nilsson \& McCann,
-2016). Emerging methods have been proposed in this sense promising ways
-to estimate shifts in species interactions within food webs (Gauzens et
-al., 2019; Gellner, McCann, \& Hastings, 2023). These shifts, in turn,
-could lead to changes in energy fluxes within the ecosystem.
-
-As summarized in Table 2, in the selected study areas of the southwest
-Atlantic - Antarctic latitudinal gradient several stressors might be
-directly affecting consumer's diets, triggered by modified environmental
-conditions (sea warming, reduced sea ice extent), new habitats (due to
-distributional shifts) and/or new species (alien species). Moreover, the
-population trend of important species is also changing (e.g., Funes
-(2020), Constable et al. (2014), Pineda-Metz (2019), Hindell et al.
-(2020), Woods et al. (2023)) driving changes in their roles as either
-predators or prey (e.g. Belleggia et al. (2017), Pasti et al. (2021)).
-These diet and biomass updates, either considered as a short or
-long-term effect, should be contemplated in order to generate reliable
-predictions of food web responses to multiple stressors in the southwest
-Atlantic - Antarctic region. Examples of these interactions between
-diet, relative biomass, and their effects on food webs at different
-temporal scales include biological invasions and trawl fisheries. Both
-stressors, in the short term, increase the complexity of food webs by
-adding generalist predators and/or new prey (e.g., Cordone, Galván, \&
-Momo (2023)) or by enabling discard consumption (e.g., Funes et al.
-(2022)). However, in the long term, both stressors may lead to the
-biological extinction of certain prey and competitors (e.g., Anton et
-al. (2019)) or a significant reduction in target and incidental catch
-species (e.g., Dulvy et al. (2014)), thereby promoting food web
-simplification.
-
-Regarding data gaps, we should mention the cases for Beagle Channel and
-Burdwood Bank ecosystems, where almost no information exists for the
-impact of global warming effects (sea warming, glacial retreat, ocean
-acidification) in natural populations/communities, though warming
-effects have been shown at a regional scale (Franco et al., 2020). It is
-worth mentioning that in Beagle Channel recent experimental studies have
-tested the tolerance of fishes to scenarios of sea warming and/or
-acidification suggesting potential metabolic impacts (María Eugenia
-Lattuca, Boy, Vanella, Barrantes, \& Fernández, 2018; María E. Lattuca
-et al., 2023).
+perspectives}\label{gaps-and-future-perspectives}
+
+In the selected study areas along the southwest Atlantic to Antarctic
+latitudinal gradient, several stressors may directly affect consumers'
+diets triggered by modified environmental conditions (sea warming,
+reduced sea ice extent) and new species (due to species' distributional
+shifts and introductions). Moreover, the population trends (biomasses
+and abundances) of important species are also changing (Hindell et al.,
+2020; Funes, 2020; Woods et al., 2023) driving shifts in their roles as
+either predators or prey (e.g. Belleggia, Giberto, \& Bremec (2017),
+Pasti et al. (2021)). These diet and biomass shifts should be
+investigated in order to generate reliable predictions of food web
+responses to multiple stressors in the southwest Atlantic - Antarctic
+region. One could argue that both shifts might increase the complexity
+of food webs in the short term by adding generalist predators or new
+prey (e.g., Cordone, Galván, \& Momo (2023)) or by enabling discard
+consumption (e.g. Funes et al. (2022)). However, in the long term, both
+stressors may lead to the biological extinction of certain prey and
+competitors (e.g. Anton et al. (2019)) or a significant reduction in
+target and incidental catch species (e.g. Dulvy et al. (2014)), thereby
+promoting food web simplification.
+
+Since this review deals with qualitative data of prey-predator
+interactions and stressor effects influencing them, adding quantitative
+data to the food webs (i.e.~interaction strength) and to the stressors
+(i.e.~magnitude) would lead to a better comprehension of how a given
+stressor acts on specific species which might translate into food web
+effects. In this context, it would be useful to develop quantitative
+food web models where the strength of interactions reflect energy fluxes
+among species (Nilsson \& McCann, 2016; Kortsch et al., 2021). Emerging
+methods such as bioenergetic food web modeling have been proposed in
+this regard and present promising ways to estimate shifts in species
+interactions within food webs as a response to stressors (Gauzens,
+Brose, Delmas, \& Berti, n.d.; Gellner, McCann, \& Hastings, 2023).
+Shifts that can lead to changes in overall ecosystem functioning and
+stability.
+
+Regarding knowledge and data gaps on species and their stressors,
+especially the Beagle Channel and Burdwood Bank are poorly sampled study
+regions. Almost no information exists on the impact of global warming
+effects (sea warming, glacial retreat, ocean acidification) on
+communities in these ecosystems, though warming of mid-water and bottom
+layers have been shown at a regional scale (Franco et al., 2020). Yet in
+Beagle Channel recent experimental studies have tested the tolerance of
+fishes to scenarios of sea warming and/or acidification suggesting
+potential metabolic impacts on species (María Eugenia Lattuca, Boy,
+Vanella, Barrantes, \& Fernández, 2018; María E. Lattuca et al., 2023).
 
 Analyzing the impact of multiple stressors through observational studies
-can be challenging (Julian Gutt et al., 2021). This complexity arises
-from the potential for antagonistic effects, where impacts cancel each
+is challenging (Gutt et al., 2021). This complexity arises partly
+because of potential for antagonistic effects, where impacts cancel each
 other out, or synergistic effects, where the combined impact is greater
-than the sum of individual effects (Crain et al., 2008; Boyd, Lennartz,
-Glover, \& Doney, 2015; Côté et al., 2016). These effects are further
+than the sum of individual effects (Boyd, Lennartz, Glover, \& Doney,
+2015; Côté et al., 2016). Moreover, these interactive effects are
 complicated to handle in the framework of complex food webs. The number
-of pathways of effect through which a species may affect or be affected
-by other species, and through which stressors may permeate communities,
-increases exponentially with the number of species and interactions in a
-network (Menge, 1995). In this sense, Beauchesne, Cazelles, Archambault,
-Dee, \& Gravel (2021) have developed a theory-grounded approach using
-motifs (i.e.~groups of species that, when put together, construct whole
-food webs) to simplify food webs; methodology that could be applied to
-our food web study cases.
-
-\hypertarget{conclusions}{%
-\subsection{Conclusions}\label{conclusions}}
-
-In the light of cumulative knowledge on how global warming and emerging
-stressors are affecting species inhabiting marine ecosystems in the
-Southern Hemisphere (e.g. Julian Gutt et al. (2021), Galván et al.
-(2022)), there is a need to better understand these changes in a more
-real framework where species interact and, consequently, might spread
-the stressor effect to other species in complex ways. To this end, we
-have reviewed the main environmental and anthropogenic stressors acting
-in six different areas along a large-scale latitudinal gradient, from
-temperate to Antarctic ecosystems. Using a theoretical framework that
-combines node (species) and network (food web) level data, we show how
-warming effects might affect food web structure and functioning. These
-qualitative predictions are intended to serve as the basis to studies
-that quantify how much the ongoing stressors are affecting food web
-properties, such as energy fluxes and stability, in marine ecosystems of
-the Southern Hemisphere.
-
-\hypertarget{references}{%
-\subsection*{References}\label{references}}
+of pathways through which a species may affect or be affected by other
+species, and through which stressors may permeate communities, increases
+exponentially with the number of species and interactions in a network
+(Menge, 1995). To tackle this complexity, Beauchesne, Cazelles,
+Archambault, Dee, \& Gravel (2021) developed a theory-grounded approach
+using motifs (i.e.~groups of species that, when put together, construct
+whole food webs) to simplify food webs; a methodology that could be
+applied to our food web study cases.
+
+\subsection{Conclusions}\label{conclusions}
+
+We have reviewed the main environmental and anthropogenic stressors
+acting in six different areas along a large-scale latitudinal gradient,
+from temperate Atlantic to cold Antarctic ecosystems. Using a
+theoretical framework that combines species and food web level data, we
+suggest how warming effects may impact food web structure and
+functioning. These qualitative predictions are intended to serve as the
+basis for future studies in marine ecosystems of the Southern Hemisphere
+that aim at quantifying the magnitude of these stressors and how they
+are affecting quantitative food web properties, such as energy fluxes
+and stability. There is an urgent need to assess these changes using a
+holistic and quantitative framework where the magnitude of stressors and
+species interactions are taken into account.
+
+\subsection{Acknowledgements}\label{acknowledgements}
+
+This review is a product of the project ``¿Cuáles son los efectos de los
+cambios ambientales antropogénicos en las interacciones tróficas de las
+comunidades de los ecosistemas marinos en el gradiente latitudinal
+Atlántico Sudoccidental - Antártida?'', funded by Consejo Nacional de
+Investigaciones Científicas (CONICET, code PIP 2022-2024 \#0907).
+
+\subsection*{References}\label{references}
 \addcontentsline{toc}{subsection}{References}
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Acha2004}{}}%
+\bibitem[\citeproctext]{ref-Acha2004}
 Acha, E. M., Mianzan, H. W., Guerrero, R. A., Favero, M., \& Bava, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-APN2022}{}}%
+\bibitem[\citeproctext]{ref-APN2022}
 Administración de Parques Nacionales. (2022). {Plan de gestión AMP
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Albert2002}{}}%
+\bibitem[\citeproctext]{ref-Albert2002}
 Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Allega2019}{}}%
+\bibitem[\citeproctext]{ref-Allega2019}
 Allega, Lucrecia, Braverman, M. S., Cabreira, A. G., Campodónico, S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Allega2020}{}}%
+\bibitem[\citeproctext]{ref-Allega2020}
 Allega, L., Braverman, M., Campodónico, S., Carozza, C. R., Cepeda, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Anton2019}{}}%
+\bibitem[\citeproctext]{ref-Anton2019}
 Anton, A., Geraldi, N. R., Lovelock, C. E., Apostolaki, E. T., Bennett,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Antoni2020}{}}%
+\bibitem[\citeproctext]{ref-Antoni2020}
 Antoni, J. S., Almandoz, G. O., Ferrario, M. E., Hernando, M. P.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Atkinson2004}{}}%
+\bibitem[\citeproctext]{ref-Atkinson2004}
 Atkinson, A., Siegel, V., Pakhomov, E., \& Rothery, P. (2004). Long-term
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baiser2012}{}}%
-Baiser, B., Gotelli, N. J., Buckley, H. L., Miller, T. E., \& Ellison,
-A. M. (2012). Geographic variation in network structure of a nearctic
-aquatic food web. \emph{Global Ecology and Biogeography}, \emph{21}(5),
-579--591.
-doi:\href{https://doi.org/10.1111/j.1466-8238.2011.00705.x}{10.1111/j.1466-8238.2011.00705.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Balech2008}{}}%
+\bibitem[\citeproctext]{ref-Balech2008}
 Balech, E., \& Ehrlich, M. D. (2008). {Esquema biogeográfico del Mar
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ballerini2014}{}}%
-Ballerini, T., Hofmann, E. E., Ainley, D. G., Daly, K., Marrari, M.,
-Ribic, C. A., \ldots{} Steele, J. H. (2014). Productivity and linkages
-of the food web of the southern region of the western {Antarctic
-Peninsula} continental shelf. \emph{Progress in Oceanography},
-\emph{122}, 10--29.
-doi:\href{https://doi.org/10.1016/j.pocean.2013.11.007}{10.1016/j.pocean.2013.11.007}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bartley2019}{}}%
+\bibitem[\citeproctext]{ref-Bartley2019}
 Bartley, T. J., McCann, K. S., Bieg, C., Cazelles, K., Granados, M.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Bauer2022}{}}%
+\bibitem[\citeproctext]{ref-Bauer2022}
 Bauer, B., Berti, E., Ryser, R., Gauzens, B., Hirt, M. R., Rosenbaum,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Beauchesne2021}{}}%
+\bibitem[\citeproctext]{ref-Beauchesne2021}
 Beauchesne, D., Cazelles, K., Archambault, P., Dee, L. E., \& Gravel, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Belgrano2005}{}}%
+\bibitem[\citeproctext]{ref-Belgrano2005}
 Belgrano, A., Scharler, S. E. R. C. U. M., Scharler, U. M., Dunne, J.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Belleggia2017}{}}%
+\bibitem[\citeproctext]{ref-Belleggia2017}
 Belleggia, M., Giberto, D., \& Bremec, C. (2017). Adaptation of diet in
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Bers2013}{}}%
-Bers, A. V., Momo, F., Schloss, I. R., \& Abele, D. (2013). Analysis of
-trends and sudden changes in long-term environmental data from {King
-George Island} ({Antarctica}): Relationships between global climatic
-oscillations and local system response. \emph{Climatic Change},
-\emph{116}(3), 789--803.
-doi:\href{https://doi.org/10.1007/s10584-012-0523-4}{10.1007/s10584-012-0523-4}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bogazzi2005}{}}%
-Bogazzi, E., Baldoni, A., Rivas, A., Martos, P., Reta, R., Orensanz, J.
-M. (lobo)., \ldots{} Werner, F. (2005). Spatial correspondence between
-areas of concentration of {Patagonian} scallop ({Zygochlamys}
-patagonica) and frontal systems in the southwestern {Atlantic}.
-\emph{Fisheries Oceanography}, \emph{14}(5), 359--376.
-doi:\href{https://doi.org/10.1111/j.1365-2419.2005.00340.x}{10.1111/j.1365-2419.2005.00340.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bovcon2013}{}}%
+\bibitem[\citeproctext]{ref-Bovcon2013}
 Bovcon, N. D., Góngora, M. E., Marinao, C., \& González-Zevallos, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Boyd2015}{}}%
+\bibitem[\citeproctext]{ref-Boyd2015}
 Boyd, P. W., Lennartz, S. T., Glover, D. M., \& Doney, S. C. (2015).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Braeckman2021}{}}%
+\bibitem[\citeproctext]{ref-Braeckman2021}
 Braeckman, U., Pasotti, F., Hoffmann, R., Vázquez, S., Wulff, A.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Braithwaite2015}{}}%
+\bibitem[\citeproctext]{ref-Braithwaite2015}
 Braithwaite, J. E., Meeuwig, J. J., Letessier, T. B., Jenner, K. C. S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Brown2004}{}}%
+\bibitem[\citeproctext]{ref-Brown2004}
 Brown, J. H., Gillooly, J. F., Allen, A. P., Savage, V. M., \& West, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Bruder2019}{}}%
+\bibitem[\citeproctext]{ref-Bruder2019}
 Bruder, A., Frainer, A., Rota, T., \& Primicerio, R. (2019). The
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Bruno2023}{}}%
+\bibitem[\citeproctext]{ref-Bruno2023}
 Bruno, D. O., Riccialdelli, L., Acha, E. M., \& Fernández, D. A. (2023).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Buskey2016}{}}%
-Buskey, E. J., White, H. K., \& Esbaugh, A. J. (2016). Impact of {Oil
-Spills} on {Marine Life} in the {Gulf} of {Mexico}: {EFFECTS ON
-PLANKTON}, {NEKTON}, {AND DEEP-SEA BENTHOS}. \emph{Oceanography},
-\emph{29}(3), 174--181. Retrieved from
-\url{https://www.jstor.org/stable/24862719}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Campana2018}{}}%
-Campana, G. L., Zacher, K., Deregibus, D., Momo, F. R., Wiencke, C., \&
-Quartino, M. L. (2018). Succession of {Antarctic} benthic algae ({Potter
-Cove}, {South Shetland Islands}): Structural patterns and glacial impact
-over a four-year period. \emph{Polar Biology}, \emph{41}(2), 377--396.
-doi:\href{https://doi.org/10.1007/s00300-017-2197-x}{10.1007/s00300-017-2197-x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Chown2022}{}}%
+\bibitem[\citeproctext]{ref-Chown2022}
 Chown, S. L., Leihy, R. I., Naish, T. R., Brooks, C. M., Convey, P.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ciancio2008}{}}%
+\bibitem[\citeproctext]{ref-Ciancio2008}
 Ciancio, J. E., Pascual, M. A., Botto, F., Frere, E., \& Iribarne, O.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ciancio2010}{}}%
-Ciancio, J., Beauchamp, D. A., \& Pascual, M. (2010). Marine effect of
-introduced salmonids: {Prey} consumption by exotic steelhead and
-anadromous brown trout in the {Patagonian Continental Shelf}.
-\emph{Limnology and Oceanography}, \emph{55}(5), 2181--2192.
-doi:\href{https://doi.org/10.4319/lo.2010.55.5.2181}{10.4319/lo.2010.55.5.2181}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Cirtwill2015}{}}%
+\bibitem[\citeproctext]{ref-Cirtwill2015}
 Cirtwill, A. R., Stouffer, D. B., \& Romanuk, T. N. (2015). Latitudinal
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Clark2013}{}}%
-Clark, G. F., Stark, J. S., Johnston, E. L., Runcie, J. W., Goldsworthy,
-P. M., Raymond, B., \& Riddle, M. J. (2013). Light-driven tipping points
-in polar ecosystems. \emph{Global Change Biology}, \emph{19}(12),
-3749--3761.
-doi:\href{https://doi.org/10.1111/gcb.12337}{10.1111/gcb.12337}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Collins2010}{}}%
+\bibitem[\citeproctext]{ref-Collins2010}
 Collins, M. A., Brickle, P., Brown, J., \& Belchier, M. (2010). Chapter
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Commendatore2012}{}}%
+\bibitem[\citeproctext]{ref-Commendatore2012}
 Commendatore, M. G., Nievas, M. L., Amin, O., \& Esteves, J. L. (2012).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Constable2014}{}}%
+\bibitem[\citeproctext]{ref-Constable2014}
 Constable, A. J., Melbourne-Thomas, J., Corney, S. P., Arrigo, K. R.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cordone2023}{}}%
+\bibitem[\citeproctext]{ref-Cordone2023}
 Cordone, G., Galván, D. E., \& Momo, F. R. (2023). Impacts of an
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cordone2020}{}}%
+\bibitem[\citeproctext]{ref-Cordone2020}
 Cordone, G., Salinas, V., Marina, T. I., Doyle, S. R., Pasotti, F.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Correa2008}{}}%
+\bibitem[\citeproctext]{ref-Correa2008}
 Correa, C., \& Gross, M. R. (2008). Chinook salmon invade southern
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cossi2021}{}}%
+\bibitem[\citeproctext]{ref-Cossi2021}
 Cossi, P. F., Ojeda, M., Chiesa, I. L., Rimondino, G. N., Fraysse, C.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cote2016}{}}%
+\bibitem[\citeproctext]{ref-Cote2016}
 Côté, I. M., Darling, E. S., \& Brown, C. J. (2016). Interactions among
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Crain2008}{}}%
-Crain, C. M., Kroeker, K., \& Halpern, B. S. (2008). Interactive and
-cumulative effects of multiple human stressors in marine systems.
-\emph{Ecology Letters}, \emph{11}(12), 1304--1315.
-doi:\href{https://doi.org/10.1111/j.1461-0248.2008.01253.x}{10.1111/j.1461-0248.2008.01253.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-DAlelio2016}{}}%
-D'Alelio, D., Libralato, S., Wyatt, T., \& Ribera d'Alcalà, M. (2016).
-Ecological-network models link diversity, structure and function in the
-plankton food-web. \emph{Scientific Reports}, \emph{6}(1), 21806.
-doi:\href{https://doi.org/10.1038/srep21806}{10.1038/srep21806}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dayton1990}{}}%
-Dayton, P. K. (1990). Polar {Benthos}. In \emph{Polar {Oceanography Part
-B}: {Chemistry}, {Biology} and {Geology}} (W.O. Smith, Jr., pp.
-631--685). {London}: {Academic Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-deHaro2022}{}}%
+\bibitem[\citeproctext]{ref-deHaro2022}
 de Haro, J. C., Perez Orsi, H., Cané, S., Di Pangracio, A., Falabella,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Deppeler2020}{}}%
-Deppeler, S., Schulz, K. G., Hancock, A., Pascoe, P., McKinlay, J., \&
-Davidson, A. (2020). Ocean acidification reduces growth and grazing
-impact of {Antarctic} heterotrophic nanoflagellates.
-\emph{Biogeosciences}, \emph{17}(16), 4153--4171.
-doi:\href{https://doi.org/10.5194/bg-17-4153-2020}{10.5194/bg-17-4153-2020}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2023}{}}%
+\bibitem[\citeproctext]{ref-Deregibus2023}
 Deregibus, Dolores, Campana, G. L., Neder, C., Barnes, D. K. A., Zacher,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2016}{}}%
-Deregibus, D., Quartino, M. L., Campana, G. L., Momo, F. R., Wiencke,
-C., \& Zacher, K. (2016). Photosynthetic light requirements and vertical
-distribution of macroalgae in newly ice-free areas in {Potter Cove},
-{South Shetland Islands}, {Antarctica}. \emph{Polar Biology},
-\emph{39}(1), 153--166.
-doi:\href{https://doi.org/10.1007/s00300-015-1679-y}{10.1007/s00300-015-1679-y}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2017}{}}%
+\bibitem[\citeproctext]{ref-Deregibus2017}
 Deregibus, D., Quartino, M. L., Zacher, K., Campana, G. L., \& Barnes,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2020}{}}%
+\bibitem[\citeproctext]{ref-Deregibus2020}
 Deregibus, Dolores, Zacher, K., Bartsch, I., Campana, G. L., Momo, F.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-DiMauro2022}{}}%
+\bibitem[\citeproctext]{ref-DiMauro2022}
 Di Mauro, R., Castillo, S., Pérez, A., Iachetti, C. M., Silva, L.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dinniman2023}{}}%
-Dinniman, M. S., St-Laurent, P., Arrigo, K. R., Hofmann, E. E., \& van
-Dijken, G. L. (2023). Sensitivity of the {Relationship Between Antarctic
-Ice Shelves} and {Iron Supply} to {Projected Changes} in the
-{Atmospheric Forcing}. \emph{Journal of Geophysical Research: Oceans},
-\emph{128}(2), e2022JC019210.
-doi:\href{https://doi.org/10.1029/2022JC019210}{10.1029/2022JC019210}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dodino2022}{}}%
+\bibitem[\citeproctext]{ref-Dodino2022}
 Dodino, S., Riccialdelli, L., Polito, M. J., Pütz, K., Brasso, R. L., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Duarte2011}{}}%
+\bibitem[\citeproctext]{ref-Duarte2011}
 Duarte, C. A., Giarratano, E., Amin, O. A., \& Comoglio, L. I. (2011).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Duffy2007}{}}%
+\bibitem[\citeproctext]{ref-Duffy2007}
 Duffy, J. E., Cardinale, B. J., France, K. E., McIntyre, P. B.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dulvy2014}{}}%
+\bibitem[\citeproctext]{ref-Dulvy2014}
 Dulvy, N. K., Fowler, S. L., Musick, J. A., Cavanagh, R. D., Kyne, P.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002a}{}}%
+\bibitem[\citeproctext]{ref-Dunne2002a}
 Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Food-web
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
+\bibitem[\citeproctext]{ref-Dunne2002}
 Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). Network
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Fernandez2010}{}}%
+\bibitem[\citeproctext]{ref-Fernandez2010}
 Fernández, D. A., Ciancio, J., Ceballos, S. G., Riva-Rossi, C., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Franco2020}{}}%
+\bibitem[\citeproctext]{ref-Franco2020}
 Franco, B. C., Combes, V., \& González Carman, V. (2020). Subsurface
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Frelat2022}{}}%
-Frelat, R., Kortsch, S., Kröncke, I., Neumann, H., Nordström, M. C.,
-Olivier, P. E. N., \& Sell, A. F. (2022). Food web structure and
-community composition: A comparison across space and time in the {North
-Sea}. \emph{Ecography}, \emph{2022}(2), ecog.05945.
-doi:\href{https://doi.org/10.1111/ecog.05945}{10.1111/ecog.05945}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fretwell2023}{}}%
+\bibitem[\citeproctext]{ref-Fretwell2023}
 Fretwell, P. T., Boutet, A., \& Ratcliffe, N. (2023). Record low 2022
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Fuentes2016}{}}%
+\bibitem[\citeproctext]{ref-Fuentes2016}
 Fuentes, V., Alurralde, G., Meyer, B., Aguirre, G. E., Canepa, A.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Funes2020}{}}%
+\bibitem[\citeproctext]{ref-Funes2020}
 Funes, M. (2020, March). \emph{Efectos de la pesca de arrastre sobre la
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Funes2019}{}}%
+\bibitem[\citeproctext]{ref-Funes2019}
 Funes, M., Marinao, C., \& Galván, D. E. (2019). Does trawl fisheries
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Funes2022}{}}%
+\bibitem[\citeproctext]{ref-Funes2022}
 Funes, M., Saravia, L. A., Cordone, G., Iribarne, O. O., \& Galván, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gaitan2016}{}}%
+\bibitem[\citeproctext]{ref-Gaitan2016}
 Gaitán, E., \& Marí, N. (2016). {Análisis de las comunidades bentónicas
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Garcia-Borboroglu2008}{}}%
+\bibitem[\citeproctext]{ref-Garcia-Borboroglu2008}
 García-Borboroglu, P., Boersma, P. D., Reyes, L., \& Skewgar, E. (2008).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Garrott1993}{}}%
-Garrott, R. A., Eberhardt, L. L., \& Burn, D. M. (1993). Mortality of
-{Sea Otters} in {Prince William Sound Following} the {Exxon Valdez Oil
-Spill}. \emph{Marine Mammal Science}, \emph{9}(4), 343--359.
-doi:\href{https://doi.org/10.1111/j.1748-7692.1993.tb00468.x}{10.1111/j.1748-7692.1993.tb00468.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gauzens2019}{}}%
-Gauzens, B., Barnes, A., Giling, D. P., Hines, J., Jochum, M., Lefcheck,
-J. S., \ldots{} Brose, U. (2019). Fluxweb: {An R} package to easily
-estimate energy fluxes in food webs. \emph{Methods in Ecology and
-Evolution}, \emph{10}(2), 270--279.
-doi:\href{https://doi.org/10.1111/2041-210X.13109}{10.1111/2041-210X.13109}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gellner2023}{}}%
+\bibitem[\citeproctext]{ref-Gauzens2023}
+Gauzens, B., Brose, U., Delmas, E., \& Berti, E. (n.d.). {ATNr}:
+{Allometric Trophic Network} models in {R}. \emph{Methods in Ecology and
+Evolution}, \emph{n/a}(n/a).
+doi:\href{https://doi.org/10.1111/2041-210X.14212}{10.1111/2041-210X.14212}
+
+\bibitem[\citeproctext]{ref-Gellner2023}
 Gellner, G., McCann, K., \& Hastings, A. (2023). Stable diverse food
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Giarratano2010}{}}%
-Giarratano, E., \& Amin, O. A. (2010). Heavy metals monitoring in the
-southernmost mussel farm of the world ({Beagle Channel}, {Argentina}).
-\emph{Ecotoxicology and Environmental Safety}, \emph{73}(6), 1378--1384.
-doi:\href{https://doi.org/10.1016/j.ecoenv.2010.06.023}{10.1016/j.ecoenv.2010.06.023}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gil2011}{}}%
+\bibitem[\citeproctext]{ref-Gil2011}
 Gil, M. N., Torres, A. I., Amin, O., \& Esteves, J. L. (2011).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Glembocki2015}{}}%
+\bibitem[\citeproctext]{ref-Glembocki2015}
 Glembocki, N. G., Williams, G. N., Góngora, M. E., Gagliardini, D. A.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Glorioso1995}{}}%
-Glorioso, P. D., \& Flather, R. A. (1995). A barotropic model of the
-currents off {SE South America}. \emph{Journal of Geophysical Research:
-Oceans}, \emph{100}(C7), 13427--13440.
-doi:\href{https://doi.org/10.1029/95JC00942}{10.1029/95JC00942}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gongora2009}{}}%
-Góngora, María E., Bovcon, N. D., \& Cochia, P. D. (2009). Ictiofauna
-capturada incidentalmente en la pesquería de langostino patagónico
-{Pleoticus} muelleri {Bate}, 1888. \emph{Revista de Biología Marina y
-Oceanografía}, \emph{44}(3), 583--593.
-doi:\href{https://doi.org/10.4067/S0718-19572009000300006}{10.4067/S0718-19572009000300006}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gongora2012}{}}%
-Góngora, María Eva, González-Zevallos, D., Pettovello, A., \& Mendía, L.
+\bibitem[\citeproctext]{ref-Gongora2012}
+Góngora, M. E., González-Zevallos, D., Pettovello, A., \& Mendía, L.
 (2012). Caracterización de las principales pesquerías del golfo {San
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gonzalez-Zevallos2006}{}}%
+\bibitem[\citeproctext]{ref-Gonzalez-Zevallos2006}
 González-Zevallos, D., \& Yorio, P. (2006). Seabird use of discards and
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gonzalez-Zevallos2011}{}}%
-González-Zevallos, D., \& Yorio, P. (2011). Consumption of discards and
-interactions between {Black-browed Albatrosses} ({Thalassarche}
-melanophrys) and {Kelp Gulls} ({Larus} dominicanus) at trawl fisheries
-in {Golfo San Jorge}, {Argentina}. \emph{Journal of Ornithology},
-\emph{152}(4), 827--838.
-doi:\href{https://doi.org/10.1007/s10336-011-0657-6}{10.1007/s10336-011-0657-6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gorini2021}{}}%
+\bibitem[\citeproctext]{ref-Gorini2021}
 Gorini, F. L., Lukaszewicz, G., \& Giussi, A. R. (2021).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Guihou2020}{}}%
+\bibitem[\citeproctext]{ref-Guihou2020}
 Guihou, K., Piola, A. R., Palma, E. D., \& Chidichimo, M. P. (2020).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt2001a}{}}%
-Gutt, Julian. (2001). On the direct impact of ice on marine benthic
+\bibitem[\citeproctext]{ref-Gutt2001a}
+Gutt, J. (2001). On the direct impact of ice on marine benthic
 communities, a review. \emph{Polar Biology}, \emph{24}(8), 553--564.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt2015}{}}%
-Gutt, Julian, Bertler, N., Bracegirdle, T. J., Buschmann, A., Comiso,
-J., Hosie, G., \ldots{} Xavier, J. C. (2015). The {Southern Ocean}
-ecosystem under multiple climate change stresses - an integrated
-circumpolar assessment. \emph{Global Change Biology}, \emph{21}(4),
-1434--1453.
+\bibitem[\citeproctext]{ref-Gutt2015}
+Gutt, J., Bertler, N., Bracegirdle, T. J., Buschmann, A., Comiso, J.,
+Hosie, G., \ldots{} Xavier, J. C. (2015). The {Southern Ocean} ecosystem
+under multiple climate change stresses - an integrated circumpolar
+assessment. \emph{Global Change Biology}, \emph{21}(4), 1434--1453.
 doi:\href{https://doi.org/10.1111/gcb.12794}{10.1111/gcb.12794}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt2021}{}}%
-Gutt, Julian, Isla, E., Xavier, J. C., Adams, B. J., Ahn, I.-Y., Cheng,
+\bibitem[\citeproctext]{ref-Gutt2021}
+Gutt, J., Isla, E., Xavier, J. C., Adams, B. J., Ahn, I.-Y., Cheng,
 C.-H. C., \ldots{} Wall, D. H. (2021). Antarctic ecosystems in
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt2003}{}}%
-Gutt, Julian, \& Piepenburg, D. (2003). Scale-dependent impact on
-diversity of {Antarctic} benthos caused by grounding of icebergs.
-\emph{Marine Ecology Progress Series}, \emph{253}, 77--83.
+\bibitem[\citeproctext]{ref-Gutt2003}
+Gutt, J., \& Piepenburg, D. (2003). Scale-dependent impact on diversity
+of {Antarctic} benthos caused by grounding of icebergs. \emph{Marine
+Ecology Progress Series}, \emph{253}, 77--83.
 doi:\href{https://doi.org/10.3354/meps253077}{10.3354/meps253077}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt2001}{}}%
-Gutt, Julian, \& Starmans, A. (2001). Quantification of iceberg impact
-and benthic recolonisation patterns in the {Weddell Sea} ({Antarctica}).
+\bibitem[\citeproctext]{ref-Gutt2001}
+Gutt, J., \& Starmans, A. (2001). Quantification of iceberg impact and
+benthic recolonisation patterns in the {Weddell Sea} ({Antarctica}).
 \emph{Polar Biology}, \emph{24}(8), 615--619.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gutt1996}{}}%
-Gutt, J., Starmans, A., \& Dieckmann, G. (1996). Impact of iceberg
-scouring on polar benthic habitats. \emph{Marine Ecology Progress
-Series}, \emph{137}, 311--316.
-doi:\href{https://doi.org/10.3354/meps137311}{10.3354/meps137311}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hendry2018}{}}%
-Hendry, K. R., Meredith, M. P., \& Ducklow, H. W. (2018). The marine
-system of the {West Antarctic Peninsula}: Status and strategy for
-progress. \emph{Philosophical Transactions of the Royal Society A:
-Mathematical, Physical and Engineering Sciences}, \emph{376}(2122),
-20170179.
-doi:\href{https://doi.org/10.1098/rsta.2017.0179}{10.1098/rsta.2017.0179}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hernandez2019}{}}%
-Hernández, E. A., Lopez, J. L., Piquet, A. M.-T., Mac Cormack, W. P., \&
-Buma, A. G. J. (2019). Changes in salinity and temperature drive marine
-bacterial communities' structure at {Potter Cove}, {Antarctica}.
-\emph{Polar Biology}, \emph{42}(12), 2177--2191.
-doi:\href{https://doi.org/10.1007/s00300-019-02590-5}{10.1007/s00300-019-02590-5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hilborn2017}{}}%
+\bibitem[\citeproctext]{ref-Hilborn2017}
 Hilborn, R., Amoroso, R. O., Bogazzi, E., Jensen, O. P., Parma, A. M.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hill2012}{}}%
-Hill, S. L., Keeble, K., Atkinson, A., \& Murphy, E. J. (2012). A
-foodweb model to explore uncertainties in the {South Georgia} shelf
-pelagic ecosystem. \emph{Deep Sea Research Part II: Topical Studies in
-Oceanography}, \emph{59--60}, 237--252.
-doi:\href{https://doi.org/10.1016/j.dsr2.2011.09.001}{10.1016/j.dsr2.2011.09.001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hill2013}{}}%
-Hill, S. L., Phillips, T., \& Atkinson, A. (2013). Potential {Climate
-Change Effects} on the {Habitat} of {Antarctic Krill} in the {Weddell
-Quadrant} of the {Southern Ocean}. \emph{PLOS ONE}, \emph{8}(8), e72246.
-doi:\href{https://doi.org/10.1371/journal.pone.0072246}{10.1371/journal.pone.0072246}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hindell2020}{}}%
+\bibitem[\citeproctext]{ref-Hindell2020}
 Hindell, M. A., Reisinger, R. R., Ropert-Coudert, Y., Hückstädt, L. A.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hoffmann2019}{}}%
+\bibitem[\citeproctext]{ref-Hoffmann2019}
 Hoffmann, R., Al-Handal, A. Y., Wulff, A., Deregibus, D., Zacher, K.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Iken2023}{}}%
+\bibitem[\citeproctext]{ref-Iken2023}
 Iken, K., Amsler, C. D., Gorman, K. B., Klein, A. G., Galloway, A. W.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Irons2000}{}}%
+\bibitem[\citeproctext]{ref-Irons2000}
 Irons, D. B., Kendall, S. J., Erickson, W. P., McDonald, L. L., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Isla2023}{}}%
+\bibitem[\citeproctext]{ref-Isla2023}
 Isla, E. (2023). Animal\textendash{{Energy Relationships}} in a
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Jacob2011}{}}%
+\bibitem[\citeproctext]{ref-Jacob2011}
 Jacob, U., Thierry, A., Brose, U., Arntz, W. E., Berg, S., Brey, T.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Jerosch2018}{}}%
+\bibitem[\citeproctext]{ref-Jerosch2018}
 Jerosch, K., Pehlke, H., Monien, P., Scharf, F., Weber, L., Kuhn, G.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Jordan2007}{}}%
+\bibitem[\citeproctext]{ref-Jordan2007}
 Jordán, F., Benedek, Z., \& Podani, J. (2007). Quantifying positional
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kaminskyinprep}{}}%
+\bibitem[\citeproctext]{ref-Kaminskyinprep}
 Kaminsky, J., Bagur, M., Boraso, A., Schloss, I. R., Buschmann, A. H.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kawaguchi2013}{}}%
-Kawaguchi, S., Ishida, A., King, R., Raymond, B., Waller, N., Constable,
-A., \ldots{} Ishimatsu, A. (2013). Risk maps for {Antarctic} krill under
-projected {Southern Ocean} acidification. \emph{Nature Climate Change},
-\emph{3}(9), 843--847.
-doi:\href{https://doi.org/10.1038/nclimate1937}{10.1038/nclimate1937}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kawaguchi2010}{}}%
-Kawaguchi, So, Kurihara, H., King, R., Hale, L., Berli, T., Robinson, J.
-P., \ldots{} Ishimatsu, A. (2010). Will krill fare well under {Southern
-Ocean} acidification? \emph{Biology Letters}, \emph{7}(2), 288--291.
-doi:\href{https://doi.org/10.1098/rsbl.2010.0777}{10.1098/rsbl.2010.0777}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kawaguchi2009}{}}%
-Kawaguchi, So, Nicol, S., \& Press, A. (2009). Direct effects of climate
+\bibitem[\citeproctext]{ref-Kawaguchi2009}
+Kawaguchi, S., Nicol, S., \& Press, A. (2009). Direct effects of climate
 change on the {Antarctic} krill fishery.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Klein2018}{}}%
+\bibitem[\citeproctext]{ref-Klein2018}
 Klein, E. S., Hill, S. L., Hinke, J. T., Phillips, T., \& Watters, G. M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2019}{}}%
+\bibitem[\citeproctext]{ref-Kortsch2021}
+Kortsch, S., Frelat, R., Pecuchet, L., Olivier, P., Putnis, I.,
+Bonsdorff, E., \ldots{} Nordström, M. C. (2021). Disentangling temporal
+food web dynamics facilitates understanding of ecosystem functioning.
+\emph{Journal of Animal Ecology}, \emph{90}(5), 1205--1216.
+doi:\href{https://doi.org/10.1111/1365-2656.13447}{10.1111/1365-2656.13447}
+
+\bibitem[\citeproctext]{ref-Kortsch2019}
 Kortsch, S., Primicerio, R., Aschan, M., Lind, S., Dolgov, A. V., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2015}{}}%
+\bibitem[\citeproctext]{ref-Kortsch2015}
 Kortsch, S., Primicerio, R., Fossheim, M., Dolgov, A. V., \& Aschan, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kratina2012}{}}%
+\bibitem[\citeproctext]{ref-Kratina2012}
 Kratina, P., LeCraw, R. M., Ingram, T., \& Anholt, B. R. (2012).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lagger2018}{}}%
-Lagger, C., Nime, M., Torre, L., Servetto, N., Tatián, M., \& Sahade, R.
-(2018). Climate change, glacier retreat and a new ice-free island offer
-new insights on {Antarctic} benthic responses. \emph{Ecography},
-\emph{41}(4), 579--591.
-doi:\href{https://doi.org/10.1111/ecog.03018}{10.1111/ecog.03018}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lagger2017}{}}%
-Lagger, C., Servetto, N., Torre, L., \& Sahade, R. (2017). Benthic
-colonization in newly ice-free soft-bottom areas in an {Antarctic}
-fjord. \emph{PLOS ONE}, \emph{12}(11), e0186756.
-doi:\href{https://doi.org/10.1371/journal.pone.0186756}{10.1371/journal.pone.0186756}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Latorre2023}{}}%
+\bibitem[\citeproctext]{ref-Latorre2023}
 Latorre, M. P., Iachetti, C. M., Schloss, I. R., Antoni, J., Malits, A.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lattuca2018}{}}%
+\bibitem[\citeproctext]{ref-Lattuca2018}
 Lattuca, María Eugenia, Boy, C. C., Vanella, F. A., Barrantes, M. E., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lattuca2023}{}}%
+\bibitem[\citeproctext]{ref-Lattuca2023}
 Lattuca, María E., Vanella, F. A., Malanga, G., Rubel, M. D., Manríquez,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lin2021}{}}%
+\bibitem[\citeproctext]{ref-Lin2021}
 Lin, Y., Moreno, C., Marchetti, A., Ducklow, H., Schofield, O., Delage,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Llorca2012}{}}%
+\bibitem[\citeproctext]{ref-Llorca2012}
 Llorca, M., Farré, M., Tavano, M. S., Alonso, B., Koremblit, G., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lopez-Gappa2022}{}}%
+\bibitem[\citeproctext]{ref-Lopez-Gappa2022}
 López-Gappa, J. (2022). The {Impact} of {Global Change} on {Marine
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lopez-Lopez2022}{}}%
+\bibitem[\citeproctext]{ref-Lopez-Lopez2022}
 López-López, L., Genner, M. J., Tarling, G. A., Saunders, R. A., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Manno2022}{}}%
-Manno, C., Peck, V. L., Corsi, I., \& Bergami, E. (2022). Under
-pressure: {Nanoplastics} as a further stressor for sub-{Antarctic}
-pteropods already tackling ocean acidification. \emph{Marine Pollution
-Bulletin}, \emph{174}, 113176.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2021.113176}{10.1016/j.marpolbul.2021.113176}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Marina2018}{}}%
+\bibitem[\citeproctext]{ref-Marina2018}
 Marina, T. I., Salinas, V., Cordone, G., Campana, G., Moreira, E.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Marinainrev}{}}%
+\bibitem[\citeproctext]{ref-Marinainrev}
 Marina, T. I., Schloss, I. R., Lovrich, G. A., Boy, C. C., Bruno, D. O.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martinez2022}{}}%
-Martínez, Patricia A., Wöhler, O. C., Troccoli, G. H., Di Marco, E., \&
+\bibitem[\citeproctext]{ref-Martinez2022}
+Martínez, P. A., Wöhler, O. C., Troccoli, G. H., Di Marco, E., \&
 Maydana, L. (2022). \emph{{Descripción de las capturas incidentales de
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martinez2015}{}}%
-Martínez, P. A., Wöhler, O. G., \& Troccoli, G. H. (2015). \emph{{La
-evolución de la pesquería de merluza negra (Dissostichus eleginoides) en
-el espacio marítimo argentino. Periodo 2003- 2014}} (\{Technical
-report\} No. 11/15) (p. 12). {Instituto Nacional de Investigación y
-Desarrollo Pesquero (INIDEP), Argentina}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Matano2019}{}}%
+\bibitem[\citeproctext]{ref-Matano2019}
 Matano, Ricardo P., Palma, E. D., \& Combes, V. (2019). The {Burdwood
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Matano2010}{}}%
+\bibitem[\citeproctext]{ref-Matano2010}
 Matano, R. P., Palma, E. D., \& Piola, A. R. (2010). The influence of
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-McCann1998}{}}%
-McCann, K., Hastings, A., \& Huxel, G. R. (1998). Weak trophic
-interactions and the balance of nature. \emph{Nature}, \emph{395}(6704),
-794--798. doi:\href{https://doi.org/10.1038/27427}{10.1038/27427}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Menge1995}{}}%
+\bibitem[\citeproctext]{ref-Menge1995}
 Menge, B. A. (1995). Indirect {Effects} in {Marine Rocky Intertidal
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meredith2018}{}}%
+\bibitem[\citeproctext]{ref-Meredith2018}
 Meredith, M. P., Falk, U., Bers, A. V., Mackensen, A., Schloss, I. R.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meyer2017}{}}%
-Meyer, B., Freier, U., Grimm, V., Groeneveld, J., Hunt, B. P. V.,
-Kerwath, S., \ldots{} Yilmaz, N. I. (2017). The winter pack-ice zone
-provides a sheltered but food-poor habitat for larval {Antarctic} krill.
-\emph{Nature Ecology \& Evolution}, \emph{1}(12), 1853--1861.
-doi:\href{https://doi.org/10.1038/s41559-017-0368-3}{10.1038/s41559-017-0368-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Michel2019}{}}%
+\bibitem[\citeproctext]{ref-Michel2019}
 Michel, L. N., Danis, B., Dubois, P., Eleaume, M., Fournier, J., Gallut,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mintenbeck2012}{}}%
+\bibitem[\citeproctext]{ref-Mintenbeck2012}
 Mintenbeck, K., Barrera-Oro, E. R., Brey, T., Jacob, U., Knust, R.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Montoya2009}{}}%
+\bibitem[\citeproctext]{ref-Montoya2009}
 Montoya, JoséM., Woodward, G., Emmerson, M. C., \& Solé, R. V. (2009).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Moore1974}{}}%
-Moore, S. F., \& Dwyer, R. L. (1974). Effects of oil on marine
-organisms: {A} critical assessment of published data. \emph{Water
-Research}, \emph{8}(10), 819--827.
-doi:\href{https://doi.org/10.1016/0043-1354(74)90028-1}{10.1016/0043-1354(74)90028-1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Moy2009}{}}%
-Moy, A. D., Howard, W. R., Bray, S. G., \& Trull, T. W. (2009). Reduced
-calcification in modern {Southern Ocean} planktonic foraminifera.
-\emph{Nature Geoscience}, \emph{2}(4), 276--280.
-doi:\href{https://doi.org/10.1038/ngeo460}{10.1038/ngeo460}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Murphy2007}{}}%
+\bibitem[\citeproctext]{ref-Murphy2007}
 Murphy, E. J., Trathan, P. N., Watkins, J. L., Reid, K., Meredith, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Murphy2006}{}}%
+\bibitem[\citeproctext]{ref-Murphy2006}
 Murphy, E. j., Watkins, J. l., Trathan, P. n., Reid, K., Meredith, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Nardi2019}{}}%
+\bibitem[\citeproctext]{ref-Nardi2019}
 Nardi, C. F., Fernández, D. A., Vanella, F. A., \& Chalde, T. (2019).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Neder2023}{}}%
-Neder, C. (2023). \emph{{El bentos antártico y su respuesta al cambio
-climático: una aproximación usando modelos de distribución de especies
-como caso de estudio en caleta Potter}} (PhD thesis). Universidad
-Nacional de Córdoba, {Córdoba, Argentina}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Neder2022}{}}%
-Neder, C., Fofonova, V., Androsov, A., Kuznetsov, I., Abele, D., Falk,
-U., \ldots{} Jerosch, K. (2022). Modelling suspended particulate matter
-dynamics at an {Antarctic} fjord impacted by glacier melt. \emph{Journal
-of Marine Systems}, \emph{231}, 103734.
-doi:\href{https://doi.org/10.1016/j.jmarsys.2022.103734}{10.1016/j.jmarsys.2022.103734}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Nilsson2016}{}}%
+\bibitem[\citeproctext]{ref-Nilsson2016}
 Nilsson, K. A., \& McCann, K. S. (2016). Interaction strength
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Nowacek2015}{}}%
+\bibitem[\citeproctext]{ref-Nowacek2015}
 Nowacek, D. P., Clark, C. W., Mann, D., Miller, P. J., Rosenbaum, H. C.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-OGorman2012}{}}%
+\bibitem[\citeproctext]{ref-OGorman2012}
 O'Gorman, E. J., Fitch, J. E., \& Crowe, T. P. (2012). Multiple
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-OGorman2019}{}}%
+\bibitem[\citeproctext]{ref-OGorman2019}
 O'Gorman, E. J., Petchey, O. L., Faulkner, K. J., Gallo, B., Gordon, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ojeda2021}{}}%
+\bibitem[\citeproctext]{ref-Ojeda2021}
 Ojeda, M., Cossi, P. F., Rimondino, G. N., Chiesa, I. L., Boy, C. C., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Oliver2018}{}}%
+\bibitem[\citeproctext]{ref-Oliver2018}
 Oliver, E. C. J., Donat, M. G., Burrows, M. T., Moore, P. J., Smale, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Olivier2019}{}}%
+\bibitem[\citeproctext]{ref-Olivier2019}
 Olivier, P., Frelat, R., Bonsdorff, E., Kortsch, S., Kröncke, I.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Orgeira2021}{}}%
+\bibitem[\citeproctext]{ref-Orgeira2021}
 Orgeira, J. L., Alvarez, F., \& Salvó, C. S. (2021). The same pathway to
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Orr2020}{}}%
+\bibitem[\citeproctext]{ref-Orr2020}
 Orr, J. A., Vinebrooke, R. D., Jackson, M. C., Kroeker, K. J., Kordas,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Paine1996}{}}%
+\bibitem[\citeproctext]{ref-Paine1996}
 Paine, R. T., Ruesink, J. L., Sun, A., Soulanille, E. L., Wonham, M. J.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pallin2023}{}}%
+\bibitem[\citeproctext]{ref-Pallin2023}
 Pallin, L. J., Kellar, N. M., Steel, D., Botero-Acosta, N., Baker, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pante2023}{}}%
+\bibitem[\citeproctext]{ref-Pante2023}
 Pante, E., Simon-Bouhet, B., \& Irisson, J. (2023). Marmap: {Import},
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pasotti2015}{}}%
+\bibitem[\citeproctext]{ref-Pasotti2015}
 Pasotti, F., Saravia, L. A., Troch, M. D., Tarantelli, M. S., Sahade,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pasti2021}{}}%
+\bibitem[\citeproctext]{ref-Pasti2021}
 Pasti, A. T., Bovcon, N. D., Ruibal-Núñez, J., Navoa, X., Jacobi, K. J.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pauli2021}{}}%
+\bibitem[\citeproctext]{ref-Pauli2021}
 Pauli, N.-C., Flintrop, C. M., Konrad, C., Pakhomov, E. A., Swoboda, S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pecuchet2022}{}}%
+\bibitem[\citeproctext]{ref-Pecuchet2022}
 Pecuchet, L., Jørgensen, L. L., Dolgov, A. V., Eriksen, E., Husson, B.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pecuchet2020}{}}%
+\bibitem[\citeproctext]{ref-Pecuchet2020}
 Pecuchet, L., Lindegren, M., Kortsch, S., Całkiewicz, J., Jurgensone,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Perez2021}{}}%
-Pérez, A. F., Ojeda, M., Cossi, P. F., Rimondino, G. N., Chiesa, I. L.,
-Fraysse, C., \& Calcagno, J. (2021). {Microplásticos en organismos
-marinos de altas latitudes}. In \emph{{I Jornadas de la Red Científica
-Argentina para el estudio de los plásticos y sus impactos en el ambiente
-(SEPIA)}}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Perez2020}{}}%
-Pérez, Analía F., Ojeda, M., Rimondino, G. N., Chiesa, I. L., Di Mauro,
-R., Boy, C. C., \& Calcagno, J. A. (2020). First report of microplastics
+\bibitem[\citeproctext]{ref-Perez2020}
+Pérez, A. F., Ojeda, M., Rimondino, G. N., Chiesa, I. L., Di Mauro, R.,
+Boy, C. C., \& Calcagno, J. A. (2020). First report of microplastics
 presence in the mussel {Mytilus} chilensis from {Ushuaia Bay} ({Beagle
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Peterson2001}{}}%
+\bibitem[\citeproctext]{ref-Peterson2001}
 Peterson, C. H. (2001). The {`{Exxon Valdez}'} oil spill in {Alaska}:
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pineda-Metz2019a}{}}%
-Pineda-Metz, S. E. A. (2019). \emph{Benthic communities of the {Weddell
-Sea}: Past, present and future} (PhD thesis). University of Bremen,
-{Germany}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pineda-Metz2020}{}}%
+\bibitem[\citeproctext]{ref-Pineda-Metz2020}
 Pineda-Metz, S. E. A., Gerdes, D., \& Richter, C. (2020). Benthic fauna
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pinkerton2021}{}}%
+\bibitem[\citeproctext]{ref-Pinkerton2021}
 Pinkerton, M. H., Boyd, P. W., Deppeler, S., Hayward, A., Höfer, J., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pinones2016}{}}%
-Piñones, A., \& Fedorov, A. V. (2016). Projected changes of {Antarctic}
-krill habitat by the end of the 21st century. \emph{Geophysical Research
-Letters}, \emph{43}(16), 8580--8589.
-doi:\href{https://doi.org/10.1002/2016GL069656}{10.1002/2016GL069656}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Piola2009}{}}%
-Piola, A. R., \& Falabella, V. (2009). {El mar Patagónico}. In
-\emph{{Atlas del Mar Patagónico. Especies y Espacios}} (Falabella, V.,
-Campagna, C. y Croxall, J. Ed., pp. 54--75). {Buenos Aires, Argentina}:
-{Wildlife Conservation Society y Birdlife Internacional}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Polazzo2022}{}}%
-Polazzo, F., Marina, T. I., Crettaz-Minaglia, M., \& Rico, A. (2022).
-Food web rewiring drives long-term compositional differences and
-late-disturbance interactions at the community level. \emph{Proceedings
-of the National Academy of Sciences}, \emph{119}(17), e2117364119.
-doi:\href{https://doi.org/10.1073/pnas.2117364119}{10.1073/pnas.2117364119}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Poloczanska2013}{}}%
+\bibitem[\citeproctext]{ref-Poloczanska2013}
 Poloczanska, E. S., Brown, C. J., Sydeman, W. J., Kiessling, W.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Quartino2008}{}}%
+\bibitem[\citeproctext]{ref-Quartino2008}
 Quartino, M. L., \& Boraso de Zaixso, A. L. (2008). Summer macroalgal
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Quartino2013}{}}%
+\bibitem[\citeproctext]{ref-Quartino2013}
 Quartino, María Liliana, Deregibus, D., Campana, G. L., Latorre, G. E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Raymond2011}{}}%
+\bibitem[\citeproctext]{ref-Raymond2011}
 Raymond, B. (2011). \emph{A circumpolar pelagic regionalisation of the
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2020}{}}%
+\bibitem[\citeproctext]{ref-Riccialdelli2020}
 Riccialdelli, L., Becker, Y. A., Fioramonti, N. E., Torres, M., Bruno,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2013}{}}%
+\bibitem[\citeproctext]{ref-Riccialdelli2013}
 Riccialdelli, L., Newsome, S. D., Dellabianca, N. A., Bastida, R.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2017}{}}%
-Riccialdelli, L., Newsome, S. D., Fogel, M. L., \& Fernández, D. A.
-(2017). Trophic interactions and food web structure of a subantarctic
-marine food web in the {Beagle Channel}: {Bahía Lapataia}, {Argentina}.
-\emph{Polar Biology}, \emph{40}(4), 807--821.
-doi:\href{https://doi.org/10.1007/s00300-016-2007-x}{10.1007/s00300-016-2007-x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Rincon-Diaz2021}{}}%
+\bibitem[\citeproctext]{ref-Rincon-Diaz2021}
 Rincón-Díaz, M. P., Bovcon, N. D., Cochia, P. D., Góngora, M. E., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Rodriguez2022}{}}%
+\bibitem[\citeproctext]{ref-Rodriguez2022}
 Rodriguez, I. D., Marina, T. I., Schloss, I. R., \& Saravia, L. A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Rossi2019}{}}%
-Rossi, L., Sporta Caputi, S., Calizza, E., Careddu, G., Oliverio, M.,
-Schiaparelli, S., \& Costantini, M. L. (2019). Antarctic food web
-architecture under varying dynamics of sea ice cover. \emph{Scientific
-Reports}, \emph{9}(1), 12454.
-doi:\href{https://doi.org/10.1038/s41598-019-48245-7}{10.1038/s41598-019-48245-7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Rowlands2021}{}}%
+\bibitem[\citeproctext]{ref-Rowlands2021}
 Rowlands, E., Galloway, T., Cole, M., Lewis, C., Peck, V., Thorpe, S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ruckamp2011}{}}%
+\bibitem[\citeproctext]{ref-Ruckamp2011}
 Rückamp, M., Braun, M., Suckro, S., \& Blindow, N. (2011). Observed
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RuibalNunez2020}{}}%
+\bibitem[\citeproctext]{ref-RuibalNunez2020}
 Ruibal Nuñez, J. (2020). \emph{{Impacto ecológico de la actividad
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sahade2015}{}}%
+\bibitem[\citeproctext]{ref-Sahade2015}
 Sahade, R., Lagger, C., Torre, L., Momo, F., Monien, P., Schloss, I.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sailley2013}{}}%
-Sailley, S. F., Ducklow, H. W., Moeller, H. V., Fraser, W. R.,
-Schofield, O. M., Steinberg, D. K., \ldots{} Doney, S. C. (2013). Carbon
-fluxes and pelagic ecosystem dynamics near two western {Antarctic
-Peninsula Adélie} penguin colonies: An inverse model approach.
-\emph{Marine Ecology Progress Series}, \emph{492}, 253--272.
-doi:\href{https://doi.org/10.3354/meps10534}{10.3354/meps10534}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Saravia2021}{}}%
-Saravia, J., Paschke, K., Oyarzún-Salazar, R., Cheng, C.-H. C., Navarro,
-J. M., \& Vargas-Chacoff, L. (2021). Effects of warming rates on
-physiological and molecular components of response to {CTMax} heat
-stress in the {Antarctic} fish {Harpagifer} antarcticus. \emph{Journal
-of Thermal Biology}, \emph{99}, 103021.
-doi:\href{https://doi.org/10.1016/j.jtherbio.2021.103021}{10.1016/j.jtherbio.2021.103021}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Saunders2019}{}}%
+\bibitem[\citeproctext]{ref-Saunders2019}
 Saunders, R. A., Hill, S. L., Tarling, G. A., \& Murphy, E. J. (2019).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schejter2021}{}}%
+\bibitem[\citeproctext]{ref-Schejter2021}
 Schejter, L., \& Albano, M. (2021). Benthic communities at the marine
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schloss2012}{}}%
+\bibitem[\citeproctext]{ref-Schloss2012}
 Schloss, I. R., Abele, D., Moreau, S., Demers, S., Bers, A. V.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schloss2023}{}}%
+\bibitem[\citeproctext]{ref-Schloss2023}
 Schloss, I. R., Pizarro, G., Cadaillon, A. M., Giesecke, R., Hernando,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2011}{}}%
+\bibitem[\citeproctext]{ref-Schmidt2011}
 Schmidt, K., Atkinson, A., Steigenberger, S., Fielding, S., Lindsay, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Seco2021}{}}%
+\bibitem[\citeproctext]{ref-Seco2021}
 Seco, J., Aparício, S., Brierley, A. S., Bustamante, P., Ceia, F. R.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sgarlatta2023}{}}%
+\bibitem[\citeproctext]{ref-Sgarlatta2023}
 Sgarlatta, M. (2023). \emph{Mechanisms driving tropicalization of
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Siniff2008}{}}%
-Siniff, D. B., Garrott, R. A., Rotella, J. J., Fraser, W. R., \& Ainley,
-D. G. (2008). Opinion: {Projecting} the effects of environmental change
-on {Antarctic} seals. \emph{Antarctic Science}, \emph{20}(5), 425--435.
-doi:\href{https://doi.org/10.1017/S0954102008001351}{10.1017/S0954102008001351}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Smale2008}{}}%
+\bibitem[\citeproctext]{ref-Smale2008}
 Smale, Dan A., \& Barnes, D. K. A. (2008). Likely responses of the
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Smale2008a}{}}%
+\bibitem[\citeproctext]{ref-Smale2008a}
 Smale, Dan A., Brown, K. M., Barnes, D. K. A., Fraser, K. P. P., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Soeffker2022}{}}%
+\bibitem[\citeproctext]{ref-Soeffker2022}
 Soeffker, M., Hollyman, P. R., Collins, M. A., Hogg, O. T., Riley, A.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Souza2018}{}}%
-Souza, M. R. D. P. de, Herrerias, T., Zaleski, T., Forgati, M.,
-Kandalski, P. K., Machado, C., \ldots{} Donatti, L. (2018). Heat stress
-in the heart and muscle of the {Antarctic} fishes {Notothenia} rossii
-and {Notothenia} coriiceps: {Carbohydrate} metabolism and antioxidant
-defence. \emph{Biochimie}, \emph{146}, 43--55.
-doi:\href{https://doi.org/10.1016/j.biochi.2017.11.010}{10.1016/j.biochi.2017.11.010}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Steele2010}{}}%
-Steele, J. H., Thorpe, S. A., \& Turekian, K. K. (2010). \emph{Ocean
-{Currents}}. {Academic Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2011}{}}%
+\bibitem[\citeproctext]{ref-Stouffer2011}
 Stouffer, D. B., \& Bascompte, J. (2011). Compartmentalization increases
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Strobel2013}{}}%
-Strobel, A., Leo, E., Pörtner, H. O., \& Mark, F. C. (2013). Elevated
-temperature and {PCO2} shift metabolic pathways in differentially
-oxidative tissues of {Notothenia} rossii. \emph{Comparative Biochemistry
-and Physiology Part B: Biochemistry and Molecular Biology},
-\emph{166}(1), 48--57.
-doi:\href{https://doi.org/10.1016/j.cbpb.2013.06.006}{10.1016/j.cbpb.2013.06.006}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021}{}}%
-Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
-Desjardins-Proulx, P., \ldots{} Poisot, T. (2021). A roadmap towards
-predicting species interaction networks (across space and time).
-\emph{Philosophical Transactions of the Royal Society B: Biological
-Sciences}, \emph{376}(1837), 20210063.
-doi:\href{https://doi.org/10.1098/rstb.2021.0063}{10.1098/rstb.2021.0063}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Tamini2023}{}}%
+\bibitem[\citeproctext]{ref-Tamini2023}
 Tamini, L. L., Dellacasa, R. F., Chavez, L. N., Marinao, C. J., Góngora,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Tarling2018}{}}%
+\bibitem[\citeproctext]{ref-Tarling2018}
 Tarling, G. A., Ward, P., \& Thorpe, S. E. (2018). Spatial distributions
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Teixido2002}{}}%
+\bibitem[\citeproctext]{ref-Teixido2002}
 Teixidó, N., Garrabou, J., \& Arntz, W. E. (2002). Spatial pattern
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Thompson2012}{}}%
+\bibitem[\citeproctext]{ref-Thompson2012}
 Thompson, R. M., Brose, U., Dunne, J. A., Hall, R. O., Hladyz, S.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Thompson2007}{}}%
+\bibitem[\citeproctext]{ref-Thompson2007}
 Thompson, R. M., Hemberg, M., Starzomski, B. M., \& Shurin, J. B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Tombesi2020}{}}%
-Tombesi, M. L., Rabufetti, F., \& Lovrich, G. A. (2020). Las áreas
-marinas protegidas en la {Argentina}. \emph{La Lupa. Colección Fueguina
-De Divulgación Científica}, \emph{16}, 2--7.
-doi:\url{https://www.coleccionlalupa.com.ar/index.php/lalupa/article/view/79}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Trathan2023}{}}%
+\bibitem[\citeproctext]{ref-Trathan2023}
 Trathan, Philip N. (2023). The future of the {South Georgia} and {South
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Trathan2021}{}}%
+\bibitem[\citeproctext]{ref-Trathan2021}
 Trathan, P. N., Fielding, S., Hollyman, P. R., Murphy, E. J.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Trebilco2020}{}}%
-Trebilco, R., Melbourne-Thomas, J., \& Constable, A. J. (2020). The
-policy relevance of {Southern Ocean} food web structure: {Implications}
-of food web change for fisheries, conservation and carbon sequestration.
-\emph{Marine Policy}, \emph{115}, 103832.
-doi:\href{https://doi.org/10.1016/j.marpol.2020.103832}{10.1016/j.marpol.2020.103832}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Turner2020}{}}%
+\bibitem[\citeproctext]{ref-Turner2020}
 Turner, J., Guarino, M. V., Arnatt, J., Jena, B., Marshall, G. J.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Verges2019}{}}%
+\bibitem[\citeproctext]{ref-Verges2019}
 Vergés, A., McCosker, E., Mayer-Pinto, M., Coleman, M. A., Wernberg, T.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Verges2014}{}}%
+\bibitem[\citeproctext]{ref-Verges2014}
 Vergés, A., Steinberg, P. D., Hay, M. E., Poore, A. G. B., Campbell, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Vinuesa2005}{}}%
+\bibitem[\citeproctext]{ref-Vinuesa2005}
 Vinuesa, J. H. (2005). Distribución de crustáceos decápodos y
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Vinuesa2007}{}}%
+\bibitem[\citeproctext]{ref-Vinuesa2007}
 Vinuesa, J. H., \& Varisco, M. (2007). Trophic ecology of the lobster
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Vucic-Pestic2011}{}}%
+\bibitem[\citeproctext]{ref-Vucic-Pestic2011}
 Vucic-Pestic, O., Ehnes, R. B., Rall, B. C., \& Brose, U. (2011).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ward2018}{}}%
+\bibitem[\citeproctext]{ref-Ward2018}
 Ward, P., Tarling, G. A., \& Thorpe, S. E. (2018). Temporal changes in
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wege2021}{}}%
+\bibitem[\citeproctext]{ref-Wege2021}
 Wege, M., Salas, L., \& LaRue, M. (2021). Ice matters: {Life-history}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Whitehouse2008}{}}%
+\bibitem[\citeproctext]{ref-Whitehouse2008}
 Whitehouse, M. J., Meredith, M. P., Rothery, P., Atkinson, A., Ward, P.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Whitworth1980}{}}%
+\bibitem[\citeproctext]{ref-Whitworth1980}
 Whitworth, T. (1980). Zonation and geostrophic flow of the {Antarctic}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Williams2000}{}}%
+\bibitem[\citeproctext]{ref-Williams2000}
 Williams, R. J., \& Martinez, N. D. (2000). Simple rules yield complex
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wood2015}{}}%
+\bibitem[\citeproctext]{ref-Wood2015}
 Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Woods2023}{}}%
+\bibitem[\citeproctext]{ref-Woods2023}
 Woods, B. L., Van de Putte, A. P., Hindell, M. A., Raymond, B.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Woodward2010}{}}%
-Woodward, G., Benstead, J. P., Beveridge, O. S., Blanchard, J., Brey,
-T., Brown, L. E., \ldots{} Yvon-Durocher, G. (2010). Ecological
-{Networks} in a {Changing Climate}. In G. Woodward (Ed.), \emph{Advances
-in {Ecological Research}} (Vol. 42, pp. 71--138). {Academic Press}.
-doi:\href{https://doi.org/10.1016/B978-0-12-381363-3.00002-2}{10.1016/B978-0-12-381363-3.00002-2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wu2012}{}}%
+\bibitem[\citeproctext]{ref-Wu2012}
 Wu, L., Cai, W., Zhang, L., Nakamura, H., Timmermann, A., Joyce, T.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Yorio2009}{}}%
+\bibitem[\citeproctext]{ref-Yorio2009}
 Yorio, P. (2009). Marine protected areas, spatial scales, and
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Yorio2017}{}}%
-Yorio, P., González-Zevallos, D., Gatto, A., Biagioni, O., \& Castillo,
-J. (2017). Relevance of forage fish in the diet of {Magellanic} penguins
-breeding in northern {Patagonia}, {Argentina}. \emph{Marine Biology
-Research}, \emph{13}(6), 603--617.
-doi:\href{https://doi.org/10.1080/17451000.2016.1273529}{10.1080/17451000.2016.1273529}
-
 \end{CSLReferences}

### 2023-11-22 SupportingInformation.tex
Update supporting information add authors

@@
 \author{}
+
 \date{\vspace{-2.5em}}
@@
 \begin{document}
+
 \maketitle
+
+Tomás I. Marina\textsuperscript{1}, Leonardo A.
+Saravia\textsuperscript{1,2,*}, Iara D. Rodriguez\textsuperscript{3},
+Manuela Funes\textsuperscript{4}, Georgina Cordone\textsuperscript{5},
+Santiago R. Doyle\textsuperscript{3,6}, Anahí
+Silvestro\textsuperscript{6}, David E. Galván\textsuperscript{5},
+Susanne Kortsch\textsuperscript{7} \& Fernando Momo\textsuperscript{3,6}
+
+\textsuperscript{1} Centro Austral de Investigaciones Científicas
+(CADIC-CONICET), Ushuaia, Argentina;
+
+\textsuperscript{2} Instituto de Ciencias Polares, Ambiente y Recursos
+Naturales, Universidad Nacional de Tierra del Fuego (UNTdF), Ushuaia,
+Argentina;
+
+\textsuperscript{3} Instituto de Ciencias, Universidad Nacional de
+General Sarmiento (UNGS), Los Polvorines, Argentina;
+
+\textsuperscript{4} Instituto de Investigaciones Marinas y Costeras
+(IIMyC-CONICET), Mar del Plata, Argentina;
+
+\textsuperscript{5} Centro Para el Estudio de Sistemas Marinos
+(CESIMAR-CONICET), Puerto Madryn, Argentina;
+
+\textsuperscript{6} Instituto de Ecología y Desarrollo Sustentable
+(INEDES-CONICET-UNLu), Luján, Argentina;
+
+\textsuperscript{7} Tvärminne Zoological Station, University of
+Helsinki, Hanko, Finland.
+
+* corresponding author: Leonardo A. Saravia. Centro Austral de
+Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina.
+\href{mailto:lasaravia@untdf.edu.ar}{\nolinkurl{lasaravia@untdf.edu.ar}}
+
+\newpage
 

### 2023-11-27 manuscript.tex
changes SI

@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% definitions for citeproc citations
-\NewDocumentCommand\citeproctext{}{}
-\NewDocumentCommand\citeproc{mm}{%
-  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
-\makeatletter
- % allow citations to break across lines
- \let\@cite@ofmt\@firstofone
- % avoid brackets around text for \cite:
- \def\@biblabel#1{}
- \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
-\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
- {\begin{list}{}{%
-  \setlength{\itemindent}{0pt}
-  \setlength{\leftmargin}{0pt}
-  \setlength{\parsep}{0pt}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-   \setlength{\leftmargin}{\cslhangindent}
-   \setlength{\itemindent}{-1\cslhangindent}
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
   \fi
   % set entry spacing
-  \setlength{\itemsep}{#2\baselineskip}}}
- {\end{list}}
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 
+\hypertarget{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}{%
 \section{The response of trophic interaction networks to multiple
 stressors in a marine latitudinal gradient of the Southern
-Hemisphere}\label{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}
+Hemisphere}\label{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}}
+
+\hypertarget{running-title-marine-stressors-in-the-southern-hemisphere}{%
+\subsection{Running Title: Marine stressors in the Southern
+Hemisphere}\label{running-title-marine-stressors-in-the-southern-hemisphere}}
 
@@
 
-\subsection{Abstract}\label{abstract}
+\hypertarget{abstract}{%
+\subsection{Abstract}\label{abstract}}
 
@@
 
-\subsection{1. Introduction}\label{introduction}
+\hypertarget{introduction}{%
+\subsection{1. Introduction}\label{introduction}}
 
@@
 
+\hypertarget{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}{%
 \subsection{2. The structure of marine food webs in the Southwest
 Atlantic - Antarctic
-region}\label{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}
+region}\label{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}}
 
@@
 
+\hypertarget{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}{%
 \subsection{3. Environmental and anthropogenic stressors in the
 Southwest Atlantic - Antarctic
-region}\label{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}
+region}\label{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}}
 
@@
 
-\subsubsection{3.1 San Jorge Gulf}\label{san-jorge-gulf}
+\hypertarget{san-jorge-gulf}{%
+\subsubsection{3.1 San Jorge Gulf}\label{san-jorge-gulf}}
 
@@
 
-\subsubsection{3.2 Beagle Channel}\label{beagle-channel}
+\hypertarget{beagle-channel}{%
+\subsubsection{3.2 Beagle Channel}\label{beagle-channel}}
 
@@
 
-\subsubsection{3.3 Burdwood Bank}\label{burdwood-bank}
+\hypertarget{burdwood-bank}{%
+\subsubsection{3.3 Burdwood Bank}\label{burdwood-bank}}
 
@@
 
-\subsubsection{3.4 Scotia Sea}\label{scotia-sea}
+\hypertarget{scotia-sea}{%
+\subsubsection{3.4 Scotia Sea}\label{scotia-sea}}
 
@@
 
+\hypertarget{potter-cove-antarctica}{%
 \subsubsection{3.5 Potter Cove
-(Antarctica)}\label{potter-cove-antarctica}
+(Antarctica)}\label{potter-cove-antarctica}}
 
@@
 
+\hypertarget{weddell-sea-antarctica}{%
 \subsubsection{3.6 Weddell Sea
-(Antarctica)}\label{weddell-sea-antarctica}
+(Antarctica)}\label{weddell-sea-antarctica}}
 
@@
 
+\hypertarget{from-species-stressors-to-food-web-effects}{%
 \subsection{4. From species' stressors to food web
-effects}\label{from-species-stressors-to-food-web-effects}
+effects}\label{from-species-stressors-to-food-web-effects}}
 
@@
 
-\subsubsection{4.1 Main stressors effects on food webs in a southwest
+\hypertarget{main-stressor-effects-in-food-webs-in-a-southwest-atlantic---antarctic-gradient}{%
+\subsubsection{4.1 Main stressor effects in food webs in a southwest
 Atlantic - Antarctic
-gradient}\label{main-stressors-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}
+gradient}\label{main-stressor-effects-in-food-webs-in-a-southwest-atlantic---antarctic-gradient}}
 
@@
 
+\hypertarget{gaps-and-future-perspectives}{%
 \subsection{5. Gaps and future
-perspectives}\label{gaps-and-future-perspectives}
+perspectives}\label{gaps-and-future-perspectives}}
 
@@
 
-\subsection{Conclusions}\label{conclusions}
+\hypertarget{conclusions}{%
+\subsection{Conclusions}\label{conclusions}}
 
@@
 
-\subsection{Acknowledgements}\label{acknowledgements}
+\hypertarget{acknowledgements}{%
+\subsection{Acknowledgements}\label{acknowledgements}}
 
@@
 
-\subsection*{References}\label{references}
+\hypertarget{references}{%
+\subsection*{References}\label{references}}
 \addcontentsline{toc}{subsection}{References}
 
-\phantomsection\label{refs}
+\hypertarget{refs}{}
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-Acha2004}
+\leavevmode\vadjust pre{\hypertarget{ref-Acha2004}{}}%
 Acha, E. M., Mianzan, H. W., Guerrero, R. A., Favero, M., \& Bava, J.
@@
 
-\bibitem[\citeproctext]{ref-APN2022}
+\leavevmode\vadjust pre{\hypertarget{ref-APN2022}{}}%
 Administración de Parques Nacionales. (2022). {Plan de gestión AMP
@@
 
-\bibitem[\citeproctext]{ref-Albert2002}
+\leavevmode\vadjust pre{\hypertarget{ref-Albert2002}{}}%
 Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex
@@
 
-\bibitem[\citeproctext]{ref-Allega2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Allega2019}{}}%
 Allega, Lucrecia, Braverman, M. S., Cabreira, A. G., Campodónico, S.,
@@
 
-\bibitem[\citeproctext]{ref-Allega2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Allega2020}{}}%
 Allega, L., Braverman, M., Campodónico, S., Carozza, C. R., Cepeda, G.
@@
 
-\bibitem[\citeproctext]{ref-Anton2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Anton2019}{}}%
 Anton, A., Geraldi, N. R., Lovelock, C. E., Apostolaki, E. T., Bennett,
@@
 
-\bibitem[\citeproctext]{ref-Antoni2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Antoni2020}{}}%
 Antoni, J. S., Almandoz, G. O., Ferrario, M. E., Hernando, M. P.,
@@
 
-\bibitem[\citeproctext]{ref-Atkinson2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Atkinson2019}{}}%
 Atkinson, A., Hill, S. L., Pakhomov, E. A., Siegel, V., Reiss, C. S.,
@@
 
-\bibitem[\citeproctext]{ref-Atkinson2004}
+\leavevmode\vadjust pre{\hypertarget{ref-Atkinson2004}{}}%
 Atkinson, A., Siegel, V., Pakhomov, E., \& Rothery, P. (2004). Long-term
@@
 
-\bibitem[\citeproctext]{ref-Balech2008}
+\leavevmode\vadjust pre{\hypertarget{ref-Balech2008}{}}%
 Balech, E., \& Ehrlich, M. D. (2008). {Esquema biogeográfico del Mar
@@
 
-\bibitem[\citeproctext]{ref-Bartley2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Bartley2019}{}}%
 Bartley, T. J., McCann, K. S., Bieg, C., Cazelles, K., Granados, M.,
@@
 
-\bibitem[\citeproctext]{ref-Bauer2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Bauer2022}{}}%
 Bauer, B., Berti, E., Ryser, R., Gauzens, B., Hirt, M. R., Rosenbaum,
@@
 
-\bibitem[\citeproctext]{ref-Beauchesne2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Beauchesne2021}{}}%
 Beauchesne, D., Cazelles, K., Archambault, P., Dee, L. E., \& Gravel, D.
@@
 
-\bibitem[\citeproctext]{ref-Belgrano2005}
+\leavevmode\vadjust pre{\hypertarget{ref-Belgrano2005}{}}%
 Belgrano, A., Scharler, S. E. R. C. U. M., Scharler, U. M., Dunne, J.,
@@
 
-\bibitem[\citeproctext]{ref-Belleggia2017}
+\leavevmode\vadjust pre{\hypertarget{ref-Belleggia2017}{}}%
 Belleggia, M., Giberto, D., \& Bremec, C. (2017). Adaptation of diet in
@@
 
-\bibitem[\citeproctext]{ref-Bovcon2013}
+\leavevmode\vadjust pre{\hypertarget{ref-Bovcon2013}{}}%
 Bovcon, N. D., Góngora, M. E., Marinao, C., \& González-Zevallos, D.
@@
 
-\bibitem[\citeproctext]{ref-Boyd2015}
+\leavevmode\vadjust pre{\hypertarget{ref-Boyd2015}{}}%
 Boyd, P. W., Lennartz, S. T., Glover, D. M., \& Doney, S. C. (2015).
@@
 
-\bibitem[\citeproctext]{ref-Braeckman2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Braeckman2021}{}}%
 Braeckman, U., Pasotti, F., Hoffmann, R., Vázquez, S., Wulff, A.,
@@
 
-\bibitem[\citeproctext]{ref-Braithwaite2015}
+\leavevmode\vadjust pre{\hypertarget{ref-Braithwaite2015}{}}%
 Braithwaite, J. E., Meeuwig, J. J., Letessier, T. B., Jenner, K. C. S.,
@@
 
-\bibitem[\citeproctext]{ref-Brown2004}
+\leavevmode\vadjust pre{\hypertarget{ref-Brown2004}{}}%
 Brown, J. H., Gillooly, J. F., Allen, A. P., Savage, V. M., \& West, G.
@@
 
-\bibitem[\citeproctext]{ref-Bruder2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Bruder2019}{}}%
 Bruder, A., Frainer, A., Rota, T., \& Primicerio, R. (2019). The
@@
 
-\bibitem[\citeproctext]{ref-Bruno2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Bruno2023}{}}%
 Bruno, D. O., Riccialdelli, L., Acha, E. M., \& Fernández, D. A. (2023).
@@
 
-\bibitem[\citeproctext]{ref-Chown2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Chown2022}{}}%
 Chown, S. L., Leihy, R. I., Naish, T. R., Brooks, C. M., Convey, P.,
@@
 
-\bibitem[\citeproctext]{ref-Ciancio2008}
+\leavevmode\vadjust pre{\hypertarget{ref-Ciancio2008}{}}%
 Ciancio, J. E., Pascual, M. A., Botto, F., Frere, E., \& Iribarne, O.
@@
 
-\bibitem[\citeproctext]{ref-Cirtwill2015}
+\leavevmode\vadjust pre{\hypertarget{ref-Cirtwill2015}{}}%
 Cirtwill, A. R., Stouffer, D. B., \& Romanuk, T. N. (2015). Latitudinal
@@
 
-\bibitem[\citeproctext]{ref-Collins2010}
+\leavevmode\vadjust pre{\hypertarget{ref-Collins2010}{}}%
 Collins, M. A., Brickle, P., Brown, J., \& Belchier, M. (2010). Chapter
@@
 
-\bibitem[\citeproctext]{ref-Commendatore2012}
+\leavevmode\vadjust pre{\hypertarget{ref-Commendatore2012}{}}%
 Commendatore, M. G., Nievas, M. L., Amin, O., \& Esteves, J. L. (2012).
@@
 
-\bibitem[\citeproctext]{ref-Constable2014}
+\leavevmode\vadjust pre{\hypertarget{ref-Constable2014}{}}%
 Constable, A. J., Melbourne-Thomas, J., Corney, S. P., Arrigo, K. R.,
@@
 
-\bibitem[\citeproctext]{ref-Cordone2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Cordone2023}{}}%
 Cordone, G., Galván, D. E., \& Momo, F. R. (2023). Impacts of an
@@
 
-\bibitem[\citeproctext]{ref-Cordone2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Cordone2020}{}}%
 Cordone, G., Salinas, V., Marina, T. I., Doyle, S. R., Pasotti, F.,
@@
 
-\bibitem[\citeproctext]{ref-Correa2008}
+\leavevmode\vadjust pre{\hypertarget{ref-Correa2008}{}}%
 Correa, C., \& Gross, M. R. (2008). Chinook salmon invade southern
@@
 
-\bibitem[\citeproctext]{ref-Cossi2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Cossi2021}{}}%
 Cossi, P. F., Ojeda, M., Chiesa, I. L., Rimondino, G. N., Fraysse, C.,
@@
 
-\bibitem[\citeproctext]{ref-Cote2016}
+\leavevmode\vadjust pre{\hypertarget{ref-Cote2016}{}}%
 Côté, I. M., Darling, E. S., \& Brown, C. J. (2016). Interactions among
@@
 
-\bibitem[\citeproctext]{ref-deHaro2022}
+\leavevmode\vadjust pre{\hypertarget{ref-deHaro2022}{}}%
 de Haro, J. C., Perez Orsi, H., Cané, S., Di Pangracio, A., Falabella,
@@
 
-\bibitem[\citeproctext]{ref-Deregibus2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2023}{}}%
 Deregibus, Dolores, Campana, G. L., Neder, C., Barnes, D. K. A., Zacher,
@@
 
-\bibitem[\citeproctext]{ref-Deregibus2017}
+\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2017}{}}%
 Deregibus, D., Quartino, M. L., Zacher, K., Campana, G. L., \& Barnes,
@@
 
-\bibitem[\citeproctext]{ref-Deregibus2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Deregibus2020}{}}%
 Deregibus, Dolores, Zacher, K., Bartsch, I., Campana, G. L., Momo, F.
@@
 
-\bibitem[\citeproctext]{ref-DiMauro2022}
+\leavevmode\vadjust pre{\hypertarget{ref-DiMauro2022}{}}%
 Di Mauro, R., Castillo, S., Pérez, A., Iachetti, C. M., Silva, L.,
@@
 
-\bibitem[\citeproctext]{ref-Dodino2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Dodino2022}{}}%
 Dodino, S., Riccialdelli, L., Polito, M. J., Pütz, K., Brasso, R. L., \&
@@
 
-\bibitem[\citeproctext]{ref-Duarte2011}
+\leavevmode\vadjust pre{\hypertarget{ref-Duarte2011}{}}%
 Duarte, C. A., Giarratano, E., Amin, O. A., \& Comoglio, L. I. (2011).
@@
 
-\bibitem[\citeproctext]{ref-Duffy2007}
+\leavevmode\vadjust pre{\hypertarget{ref-Duffy2007}{}}%
 Duffy, J. E., Cardinale, B. J., France, K. E., McIntyre, P. B.,
@@
 
-\bibitem[\citeproctext]{ref-Dulvy2014}
+\leavevmode\vadjust pre{\hypertarget{ref-Dulvy2014}{}}%
 Dulvy, N. K., Fowler, S. L., Musick, J. A., Cavanagh, R. D., Kyne, P.
@@
 
-\bibitem[\citeproctext]{ref-Dunne2002a}
+\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002a}{}}%
 Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Food-web
@@
 
-\bibitem[\citeproctext]{ref-Dunne2002}
+\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
 Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). Network
@@
 
-\bibitem[\citeproctext]{ref-Fernandez2010}
+\leavevmode\vadjust pre{\hypertarget{ref-Fernandez2010}{}}%
 Fernández, D. A., Ciancio, J., Ceballos, S. G., Riva-Rossi, C., \&
@@
 
-\bibitem[\citeproctext]{ref-Ferreira2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Ferreira2021}{}}%
 Ferreira, M. F., Lo Nostro, F. L., Fernández, D. A., \& Genovese, G.
@@
 
-\bibitem[\citeproctext]{ref-Fioramonti2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Fioramonti2022}{}}%
 Fioramonti, N. E., Ribeiro Guevara, S., Becker, Y. A., \& Riccialdelli,
@@
 
-\bibitem[\citeproctext]{ref-Flores2012}
+\leavevmode\vadjust pre{\hypertarget{ref-Flores2012}{}}%
 Flores, H., Atkinson, A., Kawaguchi, S., Krafft, B., Milinevsky, G.,
@@
 
-\bibitem[\citeproctext]{ref-Franco2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Franco2020}{}}%
 Franco, B. C., Combes, V., \& González Carman, V. (2020). Subsurface
@@
 
-\bibitem[\citeproctext]{ref-Fretwell2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Fretwell2023}{}}%
 Fretwell, P. T., Boutet, A., \& Ratcliffe, N. (2023). Record low 2022
@@
 
-\bibitem[\citeproctext]{ref-Fuentes2016}
+\leavevmode\vadjust pre{\hypertarget{ref-Fuentes2016}{}}%
 Fuentes, V., Alurralde, G., Meyer, B., Aguirre, G. E., Canepa, A.,
@@
 
-\bibitem[\citeproctext]{ref-Funes2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Funes2020}{}}%
 Funes, M. (2020, March). \emph{Efectos de la pesca de arrastre sobre la
@@
 
-\bibitem[\citeproctext]{ref-Funes2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Funes2019}{}}%
 Funes, M., Marinao, C., \& Galván, D. E. (2019). Does trawl fisheries
@@
 
-\bibitem[\citeproctext]{ref-Funes2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Funes2022}{}}%
 Funes, M., Saravia, L. A., Cordone, G., Iribarne, O. O., \& Galván, D.
@@
 
-\bibitem[\citeproctext]{ref-Gaitan2016}
+\leavevmode\vadjust pre{\hypertarget{ref-Gaitan2016}{}}%
 Gaitán, E., \& Marí, N. (2016). {Análisis de las comunidades bentónicas
@@
 
-\bibitem[\citeproctext]{ref-Galvan2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Galvan2022}{}}%
 Galván, D. E., Bovcon, N. D., Cochia, P. D., González, R. A., Lattuca,
@@
 
-\bibitem[\citeproctext]{ref-Garcia2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Garcia2019}{}}%
 Garcia, M. D., Fernández Severini, M. D., Spetter, C., López Abbate, M.
@@
 
-\bibitem[\citeproctext]{ref-Garcia2016}
+\leavevmode\vadjust pre{\hypertarget{ref-Garcia2016}{}}%
 Garcia, M. D., Hoffmeyer, M. S., Abbate, M. C. L., Barría De Cao, M. S.,
@@
 
-\bibitem[\citeproctext]{ref-Garcia-Borboroglu2008}
+\leavevmode\vadjust pre{\hypertarget{ref-Garcia-Borboroglu2008}{}}%
 García-Borboroglu, P., Boersma, P. D., Reyes, L., \& Skewgar, E. (2008).
@@
 
-\bibitem[\citeproctext]{ref-Gauzens2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Gauzens2023}{}}%
 Gauzens, B., Brose, U., Delmas, E., \& Berti, E. (n.d.). {ATNr}:
@@
 
-\bibitem[\citeproctext]{ref-Gellner2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Gellner2023}{}}%
 Gellner, G., McCann, K., \& Hastings, A. (2023). Stable diverse food
@@
 
-\bibitem[\citeproctext]{ref-Gil2011}
+\leavevmode\vadjust pre{\hypertarget{ref-Gil2011}{}}%
 Gil, M. N., Torres, A. I., Amin, O., \& Esteves, J. L. (2011).
@@
 
-\bibitem[\citeproctext]{ref-Glembocki2015}
+\leavevmode\vadjust pre{\hypertarget{ref-Glembocki2015}{}}%
 Glembocki, N. G., Williams, G. N., Góngora, M. E., Gagliardini, D. A.,
@@
 
-\bibitem[\citeproctext]{ref-Gongora2012}
+\leavevmode\vadjust pre{\hypertarget{ref-Gongora2012}{}}%
 Góngora, M. E., González-Zevallos, D., Pettovello, A., \& Mendía, L.
@@
 
-\bibitem[\citeproctext]{ref-Gonzalez-Zevallos2006}
+\leavevmode\vadjust pre{\hypertarget{ref-Gonzalez-Zevallos2006}{}}%
 González-Zevallos, D., \& Yorio, P. (2006). Seabird use of discards and
@@
 
-\bibitem[\citeproctext]{ref-Gorini2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Gorini2021}{}}%
 Gorini, F. L., Lukaszewicz, G., \& Giussi, A. R. (2021).
@@
 
-\bibitem[\citeproctext]{ref-Guihou2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Guihou2020}{}}%
 Guihou, K., Piola, A. R., Palma, E. D., \& Chidichimo, M. P. (2020).
@@
 
-\bibitem[\citeproctext]{ref-Gutt2001a}
+\leavevmode\vadjust pre{\hypertarget{ref-Gutt2001a}{}}%
 Gutt, J. (2001). On the direct impact of ice on marine benthic
@@
 
-\bibitem[\citeproctext]{ref-Gutt2015}
+\leavevmode\vadjust pre{\hypertarget{ref-Gutt2015}{}}%
 Gutt, J., Bertler, N., Bracegirdle, T. J., Buschmann, A., Comiso, J.,
@@
 
-\bibitem[\citeproctext]{ref-Gutt2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Gutt2021}{}}%
 Gutt, J., Isla, E., Xavier, J. C., Adams, B. J., Ahn, I.-Y., Cheng,
@@
 
-\bibitem[\citeproctext]{ref-Gutt2003}
+\leavevmode\vadjust pre{\hypertarget{ref-Gutt2003}{}}%
 Gutt, J., \& Piepenburg, D. (2003). Scale-dependent impact on diversity
@@
 
-\bibitem[\citeproctext]{ref-Gutt2001}
+\leavevmode\vadjust pre{\hypertarget{ref-Gutt2001}{}}%
 Gutt, J., \& Starmans, A. (2001). Quantification of iceberg impact and
@@
 
-\bibitem[\citeproctext]{ref-Hilborn2017}
+\leavevmode\vadjust pre{\hypertarget{ref-Hilborn2017}{}}%
 Hilborn, R., Amoroso, R. O., Bogazzi, E., Jensen, O. P., Parma, A. M.,
@@
 
-\bibitem[\citeproctext]{ref-Hindell2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Hindell2020}{}}%
 Hindell, M. A., Reisinger, R. R., Ropert-Coudert, Y., Hückstädt, L. A.,
@@
 
-\bibitem[\citeproctext]{ref-Hoffmann2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Hoffmann2019}{}}%
 Hoffmann, R., Al-Handal, A. Y., Wulff, A., Deregibus, D., Zacher, K.,
@@
 
-\bibitem[\citeproctext]{ref-Iken2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Iken2023}{}}%
 Iken, K., Amsler, C. D., Gorman, K. B., Klein, A. G., Galloway, A. W.
@@
 
-\bibitem[\citeproctext]{ref-Irons2000}
+\leavevmode\vadjust pre{\hypertarget{ref-Irons2000}{}}%
 Irons, D. B., Kendall, S. J., Erickson, W. P., McDonald, L. L., \&
@@
 
-\bibitem[\citeproctext]{ref-Isla2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Isla2023}{}}%
 Isla, E. (2023). Animal\textendash{{Energy Relationships}} in a
@@
 
-\bibitem[\citeproctext]{ref-Jacob2011}
+\leavevmode\vadjust pre{\hypertarget{ref-Jacob2011}{}}%
 Jacob, U., Thierry, A., Brose, U., Arntz, W. E., Berg, S., Brey, T.,
@@
 
-\bibitem[\citeproctext]{ref-Jerosch2018}
+\leavevmode\vadjust pre{\hypertarget{ref-Jerosch2018}{}}%
 Jerosch, K., Pehlke, H., Monien, P., Scharf, F., Weber, L., Kuhn, G.,
@@
 
-\bibitem[\citeproctext]{ref-Jordan2007}
+\leavevmode\vadjust pre{\hypertarget{ref-Jordan2007}{}}%
 Jordán, F., Benedek, Z., \& Podani, J. (2007). Quantifying positional
@@
 
-\bibitem[\citeproctext]{ref-Kaminskyinprep}
+\leavevmode\vadjust pre{\hypertarget{ref-Kaminskyinprep}{}}%
 Kaminsky, J., Bagur, M., Boraso, A., Schloss, I. R., Buschmann, A. H.,
@@
 
-\bibitem[\citeproctext]{ref-Kawaguchi2009}
+\leavevmode\vadjust pre{\hypertarget{ref-Kawaguchi2009}{}}%
 Kawaguchi, S., Nicol, S., \& Press, A. (2009). Direct effects of climate
@@
 
-\bibitem[\citeproctext]{ref-Klein2018}
+\leavevmode\vadjust pre{\hypertarget{ref-Klein2018}{}}%
 Klein, E. S., Hill, S. L., Hinke, J. T., Phillips, T., \& Watters, G. M.
@@
 
-\bibitem[\citeproctext]{ref-Kortsch2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2021}{}}%
 Kortsch, S., Frelat, R., Pecuchet, L., Olivier, P., Putnis, I.,
@@
 
-\bibitem[\citeproctext]{ref-Kortsch2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2019}{}}%
 Kortsch, S., Primicerio, R., Aschan, M., Lind, S., Dolgov, A. V., \&
@@
 
-\bibitem[\citeproctext]{ref-Kortsch2015}
+\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2015}{}}%
 Kortsch, S., Primicerio, R., Fossheim, M., Dolgov, A. V., \& Aschan, M.
@@
 
-\bibitem[\citeproctext]{ref-Kratina2012}
+\leavevmode\vadjust pre{\hypertarget{ref-Kratina2012}{}}%
 Kratina, P., LeCraw, R. M., Ingram, T., \& Anholt, B. R. (2012).
@@
 
-\bibitem[\citeproctext]{ref-Latorre2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Latorre2023}{}}%
 Latorre, M. P., Iachetti, C. M., Schloss, I. R., Antoni, J., Malits, A.,
@@
 
-\bibitem[\citeproctext]{ref-Lattuca2018}
+\leavevmode\vadjust pre{\hypertarget{ref-Lattuca2018}{}}%
 Lattuca, María Eugenia, Boy, C. C., Vanella, F. A., Barrantes, M. E., \&
@@
 
-\bibitem[\citeproctext]{ref-Lattuca2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Lattuca2023}{}}%
 Lattuca, María E., Vanella, F. A., Malanga, G., Rubel, M. D., Manríquez,
@@
 
-\bibitem[\citeproctext]{ref-Lin2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Lin2021}{}}%
 Lin, Y., Moreno, C., Marchetti, A., Ducklow, H., Schofield, O., Delage,
@@
 
-\bibitem[\citeproctext]{ref-Llorca2012}
+\leavevmode\vadjust pre{\hypertarget{ref-Llorca2012}{}}%
 Llorca, M., Farré, M., Tavano, M. S., Alonso, B., Koremblit, G., \&
@@
 
-\bibitem[\citeproctext]{ref-Lopez-Gappa2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Lopez-Gappa2022}{}}%
 López-Gappa, J. (2022). The {Impact} of {Global Change} on {Marine
@@
 
-\bibitem[\citeproctext]{ref-Lopez-Lopez2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Lopez-Lopez2022}{}}%
 López-López, L., Genner, M. J., Tarling, G. A., Saunders, R. A., \&
@@
 
-\bibitem[\citeproctext]{ref-Marina2018}
+\leavevmode\vadjust pre{\hypertarget{ref-Marina2018}{}}%
 Marina, T. I., Salinas, V., Cordone, G., Campana, G., Moreira, E.,
@@
 
-\bibitem[\citeproctext]{ref-Marinainrev}
+\leavevmode\vadjust pre{\hypertarget{ref-Marinainrev}{}}%
 Marina, T. I., Schloss, I. R., Lovrich, G. A., Boy, C. C., Bruno, D. O.,
@@
 
-\bibitem[\citeproctext]{ref-Martinez2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Martinez2022}{}}%
 Martínez, P. A., Wöhler, O. C., Troccoli, G. H., Di Marco, E., \&
@@
 
-\bibitem[\citeproctext]{ref-Matano2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Matano2019}{}}%
 Matano, Ricardo P., Palma, E. D., \& Combes, V. (2019). The {Burdwood
@@
 
-\bibitem[\citeproctext]{ref-Matano2010}
+\leavevmode\vadjust pre{\hypertarget{ref-Matano2010}{}}%
 Matano, R. P., Palma, E. D., \& Piola, A. R. (2010). The influence of
@@
 
-\bibitem[\citeproctext]{ref-Menge1995}
+\leavevmode\vadjust pre{\hypertarget{ref-Menge1995}{}}%
 Menge, B. A. (1995). Indirect {Effects} in {Marine Rocky Intertidal
@@
 
-\bibitem[\citeproctext]{ref-Meredith2018}
+\leavevmode\vadjust pre{\hypertarget{ref-Meredith2018}{}}%
 Meredith, M. P., Falk, U., Bers, A. V., Mackensen, A., Schloss, I. R.,
@@
 
-\bibitem[\citeproctext]{ref-Michel2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Michel2019}{}}%
 Michel, L. N., Danis, B., Dubois, P., Eleaume, M., Fournier, J., Gallut,
@@
 
-\bibitem[\citeproctext]{ref-Mintenbeck2012}
+\leavevmode\vadjust pre{\hypertarget{ref-Mintenbeck2012}{}}%
 Mintenbeck, K., Barrera-Oro, E. R., Brey, T., Jacob, U., Knust, R.,
@@
 
-\bibitem[\citeproctext]{ref-Montoya2009}
+\leavevmode\vadjust pre{\hypertarget{ref-Montoya2009}{}}%
 Montoya, JoséM., Woodward, G., Emmerson, M. C., \& Solé, R. V. (2009).
@@
 
-\bibitem[\citeproctext]{ref-Murphy2007}
+\leavevmode\vadjust pre{\hypertarget{ref-Murphy2007}{}}%
 Murphy, E. J., Trathan, P. N., Watkins, J. L., Reid, K., Meredith, M.
@@
 
-\bibitem[\citeproctext]{ref-Murphy2006}
+\leavevmode\vadjust pre{\hypertarget{ref-Murphy2006}{}}%
 Murphy, E. j., Watkins, J. l., Trathan, P. n., Reid, K., Meredith, M.
@@
 
-\bibitem[\citeproctext]{ref-Nardi2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Nardi2019}{}}%
 Nardi, C. F., Fernández, D. A., Vanella, F. A., \& Chalde, T. (2019).
@@
 
-\bibitem[\citeproctext]{ref-Nilsson2016}
+\leavevmode\vadjust pre{\hypertarget{ref-Nilsson2016}{}}%
 Nilsson, K. A., \& McCann, K. S. (2016). Interaction strength
@@
 
-\bibitem[\citeproctext]{ref-Nowacek2015}
+\leavevmode\vadjust pre{\hypertarget{ref-Nowacek2015}{}}%
 Nowacek, D. P., Clark, C. W., Mann, D., Miller, P. J., Rosenbaum, H. C.,
@@
 
-\bibitem[\citeproctext]{ref-OGorman2012}
+\leavevmode\vadjust pre{\hypertarget{ref-OGorman2012}{}}%
 O'Gorman, E. J., Fitch, J. E., \& Crowe, T. P. (2012). Multiple
@@
 
-\bibitem[\citeproctext]{ref-OGorman2019}
+\leavevmode\vadjust pre{\hypertarget{ref-OGorman2019}{}}%
 O'Gorman, E. J., Petchey, O. L., Faulkner, K. J., Gallo, B., Gordon, T.
@@
 
-\bibitem[\citeproctext]{ref-Ojeda2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Ojeda2021}{}}%
 Ojeda, M., Cossi, P. F., Rimondino, G. N., Chiesa, I. L., Boy, C. C., \&
@@
 
-\bibitem[\citeproctext]{ref-Oliver2018}
+\leavevmode\vadjust pre{\hypertarget{ref-Oliver2018}{}}%
 Oliver, E. C. J., Donat, M. G., Burrows, M. T., Moore, P. J., Smale, D.
@@
 
-\bibitem[\citeproctext]{ref-Olivier2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Olivier2019}{}}%
 Olivier, P., Frelat, R., Bonsdorff, E., Kortsch, S., Kröncke, I.,
@@
 
-\bibitem[\citeproctext]{ref-Orgeira2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Orgeira2021}{}}%
 Orgeira, J. L., Alvarez, F., \& Salvó, C. S. (2021). The same pathway to
@@
 
-\bibitem[\citeproctext]{ref-Orr2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Orr2020}{}}%
 Orr, J. A., Vinebrooke, R. D., Jackson, M. C., Kroeker, K. J., Kordas,
@@
 
-\bibitem[\citeproctext]{ref-Paine1996}
+\leavevmode\vadjust pre{\hypertarget{ref-Paine1996}{}}%
 Paine, R. T., Ruesink, J. L., Sun, A., Soulanille, E. L., Wonham, M. J.,
@@
 
-\bibitem[\citeproctext]{ref-Pallin2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Pallin2023}{}}%
 Pallin, L. J., Kellar, N. M., Steel, D., Botero-Acosta, N., Baker, C.
@@
 
-\bibitem[\citeproctext]{ref-Pante2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Pante2023}{}}%
 Pante, E., Simon-Bouhet, B., \& Irisson, J. (2023). Marmap: {Import},
@@
 
-\bibitem[\citeproctext]{ref-Pasotti2015}
+\leavevmode\vadjust pre{\hypertarget{ref-Pasotti2015}{}}%
 Pasotti, F., Saravia, L. A., Troch, M. D., Tarantelli, M. S., Sahade,
@@
 
-\bibitem[\citeproctext]{ref-Pasti2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Pasti2021}{}}%
 Pasti, A. T., Bovcon, N. D., Ruibal-Núñez, J., Navoa, X., Jacobi, K. J.,
@@
 
-\bibitem[\citeproctext]{ref-Pauli2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Pauli2021}{}}%
 Pauli, N.-C., Flintrop, C. M., Konrad, C., Pakhomov, E. A., Swoboda, S.,
@@
 
-\bibitem[\citeproctext]{ref-Pecuchet2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Pecuchet2022}{}}%
 Pecuchet, L., Jørgensen, L. L., Dolgov, A. V., Eriksen, E., Husson, B.,
@@
 
-\bibitem[\citeproctext]{ref-Pecuchet2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Pecuchet2020}{}}%
 Pecuchet, L., Lindegren, M., Kortsch, S., Całkiewicz, J., Jurgensone,
@@
 
-\bibitem[\citeproctext]{ref-Perez2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Perez2020}{}}%
 Pérez, A. F., Ojeda, M., Rimondino, G. N., Chiesa, I. L., Di Mauro, R.,
@@
 
-\bibitem[\citeproctext]{ref-Perry2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Perry2020}{}}%
 Perry, F. A., Kawaguchi, S., Atkinson, A., Sailley, S. F., Tarling, G.
@@
 
-\bibitem[\citeproctext]{ref-Peterson2001}
+\leavevmode\vadjust pre{\hypertarget{ref-Peterson2001}{}}%
 Peterson, C. H. (2001). The {`{Exxon Valdez}'} oil spill in {Alaska}:
@@
 
-\bibitem[\citeproctext]{ref-Pineda-Metz2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Pineda-Metz2020}{}}%
 Pineda-Metz, S. E. A., Gerdes, D., \& Richter, C. (2020). Benthic fauna
@@
 
-\bibitem[\citeproctext]{ref-Pinkerton2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Pinkerton2021}{}}%
 Pinkerton, M. H., Boyd, P. W., Deppeler, S., Hayward, A., Höfer, J., \&
@@
 
-\bibitem[\citeproctext]{ref-Poloczanska2013}
+\leavevmode\vadjust pre{\hypertarget{ref-Poloczanska2013}{}}%
 Poloczanska, E. S., Brown, C. J., Sydeman, W. J., Kiessling, W.,
@@
 
-\bibitem[\citeproctext]{ref-Quartino2008}
+\leavevmode\vadjust pre{\hypertarget{ref-Quartino2008}{}}%
 Quartino, M. L., \& Boraso de Zaixso, A. L. (2008). Summer macroalgal
@@
 
-\bibitem[\citeproctext]{ref-Quartino2013}
+\leavevmode\vadjust pre{\hypertarget{ref-Quartino2013}{}}%
 Quartino, María Liliana, Deregibus, D., Campana, G. L., Latorre, G. E.
@@
 
-\bibitem[\citeproctext]{ref-Raymond2011}
+\leavevmode\vadjust pre{\hypertarget{ref-Raymond2011}{}}%
 Raymond, B. (2011). \emph{A circumpolar pelagic regionalisation of the
@@
 
-\bibitem[\citeproctext]{ref-Riccialdelli2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2020}{}}%
 Riccialdelli, L., Becker, Y. A., Fioramonti, N. E., Torres, M., Bruno,
@@
 
-\bibitem[\citeproctext]{ref-Riccialdelli2013}
+\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2013}{}}%
 Riccialdelli, L., Newsome, S. D., Dellabianca, N. A., Bastida, R.,
@@
 
-\bibitem[\citeproctext]{ref-Rincon-Diaz2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Rincon-Diaz2021}{}}%
 Rincón-Díaz, M. P., Bovcon, N. D., Cochia, P. D., Góngora, M. E., \&
@@
 
-\bibitem[\citeproctext]{ref-Rodriguez2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Rodriguez2022}{}}%
 Rodriguez, I. D., Marina, T. I., Schloss, I. R., \& Saravia, L. A.
@@
 
-\bibitem[\citeproctext]{ref-Rowlands2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Rowlands2021}{}}%
 Rowlands, E., Galloway, T., Cole, M., Lewis, C., Peck, V., Thorpe, S.,
@@
 
-\bibitem[\citeproctext]{ref-Ruckamp2011}
+\leavevmode\vadjust pre{\hypertarget{ref-Ruckamp2011}{}}%
 Rückamp, M., Braun, M., Suckro, S., \& Blindow, N. (2011). Observed
@@
 
-\bibitem[\citeproctext]{ref-RuibalNunez2020}
+\leavevmode\vadjust pre{\hypertarget{ref-RuibalNunez2020}{}}%
 Ruibal Nuñez, J. (2020). \emph{{Impacto ecológico de la actividad
@@
 
-\bibitem[\citeproctext]{ref-Sahade2015}
+\leavevmode\vadjust pre{\hypertarget{ref-Sahade2015}{}}%
 Sahade, R., Lagger, C., Torre, L., Momo, F., Monien, P., Schloss, I.,
@@
 
-\bibitem[\citeproctext]{ref-Saunders2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Saunders2019}{}}%
 Saunders, R. A., Hill, S. L., Tarling, G. A., \& Murphy, E. J. (2019).
@@
 
-\bibitem[\citeproctext]{ref-Schejter2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Schejter2021}{}}%
 Schejter, L., \& Albano, M. (2021). Benthic communities at the marine
@@
 
-\bibitem[\citeproctext]{ref-Schloss2012}
+\leavevmode\vadjust pre{\hypertarget{ref-Schloss2012}{}}%
 Schloss, I. R., Abele, D., Moreau, S., Demers, S., Bers, A. V.,
@@
 
-\bibitem[\citeproctext]{ref-Schloss2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Schloss2023}{}}%
 Schloss, I. R., Pizarro, G., Cadaillon, A. M., Giesecke, R., Hernando,
@@
 
-\bibitem[\citeproctext]{ref-Schmidt2011}
+\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2011}{}}%
 Schmidt, K., Atkinson, A., Steigenberger, S., Fielding, S., Lindsay, M.
@@
 
-\bibitem[\citeproctext]{ref-Seco2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Seco2021}{}}%
 Seco, J., Aparício, S., Brierley, A. S., Bustamante, P., Ceia, F. R.,
@@
 
-\bibitem[\citeproctext]{ref-Sgarlatta2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Sgarlatta2023}{}}%
 Sgarlatta, M. (2023). \emph{Mechanisms driving tropicalization of
@@
 
-\bibitem[\citeproctext]{ref-Smale2008}
+\leavevmode\vadjust pre{\hypertarget{ref-Smale2008}{}}%
 Smale, Dan A., \& Barnes, D. K. A. (2008). Likely responses of the
@@
 
-\bibitem[\citeproctext]{ref-Smale2008a}
+\leavevmode\vadjust pre{\hypertarget{ref-Smale2008a}{}}%
 Smale, Dan A., Brown, K. M., Barnes, D. K. A., Fraser, K. P. P., \&
@@
 
-\bibitem[\citeproctext]{ref-Soeffker2022}
+\leavevmode\vadjust pre{\hypertarget{ref-Soeffker2022}{}}%
 Soeffker, M., Hollyman, P. R., Collins, M. A., Hogg, O. T., Riley, A.,
@@
 
-\bibitem[\citeproctext]{ref-Stouffer2011}
+\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2011}{}}%
 Stouffer, D. B., \& Bascompte, J. (2011). Compartmentalization increases
@@
 
-\bibitem[\citeproctext]{ref-Tamini2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Tamini2023}{}}%
 Tamini, L. L., Dellacasa, R. F., Chavez, L. N., Marinao, C. J., Góngora,
@@
 
-\bibitem[\citeproctext]{ref-Tarling2018}
+\leavevmode\vadjust pre{\hypertarget{ref-Tarling2018}{}}%
 Tarling, G. A., Ward, P., \& Thorpe, S. E. (2018). Spatial distributions
@@
 
-\bibitem[\citeproctext]{ref-Teixido2002}
+\leavevmode\vadjust pre{\hypertarget{ref-Teixido2002}{}}%
 Teixidó, N., Garrabou, J., \& Arntz, W. E. (2002). Spatial pattern
@@
 
-\bibitem[\citeproctext]{ref-Thompson2012}
+\leavevmode\vadjust pre{\hypertarget{ref-Thompson2012}{}}%
 Thompson, R. M., Brose, U., Dunne, J. A., Hall, R. O., Hladyz, S.,
@@
 
-\bibitem[\citeproctext]{ref-Thompson2007}
+\leavevmode\vadjust pre{\hypertarget{ref-Thompson2007}{}}%
 Thompson, R. M., Hemberg, M., Starzomski, B. M., \& Shurin, J. B.
@@
 
-\bibitem[\citeproctext]{ref-Trathan2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Trathan2023}{}}%
 Trathan, Philip N. (2023). The future of the {South Georgia} and {South
@@
 
-\bibitem[\citeproctext]{ref-Trathan2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Trathan2021}{}}%
 Trathan, P. N., Fielding, S., Hollyman, P. R., Murphy, E. J.,
@@
 
-\bibitem[\citeproctext]{ref-Turner2020}
+\leavevmode\vadjust pre{\hypertarget{ref-Turner2020}{}}%
 Turner, J., Guarino, M. V., Arnatt, J., Jena, B., Marshall, G. J.,
@@
 
-\bibitem[\citeproctext]{ref-Verges2019}
+\leavevmode\vadjust pre{\hypertarget{ref-Verges2019}{}}%
 Vergés, A., McCosker, E., Mayer-Pinto, M., Coleman, M. A., Wernberg, T.,
@@
 
-\bibitem[\citeproctext]{ref-Verges2014}
+\leavevmode\vadjust pre{\hypertarget{ref-Verges2014}{}}%
 Vergés, A., Steinberg, P. D., Hay, M. E., Poore, A. G. B., Campbell, A.
@@
 
-\bibitem[\citeproctext]{ref-Vinuesa2005}
+\leavevmode\vadjust pre{\hypertarget{ref-Vinuesa2005}{}}%
 Vinuesa, J. H. (2005). Distribución de crustáceos decápodos y
@@
 
-\bibitem[\citeproctext]{ref-Vinuesa2007}
+\leavevmode\vadjust pre{\hypertarget{ref-Vinuesa2007}{}}%
 Vinuesa, J. H., \& Varisco, M. (2007). Trophic ecology of the lobster
@@
 
-\bibitem[\citeproctext]{ref-Vucic-Pestic2011}
+\leavevmode\vadjust pre{\hypertarget{ref-Vucic-Pestic2011}{}}%
 Vucic-Pestic, O., Ehnes, R. B., Rall, B. C., \& Brose, U. (2011).
@@
 
-\bibitem[\citeproctext]{ref-Ward2018}
+\leavevmode\vadjust pre{\hypertarget{ref-Ward2018}{}}%
 Ward, P., Tarling, G. A., \& Thorpe, S. E. (2018). Temporal changes in
@@
 
-\bibitem[\citeproctext]{ref-Wege2021}
+\leavevmode\vadjust pre{\hypertarget{ref-Wege2021}{}}%
 Wege, M., Salas, L., \& LaRue, M. (2021). Ice matters: {Life-history}
@@
 
-\bibitem[\citeproctext]{ref-Whitehouse2008}
+\leavevmode\vadjust pre{\hypertarget{ref-Whitehouse2008}{}}%
 Whitehouse, M. J., Meredith, M. P., Rothery, P., Atkinson, A., Ward, P.,
@@
 
-\bibitem[\citeproctext]{ref-Whitworth1980}
+\leavevmode\vadjust pre{\hypertarget{ref-Whitworth1980}{}}%
 Whitworth, T. (1980). Zonation and geostrophic flow of the {Antarctic}
@@
 
-\bibitem[\citeproctext]{ref-Williams2000}
+\leavevmode\vadjust pre{\hypertarget{ref-Williams2000}{}}%
 Williams, R. J., \& Martinez, N. D. (2000). Simple rules yield complex
@@
 
-\bibitem[\citeproctext]{ref-Wood2015}
+\leavevmode\vadjust pre{\hypertarget{ref-Wood2015}{}}%
 Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
@@
 
-\bibitem[\citeproctext]{ref-Woods2023}
+\leavevmode\vadjust pre{\hypertarget{ref-Woods2023}{}}%
 Woods, B. L., Van de Putte, A. P., Hindell, M. A., Raymond, B.,
@@
 
-\bibitem[\citeproctext]{ref-Wu2012}
+\leavevmode\vadjust pre{\hypertarget{ref-Wu2012}{}}%
 Wu, L., Cai, W., Zhang, L., Nakamura, H., Timmermann, A., Joyce, T.,
@@
 
-\bibitem[\citeproctext]{ref-Yorio2009}
+\leavevmode\vadjust pre{\hypertarget{ref-Yorio2009}{}}%
 Yorio, P. (2009). Marine protected areas, spatial scales, and

### 2023-11-28 manuscript.tex
Update manuscript.tex

--- 2023-11-21 manuscript.tex
@@
 
+\subsection{Running Title: Marine stressors in the Southern
+Hemisphere}\label{running-title-marine-stressors-in-the-southern-hemisphere}
+
 Tomás I. Marina\textsuperscript{1}, Leonardo A.
@@
 
-\subsubsection{4.1 Main stressors effects on food webs in a southwest
+\subsubsection{4.1 Main stressor effects in food webs in a southwest
 Atlantic - Antarctic
-gradient}\label{main-stressors-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}
+gradient}\label{main-stressor-effects-in-food-webs-in-a-southwest-atlantic---antarctic-gradient}
 

### 2023-12-05 manuscript.tex
Update citation format

@@
 to tackle the complexity of species interactions, facilitating a better
-understanding of the structure and functioning of ecosystems (Belgrano,
-Scharler, Scharler, Dunne, \& Ulanowicz, 2005; Thompson et al., 2012).
-Trophic networks (or food webs) allow identifying properties and key
-species that may be crucial for ecosystem stability, and hence important
-for ecosystem management and biodiversity conservation (Thompson et al.,
-2012). There is a growing interest in understanding how ecological
-networks respond to environmental and anthropogenic stressors along
-geographical gradients (Cirtwill, Stouffer, \& Romanuk, 2015; Bauer et
-al., 2022). Yet, only a few studies have described variation in food web
-structure along latitudinal gradients in marine ecosystems. The few that
-have come from the Global North (Wood, Russell, Hanson, Williams, \&
-Dunne, 2015; Kortsch et al., 2019; Pecuchet et al., 2022), whereas no
+understanding of the structure and functioning of ecosystems (Belgrano
+et al. 2005; Thompson et al. 2012). Trophic networks (or food webs)
+allow identifying properties and key species that may be crucial for
+ecosystem stability, and hence important for ecosystem management and
+biodiversity conservation (Thompson et al. 2012). There is a growing
+interest in understanding how ecological networks respond to
+environmental and anthropogenic stressors along geographical gradients
+(Cirtwill et al. 2015; Bauer et al. 2022). Yet, only a few studies have
+described variation in food web structure along latitudinal gradients in
+marine ecosystems. The few that have come from the Global North (Wood et
+al. 2015; Kortsch et al. 2019; Pecuchet et al. 2022), whereas no
 studies, nor meta-analyses, on geographical variation in marine food
@@
 comprise one of the most biologically productive regions of the world's
-oceans (Acha, Mianzan, Guerrero, Favero, \& Bava, 2004; Latorre et al.,
-2023). The referred region extends from San Jorge Gulf (45ºS) in the
-Patagonian shelf to the Weddell Sea (78ºS) in the Southern Ocean, and
-covers a well-connected oceanic latitudinal gradient (R. P. Matano,
-Palma, \& Piola, 2010; Guihou, Piola, Palma, \& Chidichimo, 2020).
+oceans (Acha et al. 2004; Latorre et al. 2023). The referred region
+extends from San Jorge Gulf (45ºS) in the Patagonian shelf to the
+Weddell Sea (78ºS) in the Southern Ocean, and covers a well-connected
+oceanic latitudinal gradient (Matano et al. 2010; Guihou et al. 2020).
 
@@
 carried out addressing the trophic ecology of specific species and
-prey-predator relationships (Vinuesa \& Varisco, 2007; Pasotti et al.,
-2015; Saunders, Hill, Tarling, \& Murphy, 2019; Riccialdelli et al.,
-2020), but few studies have considered the complexity of the ecosystem
-in terms of a high resolution of species and their prey-predator
-interactions (but see Jacob et al. (2011), Marina et al. (2018), Funes,
-Saravia, Cordone, Iribarne, \& Galván (2022), López-López, Genner,
-Tarling, Saunders, \& O'Gorman (2022), Rodriguez, Marina, Schloss, \&
-Saravia (2022), Marina et al. (in rev.)). Neglecting this complexity
-might lead to a misunderstanding of the structure and functioning of the
-ecosystems, and ultimately reduce the ability to predict ecosystem
-responses to perturbations (Montoya, Woodward, Emmerson, \& Solé, 2009).
+prey-predator relationships (Vinuesa and Varisco 2007; Pasotti et al.
+2015; Saunders et al. 2019; Riccialdelli et al. 2020), but few studies
+have considered the complexity of the ecosystem in terms of a high
+resolution of species and their prey-predator interactions (but see
+Jacob et al. (2011), Marina et al. (2018), Funes et al. (2022),
+López-López et al. (2022), Rodriguez et al. (2022), Marina et al. (in
+rev.)). Neglecting this complexity might lead to a misunderstanding of
+the structure and functioning of the ecosystems, and ultimately reduce
+the ability to predict ecosystem responses to perturbations (Montoya et
+al. 2009).
 
@@
 marked with a red rectangle on the map. The map was drawn using the
-`marmap' R package (Pante, Simon-Bouhet, \& Irisson, 2023). Continental
-contour shapefiles were obtained from www.ign.gob.ar.}
+`marmap' R package (Pante et al. 2023). Continental contour shapefiles
+were obtained from www.ign.gob.ar.}
 \end{figure}
@@
 present two prominent frontal systems. These systems are the areas of
-highest productivity (Glembocki, Williams, Góngora, Gagliardini, \&
-Orensanz, 2015). The Gulf's productivity supports large invertebrate and
-vertebrate fisheries (Góngora, González-Zevallos, Pettovello, \& Mendía,
-2012), as well as marine mammal and seabird populations (Yorio, 2009).
+highest productivity (Glembocki et al. 2015). The Gulf's productivity
+supports large invertebrate and vertebrate fisheries (Góngora et al.
+2012), as well as marine mammal and seabird populations (Yorio 2009).
 The San Jorge Gulf food web comprises 165 nodes and 1015 trophic
@@
 Notably, these nodes present mid-trophic positions in the food web (3.0,
-2.5, 3.6 and 2, respectively) (Funes et al., 2022).
+2.5, 3.6 and 2, respectively) (Funes et al. 2022).
 
@@
 pattern, and a significant longitudinal gradient of glacial freshwater
-discharge (Schloss et al., 2023). Bruno, Riccialdelli, Acha, \&
-Fernández (2023) suggests that locally produced suspended particulate
-organic matter (mostly composed by phytoplankton) and organic matter
-accumulated in the sediments (macroalgae-originated detritus) are the
-primary food sources for the marine ecosystem, as opposed to
-allochthonous materials. Beagle Channel food web includes 145 nodes and
-1115 trophic interactions with a connectance of 0.05 (Table 1). The food
-web is suggested to have a wasp-waist structure, where the following
-species play a crucial role in the dynamics of the ecosystem: Fueguian
-sprat Sprattus fuegensis, longtail southern cod Patagonotothen ramsayi,
-black southern cod P. tessellata, frogmouth Cottoperca trigloides, and
-squat lobster Grimothea gregaria (Riccialdelli et al., 2020). Moreover,
-the squat lobster has been identified as a species responsible for
-linking modules and connecting the entire food web (Rodriguez et al.,
-2022).
+discharge (Schloss et al. 2023). Bruno et al. (2023) suggests that
+locally produced suspended particulate organic matter (mostly composed
+by phytoplankton) and organic matter accumulated in the sediments
+(macroalgae-originated detritus) are the primary food sources for the
+marine ecosystem, as opposed to allochthonous materials. Beagle Channel
+food web includes 145 nodes and 1115 trophic interactions with a
+connectance of 0.05 (Table 1). The food web is suggested to have a
+wasp-waist structure, where the following species play a crucial role in
+the dynamics of the ecosystem: Fueguian sprat Sprattus fuegensis,
+longtail southern cod Patagonotothen ramsayi, black southern cod P.
+tessellata, frogmouth Cottoperca trigloides, and squat lobster Grimothea
+gregaria (Riccialdelli et al. 2020). Moreover, the squat lobster has
+been identified as a species responsible for linking modules and
+connecting the entire food web (Rodriguez et al. 2022).
 
@@
 slope that reaches 4000 m in depth, respectively (Administración de
-Parques Nacionales, 2022) (Figure 1). Physical features in the plateau
+Parques Nacionales 2022) (Figure 1). Physical features in the plateau
 are fairly stable, with salinity averaging 34 all year round and
-temperature ranging between 4 and 8ºC (Acha et al., 2004). The plateau
-is surrounded by steep flanks of up to 4000 m depth, protected by the
+temperature ranging between 4 and 8ºC (Acha et al. 2004). The plateau is
+surrounded by steep flanks of up to 4000 m depth, protected by the
 Marine Protected Area Namuncurá - Burdwood Bank II (32,000 km2;
@@
 and mixing occur in relation to the slope, entraining deep nutrient-rich
-waters into the photic layer (Ricardo P. Matano, Palma, \& Combes,
-2019), and resulting in a fairly homogeneous water column both spatially
-and temporally (Ricardo P. Matano et al., 2019). The Burdwood Bank food
-web comprises 379 nodes and 1788 interactions, with a connectance of
-0.01, and an asymmetric degree distribution (i.e.~most of the species
-have a relatively low number of interactions and few species concentrate
-most of them). Almost half of the consumers are omnivores (0.48), and
-the network displays a small-world pattern (Marina et al., in rev.)
-(Table 1).
+waters into the photic layer (Matano et al. 2019), and resulting in a
+fairly homogeneous water column both spatially and temporally (Matano et
+al. 2019). The Burdwood Bank food web comprises 379 nodes and 1788
+interactions, with a connectance of 0.01, and an asymmetric degree
+distribution (i.e.~most of the species have a relatively low number of
+interactions and few species concentrate most of them). Almost half of
+the consumers are omnivores (0.48), and the network displays a
+small-world pattern (Marina et al. in rev.) (Table 1).
 
@@
 and South, with an approximate extension of 1.5 x 106 km2 and a depth
-range of 0 - 3000 m (E. j. Murphy et al., 2006) (Figure 1). Its
-oceanography is dominated by the Antarctic Circumpolar Current, which is
-spatially structured by frontal systems (Whitworth, 1980). The South
-Antarctic Circumpolar Current Front subdivides the Scotia Sea into two
+range of 0 - 3000 m (Murphy et al. 2006) (Figure 1). Its oceanography is
+dominated by the Antarctic Circumpolar Current, which is spatially
+structured by frontal systems (Whitworth 1980). The South Antarctic
+Circumpolar Current Front subdivides the Scotia Sea into two
 biogeographic regions: the Northern Scotia Sea is characterized by
@@
 lower and more stable temperatures and influenced by seasonal sea ice
-(Raymond, 2011). The analysis of the Northern and Southern Scotia Sea
+(Raymond 2011). The analysis of the Northern and Southern Scotia Sea
 food webs shows that the former is relatively more complex than the
@@
 network displays a greater proportion of omnivores and a lower mean
-trophic level (López-López et al., 2022) (Table 1).
+trophic level (López-López et al. 2022) (Table 1).
 
@@
 80 m maximum depth; and c) the external cove, ice-free for 60 years with
-a 185 m maximum depth and rocky substrate (Jerosch et al., 2018). Potter
+a 185 m maximum depth and rocky substrate (Jerosch et al. 2018). Potter
 Cove's high-latitude location results in variable environmental
 conditions due to photoperiod length seasonality. Sea ice often covers
-this area in winter (Schloss et al., 2012). With low phytoplankton
+this area in winter (Schloss et al. 2012). With low phytoplankton
 biomass, macroalgae, and microphytobenthos are likely the primary food
-sources for secondary benthic production (M. L. Quartino \& Boraso de
-Zaixso, 2008). The Potter Cove food web includes 110 nodes and 649
-interactions, with an asymmetric degree distribution, and a connectance
-value of 0.05 (Table 1). It presents a modular structure (groups of
-species interact more strongly with each other than with species
-belonging to other groups), that's positively associated with stability,
-since perturbation can be retained within modules (Rodriguez et al.,
-2022).
+sources for secondary benthic production (Quartino and Boraso de Zaixso
+2008). The Potter Cove food web includes 110 nodes and 649 interactions,
+with an asymmetric degree distribution, and a connectance value of 0.05
+(Table 1). It presents a modular structure (groups of species interact
+more strongly with each other than with species belonging to other
+groups), that's positively associated with stability, since perturbation
+can be retained within modules (Rodriguez et al. 2022).
 
 Located between 74 and 78ºS, the high Antarctic Weddell Sea shelf spans
-approximately 450 km from East to West (Jacob et al., 2011) (Figure 1).
+approximately 450 km from East to West (Jacob et al. 2011) (Figure 1).
 The water depth ranges from 200 to 500 m, with shallower regions being
@@
 benthic biomasses and an intermediate to high diversity when compared to
-benthic boreal communities (Teixidó, Garrabou, \& Arntz, 2002). The
-Weddell Sea food web exhibits a high level of network complexity,
-featuring the greatest number of nodes (490) and trophic interactions
-(16041) among the analyzed food webs in this review (Table 1). Its
-connectance (0.07) and other structural properties are intermediate
-compared to the other food webs. Recently, the interaction strengths of
-this food web were estimated, revealing the presence of numerous weak
-and few strong interactions, which is consistent with findings in other
-complex food webs (Nilsson \& McCann, 2016). Notably, this asymmetric
-distribution of interaction strength is likely to promote community
-persistence.
+benthic boreal communities (Teixidó et al. 2002). The Weddell Sea food
+web exhibits a high level of network complexity, featuring the greatest
+number of nodes (490) and trophic interactions (16041) among the
+analyzed food webs in this review (Table 1). Its connectance (0.07) and
+other structural properties are intermediate compared to the other food
+webs. Recently, the interaction strengths of this food web were
+estimated, revealing the presence of numerous weak and few strong
+interactions, which is consistent with findings in other complex food
+webs (Nilsson and McCann 2016). Notably, this asymmetric distribution of
+interaction strength is likely to promote community persistence.
 
@@
 quantifiable change, irrespective of its direction (increase or
-decrease), in a biological response (Orr et al., 2020). In the light of
+decrease), in a biological response (Orr et al. 2020). In the light of
 this, the southwest Atlantic - Antarctic marine biota has been and is
@@
 concert at any given time (e.g.~warming and fishery; acidification and
-contaminants) (Gutt et al., 2021), to date stressor assessments have
-been performed individually. Moreover, the potential for interactive
-effects of two or more stressors (synergy or antagonism) (Côté, Darling,
-\& Brown, 2016) is almost unknown for the region (Rowlands et al.,
-2021).
+contaminants) (Gutt et al. 2021), to date stressor assessments have been
+performed individually. Moreover, the potential for interactive effects
+of two or more stressors (synergy or antagonism) (Côté et al. 2016) is
+almost unknown for the region (Rowlands et al. 2021).
 
@@
 new trophic interactions to the food web which resulted in a decrease in
-trait variability and the stability of the system (Rincón-Díaz, Bovcon,
-Cochia, Góngora, \& Galván, 2021; Funes et al., 2022). Moreover, it
-changed the availability of prey to several predators. For example,
-Merluccius hubbsi one of the main bycatch species, became prey item to
-non-diving seabirds, like the kelp gull Larus dominicanus
-(González-Zevallos \& Yorio, 2006) and reef fishes (Funes, Marinao, \&
-Galván, 2019). Although juveniles of M. hubbsi are largely the main
-bycatch item, 29 other cartilaginous and 69 bony local fish species were
-also registered as incidental catch between 2005 and 2014 (Bovcon,
-Góngora, Marinao, \& González-Zevallos, 2013; Ruibal Nuñez, 2020). This
-level of impact triggered a shift in the functional diversity of the
-assemblages homogenizing the trophic function of fishes (Rincón-Díaz et
-al., 2021). Other functional changes were a decrease in the maximum
-sizes of individual fish, together with a drop in elasmobranchs biomass
-and an increase in crustaceans biomass (Funes, 2020). The significant
-increase in crustacean biomass was mostly due to the increase in
-Pleoticus muelleri and Grimothea gregaria populations (Funes, 2020).
-These species rapidly became the most important prey for the most
-abundant fishes in the area: M. hubbsi and Mustelus schmitti (Pasti et
-al., 2021). However, the above-mentioned effects of trawl fisheries on
-the structure and function of the San Jorge Gulf community may have
-changed again, since the fisheries ceased activity in 2015 (Annex I,
-Resolution CFP No 7/2018), remaining a small trawling artisanal fishery.
+trait variability and the stability of the system (Rincón-Díaz et al.
+2021; Funes et al. 2022). Moreover, it changed the availability of prey
+to several predators. For example, Merluccius hubbsi one of the main
+bycatch species, became prey item to non-diving seabirds, like the kelp
+gull Larus dominicanus (González-Zevallos and Yorio 2006) and reef
+fishes (Funes et al. 2019). Although juveniles of M. hubbsi are largely
+the main bycatch item, 29 other cartilaginous and 69 bony local fish
+species were also registered as incidental catch between 2005 and 2014
+(Bovcon et al. 2013; Ruibal Nuñez 2020). This level of impact triggered
+a shift in the functional diversity of the assemblages homogenizing the
+trophic function of fishes (Rincón-Díaz et al. 2021). Other functional
+changes were a decrease in the maximum sizes of individual fish,
+together with a drop in elasmobranchs biomass and an increase in
+crustaceans biomass (Funes 2020). The significant increase in crustacean
+biomass was mostly due to the increase in Pleoticus muelleri and
+Grimothea gregaria populations (Funes 2020). These species rapidly
+became the most important prey for the most abundant fishes in the area:
+M. hubbsi and Mustelus schmitti (Pasti et al. 2021). However, the
+above-mentioned effects of trawl fisheries on the structure and function
+of the San Jorge Gulf community may have changed again, since the
+fisheries ceased activity in 2015 (Annex I, Resolution CFP No 7/2018),
+remaining a small trawling artisanal fishery.
 
@@
 Gulf, because of the southward shifts of northern fish populations to
-the Gulf (Galván et al., 2022). The San Jorge Gulf is especially prone
-to be affected by climate-driven shifts in species ranges, because it is
+the Gulf (Galván et al. 2022). The San Jorge Gulf is especially prone to
+be affected by climate-driven shifts in species ranges, because it is
 located in the ecotone between two biogeographic provinces, the
-Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) (Balech \&
-Ehrlich, 2008). In addition to this tropicalization from northern fish
+Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) (Balech and
+Ehrlich 2008). In addition to this tropicalization from northern fish
 populations, alien species are also documented to affect the demersal
-assemblage (fish and macroinvertebrates) in the Gulf (Galván et al.,
+assemblage (fish and macroinvertebrates) in the Gulf (Galván et al.
 2022). Finally, San Jorge Gulf is exposed to urban and industrial
@@
 oil transport along the Patagonian coast registered several oil spills
-and chronic oil discharges (García-Borboroglu, Boersma, Reyes, \&
-Skewgar, 2008). Other marine systems impacted by oil spill showed an
-important decrease in marine bird populations (Irons, Kendall, Erickson,
-McDonald, \& Lance, 2000), seals and macroalgae (e.g. Paine et al.
-(1996)), with examples of cascading effects throughout the food web
-(Peterson, 2001).
+and chronic oil discharges (García-Borboroglu et al. 2008). Other marine
+systems impacted by oil spill showed an important decrease in marine
+bird populations (Irons et al. 2000), seals and macroalgae (e.g. Paine
+et al. (1996)), with examples of cascading effects throughout the food
+web (Peterson 2001).
 
@@
 dates back to April 2006, and its population has been expanding since
-then (Nardi, Fernández, Vanella, \& Chalde, 2019). Being a top predator
-Chinook salmon can compete with several native species in the Beagle
-Channel (Correa \& Gross, 2008), and prey over native species such as
-Notothenioids (Eleginops maclovinus, Patagonotothen tessellata, P.
-cornucola, P. sima, Paranotothenia magellanica, Harpagifer bispinis),
-the Atherinidae Odontesthes smitti and O. nigricans, the Fuegian sprat
-Sprattus fuegensis, and larvae of king crabs (Lithodes antarcticus and
-Paralomis granulosa) (Fernández, Ciancio, Ceballos, Riva-Rossi, \&
-Pascual, 2010). Ciancio, Pascual, Botto, Frere, \& Iribarne (2008)
-observed that Chinook salmon in the Southern Patagonian Shelf Ecosystem
-Area primarily feed on sprats and display trophic levels comparable to
-those of intermediate-sized fish and cephalopod predators species,
-showing significant dietary overlap with Magellanic penguins (Spheniscus
+then (Nardi et al. 2019). Being a top predator Chinook salmon can
+compete with several native species in the Beagle Channel (Correa and
+Gross 2008), and prey over native species such as Notothenioids
+(Eleginops maclovinus, Patagonotothen tessellata, P. cornucola, P. sima,
+Paranotothenia magellanica, Harpagifer bispinis), the Atherinidae
+Odontesthes smitti and O. nigricans, the Fuegian sprat Sprattus
+fuegensis, and larvae of king crabs (Lithodes antarcticus and Paralomis
+granulosa) (Fernández et al. 2010). Ciancio et al. (2008) observed that
+Chinook salmon in the Southern Patagonian Shelf Ecosystem Area primarily
+feed on sprats and display trophic levels comparable to those of
+intermediate-sized fish and cephalopod predators species, showing
+significant dietary overlap with Magellanic penguins (Spheniscus
 magellanicus). Another potential competitor for Chinook salmon in the
 Beagle Channel is the Commerson's dolphin (Cephalorhynchus commersonii),
-which shares a similar diet (Riccialdelli et al., 2013).
+which shares a similar diet (Riccialdelli et al. 2013).
 
@@
 reported varying heavy metal levels in sea mussel tissues and sediments,
-indicating bioavailability differences (Duarte, Giarratano, Amin, \&
-Comoglio, 2011). Other research found similar carbon and carbohydrate
-levels in Ushuaia Bay's surface sediments to those in hypertrophic
-ecosystems, along with hydrocarbons and heavy metals linked to port and
-industrial activities (Gil, Torres, Amin, \& Esteves, 2011).
-Commendatore, Nievas, Amin, \& Esteves (2012) identified three distinct
+indicating bioavailability differences (Duarte et al. 2011). Other
+research found similar carbon and carbohydrate levels in Ushuaia Bay's
+surface sediments to those in hypertrophic ecosystems, along with
+hydrocarbons and heavy metals linked to port and industrial activities
+(Gil et al. 2011). Commendatore et al. (2012) identified three distinct
 hydrocarbon accumulation zones in the Bay. Llorca et al. (2012) found
 high levels of perfluorinated compounds in algae, fish, and guano.
-Ferreira, Lo Nostro, Fernández, \& Genovese (2021) showed that black
-southern cod in Ushuaia Bay may be exposed to endocrine-disrupting
-compounds from urban and industrial pollution. Pérez et al. (2020) and
-Ojeda et al. (2021) found microplastics in M. edulis chilensis and
-Nacella magellanica, respectively. These studies link pollutants to
-Ushuaia (54°48′S 68°18′W) and its port and industrial activities. We
-expect the Beagle Channel area closest to the city to be most affected.
-Contaminants can spread through the food web, magnifying the risk to
-higher-level organisms. Fioramonti, Ribeiro Guevara, Becker, \&
-Riccialdelli (2022) studied mercury transfer in three southwest Atlantic
-Ocean food webs and found biodilution in the Beagle Channel and Atlantic
-coast of Tierra del Fuego webs. However, mercury concentrations rose
-with benthivory in these webs, and higher mercury was found in
+Ferreira et al. (2021) showed that black southern cod in Ushuaia Bay may
+be exposed to endocrine-disrupting compounds from urban and industrial
+pollution. Pérez et al. (2020) and Ojeda et al. (2021) found
+microplastics in M. edulis chilensis and Nacella magellanica,
+respectively. These studies link pollutants to Ushuaia (54°48′S 68°18′W)
+and its port and industrial activities. We expect the Beagle Channel
+area closest to the city to be most affected. Contaminants can spread
+through the food web, magnifying the risk to higher-level organisms.
+Fioramonti et al. (2022) studied mercury transfer in three southwest
+Atlantic Ocean food webs and found biodilution in the Beagle Channel and
+Atlantic coast of Tierra del Fuego webs. However, mercury concentrations
+rose with benthivory in these webs, and higher mercury was found in
 phytoplankton and Grimothea gregaria. Squat lobsters connect pelagic and
 benthic habitats, so any disruption to them could disrupt the food web
-(Rodriguez et al., 2022). Dodino et al. (2022) found the highest mercury
+(Rodriguez et al. 2022). Dodino et al. (2022) found the highest mercury
 levels in Magellanic penguin feathers from offshore colonies in Tierra
@@
 biodiversity and changes in macroalgae composition due to urban
-pollution (Kaminsky et al., in prep.).
+pollution (Kaminsky et al. in prep.).
 
@@
 known to be occurring at a regional scale (e.g.~sea surface warming,
-Franco, Combes, \& González Carman (2020)) (Table S2). Several fisheries
-targeting demersal fishes operate in the vicinity and within the
-ecosystem of the Marine Protected Areas (i.e.~Marine National Reserve
-management category). The Patagonian fisheries on the toothfish
-Dissostichus eleginoides has gained prominence in recent years (L.
-Allega et al., 2020; Gorini, Lukaszewicz, \& Giussi, 2021). Although
-these are regulated by the Argentinean government, incidental catches do
-occur, where demersal fishes of the genera Coelorinchus and Macrourus,
-seabirds and benthic invertebrates (30+ taxa) are the most common
-bycatches (Gaitán \& Marí, 2016; Martínez, Wöhler, Troccoli, Di Marco,
-\& Maydana, 2022). Noteworthy, among the invertebrates caught, 8 species
-are indicator taxa of vulnerable marine ecosystems (Gaitán \& Marí,
-2016; Schejter \& Albano, 2021). Independent assessments of these
-bycatches suggest no significant impact on the communities (Gaitán \&
-Marí, 2016; Martínez et al., 2022). Besides bycatch, species of seabirds
-are being affected by the fishery due to discards, altering its diet;
-the most frequently encountered species are Black-browed albatross
-Thalassarche melanophris, Southern giant petrel Macronectes giganteus,
-Cape petrel Daption capense, Southern royal albatross Diomedea
-epomophora, Northern giant petrel M. halli, and White-chinned petrel
-Procellaria aequinoctialis (Tamini et al., 2023). Nevertheless, there is
-a lack of knowledge considering the species' role in the ecosystem and
-the potential joint effect of both target fishes and bycatch in a
-broader food web framework.
+Franco et al. (2020)) (Table S2). Several fisheries targeting demersal
+fishes operate in the vicinity and within the ecosystem of the Marine
+Protected Areas (i.e.~Marine National Reserve management category). The
+Patagonian fisheries on the toothfish Dissostichus eleginoides has
+gained prominence in recent years (Allega et al. 2020; Gorini et al.
+2021). Although these are regulated by the Argentinean government,
+incidental catches do occur, where demersal fishes of the genera
+Coelorinchus and Macrourus, seabirds and benthic invertebrates (30+
+taxa) are the most common bycatches (Gaitán and Marí 2016; Martínez et
+al. 2022). Noteworthy, among the invertebrates caught, 8 species are
+indicator taxa of vulnerable marine ecosystems (Gaitán and Marí 2016;
+Schejter and Albano 2021). Independent assessments of these bycatches
+suggest no significant impact on the communities (Gaitán and Marí 2016;
+Martínez et al. 2022). Besides bycatch, species of seabirds are being
+affected by the fishery due to discards, altering its diet; the most
+frequently encountered species are Black-browed albatross Thalassarche
+melanophris, Southern giant petrel Macronectes giganteus, Cape petrel
+Daption capense, Southern royal albatross Diomedea epomophora, Northern
+giant petrel M. halli, and White-chinned petrel Procellaria
+aequinoctialis (Tamini et al. 2023). Nevertheless, there is a lack of
+knowledge considering the species' role in the ecosystem and the
+potential joint effect of both target fishes and bycatch in a broader
+food web framework.
 
 Anthropogenic contaminants such as microplastics and mercury are present
-in the water column of the Burdwood Bank ecosystem (Cossi et al., 2021;
-Di Mauro et al., 2022; Fioramonti et al., 2022). Microplastics are
+in the water column of the Burdwood Bank ecosystem (Cossi et al. 2021;
+Fioramonti et al. 2022; Di Mauro et al. 2022). Microplastics are
 distributed all along the water column, from surface to deep waters
-(3-2450 m) (Di Mauro et al., 2022). More importantly, microplastics were
+(3-2450 m) (Di Mauro et al. 2022). More importantly, microplastics were
 found in soft tissues of benthic macroinvertebrates (sea stars Henricia
@@
 but could also get it indirectly from prey organisms already containing
-plastics in their tissues (Cossi et al., 2021). Notably, one of the
+plastics in their tissues (Cossi et al. 2021). Notably, one of the
 contaminated species, the long tail southern cod Patagonotothen ramsayi,
 is part of the core group of species that drive the ecosystem through
-the suggested wasp-waist control (Riccialdelli et al., 2020). Mercury
+the suggested wasp-waist control (Riccialdelli et al. 2020). Mercury
 transfer and biomagnification are ongoing processes in the ecosystem,
 which are occurring at a greater pace than near coastal areas (Beagle
-Channel) (Fioramonti et al., 2022). It's important to note that the
+Channel) (Fioramonti et al. 2022). It's important to note that the
 Fuegian sprat Sprattus fuegensis, a pelagic fish with a mid-trophic
 level in the food web, presented the highest levels of mercury
-(Fioramonti et al., 2022). Considering the wasp-waist control of the
-Fuegian sprat in the food web (Riccialdelli et al., 2020), a rapid and
+(Fioramonti et al. 2022). Considering the wasp-waist control of the
+Fuegian sprat in the food web (Riccialdelli et al. 2020), a rapid and
 widespread contamination to the top predators is expected (Fioramonti et
-al., 2022).
+al. 2022).
 
@@
 and seabirds are well-known for other regions of the world (Nowacek et
-al., 2015), there is no particular knowledge for this ecosystem.
-However, several documents warn of the potential negative effects this
-may have on the species inhabiting the Burdwood Bank area (Lucrecia
-Allega et al., 2019; de Haro et al., 2022).
+al. 2015), there is no particular knowledge for this ecosystem. However,
+several documents warn of the potential negative effects this may have
+on the species inhabiting the Burdwood Bank area (Allega et al. 2019; de
+Haro et al. 2022).
 
 Despite evidence of warming at surface, mid-water and bottom layers (100
-m) in Burdwood Bank (Franco et al., 2020), specific studies on the
+m) in Burdwood Bank (Franco et al. 2020), specific studies on the
 oceanographic aspects of the system are lacking. In this sense, there is
@@
 The Scotia Sea has experienced one of the largest levels of warming
-within the polar regions (Whitehouse et al., 2008). Together with the
+within the polar regions (Whitehouse et al. 2008). Together with the
 Southern Annular Mode anomalies this has caused a long-term decrease in
 krill abundance; more pronounced in the northern than in the southern
-Scotia Sea (E. J. Murphy et al., 2007). Over the past 90 years, the
-krill also showed an increase in mean body length (Atkinson et al.,
-2019), which may also alter predator-prey interactions and allow
-reaching cooler feeding grounds near the seabed, with the potential to
-link krill to unexpected predators (Schmidt et al., 2011). Another
-consequence of the mentioned environmental stressors, is a change in
-krill distribution due to a southward contraction (Atkinson et al.,
-2019). It is noteworthy here, that the distributional shift has not
-affected all species inhabiting the Northern Scotia Sea, and most
-abundant calanoid copepods have maintained their distribution (Tarling,
-Ward, \& Thorpe, 2018). Considering the above, food web models of the
-Northern Scotia Sea have suggested shifts in the structure and
-functioning of the food web, from krill-based to non-krill-based, where
-myctophid fishes and squid are playing important roles (Saunders et al.,
-2019).
+Scotia Sea (Murphy et al. 2007). Over the past 90 years, the krill also
+showed an increase in mean body length (Atkinson et al. 2019), which may
+also alter predator-prey interactions and allow reaching cooler feeding
+grounds near the seabed, with the potential to link krill to unexpected
+predators (Schmidt et al. 2011). Another consequence of the mentioned
+environmental stressors, is a change in krill distribution due to a
+southward contraction (Atkinson et al. 2019). It is noteworthy here,
+that the distributional shift has not affected all species inhabiting
+the Northern Scotia Sea, and most abundant calanoid copepods have
+maintained their distribution (Tarling et al. 2018). Considering the
+above, food web models of the Northern Scotia Sea have suggested shifts
+in the structure and functioning of the food web, from krill-based to
+non-krill-based, where myctophid fishes and squid are playing important
+roles (Saunders et al. 2019).
 
@@
 also the many predators that depend on it as a food source (Hilborn et
-al., 2017). Yet, data currently available from monitoring of krill and
+al. 2017). Yet, data currently available from monitoring of krill and
 its predators remain insufficient, hence identifying the potential
-fishery impacts on the ecosystem is difficult (P. N. Trathan et al.,
-2021). Apart from krill fishery, two other commercial fisheries operate
-in the Scotia Sea, targeting Patagonian toothfish species Dissostichus
+fishery impacts on the ecosystem is difficult (Trathan et al. 2021).
+Apart from krill fishery, two other commercial fisheries operate in the
+Scotia Sea, targeting Patagonian toothfish species Dissostichus
 eleginoides and D. mawsoni. The D. eleginoides stock is linked to the
-stock at South Georgia (`Northern Scotia Sea') (Collins, Brickle, Brown,
-\& Belchier, 2010), while the D. mawsoni stock is linked to the
-Antarctic continental shelf (`Southern Scotia Sea') (Soeffker et al.,
-2022). Despite the fact that the mentioned fisheries are certified by
-the Marine Stewardship Council standards, Philip N. Trathan (2023)
-identified several concerns regarding aspects of fisheries itself, other
-species' population status (i.e.~recovery of baleen whales), and
-environmental stressors (i.e.~sea warming), which could have synergistic
-effects on the food web structure and functioning that are still
-unknown.
+stock at South Georgia (`Northern Scotia Sea') (Collins et al. 2010),
+while the D. mawsoni stock is linked to the Antarctic continental shelf
+(`Southern Scotia Sea') (Soeffker et al. 2022). Despite the fact that
+the mentioned fisheries are certified by the Marine Stewardship Council
+standards, Trathan (2023) identified several concerns regarding aspects
+of fisheries itself, other species' population status (i.e.~recovery of
+baleen whales), and environmental stressors (i.e.~sea warming), which
+could have synergistic effects on the food web structure and functioning
+that are still unknown.
 
@@
 (e.g.~Dissostichus eleginoides, Gymnoscopelus nicholsi), and seabirds
-(Seco et al., 2021). During years of low Antarctic krill abundance,
+(Seco et al. 2021). During years of low Antarctic krill abundance,
 predators must deal with both the stress of reduced prey availability
-and the concurrent rise in mercury exposure (Seco et al., 2021).
+and the concurrent rise in mercury exposure (Seco et al. 2021).
 
@@
 factors driving changes in Potter Cove (Western Antarctic Peninsula)
-(Chown et al., 2022). Sudden environmental changes have occurred, such
-as sea surface temperature increase, salinity decrease, suspended
+(Chown et al. 2022). Sudden environmental changes have occurred, such as
+sea surface temperature increase, salinity decrease, suspended
 particulate matter loading and chlorophyll-a increase, all linked to
 climatic cycles (Southern Annular Mode and El Niño Southern Oscillation)
-(Schloss et al., 2012). Particularly, sea warming has produced drastic
+(Schloss et al. 2012). Particularly, sea warming has produced drastic
 environmental and biological transformations (e.g.~shifts in dominance
-of benthic community) in the Potter Cove ecosystem (Schloss et al.,
-2012; María Liliana Quartino, Deregibus, Campana, Latorre, \& Momo,
-2013; Sahade et al., 2015), a system highly dependent on sea-ice
-dynamics (Table S2). In Potter Cove, total sea ice cover has decreased
-since 1991 (Schloss et al., 2012). Changes in the annual timing of
-landfast ice formation and breakup of the sea ice cover has multiple
-effects on species in the food web (Michel et al., 2019). Warmer winters
+of benthic community) in the Potter Cove ecosystem (Schloss et al. 2012;
+Quartino et al. 2013; Sahade et al. 2015), a system highly dependent on
+sea-ice dynamics (Table S2). In Potter Cove, total sea ice cover has
+decreased since 1991 (Schloss et al. 2012). Changes in the annual timing
+of landfast ice formation and breakup of the sea ice cover has multiple
+effects on species in the food web (Michel et al. 2019). Warmer winters
 and springs result in earlier sea-ice melt, causing an abrupt increase
-in the light available benthic primary producers (Dolores Deregibus et
-al., 2020). Sea ice also mediates physical disturbances to the benthos
-by influencing sedimentation and iceberg scouring. These factors affect
-the production of macroalgae, albeit in opposite ways (D. Deregibus,
-Quartino, Zacher, Campana, \& Barnes, 2017), and microphytobenthos
-(Hoffmann et al., 2019). On the other hand, sea ice is an important
-habitat for diatoms and its associated consumers, including copepods and
-krill (Flores et al., 2012), and thus important for bentho-pelagic
-nutrient and carbon cycling during winter. Additionally, a decrease in
-winter sea ice cover produces an increase in physical perturbation on
-benthic shallow communities in coastal shallows due to ice scouring (D.
-Deregibus et al., 2017). The glacier surrounding Potter Cove has been
-receding at an increasing rate since 1950 (Rückamp, Braun, Suckro, \&
-Blindow, 2011), which has caused a massive discharge of sediment-laden
-meltwater (Meredith et al., 2018). Large quantities of suspended
+in the light available benthic primary producers (Deregibus et al.
+2020). Sea ice also mediates physical disturbances to the benthos by
+influencing sedimentation and iceberg scouring. These factors affect the
+production of macroalgae, albeit in opposite ways (Deregibus et al.
+2017), and microphytobenthos (Hoffmann et al. 2019). On the other hand,
+sea ice is an important habitat for diatoms and its associated
+consumers, including copepods and krill (Flores et al. 2012), and thus
+important for bentho-pelagic nutrient and carbon cycling during winter.
+Additionally, a decrease in winter sea ice cover produces an increase in
+physical perturbation on benthic shallow communities in coastal shallows
+due to ice scouring (Deregibus et al. 2017). The glacier surrounding
+Potter Cove has been receding at an increasing rate since 1950 (Rückamp
+et al. 2011), which has caused a massive discharge of sediment-laden
+meltwater (Meredith et al. 2018). Large quantities of suspended
 particles affect growth, survival and reproduction of benthic species.
@@
 filter feeders--ascidian domination to a mixed assemblage with
-scavengers and opportunistic species (Sahade et al., 2015), and the
+scavengers and opportunistic species (Sahade et al. 2015), and the
 metabolic balance in benthos went from net autotrophy to heterotrophy
-(Braeckman et al., 2021). Additionally, massive stranding events of the
+(Braeckman et al. 2021). Additionally, massive stranding events of the
 tunicate Salpa thompsoni and the euphausiid Euphausia superba (krill)
 linked to the presence of glacial meltwater have been reported (Fuentes
-et al., 2016). Rising temperatures leading to ice and glacial melting
-has also substantial impacts on pelagic primary productivity, since it
+et al. 2016). Rising temperatures leading to ice and glacial melting has
+also substantial impacts on pelagic primary productivity, since it
 reduces water salinity, affecting water column stratification, light
-penetration and nutrient availability for photosynthesis (Schloss et
-al., 2012). In Potter Cove, changes in biomass of most phytoplankton
-species have been observed under heat wave conditions, resulting in a
-shift from a microplankton to a nanoplankton dominated community (Antoni
-et al., 2020; Latorre et al., 2023). This means that in areas strongly
-affected by glacier melt, the planktonic food web is dominated by the
-microbial loop (ciliates and heterotrophic dinoflagellates preys upon
+penetration and nutrient availability for photosynthesis (Schloss et al.
+2012). In Potter Cove, changes in biomass of most phytoplankton species
+have been observed under heat wave conditions, resulting in a shift from
+a microplankton to a nanoplankton dominated community (Antoni et al.
+2020; Latorre et al. 2023). This means that in areas strongly affected
+by glacier melt, the planktonic food web is dominated by the microbial
+loop (ciliates and heterotrophic dinoflagellates preys upon
 nanophytoplankton, which are sequentially available prey for small
 omnivorous copepods), instead of being predominantly herbivorous (Garcia
-et al., 2016, 2019). In addition, phytoplankton species under these
+et al. 2016, 2019). In addition, phytoplankton species under these
 warming conditions showed a decrease in metabolic rates and in the
-quality of the fatty acids composition (Latorre et al., 2023).
+quality of the fatty acids composition (Latorre et al. 2023).
 
@@
 reduction in sea ice is suggested to be driving changes in pelagic and
-benthic communities (Constable et al., 2014; Gutt et al., 2021). Sea ice
+benthic communities (Constable et al. 2014; Gutt et al. 2021). Sea ice
 extent has reached new record lows since the satellite era began in
@@
 temperature for February reached 1.45°C, the highest monthly mean ever
-recorded (0.56°C above the climatological mean) (Turner et al., 2020).
-In this context, it has been suggested that Antarctic krill Euphausia
+recorded (0.56°C above the climatological mean) (Turner et al. 2020). In
+this context, it has been suggested that Antarctic krill Euphausia
 superba has already declined as a result of productivity changes caused
-by sea ice declines (Atkinson, Siegel, Pakhomov, \& Rothery, 2004).
-Declining sea ice cover allows increased access to krill by predators
-(Kawaguchi, Nicol, \& Press, 2009), which further contributes to
-decreased krill abundances. This in turn can result in reduced carbon
-export due to decreased fecal pellets from krill (Pauli et al., 2021).
+by sea ice declines (Atkinson et al. 2004). Declining sea ice cover
+allows increased access to krill by predators (Kawaguchi et al. 2009),
+which further contributes to decreased krill abundances. This in turn
+can result in reduced carbon export due to decreased fecal pellets from
+krill (Pauli et al. 2021).
 
 On the other hand, sea ice loss increases light availability, triggering
-primary production by phytoplankton in the short-term (Pineda-Metz,
-Gerdes, \& Richter, 2020). Furthermore, a warmer and more stable water
-column with a shallow upper mixed layer, is expected to enhance the
-dominance of cryptophytes over diatoms which may favor salp populations
-over krill populations; thereby reducing the magnitude of energy
-transfer to higher trophic levels and the seabed (Isla, 2023).
+primary production by phytoplankton in the short-term (Pineda-Metz et
+al. 2020). Furthermore, a warmer and more stable water column with a
+shallow upper mixed layer, is expected to enhance the dominance of
+cryptophytes over diatoms which may favor salp populations over krill
+populations; thereby reducing the magnitude of energy transfer to higher
+trophic levels and the seabed (Isla 2023).
 
@@
 increased oxygen demand, most notothenioid fishes are stenothermal and
-unable to adjust their metabolic functioning (Mintenbeck et al., 2012).
+unable to adjust their metabolic functioning (Mintenbeck et al. 2012).
 It is anticipated that the thermal habitat preferred by the Antarctic
 toothfish Dissostichus mawsoni could undergo contraction in the coming
-three decades (Constable et al., 2014), further emphasizing the
-potential impact of global warming effects on these species. Marine
-mammals, Weddell and crabeater seals (Leptonychotes weddellii and
-Lobodon carcinophagus), exhibit varying levels of sensitivity. The
-latter exhibits a preference for breeding in close proximity to krill
-swarms, and thus is particularly susceptible to reductions in sea ice
+three decades (Constable et al. 2014), further emphasizing the potential
+impact of global warming effects on these species. Marine mammals,
+Weddell and crabeater seals (Leptonychotes weddellii and Lobodon
+carcinophagus), exhibit varying levels of sensitivity. The latter
+exhibits a preference for breeding in close proximity to krill swarms,
+and thus is particularly susceptible to reductions in sea ice
 concentrations and sea surface temperatures. Rescued sea ice can
 significantly affect their post- and future breeding foraging success
-(Wege, Salas, \& LaRue, 2021). In addition, the Antarctic petrel
-Thalassoica antarctica, which is one of the most abundant seabirds in
-the area, is a sea ice dependent forager and breeder (Orgeira, Alvarez,
-\& Salvó, 2021); therefore the loss of this habitat will degrade its
-foraging success and reproductive output over time. The snow petrel
-Pagodroma nivea also relies heavily on sea ice for foraging and its
-colonies in the Weddell Sea may be affected. The emperor penguin
-Aptenodytes forsteri uses sea ice for breeding; any reductions could
-constrain its populations, as evidenced by recent observations in the
-Bellingshausen Sea region (Fretwell, Boutet, \& Ratcliffe, 2023). The
-Arctic tern Sterna paradisaea spends the summer in the Weddell Sea
-exploiting krill swarms under receding ice edges, then declines in ice
-cover may reduce prey availability and quality of molting habitats.
-Continued warming is thus expected to gradually erode the abundance and
-distribution of these `primary species' that dominate the avifauna of
-the Weddell Sea through loss of critical sea ice habitat (Orgeira et
-al., 2021). Variations in sea ice extent have implications for great
-whales, such as the Humpback whale Megaptera novaeangliae, since their
-primary prey resource is the Antarctic krill (Braithwaite, Meeuwig,
-Letessier, Jenner, \& Brierley, 2015). Decreased winter ice coverage
+(Wege et al. 2021). In addition, the Antarctic petrel Thalassoica
+antarctica, which is one of the most abundant seabirds in the area, is a
+sea ice dependent forager and breeder (Orgeira et al. 2021); therefore
+the loss of this habitat will degrade its foraging success and
+reproductive output over time. The snow petrel Pagodroma nivea also
+relies heavily on sea ice for foraging and its colonies in the Weddell
+Sea may be affected. The emperor penguin Aptenodytes forsteri uses sea
+ice for breeding; any reductions could constrain its populations, as
+evidenced by recent observations in the Bellingshausen Sea region
+(Fretwell et al. 2023). The Arctic tern Sterna paradisaea spends the
+summer in the Weddell Sea exploiting krill swarms under receding ice
+edges, then declines in ice cover may reduce prey availability and
+quality of molting habitats. Continued warming is thus expected to
+gradually erode the abundance and distribution of these `primary
+species' that dominate the avifauna of the Weddell Sea through loss of
+critical sea ice habitat (Orgeira et al. 2021). Variations in sea ice
+extent have implications for great whales, such as the Humpback whale
+Megaptera novaeangliae, since their primary prey resource is the
+Antarctic krill (Braithwaite et al. 2015). Decreased winter ice coverage
 results in reduced suitable habitat and lower krill abundance
-(Braithwaite et al., 2015), with flow-on effects for whale body
-condition observed historically in harvest data. With climate
-projections indicating ongoing sea ice losses, further threats to
-critical krill populations pose risks to the energy intake and
-reproductive success and long-term viability of humpback whale
-populations dependent on consistent Antarctic feeding (Pallin et al.,
-2023).
+(Braithwaite et al. 2015), with flow-on effects for whale body condition
+observed historically in harvest data. With climate projections
+indicating ongoing sea ice losses, further threats to critical krill
+populations pose risks to the energy intake and reproductive success and
+long-term viability of humpback whale populations dependent on
+consistent Antarctic feeding (Pallin et al. 2023).
 
 Iceberg scouring is a major factor in the high biodiversity of benthic
-communities in the Weddell Sea (Gutt \& Starmans, 2001). Even at 600 m
+communities in the Weddell Sea (Gutt and Starmans 2001). Even at 600 m
 depths, iceberg scouring has a strong effect on the benthic environment,
@@
 square meters on the Antarctic continental shelf. Global warming is
-predicted to raise iceberg scouring frequency (Gutt, 2001; Dan A. Smale,
-Brown, Barnes, Fraser, \& Clarke, 2008), disrupting the environment (Dan
-A. Smale \& Barnes, 2008). Gutt et al. (2015) expects tipping points are
-significant due to these effects and lack of knowledge.
+predicted to raise iceberg scouring frequency (Gutt 2001; Smale et al.
+2008), disrupting the environment (Smale and Barnes 2008). Gutt et al.
+(2015) expects tipping points are significant due to these effects and
+lack of knowledge.
 
@@
 can capture the effects of individual and multiple stressors on
-communities and ecosystems (Montoya et al., 2009; O'Gorman, Fitch, \&
-Crowe, 2012; Bruder, Frainer, Rota, \& Primicerio, 2019).
+communities and ecosystems (Montoya et al. 2009; O'Gorman et al. 2012;
+Bruder et al. 2019).
 
@@
 species may have more significant effects on the food web robustness to
-perturbations than low-degree species. & Dunne, Williams, \& Martinez
-(2002a); Jordán, Benedek, \& Podani (2007) \\
+perturbations than low-degree species. & Dunne et al. (2002b); Jordán et
+al. (2007) \\
 Trophic position & Place in the food web relative to the basal resources
@@
 communities if ecosystem control is bottom-up, wasp-waist or top-down,
-respectively. & Williams \& Martinez (2000); Thompson, Hemberg,
-Starzomski, \& Shurin (2007) \\
+respectively. & Williams and Martinez (2000); Thompson et al. (2007) \\
 Omnivory & Consumer resource use across trophic levels. & High-omnivore
@@
 expected to have large effects on the stability and energy flux of the
-food and ecosystem, respectively. & Nilsson \& McCann (2016) \\
+food and ecosystem, respectively. & Nilsson and McCann (2016) \\
 \emph{Network-level} & & & \\
@@
 Estimator of community sensitivity to stressors. High connectance gives
-resistance and resilience to the food web. & Dunne, Williams, \&
-Martinez (2002b) \\
+resistance and resilience to the food web. & Dunne et al. (2002a) \\
 Path length & Average distance, accounted by the number of interactions,
 between any pair of species. & Short distances enhance rapid and broad
-propagation of perturbations. & Albert \& Barabási (2002) \\
+propagation of perturbations. & Albert and Barabási (2002) \\
 Mean TL & Average of all species' trophic position contained in the food
@@
 & It provides trophic flexibility to an ecosystem. Reduces probability
-of trophic cascades. & Kratina, LeCraw, Ingram, \& Anholt (2012) \\
+of trophic cascades. & Kratina et al. (2012) \\
 \end{longtable}
@@
 on marine species regarding distributional shifts induced by warming of
-marine currents (Wu et al., 2012; Poloczanska et al., 2013; Vergés et
-al., 2019). Furthermore, warmer temperatures increase species metabolic
-rates (Brown, Gillooly, Allen, Savage, \& West, 2004). Changes in
-metabolic rates can subsequently translate into shifts in species traits
-(body size, Vucic-Pestic, Ehnes, Rall, \& Brose (2011); Klein, Hill,
-Hinke, Phillips, \& Watters (2018){]}, biomass (Perry et al., 2020) and
-distribution (Kortsch, Primicerio, Fossheim, Dolgov, \& Aschan, 2015).
-Alterations in the species body size and distributions have ripple
-effects on feeding interactions, for example, it can introduce new
-feeding interactions (Vergés et al., 2014; Pecuchet et al., 2020),
-modify existing ones, and shorten energy pathways (Bartley et al., 2019;
-O'Gorman et al., 2019), and reduce trophic efficiencies (Vucic-Pestic et
-al., 2011).
-
-In recent years, several new fish (Galván et al., 2022) and
-macroinvertebrates species (Vinuesa, 2005; López-Gappa, 2022) were
+marine currents (Wu et al. 2012; Poloczanska et al. 2013; Vergés et al.
+2019). Furthermore, warmer temperatures increase species metabolic rates
+(Brown et al. 2004). Changes in metabolic rates can subsequently
+translate into shifts in species traits (body size, Vucic-Pestic et al.
+(2011); Klein et al. (2018){]}, biomass (Perry et al. 2020) and
+distribution (Kortsch et al. 2015). Alterations in the species body size
+and distributions have ripple effects on feeding interactions, for
+example, it can introduce new feeding interactions (Vergés et al. 2014;
+Pecuchet et al. 2020), modify existing ones, and shorten energy pathways
+(Bartley et al. 2019; O'Gorman et al. 2019), and reduce trophic
+efficiencies (Vucic-Pestic et al. 2011).
+
+In recent years, several new fish (Galván et al. 2022) and
+macroinvertebrates species (Vinuesa 2005; López-Gappa 2022) were
 registered in Patagonia, mostly in San Jorge Gulf in relation to the
@@
 change is driven by the tropicalization of temperate waters caused by
-sea warming (Vergés et al., 2014; Vergés et al., 2019). Because of its
+sea warming (Vergés et al. 2014; Vergés et al. 2019). Because of its
 location in the ecotone between two biogeographic provinces, the
-Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) (Balech \&
-Ehrlich, 2008), the San Jorge Gulf is prone to changes in species
+Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) (Balech and
+Ehrlich 2008), the San Jorge Gulf is prone to changes in species
 composition. We hypothesize that sea warming will alter the food web
@@
 generalist diets, hence an increase in food web connectance may be
-expected (Bartley et al., 2019). In another temperate ecosystem, an
+expected (Bartley et al. 2019). In another temperate ecosystem, an
 increase in the number of fish species, led to an increase in functional
-diversity and predation rate (Sgarlatta, 2023); consequences that may
+diversity and predation rate (Sgarlatta 2023); consequences that may
 also be expected in San Jorge Gulf. Given the short path length of the
@@
 the process of homogenization and loss of functional diversity in the
-area driven by trawl fisheries (Rincón-Díaz et al., 2021).
+area driven by trawl fisheries (Rincón-Díaz et al. 2021).
 
@@
 the Scotia Sea has experienced one of the largest levels of sea warming
-of any polar region (Whitehouse et al., 2008; Atkinson et al., 2019).
+of any polar region (Whitehouse et al. 2008; Atkinson et al. 2019).
 López-López et al. (2022) suggested that the southward distributional
@@
 modularity. The lower modularity may increase the probability of
-perturbations spreading through the network (Stouffer \& Bascompte,
+perturbations spreading through the network (Stouffer and Bascompte
 2011), which may be offset by increased connectance enhancing robustness
-to species loss (Dunne et al., 2002a). In the northern Scotia Sea around
+to species loss (Dunne et al. 2002b). In the northern Scotia Sea around
 South Georgia Island, we suggest that the declining krill biomass driven
-by sea warming (Atkinson et al., 2019), ocean acidification and
-pollution synergy (Rowlands et al., 2021), will reduce the energy
-transfer to top predators like seabirds and marine mammals. However,
-this may be buffered since the dominant copepod species have maintained
-their distribution (Tarling et al., 2018), but most importantly, showed
-an abundance increase in recent decades likely due to reduced predation
-and competition for food (Ward, Tarling, \& Thorpe, 2018). All this is
-significant for the structure of the food web given the central role of
-krill and copepods, characterized by high degree and mid-trophic
-position (Table S1). Overall, the food web's inherent resilience, marked
-by high connectance and omnivory, added to the potential compensation
-for the krill decrease due to a copepod increase, may buffer against
-structural changes (Table 3).
+by sea warming (Atkinson et al. 2019), ocean acidification and pollution
+synergy (Rowlands et al. 2021), will reduce the energy transfer to top
+predators like seabirds and marine mammals. However, this may be
+buffered since the dominant copepod species have maintained their
+distribution (Tarling et al. 2018), but most importantly, showed an
+abundance increase in recent decades likely due to reduced predation and
+competition for food (Ward et al. 2018). All this is significant for the
+structure of the food web given the central role of krill and copepods,
+characterized by high degree and mid-trophic position (Table S1).
+Overall, the food web's inherent resilience, marked by high connectance
+and omnivory, added to the potential compensation for the krill decrease
+due to a copepod increase, may buffer against structural changes (Table
+3).
 
@@
 experienced frequent events of marine heatwaves, i.e.~prolonged periods
-of anomalously high sea surface temperatures (Oliver et al., 2018;
-Latorre et al., 2023). This has led to decreases in biomasses of
-different planktonic functional groups (Garcia et al., 2019; Latorre et
-al., 2023). Given the relatively low abundance of phytoplankton,
+of anomalously high sea surface temperatures (Oliver et al. 2018;
+Latorre et al. 2023). This has led to decreases in biomasses of
+different planktonic functional groups (Garcia et al. 2019; Latorre et
+al. 2023). Given the relatively low abundance of phytoplankton,
 zooplankton's low degree, and the modular configuration of the food web,
@@
 associated to glacier retreat. The overall local effect of climate
-change on macroalgae is a net increase in their production (Dolores
-Deregibus et al., 2023). It has been proposed that larger diversity in
-primary producers can support a more diverse food web with more
-specialized consumers (Iken et al., 2023). We expect to see differential
-effects of climate change on hard and soft bottom associated food webs
-(Cordone et al., 2020). Given the high relative abundance and the high
-degree of the macroalgae functional group (Table S1), we expect a longer
-hard bottom food web, wider consumer trophic niches, and that it will
-become more stable as sea ice cover decreases and the glacier retreats
-due to global warming. In soft bottom areas of the Cove, multiple food
-web nodes are being affected by ongoing warming effects: decrease in net
-primary production of benthic microalgae (Hoffmann et al., 2019), and
-changes in the benthic community biomass, distribution and composition
-(Pasotti et al., 2015; Sahade et al., 2015). Given that the Potter Cove
-food web's present low connectance and omnivory, we suggest fragility
-and potential trophic cascade effects (Marina et al., 2018) with
-pronounced changes in energy fluxes (Table 3).
+change on macroalgae is a net increase in their production (Deregibus et
+al. 2023). It has been proposed that larger diversity in primary
+producers can support a more diverse food web with more specialized
+consumers (Iken et al. 2023). We expect to see differential effects of
+climate change on hard and soft bottom associated food webs (Cordone et
+al. 2020). Given the high relative abundance and the high degree of the
+macroalgae functional group (Table S1), we expect a longer hard bottom
+food web, wider consumer trophic niches, and that it will become more
+stable as sea ice cover decreases and the glacier retreats due to global
+warming. In soft bottom areas of the Cove, multiple food web nodes are
+being affected by ongoing warming effects: decrease in net primary
+production of benthic microalgae (Hoffmann et al. 2019), and changes in
+the benthic community biomass, distribution and composition (Sahade et
+al. 2015; Pasotti et al. 2015). Given that the Potter Cove food web's
+present low connectance and omnivory, we suggest fragility and potential
+trophic cascade effects (Marina et al. 2018) with pronounced changes in
+energy fluxes (Table 3).
 
@@
 extent, with reported anomalies in the past summer seasons (Fretwell et
-al., 2023). Declining sea ice extent has reduced the abundance of krill
-(Atkinson et al., 2004; Flores et al., 2012), and produced an increase
-in phytoplankton productivity (Pinkerton et al., 2021; Isla, 2023),
-altering the plankton community structure, and benefiting cryptophytes
-over diatoms (Lin et al., 2021). Moreover, habitat loss from sea ice
-decline will reduce the foraging success and breeding sites of seabirds
-(e.g., snow petrel Pagodroma nivea and emperor penguin Aptenodytes
-forsteri), decreasing their biomassess and modifying their
-distributions. The projected rise in iceberg scouring is expected to
-significantly alter the biomass and community structure of macrobenthos,
-which in turn will impact mid-trophic level predators such as demersal
-fish (Gutt, 2001; Mintenbeck et al., 2012). While we do not anticipate
-large-scale topological changes in the food web, local extinctions could
-lead to such changes, particularly affecting benthic species (Gutt \&
-Piepenburg, 2003). Given that the impacted species---whether
-individually like krill, or collectively like macrobenthos---present a
-mid-trophic position, high biomass and high degree (Table S1), we
-hypothesize that significant shifts in energy fluxes will occur (Table
-3). Additionally, the food web's low proportion of omnivores suggests
-reduced system resilience (Table 1), increasing the likelihood of regime
-changes (Gutt et al., 2015).
+al. 2023). Declining sea ice extent has reduced the abundance of krill
+(Atkinson et al. 2004; Flores et al. 2012), and produced an increase in
+phytoplankton productivity (Pinkerton et al. 2021; Isla 2023), altering
+the plankton community structure, and benefiting cryptophytes over
+diatoms (Lin et al. 2021). Moreover, habitat loss from sea ice decline
+will reduce the foraging success and breeding sites of seabirds (e.g.,
+snow petrel Pagodroma nivea and emperor penguin Aptenodytes forsteri),
+decreasing their biomassess and modifying their distributions. The
+projected rise in iceberg scouring is expected to significantly alter
+the biomass and community structure of macrobenthos, which in turn will
+impact mid-trophic level predators such as demersal fish (Gutt 2001;
+Mintenbeck et al. 2012). While we do not anticipate large-scale
+topological changes in the food web, local extinctions could lead to
+such changes, particularly affecting benthic species (Gutt and
+Piepenburg 2003). Given that the impacted species---whether individually
+like krill, or collectively like macrobenthos---present a mid-trophic
+position, high biomass and high degree (Table S1), we hypothesize that
+significant shifts in energy fluxes will occur (Table 3). Additionally,
+the food web's low proportion of omnivores suggests reduced system
+resilience (Table 1), increasing the likelihood of regime changes (Gutt
+et al. 2015).
 
@@
 warming. Although these areas are being impacted by sea warming,
-potentially affecting vertebrate and invertebrate species (Franco et
-al., 2020), to date no studies exist for Beagle Channel and Burdwood
-Bank ecosystems. In the Beagle Channel, the introduction of chinook
-salmon, a non-native species, poses a significant risk to the existing
-food web (Fernández et al., 2010). We hypothesize that chinook salmon's
-predation on Fuegian sprat and black southern cod will disrupt the
-established patterns of interaction within the food web. Both of these
-prey species are crucial for food web dynamics due to their mid-trophic
-positions and relatively high abundance (Table S1). Moreover, we expect
-that changes in the black southern cod population will have a more
-significant impact on the food web than changes in the Fuegian sprat
-population, as the black southern cod has a higher degree (Table S1).
-Overall, these disruptions could have far-reaching effects on the
-ecosystem. This is particularly concerning given the short path length
-of the food web, which means that changes can quickly propagate through
-the system, affecting many species and potentially destabilizing the
-entire network. This phenomenon is further heightened by the ecosystem's
-inherent vulnerability to changes at mid-trophic levels, often referred
-to as wasp-waist control (Table 3). In the Burdwood Bank region, fishing
+potentially affecting vertebrate and invertebrate species (Franco et al.
+2020), to date no studies exist for Beagle Channel and Burdwood Bank
+ecosystems. In the Beagle Channel, the introduction of chinook salmon, a
+non-native species, poses a significant risk to the existing food web
+(Fernández et al. 2010). We hypothesize that chinook salmon's predation
+on Fuegian sprat and black southern cod will disrupt the established
+patterns of interaction within the food web. Both of these prey species
+are crucial for food web dynamics due to their mid-trophic positions and
+relatively high abundance (Table S1). Moreover, we expect that changes
+in the black southern cod population will have a more significant impact
+on the food web than changes in the Fuegian sprat population, as the
+black southern cod has a higher degree (Table S1). Overall, these
+disruptions could have far-reaching effects on the ecosystem. This is
+particularly concerning given the short path length of the food web,
+which means that changes can quickly propagate through the system,
+affecting many species and potentially destabilizing the entire network.
+This phenomenon is further heightened by the ecosystem's inherent
+vulnerability to changes at mid-trophic levels, often referred to as
+wasp-waist control (Table 3). In the Burdwood Bank region, fishing
 activities may be the main stressor causing shifts in the food web
@@
 mid-level fish species, five top-level seabird species, and over 30
-types of benthic macroinvertebrates due to bycatch (Gaitán \& Marí,
-2016; Martínez et al., 2022; Tamini et al., 2023). Additionally,
+types of benthic macroinvertebrates due to bycatch (Gaitán and Marí
+2016; Martínez et al. 2022; Tamini et al. 2023). Additionally,
 alterations in the diets of six seabird species, caused by discarded
-catch (Tamini et al., 2023), are expected to disrupt the energy flow and
+catch (Tamini et al. 2023), are expected to disrupt the energy flow and
 further reduce the stability of the food web (Table 3).
@@
 shifts and introductions). Moreover, the population trends (biomasses
-and abundances) of important species are also changing (Hindell et al.,
-2020; Funes, 2020; Woods et al., 2023) driving shifts in their roles as
-either predators or prey (e.g. Belleggia, Giberto, \& Bremec (2017),
-Pasti et al. (2021)). These diet and biomass shifts should be
-investigated in order to generate reliable predictions of food web
-responses to multiple stressors in the southwest Atlantic - Antarctic
-region. One could argue that both shifts might increase the complexity
-of food webs in the short term by adding generalist predators or new
-prey (e.g., Cordone, Galván, \& Momo (2023)) or by enabling discard
-consumption (e.g. Funes et al. (2022)). However, in the long term, both
-stressors may lead to the biological extinction of certain prey and
-competitors (e.g. Anton et al. (2019)) or a significant reduction in
-target and incidental catch species (e.g. Dulvy et al. (2014)), thereby
-promoting food web simplification.
+and abundances) of important species are also changing (Funes 2020;
+Hindell et al. 2020; Woods et al. 2023) driving shifts in their roles as
+either predators or prey (e.g. Belleggia et al. (2017), Pasti et al.
+(2021)). These diet and biomass shifts should be investigated in order
+to generate reliable predictions of food web responses to multiple
+stressors in the southwest Atlantic - Antarctic region. One could argue
+that both shifts might increase the complexity of food webs in the short
+term by adding generalist predators or new prey (e.g., Cordone et al.
+(2023)) or by enabling discard consumption (e.g. Funes et al. (2022)).
+However, in the long term, both stressors may lead to the biological
+extinction of certain prey and competitors (e.g. Anton et al. (2019)) or
+a significant reduction in target and incidental catch species (e.g.
+Dulvy et al. (2014)), thereby promoting food web simplification.
 
@@
 food web models where the strength of interactions reflect energy fluxes
-among species (Nilsson \& McCann, 2016; Kortsch et al., 2021). Emerging
+among species (Nilsson and McCann 2016; Kortsch et al. 2021). Emerging
 methods such as bioenergetic food web modeling have been proposed in
 this regard and present promising ways to estimate shifts in species
-interactions within food webs as a response to stressors (Gauzens,
-Brose, Delmas, \& Berti, n.d.; Gellner, McCann, \& Hastings, 2023).
-Shifts that can lead to changes in overall ecosystem functioning and
-stability.
+interactions within food webs as a response to stressors (Gellner et al.
+2023; Gauzens et al. n.d.). Shifts that can lead to changes in overall
+ecosystem functioning and stability.
 
@@
 communities in these ecosystems, though warming of mid-water and bottom
-layers have been shown at a regional scale (Franco et al., 2020). Yet in
+layers have been shown at a regional scale (Franco et al. 2020). Yet in
 Beagle Channel recent experimental studies have tested the tolerance of
 fishes to scenarios of sea warming and/or acidification suggesting
-potential metabolic impacts on species (María Eugenia Lattuca, Boy,
-Vanella, Barrantes, \& Fernández, 2018; María E. Lattuca et al., 2023).
+potential metabolic impacts on species (Lattuca et al. 2018; Lattuca et
+al. 2023).
 
 Analyzing the impact of multiple stressors through observational studies
-is challenging (Gutt et al., 2021). This complexity arises partly
-because of potential for antagonistic effects, where impacts cancel each
-other out, or synergistic effects, where the combined impact is greater
-than the sum of individual effects (Boyd, Lennartz, Glover, \& Doney,
-2015; Côté et al., 2016). Moreover, these interactive effects are
-complicated to handle in the framework of complex food webs. The number
-of pathways through which a species may affect or be affected by other
-species, and through which stressors may permeate communities, increases
-exponentially with the number of species and interactions in a network
-(Menge, 1995). To tackle this complexity, Beauchesne, Cazelles,
-Archambault, Dee, \& Gravel (2021) developed a theory-grounded approach
-using motifs (i.e.~groups of species that, when put together, construct
-whole food webs) to simplify food webs; a methodology that could be
-applied to our food web study cases.
+is challenging (Gutt et al. 2021). This complexity arises partly because
+of potential for antagonistic effects, where impacts cancel each other
+out, or synergistic effects, where the combined impact is greater than
+the sum of individual effects (Boyd et al. 2015; Côté et al. 2016).
+Moreover, these interactive effects are complicated to handle in the
+framework of complex food webs. The number of pathways through which a
+species may affect or be affected by other species, and through which
+stressors may permeate communities, increases exponentially with the
+number of species and interactions in a network (Menge 1995). To tackle
+this complexity, Beauchesne et al. (2021) developed a theory-grounded
+approach using motifs (i.e.~groups of species that, when put together,
+construct whole food webs) to simplify food webs; a methodology that
+could be applied to our food web study cases.
 
@@
 \bibitem[\citeproctext]{ref-Acha2004}
-Acha, E. M., Mianzan, H. W., Guerrero, R. A., Favero, M., \& Bava, J.
-(2004). Marine fronts at the continental shelves of austral {South
-America}: {Physical} and ecological processes. \emph{Journal of Marine
-Systems}, \emph{44}(1), 83--105.
-doi:\href{https://doi.org/10.1016/j.jmarsys.2003.09.005}{10.1016/j.jmarsys.2003.09.005}
+Acha, E.M., Mianzan, H.W., Guerrero, R.A., Favero, M., and Bava, J.
+2004. Marine fronts at the continental shelves of austral {South
+America}: {Physical} and ecological processes. Journal of Marine Systems
+\textbf{44}(1): 83--105.
+doi:\href{https://doi.org/10.1016/j.jmarsys.2003.09.005}{10.1016/j.jmarsys.2003.09.005}.
 
 \bibitem[\citeproctext]{ref-APN2022}
-Administración de Parques Nacionales. (2022). {Plan de gestión AMP
+Administración de Parques Nacionales. 2022. {Plan de gestión AMP
 Namuncurá Banco Burdwood}. {Dirección Nacional de Áreas Marinas
@@
 \bibitem[\citeproctext]{ref-Albert2002}
-Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex
-networks. \emph{Reviews of Modern Physics}, \emph{74}(1), 47--97.
-doi:\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}
+Albert, R., and Barabási, A.-L. 2002. Statistical mechanics of complex
+networks. Reviews of Modern Physics \textbf{74}(1): 47--97. {American
+Physical Society}.
+doi:\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}.
+
+\bibitem[\citeproctext]{ref-Allega2020}
+Allega, L., Braverman, M., Campodónico, S., Carozza, C.R., Cepeda, G.D.,
+Colonello, J.H., Derisio, C., Di Mauro, R., Firpo, C.A., Gaitán, E.,
+Hozbor, C., Irusta, G., Ivanovic, M., Lagos, N., Lutz, V.A., Marí, N.R.,
+Militelli, M.I., Moriondo Danovaro, P., Navarro, G., Orlando, P.,
+Pájaro, M., Prandoni, N., Prosdocimi, L., Reta, R., Rico, M.R., Riestra,
+C., Ruarte, C., Schejter, L., Schiariti, A., Segura, V., Souto, V.S.,
+Temperoni, B., and Verón, E. 2020. {Estado del conocimiento biológico
+pesquero de los principales recursos vivos y su ambiente, con relación a
+la exploración hidrocarburífera en la Zona Económica Exclusiva argentina
+y sus adyacencias}. {Instituto Nacional de Investigación y Desarrollo
+Pesquero (INIDEP)}, {Mar del Plata}. {[}accessed 26 September 2023{]}.
 
 \bibitem[\citeproctext]{ref-Allega2019}
-Allega, Lucrecia, Braverman, M. S., Cabreira, A. G., Campodónico, S.,
-Colonello, J. H., Derisio, C. M., \ldots{} Verón, E. M. (2019).
-\emph{{Estado del conocimiento biológico pesquero de los principales
-recursos vivos y su ambiente, con relación a la exploración
-hidrocarburífera en la Zona Económica Exclusiva Argentina y
-adyacencias}}. {INIDEP}.
-
-\bibitem[\citeproctext]{ref-Allega2020}
-Allega, L., Braverman, M., Campodónico, S., Carozza, C. R., Cepeda, G.
-D., Colonello, J. H., \ldots{} Verón, E. (2020). \emph{{Estado del
-conocimiento biológico pesquero de los principales recursos vivos y su
-ambiente, con relación a la exploración hidrocarburífera en la Zona
-Económica Exclusiva argentina y sus adyacencias}}. {Mar del Plata}:
-{Instituto Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.
+Allega, L., Braverman, M.S., Cabreira, A.G., Campodónico, S., Colonello,
+J.H., Derisio, C.M., Di Mauro, R.P., Gaitán, E.N., Hozbor, M., Irusta,
+G., Lutz, V.A., Marí, N., Militelli, M.I., Moriondo, P., Navarro, G.,
+Orlando, P., Pajaro, M., Prandoni García, N.I., Prosdocimi, L., Reta,
+R., Rico, R., Riestra, C.M., Segura, V., Schejter, L., Schiariti, A.,
+Souto, V., and Verón, E.M. 2019. {Estado del conocimiento biológico
+pesquero de los principales recursos vivos y su ambiente, con relación a
+la exploración hidrocarburífera en la Zona Económica Exclusiva Argentina
+y adyacencias}. {INIDEP}. {[}accessed 10 August 2023{]}.
 
 \bibitem[\citeproctext]{ref-Anton2019}
-Anton, A., Geraldi, N. R., Lovelock, C. E., Apostolaki, E. T., Bennett,
-S., Cebrian, J., \ldots{} Duarte, C. M. (2019). Global ecological
-impacts of marine exotic species. \emph{Nature Ecology \& Evolution},
-\emph{3}(5), 787--800.
-doi:\href{https://doi.org/10.1038/s41559-019-0851-0}{10.1038/s41559-019-0851-0}
+Anton, A., Geraldi, N.R., Lovelock, C.E., Apostolaki, E.T., Bennett, S.,
+Cebrian, J., Krause-Jensen, D., Marbà, N., Martinetto, P., Pandolfi,
+J.M., Santana-Garcon, J., and Duarte, C.M. 2019. Global ecological
+impacts of marine exotic species. Nature Ecology \& Evolution
+\textbf{3}(5): 787--800. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41559-019-0851-0}{10.1038/s41559-019-0851-0}.
 
 \bibitem[\citeproctext]{ref-Antoni2020}
-Antoni, J. S., Almandoz, G. O., Ferrario, M. E., Hernando, M. P.,
-Varela, D. E., Rozema, P. D., \ldots{} Schloss, I. R. (2020). Response
-of a natural {Antarctic} phytoplankton assemblage to changes in
-temperature and salinity. \emph{Journal of Experimental Marine Biology
-and Ecology}, \emph{532}, 151444.
-doi:\href{https://doi.org/10.1016/j.jembe.2020.151444}{10.1016/j.jembe.2020.151444}
+Antoni, J.S., Almandoz, G.O., Ferrario, M.E., Hernando, M.P., Varela,
+D.E., Rozema, P.D., Buma, A.G.J., Paparazzo, F.E., and Schloss, I.R.
+2020. Response of a natural {Antarctic} phytoplankton assemblage to
+changes in temperature and salinity. Journal of Experimental Marine
+Biology and Ecology \textbf{532}: 151444.
+doi:\href{https://doi.org/10.1016/j.jembe.2020.151444}{10.1016/j.jembe.2020.151444}.
 
 \bibitem[\citeproctext]{ref-Atkinson2019}
-Atkinson, A., Hill, S. L., Pakhomov, E. A., Siegel, V., Reiss, C. S.,
-Loeb, V. J., \ldots{} Sailley, S. F. (2019). Krill ({Euphausia} superba)
-distribution contracts southward during rapid regional warming.
-\emph{Nature Climate Change}, \emph{9}(2), 142--147.
-doi:\href{https://doi.org/10.1038/s41558-018-0370-z}{10.1038/s41558-018-0370-z}
+Atkinson, A., Hill, S.L., Pakhomov, E.A., Siegel, V., Reiss, C.S., Loeb,
+V.J., Steinberg, D.K., Schmidt, K., Tarling, G.A., Gerrish, L., and
+Sailley, S.F. 2019. Krill ({Euphausia} superba) distribution contracts
+southward during rapid regional warming. Nature Climate Change
+\textbf{9}(2): 142--147. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41558-018-0370-z}{10.1038/s41558-018-0370-z}.
 
 \bibitem[\citeproctext]{ref-Atkinson2004}
-Atkinson, A., Siegel, V., Pakhomov, E., \& Rothery, P. (2004). Long-term
+Atkinson, A., Siegel, V., Pakhomov, E., and Rothery, P. 2004. Long-term
 decline in krill stock and increase in salps within the {Southern
-Ocean}. \emph{Nature}, \emph{432}(7013), 100--103.
-doi:\href{https://doi.org/10.1038/nature02996}{10.1038/nature02996}
+Ocean}. Nature \textbf{432}(7013): 100--103. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/nature02996}{10.1038/nature02996}.
 
 \bibitem[\citeproctext]{ref-Balech2008}
-Balech, E., \& Ehrlich, M. D. (2008). {Esquema biogeográfico del Mar
-Argentino}.
+Balech, E., and Ehrlich, M.D. 2008. {Esquema biogeográfico del Mar
+Argentino}. {Mar del Plata: Instituto Nacional de Investigación y
+Desarrollo Pesquero (INIDEP)}. {[}accessed 14 August 2023{]}.
 
 \bibitem[\citeproctext]{ref-Bartley2019}
-Bartley, T. J., McCann, K. S., Bieg, C., Cazelles, K., Granados, M.,
-Guzzo, M. M., \ldots{} McMeans, B. C. (2019). Food web rewiring in a
-changing world. \emph{Nature Ecology \& Evolution}, \emph{3}(3),
-345--354.
-doi:\href{https://doi.org/10.1038/s41559-018-0772-3}{10.1038/s41559-018-0772-3}
+Bartley, T.J., McCann, K.S., Bieg, C., Cazelles, K., Granados, M.,
+Guzzo, M.M., MacDougall, A.S., Tunney, T.D., and McMeans, B.C. 2019.
+Food web rewiring in a changing world. Nature Ecology \& Evolution
+\textbf{3}(3): 345--354. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41559-018-0772-3}{10.1038/s41559-018-0772-3}.
 
 \bibitem[\citeproctext]{ref-Bauer2022}
-Bauer, B., Berti, E., Ryser, R., Gauzens, B., Hirt, M. R., Rosenbaum,
-B., \ldots{} Brose, U. (2022). Biotic filtering by species' interactions
-constrains food-web variability across spatial and abiotic gradients.
-\emph{Ecology Letters}, \emph{25}(5), 1225--1236.
-doi:\href{https://doi.org/10.1111/ele.13995}{10.1111/ele.13995}
+Bauer, B., Berti, E., Ryser, R., Gauzens, B., Hirt, M.R., Rosenbaum, B.,
+Digel, C., Ott, D., Scheu, S., and Brose, U. 2022. Biotic filtering by
+species' interactions constrains food-web variability across spatial and
+abiotic gradients. Ecology Letters \textbf{25}(5): 1225--1236.
+doi:\href{https://doi.org/10.1111/ele.13995}{10.1111/ele.13995}.
 
 \bibitem[\citeproctext]{ref-Beauchesne2021}
-Beauchesne, D., Cazelles, K., Archambault, P., Dee, L. E., \& Gravel, D.
-(2021). On the sensitivity of food webs to multiple stressors.
-\emph{Ecology Letters}, \emph{24}(10), 2219--2237.
-doi:\href{https://doi.org/10.1111/ele.13841}{10.1111/ele.13841}
+Beauchesne, D., Cazelles, K., Archambault, P., Dee, L.E., and Gravel, D.
+2021. On the sensitivity of food webs to multiple stressors. Ecology
+Letters \textbf{24}(10): 2219--2237.
+doi:\href{https://doi.org/10.1111/ele.13841}{10.1111/ele.13841}.
 
 \bibitem[\citeproctext]{ref-Belgrano2005}
-Belgrano, A., Scharler, S. E. R. C. U. M., Scharler, U. M., Dunne, J.,
-\& Ulanowicz, R. E. (2005). \emph{Aquatic {Food Webs}: {An Ecosystem
-Approach}}. {OUP Oxford}.
+Belgrano, A., Scharler, S.E.R.C.U.M., Scharler, U.M., Dunne, J., and
+Ulanowicz, R.E. 2005. Aquatic {Food Webs}: {An Ecosystem Approach}. {OUP
+Oxford}.
 
 \bibitem[\citeproctext]{ref-Belleggia2017}
-Belleggia, M., Giberto, D., \& Bremec, C. (2017). Adaptation of diet in
-a changed environment: {Increased} consumption of lobster krill {Munida}
-gregaria ({Fabricius}, 1793) by {Argentine} hake. \emph{Marine Ecology},
-\emph{38}(4), e12445.
-doi:\href{https://doi.org/10.1111/maec.12445}{10.1111/maec.12445}
+Belleggia, M., Giberto, D., and Bremec, C. 2017. Adaptation of diet in a
+changed environment: {Increased} consumption of lobster krill {Munida}
+gregaria ({Fabricius}, 1793) by {Argentine} hake. Marine Ecology
+\textbf{38}(4): e12445.
+doi:\href{https://doi.org/10.1111/maec.12445}{10.1111/maec.12445}.
 
 \bibitem[\citeproctext]{ref-Bovcon2013}
-Bovcon, N. D., Góngora, M. E., Marinao, C., \& González-Zevallos, D.
-(2013). Composición de las capturas y descartes generados en la pesca de
+Bovcon, N.D., Góngora, M.E., Marinao, C., and González-Zevallos, D.
+2013. Composición de las capturas y descartes generados en la pesca de
 merluza común {Merluccius} hubbsi y langostino patagónico {Pleoticus}
 muelleri: Un caso de estudio en la flota fresquera de altura del {Golfo
-San Jorge}, {Chubut}, {Argentina}. \emph{Revista de Biología Marina y
-Oceanografía}, \emph{48}(2), 303--319.
-doi:\href{https://doi.org/10.4067/S0718-19572013000200010}{10.4067/S0718-19572013000200010}
+San Jorge}, {Chubut}, {Argentina}. Revista de biología marina y
+oceanografía \textbf{48}(2): 303--319. {Universidad de Valparaíso.
+Facultad de Ciencias del Mar}.
+doi:\href{https://doi.org/10.4067/S0718-19572013000200010}{10.4067/S0718-19572013000200010}.
 
 \bibitem[\citeproctext]{ref-Boyd2015}
-Boyd, P. W., Lennartz, S. T., Glover, D. M., \& Doney, S. C. (2015).
+Boyd, P.W., Lennartz, S.T., Glover, D.M., and Doney, S.C. 2015.
 Biological ramifications of climate-change-mediated oceanic
-multi-stressors. \emph{Nature Climate Change}, \emph{5}(1), 71--79.
-doi:\href{https://doi.org/10.1038/nclimate2441}{10.1038/nclimate2441}
+multi-stressors. Nature Climate Change \textbf{5}(1): 71--79. {Nature
+Publishing Group}.
+doi:\href{https://doi.org/10.1038/nclimate2441}{10.1038/nclimate2441}.
 
@@
 Braeckman, U., Pasotti, F., Hoffmann, R., Vázquez, S., Wulff, A.,
-Schloss, I. R., \ldots{} Vanreusel, A. (2021). Glacial melt disturbance
-shifts community metabolism of an {Antarctic} seafloor ecosystem from
-net autotrophy to heterotrophy. \emph{Communications Biology},
-\emph{4}(1), 148.
-doi:\href{https://doi.org/10.1038/s42003-021-01673-6}{10.1038/s42003-021-01673-6}
+Schloss, I.R., Falk, U., Deregibus, D., Lefaible, N., Torstensson, A.,
+Al-Handal, A., Wenzhöfer, F., and Vanreusel, A. 2021. Glacial melt
+disturbance shifts community metabolism of an {Antarctic} seafloor
+ecosystem from net autotrophy to heterotrophy. Communications Biology
+\textbf{4}(1): 148.
+doi:\href{https://doi.org/10.1038/s42003-021-01673-6}{10.1038/s42003-021-01673-6}.
 
 \bibitem[\citeproctext]{ref-Braithwaite2015}
-Braithwaite, J. E., Meeuwig, J. J., Letessier, T. B., Jenner, K. C. S.,
-\& Brierley, A. S. (2015). From sea ice to blubber: Linking whale
-condition to krill abundance using historical whaling records.
-\emph{Polar Biology}, \emph{38}(8), 1195--1202.
-doi:\href{https://doi.org/10.1007/s00300-015-1685-0}{10.1007/s00300-015-1685-0}
+Braithwaite, J.E., Meeuwig, J.J., Letessier, T.B., Jenner, K.C.S., and
+Brierley, A.S. 2015. From sea ice to blubber: Linking whale condition to
+krill abundance using historical whaling records. Polar Biology
+\textbf{38}(8): 1195--1202.
+doi:\href{https://doi.org/10.1007/s00300-015-1685-0}{10.1007/s00300-015-1685-0}.
 
 \bibitem[\citeproctext]{ref-Brown2004}
-Brown, J. H., Gillooly, J. F., Allen, A. P., Savage, V. M., \& West, G.
-B. (2004). Toward a {Metabolic Theory} of {Ecology}. \emph{Ecology},
-\emph{85}(7), 1771--1789.
-doi:\href{https://doi.org/10.1890/03-9000}{10.1890/03-9000}
+Brown, J.H., Gillooly, J.F., Allen, A.P., Savage, V.M., and West, G.B.
+2004. Toward a {Metabolic Theory} of {Ecology}. Ecology \textbf{85}(7):
+1771--1789. doi:\href{https://doi.org/10.1890/03-9000}{10.1890/03-9000}.
 
 \bibitem[\citeproctext]{ref-Bruder2019}
-Bruder, A., Frainer, A., Rota, T., \& Primicerio, R. (2019). The
+Bruder, A., Frainer, A., Rota, T., and Primicerio, R. 2019. The
 {Importance} of {Ecological Networks} in {Multiple-Stressor Research}
-and {Management}. \emph{Frontiers in Environmental Science}, \emph{7}.
+and {Management}. Frontiers in Environmental Science \textbf{7}.
+{[}accessed 29 August 2023{]}.
 
 \bibitem[\citeproctext]{ref-Bruno2023}
-Bruno, D. O., Riccialdelli, L., Acha, E. M., \& Fernández, D. A. (2023).
+Bruno, D.O., Riccialdelli, L., Acha, E.M., and Fernández, D.A. 2023.
 Seasonal variation of autochthonous and allochthonous carbon sources for
-the first levels of the {Beagle Channel} food web. \emph{Journal of
-Marine Systems}, \emph{239}, 103859.
-doi:\href{https://doi.org/10.1016/j.jmarsys.2023.103859}{10.1016/j.jmarsys.2023.103859}
+the first levels of the {Beagle Channel} food web. Journal of Marine
+Systems \textbf{239}: 103859.
+doi:\href{https://doi.org/10.1016/j.jmarsys.2023.103859}{10.1016/j.jmarsys.2023.103859}.
 
 \bibitem[\citeproctext]{ref-Chown2022}
-Chown, S. L., Leihy, R. I., Naish, T. R., Brooks, C. M., Convey, P.,
-Henley, B. J., \ldots{} Grant, S. M. (2022). Antarctic climate change
-and the environment: A decadal synopsis and recommendations for action.
+Chown, S.L., Leihy, R.I., Naish, T.R., Brooks, C.M., Convey, P., Henley,
+B.J., Mackintosh, A.N., Phillips, L.M., Kennicutt II, M.C., and Grant,
+S.M. 2022. Antarctic climate change and the environment: A decadal
+synopsis and recommendations for action.
 
 \bibitem[\citeproctext]{ref-Ciancio2008}
-Ciancio, J. E., Pascual, M. A., Botto, F., Frere, E., \& Iribarne, O.
-(2008). Trophic relationships of exotic anadromous salmonids in the
-southern {Patagonian Shelf} as inferred from stable isotopes.
-\emph{Limnology and Oceanography}, \emph{53}(2), 788--798.
-doi:\href{https://doi.org/10.4319/lo.2008.53.2.0788}{10.4319/lo.2008.53.2.0788}
+Ciancio, J.E., Pascual, M.A., Botto, F., Frere, E., and Iribarne, O.
+2008. Trophic relationships of exotic anadromous salmonids in the
+southern {Patagonian Shelf} as inferred from stable isotopes. Limnology
+and Oceanography \textbf{53}(2): 788--798.
+doi:\href{https://doi.org/10.4319/lo.2008.53.2.0788}{10.4319/lo.2008.53.2.0788}.
 
 \bibitem[\citeproctext]{ref-Cirtwill2015}
-Cirtwill, A. R., Stouffer, D. B., \& Romanuk, T. N. (2015). Latitudinal
+Cirtwill, A.R., Stouffer, D.B., and Romanuk, T.N. 2015. Latitudinal
 gradients in biotic niche breadth vary across ecosystem types.
-\emph{Proceedings of the Royal Society B: Biological Sciences},
-\emph{282}(1819), 20151589.
-doi:\href{https://doi.org/10.1098/rspb.2015.1589}{10.1098/rspb.2015.1589}
+Proceedings of the Royal Society B: Biological Sciences
+\textbf{282}(1819): 20151589. {Royal Society}.
+doi:\href{https://doi.org/10.1098/rspb.2015.1589}{10.1098/rspb.2015.1589}.
 
 \bibitem[\citeproctext]{ref-Collins2010}
-Collins, M. A., Brickle, P., Brown, J., \& Belchier, M. (2010). Chapter
+Collins, M.A., Brickle, P., Brown, J., and Belchier, M. 2010. Chapter
 {Four} - {The Patagonian Toothfish}: {Biology}, {Ecology} and {Fishery}.
-In M. Lesser (Ed.), \emph{Advances in {Marine Biology}} (Vol. 58, pp.
-227--300). {Academic Press}.
-doi:\href{https://doi.org/10.1016/B978-0-12-381015-1.00004-6}{10.1016/B978-0-12-381015-1.00004-6}
+\emph{In} Advances in {Marine Biology}. \emph{Edited by} M. Lesser.
+{Academic Press}. pp. 227--300.
+doi:\href{https://doi.org/10.1016/B978-0-12-381015-1.00004-6}{10.1016/B978-0-12-381015-1.00004-6}.
 
 \bibitem[\citeproctext]{ref-Commendatore2012}
-Commendatore, M. G., Nievas, M. L., Amin, O., \& Esteves, J. L. (2012).
+Commendatore, M.G., Nievas, M.L., Amin, O., and Esteves, J.L. 2012.
 Sources and distribution of aliphatic and polyaromatic hydrocarbons in
 coastal sediments from the {Ushuaia Bay} ({Tierra} del {Fuego},
-{Patagonia}, {Argentina}). \emph{Marine Environmental Research},
-\emph{74}, 20--31.
-doi:\href{https://doi.org/10.1016/j.marenvres.2011.11.010}{10.1016/j.marenvres.2011.11.010}
+{Patagonia}, {Argentina}). Marine Environmental Research \textbf{74}:
+20--31.
+doi:\href{https://doi.org/10.1016/j.marenvres.2011.11.010}{10.1016/j.marenvres.2011.11.010}.
 
 \bibitem[\citeproctext]{ref-Constable2014}
-Constable, A. J., Melbourne-Thomas, J., Corney, S. P., Arrigo, K. R.,
-Barbraud, C., Barnes, D. K. A., \ldots{} Ziegler, P. (2014). Climate
-change and {Southern Ocean} ecosystems {I}: How changes in physical
-habitats directly affect marine biota. \emph{Global Change Biology},
-\emph{20}(10), 3004--3025.
-doi:\href{https://doi.org/10.1111/gcb.12623}{10.1111/gcb.12623}
+Constable, A.J., Melbourne-Thomas, J., Corney, S.P., Arrigo, K.R.,
+Barbraud, C., Barnes, D.K.A., Bindoff, N.L., Boyd, P.W., Brandt, A.,
+Costa, D.P., Davidson, A.T., Ducklow, H.W., Emmerson, L., Fukuchi, M.,
+Gutt, J., Hindell, M.A., Hofmann, E.E., Hosie, G.W., Iida, T., Jacob,
+S., Johnston, N.M., Kawaguchi, S., Kokubun, N., Koubbi, P., Lea, M.-A.,
+Makhado, A., Massom, R.A., Meiners, K., Meredith, M.P., Murphy, E.J.,
+Nicol, S., Reid, K., Richerson, K., Riddle, M.J., Rintoul, S.R., Smith,
+W.O., Southwell, C., Stark, J.S., Sumner, M., Swadling, K.M., Takahashi,
+K.T., Trathan, P.N., Welsford, D.C., Weimerskirch, H., Westwood, K.J.,
+Wienecke, B.C., Wolf-Gladrow, D., Wright, S.W., Xavier, J.C., and
+Ziegler, P. 2014. Climate change and {Southern Ocean} ecosystems {I}:
+How changes in physical habitats directly affect marine biota. Global
+Change Biology \textbf{20}(10): 3004--3025.
+doi:\href{https://doi.org/10.1111/gcb.12623}{10.1111/gcb.12623}.
 
 \bibitem[\citeproctext]{ref-Cordone2023}
-Cordone, G., Galván, D. E., \& Momo, F. R. (2023). Impacts of an
-invasion by green crab {Carcinus} maenas on the intertidal food web of a
-{Patagonian} rocky shore, {Argentina}. \emph{Marine Ecology Progress
-Series}, \emph{713}, 97--115.
-doi:\href{https://doi.org/10.3354/meps14336}{10.3354/meps14336}
+Cordone, G., Galván, D.E., and Momo, F.R. 2023. Impacts of an invasion
+by green crab {Carcinus} maenas on the intertidal food web of a
+{Patagonian} rocky shore, {Argentina}. Marine Ecology Progress Series
+\textbf{713}: 97--115.
+doi:\href{https://doi.org/10.3354/meps14336}{10.3354/meps14336}.
 
 \bibitem[\citeproctext]{ref-Cordone2020}
-Cordone, G., Salinas, V., Marina, T. I., Doyle, S. R., Pasotti, F.,
-Saravia, L. A., \& Momo, F. R. (2020). Green vs brown food web:
-{Effects} of habitat type on multidimensional stability proxies for a
-highly-resolved {Antarctic} food web. \emph{Food Webs}, \emph{25},
-e00166.
-doi:\href{https://doi.org/10.1016/j.fooweb.2020.e00166}{10.1016/j.fooweb.2020.e00166}
+Cordone, G., Salinas, V., Marina, T.I., Doyle, S.R., Pasotti, F.,
+Saravia, L.A., and Momo, F.R. 2020. Green vs brown food web: {Effects}
+of habitat type on multidimensional stability proxies for a
+highly-resolved {Antarctic} food web. Food Webs \textbf{25}: e00166.
+doi:\href{https://doi.org/10.1016/j.fooweb.2020.e00166}{10.1016/j.fooweb.2020.e00166}.
 
 \bibitem[\citeproctext]{ref-Correa2008}
-Correa, C., \& Gross, M. R. (2008). Chinook salmon invade southern
-{South America}. \emph{Biological Invasions}, \emph{10}(5), 615--639.
-doi:\href{https://doi.org/10.1007/s10530-007-9157-2}{10.1007/s10530-007-9157-2}
+Correa, C., and Gross, M.R. 2008. Chinook salmon invade southern {South
+America}. Biological Invasions \textbf{10}(5): 615--639.
+doi:\href{https://doi.org/10.1007/s10530-007-9157-2}{10.1007/s10530-007-9157-2}.
 
 \bibitem[\citeproctext]{ref-Cossi2021}
-Cossi, P. F., Ojeda, M., Chiesa, I. L., Rimondino, G. N., Fraysse, C.,
-Calcagno, J., \& Pérez, A. F. (2021). First evidence of microplastics in
+Cossi, P.F., Ojeda, M., Chiesa, I.L., Rimondino, G.N., Fraysse, C.,
+Calcagno, J., and Pérez, A.F. 2021. First evidence of microplastics in
 the {Marine Protected Area Namuncurá} at {Burdwood Bank}, {Argentina}: A
 study on {Henricia} obesa and {Odontaster} penicillatus
-({Echinodermata}: {Asteroidea}). \emph{Polar Biology}, \emph{44}(12),
+({Echinodermata}: {Asteroidea}). Polar Biology \textbf{44}(12):
 2277--2287.
-doi:\href{https://doi.org/10.1007/s00300-021-02959-5}{10.1007/s00300-021-02959-5}
+doi:\href{https://doi.org/10.1007/s00300-021-02959-5}{10.1007/s00300-021-02959-5}.
 
 \bibitem[\citeproctext]{ref-Cote2016}
-Côté, I. M., Darling, E. S., \& Brown, C. J. (2016). Interactions among
-ecosystem stressors and their importance in conservation.
-\emph{Proceedings of the Royal Society B: Biological Sciences},
-\emph{283}(1824), 20152592.
-doi:\href{https://doi.org/10.1098/rspb.2015.2592}{10.1098/rspb.2015.2592}
+Côté, I.M., Darling, E.S., and Brown, C.J. 2016. Interactions among
+ecosystem stressors and their importance in conservation. Proceedings of
+the Royal Society B: Biological Sciences \textbf{283}(1824): 20152592.
+{Royal Society}.
+doi:\href{https://doi.org/10.1098/rspb.2015.2592}{10.1098/rspb.2015.2592}.
 
 \bibitem[\citeproctext]{ref-deHaro2022}
-de Haro, J. C., Perez Orsi, H., Cané, S., Di Pangracio, A., Falabella,
-V., \& Sapoznikow, A. (2022). {Informe colaborativo sobre el Estado de
+de Haro, J.C., Perez Orsi, H., Cané, S., Di Pangracio, A., Falabella,
+V., and Sapoznikow, A. 2022. {Informe colaborativo sobre el Estado de
 situación. Riesgos e impactos de la prospección sísmica en el Mar
@@
 \bibitem[\citeproctext]{ref-Deregibus2023}
-Deregibus, Dolores, Campana, G. L., Neder, C., Barnes, D. K. A., Zacher,
-K., Piscicelli, J. M., \ldots{} Quartino, M. L. (2023). Potential
+Deregibus, D., Campana, G.L., Neder, C., Barnes, D.K.A., Zacher, K.,
+Piscicelli, J.M., Jerosch, K., and Quartino, M.L. 2023. Potential
 macroalgal expansion and blue carbon gains with northern {Antarctic
-Peninsula} glacial retreat. \emph{Marine Environmental Research},
-\emph{189}, 106056.
-doi:\href{https://doi.org/10.1016/j.marenvres.2023.106056}{10.1016/j.marenvres.2023.106056}
+Peninsula} glacial retreat. Marine Environmental Research \textbf{189}:
+106056.
+doi:\href{https://doi.org/10.1016/j.marenvres.2023.106056}{10.1016/j.marenvres.2023.106056}.
 
 \bibitem[\citeproctext]{ref-Deregibus2017}
-Deregibus, D., Quartino, M. L., Zacher, K., Campana, G. L., \& Barnes,
-D. K. A. (2017). Understanding the link between sea ice, ice scour and
+Deregibus, D., Quartino, M.L., Zacher, K., Campana, G.L., and Barnes,
+D.K.A. 2017. Understanding the link between sea ice, ice scour and
 {Antarctic} benthic biodiversity\textendash the need for cross-station
-and international collaboration. \emph{Polar Record}, \emph{53}(2),
-143--152.
-doi:\href{https://doi.org/10.1017/S0032247416000875}{10.1017/S0032247416000875}
+and international collaboration. Polar Record \textbf{53}(2): 143--152.
+doi:\href{https://doi.org/10.1017/S0032247416000875}{10.1017/S0032247416000875}.
 
 \bibitem[\citeproctext]{ref-Deregibus2020}
-Deregibus, Dolores, Zacher, K., Bartsch, I., Campana, G. L., Momo, F.
-R., Wiencke, C., \ldots{} Quartino, M. L. (2020). Carbon {Balance Under}
-a {Changing Light Environment}. In I. Gómez \& P. Huovinen (Eds.),
-\emph{Antarctic {Seaweeds}: {Diversity}, {Adaptation} and {Ecosystem
-Services}} (pp. 173--191). {Cham}: {Springer International Publishing}.
-doi:\href{https://doi.org/10.1007/978-3-030-39448-6_9}{10.1007/978-3-030-39448-6\_9}
+Deregibus, D., Zacher, K., Bartsch, I., Campana, G.L., Momo, F.R.,
+Wiencke, C., Gómez, I., and Quartino, M.L. 2020. Carbon {Balance Under}
+a {Changing Light Environment}. \emph{In} Antarctic {Seaweeds}:
+{Diversity}, {Adaptation} and {Ecosystem Services}. \emph{Edited by} I.
+Gómez and P. Huovinen. {Springer International Publishing}, {Cham}. pp.
+173--191.
+doi:\href{https://doi.org/10.1007/978-3-030-39448-6_9}{10.1007/978-3-030-39448-6\_9}.
 
 \bibitem[\citeproctext]{ref-DiMauro2022}
-Di Mauro, R., Castillo, S., Pérez, A., Iachetti, C. M., Silva, L.,
-Tomba, J. P., \& Chiesa, I. L. (2022). Anthropogenic microfibers are
-highly abundant at the {Burdwood Bank} seamount, a protected
-sub-{Antarctic} environment in the {Southwestern Atlantic Ocean}.
-\emph{Environmental Pollution}, \emph{306}, 119364.
-doi:\href{https://doi.org/10.1016/j.envpol.2022.119364}{10.1016/j.envpol.2022.119364}
+Di Mauro, R., Castillo, S., Pérez, A., Iachetti, C.M., Silva, L., Tomba,
+J.P., and Chiesa, I.L. 2022. Anthropogenic microfibers are highly
+abundant at the {Burdwood Bank} seamount, a protected sub-{Antarctic}
+environment in the {Southwestern Atlantic Ocean}. Environmental
+Pollution \textbf{306}: 119364.
+doi:\href{https://doi.org/10.1016/j.envpol.2022.119364}{10.1016/j.envpol.2022.119364}.
 
 \bibitem[\citeproctext]{ref-Dodino2022}
-Dodino, S., Riccialdelli, L., Polito, M. J., Pütz, K., Brasso, R. L., \&
-Raya Rey, A. (2022). Mercury exposure driven by geographic and trophic
-factors in {Magellanic} penguins from {Tierra} del {Fuego}. \emph{Marine
-Pollution Bulletin}, \emph{174}, 113184.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2021.113184}{10.1016/j.marpolbul.2021.113184}
+Dodino, S., Riccialdelli, L., Polito, M.J., Pütz, K., Brasso, R.L., and
+Raya Rey, A. 2022. Mercury exposure driven by geographic and trophic
+factors in {Magellanic} penguins from {Tierra} del {Fuego}. Marine
+Pollution Bulletin \textbf{174}: 113184.
+doi:\href{https://doi.org/10.1016/j.marpolbul.2021.113184}{10.1016/j.marpolbul.2021.113184}.
 
 \bibitem[\citeproctext]{ref-Duarte2011}
-Duarte, C. A., Giarratano, E., Amin, O. A., \& Comoglio, L. I. (2011).
-Heavy metal concentrations and biomarkers of oxidative stress in native
+Duarte, C.A., Giarratano, E., Amin, O.A., and Comoglio, L.I. 2011. Heavy
+metal concentrations and biomarkers of oxidative stress in native
 mussels ({Mytilus} edulis chilensis) from {Beagle Channel} coast
-({Tierra} del {Fuego}, {Argentina}). \emph{Marine Pollution Bulletin},
-\emph{62}(8), 1895--1904.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2011.05.031}{10.1016/j.marpolbul.2011.05.031}
+({Tierra} del {Fuego}, {Argentina}). Marine Pollution Bulletin
+\textbf{62}(8): 1895--1904.
+doi:\href{https://doi.org/10.1016/j.marpolbul.2011.05.031}{10.1016/j.marpolbul.2011.05.031}.
 
 \bibitem[\citeproctext]{ref-Duffy2007}
-Duffy, J. E., Cardinale, B. J., France, K. E., McIntyre, P. B.,
-Thébault, E., \& Loreau, M. (2007). The functional role of biodiversity
-in ecosystems: Incorporating trophic complexity. \emph{Ecology Letters},
-\emph{10}(6), 522--538.
-doi:\href{https://doi.org/10.1111/j.1461-0248.2007.01037.x}{10.1111/j.1461-0248.2007.01037.x}
+Duffy, J.E., Cardinale, B.J., France, K.E., McIntyre, P.B., Thébault,
+E., and Loreau, M. 2007. The functional role of biodiversity in
+ecosystems: Incorporating trophic complexity. Ecology Letters
+\textbf{10}(6): 522--538.
+doi:\href{https://doi.org/10.1111/j.1461-0248.2007.01037.x}{10.1111/j.1461-0248.2007.01037.x}.
 
 \bibitem[\citeproctext]{ref-Dulvy2014}
-Dulvy, N. K., Fowler, S. L., Musick, J. A., Cavanagh, R. D., Kyne, P.
-M., Harrison, L. R., \ldots{} White, W. T. (2014). Extinction risk and
-conservation of the world's sharks and rays. \emph{eLife}, \emph{3},
-e00590.
-doi:\href{https://doi.org/10.7554/eLife.00590}{10.7554/eLife.00590}
+Dulvy, N.K., Fowler, S.L., Musick, J.A., Cavanagh, R.D., Kyne, P.M.,
+Harrison, L.R., Carlson, J.K., Davidson, L.N., Fordham, S.V., Francis,
+M.P., Pollock, C.M., Simpfendorfer, C.A., Burgess, G.H., Carpenter,
+K.E., Compagno, L.J., Ebert, D.A., Gibson, C., Heupel, M.R.,
+Livingstone, S.R., Sanciangco, J.C., Stevens, J.D., Valenti, S., and
+White, W.T. 2014. Extinction risk and conservation of the world's sharks
+and rays. eLife \textbf{3}: e00590. {eLife Sciences Publications, Ltd}.
+doi:\href{https://doi.org/10.7554/eLife.00590}{10.7554/eLife.00590}.
+
+\bibitem[\citeproctext]{ref-Dunne2002}
+Dunne, J.A., Williams, R.J., and Martinez, N.D. 2002a. Network structure
+and biodiversity loss in food webs: Robustness increases with
+connectance. Ecology Letters \textbf{5}(4): 558--567.
+doi:\href{https://doi.org/10.1046/j.1461-0248.2002.00354.x}{10.1046/j.1461-0248.2002.00354.x}.
 
 \bibitem[\citeproctext]{ref-Dunne2002a}
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Food-web
+Dunne, J.A., Williams, R.J., and Martinez, N.D. 2002b. Food-web
 structure and network theory: {The} role of connectance and size.
-\emph{Proceedings of the National Academy of Sciences}, \emph{99}(20),
-12917--12922.
-doi:\href{https://doi.org/10.1073/pnas.192407699}{10.1073/pnas.192407699}
-
-\bibitem[\citeproctext]{ref-Dunne2002}
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). Network
-structure and biodiversity loss in food webs: Robustness increases with
-connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
-doi:\href{https://doi.org/10.1046/j.1461-0248.2002.00354.x}{10.1046/j.1461-0248.2002.00354.x}
+Proceedings of the National Academy of Sciences \textbf{99}(20):
+12917--12922. {Proceedings of the National Academy of Sciences}.
+doi:\href{https://doi.org/10.1073/pnas.192407699}{10.1073/pnas.192407699}.
 
 \bibitem[\citeproctext]{ref-Fernandez2010}
-Fernández, D. A., Ciancio, J., Ceballos, S. G., Riva-Rossi, C., \&
-Pascual, M. A. (2010). Chinook salmon ({Oncorhynchus} tshawytscha,
+Fernández, D.A., Ciancio, J., Ceballos, S.G., Riva-Rossi, C., and
+Pascual, M.A. 2010. Chinook salmon ({Oncorhynchus} tshawytscha,
 {Walbaum} 1792) in the {Beagle Channel}, {Tierra} del {Fuego}: The onset
-of an invasion. \emph{Biological Invasions}, \emph{12}(9), 2991--2997.
-doi:\href{https://doi.org/10.1007/s10530-010-9731-x}{10.1007/s10530-010-9731-x}
+of an invasion. Biological Invasions \textbf{12}(9): 2991--2997.
+doi:\href{https://doi.org/10.1007/s10530-010-9731-x}{10.1007/s10530-010-9731-x}.
 
 \bibitem[\citeproctext]{ref-Ferreira2021}
-Ferreira, M. F., Lo Nostro, F. L., Fernández, D. A., \& Genovese, G.
-(2021). Endocrine disruption in the sub {Antarctic} fish
-{Patagonotothen} tessellata ({Perciformes}, {Notothenidae}) from {Beagle
-Channel} associated to anthropogenic impact. \emph{Marine Environmental
-Research}, \emph{171}, 105478.
-doi:\href{https://doi.org/10.1016/j.marenvres.2021.105478}{10.1016/j.marenvres.2021.105478}
+Ferreira, M.F., Lo Nostro, F.L., Fernández, D.A., and Genovese, G. 2021.
+Endocrine disruption in the sub {Antarctic} fish {Patagonotothen}
+tessellata ({Perciformes}, {Notothenidae}) from {Beagle Channel}
+associated to anthropogenic impact. Marine Environmental Research
+\textbf{171}: 105478.
+doi:\href{https://doi.org/10.1016/j.marenvres.2021.105478}{10.1016/j.marenvres.2021.105478}.
 
 \bibitem[\citeproctext]{ref-Fioramonti2022}
-Fioramonti, N. E., Ribeiro Guevara, S., Becker, Y. A., \& Riccialdelli,
-L. (2022). Mercury transfer in coastal and oceanic food webs from the
-{Southwest Atlantic Ocean}. \emph{Marine Pollution Bulletin},
-\emph{175}, 113365.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2022.113365}{10.1016/j.marpolbul.2022.113365}
+Fioramonti, N.E., Ribeiro Guevara, S., Becker, Y.A., and Riccialdelli,
+L. 2022. Mercury transfer in coastal and oceanic food webs from the
+{Southwest Atlantic Ocean}. Marine Pollution Bulletin \textbf{175}:
+113365.
+doi:\href{https://doi.org/10.1016/j.marpolbul.2022.113365}{10.1016/j.marpolbul.2022.113365}.
 
@@
 Flores, H., Atkinson, A., Kawaguchi, S., Krafft, B., Milinevsky, G.,
-Nicol, S., \ldots{} Werner, T. (2012). Impact of climate change on
-{Antarctic} krill. \emph{Marine Ecology Progress Series}, \emph{458},
-1--19. doi:\href{https://doi.org/10.3354/meps09831}{10.3354/meps09831}
+Nicol, S., Reiss, C., Tarling, G., Werner, R., Bravo Rebolledo, E.,
+Cirelli, V., Cuzin-Roudy, J., Fielding, S., Van Franeker, J.,
+Groeneveld, J., Haraldsson, M., Lombana, A., Marschoff, E., Meyer, B.,
+Pakhomov, E., Van De Putte, A., Rombolá, E., Schmidt, K., Siegel, V.,
+Teschke, M., Tonkes, H., Toullec, J., Trathan, P., Tremblay, N., and
+Werner, T. 2012. Impact of climate change on {Antarctic} krill. Marine
+Ecology Progress Series \textbf{458}: 1--19.
+doi:\href{https://doi.org/10.3354/meps09831}{10.3354/meps09831}.
 
 \bibitem[\citeproctext]{ref-Franco2020}
-Franco, B. C., Combes, V., \& González Carman, V. (2020). Subsurface
+Franco, B.C., Combes, V., and González Carman, V. 2020. Subsurface
 {Ocean Warming Hotspots} and {Potential Impacts} on {Marine Species}:
-{The Southwest South Atlantic Ocean Case Study}. \emph{Frontiers in
-Marine Science}, \emph{7}.
+{The Southwest South Atlantic Ocean Case Study}. Frontiers in Marine
+Science \textbf{7}. {[}accessed 10 August 2023{]}.
 
 \bibitem[\citeproctext]{ref-Fretwell2023}
-Fretwell, P. T., Boutet, A., \& Ratcliffe, N. (2023). Record low 2022
+Fretwell, P.T., Boutet, A., and Ratcliffe, N. 2023. Record low 2022
 {Antarctic} sea ice led to catastrophic breeding failure of emperor
-penguins. \emph{Communications Earth \& Environment}, \emph{4}(1), 1--6.
-doi:\href{https://doi.org/10.1038/s43247-023-00927-x}{10.1038/s43247-023-00927-x}
+penguins. Communications Earth \& Environment \textbf{4}(1): 1--6.
+{Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s43247-023-00927-x}{10.1038/s43247-023-00927-x}.
 
 \bibitem[\citeproctext]{ref-Fuentes2016}
-Fuentes, V., Alurralde, G., Meyer, B., Aguirre, G. E., Canepa, A.,
-Wölfl, A.-C., \ldots{} Schloss, I. R. (2016). Glacial melting: An
-overlooked threat to {Antarctic} krill. \emph{Scientific Reports},
-\emph{6}(1), 27234.
-doi:\href{https://doi.org/10.1038/srep27234}{10.1038/srep27234}
+Fuentes, V., Alurralde, G., Meyer, B., Aguirre, G.E., Canepa, A., Wölfl,
+A.-C., Hass, H.C., Williams, G.N., and Schloss, I.R. 2016. Glacial
+melting: An overlooked threat to {Antarctic} krill. Scientific Reports
+\textbf{6}(1): 27234. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/srep27234}{10.1038/srep27234}.
 
 \bibitem[\citeproctext]{ref-Funes2020}
-Funes, M. (2020, March). \emph{Efectos de la pesca de arrastre sobre la
-estructura trófica del norte del {Golfo San Jorge}} (PhD thesis).
+Funes, M. 2020, March. Efectos de la pesca de arrastre sobre la
+estructura trófica del norte del {Golfo San Jorge}. PhD thesis.
 
 \bibitem[\citeproctext]{ref-Funes2019}
-Funes, M., Marinao, C., \& Galván, D. E. (2019). Does trawl fisheries
+Funes, M., Marinao, C., and Galván, D.E. 2019. Does trawl fisheries
 affect the diet of fishes? {A} stable isotope analysis approach*.
-\emph{Isotopes in Environmental and Health Studies}, \emph{55}(4),
-327--343.
-doi:\href{https://doi.org/10.1080/10256016.2019.1626381}{10.1080/10256016.2019.1626381}
+Isotopes in Environmental and Health Studies \textbf{55}(4): 327--343.
+{Taylor \& Francis}.
+doi:\href{https://doi.org/10.1080/10256016.2019.1626381}{10.1080/10256016.2019.1626381}.
 
 \bibitem[\citeproctext]{ref-Funes2022}
-Funes, M., Saravia, L. A., Cordone, G., Iribarne, O. O., \& Galván, D.
-E. (2022). Network analysis suggests changes in food web stability
-produced by bottom trawl fishery in {Patagonia}. \emph{Scientific
-Reports}, \emph{12}(1), 10876.
-doi:\href{https://doi.org/10.1038/s41598-022-14363-y}{10.1038/s41598-022-14363-y}
+Funes, M., Saravia, L.A., Cordone, G., Iribarne, O.O., and Galván, D.E.
+2022. Network analysis suggests changes in food web stability produced
+by bottom trawl fishery in {Patagonia}. Scientific Reports
+\textbf{12}(1): 10876. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41598-022-14363-y}{10.1038/s41598-022-14363-y}.
 
 \bibitem[\citeproctext]{ref-Gaitan2016}
-Gaitán, E., \& Marí, N. (2016). {Análisis de las comunidades bentónicas
+Gaitán, E., and Marí, N. 2016. {Análisis de las comunidades bentónicas
 asociadas a capturas de la flota comercial dirigida a Macruronus
@@
 \bibitem[\citeproctext]{ref-Galvan2022}
-Galván, D. E., Bovcon, N. D., Cochia, P. D., González, R. A., Lattuca,
-M. E., Reinaldo, M. O., \ldots{} Svendsen, G. M. (2022). Changes in the
-{Specific} and {Biogeographic Composition} of {Coastal Fish Assemblages}
-in {Patagonia}, {Driven} by {Climate Change}, {Fishing}, and {Invasion}
-by {Alien Species}. In E. W. Helbling, M. A. Narvarte, R. A. González,
-\& V. E. Villafañe (Eds.), \emph{Global {Change} in {Atlantic Coastal
-Patagonian Ecosystems}: {A Journey Through Time}} (pp. 205--231).
-{Cham}: {Springer International Publishing}.
-doi:\href{https://doi.org/10.1007/978-3-030-86676-1_9}{10.1007/978-3-030-86676-1\_9}
+Galván, D.E., Bovcon, N.D., Cochia, P.D., González, R.A., Lattuca, M.E.,
+Reinaldo, M.O., Rincón-Díaz, M.P., Romero, M.A., Vanella, F.A., Venerus,
+L.A., and Svendsen, G.M. 2022. Changes in the {Specific} and
+{Biogeographic Composition} of {Coastal Fish Assemblages} in
+{Patagonia}, {Driven} by {Climate Change}, {Fishing}, and {Invasion} by
+{Alien Species}. \emph{In} Global {Change} in {Atlantic Coastal
+Patagonian Ecosystems}: {A Journey Through Time}. \emph{Edited by} E.W.
+Helbling, M.A. Narvarte, R.A. González, and V.E. Villafañe. {Springer
+International Publishing}, {Cham}. pp. 205--231.
+doi:\href{https://doi.org/10.1007/978-3-030-86676-1_9}{10.1007/978-3-030-86676-1\_9}.
 
 \bibitem[\citeproctext]{ref-Garcia2019}
-Garcia, M. D., Fernández Severini, M. D., Spetter, C., López Abbate, M.
-C., Tartara, M. N., Nahuelhual, E. G., \ldots{} Hoffmeyer, M. S. (2019).
-Effects of glacier melting on the planktonic communities of two
-{Antarctic} coastal areas ({Potter Cove} and {Hope Bay}) in summer.
-\emph{Regional Studies in Marine Science}, \emph{30}, 100731.
-doi:\href{https://doi.org/10.1016/j.rsma.2019.100731}{10.1016/j.rsma.2019.100731}
+Garcia, M.D., Fernández Severini, M.D., Spetter, C., López Abbate, M.C.,
+Tartara, M.N., Nahuelhual, E.G., Marcovecchio, J.E., Schloss, I.R., and
+Hoffmeyer, M.S. 2019. Effects of glacier melting on the planktonic
+communities of two {Antarctic} coastal areas ({Potter Cove} and {Hope
+Bay}) in summer. Regional Studies in Marine Science \textbf{30}: 100731.
+doi:\href{https://doi.org/10.1016/j.rsma.2019.100731}{10.1016/j.rsma.2019.100731}.
 
 \bibitem[\citeproctext]{ref-Garcia2016}
-Garcia, M. D., Hoffmeyer, M. S., Abbate, M. C. L., Barría De Cao, M. S.,
-Pettigrosso, R. E., Almandoz, G. O., \ldots{} Schloss, I. R. (2016).
-Micro- and mesozooplankton responses during two contrasting summers in a
-coastal {Antarctic} environment. \emph{Polar Biology}, \emph{39}(1),
-123--137.
-doi:\href{https://doi.org/10.1007/s00300-015-1678-z}{10.1007/s00300-015-1678-z}
+Garcia, M.D., Hoffmeyer, M.S., Abbate, M.C.L., Barría De Cao, M.S.,
+Pettigrosso, R.E., Almandoz, G.O., Hernando, M.P., and Schloss, I.R.
+2016. Micro- and mesozooplankton responses during two contrasting
+summers in a coastal {Antarctic} environment. Polar Biology
+\textbf{39}(1): 123--137.
+doi:\href{https://doi.org/10.1007/s00300-015-1678-z}{10.1007/s00300-015-1678-z}.
 
 \bibitem[\citeproctext]{ref-Garcia-Borboroglu2008}
-García-Borboroglu, P., Boersma, P. D., Reyes, L., \& Skewgar, E. (2008).
+García-Borboroglu, P., Boersma, P.D., Reyes, L., and Skewgar, E. 2008.
 Petroleum {Pollution} and {Penguins}: {Marine Conservation Tools} to
-{Reduce} the {Problem}. In \emph{Marine {Pollution}: {New} research}
-(Hofer, T.N., pp. 339--356). {New York, USA}: {Nova Science Publishers
-Inc.}
+{Reduce} the {Problem}. \emph{In} Marine {Pollution}: {New} research,
+Hofer, T.N. {Nova Science Publishers Inc.}, {New York, USA}. pp.
+339--356.
 
 \bibitem[\citeproctext]{ref-Gauzens2023}
-Gauzens, B., Brose, U., Delmas, E., \& Berti, E. (n.d.). {ATNr}:
-{Allometric Trophic Network} models in {R}. \emph{Methods in Ecology and
-Evolution}, \emph{n/a}(n/a).
-doi:\href{https://doi.org/10.1111/2041-210X.14212}{10.1111/2041-210X.14212}
+Gauzens, B., Brose, U., Delmas, E., and Berti, E. (n.d.). {ATNr}:
+{Allometric Trophic Network} models in {R}. Methods in Ecology and
+Evolution \textbf{n/a}(n/a).
+doi:\href{https://doi.org/10.1111/2041-210X.14212}{10.1111/2041-210X.14212}.
 
 \bibitem[\citeproctext]{ref-Gellner2023}
-Gellner, G., McCann, K., \& Hastings, A. (2023). Stable diverse food
-webs become more common when interactions are more biologically
-constrained. \emph{Proceedings of the National Academy of Sciences},
-\emph{120}(31), e2212061120.
-doi:\href{https://doi.org/10.1073/pnas.2212061120}{10.1073/pnas.2212061120}
+Gellner, G., McCann, K., and Hastings, A. 2023. Stable diverse food webs
+become more common when interactions are more biologically constrained.
+Proceedings of the National Academy of Sciences \textbf{120}(31):
+e2212061120. {Proceedings of the National Academy of Sciences}.
+doi:\href{https://doi.org/10.1073/pnas.2212061120}{10.1073/pnas.2212061120}.
 
 \bibitem[\citeproctext]{ref-Gil2011}
-Gil, M. N., Torres, A. I., Amin, O., \& Esteves, J. L. (2011).
-Assessment of recent sediment influence in an urban polluted
-subantarctic coastal ecosystem. {Beagle Channel} ({Southern Argentina}).
-\emph{Marine Pollution Bulletin}, \emph{62}(1), 201--207.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2010.10.004}{10.1016/j.marpolbul.2010.10.004}
+Gil, M.N., Torres, A.I., Amin, O., and Esteves, J.L. 2011. Assessment of
+recent sediment influence in an urban polluted subantarctic coastal
+ecosystem. {Beagle Channel} ({Southern Argentina}). Marine Pollution
+Bulletin \textbf{62}(1): 201--207.
+doi:\href{https://doi.org/10.1016/j.marpolbul.2010.10.004}{10.1016/j.marpolbul.2010.10.004}.
 
 \bibitem[\citeproctext]{ref-Glembocki2015}
-Glembocki, N. G., Williams, G. N., Góngora, M. E., Gagliardini, D. A.,
-\& Orensanz, J. M. (Lobo). (2015). Synoptic oceanography of {San Jorge
-Gulf} ({Argentina}): {A} template for {Patagonian} red shrimp
-({Pleoticus} muelleri) spatial dynamics. \emph{Journal of Sea Research},
-\emph{95}, 22--35.
-doi:\href{https://doi.org/10.1016/j.seares.2014.10.011}{10.1016/j.seares.2014.10.011}
+Glembocki, N.G., Williams, G.N., Góngora, M.E., Gagliardini, D.A., and
+Orensanz, J.M.(Lobo). 2015. Synoptic oceanography of {San Jorge Gulf}
+({Argentina}): {A} template for {Patagonian} red shrimp ({Pleoticus}
+muelleri) spatial dynamics. Journal of Sea Research \textbf{95}: 22--35.
+doi:\href{https://doi.org/10.1016/j.seares.2014.10.011}{10.1016/j.seares.2014.10.011}.
 
 \bibitem[\citeproctext]{ref-Gongora2012}
-Góngora, M. E., González-Zevallos, D., Pettovello, A., \& Mendía, L.
-(2012). Caracterización de las principales pesquerías del golfo {San
-Jorge Patagonia}, {Argentina}. \emph{Latin American Journal of Aquatic
-Research}, \emph{40}(1), 1--11.
+Góngora, M.E., González-Zevallos, D., Pettovello, A., and Mendía, L.
+2012. Caracterización de las principales pesquerías del golfo {San Jorge
+Patagonia}, {Argentina}. Latin american journal of aquatic research
+\textbf{40}(1): 1--11. {Pontificia Universidad Católica de Valparaíso.
+Facultad de Recursos Naturales. Escuela de Ciencias del Mar}.
+{[}accessed 14 August 2023{]}.
 
 \bibitem[\citeproctext]{ref-Gonzalez-Zevallos2006}
-González-Zevallos, D., \& Yorio, P. (2006). Seabird use of discards and
+González-Zevallos, D., and Yorio, P. 2006. Seabird use of discards and
 incidental captures at the {Argentine} hake trawl fishery in the {Golfo
-San Jorge}, {Argentina}. \emph{Marine Ecology Progress Series},
-\emph{316}, 175--183.
-doi:\href{https://doi.org/10.3354/meps316175}{10.3354/meps316175}
+San Jorge}, {Argentina}. Marine Ecology Progress Series \textbf{316}:
+175--183.
+doi:\href{https://doi.org/10.3354/meps316175}{10.3354/meps316175}.
 
 \bibitem[\citeproctext]{ref-Gorini2021}
-Gorini, F. L., Lukaszewicz, G., \& Giussi, A. R. (2021).
-\emph{{Actualización de la estadística pesquera de peces demersales
-australes en el Atlántico Sudoccidental (período 2008-2020)}} (\{Informe
-T\textbackslash\textquotesingle ecnico Oficial\}) (p. 64). {Mar del
-Plata}: {Instituto Nacional de Investigación y Desarrollo Pesquero
-(INIDEP)}.
+Gorini, F.L., Lukaszewicz, G., and Giussi, A.R. 2021. {Actualización de
+la estadística pesquera de peces demersales australes en el Atlántico
+Sudoccidental (período 2008-2020)}. \{Informe
+T\textbackslash\textquotesingle ecnico Oficial\}, {Instituto Nacional de
+Investigación y Desarrollo Pesquero (INIDEP)}, {Mar del Plata}.
 
 \bibitem[\citeproctext]{ref-Guihou2020}
-Guihou, K., Piola, A. R., Palma, E. D., \& Chidichimo, M. P. (2020).
+Guihou, K., Piola, A.R., Palma, E.D., and Chidichimo, M.P. 2020.
 Dynamical connections between large marine ecosystems of austral {South
-America} based on numerical simulations. \emph{Ocean Science},
-\emph{16}(2), 271--290.
-doi:\href{https://doi.org/10.5194/os-16-271-2020}{10.5194/os-16-271-2020}
+America} based on numerical simulations. Ocean Science \textbf{16}(2):
+271--290. {Copernicus GmbH}.
+doi:\href{https://doi.org/10.5194/os-16-271-2020}{10.5194/os-16-271-2020}.
 
 \bibitem[\citeproctext]{ref-Gutt2001a}
-Gutt, J. (2001). On the direct impact of ice on marine benthic
-communities, a review. \emph{Polar Biology}, \emph{24}(8), 553--564.
-doi:\href{https://doi.org/10.1007/s003000100262}{10.1007/s003000100262}
+Gutt, J. 2001. On the direct impact of ice on marine benthic
+communities, a review. Polar Biology \textbf{24}(8): 553--564.
+doi:\href{https://doi.org/10.1007/s003000100262}{10.1007/s003000100262}.
 
 \bibitem[\citeproctext]{ref-Gutt2015}
-Gutt, J., Bertler, N., Bracegirdle, T. J., Buschmann, A., Comiso, J.,
-Hosie, G., \ldots{} Xavier, J. C. (2015). The {Southern Ocean} ecosystem
-under multiple climate change stresses - an integrated circumpolar
-assessment. \emph{Global Change Biology}, \emph{21}(4), 1434--1453.
-doi:\href{https://doi.org/10.1111/gcb.12794}{10.1111/gcb.12794}
+Gutt, J., Bertler, N., Bracegirdle, T.J., Buschmann, A., Comiso, J.,
+Hosie, G., Isla, E., Schloss, I.R., Smith, C.R., Tournadre, J., and
+Xavier, J.C. 2015. The {Southern Ocean} ecosystem under multiple climate
+change stresses - an integrated circumpolar assessment. Global Change
+Biology \textbf{21}(4): 1434--1453.
+doi:\href{https://doi.org/10.1111/gcb.12794}{10.1111/gcb.12794}.
 
 \bibitem[\citeproctext]{ref-Gutt2021}
-Gutt, J., Isla, E., Xavier, J. C., Adams, B. J., Ahn, I.-Y., Cheng,
-C.-H. C., \ldots{} Wall, D. H. (2021). Antarctic ecosystems in
-transition \textendash{} life between stresses and opportunities.
-\emph{Biological Reviews}, \emph{96}(3), 798--821.
-doi:\href{https://doi.org/10.1111/brv.12679}{10.1111/brv.12679}
+Gutt, J., Isla, E., Xavier, J.C., Adams, B.J., Ahn, I.-Y., Cheng,
+C.-H.C., Colesie, C., Cummings, V.J., di Prisco, G., Griffiths, H.,
+Hawes, I., Hogg, I., McIntyre, T., Meiners, K.M., Pearce, D.A., Peck,
+L., Piepenburg, D., Reisinger, R.R., Saba, G.K., Schloss, I.R., Signori,
+C.N., Smith, C.R., Vacchi, M., Verde, C., and Wall, D.H. 2021. Antarctic
+ecosystems in transition \textendash{} life between stresses and
+opportunities. Biological Reviews \textbf{96}(3): 798--821.
+doi:\href{https://doi.org/10.1111/brv.12679}{10.1111/brv.12679}.
 
 \bibitem[\citeproctext]{ref-Gutt2003}
-Gutt, J., \& Piepenburg, D. (2003). Scale-dependent impact on diversity
-of {Antarctic} benthos caused by grounding of icebergs. \emph{Marine
-Ecology Progress Series}, \emph{253}, 77--83.
-doi:\href{https://doi.org/10.3354/meps253077}{10.3354/meps253077}
+Gutt, J., and Piepenburg, D. 2003. Scale-dependent impact on diversity
+of {Antarctic} benthos caused by grounding of icebergs. Marine Ecology
+Progress Series \textbf{253}: 77--83.
+doi:\href{https://doi.org/10.3354/meps253077}{10.3354/meps253077}.
 
 \bibitem[\citeproctext]{ref-Gutt2001}
-Gutt, J., \& Starmans, A. (2001). Quantification of iceberg impact and
+Gutt, J., and Starmans, A. 2001. Quantification of iceberg impact and
 benthic recolonisation patterns in the {Weddell Sea} ({Antarctica}).
-\emph{Polar Biology}, \emph{24}(8), 615--619.
-doi:\href{https://doi.org/10.1007/s003000100263}{10.1007/s003000100263}
+Polar Biology \textbf{24}(8): 615--619.
+doi:\href{https://doi.org/10.1007/s003000100263}{10.1007/s003000100263}.
 
 \bibitem[\citeproctext]{ref-Hilborn2017}
-Hilborn, R., Amoroso, R. O., Bogazzi, E., Jensen, O. P., Parma, A. M.,
-Szuwalski, C., \& Walters, C. J. (2017). When does fishing forage
-species affect their predators? \emph{Fisheries Research}, \emph{191},
-211--221.
-doi:\href{https://doi.org/10.1016/j.fishres.2017.01.008}{10.1016/j.fishres.2017.01.008}
+Hilborn, R., Amoroso, R.O., Bogazzi, E., Jensen, O.P., Parma, A.M.,
+Szuwalski, C., and Walters, C.J. 2017. When does fishing forage species
+affect their predators? Fisheries Research \textbf{191}: 211--221.
+doi:\href{https://doi.org/10.1016/j.fishres.2017.01.008}{10.1016/j.fishres.2017.01.008}.
 
 \bibitem[\citeproctext]{ref-Hindell2020}
-Hindell, M. A., Reisinger, R. R., Ropert-Coudert, Y., Hückstädt, L. A.,
-Trathan, P. N., Bornemann, H., \ldots{} Raymond, B. (2020). Tracking of
-marine predators to protect {Southern Ocean} ecosystems. \emph{Nature},
-\emph{580}(7801), 87--92.
-doi:\href{https://doi.org/10.1038/s41586-020-2126-y}{10.1038/s41586-020-2126-y}
+Hindell, M.A., Reisinger, R.R., Ropert-Coudert, Y., Hückstädt, L.A.,
+Trathan, P.N., Bornemann, H., Charrassin, J.-B., Chown, S.L., Costa,
+D.P., Danis, B., Lea, M.-A., Thompson, D., Torres, L.G., Van de Putte,
+A.P., Alderman, R., Andrews-Goff, V., Arthur, B., Ballard, G., Bengtson,
+J., Bester, M.N., Blix, A.S., Boehme, L., Bost, C.-A., Boveng, P.,
+Cleeland, J., Constantine, R., Corney, S., Crawford, R.J.M., Dalla Rosa,
+L., de Bruyn, P.J.N., Delord, K., Descamps, S., Double, M., Emmerson,
+L., Fedak, M., Friedlaender, A., Gales, N., Goebel, M.E., Goetz, K.T.,
+Guinet, C., Goldsworthy, S.D., Harcourt, R., Hinke, J.T., Jerosch, K.,
+Kato, A., Kerry, K.R., Kirkwood, R., Kooyman, G.L., Kovacs, K.M.,
+Lawton, K., Lowther, A.D., Lydersen, C., Lyver, P.O., Makhado, A.B.,
+Márquez, M.E.I., McDonald, B.I., McMahon, C.R., Muelbert, M.,
+Nachtsheim, D., Nicholls, K.W., Nordøy, E.S., Olmastroni, S., Phillips,
+R.A., Pistorius, P., Plötz, J., Pütz, K., Ratcliffe, N., Ryan, P.G.,
+Santos, M., Southwell, C., Staniland, I., Takahashi, A., Tarroux, A.,
+Trivelpiece, W., Wakefield, E., Weimerskirch, H., Wienecke, B., Xavier,
+J.C., Wotherspoon, S., Jonsen, I.D., and Raymond, B. 2020. Tracking of
+marine predators to protect {Southern Ocean} ecosystems. Nature
+\textbf{580}(7801): 87--92. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41586-020-2126-y}{10.1038/s41586-020-2126-y}.
 
 \bibitem[\citeproctext]{ref-Hoffmann2019}
-Hoffmann, R., Al-Handal, A. Y., Wulff, A., Deregibus, D., Zacher, K.,
-Quartino, M. L., \ldots{} Braeckman, U. (2019). Implications of {Glacial
-Melt-Related Processes} on the {Potential Primary Production} of a
-{Microphytobenthic Community} in {Potter Cove} ({Antarctica}).
-\emph{Frontiers in Marine Science}, \emph{6}, 655.
-doi:\href{https://doi.org/10.3389/fmars.2019.00655}{10.3389/fmars.2019.00655}
+Hoffmann, R., Al-Handal, A.Y., Wulff, A., Deregibus, D., Zacher, K.,
+Quartino, M.L., Wenzhöfer, F., and Braeckman, U. 2019. Implications of
+{Glacial Melt-Related Processes} on the {Potential Primary Production}
+of a {Microphytobenthic Community} in {Potter Cove} ({Antarctica}).
+Frontiers in Marine Science \textbf{6}: 655.
+doi:\href{https://doi.org/10.3389/fmars.2019.00655}{10.3389/fmars.2019.00655}.
 
 \bibitem[\citeproctext]{ref-Iken2023}
-Iken, K., Amsler, C. D., Gorman, K. B., Klein, A. G., Galloway, A. W.
-E., Amsler, M. O., \ldots{} McClintock, J. B. (2023). Macroalgal input
-into the coastal food web along a gradient of seasonal sea ice cover
-along the {Western Antarctic Peninsula}. \emph{Marine Ecology Progress
-Series}, \emph{718}, 1--22.
-doi:\href{https://doi.org/10.3354/meps14388}{10.3354/meps14388}
+Iken, K., Amsler, C.D., Gorman, K.B., Klein, A.G., Galloway, A.W.E.,
+Amsler, M.O., Heiser, S., Whippo, R., Lowe, A.T., Schram, J.B.,
+Schneider, Z.X., and McClintock, J.B. 2023. Macroalgal input into the
+coastal food web along a gradient of seasonal sea ice cover along the
+{Western Antarctic Peninsula}. Marine Ecology Progress Series
+\textbf{718}: 1--22.
+doi:\href{https://doi.org/10.3354/meps14388}{10.3354/meps14388}.
 
 \bibitem[\citeproctext]{ref-Irons2000}
-Irons, D. B., Kendall, S. J., Erickson, W. P., McDonald, L. L., \&
-Lance, B. K. (2000). Nine {Years After} the {Exxon Valdez Oil Spill}:
-{Effects} on {Marine Bird Populations} in {Prince William Sound},
-{Alaska}. \emph{The Condor}, \emph{102}(4), 723--737.
-doi:\href{https://doi.org/10.1093/condor/102.4.723}{10.1093/condor/102.4.723}
+Irons, D.B., Kendall, S.J., Erickson, W.P., McDonald, L.L., and Lance,
+B.K. 2000. Nine {Years After} the {Exxon Valdez Oil Spill}: {Effects} on
+{Marine Bird Populations} in {Prince William Sound}, {Alaska}. The
+Condor \textbf{102}(4): 723--737.
+doi:\href{https://doi.org/10.1093/condor/102.4.723}{10.1093/condor/102.4.723}.
 
 \bibitem[\citeproctext]{ref-Isla2023}
-Isla, E. (2023). Animal\textendash{{Energy Relationships}} in a
-{Changing Ocean}: {The Case} of {Continental Shelf Macrobenthic
-Communities} on the {Weddell Sea} and the {Vicinity} of the {Antarctic
-Peninsula}. \emph{Biology}, \emph{12}(5), 659.
-doi:\href{https://doi.org/10.3390/biology12050659}{10.3390/biology12050659}
+Isla, E. 2023. Animal\textendash{{Energy Relationships}} in a {Changing
+Ocean}: {The Case} of {Continental Shelf Macrobenthic Communities} on
+the {Weddell Sea} and the {Vicinity} of the {Antarctic Peninsula}.
+Biology \textbf{12}(5): 659. {Multidisciplinary Digital Publishing
+Institute}.
+doi:\href{https://doi.org/10.3390/biology12050659}{10.3390/biology12050659}.
 
 \bibitem[\citeproctext]{ref-Jacob2011}
-Jacob, U., Thierry, A., Brose, U., Arntz, W. E., Berg, S., Brey, T.,
-\ldots{} Dunne, J. A. (2011). The {Role} of {Body Size} in {Complex Food
-Webs}: {A Cold Case}. In A. Belgrano (Ed.), \emph{Advances in
-{Ecological Research}} (Vol. 45, pp. 181--223). {Academic Press}.
-doi:\href{https://doi.org/10.1016/B978-0-12-386475-8.00005-8}{10.1016/B978-0-12-386475-8.00005-8}
+Jacob, U., Thierry, A., Brose, U., Arntz, W.E., Berg, S., Brey, T.,
+Fetzer, I., Jonsson, T., Mintenbeck, K., Möllmann, C., Petchey, O.L.,
+Riede, J.O., and Dunne, J.A. 2011. The {Role} of {Body Size} in {Complex
+Food Webs}: {A Cold Case}. \emph{In} Advances in {Ecological Research}.
+\emph{Edited by} A. Belgrano. {Academic Press}. pp. 181--223.
+doi:\href{https://doi.org/10.1016/B978-0-12-386475-8.00005-8}{10.1016/B978-0-12-386475-8.00005-8}.
 
@@
 Jerosch, K., Pehlke, H., Monien, P., Scharf, F., Weber, L., Kuhn, G.,
-\ldots{} Abele, D. (2018). Benthic meltwater fjord habitats formed by
-rapid glacier recession on {King George Island}, {Antarctica}.
-\emph{Philosophical Transactions of the Royal Society A: Mathematical,
-Physical and Engineering Sciences}, \emph{376}(2122), 20170178.
-doi:\href{https://doi.org/10.1098/rsta.2017.0178}{10.1098/rsta.2017.0178}
+Braun, M.H., and Abele, D. 2018. Benthic meltwater fjord habitats formed
+by rapid glacier recession on {King George Island}, {Antarctica}.
+Philosophical Transactions of the Royal Society A: Mathematical,
+Physical and Engineering Sciences \textbf{376}(2122): 20170178.
+doi:\href{https://doi.org/10.1098/rsta.2017.0178}{10.1098/rsta.2017.0178}.
 
 \bibitem[\citeproctext]{ref-Jordan2007}
-Jordán, F., Benedek, Z., \& Podani, J. (2007). Quantifying positional
+Jordán, F., Benedek, Z., and Podani, J. 2007. Quantifying positional
 importance in food webs: {A} comparison of centrality indices.
-\emph{Ecological Modelling}, \emph{205}(1), 270--275.
-doi:\href{https://doi.org/10.1016/j.ecolmodel.2007.02.032}{10.1016/j.ecolmodel.2007.02.032}
+Ecological Modelling \textbf{205}(1): 270--275.
+doi:\href{https://doi.org/10.1016/j.ecolmodel.2007.02.032}{10.1016/j.ecolmodel.2007.02.032}.
 
 \bibitem[\citeproctext]{ref-Kaminskyinprep}
-Kaminsky, J., Bagur, M., Boraso, A., Schloss, I. R., Buschmann, A. H.,
-\& Quartino, M. L. (in prep.). Kelp recruitment declines in a
-sub-{Antarctic} ecosystem with high sediment inputs and changes in the
-understory algae.
+Kaminsky, J., Bagur, M., Boraso, A., Schloss, I.R., Buschmann, A.H., and
+Quartino, M.L. in prep. Kelp recruitment declines in a sub-{Antarctic}
+ecosystem with high sediment inputs and changes in the understory algae.
 
 \bibitem[\citeproctext]{ref-Kawaguchi2009}
-Kawaguchi, S., Nicol, S., \& Press, A. (2009). Direct effects of climate
-change on the {Antarctic} krill fishery.
+Kawaguchi, S., Nicol, S., and Press, A. 2009. Direct effects of climate
+change on the {Antarctic} krill fishery. {University Of Tasmania}.
+{[}accessed 13 September 2023{]}.
 
 \bibitem[\citeproctext]{ref-Klein2018}
-Klein, E. S., Hill, S. L., Hinke, J. T., Phillips, T., \& Watters, G. M.
-(2018). Impacts of rising sea temperature on krill increase risks for
-predators in the {Scotia Sea}. \emph{PLOS ONE}, \emph{13}(1), e0191011.
-doi:\href{https://doi.org/10.1371/journal.pone.0191011}{10.1371/journal.pone.0191011}
+Klein, E.S., Hill, S.L., Hinke, J.T., Phillips, T., and Watters, G.M.
+2018. Impacts of rising sea temperature on krill increase risks for
+predators in the {Scotia Sea}. PLOS ONE \textbf{13}(1): e0191011.
+{Public Library of Science}.
+doi:\href{https://doi.org/10.1371/journal.pone.0191011}{10.1371/journal.pone.0191011}.
 
@@
 Kortsch, S., Frelat, R., Pecuchet, L., Olivier, P., Putnis, I.,
-Bonsdorff, E., \ldots{} Nordström, M. C. (2021). Disentangling temporal
-food web dynamics facilitates understanding of ecosystem functioning.
-\emph{Journal of Animal Ecology}, \emph{90}(5), 1205--1216.
-doi:\href{https://doi.org/10.1111/1365-2656.13447}{10.1111/1365-2656.13447}
+Bonsdorff, E., Ojaveer, H., Jurgensone, I., Strāķe, S., Rubene, G.,
+Krūze, Ē., and Nordström, M.C. 2021. Disentangling temporal food web
+dynamics facilitates understanding of ecosystem functioning. Journal of
+Animal Ecology \textbf{90}(5): 1205--1216.
+doi:\href{https://doi.org/10.1111/1365-2656.13447}{10.1111/1365-2656.13447}.
 
 \bibitem[\citeproctext]{ref-Kortsch2019}
-Kortsch, S., Primicerio, R., Aschan, M., Lind, S., Dolgov, A. V., \&
-Planque, B. (2019). Food-web structure varies along environmental
-gradients in a high-latitude marine ecosystem. \emph{Ecography},
-\emph{42}(2), 295--308.
-doi:\href{https://doi.org/10.1111/ecog.03443}{10.1111/ecog.03443}
+Kortsch, S., Primicerio, R., Aschan, M., Lind, S., Dolgov, A.V., and
+Planque, B. 2019. Food-web structure varies along environmental
+gradients in a high-latitude marine ecosystem. Ecography \textbf{42}(2):
+295--308.
+doi:\href{https://doi.org/10.1111/ecog.03443}{10.1111/ecog.03443}.
 
 \bibitem[\citeproctext]{ref-Kortsch2015}
-Kortsch, S., Primicerio, R., Fossheim, M., Dolgov, A. V., \& Aschan, M.
-(2015). Climate change alters the structure of arctic marine food webs
-due to poleward shifts of boreal generalists. \emph{Proceedings of the
-Royal Society B: Biological Sciences}, \emph{282}(1814), 20151546.
-doi:\href{https://doi.org/10.1098/rspb.2015.1546}{10.1098/rspb.2015.1546}
+Kortsch, S., Primicerio, R., Fossheim, M., Dolgov, A.V., and Aschan, M.
+2015. Climate change alters the structure of arctic marine food webs due
+to poleward shifts of boreal generalists. Proceedings of the Royal
+Society B: Biological Sciences \textbf{282}(1814): 20151546.
+doi:\href{https://doi.org/10.1098/rspb.2015.1546}{10.1098/rspb.2015.1546}.
 
 \bibitem[\citeproctext]{ref-Kratina2012}
-Kratina, P., LeCraw, R. M., Ingram, T., \& Anholt, B. R. (2012).
-Stability and persistence of food webs with omnivory: {Is} there a
-general pattern? \emph{Ecosphere}, \emph{3}(6), art50.
-doi:\href{https://doi.org/10.1890/ES12-00121.1}{10.1890/ES12-00121.1}
+Kratina, P., LeCraw, R.M., Ingram, T., and Anholt, B.R. 2012. Stability
+and persistence of food webs with omnivory: {Is} there a general
+pattern? Ecosphere \textbf{3}(6): art50.
+doi:\href{https://doi.org/10.1890/ES12-00121.1}{10.1890/ES12-00121.1}.
 
 \bibitem[\citeproctext]{ref-Latorre2023}
-Latorre, M. P., Iachetti, C. M., Schloss, I. R., Antoni, J., Malits, A.,
-De La Rosa, F., \ldots{} Hernando, M. (2023). Summer heatwaves affect
-coastal {Antarctic} plankton metabolism and community structure.
-\emph{Journal of Experimental Marine Biology and Ecology}, \emph{567},
-151926.
-doi:\href{https://doi.org/10.1016/j.jembe.2023.151926}{10.1016/j.jembe.2023.151926}
+Latorre, M.P., Iachetti, C.M., Schloss, I.R., Antoni, J., Malits, A., De
+La Rosa, F., De Troch, M., Garcia, M.D., Flores-Melo, X., Romero, S.I.,
+Gil, M.N., and Hernando, M. 2023. Summer heatwaves affect coastal
+{Antarctic} plankton metabolism and community structure. Journal of
+Experimental Marine Biology and Ecology \textbf{567}: 151926.
+doi:\href{https://doi.org/10.1016/j.jembe.2023.151926}{10.1016/j.jembe.2023.151926}.
 
 \bibitem[\citeproctext]{ref-Lattuca2018}
-Lattuca, María Eugenia, Boy, C. C., Vanella, F. A., Barrantes, M. E., \&
-Fernández, D. A. (2018). Thermal responses of three native fishes from
-estuarine areas of the {Beagle Channel}, and their implications for
-climate change. \emph{Hydrobiologia}, \emph{808}(1), 235--249.
-doi:\href{https://doi.org/10.1007/s10750-017-3424-8}{10.1007/s10750-017-3424-8}
+Lattuca, M.E., Boy, C.C., Vanella, F.A., Barrantes, M.E., and Fernández,
+D.A. 2018. Thermal responses of three native fishes from estuarine areas
+of the {Beagle Channel}, and their implications for climate change.
+Hydrobiologia \textbf{808}(1): 235--249.
+doi:\href{https://doi.org/10.1007/s10750-017-3424-8}{10.1007/s10750-017-3424-8}.
 
 \bibitem[\citeproctext]{ref-Lattuca2023}
-Lattuca, María E., Vanella, F. A., Malanga, G., Rubel, M. D., Manríquez,
-P. H., Torres, R., \ldots{} Fernández, D. A. (2023). Ocean acidification
-and seasonal temperature extremes combine to impair the thermal
-physiology of a sub-{Antarctic} fish. \emph{Science of The Total
-Environment}, \emph{856}, 159284.
-doi:\href{https://doi.org/10.1016/j.scitotenv.2022.159284}{10.1016/j.scitotenv.2022.159284}
+Lattuca, M.E., Vanella, F.A., Malanga, G., Rubel, M.D., Manríquez, P.H.,
+Torres, R., Alter, K., Marras, S., Peck, M.A., Domenici, P., and
+Fernández, D.A. 2023. Ocean acidification and seasonal temperature
+extremes combine to impair the thermal physiology of a sub-{Antarctic}
+fish. Science of The Total Environment \textbf{856}: 159284.
+doi:\href{https://doi.org/10.1016/j.scitotenv.2022.159284}{10.1016/j.scitotenv.2022.159284}.
 
@@
 Lin, Y., Moreno, C., Marchetti, A., Ducklow, H., Schofield, O., Delage,
-E., \ldots{} Cassar, N. (2021). Decline in plankton diversity and carbon
-flux with reduced sea ice extent along the {Western Antarctic
-Peninsula}. \emph{Nature Communications}, \emph{12}(1), 4948.
-doi:\href{https://doi.org/10.1038/s41467-021-25235-w}{10.1038/s41467-021-25235-w}
+E., Meredith, M., Li, Z., Eveillard, D., Chaffron, S., and Cassar, N.
+2021. Decline in plankton diversity and carbon flux with reduced sea ice
+extent along the {Western Antarctic Peninsula}. Nature Communications
+\textbf{12}(1): 4948. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41467-021-25235-w}{10.1038/s41467-021-25235-w}.
 
 \bibitem[\citeproctext]{ref-Llorca2012}
-Llorca, M., Farré, M., Tavano, M. S., Alonso, B., Koremblit, G., \&
-Barceló, D. (2012). Fate of a broad spectrum of perfluorinated compounds
+Llorca, M., Farré, M., Tavano, M.S., Alonso, B., Koremblit, G., and
+Barceló, D. 2012. Fate of a broad spectrum of perfluorinated compounds
 in soils and biota from {Tierra} del {Fuego} and {Antarctica}.
-\emph{Environmental Pollution}, \emph{163}, 158--166.
-doi:\href{https://doi.org/10.1016/j.envpol.2011.10.027}{10.1016/j.envpol.2011.10.027}
+Environmental Pollution \textbf{163}: 158--166.
+doi:\href{https://doi.org/10.1016/j.envpol.2011.10.027}{10.1016/j.envpol.2011.10.027}.
 
 \bibitem[\citeproctext]{ref-Lopez-Gappa2022}
-López-Gappa, J. (2022). The {Impact} of {Global Change} on {Marine
-Benthic Invertebrates}. In E. W. Helbling, M. A. Narvarte, R. A.
-González, \& V. E. Villafañe (Eds.), \emph{Global {Change} in {Atlantic
-Coastal Patagonian Ecosystems}: {A Journey Through Time}} (pp.
-177--204). {Cham}: {Springer International Publishing}.
-doi:\href{https://doi.org/10.1007/978-3-030-86676-1_8}{10.1007/978-3-030-86676-1\_8}
+López-Gappa, J. 2022. The {Impact} of {Global Change} on {Marine Benthic
+Invertebrates}. \emph{In} Global {Change} in {Atlantic Coastal
+Patagonian Ecosystems}: {A Journey Through Time}. \emph{Edited by} E.W.
+Helbling, M.A. Narvarte, R.A. González, and V.E. Villafañe. {Springer
+International Publishing}, {Cham}. pp. 177--204.
+doi:\href{https://doi.org/10.1007/978-3-030-86676-1_8}{10.1007/978-3-030-86676-1\_8}.
 
 \bibitem[\citeproctext]{ref-Lopez-Lopez2022}
-López-López, L., Genner, M. J., Tarling, G. A., Saunders, R. A., \&
-O'Gorman, E. J. (2022). Ecological {Networks} in the {Scotia Sea}:
-{Structural Changes Across Latitude} and {Depth}. \emph{Ecosystems},
-\emph{25}(2), 457--470.
-doi:\href{https://doi.org/10.1007/s10021-021-00665-1}{10.1007/s10021-021-00665-1}
+López-López, L., Genner, M.J., Tarling, G.A., Saunders, R.A., and
+O'Gorman, E.J. 2022. Ecological {Networks} in the {Scotia Sea}:
+{Structural Changes Across Latitude} and {Depth}. Ecosystems
+\textbf{25}(2): 457--470.
+doi:\href{https://doi.org/10.1007/s10021-021-00665-1}{10.1007/s10021-021-00665-1}.
 
 \bibitem[\citeproctext]{ref-Marina2018}
-Marina, T. I., Salinas, V., Cordone, G., Campana, G., Moreira, E.,
-Deregibus, D., \ldots{} Momo, F. R. (2018). The {Food Web} of {Potter
-Cove} ({Antarctica}): Complexity, structure and function.
-\emph{Estuarine, Coastal and Shelf Science}, \emph{200}, 141--151.
-doi:\href{https://doi.org/10.1016/j.ecss.2017.10.015}{10.1016/j.ecss.2017.10.015}
+Marina, T.I., Salinas, V., Cordone, G., Campana, G., Moreira, E.,
+Deregibus, D., Torre, L., Sahade, R., Tatián, M., Barrera Oro, E., De
+Troch, M., Doyle, S., Quartino, M.L., Saravia, L.A., and Momo, F.R.
+2018. The {Food Web} of {Potter Cove} ({Antarctica}): Complexity,
+structure and function. Estuarine, Coastal and Shelf Science
+\textbf{200}: 141--151.
+doi:\href{https://doi.org/10.1016/j.ecss.2017.10.015}{10.1016/j.ecss.2017.10.015}.
 
 \bibitem[\citeproctext]{ref-Marinainrev}
-Marina, T. I., Schloss, I. R., Lovrich, G. A., Boy, C. C., Bruno, D. O.,
-Capitanio, F. L., \ldots{} Riccialdelli, L. (in rev.). The complex
-network of trophic interactions in a {Subantarctic} oceanic {Marine
-Protected Area}. \emph{Marine Ecology Progress Series}.
+Marina, T.I., Schloss, I.R., Lovrich, G.A., Boy, C.C., Bruno, D.O.,
+Capitanio, F.L., Delpiani, S.M., Díaz de Astarloa, J.M., Fraysse, C.,
+García Alonso, V.A., Raya Rey, A., Schejter, L., Spinelli, M., Tatián,
+M., Urteaga, D., and Riccialdelli, L. in rev. The complex network of
+trophic interactions in a {Subantarctic} oceanic {Marine Protected
+Area}. Marine Ecology Progress Series.
 
 \bibitem[\citeproctext]{ref-Martinez2022}
-Martínez, P. A., Wöhler, O. C., Troccoli, G. H., Di Marco, E., \&
-Maydana, L. (2022). \emph{{Descripción de las capturas incidentales de
-granaderos presentes en los lances dirigidos a merluza negra en la
-pesquería argentina de arrastre: período 2010-2019.}} {Instituto
-Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.
+Martínez, P.A., Wöhler, O.C., Troccoli, G.H., Di Marco, E., and Maydana,
+L. 2022. {Descripción de las capturas incidentales de granaderos
+presentes en los lances dirigidos a merluza negra en la pesquería
+argentina de arrastre: período 2010-2019.} {Instituto Nacional de
+Investigación y Desarrollo Pesquero (INIDEP)}. {[}accessed 10 August
+2023{]}.
 
 \bibitem[\citeproctext]{ref-Matano2019}
-Matano, Ricardo P., Palma, E. D., \& Combes, V. (2019). The {Burdwood
-Bank Circulation}. \emph{Journal of Geophysical Research: Oceans},
-\emph{124}(10), 6904--6926.
-doi:\href{https://doi.org/10.1029/2019JC015001}{10.1029/2019JC015001}
+Matano, R.P., Palma, E.D., and Combes, V. 2019. The {Burdwood Bank
+Circulation}. Journal of Geophysical Research: Oceans \textbf{124}(10):
+6904--6926.
+doi:\href{https://doi.org/10.1029/2019JC015001}{10.1029/2019JC015001}.
 
 \bibitem[\citeproctext]{ref-Matano2010}
-Matano, R. P., Palma, E. D., \& Piola, A. R. (2010). The influence of
-the {Brazil} and {Malvinas Currents} on the {Southwestern Atlantic
-Shelf} circulation. \emph{Ocean Science}, \emph{6}(4), 983--995.
-doi:\href{https://doi.org/10.5194/os-6-983-2010}{10.5194/os-6-983-2010}
+Matano, R.P., Palma, E.D., and Piola, A.R. 2010. The influence of the
+{Brazil} and {Malvinas Currents} on the {Southwestern Atlantic Shelf}
+circulation. Ocean Science \textbf{6}(4): 983--995. {Copernicus GmbH}.
+doi:\href{https://doi.org/10.5194/os-6-983-2010}{10.5194/os-6-983-2010}.
 
 \bibitem[\citeproctext]{ref-Menge1995}
-Menge, B. A. (1995). Indirect {Effects} in {Marine Rocky Intertidal
-Interaction Webs}: {Patterns} and {Importance}. \emph{Ecological
-Monographs}, \emph{65}(1), 21--74.
-doi:\href{https://doi.org/10.2307/2937158}{10.2307/2937158}
+Menge, B.A. 1995. Indirect {Effects} in {Marine Rocky Intertidal
+Interaction Webs}: {Patterns} and {Importance}. Ecological Monographs
+\textbf{65}(1): 21--74.
+doi:\href{https://doi.org/10.2307/2937158}{10.2307/2937158}.
 
 \bibitem[\citeproctext]{ref-Meredith2018}
-Meredith, M. P., Falk, U., Bers, A. V., Mackensen, A., Schloss, I. R.,
-Ruiz Barlett, E., \ldots{} Abele, D. (2018). Anatomy of a glacial
-meltwater discharge event in an {Antarctic} cove. \emph{Philosophical
-Transactions of the Royal Society A: Mathematical, Physical and
-Engineering Sciences}, \emph{376}(2122), 20170163.
-doi:\href{https://doi.org/10.1098/rsta.2017.0163}{10.1098/rsta.2017.0163}
+Meredith, M.P., Falk, U., Bers, A.V., Mackensen, A., Schloss, I.R., Ruiz
+Barlett, E., Jerosch, K., Silva Busso, A., and Abele, D. 2018. Anatomy
+of a glacial meltwater discharge event in an {Antarctic} cove.
+Philosophical Transactions of the Royal Society A: Mathematical,
+Physical and Engineering Sciences \textbf{376}(2122): 20170163.
+doi:\href{https://doi.org/10.1098/rsta.2017.0163}{10.1098/rsta.2017.0163}.
 
 \bibitem[\citeproctext]{ref-Michel2019}
-Michel, L. N., Danis, B., Dubois, P., Eleaume, M., Fournier, J., Gallut,
-C., \ldots{} Lepoint, G. (2019). Increased sea ice cover alters food web
-structure in {East Antarctica}. \emph{Scientific Reports}, \emph{9}(1),
-8062.
-doi:\href{https://doi.org/10.1038/s41598-019-44605-5}{10.1038/s41598-019-44605-5}
+Michel, L.N., Danis, B., Dubois, P., Eleaume, M., Fournier, J., Gallut,
+C., Jane, P., and Lepoint, G. 2019. Increased sea ice cover alters food
+web structure in {East Antarctica}. Scientific Reports \textbf{9}(1):
+8062. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41598-019-44605-5}{10.1038/s41598-019-44605-5}.
 
 \bibitem[\citeproctext]{ref-Mintenbeck2012}
-Mintenbeck, K., Barrera-Oro, E. R., Brey, T., Jacob, U., Knust, R.,
-Mark, F. C., \ldots{} Arntz, W. E. (2012). Impact of {Climate Change} on
-{Fishes} in {Complex Antarctic Ecosystems}. In U. Jacob \& G. Woodward
-(Eds.), \emph{Advances in {Ecological Research}} (Vol. 46, pp.
-361--426). {Burlington}: {Academic Press}.
-doi:\href{https://doi.org/10.1016/B978-0-12-396992-7.00006-X}{10.1016/B978-0-12-396992-7.00006-X}
+Mintenbeck, K., Barrera-Oro, E.R., Brey, T., Jacob, U., Knust, R., Mark,
+F.C., Moreira, E., Strobel, A., and Arntz, W.E. 2012. Impact of {Climate
+Change} on {Fishes} in {Complex Antarctic Ecosystems}. \emph{In}
+Advances in {Ecological Research}. \emph{Edited by} U. Jacob and G.
+Woodward. {Academic Press}, {Burlington}. pp. 361--426.
+doi:\href{https://doi.org/10.1016/B978-0-12-396992-7.00006-X}{10.1016/B978-0-12-396992-7.00006-X}.
 
 \bibitem[\citeproctext]{ref-Montoya2009}
-Montoya, JoséM., Woodward, G., Emmerson, M. C., \& Solé, R. V. (2009).
-Press perturbations and indirect effects in real food webs.
-\emph{Ecology}, \emph{90}(9), 2426--2433.
-doi:\href{https://doi.org/10.1890/08-0657.1}{10.1890/08-0657.1}
+Montoya, JoséM., Woodward, G., Emmerson, M.C., and Solé, R.V. 2009.
+Press perturbations and indirect effects in real food webs. Ecology
+\textbf{90}(9): 2426--2433.
+doi:\href{https://doi.org/10.1890/08-0657.1}{10.1890/08-0657.1}.
 
 \bibitem[\citeproctext]{ref-Murphy2007}
-Murphy, E. J., Trathan, P. N., Watkins, J. L., Reid, K., Meredith, M.
-P., Forcada, J., \ldots{} Rothery, P. (2007). Climatically driven
-fluctuations in {Southern Ocean} ecosystems. \emph{Proceedings of the
-Royal Society B: Biological Sciences}, \emph{274}(1629), 3057--3067.
-doi:\href{https://doi.org/10.1098/rspb.2007.1180}{10.1098/rspb.2007.1180}
+Murphy, E.J., Trathan, P.N., Watkins, J.L., Reid, K., Meredith, M.P.,
+Forcada, J., Thorpe, S.E., Johnston, N.M., and Rothery, P. 2007.
+Climatically driven fluctuations in {Southern Ocean} ecosystems.
+Proceedings of the Royal Society B: Biological Sciences
+\textbf{274}(1629): 3057--3067. {Royal Society}.
+doi:\href{https://doi.org/10.1098/rspb.2007.1180}{10.1098/rspb.2007.1180}.
 
 \bibitem[\citeproctext]{ref-Murphy2006}
-Murphy, E. j., Watkins, J. l., Trathan, P. n., Reid, K., Meredith, M.
-p., Thorpe, S. e., \ldots{} Fleming, A. h. (2006). Spatial and temporal
-operation of the {Scotia Sea} ecosystem: A review of large-scale links
-in a krill centred food web. \emph{Philosophical Transactions of the
-Royal Society B: Biological Sciences}, \emph{362}(1477), 113--148.
-doi:\href{https://doi.org/10.1098/rstb.2006.1957}{10.1098/rstb.2006.1957}
+Murphy, E.j., Watkins, J.l., Trathan, P.n., Reid, K., Meredith, M.p.,
+Thorpe, S.e., Johnston, N.m., Clarke, A., Tarling, G.a., Collins, M.a.,
+Forcada, J., Shreeve, R.s., Atkinson, A., Korb, R., Whitehouse, M.j.,
+Ward, P., Rodhouse, P.g., Enderlein, P., Hirst, A.g., Martin, A.r.,
+Hill, S.l., Staniland, I.j., Pond, D.w., Briggs, D.r., Cunningham, N.j.,
+and Fleming, A.h. 2006. Spatial and temporal operation of the {Scotia
+Sea} ecosystem: A review of large-scale links in a krill centred food
+web. Philosophical Transactions of the Royal Society B: Biological
+Sciences \textbf{362}(1477): 113--148. {Royal Society}.
+doi:\href{https://doi.org/10.1098/rstb.2006.1957}{10.1098/rstb.2006.1957}.
 
 \bibitem[\citeproctext]{ref-Nardi2019}
-Nardi, C. F., Fernández, D. A., Vanella, F. A., \& Chalde, T. (2019).
-The expansion of exotic {Chinook} salmon ({Oncorhynchus} tshawytscha) in
-the extreme south of {Patagonia}: An environmental {DNA} approach.
-\emph{Biological Invasions}, \emph{21}(4), 1415--1425.
-doi:\href{https://doi.org/10.1007/s10530-018-1908-8}{10.1007/s10530-018-1908-8}
+Nardi, C.F., Fernández, D.A., Vanella, F.A., and Chalde, T. 2019. The
+expansion of exotic {Chinook} salmon ({Oncorhynchus} tshawytscha) in the
+extreme south of {Patagonia}: An environmental {DNA} approach.
+Biological Invasions \textbf{21}(4): 1415--1425.
+doi:\href{https://doi.org/10.1007/s10530-018-1908-8}{10.1007/s10530-018-1908-8}.
 
 \bibitem[\citeproctext]{ref-Nilsson2016}
-Nilsson, K. A., \& McCann, K. S. (2016). Interaction strength
+Nilsson, K.A., and McCann, K.S. 2016. Interaction strength
 revisited\textemdash clarifying the role of energy flux for food web
-stability. \emph{Theoretical Ecology}, \emph{9}(1), 59--71.
-doi:\href{https://doi.org/10.1007/s12080-015-0282-8}{10.1007/s12080-015-0282-8}
+stability. Theoretical Ecology \textbf{9}(1): 59--71.
+doi:\href{https://doi.org/10.1007/s12080-015-0282-8}{10.1007/s12080-015-0282-8}.
 
 \bibitem[\citeproctext]{ref-Nowacek2015}
-Nowacek, D. P., Clark, C. W., Mann, D., Miller, P. J., Rosenbaum, H. C.,
-Golden, J. S., \ldots{} Southall, B. L. (2015). Marine seismic surveys
-and ocean noise: Time for coordinated and prudent planning.
-\emph{Frontiers in Ecology and the Environment}, \emph{13}(7), 378--386.
-doi:\href{https://doi.org/10.1890/130286}{10.1890/130286}
+Nowacek, D.P., Clark, C.W., Mann, D., Miller, P.J., Rosenbaum, H.C.,
+Golden, J.S., Jasny, M., Kraska, J., and Southall, B.L. 2015. Marine
+seismic surveys and ocean noise: Time for coordinated and prudent
+planning. Frontiers in Ecology and the Environment \textbf{13}(7):
+378--386. doi:\href{https://doi.org/10.1890/130286}{10.1890/130286}.
 
 \bibitem[\citeproctext]{ref-OGorman2012}
-O'Gorman, E. J., Fitch, J. E., \& Crowe, T. P. (2012). Multiple
+O'Gorman, E.J., Fitch, J.E., and Crowe, T.P. 2012. Multiple
 anthropogenic stressors and the structural properties of food webs.
-\emph{Ecology}, \emph{93}(3), 441--448.
-doi:\href{https://doi.org/10.1890/11-0982.1}{10.1890/11-0982.1}
+Ecology \textbf{93}(3): 441--448.
+doi:\href{https://doi.org/10.1890/11-0982.1}{10.1890/11-0982.1}.
 
 \bibitem[\citeproctext]{ref-OGorman2019}
-O'Gorman, E. J., Petchey, O. L., Faulkner, K. J., Gallo, B., Gordon, T.
-A. C., Neto-Cerejeira, J., \ldots{} Woodward, G. (2019). A simple model
-predicts how warming simplifies wild food webs. \emph{Nature Climate
-Change}, \emph{9}(8), 611--616.
-doi:\href{https://doi.org/10.1038/s41558-019-0513-x}{10.1038/s41558-019-0513-x}
+O'Gorman, E.J., Petchey, O.L., Faulkner, K.J., Gallo, B., Gordon,
+T.A.C., Neto-Cerejeira, J., Ólafsson, J.S., Pichler, D.E., Thompson,
+M.S.A., and Woodward, G. 2019. A simple model predicts how warming
+simplifies wild food webs. Nature Climate Change \textbf{9}(8):
+611--616. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41558-019-0513-x}{10.1038/s41558-019-0513-x}.
 
 \bibitem[\citeproctext]{ref-Ojeda2021}
-Ojeda, M., Cossi, P. F., Rimondino, G. N., Chiesa, I. L., Boy, C. C., \&
-Pérez, A. F. (2021). Microplastics pollution in the intertidal limpet,
-{Nacella} magellanica, from {Beagle Channel} ({Argentina}).
-\emph{Science of The Total Environment}, \emph{795}, 148866.
-doi:\href{https://doi.org/10.1016/j.scitotenv.2021.148866}{10.1016/j.scitotenv.2021.148866}
+Ojeda, M., Cossi, P.F., Rimondino, G.N., Chiesa, I.L., Boy, C.C., and
+Pérez, A.F. 2021. Microplastics pollution in the intertidal limpet,
+{Nacella} magellanica, from {Beagle Channel} ({Argentina}). Science of
+The Total Environment \textbf{795}: 148866.
+doi:\href{https://doi.org/10.1016/j.scitotenv.2021.148866}{10.1016/j.scitotenv.2021.148866}.
 
 \bibitem[\citeproctext]{ref-Oliver2018}
-Oliver, E. C. J., Donat, M. G., Burrows, M. T., Moore, P. J., Smale, D.
-A., Alexander, L. V., \ldots{} Wernberg, T. (2018). Longer and more
-frequent marine heatwaves over the past century. \emph{Nature
-Communications}, \emph{9}(1), 1324.
-doi:\href{https://doi.org/10.1038/s41467-018-03732-9}{10.1038/s41467-018-03732-9}
+Oliver, E.C.J., Donat, M.G., Burrows, M.T., Moore, P.J., Smale, D.A.,
+Alexander, L.V., Benthuysen, J.A., Feng, M., Sen Gupta, A., Hobday,
+A.J., Holbrook, N.J., Perkins-Kirkpatrick, S.E., Scannell, H.A., Straub,
+S.C., and Wernberg, T. 2018. Longer and more frequent marine heatwaves
+over the past century. Nature Communications \textbf{9}(1): 1324.
+{Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41467-018-03732-9}{10.1038/s41467-018-03732-9}.
 
@@
 Olivier, P., Frelat, R., Bonsdorff, E., Kortsch, S., Kröncke, I.,
-Möllmann, C., \ldots{} Nordström, M. C. (2019). Exploring the temporal
-variability of a food web using long-term biomonitoring data.
-\emph{Ecography}, \emph{42}(12), 2107--2121.
-doi:\href{https://doi.org/10.1111/ecog.04461}{10.1111/ecog.04461}
+Möllmann, C., Neumann, H., Sell, A.F., and Nordström, M.C. 2019.
+Exploring the temporal variability of a food web using long-term
+biomonitoring data. Ecography \textbf{42}(12): 2107--2121.
+doi:\href{https://doi.org/10.1111/ecog.04461}{10.1111/ecog.04461}.
 
 \bibitem[\citeproctext]{ref-Orgeira2021}
-Orgeira, J. L., Alvarez, F., \& Salvó, C. S. (2021). The same pathway to
+Orgeira, J.L., Alvarez, F., and Salvó, C.S. 2021. The same pathway to
 the {Weddell Sea} birdlife, after 65 years: Similarities in the species
-composition, richness and abundances. \emph{Czech Polar Reports},
-\emph{11}(2), 291--304.
-doi:\href{https://doi.org/10.5817/CPR2021-2-20}{10.5817/CPR2021-2-20}
+composition, richness and abundances. Czech Polar Reports
+\textbf{11}(2): 291--304.
+doi:\href{https://doi.org/10.5817/CPR2021-2-20}{10.5817/CPR2021-2-20}.
 
 \bibitem[\citeproctext]{ref-Orr2020}
-Orr, J. A., Vinebrooke, R. D., Jackson, M. C., Kroeker, K. J., Kordas,
-R. L., Mantyka-Pringle, C., \ldots{} Piggott, J. J. (2020). Towards a
-unified study of multiple stressors: Divisions and common goals across
-research disciplines. \emph{Proceedings of the Royal Society B:
-Biological Sciences}, \emph{287}(1926), 20200421.
-doi:\href{https://doi.org/10.1098/rspb.2020.0421}{10.1098/rspb.2020.0421}
+Orr, J.A., Vinebrooke, R.D., Jackson, M.C., Kroeker, K.J., Kordas, R.L.,
+Mantyka-Pringle, C., Van den Brink, P.J., De Laender, F., Stoks, R.,
+Holmstrup, M., Matthaei, C.D., Monk, W.A., Penk, M.R., Leuzinger, S.,
+Schäfer, R.B., and Piggott, J.J. 2020. Towards a unified study of
+multiple stressors: Divisions and common goals across research
+disciplines. Proceedings of the Royal Society B: Biological Sciences
+\textbf{287}(1926): 20200421. {Royal Society}.
+doi:\href{https://doi.org/10.1098/rspb.2020.0421}{10.1098/rspb.2020.0421}.
 
 \bibitem[\citeproctext]{ref-Paine1996}
-Paine, R. T., Ruesink, J. L., Sun, A., Soulanille, E. L., Wonham, M. J.,
-Harley, C. D. G., \ldots{} Secord, D. L. (1996). {TROUBLE ON OILED
-WATERS}: {Lessons} from the {\emph{Exxon Valdez}} {Oil Spill}.
-\emph{Annual Review of Ecology and Systematics}, \emph{27}(1), 197--235.
-doi:\href{https://doi.org/10.1146/annurev.ecolsys.27.1.197}{10.1146/annurev.ecolsys.27.1.197}
+Paine, R.T., Ruesink, J.L., Sun, A., Soulanille, E.L., Wonham, M.J.,
+Harley, C.D.G., Brumbaugh, D.R., and Secord, D.L. 1996. {TROUBLE ON
+OILED WATERS}: {Lessons} from the {\emph{Exxon Valdez}} {Oil Spill}.
+Annual Review of Ecology and Systematics \textbf{27}(1): 197--235.
+doi:\href{https://doi.org/10.1146/annurev.ecolsys.27.1.197}{10.1146/annurev.ecolsys.27.1.197}.
 
 \bibitem[\citeproctext]{ref-Pallin2023}
-Pallin, L. J., Kellar, N. M., Steel, D., Botero-Acosta, N., Baker, C.
-S., Conroy, J. A., \ldots{} Friedlaender, A. S. (2023). A surplus no
-more? {Variation} in krill availability impacts reproductive rates of
-{Antarctic} baleen whales. \emph{Global Change Biology}, \emph{29}(8),
+Pallin, L.J., Kellar, N.M., Steel, D., Botero-Acosta, N., Baker, C.S.,
+Conroy, J.A., Costa, D.P., Johnson, C.M., Johnston, D.W., Nichols, R.C.,
+Nowacek, D.P., Read, A.J., Savenko, O., Schofield, O.M., Stammerjohn,
+S.E., Steinberg, D.K., and Friedlaender, A.S. 2023. A surplus no more?
+{Variation} in krill availability impacts reproductive rates of
+{Antarctic} baleen whales. Global Change Biology \textbf{29}(8):
 2108--2121.
-doi:\href{https://doi.org/10.1111/gcb.16559}{10.1111/gcb.16559}
+doi:\href{https://doi.org/10.1111/gcb.16559}{10.1111/gcb.16559}.
 
 \bibitem[\citeproctext]{ref-Pante2023}
-Pante, E., Simon-Bouhet, B., \& Irisson, J. (2023). Marmap: {Import},
+Pante, E., Simon-Bouhet, B., and Irisson, J. 2023. Marmap: {Import},
 {Plot} and {Analyze Bathymetric} and {Topographic Data}.
@@
 \bibitem[\citeproctext]{ref-Pasotti2015}
-Pasotti, F., Saravia, L. A., Troch, M. D., Tarantelli, M. S., Sahade,
-R., \& Vanreusel, A. (2015). Benthic {Trophic Interactions} in an
-{Antarctic Shallow Water Ecosystem Affected} by {Recent Glacier
-Retreat}. \emph{PLOS ONE}, \emph{10}(11), e0141742.
-doi:\href{https://doi.org/10.1371/journal.pone.0141742}{10.1371/journal.pone.0141742}
+Pasotti, F., Saravia, L.A., Troch, M.D., Tarantelli, M.S., Sahade, R.,
+and Vanreusel, A. 2015. Benthic {Trophic Interactions} in an {Antarctic
+Shallow Water Ecosystem Affected} by {Recent Glacier Retreat}. PLOS ONE
+\textbf{10}(11): e0141742.
+doi:\href{https://doi.org/10.1371/journal.pone.0141742}{10.1371/journal.pone.0141742}.
 
 \bibitem[\citeproctext]{ref-Pasti2021}
-Pasti, A. T., Bovcon, N. D., Ruibal-Núñez, J., Navoa, X., Jacobi, K. J.,
-\& Galván, D. E. (2021). The diet of {Mustelus} schmitti in areas with
-and without commercial bottom trawling ({Central Patagonia},
-{Southwestern Atlantic}): {Is} it evidence of trophic interaction with
-the {Patagonian} shrimp fishery? \emph{Food Webs}, \emph{29}, e00214.
-doi:\href{https://doi.org/10.1016/j.fooweb.2021.e00214}{10.1016/j.fooweb.2021.e00214}
+Pasti, A.T., Bovcon, N.D., Ruibal-Núñez, J., Navoa, X., Jacobi, K.J.,
+and Galván, D.E. 2021. The diet of {Mustelus} schmitti in areas with and
+without commercial bottom trawling ({Central Patagonia}, {Southwestern
+Atlantic}): {Is} it evidence of trophic interaction with the
+{Patagonian} shrimp fishery? Food Webs \textbf{29}: e00214.
+doi:\href{https://doi.org/10.1016/j.fooweb.2021.e00214}{10.1016/j.fooweb.2021.e00214}.
 
 \bibitem[\citeproctext]{ref-Pauli2021}
-Pauli, N.-C., Flintrop, C. M., Konrad, C., Pakhomov, E. A., Swoboda, S.,
-Koch, F., \ldots{} Iversen, M. H. (2021). Krill and salp faecal pellets
+Pauli, N.-C., Flintrop, C.M., Konrad, C., Pakhomov, E.A., Swoboda, S.,
+Koch, F., Wang, X.-L., Zhang, J.-C., Brierley, A.S., Bernasconi, M.,
+Meyer, B., and Iversen, M.H. 2021. Krill and salp faecal pellets
 contribute equally to the carbon flux at the {Antarctic Peninsula}.
-\emph{Nature Communications}, \emph{12}(1), 7168.
-doi:\href{https://doi.org/10.1038/s41467-021-27436-9}{10.1038/s41467-021-27436-9}
+Nature Communications \textbf{12}(1): 7168. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41467-021-27436-9}{10.1038/s41467-021-27436-9}.
 
 \bibitem[\citeproctext]{ref-Pecuchet2022}
-Pecuchet, L., Jørgensen, L. L., Dolgov, A. V., Eriksen, E., Husson, B.,
-Skern-Mauritzen, M., \& Primicerio, R. (2022). Spatio-temporal turnover
+Pecuchet, L., Jørgensen, L.L., Dolgov, A.V., Eriksen, E., Husson, B.,
+Skern-Mauritzen, M., and Primicerio, R. 2022. Spatio-temporal turnover
 and drivers of bentho-demersal community and food web structure in a
-high-latitude marine ecosystem. \emph{Diversity and Distributions},
-\emph{28}(12), 2503--2520.
-doi:\href{https://doi.org/10.1111/ddi.13580}{10.1111/ddi.13580}
+high-latitude marine ecosystem. Diversity and Distributions
+\textbf{28}(12): 2503--2520.
+doi:\href{https://doi.org/10.1111/ddi.13580}{10.1111/ddi.13580}.
 
@@
 Pecuchet, L., Lindegren, M., Kortsch, S., Całkiewicz, J., Jurgensone,
-I., Margonski, P., \ldots{} Nordström, M. C. (2020). Spatio-temporal
-dynamics of multi-trophic communities reveal ecosystem-wide functional
-reorganization. \emph{Ecography}, \emph{43}(2), 197--208.
-doi:\href{https://doi.org/10.1111/ecog.04643}{10.1111/ecog.04643}
+I., Margonski, P., Otto, S.A., Putnis, I., Strāķe, S., and Nordström,
+M.C. 2020. Spatio-temporal dynamics of multi-trophic communities reveal
+ecosystem-wide functional reorganization. Ecography \textbf{43}(2):
+197--208.
+doi:\href{https://doi.org/10.1111/ecog.04643}{10.1111/ecog.04643}.
 
 \bibitem[\citeproctext]{ref-Perez2020}
-Pérez, A. F., Ojeda, M., Rimondino, G. N., Chiesa, I. L., Di Mauro, R.,
-Boy, C. C., \& Calcagno, J. A. (2020). First report of microplastics
+Pérez, A.F., Ojeda, M., Rimondino, G.N., Chiesa, I.L., Di Mauro, R.,
+Boy, C.C., and Calcagno, J.A. 2020. First report of microplastics
 presence in the mussel {Mytilus} chilensis from {Ushuaia Bay} ({Beagle
-Channel}, {Tierra} del {Fuego}, {Argentina}). \emph{Marine Pollution
-Bulletin}, \emph{161}, 111753.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2020.111753}{10.1016/j.marpolbul.2020.111753}
+Channel}, {Tierra} del {Fuego}, {Argentina}). Marine Pollution Bulletin
+\textbf{161}: 111753.
+doi:\href{https://doi.org/10.1016/j.marpolbul.2020.111753}{10.1016/j.marpolbul.2020.111753}.
 
 \bibitem[\citeproctext]{ref-Perry2020}
-Perry, F. A., Kawaguchi, S., Atkinson, A., Sailley, S. F., Tarling, G.
-A., Mayor, D. J., \ldots{} Cooper, A. (2020).
+Perry, F.A., Kawaguchi, S., Atkinson, A., Sailley, S.F., Tarling, G.A.,
+Mayor, D.J., Lucas, C.H., King, R., and Cooper, A. 2020.
 Temperature\textendash{{Induced Hatch Failure}} and {Nauplii
-Malformation} in {Antarctic Krill}. \emph{Frontiers in Marine Science},
-\emph{7}.
+Malformation} in {Antarctic Krill}. Frontiers in Marine Science
+\textbf{7}. {[}accessed 11 August 2023{]}.
 
 \bibitem[\citeproctext]{ref-Peterson2001}
-Peterson, C. H. (2001). The {`{Exxon Valdez}'} oil spill in {Alaska}:
-{Acute}, indirect and chronic effects on the ecosystem. In
-\emph{Advances in {Marine Biology}} (Vol. 39, pp. 1--103). {Academic
-Press}.
-doi:\href{https://doi.org/10.1016/S0065-2881(01)39008-9}{10.1016/S0065-2881(01)39008-9}
+Peterson, C.H. 2001. The {``{Exxon Valdez}''} oil spill in {Alaska}:
+{Acute}, indirect and chronic effects on the ecosystem. \emph{In}
+Advances in {Marine Biology}. {Academic Press}. pp. 1--103.
+doi:\href{https://doi.org/10.1016/S0065-2881(01)39008-9}{10.1016/S0065-2881(01)39008-9}.
 
 \bibitem[\citeproctext]{ref-Pineda-Metz2020}
-Pineda-Metz, S. E. A., Gerdes, D., \& Richter, C. (2020). Benthic fauna
-declined on a whitening {Antarctic} continental shelf. \emph{Nature
-Communications}, \emph{11}(1), 2226.
-doi:\href{https://doi.org/10.1038/s41467-020-16093-z}{10.1038/s41467-020-16093-z}
+Pineda-Metz, S.E.A., Gerdes, D., and Richter, C. 2020. Benthic fauna
+declined on a whitening {Antarctic} continental shelf. Nature
+Communications \textbf{11}(1): 2226. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/s41467-020-16093-z}{10.1038/s41467-020-16093-z}.
 
 \bibitem[\citeproctext]{ref-Pinkerton2021}
-Pinkerton, M. H., Boyd, P. W., Deppeler, S., Hayward, A., Höfer, J., \&
-Moreau, S. (2021). Evidence for the {Impact} of {Climate Change} on
-{Primary Producers} in the {Southern Ocean}. \emph{Frontiers in Ecology
-and Evolution}, \emph{9}.
+Pinkerton, M.H., Boyd, P.W., Deppeler, S., Hayward, A., Höfer, J., and
+Moreau, S. 2021. Evidence for the {Impact} of {Climate Change} on
+{Primary Producers} in the {Southern Ocean}. Frontiers in Ecology and
+Evolution \textbf{9}. {[}accessed 11 September 2023{]}.
 
 \bibitem[\citeproctext]{ref-Poloczanska2013}
-Poloczanska, E. S., Brown, C. J., Sydeman, W. J., Kiessling, W.,
-Schoeman, D. S., Moore, P. J., \ldots{} Richardson, A. J. (2013). Global
-imprint of climate change on marine life. \emph{Nature Climate Change},
-\emph{3}(10), 919--925.
-doi:\href{https://doi.org/10.1038/nclimate1958}{10.1038/nclimate1958}
+Poloczanska, E.S., Brown, C.J., Sydeman, W.J., Kiessling, W., Schoeman,
+D.S., Moore, P.J., Brander, K., Bruno, J.F., Buckley, L.B., Burrows,
+M.T., Duarte, C.M., Halpern, B.S., Holding, J., Kappel, C.V., O'Connor,
+M.I., Pandolfi, J.M., Parmesan, C., Schwing, F., Thompson, S.A., and
+Richardson, A.J. 2013. Global imprint of climate change on marine life.
+Nature Climate Change \textbf{3}(10): 919--925. {Nature Publishing
+Group}.
+doi:\href{https://doi.org/10.1038/nclimate1958}{10.1038/nclimate1958}.
 
 \bibitem[\citeproctext]{ref-Quartino2008}
-Quartino, M. L., \& Boraso de Zaixso, A. L. (2008). Summer macroalgal
+Quartino, M.L., and Boraso de Zaixso, A.L. 2008. Summer macroalgal
 biomass in {Potter Cove}, {South Shetland Islands}, {Antarctica}: Its
-production and flux to the ecosystem. \emph{Polar Biology},
-\emph{31}(3), 281--294.
-doi:\href{https://doi.org/10.1007/s00300-007-0356-1}{10.1007/s00300-007-0356-1}
+production and flux to the ecosystem. Polar Biology \textbf{31}(3):
+281--294.
+doi:\href{https://doi.org/10.1007/s00300-007-0356-1}{10.1007/s00300-007-0356-1}.
 
 \bibitem[\citeproctext]{ref-Quartino2013}
-Quartino, María Liliana, Deregibus, D., Campana, G. L., Latorre, G. E.
-J., \& Momo, F. R. (2013). Evidence of {Macroalgal Colonization} on
-{Newly Ice-Free Areas} following {Glacial Retreat} in {Potter Cove}
-({South Shetland Islands}), {Antarctica}. \emph{PLoS ONE}, \emph{8}(3),
-e58223.
-doi:\href{https://doi.org/10.1371/journal.pone.0058223}{10.1371/journal.pone.0058223}
+Quartino, M.L., Deregibus, D., Campana, G.L., Latorre, G.E.J., and Momo,
+F.R. 2013. Evidence of {Macroalgal Colonization} on {Newly Ice-Free
+Areas} following {Glacial Retreat} in {Potter Cove} ({South Shetland
+Islands}), {Antarctica}. PLoS ONE \textbf{8}(3): e58223.
+doi:\href{https://doi.org/10.1371/journal.pone.0058223}{10.1371/journal.pone.0058223}.
 
 \bibitem[\citeproctext]{ref-Raymond2011}
-Raymond, B. (2011). \emph{A circumpolar pelagic regionalisation of the
-{Southern Ocean}. {CCAMLR WS-MPA}, {Brest}, {France}, 29
-{Aug}\textendash 2 {Sep} 2011. {Document WS-MPA-11}/6.
-{http://data.aad.gov.au/regionalisation}}.
+Raymond, B. 2011. A circumpolar pelagic regionalisation of the {Southern
+Ocean}. {CCAMLR WS-MPA}, {Brest}, {France}, 29 {Aug}\textendash 2 {Sep}
+2011. {Document WS-MPA-11}/6. {http://data.aad.gov.au/regionalisation}.
 
 \bibitem[\citeproctext]{ref-Riccialdelli2020}
-Riccialdelli, L., Becker, Y. A., Fioramonti, N. E., Torres, M., Bruno,
-D. O., Rey, A. R., \& Fernández, D. A. (2020). Trophic structure of
-southern marine ecosystems: A comparative isotopic analysis from the
-{Beagle Channel} to the oceanic {Burdwood Bank} area under a wasp-waist
-assumption. \emph{Marine Ecology Progress Series}, \emph{655}, 1--27.
-doi:\href{https://doi.org/10.3354/meps13524}{10.3354/meps13524}
+Riccialdelli, L., Becker, Y.A., Fioramonti, N.E., Torres, M., Bruno,
+D.O., Rey, A.R., and Fernández, D.A. 2020. Trophic structure of southern
+marine ecosystems: A comparative isotopic analysis from the {Beagle
+Channel} to the oceanic {Burdwood Bank} area under a wasp-waist
+assumption. Marine Ecology Progress Series \textbf{655}: 1--27.
+doi:\href{https://doi.org/10.3354/meps13524}{10.3354/meps13524}.
 
 \bibitem[\citeproctext]{ref-Riccialdelli2013}
-Riccialdelli, L., Newsome, S. D., Dellabianca, N. A., Bastida, R.,
-Fogel, M. L., \& Goodall, R. N. P. (2013). Ontogenetic diet shift in
-{Commerson}'s dolphin ({Cephalorhynchus} commersonii commersonii) off
-{Tierra} del {Fuego}. \emph{Polar Biology}, \emph{36}(5), 617--627.
-doi:\href{https://doi.org/10.1007/s00300-013-1289-5}{10.1007/s00300-013-1289-5}
+Riccialdelli, L., Newsome, S.D., Dellabianca, N.A., Bastida, R., Fogel,
+M.L., and Goodall, R.N.P. 2013. Ontogenetic diet shift in {Commerson}'s
+dolphin ({Cephalorhynchus} commersonii commersonii) off {Tierra} del
+{Fuego}. Polar Biology \textbf{36}(5): 617--627.
+doi:\href{https://doi.org/10.1007/s00300-013-1289-5}{10.1007/s00300-013-1289-5}.
 
 \bibitem[\citeproctext]{ref-Rincon-Diaz2021}
-Rincón-Díaz, M. P., Bovcon, N. D., Cochia, P. D., Góngora, M. E., \&
-Galván, D. E. (2021). Fish functional diversity as an indicator of
-resilience to industrial fishing in {Patagonia Argentina}. \emph{Journal
-of Fish Biology}, \emph{99}(5), 1650--1667.
-doi:\href{https://doi.org/10.1111/jfb.14873}{10.1111/jfb.14873}
+Rincón-Díaz, M.P., Bovcon, N.D., Cochia, P.D., Góngora, M.E., and
+Galván, D.E. 2021. Fish functional diversity as an indicator of
+resilience to industrial fishing in {Patagonia Argentina}. Journal of
+Fish Biology \textbf{99}(5): 1650--1667.
+doi:\href{https://doi.org/10.1111/jfb.14873}{10.1111/jfb.14873}.
 
 \bibitem[\citeproctext]{ref-Rodriguez2022}
-Rodriguez, I. D., Marina, T. I., Schloss, I. R., \& Saravia, L. A.
-(2022). Marine food webs are more complex but less stable in
-sub-{Antarctic} ({Beagle Channel}, {Argentina}) than in {Antarctic}
-({Potter Cove}, {Antarctic Peninsula}) regions. \emph{Marine
-Environmental Research}, \emph{174}, 105561.
-doi:\href{https://doi.org/10.1016/j.marenvres.2022.105561}{10.1016/j.marenvres.2022.105561}
+Rodriguez, I.D., Marina, T.I., Schloss, I.R., and Saravia, L.A. 2022.
+Marine food webs are more complex but less stable in sub-{Antarctic}
+({Beagle Channel}, {Argentina}) than in {Antarctic} ({Potter Cove},
+{Antarctic Peninsula}) regions. Marine Environmental Research
+\textbf{174}: 105561.
+doi:\href{https://doi.org/10.1016/j.marenvres.2022.105561}{10.1016/j.marenvres.2022.105561}.
 
@@
 Rowlands, E., Galloway, T., Cole, M., Lewis, C., Peck, V., Thorpe, S.,
-\& Manno, C. (2021). The {Effects} of {Combined Ocean Acidification} and
+and Manno, C. 2021. The {Effects} of {Combined Ocean Acidification} and
 {Nanoplastic Exposures} on the {Embryonic Development} of {Antarctic
-Krill}. \emph{Frontiers in Marine Science}, \emph{8}.
+Krill}. Frontiers in Marine Science \textbf{8}. {[}accessed 11 August
+2023{]}.
 
 \bibitem[\citeproctext]{ref-Ruckamp2011}
-Rückamp, M., Braun, M., Suckro, S., \& Blindow, N. (2011). Observed
+Rückamp, M., Braun, M., Suckro, S., and Blindow, N. 2011. Observed
 glacial changes on the {King George Island} ice cap, {Antarctica}, in
-the last decade. \emph{Global and Planetary Change}, \emph{79}(1-2),
-99--109.
-doi:\href{https://doi.org/10.1016/j.gloplacha.2011.06.009}{10.1016/j.gloplacha.2011.06.009}
+the last decade. Global and Planetary Change \textbf{79}(1-2): 99--109.
+doi:\href{https://doi.org/10.1016/j.gloplacha.2011.06.009}{10.1016/j.gloplacha.2011.06.009}.
 
 \bibitem[\citeproctext]{ref-RuibalNunez2020}
-Ruibal Nuñez, J. (2020). \emph{{Impacto ecológico de la actividad
-pesquera en las poblaciones de condrictios en el litoral de la Provincia
-de Chubut y Golfo San Jorge}} (PhD thesis). Universidad Nacional de Mar
-del Plata (UNMdP), {Argentina}.
+Ruibal Nuñez, J. 2020. {Impacto ecológico de la actividad pesquera en
+las poblaciones de condrictios en el litoral de la Provincia de Chubut y
+Golfo San Jorge}. PhD thesis, Universidad Nacional de Mar del Plata
+(UNMdP), {Argentina}.
 
@@
 Sahade, R., Lagger, C., Torre, L., Momo, F., Monien, P., Schloss, I.,
-\ldots{} Abele, D. (2015). Climate change and glacier retreat drive
-shifts in an {Antarctic} benthic ecosystem. \emph{Science Advances},
-\emph{1}(10), e1500050.
-doi:\href{https://doi.org/10.1126/sciadv.1500050}{10.1126/sciadv.1500050}
+Barnes, D.K.A., Servetto, N., Tarantelli, S., Tatián, M., Zamboni, N.,
+and Abele, D. 2015. Climate change and glacier retreat drive shifts in
+an {Antarctic} benthic ecosystem. Science Advances \textbf{1}(10):
+e1500050. {American Association for the Advancement of Science}.
+doi:\href{https://doi.org/10.1126/sciadv.1500050}{10.1126/sciadv.1500050}.
 
 \bibitem[\citeproctext]{ref-Saunders2019}
-Saunders, R. A., Hill, S. L., Tarling, G. A., \& Murphy, E. J. (2019).
+Saunders, R.A., Hill, S.L., Tarling, G.A., and Murphy, E.J. 2019.
 Myctophid {Fish} ({Family Myctophidae}) {Are Central Consumers} in the
-{Food Web} of the {Scotia Sea} ({Southern Ocean}). \emph{Frontiers in
-Marine Science}, \emph{6}.
+{Food Web} of the {Scotia Sea} ({Southern Ocean}). Frontiers in Marine
+Science \textbf{6}. {[}accessed 11 August 2023{]}.
 
 \bibitem[\citeproctext]{ref-Schejter2021}
-Schejter, L., \& Albano, M. (2021). Benthic communities at the marine
+Schejter, L., and Albano, M. 2021. Benthic communities at the marine
 protected area {Namuncurá}/{Burdwood} bank, {SW Atlantic Ocean}:
 Detection of vulnerable marine ecosystems and contributions to the
-assessment of the rezoning process. \emph{Polar Biology}, \emph{44}(10),
+assessment of the rezoning process. Polar Biology \textbf{44}(10):
 2023--2037.
-doi:\href{https://doi.org/10.1007/s00300-021-02936-y}{10.1007/s00300-021-02936-y}
+doi:\href{https://doi.org/10.1007/s00300-021-02936-y}{10.1007/s00300-021-02936-y}.
 
 \bibitem[\citeproctext]{ref-Schloss2012}
-Schloss, I. R., Abele, D., Moreau, S., Demers, S., Bers, A. V.,
-González, O., \& Ferreyra, G. A. (2012). Response of phytoplankton
-dynamics to 19-year (1991\textendash 2009) climate trends in {Potter
-Cove} ({Antarctica}). \emph{Journal of Marine Systems}, \emph{92}(1),
-53--66.
-doi:\href{https://doi.org/10.1016/j.jmarsys.2011.10.006}{10.1016/j.jmarsys.2011.10.006}
+Schloss, I.R., Abele, D., Moreau, S., Demers, S., Bers, A.V., González,
+O., and Ferreyra, G.A. 2012. Response of phytoplankton dynamics to
+19-year (1991\textendash 2009) climate trends in {Potter Cove}
+({Antarctica}). Journal of Marine Systems \textbf{92}(1): 53--66.
+doi:\href{https://doi.org/10.1016/j.jmarsys.2011.10.006}{10.1016/j.jmarsys.2011.10.006}.
 
 \bibitem[\citeproctext]{ref-Schloss2023}
-Schloss, I. R., Pizarro, G., Cadaillon, A. M., Giesecke, R., Hernando,
-M. P., Almandoz, G. O., \ldots{} Ruiz, C. (2023). Alexandrium catenella
-dynamics and paralytic shellfish toxins distribution along the {Beagle
-Channel} (southern {Patagonia}). \emph{Journal of Marine Systems},
-\emph{239}, 103856.
-doi:\href{https://doi.org/10.1016/j.jmarsys.2022.103856}{10.1016/j.jmarsys.2022.103856}
+Schloss, I.R., Pizarro, G., Cadaillon, A.M., Giesecke, R., Hernando,
+M.P., Almandoz, G.O., Latorre, M.P., Malits, A., Flores-Melo, X.,
+Saravia, L.A., Martín, J., Guzmán, L., Iachetti, C.M., and Ruiz, C.
+2023. Alexandrium catenella dynamics and paralytic shellfish toxins
+distribution along the {Beagle Channel} (southern {Patagonia}). Journal
+of Marine Systems \textbf{239}: 103856.
+doi:\href{https://doi.org/10.1016/j.jmarsys.2022.103856}{10.1016/j.jmarsys.2022.103856}.
 
 \bibitem[\citeproctext]{ref-Schmidt2011}
-Schmidt, K., Atkinson, A., Steigenberger, S., Fielding, S., Lindsay, M.
-C. M., Pond, D. W., \ldots{} Achterberg, E. P. (2011). Seabed foraging
-by {Antarctic} krill: {Implications} for stock assessment,
-bentho-pelagic coupling, and the vertical transfer of iron.
-\emph{Limnology and Oceanography}, \emph{56}(4), 1411--1428.
-doi:\href{https://doi.org/10.4319/lo.2011.56.4.1411}{10.4319/lo.2011.56.4.1411}
+Schmidt, K., Atkinson, A., Steigenberger, S., Fielding, S., Lindsay,
+M.C.M., Pond, D.W., Tarling, G.A., Klevjer, T.A., Allen, C.S., Nicol,
+S., and Achterberg, E.P. 2011. Seabed foraging by {Antarctic} krill:
+{Implications} for stock assessment, bentho-pelagic coupling, and the
+vertical transfer of iron. Limnology and Oceanography \textbf{56}(4):
+1411--1428.
+doi:\href{https://doi.org/10.4319/lo.2011.56.4.1411}{10.4319/lo.2011.56.4.1411}.
 
 \bibitem[\citeproctext]{ref-Seco2021}
-Seco, J., Aparício, S., Brierley, A. S., Bustamante, P., Ceia, F. R.,
-Coelho, J. P., \ldots{} Xavier, J. C. (2021). Mercury biomagnification
-in a {Southern Ocean} food web. \emph{Environmental Pollution},
-\emph{275}, 116620.
-doi:\href{https://doi.org/10.1016/j.envpol.2021.116620}{10.1016/j.envpol.2021.116620}
+Seco, J., Aparício, S., Brierley, A.S., Bustamante, P., Ceia, F.R.,
+Coelho, J.P., Philips, R.A., Saunders, R.A., Fielding, S., Gregory, S.,
+Matias, R., Pardal, M.A., Pereira, E., Stowasser, G., Tarling, G.A., and
+Xavier, J.C. 2021. Mercury biomagnification in a {Southern Ocean} food
+web. Environmental Pollution \textbf{275}: 116620.
+doi:\href{https://doi.org/10.1016/j.envpol.2021.116620}{10.1016/j.envpol.2021.116620}.
 
 \bibitem[\citeproctext]{ref-Sgarlatta2023}
-Sgarlatta, M. (2023). \emph{Mechanisms driving tropicalization of
-temperate reef fish assemblages} (Thesis). UNSW Sydney.
-doi:/\href{https://doi.org/10.26190/unsworks/25104}{10.26190/unsworks/25104}
+Sgarlatta, M. 2023. Mechanisms driving tropicalization of temperate reef
+fish assemblages. Thesis, UNSW Sydney.
+doi:\href{https://doi.org/10.26190/unsworks/25104}{10.26190/unsworks/25104}.
 
 \bibitem[\citeproctext]{ref-Smale2008}
-Smale, Dan A., \& Barnes, D. K. A. (2008). Likely responses of the
+Smale, D.A., and Barnes, D.K.A. 2008. Likely responses of the
 {Antarctic} benthos to climate-related changes in physical disturbance
 during the 21st century, based primarily on evidence from the {West
-Antarctic Peninsula} region. \emph{Ecography}, \emph{31}(3), 289--305.
-doi:\href{https://doi.org/10.1111/j.0906-7590.2008.05456.x}{10.1111/j.0906-7590.2008.05456.x}
+Antarctic Peninsula} region. Ecography \textbf{31}(3): 289--305.
+{Blackwell Publishing Ltd}.
+doi:\href{https://doi.org/10.1111/j.0906-7590.2008.05456.x}{10.1111/j.0906-7590.2008.05456.x}.
 
 \bibitem[\citeproctext]{ref-Smale2008a}
-Smale, Dan A., Brown, K. M., Barnes, D. K. A., Fraser, K. P. P., \&
-Clarke, A. (2008). Ice {Scour Disturbance} in {Antarctic Waters}.
-\emph{Science}, \emph{321}(5887), 371--371.
-doi:\href{https://doi.org/10.1126/science.1158647}{10.1126/science.1158647}
+Smale, D.A., Brown, K.M., Barnes, D.K.A., Fraser, K.P.P., and Clarke, A.
+2008. Ice {Scour Disturbance} in {Antarctic Waters}. Science
+\textbf{321}(5887): 371--371. {American Association for the Advancement
+of Science}.
+doi:\href{https://doi.org/10.1126/science.1158647}{10.1126/science.1158647}.
 
 \bibitem[\citeproctext]{ref-Soeffker2022}
-Soeffker, M., Hollyman, P. R., Collins, M. A., Hogg, O. T., Riley, A.,
-Laptikhovsky, V., \ldots{} Darby, C. (2022). Contrasting life-history
-traits of two toothfish ({Dissostichus} spp.) species at their range
-edge around the {South Sandwich Islands}. \emph{Deep Sea Research Part
-II: Topical Studies in Oceanography}, \emph{201}, 105098.
-doi:\href{https://doi.org/10.1016/j.dsr2.2022.105098}{10.1016/j.dsr2.2022.105098}
+Soeffker, M., Hollyman, P.R., Collins, M.A., Hogg, O.T., Riley, A.,
+Laptikhovsky, V., Earl, T., Roberts, J., MacLeod, E., Belchier, M., and
+Darby, C. 2022. Contrasting life-history traits of two toothfish
+({Dissostichus} spp.) species at their range edge around the {South
+Sandwich Islands}. Deep Sea Research Part II: Topical Studies in
+Oceanography \textbf{201}: 105098.
+doi:\href{https://doi.org/10.1016/j.dsr2.2022.105098}{10.1016/j.dsr2.2022.105098}.
 
 \bibitem[\citeproctext]{ref-Stouffer2011}
-Stouffer, D. B., \& Bascompte, J. (2011). Compartmentalization increases
-food-web persistence. \emph{Proceedings of the National Academy of
-Sciences}, \emph{108}(9), 3648--3652.
-doi:\href{https://doi.org/10.1073/pnas.1014353108}{10.1073/pnas.1014353108}
+Stouffer, D.B., and Bascompte, J. 2011. Compartmentalization increases
+food-web persistence. Proceedings of the National Academy of Sciences
+\textbf{108}(9): 3648--3652. {Proceedings of the National Academy of
+Sciences}.
+doi:\href{https://doi.org/10.1073/pnas.1014353108}{10.1073/pnas.1014353108}.
 
 \bibitem[\citeproctext]{ref-Tamini2023}
-Tamini, L. L., Dellacasa, R. F., Chavez, L. N., Marinao, C. J., Góngora,
-M. E., Crawford, R., \& Frere, E. (2023). Bird scaring lines reduce
-seabird mortality in mid-water and bottom trawlers in {Argentina}.
-\emph{ICES Journal of Marine Science}, fsad109.
-doi:\href{https://doi.org/10.1093/icesjms/fsad109}{10.1093/icesjms/fsad109}
+Tamini, L.L., Dellacasa, R.F., Chavez, L.N., Marinao, C.J., Góngora,
+M.E., Crawford, R., and Frere, E. 2023. Bird scaring lines reduce
+seabird mortality in mid-water and bottom trawlers in {Argentina}. ICES
+Journal of Marine Science: fsad109.
+doi:\href{https://doi.org/10.1093/icesjms/fsad109}{10.1093/icesjms/fsad109}.
 
 \bibitem[\citeproctext]{ref-Tarling2018}
-Tarling, G. A., Ward, P., \& Thorpe, S. E. (2018). Spatial distributions
-of {Southern Ocean} mesozooplankton communities have been resilient to
-long-term surface warming. \emph{Global Change Biology}, \emph{24}(1),
+Tarling, G.A., Ward, P., and Thorpe, S.E. 2018. Spatial distributions of
+{Southern Ocean} mesozooplankton communities have been resilient to
+long-term surface warming. Global Change Biology \textbf{24}(1):
 132--142.
-doi:\href{https://doi.org/10.1111/gcb.13834}{10.1111/gcb.13834}
+doi:\href{https://doi.org/10.1111/gcb.13834}{10.1111/gcb.13834}.
 
 \bibitem[\citeproctext]{ref-Teixido2002}
-Teixidó, N., Garrabou, J., \& Arntz, W. E. (2002). Spatial pattern
+Teixidó, N., Garrabou, J., and Arntz, W.E. 2002. Spatial pattern
 quantification of {Antarctic} benthic communities using landscape
-indices. \emph{Marine Ecology Progress Series}, \emph{242}, 1--14.
-doi:\href{https://doi.org/10.3354/meps242001}{10.3354/meps242001}
+indices. Marine Ecology Progress Series \textbf{242}: 1--14.
+doi:\href{https://doi.org/10.3354/meps242001}{10.3354/meps242001}.
 
 \bibitem[\citeproctext]{ref-Thompson2012}
-Thompson, R. M., Brose, U., Dunne, J. A., Hall, R. O., Hladyz, S.,
-Kitching, R. L., \ldots{} Tylianakis, J. M. (2012). Food webs:
-Reconciling the structure and function of biodiversity. \emph{Trends in
-Ecology \& Evolution}, \emph{27}(12), 689--697.
-doi:\href{https://doi.org/10.1016/j.tree.2012.08.005}{10.1016/j.tree.2012.08.005}
+Thompson, R.M., Brose, U., Dunne, J.A., Hall, R.O., Hladyz, S.,
+Kitching, R.L., Martinez, N.D., Rantala, H., Romanuk, T.N., Stouffer,
+D.B., and Tylianakis, J.M. 2012. Food webs: Reconciling the structure
+and function of biodiversity. Trends in Ecology \& Evolution
+\textbf{27}(12): 689--697. {Elsevier}.
+doi:\href{https://doi.org/10.1016/j.tree.2012.08.005}{10.1016/j.tree.2012.08.005}.
 
 \bibitem[\citeproctext]{ref-Thompson2007}
-Thompson, R. M., Hemberg, M., Starzomski, B. M., \& Shurin, J. B.
-(2007). Trophic {Levels} and {Trophic Tangles}: {The Prevalence} of
-{Omnivory} in {Real Food Webs}. \emph{Ecology}, \emph{88}(3), 612--617.
-doi:\href{https://doi.org/10.1890/05-1454}{10.1890/05-1454}
+Thompson, R.M., Hemberg, M., Starzomski, B.M., and Shurin, J.B. 2007.
+Trophic {Levels} and {Trophic Tangles}: {The Prevalence} of {Omnivory}
+in {Real Food Webs}. Ecology \textbf{88}(3): 612--617.
+doi:\href{https://doi.org/10.1890/05-1454}{10.1890/05-1454}.
 
 \bibitem[\citeproctext]{ref-Trathan2023}
-Trathan, Philip N. (2023). The future of the {South Georgia} and {South
+Trathan, P.N. 2023. The future of the {South Georgia} and {South
 Sandwich Islands} marine protected area in a changing environment: {The}
-choice between industrial fisheries, or ecosystem protection.
-\emph{Marine Policy}, \emph{155}, 105773.
-doi:\href{https://doi.org/10.1016/j.marpol.2023.105773}{10.1016/j.marpol.2023.105773}
+choice between industrial fisheries, or ecosystem protection. Marine
+Policy \textbf{155}: 105773.
+doi:\href{https://doi.org/10.1016/j.marpol.2023.105773}{10.1016/j.marpol.2023.105773}.
 
 \bibitem[\citeproctext]{ref-Trathan2021}
-Trathan, P. N., Fielding, S., Hollyman, P. R., Murphy, E. J.,
-Warwick-Evans, V., \& Collins, M. A. (2021). Enhancing the ecosystem
+Trathan, P.N., Fielding, S., Hollyman, P.R., Murphy, E.J.,
+Warwick-Evans, V., and Collins, M.A. 2021. Enhancing the ecosystem
 approach for the fishery for {Antarctic} krill within the complex,
-variable, and changing ecosystem at {South Georgia}. \emph{ICES Journal
-of Marine Science}, \emph{78}(6), 2065--2081.
-doi:\href{https://doi.org/10.1093/icesjms/fsab092}{10.1093/icesjms/fsab092}
+variable, and changing ecosystem at {South Georgia}. ICES Journal of
+Marine Science \textbf{78}(6): 2065--2081.
+doi:\href{https://doi.org/10.1093/icesjms/fsab092}{10.1093/icesjms/fsab092}.
 
 \bibitem[\citeproctext]{ref-Turner2020}
-Turner, J., Guarino, M. V., Arnatt, J., Jena, B., Marshall, G. J.,
-Phillips, T., \ldots{} Cavanagh, R. (2020). Recent {Decrease} of {Summer
-Sea Ice} in the {Weddell Sea}, {Antarctica}. \emph{Geophysical Research
-Letters}, \emph{47}(11), e2020GL087127.
-doi:\href{https://doi.org/10.1029/2020GL087127}{10.1029/2020GL087127}
+Turner, J., Guarino, M.V., Arnatt, J., Jena, B., Marshall, G.J.,
+Phillips, T., Bajish, C.C., Clem, K., Wang, Z., Andersson, T., Murphy,
+E.J., and Cavanagh, R. 2020. Recent {Decrease} of {Summer Sea Ice} in
+the {Weddell Sea}, {Antarctica}. Geophysical Research Letters
+\textbf{47}(11): e2020GL087127.
+doi:\href{https://doi.org/10.1029/2020GL087127}{10.1029/2020GL087127}.
 
 \bibitem[\citeproctext]{ref-Verges2019}
-Vergés, A., McCosker, E., Mayer-Pinto, M., Coleman, M. A., Wernberg, T.,
-Ainsworth, T., \& Steinberg, P. D. (2019). Tropicalisation of temperate
+Vergés, A., McCosker, E., Mayer-Pinto, M., Coleman, M.A., Wernberg, T.,
+Ainsworth, T., and Steinberg, P.D. 2019. Tropicalisation of temperate
 reefs: {Implications} for ecosystem functions and management actions.
-\emph{Functional Ecology}, \emph{33}(6), 1000--1013.
-doi:\href{https://doi.org/10.1111/1365-2435.13310}{10.1111/1365-2435.13310}
+Functional Ecology \textbf{33}(6): 1000--1013.
+doi:\href{https://doi.org/10.1111/1365-2435.13310}{10.1111/1365-2435.13310}.
 
 \bibitem[\citeproctext]{ref-Verges2014}
-Vergés, A., Steinberg, P. D., Hay, M. E., Poore, A. G. B., Campbell, A.
-H., Ballesteros, E., \ldots{} Wilson, S. K. (2014). The tropicalization
-of temperate marine ecosystems: Climate-mediated changes in herbivory
-and community phase shifts. \emph{Proceedings of the Royal Society B:
-Biological Sciences}, \emph{281}(1789), 20140846.
-doi:\href{https://doi.org/10.1098/rspb.2014.0846}{10.1098/rspb.2014.0846}
+Vergés, A., Steinberg, P.D., Hay, M.E., Poore, A.G.B., Campbell, A.H.,
+Ballesteros, E., Heck, K.L., Booth, D.J., Coleman, M.A., Feary, D.A.,
+Figueira, W., Langlois, T., Marzinelli, E.M., Mizerek, T., Mumby, P.J.,
+Nakamura, Y., Roughan, M., van Sebille, E., Gupta, A.S., Smale, D.A.,
+Tomas, F., Wernberg, T., and Wilson, S.K. 2014. The tropicalization of
+temperate marine ecosystems: Climate-mediated changes in herbivory and
+community phase shifts. Proceedings of the Royal Society B: Biological
+Sciences \textbf{281}(1789): 20140846. {Royal Society}.
+doi:\href{https://doi.org/10.1098/rspb.2014.0846}{10.1098/rspb.2014.0846}.
 
 \bibitem[\citeproctext]{ref-Vinuesa2005}
-Vinuesa, J. H. (2005). Distribución de crustáceos decápodos y
-estomatópodos del golfo {San Jorge}, {Argentina}. \emph{Revista de
-Biología Marina y Oceanografía}, \emph{40}(1), 7--21.
-doi:\href{https://doi.org/10.4067/S0718-19572005000100002}{10.4067/S0718-19572005000100002}
+Vinuesa, J.H. 2005. Distribución de crustáceos decápodos y estomatópodos
+del golfo {San Jorge}, {Argentina}. Revista de biología marina y
+oceanografía \textbf{40}(1): 7--21. {Universidad de Valparaíso. Facultad
+de Ciencias del Mar}.
+doi:\href{https://doi.org/10.4067/S0718-19572005000100002}{10.4067/S0718-19572005000100002}.
 
 \bibitem[\citeproctext]{ref-Vinuesa2007}
-Vinuesa, J. H., \& Varisco, M. (2007). Trophic ecology of the lobster
+Vinuesa, J.H., and Varisco, M. 2007. Trophic ecology of the lobster
 krill {Munida} gregaria in {San Jorge Gulf}, {Argentina}.
-\emph{Investigaciones Marinas}, \emph{35}(2), 25--34.
-doi:\href{https://doi.org/10.4067/S0717-71782007000200003}{10.4067/S0717-71782007000200003}
+Investigaciones marinas \textbf{35}(2): 25--34. {Escuela de Ciencias del
+Mar. Pontificia Universidad Católica de Valparaíso}.
+doi:\href{https://doi.org/10.4067/S0717-71782007000200003}{10.4067/S0717-71782007000200003}.
 
 \bibitem[\citeproctext]{ref-Vucic-Pestic2011}
-Vucic-Pestic, O., Ehnes, R. B., Rall, B. C., \& Brose, U. (2011).
-Warming up the system: Higher predator feeding rates but lower energetic
-efficiencies. \emph{Global Change Biology}, \emph{17}(3), 1301--1310.
-doi:\href{https://doi.org/10.1111/j.1365-2486.2010.02329.x}{10.1111/j.1365-2486.2010.02329.x}
+Vucic-Pestic, O., Ehnes, R.B., Rall, B.C., and Brose, U. 2011. Warming
+up the system: Higher predator feeding rates but lower energetic
+efficiencies. Global Change Biology \textbf{17}(3): 1301--1310.
+doi:\href{https://doi.org/10.1111/j.1365-2486.2010.02329.x}{10.1111/j.1365-2486.2010.02329.x}.
 
 \bibitem[\citeproctext]{ref-Ward2018}
-Ward, P., Tarling, G. A., \& Thorpe, S. E. (2018). Temporal changes in
+Ward, P., Tarling, G.A., and Thorpe, S.E. 2018. Temporal changes in
 abundances of large calanoid copepods in the {Scotia Sea}: Comparing the
-1930s with contemporary times. \emph{Polar Biology}, \emph{41}(11),
+1930s with contemporary times. Polar Biology \textbf{41}(11):
 2297--2310.
-doi:\href{https://doi.org/10.1007/s00300-018-2369-3}{10.1007/s00300-018-2369-3}
+doi:\href{https://doi.org/10.1007/s00300-018-2369-3}{10.1007/s00300-018-2369-3}.
 
 \bibitem[\citeproctext]{ref-Wege2021}
-Wege, M., Salas, L., \& LaRue, M. (2021). Ice matters: {Life-history}
+Wege, M., Salas, L., and LaRue, M. 2021. Ice matters: {Life-history}
 strategies of two {Antarctic} seals dictate climate change eventualities
-in the {Weddell Sea}. \emph{Global Change Biology}, \emph{27}(23),
-6252--6262.
-doi:\href{https://doi.org/10.1111/gcb.15828}{10.1111/gcb.15828}
+in the {Weddell Sea}. Global Change Biology \textbf{27}(23): 6252--6262.
+doi:\href{https://doi.org/10.1111/gcb.15828}{10.1111/gcb.15828}.
 
 \bibitem[\citeproctext]{ref-Whitehouse2008}
-Whitehouse, M. J., Meredith, M. P., Rothery, P., Atkinson, A., Ward, P.,
-\& Korb, R. E. (2008). Rapid warming of the ocean around {South
-Georgia}, {Southern Ocean}, during the 20th century: {Forcings},
-characteristics and implications for lower trophic levels. \emph{Deep
-Sea Research Part I: Oceanographic Research Papers}, \emph{55}(10),
-1218--1228.
-doi:\href{https://doi.org/10.1016/j.dsr.2008.06.002}{10.1016/j.dsr.2008.06.002}
+Whitehouse, M.J., Meredith, M.P., Rothery, P., Atkinson, A., Ward, P.,
+and Korb, R.E. 2008. Rapid warming of the ocean around {South Georgia},
+{Southern Ocean}, during the 20th century: {Forcings}, characteristics
+and implications for lower trophic levels. Deep Sea Research Part I:
+Oceanographic Research Papers \textbf{55}(10): 1218--1228.
+doi:\href{https://doi.org/10.1016/j.dsr.2008.06.002}{10.1016/j.dsr.2008.06.002}.
 
 \bibitem[\citeproctext]{ref-Whitworth1980}
-Whitworth, T. (1980). Zonation and geostrophic flow of the {Antarctic}
-circumpolar current at {Drake Passage}. \emph{Deep Sea Research Part A.
-Oceanographic Research Papers}, \emph{27}(7), 497--507.
-doi:\href{https://doi.org/10.1016/0198-0149(80)90036-9}{10.1016/0198-0149(80)90036-9}
+Whitworth, T. 1980. Zonation and geostrophic flow of the {Antarctic}
+circumpolar current at {Drake Passage}. Deep Sea Research Part A.
+Oceanographic Research Papers \textbf{27}(7): 497--507.
+doi:\href{https://doi.org/10.1016/0198-0149(80)90036-9}{10.1016/0198-0149(80)90036-9}.
 
 \bibitem[\citeproctext]{ref-Williams2000}
-Williams, R. J., \& Martinez, N. D. (2000). Simple rules yield complex
-food webs. \emph{Nature}, \emph{404}(6774), 180--183.
-doi:\href{https://doi.org/10.1038/35004572}{10.1038/35004572}
+Williams, R.J., and Martinez, N.D. 2000. Simple rules yield complex food
+webs. Nature \textbf{404}(6774): 180--183. {Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/35004572}{10.1038/35004572}.
 
 \bibitem[\citeproctext]{ref-Wood2015}
-Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
-(2015). Effects of spatial scale of sampling on food web structure.
-\emph{Ecology and Evolution}, \emph{5}(17), 3769--3782.
-doi:\href{https://doi.org/10.1002/ece3.1640}{10.1002/ece3.1640}
+Wood, S.A., Russell, R., Hanson, D., Williams, R.J., and Dunne, J.A.
+2015. Effects of spatial scale of sampling on food web structure.
+Ecology and Evolution \textbf{5}(17): 3769--3782.
+doi:\href{https://doi.org/10.1002/ece3.1640}{10.1002/ece3.1640}.
 
 \bibitem[\citeproctext]{ref-Woods2023}
-Woods, B. L., Van de Putte, A. P., Hindell, M. A., Raymond, B.,
-Saunders, R. A., Walters, A., \& Trebilco, R. (2023). Species
-distribution models describe spatial variability in mesopelagic fish
-abundance in the {Southern Ocean}. \emph{Frontiers in Marine Science},
-\emph{9}.
+Woods, B.L., Van de Putte, A.P., Hindell, M.A., Raymond, B., Saunders,
+R.A., Walters, A., and Trebilco, R. 2023. Species distribution models
+describe spatial variability in mesopelagic fish abundance in the
+{Southern Ocean}. Frontiers in Marine Science \textbf{9}. {[}accessed 16
+September 2023{]}.
 
@@
 Wu, L., Cai, W., Zhang, L., Nakamura, H., Timmermann, A., Joyce, T.,
-\ldots{} Giese, B. (2012). Enhanced warming over the global subtropical
-western boundary currents. \emph{Nature Climate Change}, \emph{2}(3),
-161--166.
-doi:\href{https://doi.org/10.1038/nclimate1353}{10.1038/nclimate1353}
+McPhaden, M.J., Alexander, M., Qiu, B., Visbeck, M., Chang, P., and
+Giese, B. 2012. Enhanced warming over the global subtropical western
+boundary currents. Nature Climate Change \textbf{2}(3): 161--166.
+{Nature Publishing Group}.
+doi:\href{https://doi.org/10.1038/nclimate1353}{10.1038/nclimate1353}.
 
 \bibitem[\citeproctext]{ref-Yorio2009}
-Yorio, P. (2009). Marine protected areas, spatial scales, and
-governance: Implications for the conservation of breeding seabirds.
-\emph{Conservation Letters}, \emph{2}(4), 171--178.
-doi:\href{https://doi.org/10.1111/j.1755-263X.2009.00062.x}{10.1111/j.1755-263X.2009.00062.x}
+Yorio, P. 2009. Marine protected areas, spatial scales, and governance:
+Implications for the conservation of breeding seabirds. Conservation
+Letters \textbf{2}(4): 171--178.
+doi:\href{https://doi.org/10.1111/j.1755-263X.2009.00062.x}{10.1111/j.1755-263X.2009.00062.x}.
 

### 2024-03-25 manuscript.Rmd
Change to Rmd for trackdow

---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
bibliography: JAE_Review.bib
csl: "environmental-reviews.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{pdflscape,booktabs}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \linenumbers
---

# The response of trophic interaction networks to multiple stressors in a marine latitudinal gradient of the Southern Hemisphere
## Running Title: Marine stressors in the Southern Hemisphere

Tomás I. Marina^1^, Leonardo A. Saravia^1,2,\*^, Iara D. Rodriguez^3^,
Manuela Funes^4^, Georgina Cordone^5^, Santiago R. Doyle^3,6^, Anahí
Silvestro^6^, David E. Galván^5^, Susanne Kortsch^7^ & Fernando
Momo^3,6^

^1^ Centro Austral de Investigaciones Científicas (CADIC-CONICET),
Ushuaia, Argentina;

^2^ Instituto de Ciencias Polares, Ambiente y Recursos Naturales,
Universidad Nacional de Tierra del Fuego (UNTdF), Ushuaia, Argentina;

^3^ Instituto de Ciencias, Universidad Nacional de General Sarmiento
(UNGS), Los Polvorines, Argentina;

^4^ Instituto de Investigaciones Marinas y Costeras (IIMyC-CONICET), Mar
del Plata, Argentina;

^5^ Centro Para el Estudio de Sistemas Marinos (CESIMAR-CONICET), Puerto
Madryn, Argentina;

^6^ Instituto de Ecología y Desarrollo Sustentable
(INEDES-CONICET-UNLu), Luján, Argentina;

^7^ Tvärminne Zoological Station, University of Helsinki, Hanko,
Finland.

\* corresponding author: Leonardo A. Saravia. Centro Austral de
Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina.
lasaravia@untdf.edu.ar

## Abstract

Ecological networks offer valuable insights into community structure, key species identification, and ecosystem management for biodiversity conservation. Understanding how these networks react to environmental and anthropogenic stressors, especially along geographical gradients, is of increasing interest.
This review presents a pioneering analysis of stressor responses in marine food webs from the southwest Atlantic to the Antarctic (45 - 78ºS), encompassing areas such as San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea, Potter Cove, and the Weddell Sea in Antarctica. Our objectives are to: 1) describe the structure of marine food webs along this axis using a network approach; 2) identify predominant environmental and anthropogenic stressors affecting each ecosystem; and 3) summarize observed food web changes and hypothesize on stressor impacts.
Our collaborative team, comprising regional experts and global authorities on high-latitude marine food webs and stressor effects, ensures a comprehensive and credible literature review. We assessed the effects of stressors primarily at the species level, with notable exceptions like fisheries in San Jorge Gulf.
Hypotheses for each study area were formulated considering: a) stressors; b) impacted parameters; c) node-level species properties; and d) network-level food web properties. Global warming emerges as the most common stressor across the gradient, except in the Beagle Channel and Burdwood Bank, where alien species introduction and fisheries are more influential, respectively. We offer specific hypotheses on how warming may affect food webs.
Our findings highlight the benefits of a network approach in understanding and predicting stressor effects in Southern Hemisphere marine ecosystems. This approach provides a holistic understanding of ecological networks, enhances our ability to identify key species and interactions, and offers insights for ecosystem management and conservation in the face of various stressors.

Keywords: anthropogenic stressors, environmental stressors, food webs, latitudinal gradient, Southern Hemisphere

## 1. Introduction

The application of a network perspective has emerged as a powerful tool to tackle the complexity of species interactions, facilitating a better understanding of the structure and functioning of ecosystems [@Belgrano2005; @Thompson2012]. Trophic networks (or food webs) allow identifying properties and key species that may be crucial for ecosystem stability, and hence important for ecosystem management and biodiversity conservation [@Thompson2012].
There is a growing interest in understanding how ecological networks respond to environmental and anthropogenic stressors along geographical gradients [@Bauer2022; @Cirtwill2015]. Yet, only a few studies have described variation in food web structure along latitudinal gradients in marine ecosystems. The few that have come from the Global North [@Wood2015; @Kortsch2019; @Pecuchet2022], whereas no studies, nor meta-analyses, on geographical variation in marine food webs exist for the Global South (Southern Hemisphere).

Here we review for the first time the state-of-the-art knowledge on stressor response of marine food webs along the southwest Atlantic to Antarctic gradient (45 - 78ºS, Figure 1). We focus on proven and expected changes in food webs driven by stressors in selected areas along this large-scale latitudinal gradient. We recruited food web experts from different marine systems of Argentina and the world (see co-authors’ list). Throughout the year 2023 we maintained regular discussion meetings, typically held every two or three weeks. The aim of this review is threefold: 1) describe the complexity and structure of marine food webs along the southwest Atlantic to Antarctic axis from a network perspective; 2) identify the ongoing environmental and anthropogenic stressors for each marine ecosystem containing the food webs; and 3) review proven food web changes and elaborate hypotheses on how the identified stressors might affect food web features (e.g. energy flow, stability), combining information on node- and network-level properties. Finally, we suggest which additional data and analyses are needed to gain insights into the stressors’ effects on food web properties in the southwest Atlantic to Antarctic region.

## 2. The structure of marine food webs in the Southwest Atlantic - Antarctic region

Together, the southwest and the Atlantic sector of the Southern Ocean comprise one of the most biologically productive regions of the world's oceans [@Acha2004;  @Latorre2023]. The referred region extends from San Jorge Gulf (45ºS) in the Patagonian shelf to the Weddell Sea (78ºS) in the Southern Ocean, and covers a well-connected oceanic latitudinal gradient [@Matano2010; @Guihou2020].

Throughout this latitudinal gradient, many investigations have been carried out addressing the trophic ecology of specific species and prey-predator relationships [@Vinuesa2007; @Pasotti2015;  @Riccialdelli2020; @Saunders2019], but few studies have considered the complexity of the ecosystem in terms of a high resolution of species and their prey-predator interactions (but see @Jacob2011, @Marina2018, @Funes2022, @Lopez-Lopez2022, @Rodriguez2022, @Marinainrev). Neglecting this complexity might lead to a misunderstanding of the structure and functioning of the ecosystems, and ultimately reduce the ability to predict ecosystem responses to perturbations [@Montoya2009].

In this review, we consider marine areas in the Southern hemisphere for which highly-resolved empirical food webs, in terms of species diversity and trophic interactions, have been previously described. These areas include: (1) San Jorge Gulf (45 - 47ºS, 65 - 68ºW), (2) Beagle Channel (~54ºS, 68ºW), (3) Burdwood Bank (~54ºS, 59ºW), (4) Scotia Sea (48 - 58ºS, 50ºW), (5) Potter Cove (62ºS, 58ºW, Antarctica), and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica) (Figure 1). The geographic locations of these marine biomes span from temperate to Antarctic, and are exposed to both environmental (sea warming, glacial retreat) and anthropogenic (fishery, pollution) stressors.

![ Map of the study areas along the southwest Atlantic - Antarctic latitudinal gradient. The areas are marked with numbers from one to six. Smaller areas (1. San Jorge Gulf, 2. Beagle Channel, 3. Burdwood Bank, and 5. Potter Cove) are shown on the panels to the left, whereas the larger areas (4. North and South Scotia Sea, and 6. Weddell Sea) are marked with a red rectangle on the map. The map was drawn using the ‘marmap’ R package [@Pante2023]. Continental contour shapefiles were obtained from www.ign.gob.ar.](Figures/Map_final.jpg){width="6.27in"
height="3.528in"}

San Jorge Gulf is the northernmost study area considered in this review. It is a partially enclosed basin spanning approximately 34,000 km2 and ~100 m of maximum depths, located from Cabo dos Bahias (44°55'S) to Cabo tres Puntas (47°06'S) (Figure 1). The shallower northern and southern ends of the Gulf (with depths ~40 m) present two prominent frontal systems. These systems are the areas of highest productivity [@Glembocki2015]. The Gulf’s productivity supports large invertebrate and vertebrate fisheries [@Gongora2012], as well as marine mammal and seabird populations [@Yorio2009].
The San Jorge Gulf food web comprises 165 nodes and 1015 trophic interactions with a connectance of 0.04. The percentage of top predators is 16%, 78% of intermediate nodes and 6% of basal nodes; 60% of predators are omnivorous (Table 1). The most connected nodes are: the Argentine red shrimp Pleoticus muelleri, the squat lobster Gimothea gregaria, squids (Illex argentinus as dominant species) and Amphipoda. Notably, these nodes present mid-trophic positions in the food web (3.0, 2.5, 3.6 and 2, respectively) [@Funes2022].

At a southern latitude, the Beagle Channel (54°52’S, 68°8’W) is an interoceanic passage located at the southernmost tip of South America, spanning 240 km in length and 5 km in width (~1200 km2), and a range depth of 0 - 140 m (Figure 1). It features complex coastlines, varying bathymetry, a prevailing west-to-east circulation pattern, and a significant longitudinal gradient of glacial freshwater discharge [@Schloss2023]. @Bruno2023 suggests that locally produced suspended particulate organic matter (mostly composed by phytoplankton) and organic matter accumulated in the sediments (macroalgae-originated detritus) are the primary food sources for the marine ecosystem, as opposed to allochthonous materials.
Beagle Channel food web includes 145 nodes and 1115 trophic interactions with a connectance of 0.05 (Table 1). The food web is suggested to have a wasp-waist structure, where the following species play a crucial role in the dynamics of the ecosystem: Fueguian sprat Sprattus fuegensis, longtail southern cod Patagonotothen ramsayi, black southern cod P. tessellata, frogmouth Cottoperca trigloides, and squat lobster Grimothea gregaria [@Riccialdelli2020]. Moreover, the squat lobster has been identified as a species responsible for linking modules and connecting the entire food web [@Rodriguez2022].

The so-called Burdwood Bank ecosystem comprises Marine Protected Areas Namuncurá - Burdwood Bank I and II, meaning the shallow submarine plateau named Burdwood Bank with a 200 m isobath boundary, and a deep slope that reaches 4000 m in depth, respectively [@APN2022] (Figure 1). Physical features in the plateau are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC [@Acha2004]. The plateau is surrounded by steep flanks of up to 4000 m depth, protected by the Marine Protected Area Namuncurá - Burdwood Bank II (32,000 km2; ~55º - 56ºS, ~58º - 62ºW). Intense upwelling and mixing occur in relation to  the slope, entraining deep nutrient-rich waters into the photic layer [@Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Matano2019].
The Burdwood Bank food web comprises 379 nodes and 1788 interactions, with a connectance of 0.01, and an asymmetric degree distribution (i.e. most of the species have a relatively low number of interactions and few species concentrate most of them). Almost half of the consumers are omnivores (0.48), and the network displays a small-world pattern [@Marinainrev] (Table 1).

The Scotia Sea is a deep-sea basin, delimited by the Drake Passage to the West and by the island complex of the Scotia Arc to the North, East, and South, with an approximate extension of 1.5 x 106 km2 and a depth range of 0 - 3000 m [@Murphy2006] (Figure 1). Its oceanography is dominated by the Antarctic Circumpolar Current, which is spatially structured by frontal systems [@Whitworth1980]. The South Antarctic Circumpolar Current Front subdivides the Scotia Sea into two biogeographic regions: the Northern Scotia Sea is characterized by higher and more variable temperatures, and the Southern Scotia Sea by lower and more stable temperatures and influenced by seasonal sea ice [@Raymond2011].
The analysis of the Northern and Southern Scotia Sea food webs shows that the former is relatively more complex than the latter: with higher species richness (218 vs 192) and interactions (10008 vs 7241) and a higher connection overall (0.21 vs 0.20). As expected from a more complex network, the path length is shorter in the Northern Scotia Sea food web. In the same sense, the Southern Scotia Sea network displays a greater proportion of omnivores and a lower mean trophic level [@Lopez-Lopez2022] (Table 1).

In the Antarctic realm, Potter Cove is a ~9 km2 fjord with a depth range of 0 - 200 m located at 25 de Mayo/King George Island (62°14’S, 58°38’W, South Shetland Islands) on the West Antarctic Peninsula (Figure 1). The cove, bordered by the Fourcade Glacier, is divided into three areas: a) the internal cove, a high glacier-influenced, soft sediment zone with a 50 m maximum depth; b) the central cove, a mixed substrate area with low meltwater influence and an 80 m maximum depth; and c) the external cove, ice-free for 60 years with a 185 m maximum depth and rocky substrate [@Jerosch2018]. Potter Cove's high-latitude location results in variable environmental conditions due to photoperiod length seasonality. Sea ice often covers this area in winter [@Schloss2012]. With low phytoplankton biomass, macroalgae, and microphytobenthos are likely the primary food sources for secondary benthic production [@Quartino2008].
The Potter Cove food web includes 110 nodes and 649 interactions, with an asymmetric degree distribution, and a connectance value of 0.05 (Table 1). It presents a modular structure (groups of species interact more strongly with each other than with species belonging to other groups), that’s positively associated with stability, since perturbation can be retained within modules [@Rodriguez2022].

Located between 74 and 78ºS, the high Antarctic Weddell Sea shelf spans approximately 450 km from East to West [@Jacob2011] (Figure 1). The water depth ranges from 200 to 500 m, with shallower regions being covered by continental ice that forms the coastline along the eastern and southern parts of the Weddell Sea. Within this shelf area, exists a complex three-dimensional benthic habitat characterized by substantial benthic biomasses and an intermediate to high diversity when compared to benthic boreal communities [@Teixido2002].
The Weddell Sea food web exhibits a high level of network complexity, featuring the greatest number of nodes (490) and trophic interactions (16041) among the analyzed food webs in this review (Table 1). Its connectance (0.07) and other structural properties are intermediate compared to the other food webs. Recently, the interaction strengths of this food web were estimated, revealing the presence of numerous weak and few strong interactions, which is consistent with findings in other complex food webs [@Nilsson2016]. Notably, this asymmetric distribution of interaction strength is likely to promote community persistence.

\newpage
\footnotesize

Table 1. Complexity and structure properties of the marine food webs considered in the present review. Refer to Table 2 for definition of properties. mean TL: mean trophic level. Food webs are ordered by increasing latitude.

--------------------- ----------- ----------- ----------------- ----------------- ------------- -------------- -------------------------------
**Food web**           **Nodes**   **Links**   **Connectance**   **Path length**   **mean TL**   **Omnivory**   **Reference**
--------------------- ----------- ----------- ----------------- ----------------- ------------- -------------- -------------------------------
San Jorge Gulf        165         1015        0.04              2.17              3.02          0.63           @Funes2022

Beagle Channel        145         1115        0.05              2.12              2.37          0.55           @Rodriguez2022

Burdwood Bank         379         1788        0.01              2.99              2.52          0.49           @Marinainrev

Potter Cove           110         649         0.05              2.33              2.22          0.46           @Marina2018; @Rodriguez2022

N Scotia Sea          218         10008       0.21              1.87              3.29          0.73           @Lopez-Lopez2022

S Scotia Sea          192         7241        0.20              1.90              3.21          0.71           @Lopez-Lopez2022

Weddell Sea           490         16041       0.07              2.19              2.62          0.51           @Jacob2011
----------------------------------------------------------------------------------------------------------------------------------------------

\normalsize

## 3. Environmental and anthropogenic stressors in the Southwest Atlantic - Antarctic region

A stressor is any environmental or anthropogenic variable that causes a quantifiable change, irrespective of its direction (increase or decrease), in a biological response [ @Orr2020]. In the light of this, the southwest Atlantic - Antarctic marine biota has been and is currently subjected to a variety of stressors (e.g. sea warming, glacial retreat, ice changes, acidification, species invasion, fisheries, and contamination). Although it is well-known that multiple stressors act in concert at any given time (e.g. warming and fishery; acidification and contaminants) [@Gutt2021], to date stressor assessments have been performed individually. Moreover, the potential for interactive effects of two or more stressors (synergy or antagonism) [ @Cote2016] is almost unknown for the region [@Rowlands2021].

In the following subsections, we describe the main environmental and anthropogenic stressors, and the species (or trophic species) and parameters affected reported for the marine ecosystems that contain the food webs considered in this review. In Table S2 we provide an exhaustive list of all stressors affecting species inhabiting each area, considering: the type of stressor, species and parameter affected, and locality.

<!-- Aca estaba la tabla 2 -->

### 3.1 San Jorge Gulf

San Jorge Gulf experienced several environmental and anthropogenic stressors (Table S2). Trawl fisheries discard several species and add new trophic interactions to the food web which resulted in a decrease in trait variability and the stability of the system [@Funes2022; @Rincon-Diaz2021]. Moreover, it changed the availability of prey to several predators. For example, Merluccius hubbsi one of the main bycatch species, became prey item to non-diving seabirds, like the kelp gull Larus dominicanus [@Gonzalez-Zevallos2006] and reef fishes [@Funes2019]. Although juveniles of M. hubbsi are largely the main bycatch item, 29 other cartilaginous and 69 bony local fish species were also registered as incidental catch between 2005 and 2014 [@Bovcon2013; @RuibalNunez2020]. This level of impact triggered a shift in the functional diversity of the assemblages homogenizing the trophic function of fishes [@Rincon-Diaz2021]. Other functional changes were a decrease in the maximum sizes of individual fish, together with a drop in elasmobranchs biomass and an increase in crustaceans biomass [@Funes2020]. The significant increase in crustacean biomass was mostly due to the increase in Pleoticus muelleri and Grimothea gregaria populations [@Funes2020]. These species rapidly became the most important prey for the most abundant fishes in the area: M. hubbsi and Mustelus schmitti [@Pasti2021]. However, the above-mentioned effects of trawl fisheries on the structure and function of the San Jorge Gulf community may have changed again, since the fisheries ceased activity in 2015 (Annex I, Resolution CFP No 7/2018), remaining a small trawling artisanal fishery.

Sea warming is another important environmental stressor in the San Jorge Gulf, because of the southward shifts of northern fish populations to the Gulf [@Galvan2022]. The San Jorge Gulf is especially prone to be affected by climate-driven shifts in species ranges, because it is located in the ecotone between two biogeographic provinces, the Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) [@Balech2008]. In addition to this tropicalization from northern fish populations, alien species are also documented to affect the demersal assemblage (fish and macroinvertebrates) in the Gulf [@Galvan2022].
Finally, San Jorge Gulf is exposed to urban and industrial pollution due to an oil monobuoy from which oil manipulation and general oil transport along the Patagonian coast registered several oil spills and chronic oil discharges [@Garcia-Borboroglu2008]. Other marine systems impacted by oil spill showed an important decrease in marine bird populations [@Irons2000], seals and macroalgae (e.g. @Paine1996), with examples of cascading effects throughout the food web [@Peterson2001].

### 3.2 Beagle Channel

A main anthropogenic stressor in the Beagle Channel is the introduction of invasive species (Table S2). Salmonidae were introduced to Tierra del Fuego in the 1930s. Especially Chinook salmon Oncorhynchus tshawytscha causes concern. The detection of Chinook salmon in Tierra del Fuego dates back to April 2006, and its population has been expanding since then [@Nardi2019]. Being a top predator Chinook salmon can compete with several native species in the Beagle Channel [@Correa2008], and prey over native species such as Notothenioids (Eleginops maclovinus, Patagonotothen tessellata, P. cornucola, P. sima, Paranotothenia magellanica, Harpagifer bispinis), the Atherinidae Odontesthes smitti and O. nigricans, the Fuegian sprat Sprattus fuegensis, and larvae of king crabs (Lithodes antarcticus and Paralomis granulosa) [@Fernandez2010]. @Ciancio2008 observed that Chinook salmon in the Southern Patagonian Shelf Ecosystem Area primarily feed on sprats and display trophic levels comparable to those of intermediate-sized fish and cephalopod predators species, showing significant dietary overlap with Magellanic penguins (Spheniscus magellanicus). Another potential competitor for Chinook salmon in the Beagle Channel is the Commerson's dolphin (Cephalorhynchus commersonii), which shares a similar diet [@Riccialdelli2013].

In the Beagle Channel, other anthropogenic stressors include contaminants like metals, perfluorinated compounds, hydrocarbons, and microplastics found in animal tissue and sediments. Some studies reported varying heavy metal levels in sea mussel tissues and sediments, indicating bioavailability differences [@Duarte2011]. Other research found similar carbon and carbohydrate levels in Ushuaia Bay's surface sediments to those in hypertrophic ecosystems, along with hydrocarbons and heavy metals linked to port and industrial activities [@Gil2011]. @Commendatore2012 identified three distinct hydrocarbon accumulation zones in the Bay. @Llorca2012 found high levels of perfluorinated compounds in algae, fish, and guano. @Ferreira2021 showed that black southern cod in Ushuaia Bay may be exposed to endocrine-disrupting compounds from urban and industrial pollution.
@Perez2020 and @Ojeda2021 found microplastics in M. edulis chilensis and Nacella magellanica, respectively. These studies link pollutants to Ushuaia (54°48′S 68°18′W) and its port and industrial activities. We expect the Beagle Channel area closest to the city to be most affected. Contaminants can spread through the food web, magnifying the risk to higher-level organisms. @Fioramonti2022 studied mercury transfer in three southwest Atlantic Ocean food webs and found biodilution in the Beagle Channel and Atlantic coast of Tierra del Fuego webs. However, mercury concentrations rose with benthivory in these webs, and higher mercury was found in phytoplankton and Grimothea gregaria. Squat lobsters connect pelagic and benthic habitats, so any disruption to them could disrupt the food web [@Rodriguez2022]. @Dodino2022 found the highest mercury levels in Magellanic penguin feathers from offshore colonies in Tierra del Fuego. Recently, Ushuaia's kelp forests have seen a decrease in biodiversity and changes in macroalgae composition due to urban pollution [@Kaminskyinprep].

### 3.3 Burdwood Bank

The stressors reported for the ecosystem of the Marine Protected Areas Namuncurá within Burdwood Bank I and II are mostly anthropogenic; there is a lack of studies focusing on the environmental stressors that are known to be occurring at a regional scale (e.g. sea surface warming, @Franco2020) (Table S2).
Several fisheries targeting demersal fishes operate in the vicinity and within the ecosystem of the Marine Protected Areas (i.e. Marine National Reserve management category). The Patagonian fisheries  on the toothfish Dissostichus eleginoides  has gained prominence in recent years [@Allega2020; @Gorini2021]. Although these are regulated by the Argentinean government, incidental catches do occur, where demersal fishes of the genera Coelorinchus and Macrourus, seabirds and benthic invertebrates (30+ taxa) are the most common bycatches [@Gaitan2016; @Martinez2022]. Noteworthy, among the invertebrates caught, 8 species are indicator taxa of vulnerable marine ecosystems [@Gaitan2016; @Schejter2021]. Independent assessments of these bycatches suggest no significant impact on the communities [@Gaitan2016; @Martinez2022]. Besides bycatch, species of seabirds are being affected by the fishery due to discards, altering its diet; the most frequently encountered species are Black-browed albatross Thalassarche melanophris, Southern giant petrel Macronectes giganteus, Cape petrel Daption capense, Southern royal albatross Diomedea epomophora, Northern giant petrel M. halli, and White-chinned petrel Procellaria aequinoctialis [@Tamini2023]. Nevertheless, there is a lack of knowledge considering the species’ role in the ecosystem and the potential joint effect of both target fishes and bycatch in a broader food web framework.

Anthropogenic contaminants such as microplastics and mercury are present in the water column of the Burdwood Bank ecosystem [@Cossi2021; @DiMauro2022; @Fioramonti2022]. Microplastics are distributed all along the water column, from surface to deep waters (3-2450 m) [@DiMauro2022]. More importantly, microplastics were found in soft tissues of benthic macroinvertebrates (sea stars Henricia obesa and Odontaster penicillatus) and benthopelagic fishes (Patagonotothen guntheri and P. ramsayi), which not only incorporated the contaminant from the environment through their filter-feeding system but could also get it indirectly from prey organisms already containing plastics in their tissues [@Cossi2021]. Notably, one of the contaminated species, the long tail southern cod Patagonotothen ramsayi, is part of the core group of species that drive the ecosystem through the suggested wasp-waist control [@Riccialdelli2020].
Mercury transfer and biomagnification are ongoing processes in the ecosystem, which are occurring at a greater pace than near coastal areas (Beagle Channel) [@Fioramonti2022]. It’s important to note that the Fuegian sprat Sprattus fuegensis, a pelagic fish with a mid-trophic level in the food web, presented the highest levels of mercury [@Fioramonti2022]. Considering the wasp-waist control of the Fuegian sprat in the food web [@Riccialdelli2020], a rapid and widespread contamination to the top predators is expected [@Fioramonti2022].

In recent years, licenses for seismic studies and exploration of hydrocarbon resources have been granted all along the northwestern limit of the Marine Protected Areas (Secretaría de Gobierno de Energía Res. Nº 65/2018). Although effects from these types of surveys on marine mammals and seabirds are well-known for other regions of the world [@Nowacek2015], there is no particular knowledge for this ecosystem. However, several documents warn of the potential negative effects this may have on the species inhabiting the Burdwood Bank area [@Allega2019; @deHaro2022].

Despite evidence of warming at surface, mid-water and bottom layers (100 m) in Burdwood Bank [@Franco2020], specific studies on the oceanographic aspects of the system are lacking. In this sense, there is a big question mark about the environmental stressors impact on the species and trophic interactions in Burdwood Bank.

### 3.4 Scotia Sea

The Scotia Sea is a vast and heterogenous oceanic region, where especially the areas around South Georgia island represents an area of interest, here referred to as ‘Northern Scotia Sea’. The majority of studies analyzing the stressors’ effects come from this area.

The Scotia Sea has experienced one of the largest levels of warming within the polar regions [@Whitehouse2008]. Together with the Southern Annular Mode anomalies  this has caused a long-term decrease in krill abundance; more pronounced in the northern than in the southern Scotia Sea [@Murphy2007]. Over the past 90 years, the krill also showed an increase in mean body length [@Atkinson2019], which may also alter predator-prey interactions and allow reaching cooler feeding grounds near the seabed, with the potential to link krill to unexpected predators [@Schmidt2011]. Another consequence of the mentioned environmental stressors, is a change in krill distribution due to a southward contraction [@Atkinson2019]. It is noteworthy here, that the distributional shift has not affected all species inhabiting the Northern Scotia Sea, and most abundant calanoid copepods have maintained their distribution [@Tarling2018].
Considering the above, food web models of the Northern Scotia Sea have suggested shifts in the structure and functioning of the food web, from krill-based to non-krill-based, where myctophid fishes and squid are playing important roles [ @Saunders2019].

The principal anthropogenic stressor of the Scotia Sea is commercial fisheries. Krill fishery not only stresses the targeted species, but also the many predators that depend on it as a food source [@Hilborn2017]. Yet, data currently available from monitoring of krill and its predators remain insufficient, hence identifying the potential fishery impacts on the ecosystem is difficult [@Trathan2021]. Apart from krill fishery, two other commercial fisheries operate in the Scotia Sea, targeting Patagonian toothfish species Dissostichus eleginoides and D. mawsoni. The D. eleginoides stock is linked to the stock at South Georgia (‘Northern Scotia Sea’) [@Collins2010], while the D. mawsoni stock is linked to the Antarctic continental shelf (‘Southern Scotia Sea’) [@Soeffker2022]. Despite the fact that the mentioned fisheries are certified by the Marine Stewardship Council standards, @Trathan2023 identified several concerns regarding aspects of fisheries itself, other species' population status (i.e. recovery of baleen whales), and environmental stressors (i.e. sea warming), which could have synergistic effects on the food web structure and functioning that are still unknown.

Mercury transfer and biomagnification are current processes occurring in the Scotia Sea, where the total concentration of contaminants increase with trophic level and are highest in notothenioid and myctophid fishes (e.g. Dissostichus eleginoides, Gymnoscopelus nicholsi), and seabirds [@Seco2021]. During years of low Antarctic krill abundance, predators must deal with both the stress of reduced prey availability and the concurrent rise in mercury exposure [@Seco2021].

### 3.5 Potter Cove (Antarctica)

Regional warming in the last half century has been one of the main factors driving changes in Potter Cove (Western Antarctic Peninsula) [@Chown2022]. Sudden environmental changes have occurred, such as sea surface temperature increase, salinity decrease, suspended particulate matter loading and chlorophyll-a increase, all linked to climatic cycles (Southern Annular Mode and El Niño Southern Oscillation) [@Schloss2012]. Particularly, sea warming has produced drastic environmental and biological transformations (e.g. shifts in dominance of benthic community) in the Potter Cove ecosystem [@Quartino2013; @Sahade2015; @Schloss2012], a system highly dependent on sea-ice dynamics (Table S2).
In Potter Cove, total sea ice cover has decreased since 1991 [@Schloss2012]. Changes in the annual timing of landfast ice formation and breakup of the sea ice cover has multiple effects on species in the food web [@Michel2019]. Warmer winters and springs result in earlier sea-ice melt, causing an abrupt increase in the light available benthic primary producers [@Deregibus2020]. Sea ice also mediates physical disturbances to the benthos by influencing sedimentation and iceberg scouring. These factors affect the production of macroalgae, albeit in opposite ways [ @Deregibus2017], and microphytobenthos [@Hoffmann2019]. On the other hand, sea ice is an important habitat for diatoms and its associated consumers, including copepods and krill [@Flores2012], and thus important for bentho-pelagic nutrient and carbon cycling during winter. Additionally, a decrease in winter sea ice cover produces an increase in physical perturbation on benthic shallow communities in coastal shallows due to ice scouring [@Deregibus2017].
The glacier surrounding Potter Cove has been receding at an increasing rate since 1950 [@Ruckamp2011], which has caused a massive discharge of sediment-laden meltwater [@Meredith2018]. Large quantities of suspended particles affect growth, survival and reproduction of benthic species. This had led to a major shift in the benthic community structure, from a filter feeders–ascidian domination to a mixed assemblage with scavengers and opportunistic species [@Sahade2015], and the metabolic balance in benthos went from net autotrophy to heterotrophy [@Braeckman2021]. Additionally, massive stranding events of the tunicate Salpa thompsoni and the euphausiid Euphausia superba (krill) linked to the presence of glacial meltwater have been reported [@Fuentes2016].
Rising temperatures leading to ice and glacial melting has also substantial impacts on pelagic primary productivity, since it reduces water salinity, affecting water column stratification, light penetration and nutrient availability for photosynthesis [@Schloss2012]. In Potter Cove, changes in biomass of most phytoplankton species have been observed under heat wave conditions, resulting in a shift from a microplankton to a nanoplankton dominated community [@Antoni2020; @Latorre2023]. This means that in areas strongly affected by glacier melt, the planktonic food web is dominated by the microbial loop (ciliates and heterotrophic dinoflagellates preys upon nanophytoplankton, which are sequentially available prey for small omnivorous copepods), instead of being predominantly herbivorous [@Garcia2016; @Garcia2019]. In addition, phytoplankton species under these warming conditions showed a decrease in metabolic rates and in the quality of the fatty acids composition [@Latorre2023].

### 3.6 Weddell Sea (Antarctica)

In the Weddell Sea several stressors have already been triggered by global warming effects (Table S2), from which spatial and temporal reduction in sea ice is suggested to be driving changes in pelagic and benthic communities [@Constable2014; @Gutt2021]. Sea ice extent has reached new record lows since the satellite era began in 1978. Sea warming has been substantial in recent years: in 2017 the mean temperature for February reached 1.45°C, the highest monthly mean ever recorded (0.56°C above the climatological mean) [@Turner2020].
In this context, it has been suggested that Antarctic krill Euphausia superba has already declined as a result of productivity changes caused by sea ice declines [@Atkinson2004]. Declining sea ice cover allows increased access to krill by predators [@Kawaguchi2009], which further contributes to decreased krill abundances. This in turn can result in reduced carbon export due to decreased fecal pellets from krill [@Pauli2021].

On the other hand, sea ice loss increases light availability, triggering primary production by phytoplankton in the short-term [@Pineda-Metz2020]. Furthermore, a warmer and more stable water column with a shallow upper mixed layer, is expected to enhance the dominance of cryptophytes over diatoms which may favor salp populations over krill populations; thereby reducing the magnitude of energy transfer to higher trophic levels and the seabed [@Isla2023].

Higher trophic level species are expected to respond differently to global warming in the Weddell Sea. In this regard, Notothenioid fishes (e.g. Pleuragramma antarcticum) face multiple stressors (sea warming, sea ice decline, ocean acidification) that threaten their survival. While some species exhibit physiological plasticity to compensate for increased oxygen demand, most notothenioid fishes are stenothermal and unable to adjust their metabolic functioning [@Mintenbeck2012]. It is anticipated that the thermal habitat preferred by the Antarctic toothfish Dissostichus mawsoni could undergo contraction in the coming three decades [@Constable2014], further emphasizing the potential impact of global warming effects on these species.
Marine mammals, Weddell and crabeater seals (Leptonychotes weddellii and Lobodon carcinophagus), exhibit varying levels of sensitivity. The latter exhibits a preference for breeding in close proximity to krill swarms, and thus is particularly susceptible to reductions in sea ice concentrations and sea surface temperatures. Rescued sea ice can significantly affect their post- and future breeding foraging success [@Wege2021]. In addition, the Antarctic petrel Thalassoica antarctica, which is one of the most abundant seabirds in the area, is a sea ice dependent forager and breeder [@Orgeira2021]; therefore the loss of this habitat will degrade its foraging success and reproductive output over time. The snow petrel Pagodroma nivea also relies heavily on sea ice for foraging and its colonies in the Weddell Sea may be affected. The emperor penguin Aptenodytes forsteri uses sea ice for breeding; any reductions could constrain its populations, as evidenced by recent observations in the Bellingshausen Sea region [@Fretwell2023]. The Arctic tern Sterna paradisaea spends the summer in the Weddell Sea exploiting krill swarms under receding ice edges, then declines in ice cover may reduce prey availability and quality of molting habitats. Continued warming is thus expected to gradually erode the abundance and distribution of these 'primary species' that dominate the avifauna of the Weddell Sea through loss of critical sea ice habitat [@Orgeira2021].
Variations in sea ice extent have implications for great whales, such as the Humpback whale Megaptera novaeangliae, since their primary prey resource is the Antarctic krill [@Braithwaite2015]. Decreased winter ice coverage results in reduced suitable habitat and lower krill abundance [@Braithwaite2015], with flow-on effects for whale body condition observed historically in harvest data. With climate projections indicating ongoing sea ice losses, further threats to critical krill populations pose risks to the energy intake and reproductive success and long-term viability of humpback whale populations dependent on consistent Antarctic feeding [@Pallin2023].

<!-- Iceberg scouring increases -->
Iceberg scouring is a major factor in the high biodiversity of benthic communities in the Weddell Sea [@Gutt2001]. Even at 600 m depths, iceberg scouring has a strong effect on the benthic environment, disrupting the upper layers of the seabed and removing macrofauna. This patchy disturbance and distribution pattern occurs roughly every 200 square meters on the Antarctic continental shelf. Global warming is predicted to raise iceberg scouring frequency [@Gutt2001a; @Smale2008a], disrupting the environment [@Smale2008]. @Gutt2015 expects tipping points are significant due to these effects and lack of knowledge.

<!-- Multiple stressors: The Southern Ocean and nearshore Antarctic waters are also warming, sea-ice is predicted to decline, winds are strengthening, upwelling and nutrient availability is changing, mixed layer depths are shallowing, and the ocean fronts are moving southward (Deppeler & Davidson, 2017; Stark, Raymond, Deppeler, & Morrison, 2019). These stressors interact, resulting in additive, synergistic, or antagonistic effects on organisms (Boyd, Brown, Schrum, & Krishnakumar, 2015).
[@Hancock2020]

Climate change is likely to cause early breakout of seasonal sea ice in parts of Antarctica, which will dramatically increase the amount of light reaching shallow seabed. This is predicted to result in ecological regime shifts, in which invertebrate-dominated communities are replaced by macroalgal beds [@Clark2015].-->

## 4. From species’ stressors to food web effects

A major challenge in contemporary ecology lies in predicting the effects of stressors on complex multispecies systems, such as food webs. Network analysis has proved to be a powerful tool to tackle this issue, since it can capture the effects of individual and multiple stressors on communities and ecosystems [@Montoya2009; @OGorman2012; @Bruder2019].

Environmental and anthropogenic stressor effects in the southwest and the Atlantic sector of the Southern Ocean have been mostly assessed individually and at the organism and/or population, i.e., at the node level (Table S2), with one exception: the effect of fisheries in the San Jorge Gulf food web (see section below for more details). To address the most plausible stressors effects on the selected food webs, given the current information, we built hypotheses for each study area. To this aim, we developed a theoretical framework considering the following: a) stressor(s), b) parameter(s) affected, c) node-level properties of the affected species, and d) network-level properties of the food web.

We considered that a stressor will affect one of the following species’ characteristics or parameters: metabolism, biomass, distribution, and diet (Figure 2). ‘Metabolism’ refers to any change related to metabolic rate, such as reproduction, hatching, larval development, growth and mortality, and contamination due to pollutants (e.g. growth  effect in filter-feeders due to sediment in water column in Potter Cove; endocrine disruption in fish due to urban pollutants in Beagle Channel). ‘Biomass’ indicates an effect at the population level, where the density/abundance is being impacted (e.g. abundance decreases in macrobenthos due to iceberg scouring in Weddell Sea). ‘Distribution’ entails a change at the population level in the geographic space occupied by a species, e.g. southward contraction of Antarctic krill due to sea warming of the Scotia Sea. ‘Diet' includes alterations in the prey items of a species at the population level, e.g, due to prey switching, having a direct effect on the structure of the food web, e.g. new prey item (discards) for seabirds due to fishery activities in Burdwood Bank.
Next, we considered node- and network-level properties relevant to the hypothesized stressor effects on the food webs, and which have been previously calculated for the studied food webs (Table 2). At the node-level, we included: a) degree, b) trophic position, c) omnivory index, and d) relative abundance (see Table S1 in Supporting Information for properties of stressed nodes). At the network-level, we considered: a) connectance, b) path length, c) mean trophic level, and d) omnivory (Table 1).

<!--
### Leo input

The propagation of stressor-induced perturbations across food webs is significantly influenced by species interactions and cascading effects. One way to consider which are the species that more sensitive to these perturbations is the degree, which quantifies the number of connections a species has, provides a robust prediction of species importance and correlates with other indices that include indirect interactions [@Jordan2006]. There are various definitions for keystone species, and network position alone may not be the sole determinant. Considering abundance or biomass is also crucial as suggested by simulation studies [@Zhao2016].

The impacts of stressors can vary in direction and magnitude as they move through the food web, due to differences in timescales and interacting species [@Jackson2021]. One approach to measure the effects of changes in species populations on the remaining species in a food web is the method of the inverse Jacobian matrix, which requires the knowledge of interaction strengths [@Montoya2009]. Using this approach it was found that the magnitude of net effects is negatively correlated with the  degree (sum of predator and prey links) of the perturbed species in most analyzed food webs. Species with few connections have stronger net effects on other species within food webs compared to highly connected species. Highly connected species may possess compensatory mechanisms, such as enhanced apparent competition, that regulate their biomass and mitigate the impacts of disturbances [@Montoya2009]. Similarly, studies by [@Zhao2016] have shown that the extinction of highly connected species in food webs, which have many feeding interactions, may not necessarily pose the greatest threat to biodiversity loss. Instead, the strength of feeding links and the prevalence of indirect interactions have a stronger influence on food web stability. Both quantitative fluxes and species dispersing their effects across many links are important considerations in biodiversity conservation. The potential for highly connected species to act as keystone species may have been overestimated in previous studies.

Recent studies suggest that significant apex predators [@Woodward2010; @OGorman2009] and marine mammals would exhibit high susceptibility to stressors and an inclination toward experiencing synergistic impacts . This susceptibility was largely attributed to their role in food chains as primary predators, as well as their involvement in omnivory and exploitative competition interactions. Predators species were predicted to either benefit synergistically from stressor effects by occupying trophic positions as mesopredators in omnivory interactions, or to display insensitivity to stressors due to their trophic role as resources in exploitative competition interactions [@Beauchesne2021], this suggest that the trophic level of a species could be important to anticipate the impact of stressors.

But also the species' vulnerability to stressor effects might arise solely from indirect exposure. The number of stressors influencing a species does not necessarily correlate with higher sensitivity. For instance @Beauchesne2021 showed that despite stressors impacting shrimp in terms of mortality, physiology, and behavior, its trophic sensitivity was low. On the other hand, marine mammals and seabirds that were not directly affected by stressors were markedly susceptible to the indirect repercussions of stressors and nonadditive effects.-->

![Conceptual diagram: from species’ stressors to food web effects. See text for explanation.](Figures/Figure2_StressorDiagram.png){width="6.27in"
height="3.528in"}

\newpage
\scriptsize

Table 2. Node and network-level properties used to build hypotheses on the stressors’ effects.

----------------------------------------------------------------------------------------------------------
**Property**         **Definition**              **Relevance for stressor effects**        **Reference**
-------------------- --------------------------- ----------------------------------------- ---------------
*Node-level*

Degree               Number of feeding           Perturbations to high-degree species      @Dunne2002a; 
                     interactions in which       may have more significant effects on      @Jordan2007
                     the species participates    the food web robustness to perturbations 
                     as prey and/or predator.    than low-degree species.

Trophic position     Place in the food web       Perturbations on basal resources,         @Williams2000; 
                     relative to the basal       intermediate species and top predators    @Thompson2007
                     resources that support      are expected to have large effects on the 
                     the community. Classifies   rest of their communities if ecosystem 
                     species in: basal,          control is bottom-up, wasp-waist or 
                     intermediate and top.       top-down, respectively.

Omnivory             Consumer resource use       High-omnivore species (generalists)       @Thompson2007
                     across trophic levels.      are more flexible than low-omnivore
                                                 species to diet changes.

Relative abundance   Species' density in         Perturbations on abundant (dominant)      @Nilsson2016
                     proportion to the other     species are expected to have large 
                     species of the food web.    effects on the stability and energy 
                                                 flux of the food and ecosystem, 
                                                 respectively.

*Network-level*

Conectance           Proportion of actual        Estimator of community sensitivity to     @Dunne2002
                     interactions among          stressors. High connectance gives 
                     possible ones.              resistance and resilience to the 
                                                 food web.

Path length          Average distance,           Short distances enhance rapid and         @Albert2002
                     accounted by the number     broad propagation of perturbations.
                     of interactions, between 
                     any pair of species.

Mean TL              Average of all species'     Influences the magnitude and efficiency   @Duffy2007; 
                     trophic position contained  of trophic transfer. A higher mean food   @Olivier2019
                     in the food web.            chain length reflects increased energy 
                                                 availability and productivity.

Omnivory             Proportion of species that  It provides trophic flexibility to an     @Kratina2012
                     feed at different trophic   ecosystem. Reduces probability of 
                     levels.                     trophic cascades.
----------------------------------------------------------------------------------------------------------

\normalsize

### 4.1 Main stressor effects in food webs in a southwest Atlantic - Antarctic gradient

The most common stressor reported along the southwest Atlantic - Antarctic gradient is global warming, except for Beagle Channel and Burdwood Bank, which are more influenced by the introduction of an alien species and fisheries, respectively (section 3, Table 3). The main characteristics of global warming in the region, and the most plausible drivers of change, are: sea warming, glacial retreat, elevated sediment input in the water column, and reduction of the sea ice extent. These drivers act in different ways and magnitudes in the studied locations along the latitudinal gradient. 
Despite emphasizing global warming in this section, this does not mean that no other stressors act or interact with global warming in the study systems, potentially buffering the overall effect on the food web (e.g. sea warming and fishery in San Jorge Gulf).
Climate change has led to several well-documented impacts on marine species regarding distributional shifts induced by warming of marine currents [@Poloczanska2013; @Wu2012; @Verges2019]. Furthermore, warmer temperatures increase species metabolic rates [@Brown2004]. Changes in metabolic rates can subsequently translate into shifts in species traits (body size, @Vucic-Pestic2011; @Klein2018], biomass [@Perry2020] and distribution [@Kortsch2015]. Alterations in the species body size and distributions have ripple effects on feeding interactions, for example, it can introduce new feeding interactions [@Pecuchet2020; @Verges2014], modify existing ones, and shorten energy pathways [@Bartley2019; @OGorman2019], and reduce trophic efficiencies [@Vucic-Pestic2011].

In recent years, several new fish  [@Galvan2022] and macroinvertebrates species [@Vinuesa2005; @Lopez-Gappa2022] were registered in Patagonia, mostly in San Jorge Gulf in relation to the southward range shift of warm-temperate species. This distributional change is driven by the tropicalization of temperate waters caused by sea warming [@Verges2014; @Verges2019]. Because of its location in the ecotone between two biogeographic provinces, the Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) [@Balech2008], the San Jorge Gulf is prone to changes in species composition. We hypothesize that sea warming will alter the food web structure topologically, by increasing the number of species and interactions. Newcomers are, in general, mid-trophic level species with generalist diets, hence an increase in food web connectance may be expected [@Bartley2019]. In another temperate ecosystem, an increase in the number of fish species, led to an increase in functional diversity and predation rate [@Sgarlatta2023]; consequences that may also be expected in San Jorge Gulf. Given the short path length of the San Jorge Gulf food web, the disturbances from the listed stressors are expected to spread to many species of the food web (Table 3). However, it has to be acknowledged that the increase in functional diversity driven by the range expansion of warm-temperate species is contrary to the process of homogenization and loss of functional diversity in the area driven by trawl fisheries [@Rincon-Diaz2021].

In the middle of the latitudinal gradient (considered in this study), the Scotia Sea has experienced one of the largest levels of sea warming of any polar region [@Whitehouse2008; @Atkinson2019]. @Lopez-Lopez2022 suggested that the southward distributional shift of generalist predators from the northern towards southern Scotia Sea increases network connectance of the latter, while decreasing its modularity. The lower modularity may increase the probability of perturbations spreading through the network [@Stouffer2011], which may be offset by increased connectance enhancing robustness to species loss [@Dunne2002a].
In the northern Scotia Sea around South Georgia Island, we suggest that the declining krill biomass driven by sea warming [@Atkinson2019], ocean acidification and pollution synergy [@Rowlands2021], will reduce the energy transfer to top predators like seabirds and marine mammals. However, this may be buffered since the dominant copepod species have maintained their distribution [@Tarling2018], but most importantly, showed an abundance increase in recent decades likely due to reduced predation and competition for food [@Ward2018]. All this is significant for the structure of the food web given the central role of krill and copepods, characterized by high degree and mid-trophic position (Table S1). Overall, the food web's inherent resilience, marked by high connectance and omnivory, added to the potential compensation for the krill decrease due to a copepod increase, may buffer against structural changes (Table 3).

In Potter Cove, a fjord-like Antarctic ecosystem, the impacts of climate change affect many species within the food web. Potter Cove has recently experienced frequent events of marine heatwaves, i.e. prolonged periods of anomalously high sea surface temperatures [@Oliver2018; @Latorre2023]. This has led to decreases in biomasses of different planktonic functional groups [@Garcia2019; @Latorre2023]. Given the relatively low abundance of phytoplankton, zooplankton’s low degree, and the modular configuration of the food web, we hypothesize that changes in these nodes, due to increased sea temperatures, will be retained in the basal pelagic compartment of the food web and will not expand to higher trophic levels.
Benthic primary producers in Potter Cove are being influence by the decrease in winter sea ice cover (higher light availability), the increased levels of sediments in the water column due to glacial melt run-off (lower light penetration) and the newly free-ice areas available for colonization associated to glacier retreat. The overall local effect of climate change on macroalgae is a net increase in their production [@Deregibus2023]. It has been proposed that larger diversity in primary producers can support a more diverse food web with more specialized consumers [@Iken2023]. We expect to see differential effects of climate change on hard and soft bottom associated food webs [@Cordone2020]. Given the high relative abundance and the high degree of the macroalgae functional group (Table S1), we expect a longer hard bottom food web, wider consumer trophic niches, and that it will become more stable as sea ice cover decreases and the glacier retreats due to global warming.
In soft bottom areas of the Cove, multiple food web nodes are being affected by ongoing warming effects: decrease in net primary production of benthic microalgae [@Hoffmann2019], and changes in the benthic community biomass, distribution and composition [@Sahade2015; @Pasotti2015]. Given that the Potter Cove food web’s present low connectance and omnivory, we suggest fragility and potential trophic cascade effects [@Marina2018] with pronounced changes in energy fluxes (Table 3).

The southernmost location of the latitudinal gradient is the Weddell Sea, where the main effect of global warming is the decrease in sea ice extent, with reported anomalies in the past summer seasons [@Fretwell2023]. Declining sea ice extent has reduced the abundance of krill [@Atkinson2004; @Flores2012], and produced an increase in phytoplankton productivity [@Isla2023; @Pinkerton2021], altering the plankton community structure, and benefiting cryptophytes over diatoms [@Lin2021]. Moreover, habitat loss from sea ice decline will reduce the foraging success and breeding sites of seabirds (e.g., snow petrel Pagodroma nivea and emperor penguin Aptenodytes forsteri), decreasing their biomassess and modifying their distributions.
The projected rise in iceberg scouring is expected to significantly alter the biomass and community structure of macrobenthos, which in turn will impact mid-trophic level predators such as demersal fish [@Gutt2001a; @Mintenbeck2012]. While we do not anticipate large-scale topological changes in the food web, local extinctions could lead to such changes, particularly affecting benthic species [@Gutt2003]. Given that the impacted species—whether individually like krill, or collectively like macrobenthos—present a mid-trophic position, high biomass and high degree (Table S1), we hypothesize that significant shifts in energy fluxes will occur (Table 3). Additionally, the food web's low proportion of omnivores suggests reduced system resilience (Table 1), increasing the likelihood of regime changes [@Gutt2015].

The two ecosystems in the subantarctic region, the Beagle Channel and Burdwood Bank, are more affected by other anthropogenic stressors than warming. Although these areas are being impacted by sea warming, potentially affecting vertebrate and invertebrate species [@Franco2020], to date no studies exist for Beagle Channel and Burdwood Bank ecosystems.
In the Beagle Channel, the introduction of chinook salmon, a non-native species, poses a significant risk to the existing food web [@Fernandez2010]. We hypothesize that chinook salmon's predation on Fuegian sprat and black southern cod will disrupt the established patterns of interaction within the food web. Both of these prey species are crucial for food web dynamics due to their mid-trophic positions and relatively high abundance (Table S1). Moreover, we expect that changes in the black southern cod population will have a more significant impact on the food web than changes in the Fuegian sprat population, as the black southern cod has a higher degree (Table S1). Overall, these disruptions could have far-reaching effects on the ecosystem. This is particularly concerning given the short path length of the food web, which means that changes can quickly propagate through the system, affecting many species and potentially destabilizing the entire network. This phenomenon is further heightened by the ecosystem's inherent vulnerability to changes at mid-trophic levels, often referred to as wasp-waist control (Table 3).
In the Burdwood Bank region, fishing activities may be the main stressor causing shifts in the food web (Table S2). We hypothesize that a combination of factors will destabilize the already fragile ecosystem, characterized by low connectance and low omnivory (Table 1). These factors include a decline in the biomass of the Patagonian toothfish -a key, highly-connected species (Table S1)- as well as smaller changes in the biomass of four mid-level fish species, five top-level seabird species, and over 30 types of benthic macroinvertebrates due to bycatch [@Gaitan2016; @Martinez2022; @Tamini2023]. Additionally, alterations in the diets of six seabird species, caused by discarded catch [@Tamini2023], are expected to disrupt the energy flow and further reduce the stability of the food web (Table 3).

\scriptsize

Table 3. Summary of food web (FW) effects according to the main stressors
reported for each study area. \*Industrial trawl fishery ceased in 2015 remaining artisanal trawling
activity.

+-----------------------+----------------------+-----------------------+
| **Study area**        | **Stressor**         | **Food web effects**  |
|                       |                      |                       |
+=======================+======================+=======================+
| **San Jorge Gulf**    |                      |                       |
+-----------------------+----------------------+-----------------------+
|                       | Fishery\*            | ↑ FW connectance      |
|                       |                      |                       |
|                       |                      | ↓ FW stability        |
|                       |                      |                       |
|                       |                      | ↓ functional          |
|                       |                      | diversity             |
+-----------------------+----------------------+-----------------------+
|                       | Sea warming          | Shifts in FW topology |
|                       |                      |                       |
|                       |                      | ↑ FW connectance      |
|                       |                      |                       |
|                       |                      | ↑ functional          |
|                       |                      | diversity             |
+-----------------------+----------------------+-----------------------+
| **Beagle Channel**    |                      |                       |
+-----------------------+----------------------+-----------------------+
|                       | Alien species        | Shifts in FW topology |
|                       |                      |                       |
|                       |                      | ↑ spread of           |
|                       |                      | perturbations         |
+-----------------------+----------------------+-----------------------+
| **Burdwood Bank**     |                      |                       |
+-----------------------+----------------------+-----------------------+
|                       | Fishery              | Shifts in main energy |
|                       |                      | fluxes                |
|                       |                      |                       |
|                       |                      | ↓ FW stability        |
+-----------------------+----------------------+-----------------------+
| **Scotia Sea**        |                      |                       |
+-----------------------+----------------------+-----------------------+
|                       | Sea warming          | ↑ FW connectance      |
|                       |                      |                       |
|                       |                      | ↓ FW modularity       |
|                       |                      |                       |
|                       |                      | ↓ energy transfer to  |
|                       |                      | high TLs              |
|                       |                      |                       |
|                       |                      | ↑ spread of           |
|                       |                      | perturbation          |
+-----------------------+----------------------+-----------------------+
| **Potter Cove         |                      |                       |
| (Antarctica)**        |                      |                       |
+-----------------------+----------------------+-----------------------+
|                       | Sea warming          | ↓ perturbation        |
|                       |                      | spreading             |
+-----------------------+----------------------+-----------------------+
|                       | Sea ice decline +    | Differential impacts, |
|                       | glacial retreat      | by substrate: hard    |
|                       |                      | (HS) or soft (SS)     |
|                       |                      |                       |
|                       |                      | ↑ FW chain length & ↑ |
|                       |                      | trophic niches (HS)   |
|                       |                      |                       |
|                       |                      | ↑ FW fragility &      |
|                       |                      | trophic cascades (SS) |
+-----------------------+----------------------+-----------------------+
| **Weddell Sea         |                      |                       |
| (Antarctica)**        |                      |                       |
+-----------------------+----------------------+-----------------------+
|                       | Sea ice decline +    | Shifts in main energy |
|                       | iceberg scouring     | fluxes                |
|                       |                      |                       |
|                       |                      | ↑ likelihood of       |
|                       |                      | regime shifts         |
|                       |                      |                       |
|                       |                      | ↓ resilience          |
+-----------------------+----------------------+-----------------------+

\normalsize

## 5. Gaps and future perspectives

<!-- Update diet & biomass data -->
In the selected study areas along the southwest Atlantic to Antarctic latitudinal gradient, several stressors may directly affect consumers’ diets triggered by modified environmental conditions (sea warming, reduced sea ice extent) and new species (due to species’ distributional shifts and introductions). Moreover, the population trends (biomasses and abundances) of important species are also changing [@Funes2020; @Hindell2020; @Woods2023] driving shifts in their roles as either predators or prey (e.g. @Belleggia2017, @Pasti2021). These diet and biomass shifts should be investigated in order to generate reliable predictions of food web responses to multiple stressors in the southwest Atlantic - Antarctic region. One could argue that both shifts might increase the complexity of food webs in the short term by adding generalist predators or new prey (e.g., @Cordone2023) or by enabling discard consumption (e.g. @Funes2022). However, in the long term, both stressors may lead to the biological extinction of certain prey and competitors (e.g. @Anton2019) or a significant reduction in target and incidental catch species (e.g. @Dulvy2014), thereby promoting food web simplification.

<!-- Quantitative food webs & stressors -->
Since this review deals with qualitative data of  prey-predator interactions and stressor effects influencing them, adding quantitative data to the food webs (i.e. interaction strength) and to the stressors (i.e. magnitude) would lead to a better comprehension of how a given stressor acts on specific species which might translate into food web effects.
In this context, it would be useful to develop quantitative food web models  where the strength of interactions reflect energy fluxes among species [@Kortsch2021; @Nilsson2016]. Emerging methods such as bioenergetic food web modeling have been proposed in this regard and present promising ways to estimate shifts in species interactions within food webs as a response to stressors [@Gauzens2023;  @Gellner2023]. Shifts that can lead to changes in overall ecosystem functioning and stability.

<!-- Beagle & Burdwood global warming gap -->
Regarding knowledge and data gaps on species and their stressors, especially the Beagle Channel and Burdwood Bank are poorly sampled study regions. Almost no information exists on the impact of global warming effects (sea warming, glacial retreat, ocean acidification) on communities in these ecosystems, though warming of mid-water and bottom layers have been shown at a regional scale [@Franco2020]. Yet in Beagle Channel recent experimental studies have tested the tolerance of fishes to scenarios of sea warming and/or acidification suggesting potential metabolic impacts on species [@Lattuca2018; @Lattuca2023].

<!-- Multiple stressors -->
Analyzing the impact of multiple stressors through observational studies is challenging [@Gutt2021]. This complexity arises partly because of potential for antagonistic effects, where impacts cancel each other out, or synergistic effects, where the combined impact is greater than the sum of individual effects [@Boyd2015; @Cote2016]. Moreover, these interactive effects are complicated to handle in the framework of complex food webs. The number of pathways through which a species may affect or be affected by other species, and through which stressors may permeate communities, increases exponentially with the number of species and interactions in a network [@Menge1995]. To tackle this complexity, @Beauchesne2021 developed a theory-grounded approach using motifs (i.e. groups of species that, when put together, construct whole food webs) to simplify food webs; a methodology that could be applied to our food web study cases.

## Conclusions

We have reviewed the main environmental and anthropogenic stressors acting in six different areas along a large-scale latitudinal gradient, from temperate Atlantic to cold Antarctic ecosystems. Using a theoretical framework that combines species and food web level data, we suggest how warming effects may impact food web structure and functioning. These qualitative predictions are intended to serve as the basis for future studies in marine ecosystems of the Southern Hemisphere that aim at quantifying the magnitude of these stressors and how they are affecting quantitative food web properties, such as energy fluxes and stability. There is an urgent need to assess these changes using a holistic and quantitative framework where the magnitude of stressors and species interactions are taken into account.

## Acknowledgements

This review is a product of the project “¿Cuáles son los efectos de los cambios ambientales antropogénicos en las interacciones tróficas de las comunidades de los ecosistemas marinos en el gradiente latitudinal Atlántico Sudoccidental - Antártida?”, funded by Consejo Nacional de Investigaciones Científicas (CONICET, code PIP 2022-2024 #0907).

## References

### 2024-03-25 manuscript.tex
Change to Rmd for trackdow

@@
 anthropogenic stressors for each marine ecosystem containing the food
-webs; and 3) resume proven food web changes and elaborate hypotheses on
+webs; and 3) review proven food web changes and elaborate hypotheses on
 how the identified stressors might affect food web features (e.g.~energy
@@
 \bibitem[\citeproctext]{ref-APN2022}
-Administración de Parques Nacionales. 2022. {Plan de gestión AMP
-Namuncurá Banco Burdwood}. {Dirección Nacional de Áreas Marinas
-Protegidas (DNAMP), Argentina}.
+Administración de Parques Nacionales. 2022. {Plan de gesti{ó}n AMP
+Namuncur{á} Banco Burdwood}. Direcci{ó}n Nacional de {Á}reas Marinas
+Protegidas (DNAMP), Argentina.
 
@@
 Albert, R., and Barabási, A.-L. 2002. Statistical mechanics of complex
-networks. Reviews of Modern Physics \textbf{74}(1): 47--97. {American
-Physical Society}.
+networks. Reviews of Modern Physics \textbf{74}(1): 47--97. American
+Physical Society.
 doi:\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}.
@@
 C., Ruarte, C., Schejter, L., Schiariti, A., Segura, V., Souto, V.S.,
-Temperoni, B., and Verón, E. 2020. {Estado del conocimiento biológico
-pesquero de los principales recursos vivos y su ambiente, con relación a
-la exploración hidrocarburífera en la Zona Económica Exclusiva argentina
-y sus adyacencias}. {Instituto Nacional de Investigación y Desarrollo
-Pesquero (INIDEP)}, {Mar del Plata}. {[}accessed 26 September 2023{]}.
+Temperoni, B., and Verón, E. 2020. {Estado del conocimiento biol{ó}gico
+pesquero de los principales recursos vivos y su ambiente, con relaci{ó}n
+a la exploraci{ó}n hidrocarbur{í}fera en la Zona Econ{ó}mica Exclusiva
+argentina y sus adyacencias}. Instituto Nacional de Investigaci{ó}n y
+Desarrollo Pesquero (INIDEP), Mar del Plata. {[}accessed 26 September
+2023{]}.
 
@@
 R., Rico, R., Riestra, C.M., Segura, V., Schejter, L., Schiariti, A.,
-Souto, V., and Verón, E.M. 2019. {Estado del conocimiento biológico
-pesquero de los principales recursos vivos y su ambiente, con relación a
-la exploración hidrocarburífera en la Zona Económica Exclusiva Argentina
-y adyacencias}. {INIDEP}. {[}accessed 10 August 2023{]}.
+Souto, V., and Verón, E.M. 2019. {Estado del conocimiento biol{ó}gico
+pesquero de los principales recursos vivos y su ambiente, con relaci{ó}n
+a la exploraci{ó}n hidrocarbur{í}fera en la Zona Econ{ó}mica Exclusiva
+Argentina y adyacencias}. INIDEP. {[}accessed 10 August 2023{]}.
 
@@
 impacts of marine exotic species. Nature Ecology \& Evolution
-\textbf{3}(5): 787--800. {Nature Publishing Group}.
+\textbf{3}(5): 787--800. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s41559-019-0851-0}{10.1038/s41559-019-0851-0}.
@@
 southward during rapid regional warming. Nature Climate Change
-\textbf{9}(2): 142--147. {Nature Publishing Group}.
+\textbf{9}(2): 142--147. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s41558-018-0370-z}{10.1038/s41558-018-0370-z}.
@@
 decline in krill stock and increase in salps within the {Southern
-Ocean}. Nature \textbf{432}(7013): 100--103. {Nature Publishing Group}.
+Ocean}. Nature \textbf{432}(7013): 100--103. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/nature02996}{10.1038/nature02996}.
@@
 \bibitem[\citeproctext]{ref-Balech2008}
-Balech, E., and Ehrlich, M.D. 2008. {Esquema biogeográfico del Mar
-Argentino}. {Mar del Plata: Instituto Nacional de Investigación y
-Desarrollo Pesquero (INIDEP)}. {[}accessed 14 August 2023{]}.
+Balech, E., and Ehrlich, M.D. 2008. {Esquema biogeogr{á}fico del Mar
+Argentino}. Mar del Plata: Instituto Nacional de Investigaci{ó}n y
+Desarrollo Pesquero (INIDEP). {[}accessed 14 August 2023{]}.
 
@@
 Food web rewiring in a changing world. Nature Ecology \& Evolution
-\textbf{3}(3): 345--354. {Nature Publishing Group}.
+\textbf{3}(3): 345--354. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s41559-018-0772-3}{10.1038/s41559-018-0772-3}.
@@
 Belgrano, A., Scharler, S.E.R.C.U.M., Scharler, U.M., Dunne, J., and
-Ulanowicz, R.E. 2005. Aquatic {Food Webs}: {An Ecosystem Approach}. {OUP
-Oxford}.
+Ulanowicz, R.E. 2005. Aquatic {Food Webs}: {An Ecosystem Approach}. OUP
+Oxford.
 
@@
 Bovcon, N.D., Góngora, M.E., Marinao, C., and González-Zevallos, D.
-2013. Composición de las capturas y descartes generados en la pesca de
-merluza común {Merluccius} hubbsi y langostino patagónico {Pleoticus}
-muelleri: Un caso de estudio en la flota fresquera de altura del {Golfo
-San Jorge}, {Chubut}, {Argentina}. Revista de biología marina y
-oceanografía \textbf{48}(2): 303--319. {Universidad de Valparaíso.
-Facultad de Ciencias del Mar}.
+2013. Composici{ó}n de las capturas y descartes generados en la pesca de
+merluza com{ú}n {Merluccius} hubbsi y langostino patag{ó}nico
+{Pleoticus} muelleri: Un caso de estudio en la flota fresquera de altura
+del {Golfo San Jorge}, {Chubut}, {Argentina}. Revista de biolog{í}a
+marina y oceanograf{í}a \textbf{48}(2): 303--319. Universidad de
+Valpara{í}so. Facultad de Ciencias del Mar.
 doi:\href{https://doi.org/10.4067/S0718-19572013000200010}{10.4067/S0718-19572013000200010}.
@@
 Biological ramifications of climate-change-mediated oceanic
-multi-stressors. Nature Climate Change \textbf{5}(1): 71--79. {Nature
-Publishing Group}.
+multi-stressors. Nature Climate Change \textbf{5}(1): 71--79. Nature
+Publishing Group.
 doi:\href{https://doi.org/10.1038/nclimate2441}{10.1038/nclimate2441}.
@@
 Proceedings of the Royal Society B: Biological Sciences
-\textbf{282}(1819): 20151589. {Royal Society}.
+\textbf{282}(1819): 20151589. Royal Society.
 doi:\href{https://doi.org/10.1098/rspb.2015.1589}{10.1098/rspb.2015.1589}.
@@
 \emph{In} Advances in {Marine Biology}. \emph{Edited by} M. Lesser.
-{Academic Press}. pp. 227--300.
+Academic Press. pp. 227--300.
 doi:\href{https://doi.org/10.1016/B978-0-12-381015-1.00004-6}{10.1016/B978-0-12-381015-1.00004-6}.
@@
 Calcagno, J., and Pérez, A.F. 2021. First evidence of microplastics in
-the {Marine Protected Area Namuncurá} at {Burdwood Bank}, {Argentina}: A
-study on {Henricia} obesa and {Odontaster} penicillatus
+the {Marine Protected Area Namuncur{á}} at {Burdwood Bank}, {Argentina}:
+A study on {Henricia} obesa and {Odontaster} penicillatus
 ({Echinodermata}: {Asteroidea}). Polar Biology \textbf{44}(12):
@@
 the Royal Society B: Biological Sciences \textbf{283}(1824): 20152592.
-{Royal Society}.
+Royal Society.
 doi:\href{https://doi.org/10.1098/rspb.2015.2592}{10.1098/rspb.2015.2592}.
@@
 V., and Sapoznikow, A. 2022. {Informe colaborativo sobre el Estado de
-situación. Riesgos e impactos de la prospección sísmica en el Mar
-Argentino}. {Foro para la Conservación del Mar Patagónico y Áreas de
-Influencia}.
+situaci{ó}n. Riesgos e impactos de la prospecci{ó}n s{í}smica en el Mar
+Argentino}. Foro para la Conservaci{ó}n del Mar Patag{ó}nico y {Á}reas
+de Influencia.
 
@@
 D.K.A. 2017. Understanding the link between sea ice, ice scour and
-{Antarctic} benthic biodiversity\textendash the need for cross-station
-and international collaboration. Polar Record \textbf{53}(2): 143--152.
+{Antarctic} benthic biodiversity--the need for cross-station and
+international collaboration. Polar Record \textbf{53}(2): 143--152.
 doi:\href{https://doi.org/10.1017/S0032247416000875}{10.1017/S0032247416000875}.
@@
 {Diversity}, {Adaptation} and {Ecosystem Services}. \emph{Edited by} I.
-Gómez and P. Huovinen. {Springer International Publishing}, {Cham}. pp.
+Gómez and P. Huovinen. Springer International Publishing, Cham. pp.
 173--191.
@@
 White, W.T. 2014. Extinction risk and conservation of the world's sharks
-and rays. eLife \textbf{3}: e00590. {eLife Sciences Publications, Ltd}.
+and rays. eLife \textbf{3}: e00590. eLife Sciences Publications, Ltd.
 doi:\href{https://doi.org/10.7554/eLife.00590}{10.7554/eLife.00590}.
@@
 Proceedings of the National Academy of Sciences \textbf{99}(20):
-12917--12922. {Proceedings of the National Academy of Sciences}.
+12917--12922. Proceedings of the National Academy of Sciences.
 doi:\href{https://doi.org/10.1073/pnas.192407699}{10.1073/pnas.192407699}.
@@
 penguins. Communications Earth \& Environment \textbf{4}(1): 1--6.
-{Nature Publishing Group}.
+Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s43247-023-00927-x}{10.1038/s43247-023-00927-x}.
@@
 melting: An overlooked threat to {Antarctic} krill. Scientific Reports
-\textbf{6}(1): 27234. {Nature Publishing Group}.
+\textbf{6}(1): 27234. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/srep27234}{10.1038/srep27234}.
@@
 Funes, M. 2020, March. Efectos de la pesca de arrastre sobre la
-estructura trófica del norte del {Golfo San Jorge}. PhD thesis.
+estructura tr{ó}fica del norte del {Golfo San Jorge}. PhD thesis.
 
@@
 Isotopes in Environmental and Health Studies \textbf{55}(4): 327--343.
-{Taylor \& Francis}.
+Taylor \& Francis.
 doi:\href{https://doi.org/10.1080/10256016.2019.1626381}{10.1080/10256016.2019.1626381}.
@@
 by bottom trawl fishery in {Patagonia}. Scientific Reports
-\textbf{12}(1): 10876. {Nature Publishing Group}.
+\textbf{12}(1): 10876. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s41598-022-14363-y}{10.1038/s41598-022-14363-y}.
@@
 \bibitem[\citeproctext]{ref-Gaitan2016}
-Gaitán, E., and Marí, N. 2016. {Análisis de las comunidades bentónicas
-asociadas a capturas de la flota comercial dirigida a Macruronus
-magellanicus}. {Instituto Nacional de Investigación y Desarrollo
-Pesquero (INIDEP)}.
+Gaitán, E., and Marí, N. 2016. {An{á}lisis de las comunidades
+bent{ó}nicas asociadas a capturas de la flota comercial dirigida a
+Macruronus magellanicus}. Instituto Nacional de Investigaci{ó}n y
+Desarrollo Pesquero (INIDEP).
 
@@
 Patagonian Ecosystems}: {A Journey Through Time}. \emph{Edited by} E.W.
-Helbling, M.A. Narvarte, R.A. González, and V.E. Villafañe. {Springer
-International Publishing}, {Cham}. pp. 205--231.
+Helbling, M.A. Narvarte, R.A. González, and V.E. Villafañe. Springer
+International Publishing, Cham. pp. 205--231.
 doi:\href{https://doi.org/10.1007/978-3-030-86676-1_9}{10.1007/978-3-030-86676-1\_9}.
@@
 {Reduce} the {Problem}. \emph{In} Marine {Pollution}: {New} research,
-Hofer, T.N. {Nova Science Publishers Inc.}, {New York, USA}. pp.
-339--356.
+Hofer, T.N. Nova Science Publishers Inc., New York, USA. pp. 339--356.
 
@@
 Proceedings of the National Academy of Sciences \textbf{120}(31):
-e2212061120. {Proceedings of the National Academy of Sciences}.
+e2212061120. Proceedings of the National Academy of Sciences.
 doi:\href{https://doi.org/10.1073/pnas.2212061120}{10.1073/pnas.2212061120}.
@@
 Góngora, M.E., González-Zevallos, D., Pettovello, A., and Mendía, L.
-2012. Caracterización de las principales pesquerías del golfo {San Jorge
-Patagonia}, {Argentina}. Latin american journal of aquatic research
-\textbf{40}(1): 1--11. {Pontificia Universidad Católica de Valparaíso.
-Facultad de Recursos Naturales. Escuela de Ciencias del Mar}.
-{[}accessed 14 August 2023{]}.
+2012. Caracterizaci{ó}n de las principales pesquer{í}as del golfo {San
+Jorge Patagonia}, {Argentina}. Latin american journal of aquatic
+research \textbf{40}(1): 1--11. Pontificia Universidad Cat{ó}lica de
+Valpara{í}so. Facultad de Recursos Naturales. Escuela de Ciencias del
+Mar. {[}accessed 14 August 2023{]}.
 
@@
 \bibitem[\citeproctext]{ref-Gorini2021}
-Gorini, F.L., Lukaszewicz, G., and Giussi, A.R. 2021. {Actualización de
-la estadística pesquera de peces demersales australes en el Atlántico
-Sudoccidental (período 2008-2020)}. \{Informe
-T\textbackslash\textquotesingle ecnico Oficial\}, {Instituto Nacional de
-Investigación y Desarrollo Pesquero (INIDEP)}, {Mar del Plata}.
+Gorini, F.L., Lukaszewicz, G., and Giussi, A.R. 2021. {Actualizaci{ó}n
+de la estad{í}stica pesquera de peces demersales australes en el
+Atl{á}ntico Sudoccidental (per{í}odo 2008-2020)}. \{Informe
+T\{\textbackslash\textquotesingle e\}cnico Oficial\}, Instituto Nacional
+de Investigaci{ó}n y Desarrollo Pesquero (INIDEP), Mar del Plata.
 
@@
 America} based on numerical simulations. Ocean Science \textbf{16}(2):
-271--290. {Copernicus GmbH}.
+271--290. Copernicus GmbH.
 doi:\href{https://doi.org/10.5194/os-16-271-2020}{10.5194/os-16-271-2020}.
@@
 C.N., Smith, C.R., Vacchi, M., Verde, C., and Wall, D.H. 2021. Antarctic
-ecosystems in transition \textendash{} life between stresses and
-opportunities. Biological Reviews \textbf{96}(3): 798--821.
+ecosystems in transition -- life between stresses and opportunities.
+Biological Reviews \textbf{96}(3): 798--821.
 doi:\href{https://doi.org/10.1111/brv.12679}{10.1111/brv.12679}.
@@
 marine predators to protect {Southern Ocean} ecosystems. Nature
-\textbf{580}(7801): 87--92. {Nature Publishing Group}.
+\textbf{580}(7801): 87--92. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s41586-020-2126-y}{10.1038/s41586-020-2126-y}.
@@
 \bibitem[\citeproctext]{ref-Isla2023}
-Isla, E. 2023. Animal\textendash{{Energy Relationships}} in a {Changing
-Ocean}: {The Case} of {Continental Shelf Macrobenthic Communities} on
-the {Weddell Sea} and the {Vicinity} of the {Antarctic Peninsula}.
-Biology \textbf{12}(5): 659. {Multidisciplinary Digital Publishing
-Institute}.
+Isla, E. 2023. Animal--{Energy Relationships} in a {Changing Ocean}:
+{The Case} of {Continental Shelf Macrobenthic Communities} on the
+{Weddell Sea} and the {Vicinity} of the {Antarctic Peninsula}. Biology
+\textbf{12}(5): 659. Multidisciplinary Digital Publishing Institute.
 doi:\href{https://doi.org/10.3390/biology12050659}{10.3390/biology12050659}.
@@
 Food Webs}: {A Cold Case}. \emph{In} Advances in {Ecological Research}.
-\emph{Edited by} A. Belgrano. {Academic Press}. pp. 181--223.
+\emph{Edited by} A. Belgrano. Academic Press. pp. 181--223.
 doi:\href{https://doi.org/10.1016/B978-0-12-386475-8.00005-8}{10.1016/B978-0-12-386475-8.00005-8}.
@@
 Kawaguchi, S., Nicol, S., and Press, A. 2009. Direct effects of climate
-change on the {Antarctic} krill fishery. {University Of Tasmania}.
+change on the {Antarctic} krill fishery. University Of Tasmania.
 {[}accessed 13 September 2023{]}.
@@
 2018. Impacts of rising sea temperature on krill increase risks for
-predators in the {Scotia Sea}. PLOS ONE \textbf{13}(1): e0191011.
-{Public Library of Science}.
+predators in the {Scotia Sea}. PLOS ONE \textbf{13}(1): e0191011. Public
+Library of Science.
 doi:\href{https://doi.org/10.1371/journal.pone.0191011}{10.1371/journal.pone.0191011}.
@@
 extent along the {Western Antarctic Peninsula}. Nature Communications
-\textbf{12}(1): 4948. {Nature Publishing Group}.
+\textbf{12}(1): 4948. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s41467-021-25235-w}{10.1038/s41467-021-25235-w}.
@@
 Patagonian Ecosystems}: {A Journey Through Time}. \emph{Edited by} E.W.
-Helbling, M.A. Narvarte, R.A. González, and V.E. Villafañe. {Springer
-International Publishing}, {Cham}. pp. 177--204.
+Helbling, M.A. Narvarte, R.A. González, and V.E. Villafañe. Springer
+International Publishing, Cham. pp. 177--204.
 doi:\href{https://doi.org/10.1007/978-3-030-86676-1_8}{10.1007/978-3-030-86676-1\_8}.
@@
 Martínez, P.A., Wöhler, O.C., Troccoli, G.H., Di Marco, E., and Maydana,
-L. 2022. {Descripción de las capturas incidentales de granaderos
-presentes en los lances dirigidos a merluza negra en la pesquería
-argentina de arrastre: período 2010-2019.} {Instituto Nacional de
-Investigación y Desarrollo Pesquero (INIDEP)}. {[}accessed 10 August
+L. 2022. {Descripci{ó}n de las capturas incidentales de granaderos
+presentes en los lances dirigidos a merluza negra en la pesquer{í}a
+argentina de arrastre: per{í}odo 2010-2019.} Instituto Nacional de
+Investigaci{ó}n y Desarrollo Pesquero (INIDEP). {[}accessed 10 August
 2023{]}.
@@
 {Brazil} and {Malvinas Currents} on the {Southwestern Atlantic Shelf}
-circulation. Ocean Science \textbf{6}(4): 983--995. {Copernicus GmbH}.
+circulation. Ocean Science \textbf{6}(4): 983--995. Copernicus GmbH.
 doi:\href{https://doi.org/10.5194/os-6-983-2010}{10.5194/os-6-983-2010}.
@@
 web structure in {East Antarctica}. Scientific Reports \textbf{9}(1):
-8062. {Nature Publishing Group}.
+8062. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s41598-019-44605-5}{10.1038/s41598-019-44605-5}.
@@
 Advances in {Ecological Research}. \emph{Edited by} U. Jacob and G.
-Woodward. {Academic Press}, {Burlington}. pp. 361--426.
+Woodward. Academic Press, Burlington. pp. 361--426.
 doi:\href{https://doi.org/10.1016/B978-0-12-396992-7.00006-X}{10.1016/B978-0-12-396992-7.00006-X}.
@@
 Proceedings of the Royal Society B: Biological Sciences
-\textbf{274}(1629): 3057--3067. {Royal Society}.
+\textbf{274}(1629): 3057--3067. Royal Society.
 doi:\href{https://doi.org/10.1098/rspb.2007.1180}{10.1098/rspb.2007.1180}.
@@
 web. Philosophical Transactions of the Royal Society B: Biological
-Sciences \textbf{362}(1477): 113--148. {Royal Society}.
+Sciences \textbf{362}(1477): 113--148. Royal Society.
 doi:\href{https://doi.org/10.1098/rstb.2006.1957}{10.1098/rstb.2006.1957}.
@@
 Nilsson, K.A., and McCann, K.S. 2016. Interaction strength
-revisited\textemdash clarifying the role of energy flux for food web
-stability. Theoretical Ecology \textbf{9}(1): 59--71.
+revisited---clarifying the role of energy flux for food web stability.
+Theoretical Ecology \textbf{9}(1): 59--71.
 doi:\href{https://doi.org/10.1007/s12080-015-0282-8}{10.1007/s12080-015-0282-8}.
@@
 simplifies wild food webs. Nature Climate Change \textbf{9}(8):
-611--616. {Nature Publishing Group}.
+611--616. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s41558-019-0513-x}{10.1038/s41558-019-0513-x}.
@@
 S.C., and Wernberg, T. 2018. Longer and more frequent marine heatwaves
-over the past century. Nature Communications \textbf{9}(1): 1324.
-{Nature Publishing Group}.
+over the past century. Nature Communications \textbf{9}(1): 1324. Nature
+Publishing Group.
 doi:\href{https://doi.org/10.1038/s41467-018-03732-9}{10.1038/s41467-018-03732-9}.
@@
 disciplines. Proceedings of the Royal Society B: Biological Sciences
-\textbf{287}(1926): 20200421. {Royal Society}.
+\textbf{287}(1926): 20200421. Royal Society.
 doi:\href{https://doi.org/10.1098/rspb.2020.0421}{10.1098/rspb.2020.0421}.
@@
 contribute equally to the carbon flux at the {Antarctic Peninsula}.
-Nature Communications \textbf{12}(1): 7168. {Nature Publishing Group}.
+Nature Communications \textbf{12}(1): 7168. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s41467-021-27436-9}{10.1038/s41467-021-27436-9}.
@@
 Mayor, D.J., Lucas, C.H., King, R., and Cooper, A. 2020.
-Temperature\textendash{{Induced Hatch Failure}} and {Nauplii
-Malformation} in {Antarctic Krill}. Frontiers in Marine Science
-\textbf{7}. {[}accessed 11 August 2023{]}.
+Temperature--{Induced Hatch Failure} and {Nauplii Malformation} in
+{Antarctic Krill}. Frontiers in Marine Science \textbf{7}. {[}accessed
+11 August 2023{]}.
 
@@
 {Acute}, indirect and chronic effects on the ecosystem. \emph{In}
-Advances in {Marine Biology}. {Academic Press}. pp. 1--103.
+Advances in {Marine Biology}. Academic Press. pp. 1--103.
 doi:\href{https://doi.org/10.1016/S0065-2881(01)39008-9}{10.1016/S0065-2881(01)39008-9}.
@@
 declined on a whitening {Antarctic} continental shelf. Nature
-Communications \textbf{11}(1): 2226. {Nature Publishing Group}.
+Communications \textbf{11}(1): 2226. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/s41467-020-16093-z}{10.1038/s41467-020-16093-z}.
@@
 Richardson, A.J. 2013. Global imprint of climate change on marine life.
-Nature Climate Change \textbf{3}(10): 919--925. {Nature Publishing
-Group}.
+Nature Climate Change \textbf{3}(10): 919--925. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/nclimate1958}{10.1038/nclimate1958}.
@@
 Raymond, B. 2011. A circumpolar pelagic regionalisation of the {Southern
-Ocean}. {CCAMLR WS-MPA}, {Brest}, {France}, 29 {Aug}\textendash 2 {Sep}
-2011. {Document WS-MPA-11}/6. {http://data.aad.gov.au/regionalisation}.
+Ocean}. {CCAMLR WS-MPA}, {Brest}, {France}, 29 {Aug}--2 {Sep} 2011.
+{Document WS-MPA-11}/6. {http://data.aad.gov.au/regionalisation}.
 
@@
 \bibitem[\citeproctext]{ref-RuibalNunez2020}
-Ruibal Nuñez, J. 2020. {Impacto ecológico de la actividad pesquera en
+Ruibal Nuñez, J. 2020. {Impacto ecol{ó}gico de la actividad pesquera en
 las poblaciones de condrictios en el litoral de la Provincia de Chubut y
 Golfo San Jorge}. PhD thesis, Universidad Nacional de Mar del Plata
-(UNMdP), {Argentina}.
+(UNMdP), Argentina.
 
@@
 an {Antarctic} benthic ecosystem. Science Advances \textbf{1}(10):
-e1500050. {American Association for the Advancement of Science}.
+e1500050. American Association for the Advancement of Science.
 doi:\href{https://doi.org/10.1126/sciadv.1500050}{10.1126/sciadv.1500050}.
@@
 Schejter, L., and Albano, M. 2021. Benthic communities at the marine
-protected area {Namuncurá}/{Burdwood} bank, {SW Atlantic Ocean}:
+protected area {Namuncur{á}}/{Burdwood} bank, {SW Atlantic Ocean}:
 Detection of vulnerable marine ecosystems and contributions to the
@@
 O., and Ferreyra, G.A. 2012. Response of phytoplankton dynamics to
-19-year (1991\textendash 2009) climate trends in {Potter Cove}
-({Antarctica}). Journal of Marine Systems \textbf{92}(1): 53--66.
+19-year (1991--2009) climate trends in {Potter Cove} ({Antarctica}).
+Journal of Marine Systems \textbf{92}(1): 53--66.
 doi:\href{https://doi.org/10.1016/j.jmarsys.2011.10.006}{10.1016/j.jmarsys.2011.10.006}.
@@
 Antarctic Peninsula} region. Ecography \textbf{31}(3): 289--305.
-{Blackwell Publishing Ltd}.
+Blackwell Publishing Ltd.
 doi:\href{https://doi.org/10.1111/j.0906-7590.2008.05456.x}{10.1111/j.0906-7590.2008.05456.x}.
@@
 2008. Ice {Scour Disturbance} in {Antarctic Waters}. Science
-\textbf{321}(5887): 371--371. {American Association for the Advancement
-of Science}.
+\textbf{321}(5887): 371--371. American Association for the Advancement
+of Science.
 doi:\href{https://doi.org/10.1126/science.1158647}{10.1126/science.1158647}.
@@
 food-web persistence. Proceedings of the National Academy of Sciences
-\textbf{108}(9): 3648--3652. {Proceedings of the National Academy of
-Sciences}.
+\textbf{108}(9): 3648--3652. Proceedings of the National Academy of
+Sciences.
 doi:\href{https://doi.org/10.1073/pnas.1014353108}{10.1073/pnas.1014353108}.
@@
 and function of biodiversity. Trends in Ecology \& Evolution
-\textbf{27}(12): 689--697. {Elsevier}.
+\textbf{27}(12): 689--697. Elsevier.
 doi:\href{https://doi.org/10.1016/j.tree.2012.08.005}{10.1016/j.tree.2012.08.005}.
@@
 community phase shifts. Proceedings of the Royal Society B: Biological
-Sciences \textbf{281}(1789): 20140846. {Royal Society}.
+Sciences \textbf{281}(1789): 20140846. Royal Society.
 doi:\href{https://doi.org/10.1098/rspb.2014.0846}{10.1098/rspb.2014.0846}.
@@
 \bibitem[\citeproctext]{ref-Vinuesa2005}
-Vinuesa, J.H. 2005. Distribución de crustáceos decápodos y estomatópodos
-del golfo {San Jorge}, {Argentina}. Revista de biología marina y
-oceanografía \textbf{40}(1): 7--21. {Universidad de Valparaíso. Facultad
-de Ciencias del Mar}.
+Vinuesa, J.H. 2005. Distribuci{ó}n de crust{á}ceos dec{á}podos y
+estomat{ó}podos del golfo {San Jorge}, {Argentina}. Revista de
+biolog{í}a marina y oceanograf{í}a \textbf{40}(1): 7--21. Universidad de
+Valpara{í}so. Facultad de Ciencias del Mar.
 doi:\href{https://doi.org/10.4067/S0718-19572005000100002}{10.4067/S0718-19572005000100002}.
@@
 krill {Munida} gregaria in {San Jorge Gulf}, {Argentina}.
-Investigaciones marinas \textbf{35}(2): 25--34. {Escuela de Ciencias del
-Mar. Pontificia Universidad Católica de Valparaíso}.
+Investigaciones marinas \textbf{35}(2): 25--34. Escuela de Ciencias del
+Mar. Pontificia Universidad Cat{ó}lica de Valpara{í}so.
 doi:\href{https://doi.org/10.4067/S0717-71782007000200003}{10.4067/S0717-71782007000200003}.
@@
 Williams, R.J., and Martinez, N.D. 2000. Simple rules yield complex food
-webs. Nature \textbf{404}(6774): 180--183. {Nature Publishing Group}.
+webs. Nature \textbf{404}(6774): 180--183. Nature Publishing Group.
 doi:\href{https://doi.org/10.1038/35004572}{10.1038/35004572}.
@@
 Giese, B. 2012. Enhanced warming over the global subtropical western
-boundary currents. Nature Climate Change \textbf{2}(3): 161--166.
-{Nature Publishing Group}.
+boundary currents. Nature Climate Change \textbf{2}(3): 161--166. Nature
+Publishing Group.
 doi:\href{https://doi.org/10.1038/nclimate1353}{10.1038/nclimate1353}.

### 2024-03-27 manuscript.Rmd
Ms corrections

@@
     keep_tex: yes
+  word_document: default
 bibliography: JAE_Review.bib
@@
 Furthermore, warmer temperatures increase species metabolic rates [@Brown2004].
-Changes in metabolic rates can subsequently translate into shifts in species traits (body size, @Vucic-Pestic2011; @Klein2018], biomass [@Perry2020] and distribution [@Kortsch2015].
+Changes in metabolic rates can subsequently translate into shifts in species traits (e.g.
+body size, @Vucic-Pestic2011; @Klein2018), biomass [@Perry2020], and distribution [@Kortsch2015].
 Alterations in the species body size and distributions have ripple effects on feeding interactions, for example, it can introduce new feeding interactions [@Pecuchet2020; @Verges2014], modify existing ones, and shorten energy pathways [@Bartley2019; @OGorman2019], and reduce trophic efficiencies [@Vucic-Pestic2011].

### 2024-04-18 manuscript.Rmd
Ms reorganization almost to submit

@@
 
-# The response of trophic interaction networks to multiple stressors in a marine latitudinal gradient of the Southern Hemisphere
+# The response of trophic interaction networks to multiple stressors along a large-scale latitudinal range in the Southern Hemisphere
 ## Running Title: Marine stressors in the Southern Hemisphere
@@
 
-Ecological networks offer valuable insights into community structure, key species identification, and ecosystem management for biodiversity conservation.
-Understanding how these networks react to environmental and anthropogenic stressors, especially along geographical gradients, is of increasing interest.
-This review presents a pioneering analysis of stressor responses in marine food webs from the southwest Atlantic to the Antarctic (45 - 78ºS), encompassing areas such as San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea, Potter Cove, and the Weddell Sea in Antarctica.
-Our objectives are to: 1) describe the structure of marine food webs along this axis using a network approach; 2) identify predominant environmental and anthropogenic stressors affecting each ecosystem; and 3) summarize observed food web changes and hypothesize on stressor impacts.
-Our collaborative team, comprising regional experts and global authorities on high-latitude marine food webs and stressor effects, ensures a comprehensive and credible literature review.
-We assessed the effects of stressors primarily at the species level, with notable exceptions like fisheries in San Jorge Gulf.
-Hypotheses for each study area were formulated considering: a) stressors; b) impacted parameters; c) node-level species properties; and d) network-level food web properties.
-Global warming emerges as the most common stressor across the gradient, except in the Beagle Channel and Burdwood Bank, where alien species introduction and fisheries are more influential, respectively.
-We offer specific hypotheses on how warming may affect food webs.
-Our findings highlight the benefits of a network approach in understanding and predicting stressor effects in Southern Hemisphere marine ecosystems.
-This approach provides a holistic understanding of ecological networks, enhances our ability to identify key species and interactions, and offers insights for ecosystem management and conservation in the face of various stressors.
+Ecological networks offer valuable insights into community structure, key species identification, and ecosystem management.
+Understanding how these networks respond to global change stressors is of increasing interest, especially along geographical gradients.
+This review summarizes potential stressor responses in marine food webs from the Southwest Atlantic to the Antarctic (45 - 78ºS), encompassing areas such as San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea, Potter Cove, and the Weddell Sea in Antarctica.
+The objectives are: 1) to describe the structure of marine food webs along this latitudinal axis using a network approach; 2) to identify predominant global change-related stressors affecting each ecosystem; and 3) to summarize observed food web changes and hypothesize on stressor impacts.
+The effects of stressors were primarily reviewed at the species level.
+Alternative hypotheses for each study area were formulated considering: a) main stressors; b) impacted parameters; c) node-level species properties; and d) network-level food web properties.
+Global warming emerges as the most common stressor among the studied areas across the latitudinal gradient, except in the Beagle Channel and Burdwood Bank, where alien species introduction and fisheries are more influential.
+We offer a series of alternative hypotheses on how warming may affect the food webs.
+This review emphasizes the benefits of using a network approach to understand and predict stressor effects in Southern Hemisphere marine ecosystems.
+This approach provides a holistic understanding of ecosystems, which enhances our ability to identify key species and their interactions, offering insights for ecosystem management and conservation in the face of global change stressors.
 
-Keywords: anthropogenic stressors, environmental stressors, food webs, latitudinal gradient, Southern Hemisphere
+Keywords: stressors, global warming, food webs, latitudinal gradient, Southern Hemisphere
 
@@
 Yet, only a few studies have described variation in food web structure along latitudinal gradients in marine ecosystems.
-The few that have come from the Global North [@Wood2015; @Kortsch2019; @Pecuchet2022], whereas no studies, nor meta-analyses, on geographical variation in marine food webs exist for the Global South (Southern Hemisphere).
+The few that have come from the Global North [@Wood2015; @Kortsch2019; @Pecuchet2020], whereas no studies, nor meta-analyses, on geographical variation in marine food webs exist for the Global South (Southern Hemisphere).
 
-Here we review for the first time the state-of-the-art knowledge on stressor response of marine food webs along the southwest Atlantic to Antarctic gradient (45 - 78ºS, Figure 1).
-We focus on proven and expected changes in food webs driven by stressors in selected areas along this large-scale latitudinal gradient.
-We recruited food web experts from different marine systems of Argentina and the world (see co-authors’ list).
-Throughout the year 2023 we maintained regular discussion meetings, typically held every two or three weeks.
-The aim of this review is threefold: 1) describe the complexity and structure of marine food webs along the southwest Atlantic to Antarctic axis from a network perspective; 2) identify the ongoing environmental and anthropogenic stressors for each marine ecosystem containing the food webs; and 3) review proven food web changes and elaborate hypotheses on how the identified stressors might affect food web features (e.g.
-energy flow, stability), combining information on node- and network-level properties.
-Finally, we suggest which additional data and analyses are needed to gain insights into the stressors’ effects on food web properties in the southwest Atlantic to Antarctic region.
+Here we review for the first time stressor responses of marine food webs for areas located along a Southwest Atlantic to Antarctic gradient (45 - 78ºS, Figure 1).
+We considered proven and expected changes in food webs driven by global change-related stressors in selected areas along this large-scale latitudinal range.
+The aim of this review is threefold: 1) describe the complexity and structure of marine food webs along the Southwest Atlantic to Antarctic axis from a network perspective; 2) identify the ongoing global change-related stressors for each marine ecosystem containing the food webs; and 3) review proven food web changes and elaborate on a series of alternative hypotheses on how the identified stressors might affect food web features (energy flow, stability and topology), combining information on node- and network-level properties.
+To identify the main stressors, we performed an exploratory and configurative review instead of a systematic review [@Haddaway2015], because our objective was to formulate evidenced-based hypotheses rather than providing an exhaustive list of species-level stressors for each ecosystem.
+Finally, we suggest which additional data and analyses are needed to gain insights into the stressors’ effects on food web properties in the Southwest Atlantic to Antarctic region.
 
-## 2. The structure of marine food webs in the Southwest Atlantic - Antarctic region
+________________
 
-Together, the southwest and the Atlantic sector of the Southern Ocean comprise one of the most biologically productive regions of the world's oceans [@Acha2004;  @Latorre2023].
-The referred region extends from San Jorge Gulf (45ºS) in the Patagonian shelf to the Weddell Sea (78ºS) in the Southern Ocean, and covers a well-connected oceanic latitudinal gradient [@Matano2010; @Guihou2020].
+## 2. Assessment of the food web structure and stressors in the Southwest Atlantic - Antarctic region
 
-Throughout this latitudinal gradient, many investigations have been carried out addressing the trophic ecology of specific species and prey-predator relationships [@Vinuesa2007; @Pasotti2015;  @Riccialdelli2020; @Saunders2019], but few studies have considered the complexity of the ecosystem in terms of a high resolution of species and their prey-predator interactions (but see @Jacob2011, @Marina2018, @Funes2022, @Lopez-Lopez2022, @Rodriguez2022, @Marinainrev).
-Neglecting this complexity might lead to a misunderstanding of the structure and functioning of the ecosystems, and ultimately reduce the ability to predict ecosystem responses to perturbations [@Montoya2009].
+The Southwest and the Atlantic sectors of the Southern Ocean comprise one of the most biologically productive regions of the world's oceans [@Acha2004; @Latorre2023].
+The referred region extends from San Jorge Gulf (45ºS) in the Patagonian shelf to the Weddell Sea (78ºS) in the Southern Ocean and covers a well-connected oceanic area [@Matano2010; @Guihou2020].
 
-In this review, we consider marine areas in the Southern hemisphere for which highly-resolved empirical food webs, in terms of species diversity and trophic interactions, have been previously described.
-These areas include: (1) San Jorge Gulf (45 - 47ºS, 65 - 68ºW), (2) Beagle Channel (~54ºS, 68ºW), (3) Burdwood Bank (~54ºS, 59ºW), (4) Scotia Sea (48 - 58ºS, 50ºW), (5) Potter Cove (62ºS, 58ºW, Antarctica), and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica) (Figure 1).
-The geographic locations of these marine biomes span from temperate to Antarctic, and are exposed to both environmental (sea warming, glacial retreat) and anthropogenic (fishery, pollution) stressors.
+Throughout this region, many studies address the ecology of predator-prey relationships but most of these studies are restricted to a few interacting species or certain components of the food web such as fish, crustaceans, and benthos (e.g., @Vinuesa2007, @Padovani2012, @Pasotti2015, @Riccialdelli2020, @Saunders2019, @Pasti2021, @Cordone2022).
+Only few studies consider the complexity of trophic interactions within highly resolved food webs containing hundreds of species, ranging from phytoplankton, zooplankton, benthos, fish, seabirds to whales (but see @Jacob2011, @Marina2018, @Funes2022, @Lopez-Lopez2022, @Rodriguez2022, @Marinainrev).
+Neglecting this complexity might lead to a misunderstanding of the structure and functioning of the ecosystems and ultimately reduce the ability to predict ecosystem responses to perturbations [@Montoya2009].
+
+The Southwest Atlantic - Antarctic marine biota has been and is currently subjected to a variety of stressors (e.g., sea warming, glacial retreat, ice changes, acidification, species invasion, fisheries, and contamination).
+Here, we consider a stressor as a global change variable if it causes a quantifiable change, irrespective of its direction (increase or decrease), in a biological response [@Orr2020].
+This aligns with the framework established during the early years of the International Geosphere-Biosphere Programme (IGBP) for classifying driving forces.
+These driving forces are grouped into those that modify the composition of the Earth's fluid envelopes (e.g., sea warming, acidification), and those that originate as local processes but attain global importance due to their widespread impact (e.g., species invasion, fisheries) [@Vitousek1992; @Sage2020].
+Although it is well-known that multiple stressors act in concert at any given time (e.g., warming and fishery; acidification and contaminants) [@Gutt2021], to date stressor assessments have been performed individually.
+Moreover, the potential for interactive effects of two or more stressors (synergy or antagonism) [@Cote2016] is almost unknown for the region [@Rowlands2021].
+
+In this review, we included six large marine areas in the Southern Hemisphere for which highly-resolved empirical food webs in terms of species diversity and trophic interactions have been previously described: (1) San Jorge Gulf (~45 - 47ºS, 65 - 68ºW) [@Funes2022], (2) Beagle Channel (~54ºS, 68ºW) [@Rodriguez2022], (3) Burdwood Bank (~54ºS, 59ºW) [@Marinainrev], (4) Scotia Sea (~48 - 58ºS, 50ºW) [@Lopez-Lopez2022], (5) Potter Cove (62ºS, 58ºW, Antarctica) [@Marina2018], and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica) [@Jacob2011; @Marina2024] (Figure 1).
+The geographic locations of these marine biomes span from temperate Atlantic waters to Antarctic, and are exposed to global change stressors (e.g., sea warming, glacial retreat, fishery, pollution) [@Sage2020], of which some are locally more important, e.g., fisheries in the San Jorge Gulf or glacial retreat in the Antarctic.
+
+In the following subsections, we describe the complexity and structure of the mentioned marine food webs, identify the main stressors, the species (or trophic species), and the parameters affected.
+Table 1 summarizes the properties of the marine food webs (number of nodes, trophic interactions, connectance, path length, mean trophic level, and omnivory); Table 2 provides a list of the main stressors affecting species inhabiting each area, considering: stressors’ nature, species and parameter affected, and locality.
 
@@
 
-San Jorge Gulf is the northernmost study area considered in this review.
-It is a partially enclosed basin spanning approximately 34,000 km2 and ~100 m of maximum depths, located from Cabo dos Bahias (44°55'S) to Cabo tres Puntas (47°06'S) (Figure 1).
-The shallower northern and southern ends of the Gulf (with depths ~40 m) present two prominent frontal systems.
-These systems are the areas of highest productivity [@Glembocki2015].
-The Gulf’s productivity supports large invertebrate and vertebrate fisheries [@Gongora2012], as well as marine mammal and seabird populations [@Yorio2009].
-The San Jorge Gulf food web comprises 165 nodes and 1015 trophic interactions with a connectance of 0.04.
-The percentage of top predators is 16%, 78% of intermediate nodes and 6% of basal nodes; 60% of predators are omnivorous (Table 1).
-The most connected nodes are: the Argentine red shrimp Pleoticus muelleri, the squat lobster Gimothea gregaria, squids (Illex argentinus as dominant species) and Amphipoda.
-Notably, these nodes present mid-trophic positions in the food web (3.0, 2.5, 3.6 and 2, respectively) [@Funes2022].
+### 2.1 San Jorge Gulf
 
-At a southern latitude, the Beagle Channel (54°52’S, 68°8’W) is an interoceanic passage located at the southernmost tip of South America, spanning 240 km in length and 5 km in width (~1200 km2), and a range depth of 0 - 140 m (Figure 1).
+San Jorge Gulf is the northernmost study area considered in this review (Figure 1), located from Cabo dos Bahias (44°55'S) to Cabo tres Puntas (47°06'S).
+It is a partially enclosed basin spanning approximately 34,000 km^2 and ~100 m of maximum depths.
+The gulf’s productivity supports large invertebrate and vertebrate fisheries [@Gongora2012], as well as marine mammal and seabird populations [@Yorio2009].
+Two prominent frontal systems meet in the shallower northern and southern ends of the gulf (with depths ~40 m), which are also the places of highest productivity [@Glembocki2015].
+
+The San Jorge Gulf food web contains 165 nodes (trophospecies) and 1015 trophic interactions with a connectance of 0.04.
+The percentage of top predators is 16%, 78% of the nodes are intermediate and 6% are basal; 60% of the consumers are omnivorous (Table 1).
+The most connected nodes are the Argentine red shrimp *Pleoticus muelleri*, the squat lobster *Gimothea gregaria*, squids (*Illex argentinus* as dominant species), and Amphipoda.
+Notably, these nodes are positioned at mid-trophic levels in the food web (3, 2.5, 3.6, and 2, respectively) [@Funes2022].
+
+The gulf is subject to several global change stressors (Table 2), especially fisheries [@Gonzalez-Zevallos2006; @Gonzalez-Zevallos2011; @Galvan2022].
+By discarding species, trawl fisheries add new trophic interactions to the food web which results in decreasing trait variability and stability of the system [@Funes2022; @Rincon-Diaz2021].
+Moreover, this has changed the availability of resources to some predators.
+For example, the Argentine hake *Merluccius hubbsi*, one of the main bycatch species, has become a prey item of non-diving seabirds, like the kelp gull *Larus dominicanus* [@Gonzalez-Zevallos2006] and reef fish [@Funes2019].
+Although juveniles of *M.
+hubbsi* is largely the main bycatch species, 29 cartilaginous and 69 bony local fish species were also registered as incidental catch between 2005 and 2014 [@Bovcon2013; @RuibalNunez2020].
+This level of impact has triggered a shift in the functional diversity of fish assemblages in the gulf, homogenizing their trophic function [@Rincon-Diaz2021], for example in the sites with the historical highest fishing activity, the fish assemblage experienced a relative increase in midwater fusiform species and lost variability in their depth range [@Rincon-Diaz2021].
+Other functional changes were a decrease in the maximum sizes of individual fish, together with a drop in elasmobranch biomass and an increase in crustacean biomass [@Funes2020].
+The significant increase in crustacean biomass was mainly due to the increase in the Argentine red shrimp and the squat lobster [@Funes2020].
+These species have become the most important prey for the most abundant fish in the area, the Argentine hake and the narrownose smooth-hound *Mustelus schmitti* [@Belleggia2017; @Pasti2021].
+However, since commercial fisheries ceased their activities in the San Jorge Gulf in 2015 (Annex I, Resolution CFP No 7/2018), the effects mentioned above from trawl fisheries on the structure and function of the ecosystem may have changed since then.
+Nowadays only small-scale trawling from artisanal fishery is practiced in the gulf.
+Sea warming is another important stressor in the San Jorge Gulf, because of the southward shifts of northern fish populations to the area [@Galvan2022].
+Signs of sea warming have been detected in the gulf and nearby regions.
+Anomalous bottom temperature increments of up to 2°C have been observed in the gulf since 2000 [@Isla2024], and a positive trend in sea surface temperature of 0.3°C/0.4°C per decade over a 30-year series [@Saraceno2022; @Risaro2022].
+Additionally, a positive trend in sea surface temperature (~0.5 °C increase in the last 20 years) has been reported for the Nuevo and San Jose Gulfs, both located close to and northward of the San Jorge Gulf [@Williams2023].
+The region is especially prone to be affected by climate-driven shifts in species ranges because it is situated in the ecotone of two biogeographic provinces, the Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) [@Balech2008].
+In addition to tropicalization from northern fish populations, alien species are also documented to affect demersal assemblages of fish and macroinvertebrates in the gulf [@Galvan2022].
+Finally, the gulf is exposed to urban and industrial pollution [@Verga2020].
+In particular, there is an oil monobuoy from which oil manipulation and general oil transport along the Patagonian coast registered several oil spills and chronic oil discharges [@Garcia-Borboroglu2008].
+Other marine systems impacted by the oil spill have shown extraordinary mortality events for cetacean [@Litz2014], sea turtles [@Wallace2017], and important decrease in marine bird populations [@Irons2000] sea otters [@Garrott1993] and macroalgae [@Southward1978], with cascading effects throughout the food web [@Peterson2001].
+
+### 2.2 Beagle Channel
+
+Located at a more southern latitude (~54ºS, 68ºW), the Beagle Channel (Figure 1) is an interoceanic passage at the southernmost tip of South America, spanning 240 km in length and 5 km in width (~1200 km^2), with a depth range of 0 - 140 m.
 It features complex coastlines, varying bathymetry, a prevailing west-to-east circulation pattern, and a significant longitudinal gradient of glacial freshwater discharge [@Schloss2023].
-@Bruno2023 suggests that locally produced suspended particulate organic matter (mostly composed by phytoplankton) and organic matter accumulated in the sediments (macroalgae-originated detritus) are the primary food sources for the marine ecosystem, as opposed to allochthonous materials.
-Beagle Channel food web includes 145 nodes and 1115 trophic interactions with a connectance of 0.05 (Table 1).
-The food web is suggested to have a wasp-waist structure, where the following species play a crucial role in the dynamics of the ecosystem: Fueguian sprat Sprattus fuegensis, longtail southern cod Patagonotothen ramsayi, black southern cod P.
-tessellata, frogmouth Cottoperca trigloides, and squat lobster Grimothea gregaria [@Riccialdelli2020].
-Moreover, the squat lobster has been identified as a species responsible for linking modules and connecting the entire food web [@Rodriguez2022].
+@Bruno2023 suggests that locally produced suspended particulate organic matter (mostly composed of phytoplankton) and organic matter accumulated in the sediments (macroalgae-originated detritus) are the primary food sources for the marine ecosystem, as opposed to allochthonous materials.
 
-The so-called Burdwood Bank ecosystem comprises Marine Protected Areas Namuncurá - Burdwood Bank I and II, meaning the shallow submarine plateau named Burdwood Bank with a 200 m isobath boundary, and a deep slope that reaches 4000 m in depth, respectively [@APN2022] (Figure 1).
+The Beagle Channel food web includes 145 nodes and 1115 trophic interactions with a connectance of 0.05 (Table 1).
+This food web is hypothesized to have a wasp-waist structure (i.e., the structure and dynamics of the ecosystem are regulated primarily by mid-trophic level species), where the following species play a crucial role in the dynamics of the ecosystem: Fueguian sprat *Sprattus fuegensis*, longtail southern cod *Patagonotothen ramsayi*, black southern cod *P.
+tessellata*, frogmouth *Cottoperca trigloides*, and squat lobster *G.
+gregaria* [@Riccialdelli2020].
+Moreover, the squat lobster has been identified as a species linking food web modules and connecting the entire food web [@Rodriguez2022].
+
+A main local stressor in the Beagle Channel is the introduction of invasive species (Table 2).
+Salmonidae were introduced to Tierra del Fuego in the 1930s.
+Especially, the Chinook salmon *Oncorhynchus tshawytscha* causes concern.
+The detection of this species in Tierra del Fuego dates back to April 2006, and its population has been expanding since then [@Nardi2019].
+Being a top predator, the Chinook salmon can compete for resources with several native predators in the Beagle Channel [@Correa2008], but also prey on them.
+This is the case for Notothenioids (*Eleginops maclovinus*, *Patagonotothen tessellata*, *P.
+cornucola*, *P.
+sima*, *Paranotothenia magellanica*, *Harpagifer bispinis*), the Atherinidae *Odontesthes smitti* and *O.
+nigricans*, the Fuegian sprat, and larvae of king crabs (*Lithodes antarcticus* and *Paralomis granulosa*) [@Fernandez2010].
+@Ciancio2008 observed that Chinook salmon primarily feeds on sprats in the Southern Patagonian Shelf Ecosystem area and display trophic levels comparable to those of intermediate-sized fish and cephalopod predator species, showing significant dietary overlap with the Magellanic penguin *Spheniscus magellanicus*.
+Another potential competitor for Chinook salmon in the Beagle Channel, sharing a similar diet, is the native Commerson's dolphin *Cephalorhynchus commersonii* [@Riccialdelli2013].
+In the Beagle Channel, other stressors include contaminants like metals, perfluorinated compounds, hydrocarbons, and microplastics found in animal tissue (algae, mussel, fish, and guano) and sediments [@Duarte2011; @Llorca2012].
+Carbon and carbohydrate levels in Ushuaia Bay's (54°48′S, 68°18′W) surface sediments are similar to hypertrophic ecosystems (i.e., greater input of nutrients than an eutrophic situation), along with hydrocarbons and heavy metals linked to port and industrial activities [@Gil2011; @Commendatore2012].
+@Ferreira2021 showed that the black southern cod in Ushuaia Bay may be exposed to endocrine-disrupting compounds from urban and industrial pollution.
+Moreover, @Perez2020 and @Ojeda2021 found microplastics in the Chilean mussel *Mytilus chilensis* and the sea snail *Nacella magellanica*, respectively.
+These studies link pollutants to port and industrial activities of Ushuaia; we therefore expect the area of the Beagle Channel closest to the city to be the most affected by contaminants.
+Contaminants potentially spread through the food web, magnifying the risk to higher trophic level taxa.
+In the Beagle Channel and Atlantic coast of Tierra del Fuego food webs mercury concentrations rose with benthivory, and higher mercury was found in phytoplankton and the squat lobster.
+This latter species connects pelagic and benthic habitats, so any disruption to them could disrupt the food web [@Rodriguez2022].
+@Dodino2022 found the highest mercury levels in Magellanic penguin feathers from offshore colonies in Tierra del Fuego.
+Recently, Ushuaia's kelp forests have also seen changes in composition along with a decrease in biodiversity as a result of urban pollution [@Kaminsky2024].
+It is important to note that sea warming might be a less significant stressor in the Beagle Channel compared to the other areas, as global warming is melting glaciers and the influx of cold freshwater is actually slightly cooling the seawater [@Saraceno2022].
+
+### 2.3 Burdwood Bank
+
+The so-called Burdwood Bank ecosystem comprises Marine Protected Areas Namuncurá - Burdwood Bank I and II (~54ºS, 59ºW), meaning the shallow submarine plateau named Burdwood Bank with a 200 m isobath boundary, and a deep slope that reaches 4000 m in depth, respectively [@APN2022] (Figure 1).
 Physical features in the plateau are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC [@Acha2004].
-The plateau is surrounded by steep flanks of up to 4000 m depth, protected by the Marine Protected Area Namuncurá - Burdwood Bank II (32,000 km2; ~55º - 56ºS, ~58º - 62ºW).
+The plateau is surrounded by steep flanks of up to 4000 m depth, protected by the Marine Protected Area Namuncurá - Burdwood Bank II (32,000 km^2).
 Intense upwelling and mixing occur in relation to the slope, entraining deep nutrient-rich waters into the photic layer [@Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Matano2019].
+
 The Burdwood Bank food web comprises 379 nodes and 1788 interactions, with a connectance of 0.01, and an asymmetric degree distribution (i.e.
 most of the species have a relatively low number of interactions and few species concentrate most of them).
-Almost half of the consumers are omnivores (0.48), and the network displays a small-world pattern [@Marinainrev] (Table 1).
+Almost half of the consumers are omnivores (48%), and the network displays a small-world pattern [@Marinainrev] (Table 1).
+This network pattern implies a rapid spread of a perturbation (e.g., contaminant, population fluctuation, local extinction) throughout the food web due to a short distance among species but, at the same time, a greater resistance caused by the confinement of perturbations mainly within subnetworks as a result of a high clustering coefficient [@Bornatowski2017; @Dormann2017].
 
-The Scotia Sea is a deep-sea basin, delimited by the Drake Passage to the West and by the island complex of the Scotia Arc to the North, East, and South, with an approximate extension of 1.5 x 106 km2 and a depth range of 0 - 3000 m [@Murphy2006] (Figure 1).
+The main stressors reported for the ecosystem of the Marine Protected Areas Namuncurá within Burdwood Bank I and II are related to human activities such as fisheries and contamination (Table 2).
+Several fisheries targeting demersal fish operate in the vicinity and within the Marine Protected Areas.
+The fishery of the Patagonian toothfish *Dissostichus eleginoides* has gained prominence in recent years [@Allega2020; @Gorini2021].
+Although these are regulated by the Argentinean government, incidental bycatches do occur, where demersal fish of the genera *Coelorinchus* and *Macrourus*, seabirds and benthic invertebrates (30+ taxa) are the most common bycatches [@Gaitan2016; @Martinez2022].
+Noteworthy, among the invertebrates caught, eight species are indicator taxa of vulnerable marine ecosystems [@Gaitan2016; @Schejter2021].
+However, independent assessments of these bycatches suggest no significant impact on the populations [@Gaitan2016; @Martinez2022].
+Besides bycatches, seabirds are being affected by fisheries due to discards, altering their diet; the most frequently encountered species are black-browed albatross *Thalassarche melanophris*, Southern giant petrel *Macronectes giganteus*, Cape petrel *Daption capense*, Southern royal albatross *Diomedea epomophora*, Northern giant petrel *M.
+halli*, and white-chinned petrel *Procellaria aequinoctialis* [@Tamini2023].
+Nevertheless, there is a lack of knowledge considering their role in the ecosystem and the potential joint effect of both target fish and bycatch in a broader food web framework.
+Contaminants such as microplastics and mercury occur in the water column of the Burdwood Bank ecosystem [@Cossi2021; @DiMauro2022; @Fioramonti2022].
+Microplastics are distributed along the entire water column, from surface to deep waters (3-2450 m) [@DiMauro2022].
+More importantly, microplastics were found in soft tissues of benthic macroinvertebrates (sea stars *Henricia obesa* and *Odontaster penicillatus*) and benthopelagic fish (*Patagonotothen guntheri* and *P.
+ramsayi*), which not only incorporated the contaminant from the environment through their filter-feeding system but could also get it indirectly from prey organisms already containing plastics in their tissues [@Cossi2021].
+Notably, one of the contaminated species is the longtail southern cod *P.
+ramsayi*.
+This species is part of the core group of species that drive the ecosystem through the suggested wasp-waist control [@Riccialdelli2020].
+Mercury transfer and biomagnification are occurring at a greater pace than near coastal areas such as the Beagle Channel [@Fioramonti2022].
+The Fuegian sprat *S.
+fuegensis*, a pelagic fish with a mid-trophic level in the food web, has the highest levels of mercury recorded [@Fioramonti2022].
+Considering the wasp-waist control of the Fuegian sprat in the food web [@Riccialdelli2020], a rapid and widespread contamination to the top predators is expected [@Fioramonti2022].
+Despite evidence of warming of surface, mid-water and bottom layers (100 m) in Burdwood Bank [@Franco2020], studies on the oceanographic aspects of the system are lacking.
+Warming impacts on the species and trophic interactions in Burdwood Bank are also unknown.
+
+### 2.4 Scotia Sea
+
+The Scotia Sea is a deep-sea basin (~48 - 58ºS, 50ºW), delimited by the Drake Passage to the West and by the island complex of the Scotia Arc to the North, East, and South, with an approximate extension of 1.5 x 106 km^2 and a depth range of 0 - 3000 m [@Murphy2006] (Figure 1).
 Its oceanography is dominated by the Antarctic Circumpolar Current, which is spatially structured by frontal systems [@Whitworth1980].
-The South Antarctic Circumpolar Current Front subdivides the Scotia Sea into two biogeographic regions: the Northern Scotia Sea is characterized by higher and more variable temperatures, and the Southern Scotia Sea by lower and more stable temperatures and influenced by seasonal sea ice [@Raymond2011].
-The analysis of the Northern and Southern Scotia Sea food webs shows that the former is relatively more complex than the latter: with higher species richness (218 vs 192) and interactions (10008 vs 7241) and a higher connection overall (0.21 vs 0.20).
-As expected from a more complex network, the path length is shorter in the Northern Scotia Sea food web.
-In the same sense, the Southern Scotia Sea network displays a greater proportion of omnivores and a lower mean trophic level [@Lopez-Lopez2022] (Table 1).
+The South Antarctic Circumpolar Current Front subdivides the Scotia Sea into two biogeographic regions: the Northern Scotia Sea, characterized by higher and more variable temperatures, and the Southern Scotia Sea, characterized by lower and more stable temperatures and influenced by seasonal sea ice [@Raymond2011].
 
-In the Antarctic realm, Potter Cove is a ~9 km2 fjord with a depth range of 0 - 200 m located at 25 de Mayo/King George Island (62°14’S, 58°38’W, South Shetland Islands) on the West Antarctic Peninsula (Figure 1).
+Analysis of the Northern and Southern Scotia Sea food webs shows that the former is relatively more complex in terms of number of species and links than the latter: with more species richness (218 vs 192) and interactions (10008 vs 7241) and a slightly higher connectance (0.21 vs 0.20).
+Mean path length is shorter in the Northern Scotia Sea food web, whereas the Southern Scotia Sea network displays a greater proportion of omnivores and a lower mean trophic level [@Lopez-Lopez2022] (Table 1).
+
+The Scotia Sea is a vast and heterogenous oceanic region, where especially the zone around South Georgia island represent an area of interest, here referred to as ‘Northern Scotia Sea’.
+The majority of studies analyzing the stressors’ effects come from this area (e.g., @Murphy2007; @Whitehouse2008; @Trathan2023) (Table 2).
+The main stressor of the Scotia Sea is commercial fisheries.
+Krill fishery on *Euphausia superba* not only impacts the targeted species, but also the many predators that depend on it as a food source [@Hilborn2017].
+Yet, data currently available from monitoring of krill and its predators remain insufficient, hence identifying the potential fishery impacts on the ecosystem is difficult [@Trathan2021].
+Apart from krill fishery, two other commercial fisheries operate in the Scotia Sea, targeting Patagonian toothfish species *D.
+eleginoides* and *Dissostichus mawsoni*.
+The *D.
+eleginoides* stock is linked to the stock at South Georgia (‘Northern Scotia Sea’) [@Collins2010], while the *D.
+mawsoni* stock is linked to the Antarctic continental shelf (‘Southern Scotia Sea’) [@Soeffker2022].
+Recently, @Trathan2023 has identified several concerns regarding aspects of these fisheries, highlighting that it is crucial to recognize ongoing changes such as the recovery of baleen whales and climate change.
+These factors increase uncertainty for fisheries managers, necessitating direct consideration in the management of harvested and dependent species.
+
+The Scotia Sea has experienced one of the largest levels of warming within the polar regions [@Whitehouse2008].
+Together with the Southern Annular Mode anomalies, this has caused a long-term decrease in krill abundance; more pronounced in the northern than in the southern Scotia Sea [@Murphy2007].
+Over the past 90 years, the Antarctic krill *E.
+superba* also showed an increase in mean body length [@Atkinson2019], likely altering predator-prey interactions.
+Moreover, it allows krill to reach colder feeding grounds near the seabed, with the potential to link krill to unexpected predators such as demersal fish [@Schmidt2011].
+Because of warming, the krill distribution has shifted southward [@Atkinson2019], changing the food web from a krill-based to a non-krill-based, where myctophid fish and squid are playing important roles as key species in a wasp-waist controlled system [@Saunders2019].
+While the krill distribution has shifted southward, the most abundant calanoid copepods have maintained their distribution [@Tarling2018].
+Mercury transfer and biomagnification are current processes occurring in the Scotia Sea, where the total concentration of contaminants increase with trophic level and are highest in notothenioid and myctophid fish (e.g.
+*D.
+eleginoides*, *Gymnoscopelus nicholsi*), and seabirds [@Seco2021].
+During years of low Antarctic krill abundance, predators must deal with both the stress of reduced prey availability and the concurrent rise in mercury exposure [@Seco2021].
+
+### 2.5 Potter Cove (Antarctica)
+
+In the Antarctic realm, Potter Cove is a ~9 km2 fjord with a depth range of 0 - 200 m located at 25 de Mayo/King George Island (62°S, 58°W) on the South Shetland Islands of the West Antarctic Peninsula (Figure 1).
 The cove, bordered by the Fourcade Glacier, is divided into three areas: a) the internal cove, a high glacier-influenced, soft sediment zone with a 50 m maximum depth; b) the central cove, a mixed substrate area with low meltwater influence and an 80 m maximum depth; and c) the external cove, ice-free for 60 years with a 185 m maximum depth and rocky substrate [@Jerosch2018].
@@
 With low phytoplankton biomass, macroalgae, and microphytobenthos are likely the primary food sources for secondary benthic production [@Quartino2008].
-The Potter Cove food web includes 110 nodes and 649 interactions, with an asymmetric degree distribution, and a connectance value of 0.05 (Table 1).
-It presents a modular structure (groups of species interact more strongly with each other than with species belonging to other groups), that’s positively associated with stability, since perturbation can be retained within modules [@Rodriguez2022].
+
+The Potter Cove food web includes 110 nodes and 649 interactions, and a connectance of 0.05 (Table 1).
+It presents an asymmetric degree distribution and a modular structure, i.e., groups of species interact more strongly with each other within modules than with species belonging to other modules [@Rodriguez2022].
+
+Regional warming in the West Antarctic Peninsula recorded in the last half-century [@Chown2022] has been one of the main stressors driving changes in Potter Cove (Table 2), a system highly dependent on glacier and sea ice dynamics [@Deregibus2017].
+This has caused drastic environmental and biological transformations such as shifts in dominance within the benthic community [@Quartino2013; @Sahade2015; @Schloss2012].
+In Potter Cove, there has been a decreasing trend in total sea ice cover since 1991 [@Schloss2012].
+Changes in the annual timing of landfast ice formation and the breakup of the sea ice cover has multiple effects on species [@Michel2019].
+Warmer winters and springs result in earlier sea ice melt, causing an abrupt increase in the light available for benthic primary producers [@Deregibus2020].
+Sea ice also mediates physical disturbances to the benthos by influencing sedimentation and iceberg scouring.
+These factors affect the production of macroalgae, albeit in opposite ways [@Deregibus2017], and microphytobenthos [@Hoffmann2019].
+On the other hand, sea ice is an important habitat for diatoms and their associated consumers, including copepods and the Antarctic krill [@Flores2012], and thus important for bentho-pelagic nutrient and carbon cycling during winter.
+Additionally, a decrease in winter sea ice cover produces an increase in physical perturbation on benthic shallow communities in coastal shallows due to ice scouring [@Deregibus2017].
+The glacier surrounding Potter Cove has been receding at an increasing rate since 1950 [@Ruckamp2011], which has caused a massive discharge of sediment-laden meltwater [@Meredith2018].
+Large quantities of suspended particles affect growth, survival, and reproduction of benthic species.
+This led to a major shift in the benthic community structure, from a filter feeders–ascidian domination to a mixed assemblage with scavengers and opportunistic species [@Sahade2015], and the metabolic balance in benthos went from net autotrophy to heterotrophy [@Braeckman2021].
+Additionally, massive stranding events of the tunicate *Salpa thompsoni* and the Antarctic krill linked to the presence of glacial meltwater have been reported [@Fuentes2016].
+Rising temperatures leading to ice and glacial melting has also substantial impacts on pelagic primary productivity, since it reduces water salinity, affecting water column stratification, light penetration and nutrient availability for photosynthesis [@Schloss2012].
+In Potter Cove, changes in biomass of most phytoplankton species have been observed under heat wave conditions, resulting in a shift from a microplankton to a nanoplankton dominated community [@Antoni2020; @Latorre2023].
+This means that in areas strongly affected by glacier melt, the planktonic food web is dominated by the microbial loop (i.e., ciliates and heterotrophic dinoflagellates preys upon nanophytoplankton, which are sequentially available prey for small omnivorous copepods), instead of being predominantly herbivorous [@Garcia2016; @Garcia2019].
+In addition, phytoplankton species under these warming conditions showed a decrease in metabolic rate and in the quality of the fatty acid composition [@Latorre2023].
+
+### 2.6 Weddell Sea (Antarctica)
 
@@
 The water depth ranges from 200 to 500 m, with shallower regions being covered by continental ice that forms the coastline along the eastern and southern parts of the Weddell Sea.
-Within this shelf area, exists a complex three-dimensional benthic habitat characterized by substantial benthic biomasses and an intermediate to high diversity when compared to benthic boreal communities [@Teixido2002].
-The Weddell Sea food web exhibits a high level of network complexity, featuring the greatest number of nodes (490) and trophic interactions (16041) among the analyzed food webs in this review (Table 1).
-Its connectance (0.07) and other structural properties are intermediate compared to the other food webs.
-Recently, the interaction strengths of this food web were estimated, revealing the presence of numerous weak and few strong interactions, which is consistent with findings in other complex food webs [@Nilsson2016].
-Notably, this asymmetric distribution of interaction strength is likely to promote community persistence.
+The shelf area is characterized by a complex three-dimensional benthic habitat, substantial benthic biomasses, and an intermediate to high diversity [@Teixido2002].
+
+The Weddell Sea food web exhibits a high level of network complexity, featuring the greatest number of nodes (490) and trophic interactions (16041) among the marine food webs of the Southern Hemisphere (Table 1).
+Its connectance (0.07), mean trophic level (2.62) and omnivory (51%) are intermediate compared to the other food webs (Table 1).
+Recently, the interaction strengths of this food web were estimated, revealing the presence of numerous weak and few strong interactions [@Marina2024].
+
+In the Weddell Sea, the main stressors are related to warming impacts (sea warming, sea ice extent, iceberg scouring) (Table 2), where sea warming has been substantial since the early 1980s [@Turner2020].
+For example, in 2017, the mean temperature for February reached 1.45°C, the highest monthly mean ever recorded, i.e., 0.56°C above the climatological mean [@Turner2020].
+Warming has caused spatial and temporal reductions in sea ice, impacting both pelagic and benthic communities [@Constable2014; @Gutt2021].
+Since the start of satellite imaging in 1978, sea ice extent has reached new record lows.
+Some of the most pronounced impacts of decreasing sea ice are negative changes in primary productivity [@Atkinson2004] and declines of the Antarctic krill.
+Moreover, reduced sea ice cover allows increased access to krill by its predators [@Kawaguchi2009], which further contributes to its decline.
+Some outcomes of the krill decline are reduced energy intake by higher trophic levels such as humpback whales *Megaptera novaeangliae* [@Pallin2023, @Braithwaite2015] which rely heavily on krill for foraging, as well as reduced carbon export due to fewer fecal pellets [@Pauli2021].
+Many higher trophic level species in the Weddell Sea are greatly impacted by sea ice reductions due to loss of habitat and food source availability, such as the Antarctic petrel *Thalassoica antarctica* - one of the most abundant seabirds in the Weddell Sea [@Orgeira2021].
+Other impacted sea bird species are the emperor penguin *Aptenodytes forsteri*.
+Reductions in sea ice constrain its population as evidenced by recent observations in the Bellingshausen Sea region [@Fretwell2023].
+The Arctic tern *Sterna paradisaea* spends the summer in the Weddell Sea exploiting krill swarms under receding ice edges.
+Thus, continued warming is expected to gradually erode the abundance and distribution of marine seabirds in the Weddell Sea [@Orgeira2021].
+Many marine mammals depend on for breeding and foraging such as the Weddell and Crabeater seals (*Leptonychotes weddellii* and *Lobodon carcinophagus*) [@Wege2021] and the Humpback whale.
+Reduced sea ice can significantly affect the breeding success of seals [@Wege2021] and body condition of whales [@Turner2020].
+Notothenioid fish, with *Pleuragramma antarcticum* being the most abundant species, confront numerous stressors such as sea warming, sea ice decline, and ocean acidification, posing significant threats to their survival.
+While certain species exhibit physiological plasticity to cope with increased oxygen demand, most notothenioid fish are stenothermal and incapable of adjusting their metabolic functioning [@Mintenbeck2012].
+Projections suggest that the preferred thermal habitat of the Antarctic toothfish, *Dissostichus mawsoni*, an important fish species in the Weddell Sea ecosystem, may contract over the next three decades, underscoring the potential impact of global warming on these species [@Constable2014].
+Iceberg scouring is a major factor in driving the high biodiversity of benthic communities in the Weddell Sea [@Gutt2001].
+Even at 600 m depths, iceberg scouring has a strong effect on the benthic environment, disrupting the upper layers of the seabed and removing macrofauna.
+This patchy disturbance and distribution pattern occurs roughly every 200 square meters on the Antarctic continental shelf.
+Global warming is predicted to increase iceberg scouring frequency [@Gutt2001a; @Smale2008a], disrupting the environment [@Smale2008] with the potential for tipping points  [@Gutt2015].
+________________
 
@@
 Complexity and structure properties of the marine food webs considered in the present review.
-Refer to Table 2 for definition of properties.
+Refer to Table S2 for definition of properties.
 mean TL: mean trophic level.
@@
 
-## 3. Environmental and anthropogenic stressors in the Southwest Atlantic - Antarctic region
-
-A stressor is any environmental or anthropogenic variable that causes a quantifiable change, irrespective of its direction (increase or decrease), in a biological response [ @Orr2020].
-In the light of this, the southwest Atlantic - Antarctic marine biota has been and is currently subjected to a variety of stressors (e.g.
-sea warming, glacial retreat, ice changes, acidification, species invasion, fisheries, and contamination).
-Although it is well-known that multiple stressors act in concert at any given time (e.g.
-warming and fishery; acidification and contaminants) [@Gutt2021], to date stressor assessments have been performed individually.
-Moreover, the potential for interactive effects of two or more stressors (synergy or antagonism) [ @Cote2016] is almost unknown for the region [@Rowlands2021].
-
-In the following subsections, we describe the main environmental and anthropogenic stressors, and the species (or trophic species) and parameters affected reported for the marine ecosystems that contain the food webs considered in this review.
-In Table S2 we provide an exhaustive list of all stressors affecting species inhabiting each area, considering: the type of stressor, species and parameter affected, and locality.
-
-<!-- Aca estaba la tabla 2 -->
-
-### 3.1 San Jorge Gulf
-
-San Jorge Gulf experienced several environmental and anthropogenic stressors (Table S2).
-Trawl fisheries discard several species and add new trophic interactions to the food web which resulted in a decrease in trait variability and the stability of the system [@Funes2022; @Rincon-Diaz2021].
-Moreover, it changed the availability of prey to several predators.
-For example, Merluccius hubbsi one of the main bycatch species, became prey item to non-diving seabirds, like the kelp gull Larus dominicanus [@Gonzalez-Zevallos2006] and reef fishes [@Funes2019].
-Although juveniles of M.
-hubbsi are largely the main bycatch item, 29 other cartilaginous and 69 bony local fish species were also registered as incidental catch between 2005 and 2014 [@Bovcon2013; @RuibalNunez2020].
-This level of impact triggered a shift in the functional diversity of the assemblages homogenizing the trophic function of fishes [@Rincon-Diaz2021].
-Other functional changes were a decrease in the maximum sizes of individual fish, together with a drop in elasmobranchs biomass and an increase in crustaceans biomass [@Funes2020].
-The significant increase in crustacean biomass was mostly due to the increase in Pleoticus muelleri and Grimothea gregaria populations [@Funes2020].
-These species rapidly became the most important prey for the most abundant fishes in the area: M.
-hubbsi and Mustelus schmitti [@Pasti2021].
-However, the above-mentioned effects of trawl fisheries on the structure and function of the San Jorge Gulf community may have changed again, since the fisheries ceased activity in 2015 (Annex I, Resolution CFP No 7/2018), remaining a small trawling artisanal fishery.
-
-Sea warming is another important environmental stressor in the San Jorge Gulf, because of the southward shifts of northern fish populations to the Gulf [@Galvan2022].
-The San Jorge Gulf is especially prone to be affected by climate-driven shifts in species ranges, because it is located in the ecotone between two biogeographic provinces, the Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) [@Balech2008].
-In addition to this tropicalization from northern fish populations, alien species are also documented to affect the demersal assemblage (fish and macroinvertebrates) in the Gulf [@Galvan2022].
-Finally, San Jorge Gulf is exposed to urban and industrial pollution due to an oil monobuoy from which oil manipulation and general oil transport along the Patagonian coast registered several oil spills and chronic oil discharges [@Garcia-Borboroglu2008].
-Other marine systems impacted by oil spill showed an important decrease in marine bird populations [@Irons2000], seals and macroalgae (e.g.
-@Paine1996), with examples of cascading effects throughout the food web [@Peterson2001].
-
-### 3.2 Beagle Channel
-
-A main anthropogenic stressor in the Beagle Channel is the introduction of invasive species (Table S2).
-Salmonidae were introduced to Tierra del Fuego in the 1930s.
-Especially Chinook salmon Oncorhynchus tshawytscha causes concern.
-The detection of Chinook salmon in Tierra del Fuego dates back to April 2006, and its population has been expanding since then [@Nardi2019].
-Being a top predator Chinook salmon can compete with several native species in the Beagle Channel [@Correa2008], and prey over native species such as Notothenioids (Eleginops maclovinus, Patagonotothen tessellata, P.
-cornucola, P.
-sima, Paranotothenia magellanica, Harpagifer bispinis), the Atherinidae Odontesthes smitti and O.
-nigricans, the Fuegian sprat Sprattus fuegensis, and larvae of king crabs (Lithodes antarcticus and Paralomis granulosa) [@Fernandez2010].
-@Ciancio2008 observed that Chinook salmon in the Southern Patagonian Shelf Ecosystem Area primarily feed on sprats and display trophic levels comparable to those of intermediate-sized fish and cephalopod predators species, showing significant dietary overlap with Magellanic penguins (Spheniscus magellanicus).
-Another potential competitor for Chinook salmon in the Beagle Channel is the Commerson's dolphin (Cephalorhynchus commersonii), which shares a similar diet [@Riccialdelli2013].
-
-In the Beagle Channel, other anthropogenic stressors include contaminants like metals, perfluorinated compounds, hydrocarbons, and microplastics found in animal tissue and sediments.
-Some studies reported varying heavy metal levels in sea mussel tissues and sediments, indicating bioavailability differences [@Duarte2011].
-Other research found similar carbon and carbohydrate levels in Ushuaia Bay's surface sediments to those in hypertrophic ecosystems, along with hydrocarbons and heavy metals linked to port and industrial activities [@Gil2011].
-@Commendatore2012 identified three distinct hydrocarbon accumulation zones in the Bay.
-@Llorca2012 found high levels of perfluorinated compounds in algae, fish, and guano.
-@Ferreira2021 showed that black southern cod in Ushuaia Bay may be exposed to endocrine-disrupting compounds from urban and industrial pollution.
-@Perez2020 and @Ojeda2021 found microplastics in M.
-edulis chilensis and Nacella magellanica, respectively.
-These studies link pollutants to Ushuaia (54°48′S 68°18′W) and its port and industrial activities.
-We expect the Beagle Channel area closest to the city to be most affected.
-Contaminants can spread through the food web, magnifying the risk to higher-level organisms.
-@Fioramonti2022 studied mercury transfer in three southwest Atlantic Ocean food webs and found biodilution in the Beagle Channel and Atlantic coast of Tierra del Fuego webs.
-However, mercury concentrations rose with benthivory in these webs, and higher mercury was found in phytoplankton and Grimothea gregaria.
-Squat lobsters connect pelagic and benthic habitats, so any disruption to them could disrupt the food web [@Rodriguez2022].
-@Dodino2022 found the highest mercury levels in Magellanic penguin feathers from offshore colonies in Tierra del Fuego.
-Recently, Ushuaia's kelp forests have seen a decrease in biodiversity and changes in macroalgae composition due to urban pollution [@Kaminskyinprep].
-
-### 3.3 Burdwood Bank
-
-The stressors reported for the ecosystem of the Marine Protected Areas Namuncurá within Burdwood Bank I and II are mostly anthropogenic; there is a lack of studies focusing on the environmental stressors that are known to be occurring at a regional scale (e.g.
-sea surface warming, @Franco2020) (Table S2).
-Several fisheries targeting demersal fishes operate in the vicinity and within the ecosystem of the Marine Protected Areas (i.e.
-Marine National Reserve management category).
-The Patagonian fisheries  on the toothfish Dissostichus eleginoides  has gained prominence in recent years [@Allega2020; @Gorini2021].
-Although these are regulated by the Argentinean government, incidental catches do occur, where demersal fishes of the genera Coelorinchus and Macrourus, seabirds and benthic invertebrates (30+ taxa) are the most common bycatches [@Gaitan2016; @Martinez2022].
-Noteworthy, among the invertebrates caught, 8 species are indicator taxa of vulnerable marine ecosystems [@Gaitan2016; @Schejter2021].
-Independent assessments of these bycatches suggest no significant impact on the communities [@Gaitan2016; @Martinez2022].
-Besides bycatch, species of seabirds are being affected by the fishery due to discards, altering its diet; the most frequently encountered species are Black-browed albatross Thalassarche melanophris, Southern giant petrel Macronectes giganteus, Cape petrel Daption capense, Southern royal albatross Diomedea epomophora, Northern giant petrel M.
-halli, and White-chinned petrel Procellaria aequinoctialis [@Tamini2023].
-Nevertheless, there is a lack of knowledge considering the species’ role in the ecosystem and the potential joint effect of both target fishes and bycatch in a broader food web framework.
-
-Anthropogenic contaminants such as microplastics and mercury are present in the water column of the Burdwood Bank ecosystem [@Cossi2021; @DiMauro2022; @Fioramonti2022].
-Microplastics are distributed all along the water column, from surface to deep waters (3-2450 m) [@DiMauro2022].
-More importantly, microplastics were found in soft tissues of benthic macroinvertebrates (sea stars Henricia obesa and Odontaster penicillatus) and benthopelagic fishes (Patagonotothen guntheri and P.
-ramsayi), which not only incorporated the contaminant from the environment through their filter-feeding system but could also get it indirectly from prey organisms already containing plastics in their tissues [@Cossi2021].
-Notably, one of the contaminated species, the long tail southern cod Patagonotothen ramsayi, is part of the core group of species that drive the ecosystem through the suggested wasp-waist control [@Riccialdelli2020].
-Mercury transfer and biomagnification are ongoing processes in the ecosystem, which are occurring at a greater pace than near coastal areas (Beagle Channel) [@Fioramonti2022].
-It’s important to note that the Fuegian sprat Sprattus fuegensis, a pelagic fish with a mid-trophic level in the food web, presented the highest levels of mercury [@Fioramonti2022].
-Considering the wasp-waist control of the Fuegian sprat in the food web [@Riccialdelli2020], a rapid and widespread contamination to the top predators is expected [@Fioramonti2022].
-
-In recent years, licenses for seismic studies and exploration of hydrocarbon resources have been granted all along the northwestern limit of the Marine Protected Areas (Secretaría de Gobierno de Energía Res.
-Nº 65/2018).
-Although effects from these types of surveys on marine mammals and seabirds are well-known for other regions of the world [@Nowacek2015], there is no particular knowledge for this ecosystem.
-However, several documents warn of the potential negative effects this may have on the species inhabiting the Burdwood Bank area [@Allega2019; @deHaro2022].
-
-Despite evidence of warming at surface, mid-water and bottom layers (100 m) in Burdwood Bank [@Franco2020], specific studies on the oceanographic aspects of the system are lacking.
-In this sense, there is a big question mark about the environmental stressors impact on the species and trophic interactions in Burdwood Bank.
-
-### 3.4 Scotia Sea
-
-The Scotia Sea is a vast and heterogenous oceanic region, where especially the areas around South Georgia island represents an area of interest, here referred to as ‘Northern Scotia Sea’.
-The majority of studies analyzing the stressors’ effects come from this area.
-
-The Scotia Sea has experienced one of the largest levels of warming within the polar regions [@Whitehouse2008].
-Together with the Southern Annular Mode anomalies  this has caused a long-term decrease in krill abundance; more pronounced in the northern than in the southern Scotia Sea [@Murphy2007].
-Over the past 90 years, the krill also showed an increase in mean body length [@Atkinson2019], which may also alter predator-prey interactions and allow reaching cooler feeding grounds near the seabed, with the potential to link krill to unexpected predators [@Schmidt2011].
-Another consequence of the mentioned environmental stressors, is a change in krill distribution due to a southward contraction [@Atkinson2019].
-It is noteworthy here, that the distributional shift has not affected all species inhabiting the Northern Scotia Sea, and most abundant calanoid copepods have maintained their distribution [@Tarling2018].
-Considering the above, food web models of the Northern Scotia Sea have suggested shifts in the structure and functioning of the food web, from krill-based to non-krill-based, where myctophid fishes and squid are playing important roles [ @Saunders2019].
-
-The principal anthropogenic stressor of the Scotia Sea is commercial fisheries.
-Krill fishery not only stresses the targeted species, but also the many predators that depend on it as a food source [@Hilborn2017].
-Yet, data currently available from monitoring of krill and its predators remain insufficient, hence identifying the potential fishery impacts on the ecosystem is difficult [@Trathan2021].
-Apart from krill fishery, two other commercial fisheries operate in the Scotia Sea, targeting Patagonian toothfish species Dissostichus eleginoides and D.
-mawsoni.
-The D.
-eleginoides stock is linked to the stock at South Georgia (‘Northern Scotia Sea’) [@Collins2010], while the D.
-mawsoni stock is linked to the Antarctic continental shelf (‘Southern Scotia Sea’) [@Soeffker2022].
-Despite the fact that the mentioned fisheries are certified by the Marine Stewardship Council standards, @Trathan2023 identified several concerns regarding aspects of fisheries itself, other species' population status (i.e.
-recovery of baleen whales), and environmental stressors (i.e.
-sea warming), which could have synergistic effects on the food web structure and functioning that are still unknown.
-
-Mercury transfer and biomagnification are current processes occurring in the Scotia Sea, where the total concentration of contaminants increase with trophic level and are highest in notothenioid and myctophid fishes (e.g.
-Dissostichus eleginoides, Gymnoscopelus nicholsi), and seabirds [@Seco2021].
-During years of low Antarctic krill abundance, predators must deal with both the stress of reduced prey availability and the concurrent rise in mercury exposure [@Seco2021].
-
-### 3.5 Potter Cove (Antarctica)
-
-Regional warming in the last half century has been one of the main factors driving changes in Potter Cove (Western Antarctic Peninsula) [@Chown2022].
-Sudden environmental changes have occurred, such as sea surface temperature increase, salinity decrease, suspended particulate matter loading and chlorophyll-a increase, all linked to climatic cycles (Southern Annular Mode and El Niño Southern Oscillation) [@Schloss2012].
-Particularly, sea warming has produced drastic environmental and biological transformations (e.g.
-shifts in dominance of benthic community) in the Potter Cove ecosystem [@Quartino2013; @Sahade2015; @Schloss2012], a system highly dependent on sea-ice dynamics (Table S2).
-In Potter Cove, total sea ice cover has decreased since 1991 [@Schloss2012].
-Changes in the annual timing of landfast ice formation and breakup of the sea ice cover has multiple effects on species in the food web [@Michel2019].
-Warmer winters and springs result in earlier sea-ice melt, causing an abrupt increase in the light available benthic primary producers [@Deregibus2020].
-Sea ice also mediates physical disturbances to the benthos by influencing sedimentation and iceberg scouring.
-These factors affect the production of macroalgae, albeit in opposite ways [ @Deregibus2017], and microphytobenthos [@Hoffmann2019].
-On the other hand, sea ice is an important habitat for diatoms and its associated consumers, including copepods and krill [@Flores2012], and thus important for bentho-pelagic nutrient and carbon cycling during winter.
-Additionally, a decrease in winter sea ice cover produces an increase in physical perturbation on benthic shallow communities in coastal shallows due to ice scouring [@Deregibus2017].
-The glacier surrounding Potter Cove has been receding at an increasing rate since 1950 [@Ruckamp2011], which has caused a massive discharge of sediment-laden meltwater [@Meredith2018].
-Large quantities of suspended particles affect growth, survival and reproduction of benthic species.
-This had led to a major shift in the benthic community structure, from a filter feeders–ascidian domination to a mixed assemblage with scavengers and opportunistic species [@Sahade2015], and the metabolic balance in benthos went from net autotrophy to heterotrophy [@Braeckman2021].
-Additionally, massive stranding events of the tunicate Salpa thompsoni and the euphausiid Euphausia superba (krill) linked to the presence of glacial meltwater have been reported [@Fuentes2016].
-Rising temperatures leading to ice and glacial melting has also substantial impacts on pelagic primary productivity, since it reduces water salinity, affecting water column stratification, light penetration and nutrient availability for photosynthesis [@Schloss2012].
-In Potter Cove, changes in biomass of most phytoplankton species have been observed under heat wave conditions, resulting in a shift from a microplankton to a nanoplankton dominated community [@Antoni2020; @Latorre2023].
-This means that in areas strongly affected by glacier melt, the planktonic food web is dominated by the microbial loop (ciliates and heterotrophic dinoflagellates preys upon nanophytoplankton, which are sequentially available prey for small omnivorous copepods), instead of being predominantly herbivorous [@Garcia2016; @Garcia2019].
-In addition, phytoplankton species under these warming conditions showed a decrease in metabolic rates and in the quality of the fatty acids composition [@Latorre2023].
-
-### 3.6 Weddell Sea (Antarctica)
-
-In the Weddell Sea several stressors have already been triggered by global warming effects (Table S2), from which spatial and temporal reduction in sea ice is suggested to be driving changes in pelagic and benthic communities [@Constable2014; @Gutt2021].
-Sea ice extent has reached new record lows since the satellite era began in 1978.
-Sea warming has been substantial in recent years: in 2017 the mean temperature for February reached 1.45°C, the highest monthly mean ever recorded (0.56°C above the climatological mean) [@Turner2020].
-In this context, it has been suggested that Antarctic krill Euphausia superba has already declined as a result of productivity changes caused by sea ice declines [@Atkinson2004].
-Declining sea ice cover allows increased access to krill by predators [@Kawaguchi2009], which further contributes to decreased krill abundances.
-This in turn can result in reduced carbon export due to decreased fecal pellets from krill [@Pauli2021].
-
-On the other hand, sea ice loss increases light availability, triggering primary production by phytoplankton in the short-term [@Pineda-Metz2020].
-Furthermore, a warmer and more stable water column with a shallow upper mixed layer, is expected to enhance the dominance of cryptophytes over diatoms which may favor salp populations over krill populations; thereby reducing the magnitude of energy transfer to higher trophic levels and the seabed [@Isla2023].
-
-Higher trophic level species are expected to respond differently to global warming in the Weddell Sea.
-In this regard, Notothenioid fishes (e.g.
-Pleuragramma antarcticum) face multiple stressors (sea warming, sea ice decline, ocean acidification) that threaten their survival.
-While some species exhibit physiological plasticity to compensate for increased oxygen demand, most notothenioid fishes are stenothermal and unable to adjust their metabolic functioning [@Mintenbeck2012].
-It is anticipated that the thermal habitat preferred by the Antarctic toothfish Dissostichus mawsoni could undergo contraction in the coming three decades [@Constable2014], further emphasizing the potential impact of global warming effects on these species.
-Marine mammals, Weddell and crabeater seals (Leptonychotes weddellii and Lobodon carcinophagus), exhibit varying levels of sensitivity.
-The latter exhibits a preference for breeding in close proximity to krill swarms, and thus is particularly susceptible to reductions in sea ice concentrations and sea surface temperatures.
-Rescued sea ice can significantly affect their post- and future breeding foraging success [@Wege2021].
-In addition, the Antarctic petrel Thalassoica antarctica, which is one of the most abundant seabirds in the area, is a sea ice dependent forager and breeder [@Orgeira2021]; therefore the loss of this habitat will degrade its foraging success and reproductive output over time.
-The snow petrel Pagodroma nivea also relies heavily on sea ice for foraging and its colonies in the Weddell Sea may be affected.
-The emperor penguin Aptenodytes forsteri uses sea ice for breeding; any reductions could constrain its populations, as evidenced by recent observations in the Bellingshausen Sea region [@Fretwell2023].
-The Arctic tern Sterna paradisaea spends the summer in the Weddell Sea exploiting krill swarms under receding ice edges, then declines in ice cover may reduce prey availability and quality of molting habitats.
-Continued warming is thus expected to gradually erode the abundance and distribution of these 'primary species' that dominate the avifauna of the Weddell Sea through loss of critical sea ice habitat [@Orgeira2021].
-Variations in sea ice extent have implications for great whales, such as the Humpback whale Megaptera novaeangliae, since their primary prey resource is the Antarctic krill [@Braithwaite2015].
-Decreased winter ice coverage results in reduced suitable habitat and lower krill abundance [@Braithwaite2015], with flow-on effects for whale body condition observed historically in harvest data.
-With climate projections indicating ongoing sea ice losses, further threats to critical krill populations pose risks to the energy intake and reproductive success and long-term viability of humpback whale populations dependent on consistent Antarctic feeding [@Pallin2023].
-
-<!-- Iceberg scouring increases -->
-Iceberg scouring is a major factor in the high biodiversity of benthic communities in the Weddell Sea [@Gutt2001].
-Even at 600 m depths, iceberg scouring has a strong effect on the benthic environment, disrupting the upper layers of the seabed and removing macrofauna.
-This patchy disturbance and distribution pattern occurs roughly every 200 square meters on the Antarctic continental shelf.
-Global warming is predicted to raise iceberg scouring frequency [@Gutt2001a; @Smale2008a], disrupting the environment [@Smale2008].
-@Gutt2015 expects tipping points are significant due to these effects and lack of knowledge.
-
-<!-- Multiple stressors: The Southern Ocean and nearshore Antarctic waters are also warming, sea-ice is predicted to decline, winds are strengthening, upwelling and nutrient availability is changing, mixed layer depths are shallowing, and the ocean fronts are moving southward (Deppeler & Davidson, 2017; Stark, Raymond, Deppeler, & Morrison, 2019).
-These stressors interact, resulting in additive, synergistic, or antagonistic effects on organisms (Boyd, Brown, Schrum, & Krishnakumar, 2015).
-[@Hancock2020]
-
-Climate change is likely to cause early breakout of seasonal sea ice in parts of Antarctica, which will dramatically increase the amount of light reaching shallow seabed.
-This is predicted to result in ecological regime shifts, in which invertebrate-dominated communities are replaced by macroalgal beds [@Clark2015].-->
-
-## 4. From species’ stressors to food web effects
+## 3. From species’ stressors to food web effects: a qualitative approach
 
@@
 
-Environmental and anthropogenic stressor effects in the southwest and the Atlantic sector of the Southern Ocean have been mostly assessed individually and at the organism and/or population, i.e., at the node level (Table S2), with one exception: the effect of fisheries in the San Jorge Gulf food web (see section below for more details).
-To address the most plausible stressors effects on the selected food webs, given the current information, we built hypotheses for each study area.
+Global change stressor effects in the Southwest and the Atlantic sector of the Southern Ocean have been mostly assessed individually and at the organism and/or population, i.e., at the node level (Table 2), with one exception: the effect of fisheries in the San Jorge Gulf food web (see section below for more details).
+To address the most plausible effects of the main stressors on the selected food webs, given the current information, we formulated a series of alternative hypotheses for each study area.
 To this aim, we developed a theoretical framework considering the following: a) stressor(s), b) parameter(s) affected, c) node-level properties of the affected species, and d) network-level properties of the food web.
 
-We considered that a stressor will affect one of the following species’ characteristics or parameters: metabolism, biomass, distribution, and diet (Figure 2).
-‘Metabolism’ refers to any change related to metabolic rate, such as reproduction, hatching, larval development, growth and mortality, and contamination due to pollutants (e.g.
+We considered that a stressor will affect one of the following species’ characteristics or parameters: metabolism, population biomass, distribution, and diet (Figure 2).
+‘Metabolism’ refers to any change related to metabolic rate, such as reproduction, hatching, larval development, growth and mortality (e.g.
 growth  effect in filter-feeders due to sediment in water column in Potter Cove; endocrine disruption in fish due to urban pollutants in Beagle Channel).
-‘Biomass’ indicates an effect at the population level, where the density/abundance is being impacted (e.g.
+‘Population biomass’ indicates an effect at the population level, where the density/abundance is being impacted (e.g.
 abundance decreases in macrobenthos due to iceberg scouring in Weddell Sea).
@@
 
-<!--
-### Leo input
-
-The propagation of stressor-induced perturbations across food webs is significantly influenced by species interactions and cascading effects.
-One way to consider which are the species that more sensitive to these perturbations is the degree, which quantifies the number of connections a species has, provides a robust prediction of species importance and correlates with other indices that include indirect interactions [@Jordan2006].
-There are various definitions for keystone species, and network position alone may not be the sole determinant.
-Considering abundance or biomass is also crucial as suggested by simulation studies [@Zhao2016].
-
-The impacts of stressors can vary in direction and magnitude as they move through the food web, due to differences in timescales and interacting species [@Jackson2021].
-One approach to measure the effects of changes in species populations on the remaining species in a food web is the method of the inverse Jacobian matrix, which requires the knowledge of interaction strengths [@Montoya2009].
-Using this approach it was found that the magnitude of net effects is negatively correlated with the  degree (sum of predator and prey links) of the perturbed species in most analyzed food webs.
-Species with few connections have stronger net effects on other species within food webs compared to highly connected species.
-Highly connected species may possess compensatory mechanisms, such as enhanced apparent competition, that regulate their biomass and mitigate the impacts of disturbances [@Montoya2009].
-Similarly, studies by [@Zhao2016] have shown that the extinction of highly connected species in food webs, which have many feeding interactions, may not necessarily pose the greatest threat to biodiversity loss.
-Instead, the strength of feeding links and the prevalence of indirect interactions have a stronger influence on food web stability.
-Both quantitative fluxes and species dispersing their effects across many links are important considerations in biodiversity conservation.
-The potential for highly connected species to act as keystone species may have been overestimated in previous studies.
-
-Recent studies suggest that significant apex predators [@Woodward2010; @OGorman2009] and marine mammals would exhibit high susceptibility to stressors and an inclination toward experiencing synergistic impacts .
-This susceptibility was largely attributed to their role in food chains as primary predators, as well as their involvement in omnivory and exploitative competition interactions.
-Predators species were predicted to either benefit synergistically from stressor effects by occupying trophic positions as mesopredators in omnivory interactions, or to display insensitivity to stressors due to their trophic role as resources in exploitative competition interactions [@Beauchesne2021], this suggest that the trophic level of a species could be important to anticipate the impact of stressors.
-
-But also the species' vulnerability to stressor effects might arise solely from indirect exposure.
-The number of stressors influencing a species does not necessarily correlate with higher sensitivity.
-For instance @Beauchesne2021 showed that despite stressors impacting shrimp in terms of mortality, physiology, and behavior, its trophic sensitivity was low.
-On the other hand, marine mammals and seabirds that were not directly affected by stressors were markedly susceptible to the indirect repercussions of stressors and nonadditive effects.-->
-
-![Conceptual diagram: from species’ stressors to food web effects. See text for explanation.](Figures/Figure2_StressorDiagram.png){width="6.27in"
+![Conceptual diagram: from species’ stressors to food web effects.
+A stressor (e.g., global warming) will affect one of the following species’ characteristics: metabolism, population biomass, distribution, and diet.
+‘Metabolism’ refers to any change related to metabolic rate, such as reproduction, hatching, larval development, growth and mortality, and contamination due to pollutants.
+‘Population biomass’ indicates an effect at the population level, where the density/abundance is being impacted.
+‘Distribution’ entails a change at the population level in the geographic space occupied by a species.
+‘Diet' includes alterations in the prey items of a species at the population level.
+Next, we considered node- and network-level properties relevant to the hypothesized stressor effects on the food webs.
+At the node-level, we included: a) degree, b) trophic position, c) omnivory index, and d) relative abundance.
+At the network-level, we considered: a) connectance, b) path length, c) mean trophic level, and d) omnivory.
+Finally, we elaborate a series of competing hypotheses on how the identified stressors might affect food web features (stability, energy flow, topology), combining information on node- and network-level properties.](Figures/Figure2_StressorDiagram.png){width="6.27in"
 height="3.528in"}
@@
 \newpage
+\blandscape
 \scriptsize
 
-Table 2. Node and network-level properties used to build hypotheses on the stressors’ effects.
+Table 2. Environmental and anthropogenic stressors reported for the study areas: San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea (North and South), Potter Cove, and Weddell Sea.
+Stressor categories: sea warming; glacial retreat; sediment in the water column; iceberg scouring; sea ice extent; ocean acidification; ocean acidification + plastics; microplastics; mercury; urban & industrial pollution; fishery; alien species.
+The species affected were considered at the node level, whereas effects were considered at the organism and population levels.
+Categories of affected parameters and variables: metabolism; biomass; distribution; diet (see text for explanation).
+“Locality” indicates whether a stressor for a given species was reported for the study area (‘In situ’) or in another area (‘Elsewhere’).
 
-----------------------------------------------------------------------------------------------------------
-**Property**         **Definition**              **Relevance for stressor effects**        **Reference**
--------------------- --------------------------- ----------------------------------------- ---------------
-*Node-level*
+**Study area**                  **Stressor**                                             **Species affected**                                                                                                                                                                                                          **Parameter affected**      **Locality**                                                  **Reference**
+------------------------------- -------------------------------------------------------- ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- --------------------------- ------------------------------------------------------------- ------------------------------------------------------------------------------
+**San Jorge Gulf**
+                                Sea warming                                              Fish assemblage & its prey                                                                                                                                                                                                    Distribution                In situ                                                       @Galvan2022
+                                Fishery                                                  Demersal fish community                                                                                                                                                                                                       Biomass                     In situ                                                       @Galvan2022
+                                Fishery                                                  Macroinvertebrates, fish and seabirds                                                                                                                                                                                       Diet                        In situ                                                       @Gonzalez-Zevallos2006; @Gonzalez-Zevallos2011; @Yorio2017
+                                Alien species                                            Fish assemblage & its prey                                                                                                                                                                                                    Distribution                In situ                                                       @Galvan2022; @Ciancio2010
+                                Urban & industrial pollution                             Seabirds & benthic assemblage                                                                                                                                                                                                 Biomass                     Elsewhere                                                     @Moore1974; @Buskey2016
+**Beagle Channel**
+                                Urban & industrial pollution                             Macroalgae; Mytilus edulis chilensis, Patagonotothen tessellata                                                                                                                                                               Metabolism                  In situ                                                       @Giarratano2010; @Ferreira2021; @Kaminsky2024
+                                Mercury                                                  Phytoplankton, Zooplankton, *Grimothea gregaria*                                                                                                                                                                              Metabolism                  In situ                                                       @Fioramonti2022
+                                Microplastics                                            Mytilus edulis chilensis, Nacella magellanica                                                                                                                                                                                 Metabolism                  In situ                                                       @Perez2020; @Ojeda2021
+                                Alien species: Chinook salmon Oncorhynchus tshawytscha   Patagonotothen tessellata, Sprattus fuegensis                                                                                                                                                                                 Diet/Biomass                In situ (the presence), Elsewhere (changes in prey biomass)   @Fernandez2010; @Ciancio2008
+**Burdwood Bank**
+                                Mercury                                                  Dissostichus eleginoides, Sprattus fuegensis, Patagonotothen ramsayi, Cottoperca trigloides (fish) & squids                                                                                                                 Metabolism                  In situ                                                       @Fioramonti2022
+                                Microplastics                                            Henricia obesa & Odontaster penicillatus (sea stars); Patagonotothen guntheri & P.
+ramsayi (fish)                                                                                                                           Metabolism                  In situ                                                       @Cossi2021; @Perez2021
+                                Fishery                                                  Target: Dissostichus eleginoides.
+Bycatch: Macrourus sp., Coelorinchus sp.
+(fish), Daption capense, Thalassarche melanophris, Macronectes giganteus, T.
+chrysostoma, Diomedea epomophora (seabirds), 30+ spp macrobenthos   Biomass                     Elsewhere                                                     @Gaitan2016; @Martinez2022; @APN2022; @Tamini2023
+                                Fishery                                                  Thalassarche melanophris, Macronectes giganteus, Daption capense, Diomedea epomophora, M.
+halli, Procellaria aequinoctialis (seabirds)                                                                                        Diet                        Elsewhere                                                     @Tamini2023
+**Scotia Sea, North & South**
+                                Mercury                                                  Krefftichthys anderssoni, Protomyctophum bolini, Electrona antarctica, Gymnoscopelus nicholsi, Gymnoscopelus braueri, Dissostichus eleginoides                                                                                Metabolism                  In situ                                                       @Seco2021
+                                Ocean acidification + plastics                           Euphausia superba, Limacina retroversa (Pteropoda)                                                                                                                                                                            Metabolism                  In situ                                                       @Rowlands2021; @Manno2022
+                                Sea warming                                              Euphausia superba                                                                                                                                                                                                             Metabolism                  In situ                                                       @Murphy2007; @Perry2020
+                                Sea warming                                              Euphausia superba                                                                                                                                                                                                             Distribution                In situ                                                       @Atkinson2019
+                                Fishery                                                  Euphausia superba                                                                                                                                                                                                             Biomass                     In situ                                                       @Trathan2021
+**Potter Cove (Antarctica)**
+                                Sediment in water column                                 Microphytobenthos, macroalgae, benthic filter feeders (ascidians), pelagic filter feeders (krill, salps)                                                                                                                      Metabolism                  In situ                                                       @Sahade2015; @Deregibus2016; @Fuentes2016; @Hoffmann2019
+                                Sea ice extent                                           Krill                                                                                                                                                                                                                         Biomass                     Elsewhere                                                     @Flores2012
+                                Sea ice extent                                           Benthic community (macroalgae, invertebrates)                                                                                                                                                                                 Metabolism                  Elsewhere                                                     @Clark2013; @Campana2018
+                                Glacial retreat                                          Benthic community (macroalgae, invertebrates)                                                                                                                                                                                 Biomass                     In situ                                                       @Quartino2013; @Lagger2017; @Lagger2018
+                                Iceberg scouring                                         Benthic community                                                                                                                                                                                                             Biomass                     In situ                                                       @Deregibus2017; @Deregibus2023
+                                Sea warming                                              Phytoplankton                                                                                                                                                                                                                 Metabolism, biomass         In situ                                                       @Antoni2020; @Latorre2023
+                                Sea warming                                              Zooplankton                                                                                                                                                                                                                   Metabolism, biomass, diet   In situ                                                       @Garcia2016; @Garcia2019
+                                Sea warming                                              Fish                                                                                                                                                                                                                          Metabolism                  In situ, elsewhere                                            @Strobel2013; @Souza2018; @Saravia2021
+**Weddell Sea (Antarctica)**
+                                Iceberg scouring                                         Macrobentos                                                                                                                                                                                                                   Biomass                     In situ                                                       @Isla2023; @Gutt2015; @Smale2008a; @Gutt1996
+                                Iceberg scouring                                         Hexactinellida sponges                                                                                                                                                                                                        Biomass                     In situ                                                       @Gutt2001; @Pineda-Metz2020; @Gutt2001a; @Gutt2003
+                                Ocean acidification                                      Primary producers / krill / foraminifera / flagellates                                                                                                                                                                        Metabolism                  Elsewhere                                                     @Deppeler2020; @Isla2023; @Gutt2015; @Moy2009
+                                Ocean acidification                                      Euphausia superba, Pleuragramma antarcticum                                                                                                                                                                                   Metabolism                  In situ                                                       @Kawaguchi2010; @Kawaguchi2013; @Pinones2016; @Mintenbeck2012
+                                Sea warming                                              Large (diatoms) & small (cryptophytes) phytoplankton, zooplankton (salps)                                                                                                                                                     Metabolism                  Elsewhere                                                     @Isla2023; @Gutt2015; @Trebilco2020
+                                Sea warming                                              Euphausia superba, Nototheniid fish, Pleuragramma antarcticum                                                                                                                                                               Metabolism                  In situ                                                       @Meyer2017; @Hill2013; @Mintenbeck2012; @Constable2014; @Mintenbeck2012
+                                Sea ice extent                                           Phytoplankton, Lobodon carcinophaga, Hydrurga leptonyx, Leptonychotes weddellii, Ommataphoca rossii, Mirounga leonina, Arctocephalus gazella                                                                                  Metabolism                  In situ                                                       @Pineda-Metz2020; @Wege2021; @Siniff2008
+                                Sea ice extent                                           Euphausia superba, Pleuragramma antarcticum, Pagodroma nivea, Thalassoica antarctica, Pygoscelis adeliae                                                                                                                      Metabolism                  In situ                                                       @Orgeira2021; @Braithwaite2015; @Hill2013; @Mintenbeck2012
+                                Sea ice extent                                           Megaptera novaeangliae                                                                                                                                                                                                        Metabolism                  Elsewhere                                                     @Pallin2023
+                                Sea ice extent                                           Aptenodytes forsteri                                                                                                                                                                                                          Metabolism                  Elsewhere                                                     @Orgeira2021
 
-Degree               Number of feeding           Perturbations to high-degree species      @Dunne2002a; 
-                     interactions in which       may have more significant effects on      @Jordan2007
-                     the species participates    the food web robustness to perturbations 
-                     as prey and/or predator.    than low-degree species.
-
-Trophic position     Place in the food web       Perturbations on basal resources,         @Williams2000; 
-                     relative to the basal       intermediate species and top predators    @Thompson2007
-                     resources that support      are expected to have large effects on the 
-                     the community. Classifies   rest of their communities if ecosystem 
-                     species in: basal,          control is bottom-up, wasp-waist or 
-                     intermediate and top.       top-down, respectively.
-
-Omnivory             Consumer resource use       High-omnivore species (generalists)       @Thompson2007
-                     across trophic levels.      are more flexible than low-omnivore
-                                                 species to diet changes.
-
-Relative abundance   Species' density in         Perturbations on abundant (dominant)      @Nilsson2016
-                     proportion to the other     species are expected to have large 
-                     species of the food web.    effects on the stability and energy 
-                                                 flux of the food and ecosystem, 
-                                                 respectively.
-
-*Network-level*
-
-Conectance           Proportion of actual        Estimator of community sensitivity to     @Dunne2002
-                     interactions among          stressors. High connectance gives 
-                     possible ones.              resistance and resilience to the 
-                                                 food web.
-
-Path length          Average distance,           Short distances enhance rapid and         @Albert2002
-                     accounted by the number     broad propagation of perturbations.
-                     of interactions, between 
-                     any pair of species.
-
-Mean TL              Average of all species'     Influences the magnitude and efficiency   @Duffy2007; 
-                     trophic position contained  of trophic transfer. A higher mean food   @Olivier2019
-                     in the food web.            chain length reflects increased energy 
-                                                 availability and productivity.
-
-Omnivory             Proportion of species that  It provides trophic flexibility to an     @Kratina2012
-                     feed at different trophic   ecosystem. Reduces probability of 
-                     levels.                     trophic cascades.
-----------------------------------------------------------------------------------------------------------
+\elandscape
 
@@
 
-### 4.1 Main stressor effects in food webs in a southwest Atlantic - Antarctic gradient
+### 3.1 Hypotheses on the main stressor effects in food webs in a southwest Atlantic - Antarctic gradient
 
-The most common stressor reported along the southwest Atlantic - Antarctic gradient is global warming, except for Beagle Channel and Burdwood Bank, which are more influenced by the introduction of an alien species and fisheries, respectively (section 3, Table 3).
-The main characteristics of global warming in the region, and the most plausible drivers of change, are: sea warming, glacial retreat, elevated sediment input in the water column, and reduction of the sea ice extent.
+The most common stressor reported along the Southwest Atlantic - Antarctic gradient is global warming, except for Beagle Channel and Burdwood Bank, which are more influenced by the introduction of an alien species and fisheries, respectively (Section 2, Table 2).
+The main characteristics of global warming in the region, and the most plausible drivers of change, are sea warming, glacial retreat, elevated sediment input to the water column, and reduction of the sea ice extent.
 These drivers act in different ways and magnitudes in the studied locations along the latitudinal gradient.
-Despite emphasizing global warming in this section, this does not mean that no other stressors act or interact with global warming in the study systems, potentially buffering the overall effect on the food web (e.g.
+Despite emphasizing global warming in this section, this does not mean that no other stressors act or interact with global warming in the study systems, potentially buffering or even amplifying the overall effect on the food web (e.g.
 sea warming and fishery in San Jorge Gulf).
@@
 Changes in metabolic rates can subsequently translate into shifts in species traits (e.g.
-body size, @Vucic-Pestic2011; @Klein2018), biomass [@Perry2020], and distribution [@Kortsch2015].
+body size, @Vucic-Pestic2011; @Klein2018), population biomass [@Perry2020], and distribution [@Kortsch2015].
 Alterations in the species body size and distributions have ripple effects on feeding interactions, for example, it can introduce new feeding interactions [@Pecuchet2020; @Verges2014], modify existing ones, and shorten energy pathways [@Bartley2019; @OGorman2019], and reduce trophic efficiencies [@Vucic-Pestic2011].
 
-In recent years, several new fish  [@Galvan2022] and macroinvertebrates species [@Vinuesa2005; @Lopez-Gappa2022] were registered in Patagonia, mostly in San Jorge Gulf in relation to the southward range shift of warm-temperate species.
+#### 3.1.1 San Jorge Gulf
+
+In recent years, several new fish [@Galvan2022] and macroinvertebrates species [@Vinuesa2005; @Lopez-Gappa2022] were registered in Patagonia, mostly in San Jorge Gulf concerning the southward range shift of warm-temperate species.
 This distributional change is driven by the tropicalization of temperate waters caused by sea warming [@Verges2014; @Verges2019].
@@
 Newcomers are, in general, mid-trophic level species with generalist diets, hence an increase in food web connectance may be expected [@Bartley2019].
-In another temperate ecosystem, an increase in the number of fish species, led to an increase in functional diversity and predation rate [@Sgarlatta2023]; consequences that may also be expected in San Jorge Gulf.
+In another temperate ecosystem, an increase in the number of fish species led to increases in functional diversity and predation rate [@Sgarlatta2023]; consequences that may also be expected in San Jorge Gulf.
 Given the short path length of the San Jorge Gulf food web, the disturbances from the listed stressors are expected to spread to many species of the food web (Table 3).
@@
 
-In the middle of the latitudinal gradient (considered in this study), the Scotia Sea has experienced one of the largest levels of sea warming of any polar region [@Whitehouse2008; @Atkinson2019].
+#### 3.1.2 Scotia Sea
+
+In the middle of the latitudinal gradient considered in this study, the Scotia Sea has experienced one of the largest levels of sea warming of any polar region [@Whitehouse2008; @Atkinson2019].
 @Lopez-Lopez2022 suggested that the southward distributional shift of generalist predators from the northern towards southern Scotia Sea increases network connectance of the latter, while decreasing its modularity.
-The lower modularity may increase the probability of perturbations spreading through the network [@Stouffer2011], which may be offset by increased connectance enhancing robustness to species loss [@Dunne2002a].
+The lower modularity may increase the probability of perturbations spreading through the network [@Stouffer2011].
 In the northern Scotia Sea around South Georgia Island, we suggest that the declining krill biomass driven by sea warming [@Atkinson2019], ocean acidification and pollution synergy [@Rowlands2021], will reduce the energy transfer to top predators like seabirds and marine mammals.
-However, this may be buffered since the dominant copepod species have maintained their distribution [@Tarling2018], but most importantly, showed an abundance increase in recent decades likely due to reduced predation and competition for food [@Ward2018].
-All this is significant for the structure of the food web given the central role of krill and copepods, characterized by high degree and mid-trophic position (Table S1).
-Overall, the food web's inherent resilience, marked by high connectance and omnivory, added to the potential compensation for the krill decrease due to a copepod increase, may buffer against structural changes (Table 3).
+However, this may be buffered because the dominant copepod species have maintained their distribution [@Tarling2018], but most importantly shown an abundance increase in recent decades likely due to reduced predation and competition for food [@Ward2018].
+The potential compensation for the decrease in krill by increasing abundance of copepod may buffer against structural and functional changes in the food web (Table 3), since krill and copepod play similar (central) roles in the food web, characterized by a high degree and mid-trophic position.
 
-In Potter Cove, a fjord-like Antarctic ecosystem, the impacts of climate change affect many species within the food web.
-Potter Cove has recently experienced frequent events of marine heatwaves, i.e.
-prolonged periods of anomalously high sea surface temperatures [@Oliver2018; @Latorre2023].
+#### 3.1.3 Potter Cove (Antarctica)
+
+In Potter Cove, a fjord-like Antarctic ecosystem, the repercussions of climate change extend across numerous species.
+Noteworthy, these effects are non-uniform within the food web, manifesting differently across its various compartments [@Cordone2020; @Rodriguez2022].
+Potter Cove has recently experienced frequent events of marine heatwaves, i.e., prolonged periods of anomalously high sea surface temperature [@Oliver2018; @Latorre2023].
 This has led to decreases in biomasses of different planktonic functional groups [@Garcia2019; @Latorre2023].
-Given the relatively low abundance of phytoplankton, zooplankton’s low degree, and the modular configuration of the food web, we hypothesize that changes in these nodes, due to increased sea temperatures, will be retained in the basal pelagic compartment of the food web and will not expand to higher trophic levels.
-Benthic primary producers in Potter Cove are being influence by the decrease in winter sea ice cover (higher light availability), the increased levels of sediments in the water column due to glacial melt run-off (lower light penetration) and the newly free-ice areas available for colonization associated to glacier retreat.
+Given the relatively low abundance of phytoplankton and zooplankton’s low mean degree, resulting in weak interaction strengths between these low trophic levels and higher ones [@Rodriguez2024], added to the modular configuration of the food web [@Rodriguez2022], we hypothesize that changes in these nodes due to warming will be retained at the basal level of the pelagic compartment and will not expand to higher trophic levels.
+Benthic primary producers in Potter Cove are being influenced by the decrease in winter sea ice cover (higher light availability), the increased levels of sediments in the water column due to glacial melt run-off (lower light penetration) and the newly free-ice areas available for colonization associated to glacier retreat.
 The overall local effect of climate change on macroalgae is a net increase in their production [@Deregibus2023].
 It has been proposed that larger diversity in primary producers can support a more diverse food web with more specialized consumers [@Iken2023].
-We expect to see differential effects of climate change on hard and soft bottom associated food webs [@Cordone2020].
-Given the high relative abundance and the high degree of the macroalgae functional group (Table S1), we expect a longer hard bottom food web, wider consumer trophic niches, and that it will become more stable as sea ice cover decreases and the glacier retreats due to global warming.
-In soft bottom areas of the Cove, multiple food web nodes are being affected by ongoing warming effects: decrease in net primary production of benthic microalgae [@Hoffmann2019], and changes in the benthic community biomass, distribution and composition [@Sahade2015; @Pasotti2015].
-Given that the Potter Cove food web’s present low connectance and omnivory, we suggest fragility and potential trophic cascade effects [@Marina2018] with pronounced changes in energy fluxes (Table 3).
+Given the high relative abundance and the high degree of the macroalgae functional group (Table S1), we expect a longer hard bottom food web (i.e., number of interactions connecting low and high-trophic levels), wider consumer trophic niches, and a more stable benthic food web as sea ice cover decreases and glaciers retreat due to global warming.
+In soft bottom areas of the cove, multiple food web nodes are being affected by ongoing warming effects: decrease in net primary production of benthic microalgae [@Hoffmann2019], and changes in the benthic community biomass, distribution and composition [@Sahade2015; @Pasotti2015].
+Given that the Potter Cove food web has low connectance and omnivory, we suggest fragility and potential trophic cascade effects [@Marina2018], especially between species of the soft bottom compartment (Table 3).
+Overall, we anticipate significant shifts in energy fluxes, rather than alterations in the overall structure of the Potter Cove food web, with strengthening of connections within compartments.
 
-The southernmost location of the latitudinal gradient is the Weddell Sea, where the main effect of global warming is the decrease in sea ice extent, with reported anomalies in the past summer seasons [@Fretwell2023].
+#### 3.1.4 Weddell Sea (Antarctica)
+
+In the southernmost food web, the Weddell Sea, the main effect of global warming is the decrease in sea ice extent, with reported anomalies in the past summer seasons [@Fretwell2023].
 Declining sea ice extent has reduced the abundance of krill [@Atkinson2004; @Flores2012], and produced an increase in phytoplankton productivity [@Isla2023; @Pinkerton2021], altering the plankton community structure, and benefiting cryptophytes over diatoms [@Lin2021].
-Moreover, habitat loss from sea ice decline will reduce the foraging success and breeding sites of seabirds (e.g., snow petrel Pagodroma nivea and emperor penguin Aptenodytes forsteri), decreasing their biomassess and modifying their distributions.
+Moreover, habitat loss from sea ice decline will reduce the foraging success and breeding sites of seabirds (e.g., snow petrel *P.
+nivea* and emperor penguin), decreasing their population biomassess and modifying their distributions.
 The projected rise in iceberg scouring is expected to significantly alter the biomass and community structure of macrobenthos, which in turn will impact mid-trophic level predators such as demersal fish [@Gutt2001a; @Mintenbeck2012].
-While we do not anticipate large-scale topological changes in the food web, local extinctions could lead to such changes, particularly affecting benthic species [@Gutt2003].
-Given that the impacted species—whether individually like krill, or collectively like macrobenthos—present a mid-trophic position, high biomass and high degree (Table S1), we hypothesize that significant shifts in energy fluxes will occur (Table 3).
+While we do not anticipate large-scale topological changes in the mean food web attributes, local extinctions could lead to such changes, particularly affecting benthic species [@Gutt2003].
+Given that the impacted species—whether individually like krill, or collectively like macrobenthos and notothenioids (e.g., *P.
+antarcticum*)—present a mid-trophic position, high population biomasses and high degree (Table S1), we hypothesize that significant shifts in energy fluxes will occur (Table 3).
 Additionally, the food web's low proportion of omnivores suggests reduced system resilience (Table 1), increasing the likelihood of regime changes [@Gutt2015].
 
-The two ecosystems in the subantarctic region, the Beagle Channel and Burdwood Bank, are more affected by other anthropogenic stressors than warming.
-Although these areas are being impacted by sea warming, potentially affecting vertebrate and invertebrate species [@Franco2020], to date no studies exist for Beagle Channel and Burdwood Bank ecosystems.
+#### 3.1.5 Beagle Channel and Burdwood Bank
+
+The Beagle Channel and Burdwood Bank -the two ecosystems in the subantarctic region- are more affected by other stressors than warming.
+That said, there are impacts of warming in these ecosystems, especially  affecting vertebrate and invertebrate species [@Franco2020], but generally studies addressing these impacts are lacking for the Beagle Channel and Burdwood Bank ecosystems.
 In the Beagle Channel, the introduction of chinook salmon, a non-native species, poses a significant risk to the existing food web [@Fernandez2010].
@@
 This phenomenon is further heightened by the ecosystem's inherent vulnerability to changes at mid-trophic levels, often referred to as wasp-waist control (Table 3).
-In the Burdwood Bank region, fishing activities may be the main stressor causing shifts in the food web (Table S2).
+In the Burdwood Bank region, fishing activities may be the main stressor causing shifts in the food web (Table 2).
 We hypothesize that a combination of factors will destabilize the already fragile ecosystem, characterized by low connectance and low omnivory (Table 1).
-These factors include a decline in the biomass of the Patagonian toothfish -a key, highly-connected species (Table S1)- as well as smaller changes in the biomass of four mid-level fish species, five top-level seabird species, and over 30 types of benthic macroinvertebrates due to bycatch [@Gaitan2016; @Martinez2022; @Tamini2023].
+These factors include a decline in the biomass of the Patagonian toothfish -a highly-connected, key species (Table S1)- as well as smaller changes in the population biomass of four mid trophic level fish species, five top trophic level seabird species, and over 30 types of benthic macroinvertebrates due to bycatch [@Gaitan2016; @Martinez2022; @Tamini2023].
 Additionally, alterations in the diets of six seabird species, caused by discarded catch [@Tamini2023], are expected to disrupt the energy flow and further reduce the stability of the food web (Table 3).
@@
 
-Table 3. Summary of food web (FW) effects according to the main stressors
+Table 3. Summary of hypothesized food web (FW) effects according to the main stressors
 reported for each study area. \*Industrial trawl fishery ceased in 2015 remaining artisanal trawling
@@
 +-----------------------+----------------------+-----------------------+
-| **Study area**        | **Stressor**         | **Food web effects**  |
+| **Study area**        | **Stressor**         | **Hypothesis on food web effects**  |
 |                       |                      |                       |
@@
 
-## 5. Gaps and future perspectives
+## 4. Gaps and future perspectives
 
-<!-- Update diet & biomass data -->
-In the selected study areas along the southwest Atlantic to Antarctic latitudinal gradient, several stressors may directly affect consumers’ diets triggered by modified environmental conditions (sea warming, reduced sea ice extent) and new species (due to species’ distributional shifts and introductions).
+In the selected study areas along the Southwest Atlantic to Antarctic latitudinal axis, several stressors may directly affect consumers’ diets triggered by modified environmental conditions (sea warming, reduced sea ice extent) and new species (due to species’ distributional shifts and introductions).
 Moreover, the population trends (biomasses and abundances) of important species are also changing [@Funes2020; @Hindell2020; @Woods2023] driving shifts in their roles as either predators or prey (e.g.
 @Belleggia2017, @Pasti2021).
-These diet and biomass shifts should be investigated in order to generate reliable predictions of food web responses to multiple stressors in the southwest Atlantic - Antarctic region.
+These diet and population biomass shifts should be investigated to generate reliable predictions of food web responses to multiple stressors in the Southwest Atlantic - Antarctic region.
 One could argue that both shifts might increase the complexity of food webs in the short term by adding generalist predators or new prey (e.g., @Cordone2023) or by enabling discard consumption (e.g.
@@
 @Anton2019) or a significant reduction in target and incidental catch species (e.g.
-@Dulvy2014), thereby promoting food web simplification.
+@Dulvy2014), thereby promoting food web simplification and decreases in robustness.
 
-<!-- Quantitative food webs & stressors -->
-Since this review deals with qualitative data of  prey-predator interactions and stressor effects influencing them, adding quantitative data to the food webs (i.e.
-interaction strength) and to the stressors (i.e.
-magnitude) would lead to a better comprehension of how a given stressor acts on specific species which might translate into food web effects.
-In this context, it would be useful to develop quantitative food web models  where the strength of interactions reflect energy fluxes among species [@Kortsch2021; @Nilsson2016].
-Emerging methods such as bioenergetic food web modeling have been proposed in this regard and present promising ways to estimate shifts in species interactions within food webs as a response to stressors [@Gauzens2023;  @Gellner2023].
+Since this review deals with qualitative data of predator-prey interactions and stressor effects influencing them, adding quantitative data to the food webs (e.g., interaction strength) and to the stressors (e.g., magnitude) would lead to a better understanding of how a given stressor acts on specific species which might translate into food web effects.
+In this context, it would be useful to develop quantitative food web models where the strength of interactions reflects energy fluxes among species [@Kortsch2021; @Nilsson2016].
+Emerging methods such as bioenergetic food web modeling have been proposed in this regard and present promising ways to estimate shifts in species interactions and energy fluxes within food webs as a response to stressors [@Gauzens2023;  @Gellner2023].
 Shifts that can lead to changes in overall ecosystem functioning and stability.
 
-<!-- Beagle & Burdwood global warming gap -->
 Regarding knowledge and data gaps on species and their stressors, especially the Beagle Channel and Burdwood Bank are poorly sampled study regions.
-Almost no information exists on the impact of global warming effects (sea warming, glacial retreat, ocean acidification) on communities in these ecosystems, though warming of mid-water and bottom layers have been shown at a regional scale [@Franco2020].
-Yet in Beagle Channel recent experimental studies have tested the tolerance of fishes to scenarios of sea warming and/or acidification suggesting potential metabolic impacts on species [@Lattuca2018; @Lattuca2023].
+Almost no information exists on the impact of global warming (sea warming, glacial retreat, ocean acidification) on communities in these ecosystems, although warming of mid-water and bottom layers has been shown at a regional scale [@Franco2020].
+Yet, in Beagle Channel recent experimental studies have tested the tolerance of fish to scenarios of sea warming and/or acidification suggesting high vulnerability to projected climate-driven environmental conditions [@Lattuca2018; @Lattuca2023].
 
-<!-- Multiple stressors -->
 Analyzing the impact of multiple stressors through observational studies is challenging [@Gutt2021].
-This complexity arises partly because of potential for antagonistic effects, where impacts cancel each other out, or synergistic effects, where the combined impact is greater than the sum of individual effects [@Boyd2015; @Cote2016].
+This complexity arises partly because of the potential for antagonistic effects, where impacts cancel each other out, or synergistic effects, where the combined impact is greater than the sum of individual effects [@Boyd2015; @Cote2016].
 Moreover, these interactive effects are complicated to handle in the framework of complex food webs.
@@
 
-## Conclusions
+In this review, we proposed a series of alternative hypotheses on how global stressors may affect food webs in the Southwest Atlantic to Southern Ocean.
+Despite being qualitative, this is a first important step in synthesizing food webs and stressor effects on food webs for this region.
+These qualitative assessments must be complemented with further investigations that test their validity.
+To achieve this, we suggest using a combination of observational data such as reported biomass changes and historic records of sea temperature for the region [e.g., @Laptikhovsky2013; @Funes2019; @Franco2020a; @Winter2023], and food web modeling methods such as stressor-response matrices (@Bracewell2019) and flux modeling (e.g., @Gauzens2019; @Beauchesne2021; @Polazzo2022).
 
-We have reviewed the main environmental and anthropogenic stressors acting in six different areas along a large-scale latitudinal gradient, from temperate Atlantic to cold Antarctic ecosystems.
-Using a theoretical framework that combines species and food web level data, we suggest how warming effects may impact food web structure and functioning.
-These qualitative predictions are intended to serve as the basis for future studies in marine ecosystems of the Southern Hemisphere that aim at quantifying the magnitude of these stressors and how they are affecting quantitative food web properties, such as energy fluxes and stability.
+## 5. Conclusions
+
+We reviewed  global change stressors acting in six different areas along a large-scale latitudinal gradient from temperate Atlantic to cold Antarctic ecosystems.
+Using a theoretical framework that combines species and food web-level data, we suggest how warming effects may impact food web structure and functioning.
+Besides there is an important amount of uncertainty, these qualitative predictions are intended to serve as the basis for future studies in marine ecosystems of the Southern Hemisphere that aim at quantifying the magnitude of these stressors and how they are affecting quantitative food web properties, such as energy fluxes and stability.
 There is an urgent need to assess these changes using a holistic and quantitative framework where the magnitude of stressors and species interactions are taken into account.
@@
 
-This review is a product of the project “¿Cuáles son los efectos de los cambios ambientales antropogénicos en las interacciones tróficas de las comunidades de los ecosistemas marinos en el gradiente latitudinal Atlántico Sudoccidental - Antártida?”, funded by Consejo Nacional de Investigaciones Científicas (CONICET, code PIP 2022-2024 #0907).
+This review is a product of the project “¿Cuáles son los efectos de los cambios ambientales antropogénicos en las interacciones tróficas de las comunidades de los ecosistemas marinos en el gradiente latitudinal Atlántico Sudoccidental - Antártida?”, funded by Consejo Nacional de Investigaciones Científicas (CONICET, code PIP 2022-2024 #0907), Argentina.
+S.K.
+gratefully acknowledges the support from the Walter and Andrée de Nottbeck Foundation, Finland.
 

### 2024-04-18 manuscript.tex
Ms corrections
Ms reorganization almost to submit

@@
 \usepackage{longtable,booktabs,array}
+\usepackage{multirow}
 \usepackage{calc} % for calculating minipage widths
@@
 \section{The response of trophic interaction networks to multiple
-stressors in a marine latitudinal gradient of the Southern
-Hemisphere}\label{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}
+stressors along a large-scale latitudinal range in the Southern
+Hemisphere}\label{the-response-of-trophic-interaction-networks-to-multiple-stressors-along-a-large-scale-latitudinal-range-in-the-southern-hemisphere}
 
@@
 Ecological networks offer valuable insights into community structure,
-key species identification, and ecosystem management for biodiversity
-conservation. Understanding how these networks react to environmental
-and anthropogenic stressors, especially along geographical gradients, is
-of increasing interest. This review presents a pioneering analysis of
-stressor responses in marine food webs from the southwest Atlantic to
-the Antarctic (45 - 78ºS), encompassing areas such as San Jorge Gulf,
-Beagle Channel, Burdwood Bank, Scotia Sea, Potter Cove, and the Weddell
-Sea in Antarctica. Our objectives are to: 1) describe the structure of
-marine food webs along this axis using a network approach; 2) identify
-predominant environmental and anthropogenic stressors affecting each
-ecosystem; and 3) summarize observed food web changes and hypothesize on
-stressor impacts. Our collaborative team, comprising regional experts
-and global authorities on high-latitude marine food webs and stressor
-effects, ensures a comprehensive and credible literature review. We
-assessed the effects of stressors primarily at the species level, with
-notable exceptions like fisheries in San Jorge Gulf. Hypotheses for each
-study area were formulated considering: a) stressors; b) impacted
-parameters; c) node-level species properties; and d) network-level food
-web properties. Global warming emerges as the most common stressor
-across the gradient, except in the Beagle Channel and Burdwood Bank,
-where alien species introduction and fisheries are more influential,
-respectively. We offer specific hypotheses on how warming may affect
-food webs. Our findings highlight the benefits of a network approach in
-understanding and predicting stressor effects in Southern Hemisphere
-marine ecosystems. This approach provides a holistic understanding of
-ecological networks, enhances our ability to identify key species and
-interactions, and offers insights for ecosystem management and
-conservation in the face of various stressors.
-
-Keywords: anthropogenic stressors, environmental stressors, food webs,
-latitudinal gradient, Southern Hemisphere
+key species identification, and ecosystem management. Understanding how
+these networks respond to global change stressors is of increasing
+interest, especially along geographical gradients. This review
+summarizes potential stressor responses in marine food webs from the
+Southwest Atlantic to the Antarctic (45 - 78ºS), encompassing areas such
+as San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea, Potter
+Cove, and the Weddell Sea in Antarctica. The objectives are: 1) to
+describe the structure of marine food webs along this latitudinal axis
+using a network approach; 2) to identify predominant global
+change-related stressors affecting each ecosystem; and 3) to summarize
+observed food web changes and hypothesize on stressor impacts. The
+effects of stressors were primarily reviewed at the species level.
+Alternative hypotheses for each study area were formulated considering:
+a) main stressors; b) impacted parameters; c) node-level species
+properties; and d) network-level food web properties. Global warming
+emerges as the most common stressor among the studied areas across the
+latitudinal gradient, except in the Beagle Channel and Burdwood Bank,
+where alien species introduction and fisheries are more influential. We
+offer a series of alternative hypotheses on how warming may affect the
+food webs. This review emphasizes the benefits of using a network
+approach to understand and predict stressor effects in Southern
+Hemisphere marine ecosystems. This approach provides a holistic
+understanding of ecosystems, which enhances our ability to identify key
+species and their interactions, offering insights for ecosystem
+management and conservation in the face of global change stressors.
+
+Keywords: stressors, global warming, food webs, latitudinal gradient,
+Southern Hemisphere
 
@@
 marine ecosystems. The few that have come from the Global North (Wood et
-al. 2015; Kortsch et al. 2019; Pecuchet et al. 2022), whereas no
+al. 2015; Kortsch et al. 2019; Pecuchet et al. 2020), whereas no
 studies, nor meta-analyses, on geographical variation in marine food
@@
 
-Here we review for the first time the state-of-the-art knowledge on
-stressor response of marine food webs along the southwest Atlantic to
-Antarctic gradient (45 - 78ºS, Figure 1). We focus on proven and
-expected changes in food webs driven by stressors in selected areas
-along this large-scale latitudinal gradient. We recruited food web
-experts from different marine systems of Argentina and the world (see
-co-authors' list). Throughout the year 2023 we maintained regular
-discussion meetings, typically held every two or three weeks. The aim of
-this review is threefold: 1) describe the complexity and structure of
-marine food webs along the southwest Atlantic to Antarctic axis from a
-network perspective; 2) identify the ongoing environmental and
-anthropogenic stressors for each marine ecosystem containing the food
-webs; and 3) review proven food web changes and elaborate hypotheses on
-how the identified stressors might affect food web features (e.g.~energy
-flow, stability), combining information on node- and network-level
-properties. Finally, we suggest which additional data and analyses are
-needed to gain insights into the stressors' effects on food web
-properties in the southwest Atlantic to Antarctic region.
-
-\subsection{2. The structure of marine food webs in the Southwest
-Atlantic - Antarctic
-region}\label{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}
-
-Together, the southwest and the Atlantic sector of the Southern Ocean
-comprise one of the most biologically productive regions of the world's
-oceans (Acha et al. 2004; Latorre et al. 2023). The referred region
-extends from San Jorge Gulf (45ºS) in the Patagonian shelf to the
-Weddell Sea (78ºS) in the Southern Ocean, and covers a well-connected
-oceanic latitudinal gradient (Matano et al. 2010; Guihou et al. 2020).
-
-Throughout this latitudinal gradient, many investigations have been
-carried out addressing the trophic ecology of specific species and
-prey-predator relationships (Vinuesa and Varisco 2007; Pasotti et al.
-2015; Saunders et al. 2019; Riccialdelli et al. 2020), but few studies
-have considered the complexity of the ecosystem in terms of a high
-resolution of species and their prey-predator interactions (but see
-Jacob et al. (2011), Marina et al. (2018), Funes et al. (2022),
-López-López et al. (2022), Rodriguez et al. (2022), Marina et al. (in
-rev.)). Neglecting this complexity might lead to a misunderstanding of
-the structure and functioning of the ecosystems, and ultimately reduce
-the ability to predict ecosystem responses to perturbations (Montoya et
-al. 2009).
-
-In this review, we consider marine areas in the Southern hemisphere for
-which highly-resolved empirical food webs, in terms of species diversity
-and trophic interactions, have been previously described. These areas
-include: (1) San Jorge Gulf (45 - 47ºS, 65 - 68ºW), (2) Beagle Channel
-(\textasciitilde54ºS, 68ºW), (3) Burdwood Bank (\textasciitilde54ºS,
-59ºW), (4) Scotia Sea (48 - 58ºS, 50ºW), (5) Potter Cove (62ºS, 58ºW,
-Antarctica), and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica) (Figure
-1). The geographic locations of these marine biomes span from temperate
-to Antarctic, and are exposed to both environmental (sea warming,
-glacial retreat) and anthropogenic (fishery, pollution) stressors.
+Here we review for the first time stressor responses of marine food webs
+for areas located along a Southwest Atlantic to Antarctic gradient (45 -
+78ºS, Figure 1). We considered proven and expected changes in food webs
+driven by global change-related stressors in selected areas along this
+large-scale latitudinal range. The aim of this review is threefold: 1)
+describe the complexity and structure of marine food webs along the
+Southwest Atlantic to Antarctic axis from a network perspective; 2)
+identify the ongoing global change-related stressors for each marine
+ecosystem containing the food webs; and 3) review proven food web
+changes and elaborate on a series of alternative hypotheses on how the
+identified stressors might affect food web features (energy flow,
+stability and topology), combining information on node- and
+network-level properties. To identify the main stressors, we performed
+an exploratory and configurative review instead of a systematic review
+(Haddaway et al. 2015), because our objective was to formulate
+evidenced-based hypotheses rather than providing an exhaustive list of
+species-level stressors for each ecosystem. Finally, we suggest which
+additional data and analyses are needed to gain insights into the
+stressors' effects on food web properties in the Southwest Atlantic to
+Antarctic region.
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+\subsection{2. Assessment of the food web structure and stressors in the
+Southwest Atlantic - Antarctic
+region}\label{assessment-of-the-food-web-structure-and-stressors-in-the-southwest-atlantic---antarctic-region}
+
+The Southwest and the Atlantic sectors of the Southern Ocean comprise
+one of the most biologically productive regions of the world's oceans
+(Acha et al. 2004; Latorre et al. 2023). The referred region extends
+from San Jorge Gulf (45ºS) in the Patagonian shelf to the Weddell Sea
+(78ºS) in the Southern Ocean and covers a well-connected oceanic area
+(Matano et al. 2010; Guihou et al. 2020).
+
+Throughout this region, many studies address the ecology of
+predator-prey relationships but most of these studies are restricted to
+a few interacting species or certain components of the food web such as
+fish, crustaceans, and benthos (e.g., Vinuesa and Varisco (2007),
+Padovani et al. (2012), Pasotti et al. (2015), Riccialdelli et al.
+(2020), Saunders et al. (2019), Pasti et al. (2021), Cordone et al.
+(2022)). Only few studies consider the complexity of trophic
+interactions within highly resolved food webs containing hundreds of
+species, ranging from phytoplankton, zooplankton, benthos, fish,
+seabirds to whales (but see Jacob et al. (2011), Marina et al. (2018),
+Funes et al. (2022), López-López et al. (2022), Rodriguez et al. (2022),
+Marina et al. (in rev.)). Neglecting this complexity might lead to a
+misunderstanding of the structure and functioning of the ecosystems and
+ultimately reduce the ability to predict ecosystem responses to
+perturbations (Montoya et al. 2009).
+
+The Southwest Atlantic - Antarctic marine biota has been and is
+currently subjected to a variety of stressors (e.g., sea warming,
+glacial retreat, ice changes, acidification, species invasion,
+fisheries, and contamination). Here, we consider a stressor as a global
+change variable if it causes a quantifiable change, irrespective of its
+direction (increase or decrease), in a biological response (Orr et al.
+2020). This aligns with the framework established during the early years
+of the International Geosphere-Biosphere Programme (IGBP) for
+classifying driving forces. These driving forces are grouped into those
+that modify the composition of the Earth's fluid envelopes (e.g., sea
+warming, acidification), and those that originate as local processes but
+attain global importance due to their widespread impact (e.g., species
+invasion, fisheries) (Vitousek 1992; Sage 2020). Although it is
+well-known that multiple stressors act in concert at any given time
+(e.g., warming and fishery; acidification and contaminants) (Gutt et al.
+2021), to date stressor assessments have been performed individually.
+Moreover, the potential for interactive effects of two or more stressors
+(synergy or antagonism) (Côté et al. 2016) is almost unknown for the
+region (Rowlands et al. 2021).
+
+In this review, we included six large marine areas in the Southern
+Hemisphere for which highly-resolved empirical food webs in terms of
+species diversity and trophic interactions have been previously
+described: (1) San Jorge Gulf (\textasciitilde45 - 47ºS, 65 - 68ºW)
+(Funes et al. 2022), (2) Beagle Channel (\textasciitilde54ºS, 68ºW)
+(Rodriguez et al. 2022), (3) Burdwood Bank (\textasciitilde54ºS, 59ºW)
+(Marina et al. in rev.), (4) Scotia Sea (\textasciitilde48 - 58ºS, 50ºW)
+(López-López et al. 2022), (5) Potter Cove (62ºS, 58ºW, Antarctica)
+(Marina et al. 2018), and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica)
+(Jacob et al. 2011; Marina et al. 2024) (Figure 1). The geographic
+locations of these marine biomes span from temperate Atlantic waters to
+Antarctic, and are exposed to global change stressors (e.g., sea
+warming, glacial retreat, fishery, pollution) (Sage 2020), of which some
+are locally more important, e.g., fisheries in the San Jorge Gulf or
+glacial retreat in the Antarctic.
+
+In the following subsections, we describe the complexity and structure
+of the mentioned marine food webs, identify the main stressors, the
+species (or trophic species), and the parameters affected. Table 1
+summarizes the properties of the marine food webs (number of nodes,
+trophic interactions, connectance, path length, mean trophic level, and
+omnivory); Table 2 provides a list of the main stressors affecting
+species inhabiting each area, considering: stressors' nature, species
+and parameter affected, and locality.
 
@@
 
-San Jorge Gulf is the northernmost study area considered in this review.
-It is a partially enclosed basin spanning approximately 34,000 km2 and
-\textasciitilde100 m of maximum depths, located from Cabo dos Bahias
-(44°55'S) to Cabo tres Puntas (47°06'S) (Figure 1). The shallower
-northern and southern ends of the Gulf (with depths \textasciitilde40 m)
-present two prominent frontal systems. These systems are the areas of
-highest productivity (Glembocki et al. 2015). The Gulf's productivity
-supports large invertebrate and vertebrate fisheries (Góngora et al.
-2012), as well as marine mammal and seabird populations (Yorio 2009).
-The San Jorge Gulf food web comprises 165 nodes and 1015 trophic
-interactions with a connectance of 0.04. The percentage of top predators
-is 16\%, 78\% of intermediate nodes and 6\% of basal nodes; 60\% of
-predators are omnivorous (Table 1). The most connected nodes are: the
-Argentine red shrimp Pleoticus muelleri, the squat lobster Gimothea
-gregaria, squids (Illex argentinus as dominant species) and Amphipoda.
-Notably, these nodes present mid-trophic positions in the food web (3.0,
-2.5, 3.6 and 2, respectively) (Funes et al. 2022).
-
-At a southern latitude, the Beagle Channel (54°52'S, 68°8'W) is an
-interoceanic passage located at the southernmost tip of South America,
-spanning 240 km in length and 5 km in width (\textasciitilde1200 km2),
-and a range depth of 0 - 140 m (Figure 1). It features complex
-coastlines, varying bathymetry, a prevailing west-to-east circulation
-pattern, and a significant longitudinal gradient of glacial freshwater
-discharge (Schloss et al. 2023). Bruno et al. (2023) suggests that
-locally produced suspended particulate organic matter (mostly composed
-by phytoplankton) and organic matter accumulated in the sediments
-(macroalgae-originated detritus) are the primary food sources for the
-marine ecosystem, as opposed to allochthonous materials. Beagle Channel
-food web includes 145 nodes and 1115 trophic interactions with a
-connectance of 0.05 (Table 1). The food web is suggested to have a
-wasp-waist structure, where the following species play a crucial role in
-the dynamics of the ecosystem: Fueguian sprat Sprattus fuegensis,
-longtail southern cod Patagonotothen ramsayi, black southern cod P.
-tessellata, frogmouth Cottoperca trigloides, and squat lobster Grimothea
-gregaria (Riccialdelli et al. 2020). Moreover, the squat lobster has
-been identified as a species responsible for linking modules and
-connecting the entire food web (Rodriguez et al. 2022).
+\subsubsection{2.1 San Jorge Gulf}\label{san-jorge-gulf}
+
+San Jorge Gulf is the northernmost study area considered in this review
+(Figure 1), located from Cabo dos Bahias (44°55'S) to Cabo tres Puntas
+(47°06'S). It is a partially enclosed basin spanning approximately
+34,000 km\^{}2 and \textasciitilde100 m of maximum depths. The gulf's
+productivity supports large invertebrate and vertebrate fisheries
+(Góngora et al. 2012), as well as marine mammal and seabird populations
+(Yorio 2009). Two prominent frontal systems meet in the shallower
+northern and southern ends of the gulf (with depths \textasciitilde40
+m), which are also the places of highest productivity (Glembocki et al.
+2015).
+
+The San Jorge Gulf food web contains 165 nodes (trophospecies) and 1015
+trophic interactions with a connectance of 0.04. The percentage of top
+predators is 16\%, 78\% of the nodes are intermediate and 6\% are basal;
+60\% of the consumers are omnivorous (Table 1). The most connected nodes
+are the Argentine red shrimp \emph{Pleoticus muelleri}, the squat
+lobster \emph{Gimothea gregaria}, squids (\emph{Illex argentinus} as
+dominant species), and Amphipoda. Notably, these nodes are positioned at
+mid-trophic levels in the food web (3, 2.5, 3.6, and 2, respectively)
+(Funes et al. 2022).
+
+The gulf is subject to several global change stressors (Table 2),
+especially fisheries (González-Zevallos and Yorio 2006, 2011; Galván et
+al. 2022). By discarding species, trawl fisheries add new trophic
+interactions to the food web which results in decreasing trait
+variability and stability of the system (Rincón-Díaz et al. 2021; Funes
+et al. 2022). Moreover, this has changed the availability of resources
+to some predators. For example, the Argentine hake \emph{Merluccius
+hubbsi}, one of the main bycatch species, has become a prey item of
+non-diving seabirds, like the kelp gull \emph{Larus dominicanus}
+(González-Zevallos and Yorio 2006) and reef fish (Funes et al. 2019).
+Although juveniles of \emph{M. hubbsi} is largely the main bycatch
+species, 29 cartilaginous and 69 bony local fish species were also
+registered as incidental catch between 2005 and 2014 (Bovcon et al.
+2013; Ruibal Nuñez 2020). This level of impact has triggered a shift in
+the functional diversity of fish assemblages in the gulf, homogenizing
+their trophic function (Rincón-Díaz et al. 2021), for example in the
+sites with the historical highest fishing activity, the fish assemblage
+experienced a relative increase in midwater fusiform species and lost
+variability in their depth range (Rincón-Díaz et al. 2021). Other
+functional changes were a decrease in the maximum sizes of individual
+fish, together with a drop in elasmobranch biomass and an increase in
+crustacean biomass (Funes 2020). The significant increase in crustacean
+biomass was mainly due to the increase in the Argentine red shrimp and
+the squat lobster (Funes 2020). These species have become the most
+important prey for the most abundant fish in the area, the Argentine
+hake and the narrownose smooth-hound \emph{Mustelus schmitti} (Belleggia
+et al. 2017; Pasti et al. 2021). However, since commercial fisheries
+ceased their activities in the San Jorge Gulf in 2015 (Annex I,
+Resolution CFP No 7/2018), the effects mentioned above from trawl
+fisheries on the structure and function of the ecosystem may have
+changed since then. Nowadays only small-scale trawling from artisanal
+fishery is practiced in the gulf. Sea warming is another important
+stressor in the San Jorge Gulf, because of the southward shifts of
+northern fish populations to the area (Galván et al. 2022). Signs of sea
+warming have been detected in the gulf and nearby regions. Anomalous
+bottom temperature increments of up to 2°C have been observed in the
+gulf since 2000 (Isla and Cortizo 2024), and a positive trend in sea
+surface temperature of 0.3°C/0.4°C per decade over a 30-year series
+(Saraceno et al. 2022; Risaro et al. 2022). Additionally, a positive
+trend in sea surface temperature (\textasciitilde0.5 °C increase in the
+last 20 years) has been reported for the Nuevo and San Jose Gulfs, both
+located close to and northward of the San Jorge Gulf (Williams and
+Nocera 2023). The region is especially prone to be affected by
+climate-driven shifts in species ranges because it is situated in the
+ecotone of two biogeographic provinces, the Argentine (30°S - 44°S) and
+the Magellanic (43°S - 55°S) (Balech and Ehrlich 2008). In addition to
+tropicalization from northern fish populations, alien species are also
+documented to affect demersal assemblages of fish and macroinvertebrates
+in the gulf (Galván et al. 2022). Finally, the gulf is exposed to urban
+and industrial pollution (Verga et al. 2020). In particular, there is an
+oil monobuoy from which oil manipulation and general oil transport along
+the Patagonian coast registered several oil spills and chronic oil
+discharges (García-Borboroglu et al. 2008). Other marine systems
+impacted by the oil spill have shown extraordinary mortality events for
+cetacean (Litz et al. 2014), sea turtles (Wallace et al. 2017), and
+important decrease in marine bird populations (Irons et al. 2000) sea
+otters (Garrott et al. 1993) and macroalgae (Southward and Southward
+1978), with cascading effects throughout the food web (Peterson 2001).
+
+\subsubsection{2.2 Beagle Channel}\label{beagle-channel}
+
+Located at a more southern latitude (\textasciitilde54ºS, 68ºW), the
+Beagle Channel (Figure 1) is an interoceanic passage at the southernmost
+tip of South America, spanning 240 km in length and 5 km in width
+(\textasciitilde1200 km\^{}2), with a depth range of 0 - 140 m. It
+features complex coastlines, varying bathymetry, a prevailing
+west-to-east circulation pattern, and a significant longitudinal
+gradient of glacial freshwater discharge (Schloss et al. 2023). Bruno et
+al. (2023) suggests that locally produced suspended particulate organic
+matter (mostly composed of phytoplankton) and organic matter accumulated
+in the sediments (macroalgae-originated detritus) are the primary food
+sources for the marine ecosystem, as opposed to allochthonous materials.
+
+The Beagle Channel food web includes 145 nodes and 1115 trophic
+interactions with a connectance of 0.05 (Table 1). This food web is
+hypothesized to have a wasp-waist structure (i.e., the structure and
+dynamics of the ecosystem are regulated primarily by mid-trophic level
+species), where the following species play a crucial role in the
+dynamics of the ecosystem: Fueguian sprat \emph{Sprattus fuegensis},
+longtail southern cod \emph{Patagonotothen ramsayi}, black southern cod
+\emph{P. tessellata}, frogmouth \emph{Cottoperca trigloides}, and squat
+lobster \emph{G. gregaria} (Riccialdelli et al. 2020). Moreover, the
+squat lobster has been identified as a species linking food web modules
+and connecting the entire food web (Rodriguez et al. 2022).
+
+A main local stressor in the Beagle Channel is the introduction of
+invasive species (Table 2). Salmonidae were introduced to Tierra del
+Fuego in the 1930s. Especially, the Chinook salmon \emph{Oncorhynchus
+tshawytscha} causes concern. The detection of this species in Tierra del
+Fuego dates back to April 2006, and its population has been expanding
+since then (Nardi et al. 2019). Being a top predator, the Chinook salmon
+can compete for resources with several native predators in the Beagle
+Channel (Correa and Gross 2008), but also prey on them. This is the case
+for Notothenioids (\emph{Eleginops maclovinus}, \emph{Patagonotothen
+tessellata}, \emph{P. cornucola}, \emph{P. sima}, \emph{Paranotothenia
+magellanica}, \emph{Harpagifer bispinis}), the Atherinidae
+\emph{Odontesthes smitti} and \emph{O. nigricans}, the Fuegian sprat,
+and larvae of king crabs (\emph{Lithodes antarcticus} and
+\emph{Paralomis granulosa}) (Fernández et al. 2010). Ciancio et al.
+(2008) observed that Chinook salmon primarily feeds on sprats in the
+Southern Patagonian Shelf Ecosystem area and display trophic levels
+comparable to those of intermediate-sized fish and cephalopod predator
+species, showing significant dietary overlap with the Magellanic penguin
+\emph{Spheniscus magellanicus}. Another potential competitor for Chinook
+salmon in the Beagle Channel, sharing a similar diet, is the native
+Commerson's dolphin \emph{Cephalorhynchus commersonii} (Riccialdelli et
+al. 2013). In the Beagle Channel, other stressors include contaminants
+like metals, perfluorinated compounds, hydrocarbons, and microplastics
+found in animal tissue (algae, mussel, fish, and guano) and sediments
+(Duarte et al. 2011; Llorca et al. 2012). Carbon and carbohydrate levels
+in Ushuaia Bay's (54°48′S, 68°18′W) surface sediments are similar to
+hypertrophic ecosystems (i.e., greater input of nutrients than an
+eutrophic situation), along with hydrocarbons and heavy metals linked to
+port and industrial activities (Gil et al. 2011; Commendatore et al.
+2012). Ferreira et al. (2021) showed that the black southern cod in
+Ushuaia Bay may be exposed to endocrine-disrupting compounds from urban
+and industrial pollution. Moreover, Pérez et al. (2020) and Ojeda et al.
+(2021) found microplastics in the Chilean mussel \emph{Mytilus
+chilensis} and the sea snail \emph{Nacella magellanica}, respectively.
+These studies link pollutants to port and industrial activities of
+Ushuaia; we therefore expect the area of the Beagle Channel closest to
+the city to be the most affected by contaminants. Contaminants
+potentially spread through the food web, magnifying the risk to higher
+trophic level taxa. In the Beagle Channel and Atlantic coast of Tierra
+del Fuego food webs mercury concentrations rose with benthivory, and
+higher mercury was found in phytoplankton and the squat lobster. This
+latter species connects pelagic and benthic habitats, so any disruption
+to them could disrupt the food web (Rodriguez et al. 2022). Dodino et
+al. (2022) found the highest mercury levels in Magellanic penguin
+feathers from offshore colonies in Tierra del Fuego. Recently, Ushuaia's
+kelp forests have also seen changes in composition along with a decrease
+in biodiversity as a result of urban pollution (Kaminsky et al. 2023).
+It is important to note that sea warming might be a less significant
+stressor in the Beagle Channel compared to the other areas, as global
+warming is melting glaciers and the influx of cold freshwater is
+actually slightly cooling the seawater (Saraceno et al. 2022).
+
+\subsubsection{2.3 Burdwood Bank}\label{burdwood-bank}
 
 The so-called Burdwood Bank ecosystem comprises Marine Protected Areas
-Namuncurá - Burdwood Bank I and II, meaning the shallow submarine
-plateau named Burdwood Bank with a 200 m isobath boundary, and a deep
-slope that reaches 4000 m in depth, respectively (Administración de
-Parques Nacionales 2022) (Figure 1). Physical features in the plateau
-are fairly stable, with salinity averaging 34 all year round and
-temperature ranging between 4 and 8ºC (Acha et al. 2004). The plateau is
-surrounded by steep flanks of up to 4000 m depth, protected by the
-Marine Protected Area Namuncurá - Burdwood Bank II (32,000 km2;
-\textasciitilde55º - 56ºS, \textasciitilde58º - 62ºW). Intense upwelling
-and mixing occur in relation to the slope, entraining deep nutrient-rich
-waters into the photic layer (Matano et al. 2019), and resulting in a
-fairly homogeneous water column both spatially and temporally (Matano et
-al. 2019). The Burdwood Bank food web comprises 379 nodes and 1788
-interactions, with a connectance of 0.01, and an asymmetric degree
-distribution (i.e.~most of the species have a relatively low number of
-interactions and few species concentrate most of them). Almost half of
-the consumers are omnivores (0.48), and the network displays a
-small-world pattern (Marina et al. in rev.) (Table 1).
-
-The Scotia Sea is a deep-sea basin, delimited by the Drake Passage to
-the West and by the island complex of the Scotia Arc to the North, East,
-and South, with an approximate extension of 1.5 x 106 km2 and a depth
-range of 0 - 3000 m (Murphy et al. 2006) (Figure 1). Its oceanography is
-dominated by the Antarctic Circumpolar Current, which is spatially
-structured by frontal systems (Whitworth 1980). The South Antarctic
-Circumpolar Current Front subdivides the Scotia Sea into two
-biogeographic regions: the Northern Scotia Sea is characterized by
-higher and more variable temperatures, and the Southern Scotia Sea by
-lower and more stable temperatures and influenced by seasonal sea ice
-(Raymond 2011). The analysis of the Northern and Southern Scotia Sea
-food webs shows that the former is relatively more complex than the
-latter: with higher species richness (218 vs 192) and interactions
-(10008 vs 7241) and a higher connection overall (0.21 vs 0.20). As
-expected from a more complex network, the path length is shorter in the
-Northern Scotia Sea food web. In the same sense, the Southern Scotia Sea
-network displays a greater proportion of omnivores and a lower mean
-trophic level (López-López et al. 2022) (Table 1).
+Namuncurá - Burdwood Bank I and II (\textasciitilde54ºS, 59ºW), meaning
+the shallow submarine plateau named Burdwood Bank with a 200 m isobath
+boundary, and a deep slope that reaches 4000 m in depth, respectively
+(Administración de Parques Nacionales 2022) (Figure 1). Physical
+features in the plateau are fairly stable, with salinity averaging 34
+all year round and temperature ranging between 4 and 8ºC (Acha et al.
+2004). The plateau is surrounded by steep flanks of up to 4000 m depth,
+protected by the Marine Protected Area Namuncurá - Burdwood Bank II
+(32,000 km\^{}2). Intense upwelling and mixing occur in relation to the
+slope, entraining deep nutrient-rich waters into the photic layer
+(Matano et al. 2019), and resulting in a fairly homogeneous water column
+both spatially and temporally (Matano et al. 2019).
+
+The Burdwood Bank food web comprises 379 nodes and 1788 interactions,
+with a connectance of 0.01, and an asymmetric degree distribution
+(i.e.~most of the species have a relatively low number of interactions
+and few species concentrate most of them). Almost half of the consumers
+are omnivores (48\%), and the network displays a small-world pattern
+(Marina et al. in rev.) (Table 1). This network pattern implies a rapid
+spread of a perturbation (e.g., contaminant, population fluctuation,
+local extinction) throughout the food web due to a short distance among
+species but, at the same time, a greater resistance caused by the
+confinement of perturbations mainly within subnetworks as a result of a
+high clustering coefficient (Bornatowski et al. 2017; Dormann et al.
+2017).
+
+The main stressors reported for the ecosystem of the Marine Protected
+Areas Namuncurá within Burdwood Bank I and II are related to human
+activities such as fisheries and contamination (Table 2). Several
+fisheries targeting demersal fish operate in the vicinity and within the
+Marine Protected Areas. The fishery of the Patagonian toothfish
+\emph{Dissostichus eleginoides} has gained prominence in recent years
+(Allega et al. 2020; Gorini et al. 2021). Although these are regulated
+by the Argentinean government, incidental bycatches do occur, where
+demersal fish of the genera \emph{Coelorinchus} and \emph{Macrourus},
+seabirds and benthic invertebrates (30+ taxa) are the most common
+bycatches (Gaitán and Marí 2016; Martínez et al. 2022). Noteworthy,
+among the invertebrates caught, eight species are indicator taxa of
+vulnerable marine ecosystems (Gaitán and Marí 2016; Schejter and Albano
+2021). However, independent assessments of these bycatches suggest no
+significant impact on the populations (Gaitán and Marí 2016; Martínez et
+al. 2022). Besides bycatches, seabirds are being affected by fisheries
+due to discards, altering their diet; the most frequently encountered
+species are black-browed albatross \emph{Thalassarche melanophris},
+Southern giant petrel \emph{Macronectes giganteus}, Cape petrel
+\emph{Daption capense}, Southern royal albatross \emph{Diomedea
+epomophora}, Northern giant petrel \emph{M. halli}, and white-chinned
+petrel \emph{Procellaria aequinoctialis} (Tamini et al. 2023).
+Nevertheless, there is a lack of knowledge considering their role in the
+ecosystem and the potential joint effect of both target fish and bycatch
+in a broader food web framework. Contaminants such as microplastics and
+mercury occur in the water column of the Burdwood Bank ecosystem (Cossi
+et al. 2021; Fioramonti et al. 2022; Di Mauro et al. 2022).
+Microplastics are distributed along the entire water column, from
+surface to deep waters (3-2450 m) (Di Mauro et al. 2022). More
+importantly, microplastics were found in soft tissues of benthic
+macroinvertebrates (sea stars \emph{Henricia obesa} and \emph{Odontaster
+penicillatus}) and benthopelagic fish (\emph{Patagonotothen guntheri}
+and \emph{P. ramsayi}), which not only incorporated the contaminant from
+the environment through their filter-feeding system but could also get
+it indirectly from prey organisms already containing plastics in their
+tissues (Cossi et al. 2021). Notably, one of the contaminated species is
+the longtail southern cod \emph{P. ramsayi}. This species is part of the
+core group of species that drive the ecosystem through the suggested
+wasp-waist control (Riccialdelli et al. 2020). Mercury transfer and
+biomagnification are occurring at a greater pace than near coastal areas
+such as the Beagle Channel (Fioramonti et al. 2022). The Fuegian sprat
+\emph{S. fuegensis}, a pelagic fish with a mid-trophic level in the food
+web, has the highest levels of mercury recorded (Fioramonti et al.
+2022). Considering the wasp-waist control of the Fuegian sprat in the
+food web (Riccialdelli et al. 2020), a rapid and widespread
+contamination to the top predators is expected (Fioramonti et al. 2022).
+Despite evidence of warming of surface, mid-water and bottom layers (100
+m) in Burdwood Bank (Franco et al. 2020a), studies on the oceanographic
+aspects of the system are lacking. Warming impacts on the species and
+trophic interactions in Burdwood Bank are also unknown.
+
+\subsubsection{2.4 Scotia Sea}\label{scotia-sea}
+
+The Scotia Sea is a deep-sea basin (\textasciitilde48 - 58ºS, 50ºW),
+delimited by the Drake Passage to the West and by the island complex of
+the Scotia Arc to the North, East, and South, with an approximate
+extension of 1.5 x 106 km\^{}2 and a depth range of 0 - 3000 m (Murphy
+et al. 2006) (Figure 1). Its oceanography is dominated by the Antarctic
+Circumpolar Current, which is spatially structured by frontal systems
+(Whitworth 1980). The South Antarctic Circumpolar Current Front
+subdivides the Scotia Sea into two biogeographic regions: the Northern
+Scotia Sea, characterized by higher and more variable temperatures, and
+the Southern Scotia Sea, characterized by lower and more stable
+temperatures and influenced by seasonal sea ice (Raymond 2011).
+
+Analysis of the Northern and Southern Scotia Sea food webs shows that
+the former is relatively more complex in terms of number of species and
+links than the latter: with more species richness (218 vs 192) and
+interactions (10008 vs 7241) and a slightly higher connectance (0.21 vs
+0.20). Mean path length is shorter in the Northern Scotia Sea food web,
+whereas the Southern Scotia Sea network displays a greater proportion of
+omnivores and a lower mean trophic level (López-López et al. 2022)
+(Table 1).
+
+The Scotia Sea is a vast and heterogenous oceanic region, where
+especially the zone around South Georgia island represent an area of
+interest, here referred to as `Northern Scotia Sea'. The majority of
+studies analyzing the stressors' effects come from this area (e.g.,
+Murphy et al. (2007); Whitehouse et al. (2008); Trathan (2023)) (Table
+2). The main stressor of the Scotia Sea is commercial fisheries. Krill
+fishery on \emph{Euphausia superba} not only impacts the targeted
+species, but also the many predators that depend on it as a food source
+(Hilborn et al. 2017). Yet, data currently available from monitoring of
+krill and its predators remain insufficient, hence identifying the
+potential fishery impacts on the ecosystem is difficult (Trathan et al.
+2021). Apart from krill fishery, two other commercial fisheries operate
+in the Scotia Sea, targeting Patagonian toothfish species \emph{D.
+eleginoides} and \emph{Dissostichus mawsoni}. The \emph{D. eleginoides}
+stock is linked to the stock at South Georgia (`Northern Scotia Sea')
+(Collins et al. 2010), while the \emph{D. mawsoni} stock is linked to
+the Antarctic continental shelf (`Southern Scotia Sea') (Soeffker et al.
+2022). Recently, Trathan (2023) has identified several concerns
+regarding aspects of these fisheries, highlighting that it is crucial to
+recognize ongoing changes such as the recovery of baleen whales and
+climate change. These factors increase uncertainty for fisheries
+managers, necessitating direct consideration in the management of
+harvested and dependent species.
+
+The Scotia Sea has experienced one of the largest levels of warming
+within the polar regions (Whitehouse et al. 2008). Together with the
+Southern Annular Mode anomalies, this has caused a long-term decrease in
+krill abundance; more pronounced in the northern than in the southern
+Scotia Sea (Murphy et al. 2007). Over the past 90 years, the Antarctic
+krill \emph{E. superba} also showed an increase in mean body length
+(Atkinson et al. 2019), likely altering predator-prey interactions.
+Moreover, it allows krill to reach colder feeding grounds near the
+seabed, with the potential to link krill to unexpected predators such as
+demersal fish (Schmidt et al. 2011). Because of warming, the krill
+distribution has shifted southward (Atkinson et al. 2019), changing the
+food web from a krill-based to a non-krill-based, where myctophid fish
+and squid are playing important roles as key species in a wasp-waist
+controlled system (Saunders et al. 2019). While the krill distribution
+has shifted southward, the most abundant calanoid copepods have
+maintained their distribution (Tarling et al. 2018). Mercury transfer
+and biomagnification are current processes occurring in the Scotia Sea,
+where the total concentration of contaminants increase with trophic
+level and are highest in notothenioid and myctophid fish (e.g.~\emph{D.
+eleginoides}, \emph{Gymnoscopelus nicholsi}), and seabirds (Seco et al.
+2021). During years of low Antarctic krill abundance, predators must
+deal with both the stress of reduced prey availability and the
+concurrent rise in mercury exposure (Seco et al. 2021).
+
+\subsubsection{2.5 Potter Cove
+(Antarctica)}\label{potter-cove-antarctica}
 
@@
 a depth range of 0 - 200 m located at 25 de Mayo/King George Island
-(62°14'S, 58°38'W, South Shetland Islands) on the West Antarctic
+(62°S, 58°W) on the South Shetland Islands of the West Antarctic
 Peninsula (Figure 1). The cove, bordered by the Fourcade Glacier, is
@@
 sources for secondary benthic production (Quartino and Boraso de Zaixso
-2008). The Potter Cove food web includes 110 nodes and 649 interactions,
-with an asymmetric degree distribution, and a connectance value of 0.05
-(Table 1). It presents a modular structure (groups of species interact
-more strongly with each other than with species belonging to other
-groups), that's positively associated with stability, since perturbation
-can be retained within modules (Rodriguez et al. 2022).
+2008).
+
+The Potter Cove food web includes 110 nodes and 649 interactions, and a
+connectance of 0.05 (Table 1). It presents an asymmetric degree
+distribution and a modular structure, i.e., groups of species interact
+more strongly with each other within modules than with species belonging
+to other modules (Rodriguez et al. 2022).
+
+Regional warming in the West Antarctic Peninsula recorded in the last
+half-century (Chown et al. 2022) has been one of the main stressors
+driving changes in Potter Cove (Table 2), a system highly dependent on
+glacier and sea ice dynamics (Deregibus et al. 2017). This has caused
+drastic environmental and biological transformations such as shifts in
+dominance within the benthic community (Schloss et al. 2012; Quartino et
+al. 2013; Sahade et al. 2015). In Potter Cove, there has been a
+decreasing trend in total sea ice cover since 1991 (Schloss et al.
+2012). Changes in the annual timing of landfast ice formation and the
+breakup of the sea ice cover has multiple effects on species (Michel et
+al. 2019). Warmer winters and springs result in earlier sea ice melt,
+causing an abrupt increase in the light available for benthic primary
+producers (Deregibus et al. 2020). Sea ice also mediates physical
+disturbances to the benthos by influencing sedimentation and iceberg
+scouring. These factors affect the production of macroalgae, albeit in
+opposite ways (Deregibus et al. 2017), and microphytobenthos (Hoffmann
+et al. 2019). On the other hand, sea ice is an important habitat for
+diatoms and their associated consumers, including copepods and the
+Antarctic krill (Flores et al. 2012), and thus important for
+bentho-pelagic nutrient and carbon cycling during winter. Additionally,
+a decrease in winter sea ice cover produces an increase in physical
+perturbation on benthic shallow communities in coastal shallows due to
+ice scouring (Deregibus et al. 2017). The glacier surrounding Potter
+Cove has been receding at an increasing rate since 1950 (Rückamp et al.
+2011), which has caused a massive discharge of sediment-laden meltwater
+(Meredith et al. 2018). Large quantities of suspended particles affect
+growth, survival, and reproduction of benthic species. This led to a
+major shift in the benthic community structure, from a filter
+feeders--ascidian domination to a mixed assemblage with scavengers and
+opportunistic species (Sahade et al. 2015), and the metabolic balance in
+benthos went from net autotrophy to heterotrophy (Braeckman et al.
+2021). Additionally, massive stranding events of the tunicate
+\emph{Salpa thompsoni} and the Antarctic krill linked to the presence of
+glacial meltwater have been reported (Fuentes et al. 2016). Rising
+temperatures leading to ice and glacial melting has also substantial
+impacts on pelagic primary productivity, since it reduces water
+salinity, affecting water column stratification, light penetration and
+nutrient availability for photosynthesis (Schloss et al. 2012). In
+Potter Cove, changes in biomass of most phytoplankton species have been
+observed under heat wave conditions, resulting in a shift from a
+microplankton to a nanoplankton dominated community (Antoni et al. 2020;
+Latorre et al. 2023). This means that in areas strongly affected by
+glacier melt, the planktonic food web is dominated by the microbial loop
+(i.e., ciliates and heterotrophic dinoflagellates preys upon
+nanophytoplankton, which are sequentially available prey for small
+omnivorous copepods), instead of being predominantly herbivorous (Garcia
+et al. 2016, 2019). In addition, phytoplankton species under these
+warming conditions showed a decrease in metabolic rate and in the
+quality of the fatty acid composition (Latorre et al. 2023).
+
+\subsubsection{2.6 Weddell Sea
+(Antarctica)}\label{weddell-sea-antarctica}
 
@@
 covered by continental ice that forms the coastline along the eastern
-and southern parts of the Weddell Sea. Within this shelf area, exists a
-complex three-dimensional benthic habitat characterized by substantial
-benthic biomasses and an intermediate to high diversity when compared to
-benthic boreal communities (Teixidó et al. 2002). The Weddell Sea food
-web exhibits a high level of network complexity, featuring the greatest
-number of nodes (490) and trophic interactions (16041) among the
-analyzed food webs in this review (Table 1). Its connectance (0.07) and
-other structural properties are intermediate compared to the other food
-webs. Recently, the interaction strengths of this food web were
-estimated, revealing the presence of numerous weak and few strong
-interactions, which is consistent with findings in other complex food
-webs (Nilsson and McCann 2016). Notably, this asymmetric distribution of
-interaction strength is likely to promote community persistence.
+and southern parts of the Weddell Sea. The shelf area is characterized
+by a complex three-dimensional benthic habitat, substantial benthic
+biomasses, and an intermediate to high diversity (Teixidó et al. 2002).
+
+The Weddell Sea food web exhibits a high level of network complexity,
+featuring the greatest number of nodes (490) and trophic interactions
+(16041) among the marine food webs of the Southern Hemisphere (Table 1).
+Its connectance (0.07), mean trophic level (2.62) and omnivory (51\%)
+are intermediate compared to the other food webs (Table 1). Recently,
+the interaction strengths of this food web were estimated, revealing the
+presence of numerous weak and few strong interactions (Marina et al.
+2024).
+
+In the Weddell Sea, the main stressors are related to warming impacts
+(sea warming, sea ice extent, iceberg scouring) (Table 2), where sea
+warming has been substantial since the early 1980s (Turner et al. 2020).
+For example, in 2017, the mean temperature for February reached 1.45°C,
+the highest monthly mean ever recorded, i.e., 0.56°C above the
+climatological mean (Turner et al. 2020). Warming has caused spatial and
+temporal reductions in sea ice, impacting both pelagic and benthic
+communities (Constable et al. 2014; Gutt et al. 2021). Since the start
+of satellite imaging in 1978, sea ice extent has reached new record
+lows. Some of the most pronounced impacts of decreasing sea ice are
+negative changes in primary productivity (Atkinson et al. 2004) and
+declines of the Antarctic krill. Moreover, reduced sea ice cover allows
+increased access to krill by its predators (Kawaguchi et al. 2009),
+which further contributes to its decline. Some outcomes of the krill
+decline are reduced energy intake by higher trophic levels such as
+humpback whales \emph{Megaptera novaeangliae} Braithwaite et al. (2015)
+which rely heavily on krill for foraging, as well as reduced carbon
+export due to fewer fecal pellets (Pauli et al. 2021). Many higher
+trophic level species in the Weddell Sea are greatly impacted by sea ice
+reductions due to loss of habitat and food source availability, such as
+the Antarctic petrel \emph{Thalassoica antarctica} - one of the most
+abundant seabirds in the Weddell Sea (Orgeira et al. 2021). Other
+impacted sea bird species are the emperor penguin \emph{Aptenodytes
+forsteri}. Reductions in sea ice constrain its population as evidenced
+by recent observations in the Bellingshausen Sea region (Fretwell et al.
+2023). The Arctic tern \emph{Sterna paradisaea} spends the summer in the
+Weddell Sea exploiting krill swarms under receding ice edges. Thus,
+continued warming is expected to gradually erode the abundance and
+distribution of marine seabirds in the Weddell Sea (Orgeira et al.
+2021). Many marine mammals depend on for breeding and foraging such as
+the Weddell and Crabeater seals (\emph{Leptonychotes weddellii} and
+\emph{Lobodon carcinophagus}) (Wege et al. 2021) and the Humpback whale.
+Reduced sea ice can significantly affect the breeding success of seals
+(Wege et al. 2021) and body condition of whales (Turner et al. 2020).
+Notothenioid fish, with \emph{Pleuragramma antarcticum} being the most
+abundant species, confront numerous stressors such as sea warming, sea
+ice decline, and ocean acidification, posing significant threats to
+their survival. While certain species exhibit physiological plasticity
+to cope with increased oxygen demand, most notothenioid fish are
+stenothermal and incapable of adjusting their metabolic functioning
+(Mintenbeck et al. 2012). Projections suggest that the preferred thermal
+habitat of the Antarctic toothfish, \emph{Dissostichus mawsoni}, an
+important fish species in the Weddell Sea ecosystem, may contract over
+the next three decades, underscoring the potential impact of global
+warming on these species (Constable et al. 2014). Iceberg scouring is a
+major factor in driving the high biodiversity of benthic communities in
+the Weddell Sea (Gutt and Starmans 2001). Even at 600 m depths, iceberg
+scouring has a strong effect on the benthic environment, disrupting the
+upper layers of the seabed and removing macrofauna. This patchy
+disturbance and distribution pattern occurs roughly every 200 square
+meters on the Antarctic continental shelf. Global warming is predicted
+to increase iceberg scouring frequency (Gutt 2001; Smale et al. 2008),
+disrupting the environment (Smale and Barnes 2008) with the potential
+for tipping points (Gutt et al. 2015). \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
 
@@
 Table 1. Complexity and structure properties of the marine food webs
-considered in the present review. Refer to Table 2 for definition of
+considered in the present review. Refer to Table S2 for definition of
 properties. mean TL: mean trophic level. Food webs are ordered by
@@
 
-\subsection{3. Environmental and anthropogenic stressors in the
-Southwest Atlantic - Antarctic
-region}\label{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}
-
-A stressor is any environmental or anthropogenic variable that causes a
-quantifiable change, irrespective of its direction (increase or
-decrease), in a biological response (Orr et al. 2020). In the light of
-this, the southwest Atlantic - Antarctic marine biota has been and is
-currently subjected to a variety of stressors (e.g.~sea warming, glacial
-retreat, ice changes, acidification, species invasion, fisheries, and
-contamination). Although it is well-known that multiple stressors act in
-concert at any given time (e.g.~warming and fishery; acidification and
-contaminants) (Gutt et al. 2021), to date stressor assessments have been
-performed individually. Moreover, the potential for interactive effects
-of two or more stressors (synergy or antagonism) (Côté et al. 2016) is
-almost unknown for the region (Rowlands et al. 2021).
-
-In the following subsections, we describe the main environmental and
-anthropogenic stressors, and the species (or trophic species) and
-parameters affected reported for the marine ecosystems that contain the
-food webs considered in this review. In Table S2 we provide an
-exhaustive list of all stressors affecting species inhabiting each area,
-considering: the type of stressor, species and parameter affected, and
-locality.
-
-\subsubsection{3.1 San Jorge Gulf}\label{san-jorge-gulf}
-
-San Jorge Gulf experienced several environmental and anthropogenic
-stressors (Table S2). Trawl fisheries discard several species and add
-new trophic interactions to the food web which resulted in a decrease in
-trait variability and the stability of the system (Rincón-Díaz et al.
-2021; Funes et al. 2022). Moreover, it changed the availability of prey
-to several predators. For example, Merluccius hubbsi one of the main
-bycatch species, became prey item to non-diving seabirds, like the kelp
-gull Larus dominicanus (González-Zevallos and Yorio 2006) and reef
-fishes (Funes et al. 2019). Although juveniles of M. hubbsi are largely
-the main bycatch item, 29 other cartilaginous and 69 bony local fish
-species were also registered as incidental catch between 2005 and 2014
-(Bovcon et al. 2013; Ruibal Nuñez 2020). This level of impact triggered
-a shift in the functional diversity of the assemblages homogenizing the
-trophic function of fishes (Rincón-Díaz et al. 2021). Other functional
-changes were a decrease in the maximum sizes of individual fish,
-together with a drop in elasmobranchs biomass and an increase in
-crustaceans biomass (Funes 2020). The significant increase in crustacean
-biomass was mostly due to the increase in Pleoticus muelleri and
-Grimothea gregaria populations (Funes 2020). These species rapidly
-became the most important prey for the most abundant fishes in the area:
-M. hubbsi and Mustelus schmitti (Pasti et al. 2021). However, the
-above-mentioned effects of trawl fisheries on the structure and function
-of the San Jorge Gulf community may have changed again, since the
-fisheries ceased activity in 2015 (Annex I, Resolution CFP No 7/2018),
-remaining a small trawling artisanal fishery.
-
-Sea warming is another important environmental stressor in the San Jorge
-Gulf, because of the southward shifts of northern fish populations to
-the Gulf (Galván et al. 2022). The San Jorge Gulf is especially prone to
-be affected by climate-driven shifts in species ranges, because it is
-located in the ecotone between two biogeographic provinces, the
-Argentine (30°S - 44°S) and the Magellanic (43°S - 55°S) (Balech and
-Ehrlich 2008). In addition to this tropicalization from northern fish
-populations, alien species are also documented to affect the demersal
-assemblage (fish and macroinvertebrates) in the Gulf (Galván et al.
-2022). Finally, San Jorge Gulf is exposed to urban and industrial
-pollution due to an oil monobuoy from which oil manipulation and general
-oil transport along the Patagonian coast registered several oil spills
-and chronic oil discharges (García-Borboroglu et al. 2008). Other marine
-systems impacted by oil spill showed an important decrease in marine
-bird populations (Irons et al. 2000), seals and macroalgae (e.g. Paine
-et al. (1996)), with examples of cascading effects throughout the food
-web (Peterson 2001).
-
-\subsubsection{3.2 Beagle Channel}\label{beagle-channel}
-
-A main anthropogenic stressor in the Beagle Channel is the introduction
-of invasive species (Table S2). Salmonidae were introduced to Tierra del
-Fuego in the 1930s. Especially Chinook salmon Oncorhynchus tshawytscha
-causes concern. The detection of Chinook salmon in Tierra del Fuego
-dates back to April 2006, and its population has been expanding since
-then (Nardi et al. 2019). Being a top predator Chinook salmon can
-compete with several native species in the Beagle Channel (Correa and
-Gross 2008), and prey over native species such as Notothenioids
-(Eleginops maclovinus, Patagonotothen tessellata, P. cornucola, P. sima,
-Paranotothenia magellanica, Harpagifer bispinis), the Atherinidae
-Odontesthes smitti and O. nigricans, the Fuegian sprat Sprattus
-fuegensis, and larvae of king crabs (Lithodes antarcticus and Paralomis
-granulosa) (Fernández et al. 2010). Ciancio et al. (2008) observed that
-Chinook salmon in the Southern Patagonian Shelf Ecosystem Area primarily
-feed on sprats and display trophic levels comparable to those of
-intermediate-sized fish and cephalopod predators species, showing
-significant dietary overlap with Magellanic penguins (Spheniscus
-magellanicus). Another potential competitor for Chinook salmon in the
-Beagle Channel is the Commerson's dolphin (Cephalorhynchus commersonii),
-which shares a similar diet (Riccialdelli et al. 2013).
-
-In the Beagle Channel, other anthropogenic stressors include
-contaminants like metals, perfluorinated compounds, hydrocarbons, and
-microplastics found in animal tissue and sediments. Some studies
-reported varying heavy metal levels in sea mussel tissues and sediments,
-indicating bioavailability differences (Duarte et al. 2011). Other
-research found similar carbon and carbohydrate levels in Ushuaia Bay's
-surface sediments to those in hypertrophic ecosystems, along with
-hydrocarbons and heavy metals linked to port and industrial activities
-(Gil et al. 2011). Commendatore et al. (2012) identified three distinct
-hydrocarbon accumulation zones in the Bay. Llorca et al. (2012) found
-high levels of perfluorinated compounds in algae, fish, and guano.
-Ferreira et al. (2021) showed that black southern cod in Ushuaia Bay may
-be exposed to endocrine-disrupting compounds from urban and industrial
-pollution. Pérez et al. (2020) and Ojeda et al. (2021) found
-microplastics in M. edulis chilensis and Nacella magellanica,
-respectively. These studies link pollutants to Ushuaia (54°48′S 68°18′W)
-and its port and industrial activities. We expect the Beagle Channel
-area closest to the city to be most affected. Contaminants can spread
-through the food web, magnifying the risk to higher-level organisms.
-Fioramonti et al. (2022) studied mercury transfer in three southwest
-Atlantic Ocean food webs and found biodilution in the Beagle Channel and
-Atlantic coast of Tierra del Fuego webs. However, mercury concentrations
-rose with benthivory in these webs, and higher mercury was found in
-phytoplankton and Grimothea gregaria. Squat lobsters connect pelagic and
-benthic habitats, so any disruption to them could disrupt the food web
-(Rodriguez et al. 2022). Dodino et al. (2022) found the highest mercury
-levels in Magellanic penguin feathers from offshore colonies in Tierra
-del Fuego. Recently, Ushuaia's kelp forests have seen a decrease in
-biodiversity and changes in macroalgae composition due to urban
-pollution (Kaminsky et al. in prep.).
-
-\subsubsection{3.3 Burdwood Bank}\label{burdwood-bank}
-
-The stressors reported for the ecosystem of the Marine Protected Areas
-Namuncurá within Burdwood Bank I and II are mostly anthropogenic; there
-is a lack of studies focusing on the environmental stressors that are
-known to be occurring at a regional scale (e.g.~sea surface warming,
-Franco et al. (2020)) (Table S2). Several fisheries targeting demersal
-fishes operate in the vicinity and within the ecosystem of the Marine
-Protected Areas (i.e.~Marine National Reserve management category). The
-Patagonian fisheries on the toothfish Dissostichus eleginoides has
-gained prominence in recent years (Allega et al. 2020; Gorini et al.
-2021). Although these are regulated by the Argentinean government,
-incidental catches do occur, where demersal fishes of the genera
-Coelorinchus and Macrourus, seabirds and benthic invertebrates (30+
-taxa) are the most common bycatches (Gaitán and Marí 2016; Martínez et
-al. 2022). Noteworthy, among the invertebrates caught, 8 species are
-indicator taxa of vulnerable marine ecosystems (Gaitán and Marí 2016;
-Schejter and Albano 2021). Independent assessments of these bycatches
-suggest no significant impact on the communities (Gaitán and Marí 2016;
-Martínez et al. 2022). Besides bycatch, species of seabirds are being
-affected by the fishery due to discards, altering its diet; the most
-frequently encountered species are Black-browed albatross Thalassarche
-melanophris, Southern giant petrel Macronectes giganteus, Cape petrel
-Daption capense, Southern royal albatross Diomedea epomophora, Northern
-giant petrel M. halli, and White-chinned petrel Procellaria
-aequinoctialis (Tamini et al. 2023). Nevertheless, there is a lack of
-knowledge considering the species' role in the ecosystem and the
-potential joint effect of both target fishes and bycatch in a broader
-food web framework.
-
-Anthropogenic contaminants such as microplastics and mercury are present
-in the water column of the Burdwood Bank ecosystem (Cossi et al. 2021;
-Fioramonti et al. 2022; Di Mauro et al. 2022). Microplastics are
-distributed all along the water column, from surface to deep waters
-(3-2450 m) (Di Mauro et al. 2022). More importantly, microplastics were
-found in soft tissues of benthic macroinvertebrates (sea stars Henricia
-obesa and Odontaster penicillatus) and benthopelagic fishes
-(Patagonotothen guntheri and P. ramsayi), which not only incorporated
-the contaminant from the environment through their filter-feeding system
-but could also get it indirectly from prey organisms already containing
-plastics in their tissues (Cossi et al. 2021). Notably, one of the
-contaminated species, the long tail southern cod Patagonotothen ramsayi,
-is part of the core group of species that drive the ecosystem through
-the suggested wasp-waist control (Riccialdelli et al. 2020). Mercury
-transfer and biomagnification are ongoing processes in the ecosystem,
-which are occurring at a greater pace than near coastal areas (Beagle
-Channel) (Fioramonti et al. 2022). It's important to note that the
-Fuegian sprat Sprattus fuegensis, a pelagic fish with a mid-trophic
-level in the food web, presented the highest levels of mercury
-(Fioramonti et al. 2022). Considering the wasp-waist control of the
-Fuegian sprat in the food web (Riccialdelli et al. 2020), a rapid and
-widespread contamination to the top predators is expected (Fioramonti et
-al. 2022).
-
-In recent years, licenses for seismic studies and exploration of
-hydrocarbon resources have been granted all along the northwestern limit
-of the Marine Protected Areas (Secretaría de Gobierno de Energía Res. Nº
-65/2018). Although effects from these types of surveys on marine mammals
-and seabirds are well-known for other regions of the world (Nowacek et
-al. 2015), there is no particular knowledge for this ecosystem. However,
-several documents warn of the potential negative effects this may have
-on the species inhabiting the Burdwood Bank area (Allega et al. 2019; de
-Haro et al. 2022).
-
-Despite evidence of warming at surface, mid-water and bottom layers (100
-m) in Burdwood Bank (Franco et al. 2020), specific studies on the
-oceanographic aspects of the system are lacking. In this sense, there is
-a big question mark about the environmental stressors impact on the
-species and trophic interactions in Burdwood Bank.
-
-\subsubsection{3.4 Scotia Sea}\label{scotia-sea}
-
-The Scotia Sea is a vast and heterogenous oceanic region, where
-especially the areas around South Georgia island represents an area of
-interest, here referred to as `Northern Scotia Sea'. The majority of
-studies analyzing the stressors' effects come from this area.
-
-The Scotia Sea has experienced one of the largest levels of warming
-within the polar regions (Whitehouse et al. 2008). Together with the
-Southern Annular Mode anomalies this has caused a long-term decrease in
-krill abundance; more pronounced in the northern than in the southern
-Scotia Sea (Murphy et al. 2007). Over the past 90 years, the krill also
-showed an increase in mean body length (Atkinson et al. 2019), which may
-also alter predator-prey interactions and allow reaching cooler feeding
-grounds near the seabed, with the potential to link krill to unexpected
-predators (Schmidt et al. 2011). Another consequence of the mentioned
-environmental stressors, is a change in krill distribution due to a
-southward contraction (Atkinson et al. 2019). It is noteworthy here,
-that the distributional shift has not affected all species inhabiting
-the Northern Scotia Sea, and most abundant calanoid copepods have
-maintained their distribution (Tarling et al. 2018). Considering the
-above, food web models of the Northern Scotia Sea have suggested shifts
-in the structure and functioning of the food web, from krill-based to
-non-krill-based, where myctophid fishes and squid are playing important
-roles (Saunders et al. 2019).
-
-The principal anthropogenic stressor of the Scotia Sea is commercial
-fisheries. Krill fishery not only stresses the targeted species, but
-also the many predators that depend on it as a food source (Hilborn et
-al. 2017). Yet, data currently available from monitoring of krill and
-its predators remain insufficient, hence identifying the potential
-fishery impacts on the ecosystem is difficult (Trathan et al. 2021).
-Apart from krill fishery, two other commercial fisheries operate in the
-Scotia Sea, targeting Patagonian toothfish species Dissostichus
-eleginoides and D. mawsoni. The D. eleginoides stock is linked to the
-stock at South Georgia (`Northern Scotia Sea') (Collins et al. 2010),
-while the D. mawsoni stock is linked to the Antarctic continental shelf
-(`Southern Scotia Sea') (Soeffker et al. 2022). Despite the fact that
-the mentioned fisheries are certified by the Marine Stewardship Council
-standards, Trathan (2023) identified several concerns regarding aspects
-of fisheries itself, other species' population status (i.e.~recovery of
-baleen whales), and environmental stressors (i.e.~sea warming), which
-could have synergistic effects on the food web structure and functioning
-that are still unknown.
-
-Mercury transfer and biomagnification are current processes occurring in
-the Scotia Sea, where the total concentration of contaminants increase
-with trophic level and are highest in notothenioid and myctophid fishes
-(e.g.~Dissostichus eleginoides, Gymnoscopelus nicholsi), and seabirds
-(Seco et al. 2021). During years of low Antarctic krill abundance,
-predators must deal with both the stress of reduced prey availability
-and the concurrent rise in mercury exposure (Seco et al. 2021).
-
-\subsubsection{3.5 Potter Cove
-(Antarctica)}\label{potter-cove-antarctica}
-
-Regional warming in the last half century has been one of the main
-factors driving changes in Potter Cove (Western Antarctic Peninsula)
-(Chown et al. 2022). Sudden environmental changes have occurred, such as
-sea surface temperature increase, salinity decrease, suspended
-particulate matter loading and chlorophyll-a increase, all linked to
-climatic cycles (Southern Annular Mode and El Niño Southern Oscillation)
-(Schloss et al. 2012). Particularly, sea warming has produced drastic
-environmental and biological transformations (e.g.~shifts in dominance
-of benthic community) in the Potter Cove ecosystem (Schloss et al. 2012;
-Quartino et al. 2013; Sahade et al. 2015), a system highly dependent on
-sea-ice dynamics (Table S2). In Potter Cove, total sea ice cover has
-decreased since 1991 (Schloss et al. 2012). Changes in the annual timing
-of landfast ice formation and breakup of the sea ice cover has multiple
-effects on species in the food web (Michel et al. 2019). Warmer winters
-and springs result in earlier sea-ice melt, causing an abrupt increase
-in the light available benthic primary producers (Deregibus et al.
-2020). Sea ice also mediates physical disturbances to the benthos by
-influencing sedimentation and iceberg scouring. These factors affect the
-production of macroalgae, albeit in opposite ways (Deregibus et al.
-2017), and microphytobenthos (Hoffmann et al. 2019). On the other hand,
-sea ice is an important habitat for diatoms and its associated
-consumers, including copepods and krill (Flores et al. 2012), and thus
-important for bentho-pelagic nutrient and carbon cycling during winter.
-Additionally, a decrease in winter sea ice cover produces an increase in
-physical perturbation on benthic shallow communities in coastal shallows
-due to ice scouring (Deregibus et al. 2017). The glacier surrounding
-Potter Cove has been receding at an increasing rate since 1950 (Rückamp
-et al. 2011), which has caused a massive discharge of sediment-laden
-meltwater (Meredith et al. 2018). Large quantities of suspended
-particles affect growth, survival and reproduction of benthic species.
-This had led to a major shift in the benthic community structure, from a
-filter feeders--ascidian domination to a mixed assemblage with
-scavengers and opportunistic species (Sahade et al. 2015), and the
-metabolic balance in benthos went from net autotrophy to heterotrophy
-(Braeckman et al. 2021). Additionally, massive stranding events of the
-tunicate Salpa thompsoni and the euphausiid Euphausia superba (krill)
-linked to the presence of glacial meltwater have been reported (Fuentes
-et al. 2016). Rising temperatures leading to ice and glacial melting has
-also substantial impacts on pelagic primary productivity, since it
-reduces water salinity, affecting water column stratification, light
-penetration and nutrient availability for photosynthesis (Schloss et al.
-2012). In Potter Cove, changes in biomass of most phytoplankton species
-have been observed under heat wave conditions, resulting in a shift from
-a microplankton to a nanoplankton dominated community (Antoni et al.
-2020; Latorre et al. 2023). This means that in areas strongly affected
-by glacier melt, the planktonic food web is dominated by the microbial
-loop (ciliates and heterotrophic dinoflagellates preys upon
-nanophytoplankton, which are sequentially available prey for small
-omnivorous copepods), instead of being predominantly herbivorous (Garcia
-et al. 2016, 2019). In addition, phytoplankton species under these
-warming conditions showed a decrease in metabolic rates and in the
-quality of the fatty acids composition (Latorre et al. 2023).
-
-\subsubsection{3.6 Weddell Sea
-(Antarctica)}\label{weddell-sea-antarctica}
-
-In the Weddell Sea several stressors have already been triggered by
-global warming effects (Table S2), from which spatial and temporal
-reduction in sea ice is suggested to be driving changes in pelagic and
-benthic communities (Constable et al. 2014; Gutt et al. 2021). Sea ice
-extent has reached new record lows since the satellite era began in
-1978. Sea warming has been substantial in recent years: in 2017 the mean
-temperature for February reached 1.45°C, the highest monthly mean ever
-recorded (0.56°C above the climatological mean) (Turner et al. 2020). In
-this context, it has been suggested that Antarctic krill Euphausia
-superba has already declined as a result of productivity changes caused
-by sea ice declines (Atkinson et al. 2004). Declining sea ice cover
-allows increased access to krill by predators (Kawaguchi et al. 2009),
-which further contributes to decreased krill abundances. This in turn
-can result in reduced carbon export due to decreased fecal pellets from
-krill (Pauli et al. 2021).
-
-On the other hand, sea ice loss increases light availability, triggering
-primary production by phytoplankton in the short-term (Pineda-Metz et
-al. 2020). Furthermore, a warmer and more stable water column with a
-shallow upper mixed layer, is expected to enhance the dominance of
-cryptophytes over diatoms which may favor salp populations over krill
-populations; thereby reducing the magnitude of energy transfer to higher
-trophic levels and the seabed (Isla 2023).
-
-Higher trophic level species are expected to respond differently to
-global warming in the Weddell Sea. In this regard, Notothenioid fishes
-(e.g.~Pleuragramma antarcticum) face multiple stressors (sea warming,
-sea ice decline, ocean acidification) that threaten their survival.
-While some species exhibit physiological plasticity to compensate for
-increased oxygen demand, most notothenioid fishes are stenothermal and
-unable to adjust their metabolic functioning (Mintenbeck et al. 2012).
-It is anticipated that the thermal habitat preferred by the Antarctic
-toothfish Dissostichus mawsoni could undergo contraction in the coming
-three decades (Constable et al. 2014), further emphasizing the potential
-impact of global warming effects on these species. Marine mammals,
-Weddell and crabeater seals (Leptonychotes weddellii and Lobodon
-carcinophagus), exhibit varying levels of sensitivity. The latter
-exhibits a preference for breeding in close proximity to krill swarms,
-and thus is particularly susceptible to reductions in sea ice
-concentrations and sea surface temperatures. Rescued sea ice can
-significantly affect their post- and future breeding foraging success
-(Wege et al. 2021). In addition, the Antarctic petrel Thalassoica
-antarctica, which is one of the most abundant seabirds in the area, is a
-sea ice dependent forager and breeder (Orgeira et al. 2021); therefore
-the loss of this habitat will degrade its foraging success and
-reproductive output over time. The snow petrel Pagodroma nivea also
-relies heavily on sea ice for foraging and its colonies in the Weddell
-Sea may be affected. The emperor penguin Aptenodytes forsteri uses sea
-ice for breeding; any reductions could constrain its populations, as
-evidenced by recent observations in the Bellingshausen Sea region
-(Fretwell et al. 2023). The Arctic tern Sterna paradisaea spends the
-summer in the Weddell Sea exploiting krill swarms under receding ice
-edges, then declines in ice cover may reduce prey availability and
-quality of molting habitats. Continued warming is thus expected to
-gradually erode the abundance and distribution of these `primary
-species' that dominate the avifauna of the Weddell Sea through loss of
-critical sea ice habitat (Orgeira et al. 2021). Variations in sea ice
-extent have implications for great whales, such as the Humpback whale
-Megaptera novaeangliae, since their primary prey resource is the
-Antarctic krill (Braithwaite et al. 2015). Decreased winter ice coverage
-results in reduced suitable habitat and lower krill abundance
-(Braithwaite et al. 2015), with flow-on effects for whale body condition
-observed historically in harvest data. With climate projections
-indicating ongoing sea ice losses, further threats to critical krill
-populations pose risks to the energy intake and reproductive success and
-long-term viability of humpback whale populations dependent on
-consistent Antarctic feeding (Pallin et al. 2023).
-
-Iceberg scouring is a major factor in the high biodiversity of benthic
-communities in the Weddell Sea (Gutt and Starmans 2001). Even at 600 m
-depths, iceberg scouring has a strong effect on the benthic environment,
-disrupting the upper layers of the seabed and removing macrofauna. This
-patchy disturbance and distribution pattern occurs roughly every 200
-square meters on the Antarctic continental shelf. Global warming is
-predicted to raise iceberg scouring frequency (Gutt 2001; Smale et al.
-2008), disrupting the environment (Smale and Barnes 2008). Gutt et al.
-(2015) expects tipping points are significant due to these effects and
-lack of knowledge.
-
-\subsection{4. From species' stressors to food web
-effects}\label{from-species-stressors-to-food-web-effects}
+\subsection{3. From species' stressors to food web effects: a
+qualitative
+approach}\label{from-species-stressors-to-food-web-effects-a-qualitative-approach}
 
@@
 
-Environmental and anthropogenic stressor effects in the southwest and
-the Atlantic sector of the Southern Ocean have been mostly assessed
-individually and at the organism and/or population, i.e., at the node
-level (Table S2), with one exception: the effect of fisheries in the San
-Jorge Gulf food web (see section below for more details). To address the
-most plausible stressors effects on the selected food webs, given the
-current information, we built hypotheses for each study area. To this
-aim, we developed a theoretical framework considering the following: a)
-stressor(s), b) parameter(s) affected, c) node-level properties of the
-affected species, and d) network-level properties of the food web.
+Global change stressor effects in the Southwest and the Atlantic sector
+of the Southern Ocean have been mostly assessed individually and at the
+organism and/or population, i.e., at the node level (Table 2), with one
+exception: the effect of fisheries in the San Jorge Gulf food web (see
+section below for more details). To address the most plausible effects
+of the main stressors on the selected food webs, given the current
+information, we formulated a series of alternative hypotheses for each
+study area. To this aim, we developed a theoretical framework
+considering the following: a) stressor(s), b) parameter(s) affected, c)
+node-level properties of the affected species, and d) network-level
+properties of the food web.
 
 We considered that a stressor will affect one of the following species'
-characteristics or parameters: metabolism, biomass, distribution, and
-diet (Figure 2). `Metabolism' refers to any change related to metabolic
-rate, such as reproduction, hatching, larval development, growth and
-mortality, and contamination due to pollutants (e.g.~growth effect in
-filter-feeders due to sediment in water column in Potter Cove; endocrine
-disruption in fish due to urban pollutants in Beagle Channel). `Biomass'
+characteristics or parameters: metabolism, population biomass,
+distribution, and diet (Figure 2). `Metabolism' refers to any change
+related to metabolic rate, such as reproduction, hatching, larval
+development, growth and mortality (e.g.~growth effect in filter-feeders
+due to sediment in water column in Potter Cove; endocrine disruption in
+fish due to urban pollutants in Beagle Channel). `Population biomass'
 indicates an effect at the population level, where the density/abundance
@@
 \caption{Conceptual diagram: from species' stressors to food web
-effects. See text for explanation.}
+effects. A stressor (e.g., global warming) will affect one of the
+following species' characteristics: metabolism, population biomass,
+distribution, and diet. `Metabolism' refers to any change related to
+metabolic rate, such as reproduction, hatching, larval development,
+growth and mortality, and contamination due to pollutants. `Population
+biomass' indicates an effect at the population level, where the
+density/abundance is being impacted. `Distribution' entails a change at
+the population level in the geographic space occupied by a species.
+`Diet' includes alterations in the prey items of a species at the
+population level. Next, we considered node- and network-level properties
+relevant to the hypothesized stressor effects on the food webs. At the
+node-level, we included: a) degree, b) trophic position, c) omnivory
+index, and d) relative abundance. At the network-level, we considered:
+a) connectance, b) path length, c) mean trophic level, and d) omnivory.
+Finally, we elaborate a series of competing hypotheses on how the
+identified stressors might affect food web features (stability, energy
+flow, topology), combining information on node- and network-level
+properties.}
 \end{figure}
@@
 \newpage
+\begin{landscape}
 \scriptsize
 
-Table 2. Node and network-level properties used to build hypotheses on
-the stressors' effects.
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1963}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2617}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3925}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1495}}@{}}
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Property}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Definition}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Relevance for stressor effects}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Reference}
-\end{minipage} \\
-\midrule\noalign{}
+Table 2. Environmental and anthropogenic stressors reported for the
+study areas: San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea
+(North and South), Potter Cove, and Weddell Sea. Stressor categories:
+sea warming; glacial retreat; sediment in the water column; iceberg
+scouring; sea ice extent; ocean acidification; ocean acidification +
+plastics; microplastics; mercury; urban \& industrial pollution;
+fishery; alien species. The species affected were considered at the node
+level, whereas effects were considered at the organism and population
+levels. Categories of affected parameters and variables: metabolism;
+biomass; distribution; diet (see text for explanation). ``Locality''
+indicates whether a stressor for a given species was reported for the
+study area (`In situ') or in another area (`Elsewhere').
+
+\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
+\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
+\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
+
+\begin{longtable}{ L{2.1cm} L{2.5cm} L{4cm} L{2.5cm} L{2cm} L{3cm} }
+\hline
+\textbf{Study area} & \textbf{Stressor} & \textbf{Species affected} & \textbf{Parameter affected} & \textbf{Locality} & \textbf{Reference} \\
+\hline
 \endhead
-\bottomrule\noalign{}
+\endfoot
+\hline
 \endlastfoot
-\emph{Node-level} & & & \\
-Degree & Number of feeding interactions in which the species
-participates as prey and/or predator. & Perturbations to high-degree
-species may have more significant effects on the food web robustness to
-perturbations than low-degree species. & Dunne et al. (2002b); Jordán et
-al. (2007) \\
-Trophic position & Place in the food web relative to the basal resources
-that support the community. Classifies species in: basal, intermediate
-and top. & Perturbations on basal resources, intermediate species and
-top predators are expected to have large effects on the rest of their
-communities if ecosystem control is bottom-up, wasp-waist or top-down,
-respectively. & Williams and Martinez (2000); Thompson et al. (2007) \\
-Omnivory & Consumer resource use across trophic levels. & High-omnivore
-species (generalists) are more flexible than low-omnivore species to
-diet changes. & Thompson et al. (2007) \\
-Relative abundance & Species' density in proportion to the other species
-of the food web. & Perturbations on abundant (dominant) species are
-expected to have large effects on the stability and energy flux of the
-food and ecosystem, respectively. & Nilsson and McCann (2016) \\
-\emph{Network-level} & & & \\
-Conectance & Proportion of actual interactions among possible ones. &
-Estimator of community sensitivity to stressors. High connectance gives
-resistance and resilience to the food web. & Dunne et al. (2002a) \\
-Path length & Average distance, accounted by the number of interactions,
-between any pair of species. & Short distances enhance rapid and broad
-propagation of perturbations. & Albert and Barabási (2002) \\
-Mean TL & Average of all species' trophic position contained in the food
-web. & Influences the magnitude and efficiency of trophic transfer. A
-higher mean food chain length reflects increased energy availability and
-productivity. & Duffy et al. (2007); Olivier et al. (2019) \\
-Omnivory & Proportion of species that feed at different trophic levels.
-& It provides trophic flexibility to an ecosystem. Reduces probability
-of trophic cascades. & Kratina et al. (2012) \\
+
+\textbf{San Jorge Gulf} & & & & & \\
+& Sea warming & Fish assemblage \& its prey & Distribution & In situ &
+Galván et al. (2022) \\
+& Fishery & Demersal fish community & Biomass & In situ & Galván et al.
+(2022) \\
+& Fishery & Macroinvertebrates, fish and seabirds Di & et In & situ
+(\textbf{G?}) & onzalez-Zevallos2006; González-Zevallos and Yorio
+(2011); Yorio et al. (2017) \\
+& Alien species & Fish assemblage \& its prey & Distribution & In situ &
+Galván et al. (2022); Ciancio et al. (2010) \\
+& Urban \& industrial pollution & Seabirds \& benthic assemblage &
+Biomass & Elsewhere & Moore and Dwyer (1974); Buskey et al. (2016) \\
+\textbf{Beagle Channel} & & & & & \\
+& Urban \& industrial pollution & Macroalgae; Mytilus edulis chilensis,
+Patagonotothen tessellata & Metabolism & In situ & Giarratano and Amin
+(2010); Ferreira et al. (2021); Kaminsky et al. (2023) \\
+& Mercury & Phytoplankton, Zooplankton, \emph{Grimothea gregaria} &
+Metabolism & In situ & Fioramonti et al. (2022) \\
+& Microplastics & Mytilus edulis chilensis, Nacella magellanica &
+Metabolism & In situ & Pérez et al. (2020); Ojeda et al. (2021) \\
+& Alien species: Chinook salmon Oncorhynchus tshawytscha &
+Patagonotothen tessellata, Sprattus fuegensis & Diet/Biomass & In situ
+(the presence), Elsewhere (changes in prey biomass) & Fernández et al.
+(2010); Ciancio et al. (2008) \\
+\textbf{Burdwood Bank} & & & & & \\
+& Mercury & Dissostichus eleginoides, Sprattus fuegensis, Patagonotothen
+ramsayi, Cottoperca trigloides (fish) \& squids Me & tabolism In & situ
+(\textbf{F?}) & ioramonti2022 \\
+& Microplastics & Henricia obesa \& Odontaster penicillatus (sea stars);
+Patagonotothen guntheri \& P. ramsayi (fish) Me & tabolism In & situ
+(\textbf{C?}) & ossi2021; Pérez et al. (2021) \\
+& Fishery & Target: Dissostichus eleginoides. Bycatch: Macrourus sp.,
+Coelorinchus sp. (fish), Daption capense, Thalassarche melanophris,
+Macronectes giganteus, T. chrysostoma, Diomedea epomophora (seabirds),
+30+ spp macrobenthos Bi & omass El & sewhere (\textbf{G?}) & aitan2016;
+Martínez et al. (2022); Administración de Parques Nacionales (2022);
+Tamini et al. (2023) \\
+& Fishery & Thalassarche melanophris, Macronectes giganteus, Daption
+capense, Diomedea epomophora, M. halli, Procellaria aequinoctialis
+(seabirds) & Diet & Elsewhere & Tamini et al. (2023) \\
+\textbf{Scotia Sea, North \& South} & & & & & \\
+& Mercury & Krefftichthys anderssoni, Protomyctophum bolini, Electrona
+antarctica, Gymnoscopelus nicholsi, Gymnoscopelus braueri, Dissostichus
+eleginoides & Metabolism & In situ & Seco et al. (2021) \\
+& Ocean acidification + plastics & Euphausia superba, Limacina
+retroversa (Pteropoda) & Metabolism & In situ & Rowlands et al. (2021);
+Manno et al. (2022) \\
+& Sea warming & Euphausia superba & Metabolism & In situ & Murphy et al.
+(2007); Perry et al. (2020) \\
+& Sea warming & Euphausia superba & Distribution & In situ & Atkinson et
+al. (2019) \\
+& Fishery & Euphausia superba & Biomass & In situ & Trathan et al.
+(2021) \\
+\textbf{Potter Cove (Antarctica)} & & & & & \\
+& Sediment in water column & Microphytobenthos, macroalgae, benthic
+filter feeders (ascidians), pelagic filter feeders (krill, salps) &
+Metabolism & In situ & Sahade et al. (2015); Deregibus et al. (2016);
+Fuentes et al. (2016); Hoffmann et al. (2019) \\
+& Sea ice extent & Krill & Biomass & Elsewhere & Flores et al. (2012) \\
+& Sea ice extent & Benthic community (macroalgae, invertebrates) &
+Metabolism & Elsewhere & Clark et al. (2013); Campana et al. (2018) \\
+& Glacial retreat & Benthic community (macroalgae, invertebrates) &
+Biomass & In situ & Quartino et al. (2013); Lagger et al. (2017); Lagger
+et al. (2018) \\
+& Iceberg scouring & Benthic community & Biomass & In situ & Deregibus
+et al. (2017); Deregibus et al. (2023) \\
+& Sea warming & Phytoplankton & Metabolism, biomass & In situ & Antoni
+et al. (2020); Latorre et al. (2023) \\
+& Sea warming & Zooplankton & Metabolism, biomass, diet & In situ &
+Garcia et al. (2016); Garcia et al. (2019) \\
+& Sea warming & Fish & Metabolism & In situ, elsewhere & Strobel et al.
+(2013); Souza et al. (2018); Saravia et al. (2021) \\
+\textbf{Weddell Sea (Antarctica)} & & & & & \\
+& Iceberg scouring & Macrobentos & Biomass & In situ & Isla (2023); Gutt
+et al. (2015); Smale et al. (2008); Gutt et al. (1996) \\
+& Iceberg scouring & Hexactinellida sponges & Biomass & In situ & Gutt
+and Starmans (2001); Pineda-Metz et al. (2020); Gutt (2001); Gutt and
+Piepenburg (2003) \\
+& Ocean acidification & Primary producers / krill / foraminifera /
+flagellates & Metabolism & Elsewhere & Deppeler et al. (2020); Isla
+(2023); Gutt et al. (2015); Moy et al. (2009) \\
+& Ocean acidification & Euphausia superba, Pleuragramma antarcticum &
+Metabolism & In situ & Kawaguchi et al. (2010); Kawaguchi et al. (2013);
+Piñones and Fedorov (2016); Mintenbeck et al. (2012) \\
+& Sea warming & Large (diatoms) \& small (cryptophytes) phytoplankton,
+zooplankton (salps) & Metabolism & Elsewhere & Isla (2023); Gutt et al.
+(2015); Trebilco et al. (2020) \\
+& Sea warming & Euphausia superba, Nototheniid fish, Pleuragramma
+antarcticum Me & tabolism In & situ (\textbf{M?}) & eyer2017; Hill et
+al. (2013); Mintenbeck et al. (2012); Constable et al. (2014);
+Mintenbeck et al. (2012) \\
+& Sea ice extent & Phytoplankton, Lobodon carcinophaga, Hydrurga
+leptonyx, Leptonychotes weddellii, Ommataphoca rossii, Mirounga leonina,
+Arctocephalus gazella & Metabolism & In situ & Pineda-Metz et al.
+(2020); Wege et al. (2021); Siniff et al. (2008) \\
+& Sea ice extent & Euphausia superba, Pleuragramma antarcticum,
+Pagodroma nivea, Thalassoica antarctica, Pygoscelis adeliae & Metabolism
+& In situ & Orgeira et al. (2021); Braithwaite et al. (2015); Hill et
+al. (2013); Mintenbeck et al. (2012) \\
+& Sea ice extent & Megaptera novaeangliae & Metabolism & Elsewhere &
+Pallin et al. (2023) \\
+& Sea ice extent & Aptenodytes forsteri & Metabolism & Elsewhere &
+Orgeira et al. (2021) \\
 \end{longtable}
 
+\end{landscape}
+
 \normalsize
 
-\subsubsection{4.1 Main stressor effects in food webs in a southwest
-Atlantic - Antarctic
-gradient}\label{main-stressor-effects-in-food-webs-in-a-southwest-atlantic---antarctic-gradient}
-
-The most common stressor reported along the southwest Atlantic -
+\subsubsection{3.1 Hypotheses on the main stressor effects in food webs
+in a southwest Atlantic - Antarctic
+gradient}\label{hypotheses-on-the-main-stressor-effects-in-food-webs-in-a-southwest-atlantic---antarctic-gradient}
+
+The most common stressor reported along the Southwest Atlantic -
 Antarctic gradient is global warming, except for Beagle Channel and
 Burdwood Bank, which are more influenced by the introduction of an alien
-species and fisheries, respectively (section 3, Table 3). The main
+species and fisheries, respectively (Section 2, Table 2). The main
 characteristics of global warming in the region, and the most plausible
-drivers of change, are: sea warming, glacial retreat, elevated sediment
-input in the water column, and reduction of the sea ice extent. These
+drivers of change, are sea warming, glacial retreat, elevated sediment
+input to the water column, and reduction of the sea ice extent. These
 drivers act in different ways and magnitudes in the studied locations
@@
 this section, this does not mean that no other stressors act or interact
-with global warming in the study systems, potentially buffering the
-overall effect on the food web (e.g.~sea warming and fishery in San
-Jorge Gulf). Climate change has led to several well-documented impacts
-on marine species regarding distributional shifts induced by warming of
-marine currents (Wu et al. 2012; Poloczanska et al. 2013; Vergés et al.
-2019). Furthermore, warmer temperatures increase species metabolic rates
-(Brown et al. 2004). Changes in metabolic rates can subsequently
-translate into shifts in species traits (body size, Vucic-Pestic et al.
-(2011); Klein et al. (2018){]}, biomass (Perry et al. 2020) and
-distribution (Kortsch et al. 2015). Alterations in the species body size
-and distributions have ripple effects on feeding interactions, for
-example, it can introduce new feeding interactions (Vergés et al. 2014;
-Pecuchet et al. 2020), modify existing ones, and shorten energy pathways
-(Bartley et al. 2019; O'Gorman et al. 2019), and reduce trophic
-efficiencies (Vucic-Pestic et al. 2011).
+with global warming in the study systems, potentially buffering or even
+amplifying the overall effect on the food web (e.g.~sea warming and
+fishery in San Jorge Gulf). Climate change has led to several
+well-documented impacts on marine species regarding distributional
+shifts induced by warming of marine currents (Wu et al. 2012;
+Poloczanska et al. 2013; Vergés et al. 2019). Furthermore, warmer
+temperatures increase species metabolic rates (Brown et al. 2004).
+Changes in metabolic rates can subsequently translate into shifts in
+species traits (e.g.~body size, Vucic-Pestic et al. (2011); Klein et al.
+(2018)), population biomass (Perry et al. 2020), and distribution
+(Kortsch et al. 2015). Alterations in the species body size and
+distributions have ripple effects on feeding interactions, for example,
+it can introduce new feeding interactions (Vergés et al. 2014; Pecuchet
+et al. 2020), modify existing ones, and shorten energy pathways (Bartley
+et al. 2019; O'Gorman et al. 2019), and reduce trophic efficiencies
+(Vucic-Pestic et al. 2011).
+
+\paragraph{3.1.1 San Jorge Gulf}\label{san-jorge-gulf-1}
 
@@
 macroinvertebrates species (Vinuesa 2005; López-Gappa 2022) were
-registered in Patagonia, mostly in San Jorge Gulf in relation to the
+registered in Patagonia, mostly in San Jorge Gulf concerning the
 southward range shift of warm-temperate species. This distributional
@@
 expected (Bartley et al. 2019). In another temperate ecosystem, an
-increase in the number of fish species, led to an increase in functional
+increase in the number of fish species led to increases in functional
 diversity and predation rate (Sgarlatta 2023); consequences that may
@@
 
-In the middle of the latitudinal gradient (considered in this study),
-the Scotia Sea has experienced one of the largest levels of sea warming
-of any polar region (Whitehouse et al. 2008; Atkinson et al. 2019).
+\paragraph{3.1.2 Scotia Sea}\label{scotia-sea-1}
+
+In the middle of the latitudinal gradient considered in this study, the
+Scotia Sea has experienced one of the largest levels of sea warming of
+any polar region (Whitehouse et al. 2008; Atkinson et al. 2019).
 López-López et al. (2022) suggested that the southward distributional
@@
 perturbations spreading through the network (Stouffer and Bascompte
-2011), which may be offset by increased connectance enhancing robustness
-to species loss (Dunne et al. 2002b). In the northern Scotia Sea around
-South Georgia Island, we suggest that the declining krill biomass driven
-by sea warming (Atkinson et al. 2019), ocean acidification and pollution
-synergy (Rowlands et al. 2021), will reduce the energy transfer to top
-predators like seabirds and marine mammals. However, this may be
-buffered since the dominant copepod species have maintained their
-distribution (Tarling et al. 2018), but most importantly, showed an
-abundance increase in recent decades likely due to reduced predation and
-competition for food (Ward et al. 2018). All this is significant for the
-structure of the food web given the central role of krill and copepods,
-characterized by high degree and mid-trophic position (Table S1).
-Overall, the food web's inherent resilience, marked by high connectance
-and omnivory, added to the potential compensation for the krill decrease
-due to a copepod increase, may buffer against structural changes (Table
-3).
-
-In Potter Cove, a fjord-like Antarctic ecosystem, the impacts of climate
-change affect many species within the food web. Potter Cove has recently
-experienced frequent events of marine heatwaves, i.e.~prolonged periods
-of anomalously high sea surface temperatures (Oliver et al. 2018;
-Latorre et al. 2023). This has led to decreases in biomasses of
-different planktonic functional groups (Garcia et al. 2019; Latorre et
-al. 2023). Given the relatively low abundance of phytoplankton,
-zooplankton's low degree, and the modular configuration of the food web,
-we hypothesize that changes in these nodes, due to increased sea
-temperatures, will be retained in the basal pelagic compartment of the
-food web and will not expand to higher trophic levels. Benthic primary
-producers in Potter Cove are being influence by the decrease in winter
-sea ice cover (higher light availability), the increased levels of
-sediments in the water column due to glacial melt run-off (lower light
-penetration) and the newly free-ice areas available for colonization
-associated to glacier retreat. The overall local effect of climate
-change on macroalgae is a net increase in their production (Deregibus et
-al. 2023). It has been proposed that larger diversity in primary
-producers can support a more diverse food web with more specialized
-consumers (Iken et al. 2023). We expect to see differential effects of
-climate change on hard and soft bottom associated food webs (Cordone et
-al. 2020). Given the high relative abundance and the high degree of the
-macroalgae functional group (Table S1), we expect a longer hard bottom
-food web, wider consumer trophic niches, and that it will become more
-stable as sea ice cover decreases and the glacier retreats due to global
-warming. In soft bottom areas of the Cove, multiple food web nodes are
-being affected by ongoing warming effects: decrease in net primary
-production of benthic microalgae (Hoffmann et al. 2019), and changes in
-the benthic community biomass, distribution and composition (Sahade et
-al. 2015; Pasotti et al. 2015). Given that the Potter Cove food web's
-present low connectance and omnivory, we suggest fragility and potential
-trophic cascade effects (Marina et al. 2018) with pronounced changes in
-energy fluxes (Table 3).
-
-The southernmost location of the latitudinal gradient is the Weddell
-Sea, where the main effect of global warming is the decrease in sea ice
-extent, with reported anomalies in the past summer seasons (Fretwell et
-al. 2023). Declining sea ice extent has reduced the abundance of krill
-(Atkinson et al. 2004; Flores et al. 2012), and produced an increase in
-phytoplankton productivity (Pinkerton et al. 2021; Isla 2023), altering
-the plankton community structure, and benefiting cryptophytes over
-diatoms (Lin et al. 2021). Moreover, habitat loss from sea ice decline
-will reduce the foraging success and breeding sites of seabirds (e.g.,
-snow petrel Pagodroma nivea and emperor penguin Aptenodytes forsteri),
-decreasing their biomassess and modifying their distributions. The
-projected rise in iceberg scouring is expected to significantly alter
-the biomass and community structure of macrobenthos, which in turn will
-impact mid-trophic level predators such as demersal fish (Gutt 2001;
-Mintenbeck et al. 2012). While we do not anticipate large-scale
-topological changes in the food web, local extinctions could lead to
-such changes, particularly affecting benthic species (Gutt and
-Piepenburg 2003). Given that the impacted species---whether individually
-like krill, or collectively like macrobenthos---present a mid-trophic
-position, high biomass and high degree (Table S1), we hypothesize that
-significant shifts in energy fluxes will occur (Table 3). Additionally,
-the food web's low proportion of omnivores suggests reduced system
-resilience (Table 1), increasing the likelihood of regime changes (Gutt
-et al. 2015).
-
-The two ecosystems in the subantarctic region, the Beagle Channel and
-Burdwood Bank, are more affected by other anthropogenic stressors than
-warming. Although these areas are being impacted by sea warming,
-potentially affecting vertebrate and invertebrate species (Franco et al.
-2020), to date no studies exist for Beagle Channel and Burdwood Bank
-ecosystems. In the Beagle Channel, the introduction of chinook salmon, a
-non-native species, poses a significant risk to the existing food web
-(Fernández et al. 2010). We hypothesize that chinook salmon's predation
-on Fuegian sprat and black southern cod will disrupt the established
-patterns of interaction within the food web. Both of these prey species
-are crucial for food web dynamics due to their mid-trophic positions and
-relatively high abundance (Table S1). Moreover, we expect that changes
-in the black southern cod population will have a more significant impact
-on the food web than changes in the Fuegian sprat population, as the
-black southern cod has a higher degree (Table S1). Overall, these
-disruptions could have far-reaching effects on the ecosystem. This is
-particularly concerning given the short path length of the food web,
-which means that changes can quickly propagate through the system,
-affecting many species and potentially destabilizing the entire network.
-This phenomenon is further heightened by the ecosystem's inherent
-vulnerability to changes at mid-trophic levels, often referred to as
-wasp-waist control (Table 3). In the Burdwood Bank region, fishing
-activities may be the main stressor causing shifts in the food web
-(Table S2). We hypothesize that a combination of factors will
-destabilize the already fragile ecosystem, characterized by low
-connectance and low omnivory (Table 1). These factors include a decline
-in the biomass of the Patagonian toothfish -a key, highly-connected
-species (Table S1)- as well as smaller changes in the biomass of four
-mid-level fish species, five top-level seabird species, and over 30
-types of benthic macroinvertebrates due to bycatch (Gaitán and Marí
-2016; Martínez et al. 2022; Tamini et al. 2023). Additionally,
-alterations in the diets of six seabird species, caused by discarded
-catch (Tamini et al. 2023), are expected to disrupt the energy flow and
-further reduce the stability of the food web (Table 3).
+2011). In the northern Scotia Sea around South Georgia Island, we
+suggest that the declining krill biomass driven by sea warming (Atkinson
+et al. 2019), ocean acidification and pollution synergy (Rowlands et al.
+2021), will reduce the energy transfer to top predators like seabirds
+and marine mammals. However, this may be buffered because the dominant
+copepod species have maintained their distribution (Tarling et al.
+2018), but most importantly shown an abundance increase in recent
+decades likely due to reduced predation and competition for food (Ward
+et al. 2018). The potential compensation for the decrease in krill by
+increasing abundance of copepod may buffer against structural and
+functional changes in the food web (Table 3), since krill and copepod
+play similar (central) roles in the food web, characterized by a high
+degree and mid-trophic position.
+
+\paragraph{3.1.3 Potter Cove
+(Antarctica)}\label{potter-cove-antarctica-1}
+
+In Potter Cove, a fjord-like Antarctic ecosystem, the repercussions of
+climate change extend across numerous species. Noteworthy, these effects
+are non-uniform within the food web, manifesting differently across its
+various compartments (Cordone et al. 2020; Rodriguez et al. 2022).
+Potter Cove has recently experienced frequent events of marine
+heatwaves, i.e., prolonged periods of anomalously high sea surface
+temperature (Oliver et al. 2018; Latorre et al. 2023). This has led to
+decreases in biomasses of different planktonic functional groups (Garcia
+et al. 2019; Latorre et al. 2023). Given the relatively low abundance of
+phytoplankton and zooplankton's low mean degree, resulting in weak
+interaction strengths between these low trophic levels and higher ones
+(\textbf{Rodriguez2024?}), added to the modular configuration of the
+food web (Rodriguez et al. 2022), we hypothesize that changes in these
+nodes due to warming will be retained at the basal level of the pelagic
+compartment and will not expand to higher trophic levels. Benthic
+primary producers in Potter Cove are being influenced by the decrease in
+winter sea ice cover (higher light availability), the increased levels
+of sediments in the water column due to glacial melt run-off (lower
+light penetration) and the newly free-ice areas available for
+colonization associated to glacier retreat. The overall local effect of
+climate change on macroalgae is a net increase in their production
+(Deregibus et al. 2023). It has been proposed that larger diversity in
+primary producers can support a more diverse food web with more
+specialized consumers (Iken et al. 2023). Given the high relative
+abundance and the high degree of the macroalgae functional group (Table
+S1), we expect a longer hard bottom food web (i.e., number of
+interactions connecting low and high-trophic levels), wider consumer
+trophic niches, and a more stable benthic food web as sea ice cover
+decreases and glaciers retreat due to global warming. In soft bottom
+areas of the cove, multiple food web nodes are being affected by ongoing
+warming effects: decrease in net primary production of benthic
+microalgae (Hoffmann et al. 2019), and changes in the benthic community
+biomass, distribution and composition (Sahade et al. 2015; Pasotti et
+al. 2015). Given that the Potter Cove food web has low connectance and
+omnivory, we suggest fragility and potential trophic cascade effects
+(Marina et al. 2018), especially between species of the soft bottom
+compartment (Table 3). Overall, we anticipate significant shifts in
+energy fluxes, rather than alterations in the overall structure of the
+Potter Cove food web, with strengthening of connections within
+compartments.
+
+\paragraph{3.1.4 Weddell Sea
+(Antarctica)}\label{weddell-sea-antarctica-1}
+
+In the southernmost food web, the Weddell Sea, the main effect of global
+warming is the decrease in sea ice extent, with reported anomalies in
+the past summer seasons (Fretwell et al. 2023). Declining sea ice extent
+has reduced the abundance of krill (Atkinson et al. 2004; Flores et al.
+2012), and produced an increase in phytoplankton productivity (Pinkerton
+et al. 2021; Isla 2023), altering the plankton community structure, and
+benefiting cryptophytes over diatoms (Lin et al. 2021). Moreover,
+habitat loss from sea ice decline will reduce the foraging success and
+breeding sites of seabirds (e.g., snow petrel \emph{P. nivea} and
+emperor penguin), decreasing their population biomassess and modifying
+their distributions. The projected rise in iceberg scouring is expected
+to significantly alter the biomass and community structure of
+macrobenthos, which in turn will impact mid-trophic level predators such
+as demersal fish (Gutt 2001; Mintenbeck et al. 2012). While we do not
+anticipate large-scale topological changes in the mean food web
+attributes, local extinctions could lead to such changes, particularly
+affecting benthic species (Gutt and Piepenburg 2003). Given that the
+impacted species---whether individually like krill, or collectively like
+macrobenthos and notothenioids (e.g., \emph{P. antarcticum})---present a
+mid-trophic position, high population biomasses and high degree (Table
+S1), we hypothesize that significant shifts in energy fluxes will occur
+(Table 3). Additionally, the food web's low proportion of omnivores
+suggests reduced system resilience (Table 1), increasing the likelihood
+of regime changes (Gutt et al. 2015).
+
+\paragraph{3.1.5 Beagle Channel and Burdwood
+Bank}\label{beagle-channel-and-burdwood-bank}
+
+The Beagle Channel and Burdwood Bank -the two ecosystems in the
+subantarctic region- are more affected by other stressors than warming.
+That said, there are impacts of warming in these ecosystems, especially
+affecting vertebrate and invertebrate species (Franco et al. 2020a), but
+generally studies addressing these impacts are lacking for the Beagle
+Channel and Burdwood Bank ecosystems. In the Beagle Channel, the
+introduction of chinook salmon, a non-native species, poses a
+significant risk to the existing food web (Fernández et al. 2010). We
+hypothesize that chinook salmon's predation on Fuegian sprat and black
+southern cod will disrupt the established patterns of interaction within
+the food web. Both of these prey species are crucial for food web
+dynamics due to their mid-trophic positions and relatively high
+abundance (Table S1). Moreover, we expect that changes in the black
+southern cod population will have a more significant impact on the food
+web than changes in the Fuegian sprat population, as the black southern
+cod has a higher degree (Table S1). Overall, these disruptions could
+have far-reaching effects on the ecosystem. This is particularly
+concerning given the short path length of the food web, which means that
+changes can quickly propagate through the system, affecting many species
+and potentially destabilizing the entire network. This phenomenon is
+further heightened by the ecosystem's inherent vulnerability to changes
+at mid-trophic levels, often referred to as wasp-waist control (Table
+3). In the Burdwood Bank region, fishing activities may be the main
+stressor causing shifts in the food web (Table 2). We hypothesize that a
+combination of factors will destabilize the already fragile ecosystem,
+characterized by low connectance and low omnivory (Table 1). These
+factors include a decline in the biomass of the Patagonian toothfish -a
+highly-connected, key species (Table S1)- as well as smaller changes in
+the population biomass of four mid trophic level fish species, five top
+trophic level seabird species, and over 30 types of benthic
+macroinvertebrates due to bycatch (Gaitán and Marí 2016; Martínez et al.
+2022; Tamini et al. 2023). Additionally, alterations in the diets of six
+seabird species, caused by discarded catch (Tamini et al. 2023), are
+expected to disrupt the energy flow and further reduce the stability of
+the food web (Table 3).
 
@@
 
-Table 3. Summary of food web (FW) effects according to the main
-stressors reported for each study area. *Industrial trawl fishery ceased
-in 2015 remaining artisanal trawling activity.
+Table 3. Summary of hypothesized food web (FW) effects according to the
+main stressors reported for each study area. *Industrial trawl fishery
+ceased in 2015 remaining artisanal trawling activity.
 
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3194}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2759}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2644}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2759}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1609}}@{}}
 \toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Study area}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Stressor}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Food web effects}
-\end{minipage} \\
-\midrule\noalign{}
 \endhead
@@
 \endlastfoot
-\textbf{San Jorge Gulf} & & \\
+\multirow{2}{=}{\textbf{Study area}
+
+======================= \textbf{San Jorge Gulf}} &
+\multirow{2}{=}{\textbf{Stressor}
+
+======================} &
+\multicolumn{2}{>{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.4368} + 2\tabcolsep}@{}}{%
+\multirow{2}{=}{\textbf{Hypothesis on food web effects} \textbar{}
+=======================+ \textbar{}}} \\
+ \\
 & Fishery* & ↑ FW connectance
@@
 
-↓ functional diversity \\
+↓ functional diversity & \\
 & Sea warming & Shifts in FW topology
@@
 
-↑ functional diversity \\
-\textbf{Beagle Channel} & & \\
+↑ functional diversity & \\
+\textbf{Beagle Channel} & & & \\
 & Alien species & Shifts in FW topology
 
-↑ spread of perturbations \\
-\textbf{Burdwood Bank} & & \\
+↑ spread of perturbations & \\
+\textbf{Burdwood Bank} & & & \\
 & Fishery & Shifts in main energy fluxes
 
-↓ FW stability \\
-\textbf{Scotia Sea} & & \\
+↓ FW stability & \\
+\textbf{Scotia Sea} & & & \\
 & Sea warming & ↑ FW connectance
@@
 
-↑ spread of perturbation \\
-\textbf{Potter Cove (Antarctica)} & & \\
-& Sea warming & ↓ perturbation spreading \\
+↑ spread of perturbation & \\
+\textbf{Potter Cove (Antarctica)} & & & \\
+& Sea warming & ↓ perturbation spreading & \\
 & Sea ice decline + glacial retreat & Differential impacts, by
@@
 
-↑ FW fragility \& trophic cascades (SS) \\
-\textbf{Weddell Sea (Antarctica)} & & \\
+↑ FW fragility \& trophic cascades (SS) & \\
+\textbf{Weddell Sea (Antarctica)} & & & \\
 & Sea ice decline + iceberg scouring & Shifts in main energy fluxes
@@
 
-↓ resilience \\
+↓ resilience & \\
 \end{longtable}
@@
 
-\subsection{5. Gaps and future
+\subsection{4. Gaps and future
 perspectives}\label{gaps-and-future-perspectives}
 
-In the selected study areas along the southwest Atlantic to Antarctic
-latitudinal gradient, several stressors may directly affect consumers'
-diets triggered by modified environmental conditions (sea warming,
-reduced sea ice extent) and new species (due to species' distributional
-shifts and introductions). Moreover, the population trends (biomasses
-and abundances) of important species are also changing (Funes 2020;
-Hindell et al. 2020; Woods et al. 2023) driving shifts in their roles as
-either predators or prey (e.g. Belleggia et al. (2017), Pasti et al.
-(2021)). These diet and biomass shifts should be investigated in order
-to generate reliable predictions of food web responses to multiple
-stressors in the southwest Atlantic - Antarctic region. One could argue
+In the selected study areas along the Southwest Atlantic to Antarctic
+latitudinal axis, several stressors may directly affect consumers' diets
+triggered by modified environmental conditions (sea warming, reduced sea
+ice extent) and new species (due to species' distributional shifts and
+introductions). Moreover, the population trends (biomasses and
+abundances) of important species are also changing (Funes 2020; Hindell
+et al. 2020; Woods et al. 2023) driving shifts in their roles as either
+predators or prey (e.g. Belleggia et al. (2017), Pasti et al. (2021)).
+These diet and population biomass shifts should be investigated to
+generate reliable predictions of food web responses to multiple
+stressors in the Southwest Atlantic - Antarctic region. One could argue
 that both shifts might increase the complexity of food webs in the short
@@
 a significant reduction in target and incidental catch species (e.g.
-Dulvy et al. (2014)), thereby promoting food web simplification.
-
-Since this review deals with qualitative data of prey-predator
+Dulvy et al. (2014)), thereby promoting food web simplification and
+decreases in robustness.
+
+Since this review deals with qualitative data of predator-prey
 interactions and stressor effects influencing them, adding quantitative
-data to the food webs (i.e.~interaction strength) and to the stressors
-(i.e.~magnitude) would lead to a better comprehension of how a given
+data to the food webs (e.g., interaction strength) and to the stressors
+(e.g., magnitude) would lead to a better understanding of how a given
 stressor acts on specific species which might translate into food web
 effects. In this context, it would be useful to develop quantitative
-food web models where the strength of interactions reflect energy fluxes
-among species (Nilsson and McCann 2016; Kortsch et al. 2021). Emerging
-methods such as bioenergetic food web modeling have been proposed in
-this regard and present promising ways to estimate shifts in species
-interactions within food webs as a response to stressors (Gellner et al.
-2023; Gauzens et al. n.d.). Shifts that can lead to changes in overall
-ecosystem functioning and stability.
+food web models where the strength of interactions reflects energy
+fluxes among species (Nilsson and McCann 2016; Kortsch et al. 2021).
+Emerging methods such as bioenergetic food web modeling have been
+proposed in this regard and present promising ways to estimate shifts in
+species interactions and energy fluxes within food webs as a response to
+stressors (Gellner et al. 2023; Gauzens et al. n.d.). Shifts that can
+lead to changes in overall ecosystem functioning and stability.
 
@@
 regions. Almost no information exists on the impact of global warming
-effects (sea warming, glacial retreat, ocean acidification) on
-communities in these ecosystems, though warming of mid-water and bottom
-layers have been shown at a regional scale (Franco et al. 2020). Yet in
-Beagle Channel recent experimental studies have tested the tolerance of
-fishes to scenarios of sea warming and/or acidification suggesting
-potential metabolic impacts on species (Lattuca et al. 2018; Lattuca et
-al. 2023).
+(sea warming, glacial retreat, ocean acidification) on communities in
+these ecosystems, although warming of mid-water and bottom layers has
+been shown at a regional scale (Franco et al. 2020a). Yet, in Beagle
+Channel recent experimental studies have tested the tolerance of fish to
+scenarios of sea warming and/or acidification suggesting high
+vulnerability to projected climate-driven environmental conditions
+(Lattuca et al. 2018; Lattuca et al. 2023).
 
@@
 is challenging (Gutt et al. 2021). This complexity arises partly because
-of potential for antagonistic effects, where impacts cancel each other
-out, or synergistic effects, where the combined impact is greater than
-the sum of individual effects (Boyd et al. 2015; Côté et al. 2016).
+of the potential for antagonistic effects, where impacts cancel each
+other out, or synergistic effects, where the combined impact is greater
+than the sum of individual effects (Boyd et al. 2015; Côté et al. 2016).
 Moreover, these interactive effects are complicated to handle in the
@@
 
-\subsection{Conclusions}\label{conclusions}
-
-We have reviewed the main environmental and anthropogenic stressors
-acting in six different areas along a large-scale latitudinal gradient,
-from temperate Atlantic to cold Antarctic ecosystems. Using a
-theoretical framework that combines species and food web level data, we
-suggest how warming effects may impact food web structure and
-functioning. These qualitative predictions are intended to serve as the
-basis for future studies in marine ecosystems of the Southern Hemisphere
-that aim at quantifying the magnitude of these stressors and how they
-are affecting quantitative food web properties, such as energy fluxes
-and stability. There is an urgent need to assess these changes using a
-holistic and quantitative framework where the magnitude of stressors and
-species interactions are taken into account.
+In this review, we proposed a series of alternative hypotheses on how
+global stressors may affect food webs in the Southwest Atlantic to
+Southern Ocean. Despite being qualitative, this is a first important
+step in synthesizing food webs and stressor effects on food webs for
+this region. These qualitative assessments must be complemented with
+further investigations that test their validity. To achieve this, we
+suggest using a combination of observational data such as reported
+biomass changes and historic records of sea temperature for the region
+(e.g., Laptikhovsky et al. 2013; Funes et al. 2019; Franco et al. 2020b;
+Winter and Arkhipkin 2023), and food web modeling methods such as
+stressor-response matrices (Bracewell et al. (2019)) and flux modeling
+(e.g., Gauzens et al. (2019); Beauchesne et al. (2021); Polazzo et al.
+(2022)).
+
+\subsection{5. Conclusions}\label{conclusions}
+
+We reviewed global change stressors acting in six different areas along
+a large-scale latitudinal gradient from temperate Atlantic to cold
+Antarctic ecosystems. Using a theoretical framework that combines
+species and food web-level data, we suggest how warming effects may
+impact food web structure and functioning. Besides there is an important
+amount of uncertainty, these qualitative predictions are intended to
+serve as the basis for future studies in marine ecosystems of the
+Southern Hemisphere that aim at quantifying the magnitude of these
+stressors and how they are affecting quantitative food web properties,
+such as energy fluxes and stability. There is an urgent need to assess
+these changes using a holistic and quantitative framework where the
+magnitude of stressors and species interactions are taken into account.
 
@@
 Atlántico Sudoccidental - Antártida?'', funded by Consejo Nacional de
-Investigaciones Científicas (CONICET, code PIP 2022-2024 \#0907).
+Investigaciones Científicas (CONICET, code PIP 2022-2024 \#0907),
+Argentina. S.K. gratefully acknowledges the support from the Walter and
+Andrée de Nottbeck Foundation, Finland.
 
@@
 Protegidas (DNAMP), Argentina.
-
-\bibitem[\citeproctext]{ref-Albert2002}
-Albert, R., and Barabási, A.-L. 2002. Statistical mechanics of complex
-networks. Reviews of Modern Physics \textbf{74}(1): 47--97. American
-Physical Society.
-doi:\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}.
 
@@
 
-\bibitem[\citeproctext]{ref-Allega2019}
-Allega, L., Braverman, M.S., Cabreira, A.G., Campodónico, S., Colonello,
-J.H., Derisio, C.M., Di Mauro, R.P., Gaitán, E.N., Hozbor, M., Irusta,
-G., Lutz, V.A., Marí, N., Militelli, M.I., Moriondo, P., Navarro, G.,
-Orlando, P., Pajaro, M., Prandoni García, N.I., Prosdocimi, L., Reta,
-R., Rico, R., Riestra, C.M., Segura, V., Schejter, L., Schiariti, A.,
-Souto, V., and Verón, E.M. 2019. {Estado del conocimiento biol{ó}gico
-pesquero de los principales recursos vivos y su ambiente, con relaci{ó}n
-a la exploraci{ó}n hidrocarbur{í}fera en la Zona Econ{ó}mica Exclusiva
-Argentina y adyacencias}. INIDEP. {[}accessed 10 August 2023{]}.
-
 \bibitem[\citeproctext]{ref-Anton2019}
@@
 doi:\href{https://doi.org/10.1111/maec.12445}{10.1111/maec.12445}.
+
+\bibitem[\citeproctext]{ref-Bornatowski2017}
+Bornatowski, H., Barreto, R., Navia, A.F., and de Amorim, A.F. 2017.
+Topological redundancy and {``small-world''} patterns in a food web in a
+subtropical ecosystem of {Brazil}. Marine Ecology \textbf{38}(2):
+e12407.
+doi:\href{https://doi.org/10.1111/maec.12407}{10.1111/maec.12407}.
 
@@
 
+\bibitem[\citeproctext]{ref-Bracewell2019}
+Bracewell, S., Verdonschot, R.C.M., Schäfer, R.B., Bush, A., Lapen,
+D.R., and Van den Brink, P.J. 2019. Qualifying the effects of single and
+multiple stressors on the food web structure of {Dutch} drainage ditches
+using a literature review and conceptual models. Science of The Total
+Environment \textbf{684}: 727--740.
+doi:\href{https://doi.org/10.1016/j.scitotenv.2019.03.497}{10.1016/j.scitotenv.2019.03.497}.
+
 \bibitem[\citeproctext]{ref-Braeckman2021}
@@
 
+\bibitem[\citeproctext]{ref-Buskey2016}
+Buskey, E.J., White, H.K., and Esbaugh, A.J. 2016. Impact of {Oil
+Spills} on {Marine Life} in the {Gulf} of {Mexico}: {EFFECTS ON
+PLANKTON}, {NEKTON}, {AND DEEP-SEA BENTHOS}. Oceanography
+\textbf{29}(3): 174--181. Oceanography Society. Available from
+\url{https://www.jstor.org/stable/24862719} {[}accessed 15 September
+2023{]}.
+
+\bibitem[\citeproctext]{ref-Campana2018}
+Campana, G.L., Zacher, K., Deregibus, D., Momo, F.R., Wiencke, C., and
+Quartino, M.L. 2018. Succession of {Antarctic} benthic algae ({Potter
+Cove}, {South Shetland Islands}): Structural patterns and glacial impact
+over a four-year period. Polar Biology \textbf{41}(2): 377--396.
+doi:\href{https://doi.org/10.1007/s00300-017-2197-x}{10.1007/s00300-017-2197-x}.
+
 \bibitem[\citeproctext]{ref-Chown2022}
@@
 synopsis and recommendations for action.
+
+\bibitem[\citeproctext]{ref-Ciancio2010}
+Ciancio, J., Beauchamp, D.A., and Pascual, M. 2010. Marine effect of
+introduced salmonids: {Prey} consumption by exotic steelhead and
+anadromous brown trout in the {Patagonian Continental Shelf}. Limnology
+and Oceanography \textbf{55}(5): 2181--2192.
+doi:\href{https://doi.org/10.4319/lo.2010.55.5.2181}{10.4319/lo.2010.55.5.2181}.
 
@@
 doi:\href{https://doi.org/10.1098/rspb.2015.1589}{10.1098/rspb.2015.1589}.
+
+\bibitem[\citeproctext]{ref-Clark2013}
+Clark, G.F., Stark, J.S., Johnston, E.L., Runcie, J.W., Goldsworthy,
+P.M., Raymond, B., and Riddle, M.J. 2013. Light-driven tipping points in
+polar ecosystems. Global Change Biology \textbf{19}(12): 3749--3761.
+doi:\href{https://doi.org/10.1111/gcb.12337}{10.1111/gcb.12337}.
 
@@
 
+\bibitem[\citeproctext]{ref-Cordone2022}
+Cordone, G., Lozada, M., Vilacoba, E., Thalinger, B., Bigatti, G.,
+Lijtmaer, D.A., Steinke, D., and Galván, D.E. 2022. Metabarcoding,
+direct stomach observation and stable isotope analysis reveal a highly
+diverse diet for the invasive green crab in {Atlantic Patagonia}.
+Biological Invasions \textbf{24}(2): 505--526.
+doi:\href{https://doi.org/10.1007/s10530-021-02659-5}{10.1007/s10530-021-02659-5}.
+
 \bibitem[\citeproctext]{ref-Cordone2020}
@@
 
-\bibitem[\citeproctext]{ref-deHaro2022}
-de Haro, J.C., Perez Orsi, H., Cané, S., Di Pangracio, A., Falabella,
-V., and Sapoznikow, A. 2022. {Informe colaborativo sobre el Estado de
-situaci{ó}n. Riesgos e impactos de la prospecci{ó}n s{í}smica en el Mar
-Argentino}. Foro para la Conservaci{ó}n del Mar Patag{ó}nico y {Á}reas
-de Influencia.
+\bibitem[\citeproctext]{ref-Deppeler2020}
+Deppeler, S., Schulz, K.G., Hancock, A., Pascoe, P., McKinlay, J., and
+Davidson, A. 2020. Ocean acidification reduces growth and grazing impact
+of {Antarctic} heterotrophic nanoflagellates. Biogeosciences
+\textbf{17}(16): 4153--4171. Copernicus GmbH.
+doi:\href{https://doi.org/10.5194/bg-17-4153-2020}{10.5194/bg-17-4153-2020}.
 
@@
 doi:\href{https://doi.org/10.1016/j.marenvres.2023.106056}{10.1016/j.marenvres.2023.106056}.
+
+\bibitem[\citeproctext]{ref-Deregibus2016}
+Deregibus, D., Quartino, M.L., Campana, G.L., Momo, F.R., Wiencke, C.,
+and Zacher, K. 2016. Photosynthetic light requirements and vertical
+distribution of macroalgae in newly ice-free areas in {Potter Cove},
+{South Shetland Islands}, {Antarctica}. Polar Biology \textbf{39}(1):
+153--166.
+doi:\href{https://doi.org/10.1007/s00300-015-1679-y}{10.1007/s00300-015-1679-y}.
 
@@
 
+\bibitem[\citeproctext]{ref-Dormann2017}
+Dormann, C.F., Fründ, J., and Schaefer, H.M. 2017. Identifying {Causes}
+of {Patterns} in {Ecological Networks}: {Opportunities} and
+{Limitations}. Annual Review of Ecology, Evolution, and Systematics
+\textbf{48}: 559--584.
+doi:\href{https://doi.org/10.1146/annurev-ecolsys-110316-022928}{10.1146/annurev-ecolsys-110316-022928}.
+
 \bibitem[\citeproctext]{ref-Duarte2011}
@@
 doi:\href{https://doi.org/10.1016/j.marpolbul.2011.05.031}{10.1016/j.marpolbul.2011.05.031}.
-
-\bibitem[\citeproctext]{ref-Duffy2007}
-Duffy, J.E., Cardinale, B.J., France, K.E., McIntyre, P.B., Thébault,
-E., and Loreau, M. 2007. The functional role of biodiversity in
-ecosystems: Incorporating trophic complexity. Ecology Letters
-\textbf{10}(6): 522--538.
-doi:\href{https://doi.org/10.1111/j.1461-0248.2007.01037.x}{10.1111/j.1461-0248.2007.01037.x}.
 
@@
 doi:\href{https://doi.org/10.7554/eLife.00590}{10.7554/eLife.00590}.
-
-\bibitem[\citeproctext]{ref-Dunne2002}
-Dunne, J.A., Williams, R.J., and Martinez, N.D. 2002a. Network structure
-and biodiversity loss in food webs: Robustness increases with
-connectance. Ecology Letters \textbf{5}(4): 558--567.
-doi:\href{https://doi.org/10.1046/j.1461-0248.2002.00354.x}{10.1046/j.1461-0248.2002.00354.x}.
-
-\bibitem[\citeproctext]{ref-Dunne2002a}
-Dunne, J.A., Williams, R.J., and Martinez, N.D. 2002b. Food-web
-structure and network theory: {The} role of connectance and size.
-Proceedings of the National Academy of Sciences \textbf{99}(20):
-12917--12922. Proceedings of the National Academy of Sciences.
-doi:\href{https://doi.org/10.1073/pnas.192407699}{10.1073/pnas.192407699}.
 
@@
 \bibitem[\citeproctext]{ref-Franco2020}
-Franco, B.C., Combes, V., and González Carman, V. 2020. Subsurface
+Franco, B.C., Combes, V., and González Carman, V. 2020a. Subsurface
 {Ocean Warming Hotspots} and {Potential Impacts} on {Marine Species}:
@@
 Science \textbf{7}. {[}accessed 10 August 2023{]}.
+
+\bibitem[\citeproctext]{ref-Franco2020a}
+Franco, B.C., Defeo, O., Piola, A.R., Barreiro, M., Yang, H., Ortega,
+L., Gianelli, I., Castello, J.P., Vera, C., Buratti, C., Pájaro, M.,
+Pezzi, L.P., and Möller, O.O. 2020b. Climate change impacts on the
+atmospheric circulation, ocean, and fisheries in the southwest {South
+Atlantic Ocean}: A review. Climatic Change \textbf{162}(4): 2359--2377.
+doi:\href{https://doi.org/10.1007/s10584-020-02783-6}{10.1007/s10584-020-02783-6}.
 
@@
 
+\bibitem[\citeproctext]{ref-Garrott1993}
+Garrott, R.A., Eberhardt, L.L., and Burn, D.M. 1993. Mortality of {Sea
+Otters} in {Prince William Sound Following} the {Exxon Valdez Oil
+Spill}. Marine Mammal Science \textbf{9}(4): 343--359.
+doi:\href{https://doi.org/10.1111/j.1748-7692.1993.tb00468.x}{10.1111/j.1748-7692.1993.tb00468.x}.
+
+\bibitem[\citeproctext]{ref-Gauzens2019}
+Gauzens, B., Barnes, A., Giling, D.P., Hines, J., Jochum, M., Lefcheck,
+J.S., Rosenbaum, B., Wang, S., and Brose, U. 2019. Fluxweb: {An R}
+package to easily estimate energy fluxes in food webs. Methods in
+Ecology and Evolution \textbf{10}(2): 270--279. John Wiley \& Sons, Ltd
+(10.1111).
+doi:\href{https://doi.org/10.1111/2041-210X.13109}{10.1111/2041-210X.13109}.
+
 \bibitem[\citeproctext]{ref-Gauzens2023}
@@
 doi:\href{https://doi.org/10.1073/pnas.2212061120}{10.1073/pnas.2212061120}.
+
+\bibitem[\citeproctext]{ref-Giarratano2010}
+Giarratano, E., and Amin, O.A. 2010. Heavy metals monitoring in the
+southernmost mussel farm of the world ({Beagle Channel}, {Argentina}).
+Ecotoxicology and Environmental Safety \textbf{73}(6): 1378--1384.
+doi:\href{https://doi.org/10.1016/j.ecoenv.2010.06.023}{10.1016/j.ecoenv.2010.06.023}.
 
@@
 doi:\href{https://doi.org/10.3354/meps316175}{10.3354/meps316175}.
+
+\bibitem[\citeproctext]{ref-Gonzalez-Zevallos2011}
+González-Zevallos, D., and Yorio, P. 2011. Consumption of discards and
+interactions between {Black-browed Albatrosses} ({Thalassarche}
+melanophrys) and {Kelp Gulls} ({Larus} dominicanus) at trawl fisheries
+in {Golfo San Jorge}, {Argentina}. Journal of Ornithology
+\textbf{152}(4): 827--838.
+doi:\href{https://doi.org/10.1007/s10336-011-0657-6}{10.1007/s10336-011-0657-6}.
 
@@
 
+\bibitem[\citeproctext]{ref-Gutt1996}
+Gutt, J., Starmans, A., and Dieckmann, G. 1996. Impact of iceberg
+scouring on polar benthic habitats. Marine Ecology Progress Series
+\textbf{137}: 311--316.
+doi:\href{https://doi.org/10.3354/meps137311}{10.3354/meps137311}.
+
+\bibitem[\citeproctext]{ref-Haddaway2015}
+Haddaway, N.r., Woodcock, P., Macura, B., and Collins, A. 2015. {Making
+literature reviews more reliable through application of lessons from
+systematic reviews}. Conservation Biology \textbf{29}(6): 1596--1605.
+doi:\href{https://doi.org/10.1111/cobi.12541}{10.1111/cobi.12541}.
+
 \bibitem[\citeproctext]{ref-Hilborn2017}
@@
 doi:\href{https://doi.org/10.1016/j.fishres.2017.01.008}{10.1016/j.fishres.2017.01.008}.
+
+\bibitem[\citeproctext]{ref-Hill2013}
+Hill, S.L., Phillips, T., and Atkinson, A. 2013. Potential {Climate
+Change Effects} on the {Habitat} of {Antarctic Krill} in the {Weddell
+Quadrant} of the {Southern Ocean}. PLOS ONE \textbf{8}(8): e72246.
+Public Library of Science.
+doi:\href{https://doi.org/10.1371/journal.pone.0072246}{10.1371/journal.pone.0072246}.
 
@@
 
+\bibitem[\citeproctext]{ref-Isla2024}
+Isla, F.I., and Cortizo, L.C. 2024. Oil seeps from the {Patagonian}
+shelf: Their thermosteric fate. Marine \& Fishery Sciences (MAFIS)
+\textbf{37}(1): 233--240. Instituto Nacional de Investigaci{ó}n y
+Desarrollo Pesquero.
+
 \bibitem[\citeproctext]{ref-Jacob2011}
@@
 
-\bibitem[\citeproctext]{ref-Jordan2007}
-Jordán, F., Benedek, Z., and Podani, J. 2007. Quantifying positional
-importance in food webs: {A} comparison of centrality indices.
-Ecological Modelling \textbf{205}(1): 270--275.
-doi:\href{https://doi.org/10.1016/j.ecolmodel.2007.02.032}{10.1016/j.ecolmodel.2007.02.032}.
-
-\bibitem[\citeproctext]{ref-Kaminskyinprep}
-Kaminsky, J., Bagur, M., Boraso, A., Schloss, I.R., Buschmann, A.H., and
-Quartino, M.L. in prep. Kelp recruitment declines in a sub-{Antarctic}
-ecosystem with high sediment inputs and changes in the understory algae.
+\bibitem[\citeproctext]{ref-Kaminsky2024}
+Kaminsky, J., Bagur, M., Schloss, I.R., Diodato, S., Rodríguez, M.,
+Buschmann, A.H., and Quartino, M.L. 2023. Giant kelp ({Macrocystis}
+pyrifera) morphological and reproductive strategies in two contrasting
+sub-{Antarctic} forests. Marine Biology \textbf{171}(1): 9.
+doi:\href{https://doi.org/10.1007/s00227-023-04341-x}{10.1007/s00227-023-04341-x}.
+
+\bibitem[\citeproctext]{ref-Kawaguchi2013}
+Kawaguchi, S., Ishida, A., King, R., Raymond, B., Waller, N., Constable,
+A., Nicol, S., Wakita, M., and Ishimatsu, A. 2013. Risk maps for
+{Antarctic} krill under projected {Southern Ocean} acidification. Nature
+Climate Change \textbf{3}(9): 843--847. Nature Publishing Group.
+doi:\href{https://doi.org/10.1038/nclimate1937}{10.1038/nclimate1937}.
+
+\bibitem[\citeproctext]{ref-Kawaguchi2010}
+Kawaguchi, S., Kurihara, H., King, R., Hale, L., Berli, T., Robinson,
+J.P., Ishida, A., Wakita, M., Virtue, P., Nicol, S., and Ishimatsu, A.
+2010. Will krill fare well under {Southern Ocean} acidification? Biology
+Letters \textbf{7}(2): 288--291. Royal Society.
+doi:\href{https://doi.org/10.1098/rsbl.2010.0777}{10.1098/rsbl.2010.0777}.
 
@@
 
-\bibitem[\citeproctext]{ref-Kratina2012}
-Kratina, P., LeCraw, R.M., Ingram, T., and Anholt, B.R. 2012. Stability
-and persistence of food webs with omnivory: {Is} there a general
-pattern? Ecosphere \textbf{3}(6): art50.
-doi:\href{https://doi.org/10.1890/ES12-00121.1}{10.1890/ES12-00121.1}.
+\bibitem[\citeproctext]{ref-Lagger2018}
+Lagger, C., Nime, M., Torre, L., Servetto, N., Tatián, M., and Sahade,
+R. 2018. Climate change, glacier retreat and a new ice-free island offer
+new insights on {Antarctic} benthic responses. Ecography \textbf{41}(4):
+579--591.
+doi:\href{https://doi.org/10.1111/ecog.03018}{10.1111/ecog.03018}.
+
+\bibitem[\citeproctext]{ref-Lagger2017}
+Lagger, C., Servetto, N., Torre, L., and Sahade, R. 2017. Benthic
+colonization in newly ice-free soft-bottom areas in an {Antarctic}
+fjord. PLOS ONE \textbf{12}(11): e0186756. Public Library of Science.
+doi:\href{https://doi.org/10.1371/journal.pone.0186756}{10.1371/journal.pone.0186756}.
+
+\bibitem[\citeproctext]{ref-Laptikhovsky2013}
+Laptikhovsky, V., Arkhipkin, A., and Brickle, P. 2013. From small
+bycatch to main commercial species: {Explosion} of stocks of rock cod
+{Patagonotothen} ramsayi ({Regan}) in the {Southwest Atlantic}.
+Fisheries Research \textbf{147}: 399--403.
+doi:\href{https://doi.org/10.1016/j.fishres.2013.05.006}{10.1016/j.fishres.2013.05.006}.
 
@@
 
+\bibitem[\citeproctext]{ref-Litz2014}
+Litz, J.A., Baran, M.A., Bowen-Stevens, S.R., Carmichael, R.H.,
+Colegrove, K.M., Garrison, L.P., Fire, S.E., Fougeres, E.M., Hardy, R.,
+Holmes, S., Jones, W., Mase-Guthrie, B.E., Odell, D.K., Rosel, P.E.,
+Saliki, J.T., Shannon, D.K., Shippee, S.F., Smith, S.M., Stratton, E.M.,
+Tumlin, M.C., Whitehead, H.R., Worthy, G.A.J., and Rowles, T.K. 2014.
+Review of historical unusual mortality events ({UMEs}) in the {Gulf} of
+{Mexico} (1990-2009): Providing context for the multi-year northern
+{Gulf} of {Mexico} cetacean {UME} declared in 2010. Diseases of Aquatic
+Organisms \textbf{112}(2): 161--175.
+doi:\href{https://doi.org/10.3354/dao02807}{10.3354/dao02807}.
+
 \bibitem[\citeproctext]{ref-Llorca2012}
@@
 doi:\href{https://doi.org/10.1007/s10021-021-00665-1}{10.1007/s10021-021-00665-1}.
+
+\bibitem[\citeproctext]{ref-Manno2022}
+Manno, C., Peck, V.L., Corsi, I., and Bergami, E. 2022. Under pressure:
+{Nanoplastics} as a further stressor for sub-{Antarctic} pteropods
+already tackling ocean acidification. Marine Pollution Bulletin
+\textbf{174}: 113176.
+doi:\href{https://doi.org/10.1016/j.marpolbul.2021.113176}{10.1016/j.marpolbul.2021.113176}.
 
@@
 
+\bibitem[\citeproctext]{ref-Marina2024}
+Marina, T.I., Saravia, L.A., and Kortsch, S. 2024. New insights into the
+{Weddell Sea} ecosystem applying a quantitative network approach. Ocean
+Science \textbf{20}(1): 141--153. Copernicus GmbH.
+doi:\href{https://doi.org/10.5194/os-20-141-2024}{10.5194/os-20-141-2024}.
+
 \bibitem[\citeproctext]{ref-Marinainrev}
@@
 doi:\href{https://doi.org/10.1890/08-0657.1}{10.1890/08-0657.1}.
+
+\bibitem[\citeproctext]{ref-Moore1974}
+Moore, S.F., and Dwyer, R.L. 1974. Effects of oil on marine organisms:
+{A} critical assessment of published data. Water Research
+\textbf{8}(10): 819--827.
+doi:\href{https://doi.org/10.1016/0043-1354(74)90028-1}{10.1016/0043-1354(74)90028-1}.
+
+\bibitem[\citeproctext]{ref-Moy2009}
+Moy, A.D., Howard, W.R., Bray, S.G., and Trull, T.W. 2009. Reduced
+calcification in modern {Southern Ocean} planktonic foraminifera. Nature
+Geoscience \textbf{2}(4): 276--280. Nature Publishing Group.
+doi:\href{https://doi.org/10.1038/ngeo460}{10.1038/ngeo460}.
 
@@
 
-\bibitem[\citeproctext]{ref-Nowacek2015}
-Nowacek, D.P., Clark, C.W., Mann, D., Miller, P.J., Rosenbaum, H.C.,
-Golden, J.S., Jasny, M., Kraska, J., and Southall, B.L. 2015. Marine
-seismic surveys and ocean noise: Time for coordinated and prudent
-planning. Frontiers in Ecology and the Environment \textbf{13}(7):
-378--386. doi:\href{https://doi.org/10.1890/130286}{10.1890/130286}.
-
 \bibitem[\citeproctext]{ref-OGorman2012}
@@
 doi:\href{https://doi.org/10.1038/s41467-018-03732-9}{10.1038/s41467-018-03732-9}.
-
-\bibitem[\citeproctext]{ref-Olivier2019}
-Olivier, P., Frelat, R., Bonsdorff, E., Kortsch, S., Kröncke, I.,
-Möllmann, C., Neumann, H., Sell, A.F., and Nordström, M.C. 2019.
-Exploring the temporal variability of a food web using long-term
-biomonitoring data. Ecography \textbf{42}(12): 2107--2121.
-doi:\href{https://doi.org/10.1111/ecog.04461}{10.1111/ecog.04461}.
 
@@
 
-\bibitem[\citeproctext]{ref-Paine1996}
-Paine, R.T., Ruesink, J.L., Sun, A., Soulanille, E.L., Wonham, M.J.,
-Harley, C.D.G., Brumbaugh, D.R., and Secord, D.L. 1996. {TROUBLE ON
-OILED WATERS}: {Lessons} from the {\emph{Exxon Valdez}} {Oil Spill}.
-Annual Review of Ecology and Systematics \textbf{27}(1): 197--235.
-doi:\href{https://doi.org/10.1146/annurev.ecolsys.27.1.197}{10.1146/annurev.ecolsys.27.1.197}.
+\bibitem[\citeproctext]{ref-Padovani2012}
+Padovani, L.N., Viñas, M.D., Sánchez, F., and Mianzan, H. 2012.
+Amphipod-supported food web: {Themisto} gaudichaudii, a key food
+resource for fishes in the southern {Patagonian Shelf}. Journal of Sea
+Research \textbf{67}(1): 85--90.
+doi:\href{https://doi.org/10.1016/j.seares.2011.10.007}{10.1016/j.seares.2011.10.007}.
 
@@
 
-\bibitem[\citeproctext]{ref-Pecuchet2022}
-Pecuchet, L., Jørgensen, L.L., Dolgov, A.V., Eriksen, E., Husson, B.,
-Skern-Mauritzen, M., and Primicerio, R. 2022. Spatio-temporal turnover
-and drivers of bentho-demersal community and food web structure in a
-high-latitude marine ecosystem. Diversity and Distributions
-\textbf{28}(12): 2503--2520.
-doi:\href{https://doi.org/10.1111/ddi.13580}{10.1111/ddi.13580}.
-
 \bibitem[\citeproctext]{ref-Pecuchet2020}
@@
 
+\bibitem[\citeproctext]{ref-Perez2021}
+Pérez, A.F., Ojeda, M., Cossi, P.F., Rimondino, G.N., Chiesa, I.L.,
+Fraysse, C., and Calcagno, J. 2021. {Micropl{á}sticos en organismos
+marinos de altas latitudes}. \emph{In} {I Jornadas de la Red
+Cient{í}fica Argentina para el estudio de los pl{á}sticos y sus impactos
+en el ambiente (SEPIA)}.
+
 \bibitem[\citeproctext]{ref-Perez2020}
@@
 Evolution \textbf{9}. {[}accessed 11 September 2023{]}.
+
+\bibitem[\citeproctext]{ref-Pinones2016}
+Piñones, A., and Fedorov, A.V. 2016. Projected changes of {Antarctic}
+krill habitat by the end of the 21st century. Geophysical Research
+Letters \textbf{43}(16): 8580--8589.
+doi:\href{https://doi.org/10.1002/2016GL069656}{10.1002/2016GL069656}.
+
+\bibitem[\citeproctext]{ref-Polazzo2022}
+Polazzo, F., Marina, T.I., Crettaz-Minaglia, M., and Rico, A. 2022. Food
+web rewiring drives long-term compositional differences and
+late-disturbance interactions at the community level. Proceedings of the
+National Academy of Sciences \textbf{119}(17): e2117364119.
+doi:\href{https://doi.org/10.1073/pnas.2117364119}{10.1073/pnas.2117364119}.
 
@@
 
+\bibitem[\citeproctext]{ref-Risaro2022}
+Risaro, D.B., Chidichimo, M.P., and Piola, A.R. 2022. Interannual
+{Variability} and {Trends} of {Sea Surface Temperature Around Southern
+South America}. Frontiers in Marine Science \textbf{9}. Frontiers.
+doi:\href{https://doi.org/10.3389/fmars.2022.829144}{10.3389/fmars.2022.829144}.
+
 \bibitem[\citeproctext]{ref-Rodriguez2022}
@@
 
+\bibitem[\citeproctext]{ref-Sage2020}
+Sage, R.F. 2020. Global change biology: {A} primer. Global Change
+Biology \textbf{26}(1): 3--30.
+doi:\href{https://doi.org/10.1111/gcb.14893}{10.1111/gcb.14893}.
+
 \bibitem[\citeproctext]{ref-Sahade2015}
@@
 doi:\href{https://doi.org/10.1126/sciadv.1500050}{10.1126/sciadv.1500050}.
+
+\bibitem[\citeproctext]{ref-Saraceno2022}
+Saraceno, M., Martín, J., Moreira, D., Pisoni, J.P., and Tonini, M.H.
+2022. Physical {Changes} in the {Patagonian Shelf}. \emph{In} Global
+{Change} in {Atlantic Coastal Patagonian Ecosystems}: {A Journey Through
+Time}. \emph{Edited by} E.W. Helbling, M.A. Narvarte, R.A. González, and
+V.E. Villafañe. Springer International Publishing, Cham. pp. 43--71.
+doi:\href{https://doi.org/10.1007/978-3-030-86676-1_3}{10.1007/978-3-030-86676-1\_3}.
+
+\bibitem[\citeproctext]{ref-Saravia2021}
+Saravia, J., Paschke, K., Oyarzún-Salazar, R., Cheng, C.-H.C., Navarro,
+J.M., and Vargas-Chacoff, L. 2021. Effects of warming rates on
+physiological and molecular components of response to {CTMax} heat
+stress in the {Antarctic} fish {Harpagifer} antarcticus. Journal of
+Thermal Biology \textbf{99}: 103021.
+doi:\href{https://doi.org/10.1016/j.jtherbio.2021.103021}{10.1016/j.jtherbio.2021.103021}.
 
@@
 
+\bibitem[\citeproctext]{ref-Siniff2008}
+Siniff, D.B., Garrott, R.A., Rotella, J.J., Fraser, W.R., and Ainley,
+D.G. 2008. Opinion: {Projecting} the effects of environmental change on
+{Antarctic} seals. Antarctic Science \textbf{20}(5): 425--435. Cambridge
+University Press.
+doi:\href{https://doi.org/10.1017/S0954102008001351}{10.1017/S0954102008001351}.
+
 \bibitem[\citeproctext]{ref-Smale2008}
@@
 
+\bibitem[\citeproctext]{ref-Southward1978}
+Southward, A.J., and Southward, E.C. 1978. Recolonization of {Rocky
+Shores} in {Cornwall After Use} of {Toxic Dispersants} to {Clean Up} the
+{Torrey Canyon Spill}. Journal of the Fisheries Research Board of Canada
+\textbf{35}(5): 682--706. NRC Research Press.
+doi:\href{https://doi.org/10.1139/f78-120}{10.1139/f78-120}.
+
+\bibitem[\citeproctext]{ref-Souza2018}
+Souza, M.R.D.P. de, Herrerias, T., Zaleski, T., Forgati, M., Kandalski,
+P.K., Machado, C., Silva, D.T., Piechnik, C.A., Moura, M.O., and
+Donatti, L. 2018. Heat stress in the heart and muscle of the {Antarctic}
+fishes {Notothenia} rossii and {Notothenia} coriiceps: {Carbohydrate}
+metabolism and antioxidant defence. Biochimie \textbf{146}: 43--55.
+doi:\href{https://doi.org/10.1016/j.biochi.2017.11.010}{10.1016/j.biochi.2017.11.010}.
+
 \bibitem[\citeproctext]{ref-Stouffer2011}
@@
 doi:\href{https://doi.org/10.1073/pnas.1014353108}{10.1073/pnas.1014353108}.
+
+\bibitem[\citeproctext]{ref-Strobel2013}
+Strobel, A., Leo, E., Pörtner, H.O., and Mark, F.C. 2013. Elevated
+temperature and {PCO2} shift metabolic pathways in differentially
+oxidative tissues of {Notothenia} rossii. Comparative Biochemistry and
+Physiology Part B: Biochemistry and Molecular Biology \textbf{166}(1):
+48--57.
+doi:\href{https://doi.org/10.1016/j.cbpb.2013.06.006}{10.1016/j.cbpb.2013.06.006}.
 
@@
 
-\bibitem[\citeproctext]{ref-Thompson2007}
-Thompson, R.M., Hemberg, M., Starzomski, B.M., and Shurin, J.B. 2007.
-Trophic {Levels} and {Trophic Tangles}: {The Prevalence} of {Omnivory}
-in {Real Food Webs}. Ecology \textbf{88}(3): 612--617.
-doi:\href{https://doi.org/10.1890/05-1454}{10.1890/05-1454}.
-
 \bibitem[\citeproctext]{ref-Trathan2023}
@@
 
+\bibitem[\citeproctext]{ref-Trebilco2020}
+Trebilco, R., Melbourne-Thomas, J., and Constable, A.J. 2020. The policy
+relevance of {Southern Ocean} food web structure: {Implications} of food
+web change for fisheries, conservation and carbon sequestration. Marine
+Policy \textbf{115}: 103832.
+doi:\href{https://doi.org/10.1016/j.marpol.2020.103832}{10.1016/j.marpol.2020.103832}.
+
 \bibitem[\citeproctext]{ref-Turner2020}
@@
 doi:\href{https://doi.org/10.1029/2020GL087127}{10.1029/2020GL087127}.
+
+\bibitem[\citeproctext]{ref-Verga2020}
+Verga, R.N., Tolosano, J.A., Cazzaniga, N.J., and Gil, D.G. 2020.
+Assessment of seawater quality and bacteriological pollution of rocky
+shores in the central coast of {San Jorge Gulf} ({Patagonia},
+{Argentina}). Marine Pollution Bulletin \textbf{150}: 110749.
+doi:\href{https://doi.org/10.1016/j.marpolbul.2019.110749}{10.1016/j.marpolbul.2019.110749}.
 
@@
 
+\bibitem[\citeproctext]{ref-Vitousek1992}
+Vitousek, P.M. 1992. Global {Environmental Change}: {An Introduction}.
+Annual Review of Ecology, Evolution and Systematics \textbf{23}(Volume
+23,): 1--14. Annual Reviews.
+doi:\href{https://doi.org/10.1146/annurev.es.23.110192.000245}{10.1146/annurev.es.23.110192.000245}.
+
 \bibitem[\citeproctext]{ref-Vucic-Pestic2011}
@@
 doi:\href{https://doi.org/10.1111/j.1365-2486.2010.02329.x}{10.1111/j.1365-2486.2010.02329.x}.
+
+\bibitem[\citeproctext]{ref-Wallace2017}
+Wallace, B., Brosnan, T., McLamb, D., Rowles, T., Ruder, E., Schroeder,
+B., Schwacke, L., Stacy, B., Sullivan, L., Takeshita, R., and Wehner, D.
+2017. Effects of the {Deepwater Horizon} oil spill on protected marine
+species. Endangered Species Research \textbf{33}: 1--7.
+doi:\href{https://doi.org/10.3354/esr00789}{10.3354/esr00789}.
 
@@
 
-\bibitem[\citeproctext]{ref-Williams2000}
-Williams, R.J., and Martinez, N.D. 2000. Simple rules yield complex food
-webs. Nature \textbf{404}(6774): 180--183. Nature Publishing Group.
-doi:\href{https://doi.org/10.1038/35004572}{10.1038/35004572}.
+\bibitem[\citeproctext]{ref-Williams2023}
+Williams, G.N., and Nocera, A.C. 2023. Bio-optical trends of waters
+around {Vald{é}s Biosphere Reserve}: {An} assessment of the temporal
+variability based on 20 years of ocean color satellite data. Marine
+Environmental Research \textbf{186}: 105923.
+doi:\href{https://doi.org/10.1016/j.marenvres.2023.105923}{10.1016/j.marenvres.2023.105923}.
+
+\bibitem[\citeproctext]{ref-Winter2023}
+Winter, A., and Arkhipkin, A. 2023. Opportunistic {Survey Analyses
+Reveal} a {Recent Decline} of {Skate} ({Rajiformes}) {Biomass} in
+{Falkland Islands Waters}. Fishes \textbf{8}(1): 24. Multidisciplinary
+Digital Publishing Institute.
+doi:\href{https://doi.org/10.3390/fishes8010024}{10.3390/fishes8010024}.
 
@@
 
+\bibitem[\citeproctext]{ref-Yorio2017}
+Yorio, P., González-Zevallos, D., Gatto, A., Biagioni, O., and Castillo,
+J. 2017. Relevance of forage fish in the diet of {Magellanic} penguins
+breeding in northern {Patagonia}, {Argentina}. Marine Biology Research
+\textbf{13}(6): 603--617. Taylor \& Francis.
+doi:\href{https://doi.org/10.1080/17451000.2016.1273529}{10.1080/17451000.2016.1273529}.
+
 \end{CSLReferences}

### 2024-04-19 SupportingInformation.tex
Version to submit

@@
 \newcommand{\elandscape}{\end{landscape}}
-\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
-\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
 \ifLuaTeX
@@
 \author{}
-
 \date{\vspace{-2.5em}}
@@
 \begin{document}
-
 \maketitle
@@
 \newpage
-\begin{landscape}
 \scriptsize
 
-Table S2. Environmental and anthropogenic stressors reported for the
-study areas: San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea
-(North and South), Potter Cove, and Weddell Sea. Stressor categories:
-sea warming; glacial retreat; sediment in the water column; iceberg
-scouring; sea ice extent; ocean acidification; ocean acidification +
-plastics; microplastics; mercury; urban \& industrial pollution;
-fishery; alien species. The species affected were considered at the node
-level, whereas effects were considered at the organism and population
-levels. Categories of affected parameters and variables: metabolism;
-biomass; distribution; diet (see text for explanation). ``Locality''
-indicates whether a stressor for a given species was reported for the
-study area (`In situ') or in another area (`Elsewhere').
+Table S2. Node and network-level properties used to build hypotheses on
+the stressors' effects.
 
-\begin{longtable}{ L{2.1cm} L{2.5cm} L{4cm} L{2.5cm} L{2cm} L{3cm} }
-\hline
-\textbf{Study area} & \textbf{Stressor} & \textbf{Species affected} & \textbf{Parameter affected} & \textbf{Locality} & \textbf{Reference} \\
-\hline
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1963}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2617}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3925}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1495}}@{}}
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Property}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Definition}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Relevance for stressor effects}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Reference}
+\end{minipage} \\
+\midrule\noalign{}
 \endhead
-\endfoot
-\hline
+\bottomrule\noalign{}
 \endlastfoot
-
-\textbf{San Jorge Gulf} & & & & & \\
-& Sea warming & Fish assemblage \& its prey & Distribution & In situ &
-Galván et al. (2022) \\
-& Fishery & Demersal fish community & Biomass & In situ & Galván et al.
-(2022) \\
-& Fishery & Macroinvertebrates, fishes and seabirds & Diet & In situ &
-González-Zevallos \& Yorio (2006); González-Zevallos \& Yorio (2011);
-Yorio, González-Zevallos, Gatto, Biagioni, \& Castillo (2017) \\
-& Alien species & Fish assemblage \& its prey & Distribution & In situ &
-Galván et al. (2022); J. Ciancio, Beauchamp, \& Pascual (2010) \\
-& Urban \& industrial pollution & Seabirds \& benthic assemblage &
-Biomass & Elsewhere & Moore \& Dwyer (1974); Buskey, White, \& Esbaugh
-(2016) \\
-\textbf{Beagle Channel} & & & & & \\
-& Urban \& industrial pollution & Macroalgae; Mytilus edulis chilensis,
-Patagonotothen tessellata & Metabolism & In situ & Giarratano \& Amin
-(2010); Ferreira, Lo Nostro, Fernández, \& Genovese (2021); Kaminsky et
-al. (in prep.) \\
-& Mercury & Phytoplankton, Zooplankton, \emph{Grimothea gregaria} &
-Metabolism & In situ & Fioramonti, Ribeiro Guevara, Becker, \&
-Riccialdelli (2022) \\
-& Microplastics & Mytilus edulis chilensis, Nacella magellanica &
-Metabolism & In situ & Analía F. Pérez et al. (2020); Ojeda et al.
-(2021) \\
-& Alien species: Chinook salmon Oncorhynchus tshawytscha &
-Patagonotothen tessellata, Sprattus fuegensis & Diet/Biomass & In situ
-(the presence), Elsewhere (changes in prey biomass) & Fernández,
-Ciancio, Ceballos, Riva-Rossi, \& Pascual (2010); J. E. Ciancio,
-Pascual, Botto, Frere, \& Iribarne (2008) \\
-\textbf{Burdwood Bank} & & & & & \\
-& Mercury & Dissostichus eleginoides, Sprattus fuegensis, Patagonotothen
-ramsayi, Cottoperca trigloides (fishes) \& squids & Metabolism & In situ
-& Fioramonti et al. (2022) \\
-& Microplastics & Henricia obesa \& Odontaster penicillatus (sea stars);
-Patagonotothen guntheri \& P. ramsayi (fishes) & Metabolism & In situ &
-Cossi et al. (2021); A. F. Pérez et al. (2021) \\
-& Fishery & Target: Dissostichus eleginoides. Bycatch: Macrourus sp.,
-Coelorinchus sp. (fishes), Daption capense, Thalassarche melanophris,
-Macronectes giganteus, T. chrysostoma, Diomedea epomophora (seabirds),
-30+ spp macrobenthos & Biomass & Elsewhere & Gaitán \& Marí (2016);
-Martínez, Wöhler, Troccoli, Di Marco, \& Maydana (2022); Administración
-de Parques Nacionales (2022); Tamini et al. (2023) \\
-& Fishery & Thalassarche melanophris, Macronectes giganteus, Daption
-capense, Diomedea epomophora, M. halli, Procellaria aequinoctialis
-(seabirds) & Diet & Elsewhere & Tamini et al. (2023) \\
-\textbf{Scotia Sea, North \& South} & & & & & \\
-& Mercury & Krefftichthys anderssoni, Protomyctophum bolini, Electrona
-antarctica, Gymnoscopelus nicholsi, Gymnoscopelus braueri, Dissostichus
-eleginoides & Metabolism & In situ & Seco et al. (2021) \\
-& Ocean acidification + plastics & Euphausia superba, Limacina
-retroversa (Pteropoda) & Metabolism & In situ & Rowlands et al. (2021);
-Manno, Peck, Corsi, \& Bergami (2022) \\
-& Sea warming & Euphausia superba & Metabolism & In situ & Murphy et al.
-(2007); Perry et al. (2020) \\
-& Sea warming & Euphausia superba & Distribution & In situ & Atkinson et
-al. (2019) \\
-& Fishery & Euphausia superba & Biomass & In situ & Trathan et al.
-(2021) \\
-\textbf{Potter Cove (Antarctica)} & & & & & \\
-& Sediment in water column & Microphytobenthos, macroalgae, benthic
-filter feeders (ascidians), pelagic filter feeders (krill, salps) &
-Metabolism & In situ & Sahade et al. (2015); D. Deregibus et al. (2016);
-Fuentes et al. (2016); Hoffmann et al. (2019) \\
-& Sea ice extent & Krill & Biomass & Elsewhere & Flores et al. (2012) \\
-& Sea ice extent & Benthic community (macroalgae, invertebrates) &
-Metabolism & Elsewhere & Clark et al. (2013); Campana et al. (2018) \\
-& Glacial retreat & Benthic community (macroalgae, invertebrates) &
-Biomass & In situ & Quartino, Deregibus, Campana, Latorre, \& Momo
-(2013); Lagger, Servetto, Torre, \& Sahade (2017); Lagger et al.
-(2018) \\
-& Iceberg scouring & Benthic community & Biomass & In situ & D.
-Deregibus, Quartino, Zacher, Campana, \& Barnes (2017); Dolores
-Deregibus et al. (2023) \\
-& Sea warming & Phytoplankton & Metabolism, biomass & In situ & Antoni
-et al. (2020); Latorre et al. (2023) \\
-& Sea warming & Zooplankton & Metabolism, biomass, diet & In situ &
-Garcia et al. (2016); Garcia et al. (2019) \\
-& Sea warming & Fish & Metabolism & In situ, elsewhere & Strobel, Leo,
-Pörtner, \& Mark (2013); Souza et al. (2018); Saravia et al. (2021) \\
-\textbf{Weddell Sea (Antarctica)} & & & & & \\
-& Iceberg scouring & Macrobentos & Biomass & In situ & Isla (2023);
-Julian Gutt et al. (2015); Smale, Brown, Barnes, Fraser, \& Clarke
-(2008); J. Gutt, Starmans, \& Dieckmann (1996) \\
-& Iceberg scouring & Hexactinellida sponges & Biomass & In situ & Julian
-Gutt \& Starmans (2001); Pineda-Metz, Gerdes, \& Richter (2020); Julian
-Gutt (2001); Julian Gutt \& Piepenburg (2003) \\
-& Ocean acidification & Primary producers / krill / foraminifera /
-flagellates & Metabolism & Elsewhere & Deppeler et al. (2020); Isla
-(2023); Julian Gutt et al. (2015); Moy, Howard, Bray, \& Trull (2009) \\
-& Ocean acidification & Euphausia superba, Pleuragramma antarcticum &
-Metabolism & In situ & So Kawaguchi et al. (2010); S. Kawaguchi et al.
-(2013); Piñones \& Fedorov (2016); Mintenbeck et al. (2012) \\
-& Sea warming & Large (diatoms) \& small (cryptophytes) phytoplankton,
-zooplankton (salps) & Metabolism & Elsewhere & Isla (2023); Julian Gutt
-et al. (2015); Trebilco, Melbourne-Thomas, \& Constable (2020) \\
-& Sea warming & Euphausia superba, Nototheniid fishes, Pleuragramma
-antarcticum & Metabolism & In situ & Meyer et al. (2017); Hill,
-Phillips, \& Atkinson (2013); Mintenbeck et al. (2012); Constable et al.
-(2014); Mintenbeck et al. (2012) \\
-& Sea ice extent & Phytoplankton, Lobodon carcinophaga, Hydrurga
-leptonyx, Leptonychotes weddellii, Ommataphoca rossii, Mirounga leonina,
-Arctocephalus gazella & Metabolism & In situ & Pineda-Metz et al.
-(2020); Wege, Salas, \& LaRue (2021); Siniff, Garrott, Rotella, Fraser,
-\& Ainley (2008) \\
-& Sea ice extent & Euphausia superba, Pleuragramma antarcticum,
-Pagodroma nivea, Thalassoica antarctica, Pygoscelis adeliae & Metabolism
-& In situ & Orgeira, Alvarez, \& Salvó (2021); Braithwaite, Meeuwig,
-Letessier, Jenner, \& Brierley (2015); Hill et al. (2013); Mintenbeck et
-al. (2012) \\
-& Sea ice extent & Megaptera novaeangliae & Metabolism & Elsewhere &
-Pallin et al. (2023) \\
-& Sea ice extent & Aptenodytes forsteri & Metabolism & Elsewhere &
-Orgeira et al. (2021) \\
+\emph{Node-level} & & & \\
+Degree & Number of feeding interactions in which the species
+participates as prey and/or predator. & Perturbations to high-degree
+species may have more significant effects on the food web robustness to
+perturbations than low-degree species. & Dunne et al. (2002b); Jordán et
+al. (2007) \\
+Trophic position & Place in the food web relative to the basal resources
+that support the community. Classifies species in: basal, intermediate
+and top. & Perturbations on basal resources, intermediate species and
+top predators are expected to have large effects on the rest of their
+communities if ecosystem control is bottom-up, wasp-waist or top-down,
+respectively. & Williams and Martinez (2000); Thompson et al. (2007) \\
+Omnivory & Consumer resource use across trophic levels. & High-omnivore
+species (generalists) are more flexible than low-omnivore species to
+diet changes. & Thompson et al. (2007) \\
+Relative abundance & Species' density in proportion to the other species
+of the food web. & Perturbations on abundant (dominant) species are
+expected to have large effects on the stability and energy flux of the
+food and ecosystem, respectively. & Nilsson and McCann (2016) \\
+\emph{Network-level} & & & \\
+Conectance & Proportion of actual interactions among possible ones. &
+Estimator of community sensitivity to stressors. High connectance gives
+resistance and resilience to the food web. & Dunne et al. (2002a) \\
+Path length & Average distance, accounted by the number of interactions,
+between any pair of species. & Short distances enhance rapid and broad
+propagation of perturbations. & Albert and Barabási (2002) \\
+Mean TL & Average of all species' trophic position contained in the food
+web. & Influences the magnitude and efficiency of trophic transfer. A
+higher mean food chain length reflects increased energy availability and
+productivity. & Duffy et al. (2007); Olivier et al. (2019) \\
+Omnivory & Proportion of species that feed at different trophic levels.
+& It provides trophic flexibility to an ecosystem. Reduces probability
+of trophic cascades. & Kratina et al. (2012) \\
 \end{longtable}
-
-\end{landscape}
 
@@
 
-\subsection*{References}\label{references}
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
 
@@
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-APN2022}
-Administración de Parques Nacionales. (2022). {Plan de gestión AMP
-Namuncurá Banco Burdwood}. {Dirección Nacional de Áreas Marinas
-Protegidas (DNAMP), Argentina}.
+\bibitem[\citeproctext]{ref-Albert2002}
+Albert, R., and Barabási, A.-L. 2002. Statistical mechanics of complex
+networks. Reviews of Modern Physics \textbf{74}(1): 47--97. American
+Physical Society.
+doi:\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}.
 
-\bibitem[\citeproctext]{ref-Antoni2020}
-Antoni, J. S., Almandoz, G. O., Ferrario, M. E., Hernando, M. P.,
-Varela, D. E., Rozema, P. D., \ldots{} Schloss, I. R. (2020). Response
-of a natural {Antarctic} phytoplankton assemblage to changes in
-temperature and salinity. \emph{Journal of Experimental Marine Biology
-and Ecology}, \emph{532}, 151444.
-doi:\href{https://doi.org/10.1016/j.jembe.2020.151444}{10.1016/j.jembe.2020.151444}
+\bibitem[\citeproctext]{ref-Duffy2007}
+Duffy, J.E., Cardinale, B.J., France, K.E., McIntyre, P.B., Thébault,
+E., and Loreau, M. 2007. The functional role of biodiversity in
+ecosystems: Incorporating trophic complexity. Ecology Letters
+\textbf{10}(6): 522--538.
+doi:\href{https://doi.org/10.1111/j.1461-0248.2007.01037.x}{10.1111/j.1461-0248.2007.01037.x}.
 
-\bibitem[\citeproctext]{ref-Atkinson2019}
-Atkinson, A., Hill, S. L., Pakhomov, E. A., Siegel, V., Reiss, C. S.,
-Loeb, V. J., \ldots{} Sailley, S. F. (2019). Krill ({Euphausia} superba)
-distribution contracts southward during rapid regional warming.
-\emph{Nature Climate Change}, \emph{9}(2), 142--147.
-doi:\href{https://doi.org/10.1038/s41558-018-0370-z}{10.1038/s41558-018-0370-z}
+\bibitem[\citeproctext]{ref-Dunne2002}
+Dunne, J.A., Williams, R.J., and Martinez, N.D. 2002a. Network structure
+and biodiversity loss in food webs: Robustness increases with
+connectance. Ecology Letters \textbf{5}(4): 558--567.
+doi:\href{https://doi.org/10.1046/j.1461-0248.2002.00354.x}{10.1046/j.1461-0248.2002.00354.x}.
 
-\bibitem[\citeproctext]{ref-Braithwaite2015}
-Braithwaite, J. E., Meeuwig, J. J., Letessier, T. B., Jenner, K. C. S.,
-\& Brierley, A. S. (2015). From sea ice to blubber: Linking whale
-condition to krill abundance using historical whaling records.
-\emph{Polar Biology}, \emph{38}(8), 1195--1202.
-doi:\href{https://doi.org/10.1007/s00300-015-1685-0}{10.1007/s00300-015-1685-0}
+\bibitem[\citeproctext]{ref-Dunne2002a}
+Dunne, J.A., Williams, R.J., and Martinez, N.D. 2002b. Food-web
+structure and network theory: {The} role of connectance and size.
+Proceedings of the National Academy of Sciences \textbf{99}(20):
+12917--12922. Proceedings of the National Academy of Sciences.
+doi:\href{https://doi.org/10.1073/pnas.192407699}{10.1073/pnas.192407699}.
 
-\bibitem[\citeproctext]{ref-Buskey2016}
-Buskey, E. J., White, H. K., \& Esbaugh, A. J. (2016). Impact of {Oil
-Spills} on {Marine Life} in the {Gulf} of {Mexico}: {EFFECTS ON
-PLANKTON}, {NEKTON}, {AND DEEP-SEA BENTHOS}. \emph{Oceanography},
-\emph{29}(3), 174--181. Retrieved from
-\url{https://www.jstor.org/stable/24862719}
+\bibitem[\citeproctext]{ref-Jordan2007}
+Jordán, F., Benedek, Z., and Podani, J. 2007. Quantifying positional
+importance in food webs: {A} comparison of centrality indices.
+Ecological Modelling \textbf{205}(1): 270--275.
+doi:\href{https://doi.org/10.1016/j.ecolmodel.2007.02.032}{10.1016/j.ecolmodel.2007.02.032}.
 
-\bibitem[\citeproctext]{ref-Campana2018}
-Campana, G. L., Zacher, K., Deregibus, D., Momo, F. R., Wiencke, C., \&
-Quartino, M. L. (2018). Succession of {Antarctic} benthic algae ({Potter
-Cove}, {South Shetland Islands}): Structural patterns and glacial impact
-over a four-year period. \emph{Polar Biology}, \emph{41}(2), 377--396.
-doi:\href{https://doi.org/10.1007/s00300-017-2197-x}{10.1007/s00300-017-2197-x}
+\bibitem[\citeproctext]{ref-Kratina2012}
+Kratina, P., LeCraw, R.M., Ingram, T., and Anholt, B.R. 2012. Stability
+and persistence of food webs with omnivory: {Is} there a general
+pattern? Ecosphere \textbf{3}(6): art50.
+doi:\href{https://doi.org/10.1890/ES12-00121.1}{10.1890/ES12-00121.1}.
 
-\bibitem[\citeproctext]{ref-Ciancio2008}
-Ciancio, J. E., Pascual, M. A., Botto, F., Frere, E., \& Iribarne, O.
-(2008). Trophic relationships of exotic anadromous salmonids in the
-southern {Patagonian Shelf} as inferred from stable isotopes.
-\emph{Limnology and Oceanography}, \emph{53}(2), 788--798.
-doi:\href{https://doi.org/10.4319/lo.2008.53.2.0788}{10.4319/lo.2008.53.2.0788}
+\bibitem[\citeproctext]{ref-Nilsson2016}
+Nilsson, K.A., and McCann, K.S. 2016. Interaction strength
+revisited---clarifying the role of energy flux for food web stability.
+Theoretical Ecology \textbf{9}(1): 59--71.
+doi:\href{https://doi.org/10.1007/s12080-015-0282-8}{10.1007/s12080-015-0282-8}.
 
-\bibitem[\citeproctext]{ref-Ciancio2010}
-Ciancio, J., Beauchamp, D. A., \& Pascual, M. (2010). Marine effect of
-introduced salmonids: {Prey} consumption by exotic steelhead and
-anadromous brown trout in the {Patagonian Continental Shelf}.
-\emph{Limnology and Oceanography}, \emph{55}(5), 2181--2192.
-doi:\href{https://doi.org/10.4319/lo.2010.55.5.2181}{10.4319/lo.2010.55.5.2181}
+\bibitem[\citeproctext]{ref-Olivier2019}
+Olivier, P., Frelat, R., Bonsdorff, E., Kortsch, S., Kröncke, I.,
+Möllmann, C., Neumann, H., Sell, A.F., and Nordström, M.C. 2019.
+Exploring the temporal variability of a food web using long-term
+biomonitoring data. Ecography \textbf{42}(12): 2107--2121.
+doi:\href{https://doi.org/10.1111/ecog.04461}{10.1111/ecog.04461}.
 
-\bibitem[\citeproctext]{ref-Clark2013}
-Clark, G. F., Stark, J. S., Johnston, E. L., Runcie, J. W., Goldsworthy,
-P. M., Raymond, B., \& Riddle, M. J. (2013). Light-driven tipping points
-in polar ecosystems. \emph{Global Change Biology}, \emph{19}(12),
-3749--3761.
-doi:\href{https://doi.org/10.1111/gcb.12337}{10.1111/gcb.12337}
+\bibitem[\citeproctext]{ref-Thompson2007}
+Thompson, R.M., Hemberg, M., Starzomski, B.M., and Shurin, J.B. 2007.
+Trophic {Levels} and {Trophic Tangles}: {The Prevalence} of {Omnivory}
+in {Real Food Webs}. Ecology \textbf{88}(3): 612--617.
+doi:\href{https://doi.org/10.1890/05-1454}{10.1890/05-1454}.
 
-\bibitem[\citeproctext]{ref-Constable2014}
-Constable, A. J., Melbourne-Thomas, J., Corney, S. P., Arrigo, K. R.,
-Barbraud, C., Barnes, D. K. A., \ldots{} Ziegler, P. (2014). Climate
-change and {Southern Ocean} ecosystems {I}: How changes in physical
-habitats directly affect marine biota. \emph{Global Change Biology},
-\emph{20}(10), 3004--3025.
-doi:\href{https://doi.org/10.1111/gcb.12623}{10.1111/gcb.12623}
-
-\bibitem[\citeproctext]{ref-Cossi2021}
-Cossi, P. F., Ojeda, M., Chiesa, I. L., Rimondino, G. N., Fraysse, C.,
-Calcagno, J., \& Pérez, A. F. (2021). First evidence of microplastics in
-the {Marine Protected Area Namuncurá} at {Burdwood Bank}, {Argentina}: A
-study on {Henricia} obesa and {Odontaster} penicillatus
-({Echinodermata}: {Asteroidea}). \emph{Polar Biology}, \emph{44}(12),
-2277--2287.
-doi:\href{https://doi.org/10.1007/s00300-021-02959-5}{10.1007/s00300-021-02959-5}
-
-\bibitem[\citeproctext]{ref-Deppeler2020}
-Deppeler, S., Schulz, K. G., Hancock, A., Pascoe, P., McKinlay, J., \&
-Davidson, A. (2020). Ocean acidification reduces growth and grazing
-impact of {Antarctic} heterotrophic nanoflagellates.
-\emph{Biogeosciences}, \emph{17}(16), 4153--4171.
-doi:\href{https://doi.org/10.5194/bg-17-4153-2020}{10.5194/bg-17-4153-2020}
-
-\bibitem[\citeproctext]{ref-Deregibus2023}
-Deregibus, Dolores, Campana, G. L., Neder, C., Barnes, D. K. A., Zacher,
-K., Piscicelli, J. M., \ldots{} Quartino, M. L. (2023). Potential
-macroalgal expansion and blue carbon gains with northern {Antarctic
-Peninsula} glacial retreat. \emph{Marine Environmental Research},
-\emph{189}, 106056.
-doi:\href{https://doi.org/10.1016/j.marenvres.2023.106056}{10.1016/j.marenvres.2023.106056}
-
-\bibitem[\citeproctext]{ref-Deregibus2016}
-Deregibus, D., Quartino, M. L., Campana, G. L., Momo, F. R., Wiencke,
-C., \& Zacher, K. (2016). Photosynthetic light requirements and vertical
-distribution of macroalgae in newly ice-free areas in {Potter Cove},
-{South Shetland Islands}, {Antarctica}. \emph{Polar Biology},
-\emph{39}(1), 153--166.
-doi:\href{https://doi.org/10.1007/s00300-015-1679-y}{10.1007/s00300-015-1679-y}
-
-\bibitem[\citeproctext]{ref-Deregibus2017}
-Deregibus, D., Quartino, M. L., Zacher, K., Campana, G. L., \& Barnes,
-D. K. A. (2017). Understanding the link between sea ice, ice scour and
-{Antarctic} benthic biodiversity\textendash the need for cross-station
-and international collaboration. \emph{Polar Record}, \emph{53}(2),
-143--152.
-doi:\href{https://doi.org/10.1017/S0032247416000875}{10.1017/S0032247416000875}
-
-\bibitem[\citeproctext]{ref-Fernandez2010}
-Fernández, D. A., Ciancio, J., Ceballos, S. G., Riva-Rossi, C., \&
-Pascual, M. A. (2010). Chinook salmon ({Oncorhynchus} tshawytscha,
-{Walbaum} 1792) in the {Beagle Channel}, {Tierra} del {Fuego}: The onset
-of an invasion. \emph{Biological Invasions}, \emph{12}(9), 2991--2997.
-doi:\href{https://doi.org/10.1007/s10530-010-9731-x}{10.1007/s10530-010-9731-x}
-
-\bibitem[\citeproctext]{ref-Ferreira2021}
-Ferreira, M. F., Lo Nostro, F. L., Fernández, D. A., \& Genovese, G.
-(2021). Endocrine disruption in the sub {Antarctic} fish
-{Patagonotothen} tessellata ({Perciformes}, {Notothenidae}) from {Beagle
-Channel} associated to anthropogenic impact. \emph{Marine Environmental
-Research}, \emph{171}, 105478.
-doi:\href{https://doi.org/10.1016/j.marenvres.2021.105478}{10.1016/j.marenvres.2021.105478}
-
-\bibitem[\citeproctext]{ref-Fioramonti2022}
-Fioramonti, N. E., Ribeiro Guevara, S., Becker, Y. A., \& Riccialdelli,
-L. (2022). Mercury transfer in coastal and oceanic food webs from the
-{Southwest Atlantic Ocean}. \emph{Marine Pollution Bulletin},
-\emph{175}, 113365.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2022.113365}{10.1016/j.marpolbul.2022.113365}
-
-\bibitem[\citeproctext]{ref-Flores2012}
-Flores, H., Atkinson, A., Kawaguchi, S., Krafft, B., Milinevsky, G.,
-Nicol, S., \ldots{} Werner, T. (2012). Impact of climate change on
-{Antarctic} krill. \emph{Marine Ecology Progress Series}, \emph{458},
-1--19. doi:\href{https://doi.org/10.3354/meps09831}{10.3354/meps09831}
-
-\bibitem[\citeproctext]{ref-Fuentes2016}
-Fuentes, V., Alurralde, G., Meyer, B., Aguirre, G. E., Canepa, A.,
-Wölfl, A.-C., \ldots{} Schloss, I. R. (2016). Glacial melting: An
-overlooked threat to {Antarctic} krill. \emph{Scientific Reports},
-\emph{6}(1), 27234.
-doi:\href{https://doi.org/10.1038/srep27234}{10.1038/srep27234}
-
-\bibitem[\citeproctext]{ref-Gaitan2016}
-Gaitán, E., \& Marí, N. (2016). {Análisis de las comunidades bentónicas
-asociadas a capturas de la flota comercial dirigida a Macruronus
-magellanicus}. {Instituto Nacional de Investigación y Desarrollo
-Pesquero (INIDEP)}.
-
-\bibitem[\citeproctext]{ref-Galvan2022}
-Galván, D. E., Bovcon, N. D., Cochia, P. D., González, R. A., Lattuca,
-M. E., Reinaldo, M. O., \ldots{} Svendsen, G. M. (2022). Changes in the
-{Specific} and {Biogeographic Composition} of {Coastal Fish Assemblages}
-in {Patagonia}, {Driven} by {Climate Change}, {Fishing}, and {Invasion}
-by {Alien Species}. In E. W. Helbling, M. A. Narvarte, R. A. González,
-\& V. E. Villafañe (Eds.), \emph{Global {Change} in {Atlantic Coastal
-Patagonian Ecosystems}: {A Journey Through Time}} (pp. 205--231).
-{Cham}: {Springer International Publishing}.
-doi:\href{https://doi.org/10.1007/978-3-030-86676-1_9}{10.1007/978-3-030-86676-1\_9}
-
-\bibitem[\citeproctext]{ref-Garcia2019}
-Garcia, M. D., Fernández Severini, M. D., Spetter, C., López Abbate, M.
-C., Tartara, M. N., Nahuelhual, E. G., \ldots{} Hoffmeyer, M. S. (2019).
-Effects of glacier melting on the planktonic communities of two
-{Antarctic} coastal areas ({Potter Cove} and {Hope Bay}) in summer.
-\emph{Regional Studies in Marine Science}, \emph{30}, 100731.
-doi:\href{https://doi.org/10.1016/j.rsma.2019.100731}{10.1016/j.rsma.2019.100731}
-
-\bibitem[\citeproctext]{ref-Garcia2016}
-Garcia, M. D., Hoffmeyer, M. S., Abbate, M. C. L., Barría De Cao, M. S.,
-Pettigrosso, R. E., Almandoz, G. O., \ldots{} Schloss, I. R. (2016).
-Micro- and mesozooplankton responses during two contrasting summers in a
-coastal {Antarctic} environment. \emph{Polar Biology}, \emph{39}(1),
-123--137.
-doi:\href{https://doi.org/10.1007/s00300-015-1678-z}{10.1007/s00300-015-1678-z}
-
-\bibitem[\citeproctext]{ref-Giarratano2010}
-Giarratano, E., \& Amin, O. A. (2010). Heavy metals monitoring in the
-southernmost mussel farm of the world ({Beagle Channel}, {Argentina}).
-\emph{Ecotoxicology and Environmental Safety}, \emph{73}(6), 1378--1384.
-doi:\href{https://doi.org/10.1016/j.ecoenv.2010.06.023}{10.1016/j.ecoenv.2010.06.023}
-
-\bibitem[\citeproctext]{ref-Gonzalez-Zevallos2006}
-González-Zevallos, D., \& Yorio, P. (2006). Seabird use of discards and
-incidental captures at the {Argentine} hake trawl fishery in the {Golfo
-San Jorge}, {Argentina}. \emph{Marine Ecology Progress Series},
-\emph{316}, 175--183.
-doi:\href{https://doi.org/10.3354/meps316175}{10.3354/meps316175}
-
-\bibitem[\citeproctext]{ref-Gonzalez-Zevallos2011}
-González-Zevallos, D., \& Yorio, P. (2011). Consumption of discards and
-interactions between {Black-browed Albatrosses} ({Thalassarche}
-melanophrys) and {Kelp Gulls} ({Larus} dominicanus) at trawl fisheries
-in {Golfo San Jorge}, {Argentina}. \emph{Journal of Ornithology},
-\emph{152}(4), 827--838.
-doi:\href{https://doi.org/10.1007/s10336-011-0657-6}{10.1007/s10336-011-0657-6}
-
-\bibitem[\citeproctext]{ref-Gutt2001a}
-Gutt, Julian. (2001). On the direct impact of ice on marine benthic
-communities, a review. \emph{Polar Biology}, \emph{24}(8), 553--564.
-doi:\href{https://doi.org/10.1007/s003000100262}{10.1007/s003000100262}
-
-\bibitem[\citeproctext]{ref-Gutt2015}
-Gutt, Julian, Bertler, N., Bracegirdle, T. J., Buschmann, A., Comiso,
-J., Hosie, G., \ldots{} Xavier, J. C. (2015). The {Southern Ocean}
-ecosystem under multiple climate change stresses - an integrated
-circumpolar assessment. \emph{Global Change Biology}, \emph{21}(4),
-1434--1453.
-doi:\href{https://doi.org/10.1111/gcb.12794}{10.1111/gcb.12794}
-
-\bibitem[\citeproctext]{ref-Gutt2003}
-Gutt, Julian, \& Piepenburg, D. (2003). Scale-dependent impact on
-diversity of {Antarctic} benthos caused by grounding of icebergs.
-\emph{Marine Ecology Progress Series}, \emph{253}, 77--83.
-doi:\href{https://doi.org/10.3354/meps253077}{10.3354/meps253077}
-
-\bibitem[\citeproctext]{ref-Gutt2001}
-Gutt, Julian, \& Starmans, A. (2001). Quantification of iceberg impact
-and benthic recolonisation patterns in the {Weddell Sea} ({Antarctica}).
-\emph{Polar Biology}, \emph{24}(8), 615--619.
-doi:\href{https://doi.org/10.1007/s003000100263}{10.1007/s003000100263}
-
-\bibitem[\citeproctext]{ref-Gutt1996}
-Gutt, J., Starmans, A., \& Dieckmann, G. (1996). Impact of iceberg
-scouring on polar benthic habitats. \emph{Marine Ecology Progress
-Series}, \emph{137}, 311--316.
-doi:\href{https://doi.org/10.3354/meps137311}{10.3354/meps137311}
-
-\bibitem[\citeproctext]{ref-Hill2013}
-Hill, S. L., Phillips, T., \& Atkinson, A. (2013). Potential {Climate
-Change Effects} on the {Habitat} of {Antarctic Krill} in the {Weddell
-Quadrant} of the {Southern Ocean}. \emph{PLOS ONE}, \emph{8}(8), e72246.
-doi:\href{https://doi.org/10.1371/journal.pone.0072246}{10.1371/journal.pone.0072246}
-
-\bibitem[\citeproctext]{ref-Hoffmann2019}
-Hoffmann, R., Al-Handal, A. Y., Wulff, A., Deregibus, D., Zacher, K.,
-Quartino, M. L., \ldots{} Braeckman, U. (2019). Implications of {Glacial
-Melt-Related Processes} on the {Potential Primary Production} of a
-{Microphytobenthic Community} in {Potter Cove} ({Antarctica}).
-\emph{Frontiers in Marine Science}, \emph{6}, 655.
-doi:\href{https://doi.org/10.3389/fmars.2019.00655}{10.3389/fmars.2019.00655}
-
-\bibitem[\citeproctext]{ref-Isla2023}
-Isla, E. (2023). Animal\textendash{{Energy Relationships}} in a
-{Changing Ocean}: {The Case} of {Continental Shelf Macrobenthic
-Communities} on the {Weddell Sea} and the {Vicinity} of the {Antarctic
-Peninsula}. \emph{Biology}, \emph{12}(5), 659.
-doi:\href{https://doi.org/10.3390/biology12050659}{10.3390/biology12050659}
-
-\bibitem[\citeproctext]{ref-Kaminskyinprep}
-Kaminsky, J., Bagur, M., Boraso, A., Schloss, I. R., Buschmann, A. H.,
-\& Quartino, M. L. (in prep.). Kelp recruitment declines in a
-sub-{Antarctic} ecosystem with high sediment inputs and changes in the
-understory algae.
-
-\bibitem[\citeproctext]{ref-Kawaguchi2013}
-Kawaguchi, S., Ishida, A., King, R., Raymond, B., Waller, N., Constable,
-A., \ldots{} Ishimatsu, A. (2013). Risk maps for {Antarctic} krill under
-projected {Southern Ocean} acidification. \emph{Nature Climate Change},
-\emph{3}(9), 843--847.
-doi:\href{https://doi.org/10.1038/nclimate1937}{10.1038/nclimate1937}
-
-\bibitem[\citeproctext]{ref-Kawaguchi2010}
-Kawaguchi, So, Kurihara, H., King, R., Hale, L., Berli, T., Robinson, J.
-P., \ldots{} Ishimatsu, A. (2010). Will krill fare well under {Southern
-Ocean} acidification? \emph{Biology Letters}, \emph{7}(2), 288--291.
-doi:\href{https://doi.org/10.1098/rsbl.2010.0777}{10.1098/rsbl.2010.0777}
-
-\bibitem[\citeproctext]{ref-Lagger2018}
-Lagger, C., Nime, M., Torre, L., Servetto, N., Tatián, M., \& Sahade, R.
-(2018). Climate change, glacier retreat and a new ice-free island offer
-new insights on {Antarctic} benthic responses. \emph{Ecography},
-\emph{41}(4), 579--591.
-doi:\href{https://doi.org/10.1111/ecog.03018}{10.1111/ecog.03018}
-
-\bibitem[\citeproctext]{ref-Lagger2017}
-Lagger, C., Servetto, N., Torre, L., \& Sahade, R. (2017). Benthic
-colonization in newly ice-free soft-bottom areas in an {Antarctic}
-fjord. \emph{PLOS ONE}, \emph{12}(11), e0186756.
-doi:\href{https://doi.org/10.1371/journal.pone.0186756}{10.1371/journal.pone.0186756}
-
-\bibitem[\citeproctext]{ref-Latorre2023}
-Latorre, M. P., Iachetti, C. M., Schloss, I. R., Antoni, J., Malits, A.,
-De La Rosa, F., \ldots{} Hernando, M. (2023). Summer heatwaves affect
-coastal {Antarctic} plankton metabolism and community structure.
-\emph{Journal of Experimental Marine Biology and Ecology}, \emph{567},
-151926.
-doi:\href{https://doi.org/10.1016/j.jembe.2023.151926}{10.1016/j.jembe.2023.151926}
-
-\bibitem[\citeproctext]{ref-Manno2022}
-Manno, C., Peck, V. L., Corsi, I., \& Bergami, E. (2022). Under
-pressure: {Nanoplastics} as a further stressor for sub-{Antarctic}
-pteropods already tackling ocean acidification. \emph{Marine Pollution
-Bulletin}, \emph{174}, 113176.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2021.113176}{10.1016/j.marpolbul.2021.113176}
-
-\bibitem[\citeproctext]{ref-Martinez2022}
-Martínez, P. A., Wöhler, O. C., Troccoli, G. H., Di Marco, E., \&
-Maydana, L. (2022). \emph{{Descripción de las capturas incidentales de
-granaderos presentes en los lances dirigidos a merluza negra en la
-pesquería argentina de arrastre: período 2010-2019.}} {Instituto
-Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.
-
-\bibitem[\citeproctext]{ref-Meyer2017}
-Meyer, B., Freier, U., Grimm, V., Groeneveld, J., Hunt, B. P. V.,
-Kerwath, S., \ldots{} Yilmaz, N. I. (2017). The winter pack-ice zone
-provides a sheltered but food-poor habitat for larval {Antarctic} krill.
-\emph{Nature Ecology \& Evolution}, \emph{1}(12), 1853--1861.
-doi:\href{https://doi.org/10.1038/s41559-017-0368-3}{10.1038/s41559-017-0368-3}
-
-\bibitem[\citeproctext]{ref-Mintenbeck2012}
-Mintenbeck, K., Barrera-Oro, E. R., Brey, T., Jacob, U., Knust, R.,
-Mark, F. C., \ldots{} Arntz, W. E. (2012). Impact of {Climate Change} on
-{Fishes} in {Complex Antarctic Ecosystems}. In U. Jacob \& G. Woodward
-(Eds.), \emph{Advances in {Ecological Research}} (Vol. 46, pp.
-361--426). {Burlington}: {Academic Press}.
-doi:\href{https://doi.org/10.1016/B978-0-12-396992-7.00006-X}{10.1016/B978-0-12-396992-7.00006-X}
-
-\bibitem[\citeproctext]{ref-Moore1974}
-Moore, S. F., \& Dwyer, R. L. (1974). Effects of oil on marine
-organisms: {A} critical assessment of published data. \emph{Water
-Research}, \emph{8}(10), 819--827.
-doi:\href{https://doi.org/10.1016/0043-1354(74)90028-1}{10.1016/0043-1354(74)90028-1}
-
-\bibitem[\citeproctext]{ref-Moy2009}
-Moy, A. D., Howard, W. R., Bray, S. G., \& Trull, T. W. (2009). Reduced
-calcification in modern {Southern Ocean} planktonic foraminifera.
-\emph{Nature Geoscience}, \emph{2}(4), 276--280.
-doi:\href{https://doi.org/10.1038/ngeo460}{10.1038/ngeo460}
-
-\bibitem[\citeproctext]{ref-Murphy2007}
-Murphy, E. J., Trathan, P. N., Watkins, J. L., Reid, K., Meredith, M.
-P., Forcada, J., \ldots{} Rothery, P. (2007). Climatically driven
-fluctuations in {Southern Ocean} ecosystems. \emph{Proceedings of the
-Royal Society B: Biological Sciences}, \emph{274}(1629), 3057--3067.
-doi:\href{https://doi.org/10.1098/rspb.2007.1180}{10.1098/rspb.2007.1180}
-
-\bibitem[\citeproctext]{ref-Ojeda2021}
-Ojeda, M., Cossi, P. F., Rimondino, G. N., Chiesa, I. L., Boy, C. C., \&
-Pérez, A. F. (2021). Microplastics pollution in the intertidal limpet,
-{Nacella} magellanica, from {Beagle Channel} ({Argentina}).
-\emph{Science of The Total Environment}, \emph{795}, 148866.
-doi:\href{https://doi.org/10.1016/j.scitotenv.2021.148866}{10.1016/j.scitotenv.2021.148866}
-
-\bibitem[\citeproctext]{ref-Orgeira2021}
-Orgeira, J. L., Alvarez, F., \& Salvó, C. S. (2021). The same pathway to
-the {Weddell Sea} birdlife, after 65 years: Similarities in the species
-composition, richness and abundances. \emph{Czech Polar Reports},
-\emph{11}(2), 291--304.
-doi:\href{https://doi.org/10.5817/CPR2021-2-20}{10.5817/CPR2021-2-20}
-
-\bibitem[\citeproctext]{ref-Pallin2023}
-Pallin, L. J., Kellar, N. M., Steel, D., Botero-Acosta, N., Baker, C.
-S., Conroy, J. A., \ldots{} Friedlaender, A. S. (2023). A surplus no
-more? {Variation} in krill availability impacts reproductive rates of
-{Antarctic} baleen whales. \emph{Global Change Biology}, \emph{29}(8),
-2108--2121.
-doi:\href{https://doi.org/10.1111/gcb.16559}{10.1111/gcb.16559}
-
-\bibitem[\citeproctext]{ref-Perez2021}
-Pérez, A. F., Ojeda, M., Cossi, P. F., Rimondino, G. N., Chiesa, I. L.,
-Fraysse, C., \& Calcagno, J. (2021). {Microplásticos en organismos
-marinos de altas latitudes}. In \emph{{I Jornadas de la Red Científica
-Argentina para el estudio de los plásticos y sus impactos en el ambiente
-(SEPIA)}}.
-
-\bibitem[\citeproctext]{ref-Perez2020}
-Pérez, Analía F., Ojeda, M., Rimondino, G. N., Chiesa, I. L., Di Mauro,
-R., Boy, C. C., \& Calcagno, J. A. (2020). First report of microplastics
-presence in the mussel {Mytilus} chilensis from {Ushuaia Bay} ({Beagle
-Channel}, {Tierra} del {Fuego}, {Argentina}). \emph{Marine Pollution
-Bulletin}, \emph{161}, 111753.
-doi:\href{https://doi.org/10.1016/j.marpolbul.2020.111753}{10.1016/j.marpolbul.2020.111753}
-
-\bibitem[\citeproctext]{ref-Perry2020}
-Perry, F. A., Kawaguchi, S., Atkinson, A., Sailley, S. F., Tarling, G.
-A., Mayor, D. J., \ldots{} Cooper, A. (2020).
-Temperature\textendash{{Induced Hatch Failure}} and {Nauplii
-Malformation} in {Antarctic Krill}. \emph{Frontiers in Marine Science},
-\emph{7}.
-
-\bibitem[\citeproctext]{ref-Pineda-Metz2020}
-Pineda-Metz, S. E. A., Gerdes, D., \& Richter, C. (2020). Benthic fauna
-declined on a whitening {Antarctic} continental shelf. \emph{Nature
-Communications}, \emph{11}(1), 2226.
-doi:\href{https://doi.org/10.1038/s41467-020-16093-z}{10.1038/s41467-020-16093-z}
-
-\bibitem[\citeproctext]{ref-Pinones2016}
-Piñones, A., \& Fedorov, A. V. (2016). Projected changes of {Antarctic}
-krill habitat by the end of the 21st century. \emph{Geophysical Research
-Letters}, \emph{43}(16), 8580--8589.
-doi:\href{https://doi.org/10.1002/2016GL069656}{10.1002/2016GL069656}
-
-\bibitem[\citeproctext]{ref-Quartino2013}
-Quartino, M. L., Deregibus, D., Campana, G. L., Latorre, G. E. J., \&
-Momo, F. R. (2013). Evidence of {Macroalgal Colonization} on {Newly
-Ice-Free Areas} following {Glacial Retreat} in {Potter Cove} ({South
-Shetland Islands}), {Antarctica}. \emph{PLoS ONE}, \emph{8}(3), e58223.
-doi:\href{https://doi.org/10.1371/journal.pone.0058223}{10.1371/journal.pone.0058223}
-
-\bibitem[\citeproctext]{ref-Rowlands2021}
-Rowlands, E., Galloway, T., Cole, M., Lewis, C., Peck, V., Thorpe, S.,
-\& Manno, C. (2021). The {Effects} of {Combined Ocean Acidification} and
-{Nanoplastic Exposures} on the {Embryonic Development} of {Antarctic
-Krill}. \emph{Frontiers in Marine Science}, \emph{8}.
-
-\bibitem[\citeproctext]{ref-Sahade2015}
-Sahade, R., Lagger, C., Torre, L., Momo, F., Monien, P., Schloss, I.,
-\ldots{} Abele, D. (2015). Climate change and glacier retreat drive
-shifts in an {Antarctic} benthic ecosystem. \emph{Science Advances},
-\emph{1}(10), e1500050.
-doi:\href{https://doi.org/10.1126/sciadv.1500050}{10.1126/sciadv.1500050}
-
-\bibitem[\citeproctext]{ref-Saravia2021}
-Saravia, J., Paschke, K., Oyarzún-Salazar, R., Cheng, C.-H. C., Navarro,
-J. M., \& Vargas-Chacoff, L. (2021). Effects of warming rates on
-physiological and molecular components of response to {CTMax} heat
-stress in the {Antarctic} fish {Harpagifer} antarcticus. \emph{Journal
-of Thermal Biology}, \emph{99}, 103021.
-doi:\href{https://doi.org/10.1016/j.jtherbio.2021.103021}{10.1016/j.jtherbio.2021.103021}
-
-\bibitem[\citeproctext]{ref-Seco2021}
-Seco, J., Aparício, S., Brierley, A. S., Bustamante, P., Ceia, F. R.,
-Coelho, J. P., \ldots{} Xavier, J. C. (2021). Mercury biomagnification
-in a {Southern Ocean} food web. \emph{Environmental Pollution},
-\emph{275}, 116620.
-doi:\href{https://doi.org/10.1016/j.envpol.2021.116620}{10.1016/j.envpol.2021.116620}
-
-\bibitem[\citeproctext]{ref-Siniff2008}
-Siniff, D. B., Garrott, R. A., Rotella, J. J., Fraser, W. R., \& Ainley,
-D. G. (2008). Opinion: {Projecting} the effects of environmental change
-on {Antarctic} seals. \emph{Antarctic Science}, \emph{20}(5), 425--435.
-doi:\href{https://doi.org/10.1017/S0954102008001351}{10.1017/S0954102008001351}
-
-\bibitem[\citeproctext]{ref-Smale2008a}
-Smale, D. A., Brown, K. M., Barnes, D. K. A., Fraser, K. P. P., \&
-Clarke, A. (2008). Ice {Scour Disturbance} in {Antarctic Waters}.
-\emph{Science}, \emph{321}(5887), 371--371.
-doi:\href{https://doi.org/10.1126/science.1158647}{10.1126/science.1158647}
-
-\bibitem[\citeproctext]{ref-Souza2018}
-Souza, M. R. D. P. de, Herrerias, T., Zaleski, T., Forgati, M.,
-Kandalski, P. K., Machado, C., \ldots{} Donatti, L. (2018). Heat stress
-in the heart and muscle of the {Antarctic} fishes {Notothenia} rossii
-and {Notothenia} coriiceps: {Carbohydrate} metabolism and antioxidant
-defence. \emph{Biochimie}, \emph{146}, 43--55.
-doi:\href{https://doi.org/10.1016/j.biochi.2017.11.010}{10.1016/j.biochi.2017.11.010}
-
-\bibitem[\citeproctext]{ref-Strobel2013}
-Strobel, A., Leo, E., Pörtner, H. O., \& Mark, F. C. (2013). Elevated
-temperature and {PCO2} shift metabolic pathways in differentially
-oxidative tissues of {Notothenia} rossii. \emph{Comparative Biochemistry
-and Physiology Part B: Biochemistry and Molecular Biology},
-\emph{166}(1), 48--57.
-doi:\href{https://doi.org/10.1016/j.cbpb.2013.06.006}{10.1016/j.cbpb.2013.06.006}
-
-\bibitem[\citeproctext]{ref-Tamini2023}
-Tamini, L. L., Dellacasa, R. F., Chavez, L. N., Marinao, C. J., Góngora,
-M. E., Crawford, R., \& Frere, E. (2023). Bird scaring lines reduce
-seabird mortality in mid-water and bottom trawlers in {Argentina}.
-\emph{ICES Journal of Marine Science}, fsad109.
-doi:\href{https://doi.org/10.1093/icesjms/fsad109}{10.1093/icesjms/fsad109}
-
-\bibitem[\citeproctext]{ref-Trathan2021}
-Trathan, P. N., Fielding, S., Hollyman, P. R., Murphy, E. J.,
-Warwick-Evans, V., \& Collins, M. A. (2021). Enhancing the ecosystem
-approach for the fishery for {Antarctic} krill within the complex,
-variable, and changing ecosystem at {South Georgia}. \emph{ICES Journal
-of Marine Science}, \emph{78}(6), 2065--2081.
-doi:\href{https://doi.org/10.1093/icesjms/fsab092}{10.1093/icesjms/fsab092}
-
-\bibitem[\citeproctext]{ref-Trebilco2020}
-Trebilco, R., Melbourne-Thomas, J., \& Constable, A. J. (2020). The
-policy relevance of {Southern Ocean} food web structure: {Implications}
-of food web change for fisheries, conservation and carbon sequestration.
-\emph{Marine Policy}, \emph{115}, 103832.
-doi:\href{https://doi.org/10.1016/j.marpol.2020.103832}{10.1016/j.marpol.2020.103832}
-
-\bibitem[\citeproctext]{ref-Wege2021}
-Wege, M., Salas, L., \& LaRue, M. (2021). Ice matters: {Life-history}
-strategies of two {Antarctic} seals dictate climate change eventualities
-in the {Weddell Sea}. \emph{Global Change Biology}, \emph{27}(23),
-6252--6262.
-doi:\href{https://doi.org/10.1111/gcb.15828}{10.1111/gcb.15828}
-
-\bibitem[\citeproctext]{ref-Yorio2017}
-Yorio, P., González-Zevallos, D., Gatto, A., Biagioni, O., \& Castillo,
-J. (2017). Relevance of forage fish in the diet of {Magellanic} penguins
-breeding in northern {Patagonia}, {Argentina}. \emph{Marine Biology
-Research}, \emph{13}(6), 603--617.
-doi:\href{https://doi.org/10.1080/17451000.2016.1273529}{10.1080/17451000.2016.1273529}
+\bibitem[\citeproctext]{ref-Williams2000}
+Williams, R.J., and Martinez, N.D. 2000. Simple rules yield complex food
+webs. Nature \textbf{404}(6774): 180--183. Nature Publishing Group.
+doi:\href{https://doi.org/10.1038/35004572}{10.1038/35004572}.
 

### 2024-04-19 manuscript.Rmd
Version to submit

@@
 San Jorge Gulf is the northernmost study area considered in this review (Figure 1), located from Cabo dos Bahias (44°55'S) to Cabo tres Puntas (47°06'S).
-It is a partially enclosed basin spanning approximately 34,000 km^2 and ~100 m of maximum depths.
+It is a partially enclosed basin spanning approximately 34,000 $\text{km}^2$ and ~100 m of maximum depths.
 The gulf’s productivity supports large invertebrate and vertebrate fisheries [@Gongora2012], as well as marine mammal and seabird populations [@Yorio2009].
@@
 
-Located at a more southern latitude (~54ºS, 68ºW), the Beagle Channel (Figure 1) is an interoceanic passage at the southernmost tip of South America, spanning 240 km in length and 5 km in width (~1200 km^2), with a depth range of 0 - 140 m.
+Located at a more southern latitude (~54ºS, 68ºW), the Beagle Channel (Figure 1) is an interoceanic passage at the southernmost tip of South America, spanning 240 km in length and 5 km in width (~1200 $\text{km}^2$), with a depth range of 0 - 140 m.
 It features complex coastlines, varying bathymetry, a prevailing west-to-east circulation pattern, and a significant longitudinal gradient of glacial freshwater discharge [@Schloss2023].
@@
 
-A main local stressor in the Beagle Channel is the introduction of invasive species (Table 2).
+One of the main local stressors in the Beagle Channel is the introduction of invasive species (Table 2).
 Salmonidae were introduced to Tierra del Fuego in the 1930s.
@@
 Another potential competitor for Chinook salmon in the Beagle Channel, sharing a similar diet, is the native Commerson's dolphin *Cephalorhynchus commersonii* [@Riccialdelli2013].
+In invaded ecosystems, predation emerges as the primary driver of significant damage, often leading to cascading effects impacting even primary producers [@David2017].
 In the Beagle Channel, other stressors include contaminants like metals, perfluorinated compounds, hydrocarbons, and microplastics found in animal tissue (algae, mussel, fish, and guano) and sediments [@Duarte2011; @Llorca2012].
@@
 These studies link pollutants to port and industrial activities of Ushuaia; we therefore expect the area of the Beagle Channel closest to the city to be the most affected by contaminants.
-Contaminants potentially spread through the food web, magnifying the risk to higher trophic level taxa.
+Contaminants potentially spread through the food web, from lower to higher trophic level taxa.
 In the Beagle Channel and Atlantic coast of Tierra del Fuego food webs mercury concentrations rose with benthivory, and higher mercury was found in phytoplankton and the squat lobster.
@@
 Physical features in the plateau are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC [@Acha2004].
-The plateau is surrounded by steep flanks of up to 4000 m depth, protected by the Marine Protected Area Namuncurá - Burdwood Bank II (32,000 km^2).
+The plateau is surrounded by steep flanks of up to 4000 m depth, protected by the Marine Protected Area Namuncurá - Burdwood Bank II (32,000 $\text{km}^2$).
 Intense upwelling and mixing occur in relation to the slope, entraining deep nutrient-rich waters into the photic layer [@Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Matano2019].
@@
 
-The Scotia Sea is a deep-sea basin (~48 - 58ºS, 50ºW), delimited by the Drake Passage to the West and by the island complex of the Scotia Arc to the North, East, and South, with an approximate extension of 1.5 x 106 km^2 and a depth range of 0 - 3000 m [@Murphy2006] (Figure 1).
+The Scotia Sea is a deep-sea basin (~48 - 58ºS, 50ºW), delimited by the Drake Passage to the West and by the island complex of the Scotia Arc to the North, East, and South, with an approximate extension of 1.5 x 106 $\text{km}^2$ and a depth range of 0 - 3000 m [@Murphy2006] (Figure 1).
 Its oceanography is dominated by the Antarctic Circumpolar Current, which is spatially structured by frontal systems [@Whitworth1980].
@@
 Recently, @Trathan2023 has identified several concerns regarding aspects of these fisheries, highlighting that it is crucial to recognize ongoing changes such as the recovery of baleen whales and climate change.
-These factors increase uncertainty for fisheries managers, necessitating direct consideration in the management of harvested and dependent species.
+These factors increase the uncertainty for fishery managers, necessitating direct consideration in the management of harvested and dependent species.
 
@@
 
-In the Antarctic realm, Potter Cove is a ~9 km2 fjord with a depth range of 0 - 200 m located at 25 de Mayo/King George Island (62°S, 58°W) on the South Shetland Islands of the West Antarctic Peninsula (Figure 1).
+In the Antarctic realm, Potter Cove is a ~9 $\text{km}^2$ fjord with a depth range of 0 - 200 m located at 25 de Mayo/King George Island (62°S, 58°W) on the South Shetland Islands of the West Antarctic Peninsula (Figure 1).
 The cove, bordered by the Fourcade Glacier, is divided into three areas: a) the internal cove, a high glacier-influenced, soft sediment zone with a 50 m maximum depth; b) the central cove, a mixed substrate area with low meltwater influence and an 80 m maximum depth; and c) the external cove, ice-free for 60 years with a 185 m maximum depth and rocky substrate [@Jerosch2018].
@@
 Global warming is predicted to increase iceberg scouring frequency [@Gutt2001a; @Smale2008a], disrupting the environment [@Smale2008] with the potential for tipping points  [@Gutt2015].
-________________
 
@@
 \normalsize
-
 ## 3. From species’ stressors to food web effects: a qualitative approach
@@
 In Potter Cove, a fjord-like Antarctic ecosystem, the repercussions of climate change extend across numerous species.
-Noteworthy, these effects are non-uniform within the food web, manifesting differently across its various compartments [@Cordone2020; @Rodriguez2022].
+Noteworthy, these effects are non-uniform within the food web, manifesting differently across its pelagic and benthic compartments.
 Potter Cove has recently experienced frequent events of marine heatwaves, i.e., prolonged periods of anomalously high sea surface temperature [@Oliver2018; @Latorre2023].
 This has led to decreases in biomasses of different planktonic functional groups [@Garcia2019; @Latorre2023].
-Given the relatively low abundance of phytoplankton and zooplankton’s low mean degree, resulting in weak interaction strengths between these low trophic levels and higher ones [@Rodriguez2024], added to the modular configuration of the food web [@Rodriguez2022], we hypothesize that changes in these nodes due to warming will be retained at the basal level of the pelagic compartment and will not expand to higher trophic levels.
-Benthic primary producers in Potter Cove are being influenced by the decrease in winter sea ice cover (higher light availability), the increased levels of sediments in the water column due to glacial melt run-off (lower light penetration) and the newly free-ice areas available for colonization associated to glacier retreat.
-The overall local effect of climate change on macroalgae is a net increase in their production [@Deregibus2023].
-It has been proposed that larger diversity in primary producers can support a more diverse food web with more specialized consumers [@Iken2023].
-Given the high relative abundance and the high degree of the macroalgae functional group (Table S1), we expect a longer hard bottom food web (i.e., number of interactions connecting low and high-trophic levels), wider consumer trophic niches, and a more stable benthic food web as sea ice cover decreases and glaciers retreat due to global warming.
-In soft bottom areas of the cove, multiple food web nodes are being affected by ongoing warming effects: decrease in net primary production of benthic microalgae [@Hoffmann2019], and changes in the benthic community biomass, distribution and composition [@Sahade2015; @Pasotti2015].
-Given that the Potter Cove food web has low connectance and omnivory, we suggest fragility and potential trophic cascade effects [@Marina2018], especially between species of the soft bottom compartment (Table 3).
-Overall, we anticipate significant shifts in energy fluxes, rather than alterations in the overall structure of the Potter Cove food web, with strengthening of connections within compartments.
+Given the relatively low abundance of phytoplankton and zooplankton low mean degree (Table S1), resulting in weak interaction strengths between these low trophic levels and higher ones [@Rodriguez2024], added to the modular configuration of the food web [@Rodriguez2022], we hypothesize that changes in these nodes due to warming will be retained at the lower trophic levels of the pelagic compartment and will not expand to higher trophic levels.
+Macroalgae, important benthic primary producers, are being influenced by the decrease in winter sea ice cover (higher light availability), the increased levels of sediments in the water column due to glacial melt run-off (lower light penetration) and the newly free-ice areas available for colonization associated to glacier retreat.
+The local effect of climate change on macroalgae is a net increase in their production and macroalgal detritus [@Deregibus2023; @Iken2023; @Braeckman2019].
+On the other hand, increased glacial runoff lead to a decrease in net primary production of benthic microalgae [@Hoffmann2019]; reduced secondary benthic production; changes on the benthic community composition and an expansion of its distribution towards newly free-ice areas, specially filter and deposit feeders species [@Braeckman2024; @Sahade2015; @Pasotti2015].
+In an increasing glacial melt disturbance scenario, it’s expected a shift in the food sources of benthic species towards grazing on macroalgal and their detritus [@Braeckman2024].
+It has been proposed that larger diversity in primary sources can support a more diverse food web with more specialized consumers [@Iken2023].
+Given the high relative abundance and the high degree of the macroalgae functional group (Table S1), we expect a longer benthic food web (i.e., number of interactions connecting low and high-trophic levels), wider consumer trophic niches, meaning an increase in omnivory, and a more stable benthic food web as sea ice cover decreases and glaciers retreat due to global warming.
+As a net effect of climate change on the overall Potter Cove food web, we expect a significant shift in energy fluxes, rather than drastic alterations in the topological structure, affecting the transfer of energy from lower to higher trophic levels.
 
@@
 The projected rise in iceberg scouring is expected to significantly alter the biomass and community structure of macrobenthos, which in turn will impact mid-trophic level predators such as demersal fish [@Gutt2001a; @Mintenbeck2012].
-While we do not anticipate large-scale topological changes in the mean food web attributes, local extinctions could lead to such changes, particularly affecting benthic species [@Gutt2003].
+While we do not anticipate large-scale topological changes affecting mean food web attributes, local extinctions may produce changes in the interactions, especially impacting benthic species [@Gutt2003].
 Given that the impacted species—whether individually like krill, or collectively like macrobenthos and notothenioids (e.g., *P.
@@
 +-----------------------+----------------------+-----------------------+
-| **Study area**        | **Stressor**         | **Hypothesis on food web effects**  |
-|                       |                      |                       |
+| **Study area**        | **Stressor**         | **Hypothesis on food  |
+|                       |                      |       web effects**   |
 +=======================+======================+=======================+
@@
 +-----------------------+----------------------+-----------------------+
-|                       | Sea ice decline +    | Differential impacts, |
-|                       | glacial retreat      | by substrate: hard    |
-|                       |                      | (HS) or soft (SS)     |
-|                       |                      |                       |
-|                       |                      | ↑ FW chain length & ↑ |
-|                       |                      | trophic niches (HS)   |
-|                       |                      |                       |
-|                       |                      | ↑ FW fragility &      |
-|                       |                      | trophic cascades (SS) |
+|                       | Sea ice decline +    | ↑ FW chain length & |
+|                       | glacial retreat      | ↑ trophic niches    |
 +-----------------------+----------------------+-----------------------+
@@
 In this review, we proposed a series of alternative hypotheses on how global stressors may affect food webs in the Southwest Atlantic to Southern Ocean.
-Despite being qualitative, this is a first important step in synthesizing food webs and stressor effects on food webs for this region.
+Despite being qualitative, this is a first important step in synthesizing food webs and stressor effects on species and food webs for this region.
 These qualitative assessments must be complemented with further investigations that test their validity.
@@
 Using a theoretical framework that combines species and food web-level data, we suggest how warming effects may impact food web structure and functioning.
-Besides there is an important amount of uncertainty, these qualitative predictions are intended to serve as the basis for future studies in marine ecosystems of the Southern Hemisphere that aim at quantifying the magnitude of these stressors and how they are affecting quantitative food web properties, such as energy fluxes and stability.
+Apart from an important amount of uncertainty, these qualitative predictions are intended to serve as the basis for future studies in marine ecosystems of the Southern Hemisphere that aim at quantifying the magnitude of these stressors and how they are affecting quantitative food web properties, such as energy fluxes and stability.
 There is an urgent need to assess these changes using a holistic and quantitative framework where the magnitude of stressors and species interactions are taken into account.

### 2024-04-19 manuscript.tex
Version to submit

@@
 \usepackage{longtable,booktabs,array}
-\usepackage{multirow}
 \usepackage{calc} % for calculating minipage widths
@@
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
 \subsection{2. Assessment of the food web structure and stressors in the
@@
 (47°06'S). It is a partially enclosed basin spanning approximately
-34,000 km\^{}2 and \textasciitilde100 m of maximum depths. The gulf's
-productivity supports large invertebrate and vertebrate fisheries
+34,000 \(\text{km}^2\) and \textasciitilde100 m of maximum depths. The
+gulf's productivity supports large invertebrate and vertebrate fisheries
 (Góngora et al. 2012), as well as marine mammal and seabird populations
@@
 tip of South America, spanning 240 km in length and 5 km in width
-(\textasciitilde1200 km\^{}2), with a depth range of 0 - 140 m. It
-features complex coastlines, varying bathymetry, a prevailing
+(\textasciitilde1200 \(\text{km}^2\)), with a depth range of 0 - 140 m.
+It features complex coastlines, varying bathymetry, a prevailing
 west-to-east circulation pattern, and a significant longitudinal
@@
 
-A main local stressor in the Beagle Channel is the introduction of
-invasive species (Table 2). Salmonidae were introduced to Tierra del
-Fuego in the 1930s. Especially, the Chinook salmon \emph{Oncorhynchus
-tshawytscha} causes concern. The detection of this species in Tierra del
-Fuego dates back to April 2006, and its population has been expanding
-since then (Nardi et al. 2019). Being a top predator, the Chinook salmon
-can compete for resources with several native predators in the Beagle
-Channel (Correa and Gross 2008), but also prey on them. This is the case
-for Notothenioids (\emph{Eleginops maclovinus}, \emph{Patagonotothen
-tessellata}, \emph{P. cornucola}, \emph{P. sima}, \emph{Paranotothenia
-magellanica}, \emph{Harpagifer bispinis}), the Atherinidae
-\emph{Odontesthes smitti} and \emph{O. nigricans}, the Fuegian sprat,
-and larvae of king crabs (\emph{Lithodes antarcticus} and
-\emph{Paralomis granulosa}) (Fernández et al. 2010). Ciancio et al.
-(2008) observed that Chinook salmon primarily feeds on sprats in the
-Southern Patagonian Shelf Ecosystem area and display trophic levels
-comparable to those of intermediate-sized fish and cephalopod predator
-species, showing significant dietary overlap with the Magellanic penguin
-\emph{Spheniscus magellanicus}. Another potential competitor for Chinook
-salmon in the Beagle Channel, sharing a similar diet, is the native
-Commerson's dolphin \emph{Cephalorhynchus commersonii} (Riccialdelli et
-al. 2013). In the Beagle Channel, other stressors include contaminants
+One of the main local stressors in the Beagle Channel is the
+introduction of invasive species (Table 2). Salmonidae were introduced
+to Tierra del Fuego in the 1930s. Especially, the Chinook salmon
+\emph{Oncorhynchus tshawytscha} causes concern. The detection of this
+species in Tierra del Fuego dates back to April 2006, and its population
+has been expanding since then (Nardi et al. 2019). Being a top predator,
+the Chinook salmon can compete for resources with several native
+predators in the Beagle Channel (Correa and Gross 2008), but also prey
+on them. This is the case for Notothenioids (\emph{Eleginops
+maclovinus}, \emph{Patagonotothen tessellata}, \emph{P. cornucola},
+\emph{P. sima}, \emph{Paranotothenia magellanica}, \emph{Harpagifer
+bispinis}), the Atherinidae \emph{Odontesthes smitti} and \emph{O.
+nigricans}, the Fuegian sprat, and larvae of king crabs (\emph{Lithodes
+antarcticus} and \emph{Paralomis granulosa}) (Fernández et al. 2010).
+Ciancio et al. (2008) observed that Chinook salmon primarily feeds on
+sprats in the Southern Patagonian Shelf Ecosystem area and display
+trophic levels comparable to those of intermediate-sized fish and
+cephalopod predator species, showing significant dietary overlap with
+the Magellanic penguin \emph{Spheniscus magellanicus}. Another potential
+competitor for Chinook salmon in the Beagle Channel, sharing a similar
+diet, is the native Commerson's dolphin \emph{Cephalorhynchus
+commersonii} (Riccialdelli et al. 2013). In invaded ecosystems,
+predation emerges as the primary driver of significant damage, often
+leading to cascading effects impacting even primary producers (David et
+al. 2017). In the Beagle Channel, other stressors include contaminants
 like metals, perfluorinated compounds, hydrocarbons, and microplastics
@@
 the city to be the most affected by contaminants. Contaminants
-potentially spread through the food web, magnifying the risk to higher
-trophic level taxa. In the Beagle Channel and Atlantic coast of Tierra
-del Fuego food webs mercury concentrations rose with benthivory, and
-higher mercury was found in phytoplankton and the squat lobster. This
-latter species connects pelagic and benthic habitats, so any disruption
-to them could disrupt the food web (Rodriguez et al. 2022). Dodino et
-al. (2022) found the highest mercury levels in Magellanic penguin
-feathers from offshore colonies in Tierra del Fuego. Recently, Ushuaia's
-kelp forests have also seen changes in composition along with a decrease
-in biodiversity as a result of urban pollution (Kaminsky et al. 2023).
-It is important to note that sea warming might be a less significant
+potentially spread through the food web, from lower to higher trophic
+level taxa. In the Beagle Channel and Atlantic coast of Tierra del Fuego
+food webs mercury concentrations rose with benthivory, and higher
+mercury was found in phytoplankton and the squat lobster. This latter
+species connects pelagic and benthic habitats, so any disruption to them
+could disrupt the food web (Rodriguez et al. 2022). Dodino et al. (2022)
+found the highest mercury levels in Magellanic penguin feathers from
+offshore colonies in Tierra del Fuego. Recently, Ushuaia's kelp forests
+have also seen changes in composition along with a decrease in
+biodiversity as a result of urban pollution (Kaminsky et al. 2023). It
+is important to note that sea warming might be a less significant
 stressor in the Beagle Channel compared to the other areas, as global
@@
 protected by the Marine Protected Area Namuncurá - Burdwood Bank II
-(32,000 km\^{}2). Intense upwelling and mixing occur in relation to the
-slope, entraining deep nutrient-rich waters into the photic layer
+(32,000 \(\text{km}^2\)). Intense upwelling and mixing occur in relation
+to the slope, entraining deep nutrient-rich waters into the photic layer
 (Matano et al. 2019), and resulting in a fairly homogeneous water column
@@
 the Scotia Arc to the North, East, and South, with an approximate
-extension of 1.5 x 106 km\^{}2 and a depth range of 0 - 3000 m (Murphy
-et al. 2006) (Figure 1). Its oceanography is dominated by the Antarctic
-Circumpolar Current, which is spatially structured by frontal systems
-(Whitworth 1980). The South Antarctic Circumpolar Current Front
+extension of 1.5 x 106 \(\text{km}^2\) and a depth range of 0 - 3000 m
+(Murphy et al. 2006) (Figure 1). Its oceanography is dominated by the
+Antarctic Circumpolar Current, which is spatially structured by frontal
+systems (Whitworth 1980). The South Antarctic Circumpolar Current Front
 subdivides the Scotia Sea into two biogeographic regions: the Northern
@@
 recognize ongoing changes such as the recovery of baleen whales and
-climate change. These factors increase uncertainty for fisheries
+climate change. These factors increase the uncertainty for fishery
 managers, necessitating direct consideration in the management of
@@
 
-In the Antarctic realm, Potter Cove is a \textasciitilde9 km2 fjord with
-a depth range of 0 - 200 m located at 25 de Mayo/King George Island
-(62°S, 58°W) on the South Shetland Islands of the West Antarctic
-Peninsula (Figure 1). The cove, bordered by the Fourcade Glacier, is
-divided into three areas: a) the internal cove, a high
-glacier-influenced, soft sediment zone with a 50 m maximum depth; b) the
-central cove, a mixed substrate area with low meltwater influence and an
-80 m maximum depth; and c) the external cove, ice-free for 60 years with
-a 185 m maximum depth and rocky substrate (Jerosch et al. 2018). Potter
-Cove's high-latitude location results in variable environmental
-conditions due to photoperiod length seasonality. Sea ice often covers
-this area in winter (Schloss et al. 2012). With low phytoplankton
-biomass, macroalgae, and microphytobenthos are likely the primary food
-sources for secondary benthic production (Quartino and Boraso de Zaixso
-2008).
+In the Antarctic realm, Potter Cove is a \textasciitilde9
+\(\text{km}^2\) fjord with a depth range of 0 - 200 m located at 25 de
+Mayo/King George Island (62°S, 58°W) on the South Shetland Islands of
+the West Antarctic Peninsula (Figure 1). The cove, bordered by the
+Fourcade Glacier, is divided into three areas: a) the internal cove, a
+high glacier-influenced, soft sediment zone with a 50 m maximum depth;
+b) the central cove, a mixed substrate area with low meltwater influence
+and an 80 m maximum depth; and c) the external cove, ice-free for 60
+years with a 185 m maximum depth and rocky substrate (Jerosch et al.
+2018). Potter Cove's high-latitude location results in variable
+environmental conditions due to photoperiod length seasonality. Sea ice
+often covers this area in winter (Schloss et al. 2012). With low
+phytoplankton biomass, macroalgae, and microphytobenthos are likely the
+primary food sources for secondary benthic production (Quartino and
+Boraso de Zaixso 2008).
 
@@
 disrupting the environment (Smale and Barnes 2008) with the potential
-for tipping points (Gutt et al. 2015). \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
+for tipping points (Gutt et al. 2015).
 
@@
 \endlastfoot
-
 \textbf{San Jorge Gulf} & & & & & \\
@@
 are non-uniform within the food web, manifesting differently across its
-various compartments (Cordone et al. 2020; Rodriguez et al. 2022).
-Potter Cove has recently experienced frequent events of marine
-heatwaves, i.e., prolonged periods of anomalously high sea surface
-temperature (Oliver et al. 2018; Latorre et al. 2023). This has led to
-decreases in biomasses of different planktonic functional groups (Garcia
-et al. 2019; Latorre et al. 2023). Given the relatively low abundance of
-phytoplankton and zooplankton's low mean degree, resulting in weak
-interaction strengths between these low trophic levels and higher ones
-(\textbf{Rodriguez2024?}), added to the modular configuration of the
-food web (Rodriguez et al. 2022), we hypothesize that changes in these
-nodes due to warming will be retained at the basal level of the pelagic
-compartment and will not expand to higher trophic levels. Benthic
-primary producers in Potter Cove are being influenced by the decrease in
-winter sea ice cover (higher light availability), the increased levels
-of sediments in the water column due to glacial melt run-off (lower
-light penetration) and the newly free-ice areas available for
-colonization associated to glacier retreat. The overall local effect of
-climate change on macroalgae is a net increase in their production
-(Deregibus et al. 2023). It has been proposed that larger diversity in
-primary producers can support a more diverse food web with more
+pelagic and benthic compartments. Potter Cove has recently experienced
+frequent events of marine heatwaves, i.e., prolonged periods of
+anomalously high sea surface temperature (Oliver et al. 2018; Latorre et
+al. 2023). This has led to decreases in biomasses of different
+planktonic functional groups (Garcia et al. 2019; Latorre et al. 2023).
+Given the relatively low abundance of phytoplankton and zooplankton low
+mean degree (Table S1), resulting in weak interaction strengths between
+these low trophic levels and higher ones (Rodriguez and Saravia 2024),
+added to the modular configuration of the food web (Rodriguez et al.
+2022), we hypothesize that changes in these nodes due to warming will be
+retained at the lower trophic levels of the pelagic compartment and will
+not expand to higher trophic levels. Macroalgae, important benthic
+primary producers, are being influenced by the decrease in winter sea
+ice cover (higher light availability), the increased levels of sediments
+in the water column due to glacial melt run-off (lower light
+penetration) and the newly free-ice areas available for colonization
+associated to glacier retreat. The local effect of climate change on
+macroalgae is a net increase in their production and macroalgal detritus
+(Braeckman et al. 2019; Deregibus et al. 2023; Iken et al. 2023). On the
+other hand, increased glacial runoff lead to a decrease in net primary
+production of benthic microalgae (Hoffmann et al. 2019); reduced
+secondary benthic production; changes on the benthic community
+composition and an expansion of its distribution towards newly free-ice
+areas, specially filter and deposit feeders species (Sahade et al. 2015;
+Pasotti et al. 2015; Braeckman et al. 2024). In an increasing glacial
+melt disturbance scenario, it's expected a shift in the food sources of
+benthic species towards grazing on macroalgal and their detritus
+(Braeckman et al. 2024). It has been proposed that larger diversity in
+primary sources can support a more diverse food web with more
 specialized consumers (Iken et al. 2023). Given the high relative
 abundance and the high degree of the macroalgae functional group (Table
-S1), we expect a longer hard bottom food web (i.e., number of
-interactions connecting low and high-trophic levels), wider consumer
-trophic niches, and a more stable benthic food web as sea ice cover
-decreases and glaciers retreat due to global warming. In soft bottom
-areas of the cove, multiple food web nodes are being affected by ongoing
-warming effects: decrease in net primary production of benthic
-microalgae (Hoffmann et al. 2019), and changes in the benthic community
-biomass, distribution and composition (Sahade et al. 2015; Pasotti et
-al. 2015). Given that the Potter Cove food web has low connectance and
-omnivory, we suggest fragility and potential trophic cascade effects
-(Marina et al. 2018), especially between species of the soft bottom
-compartment (Table 3). Overall, we anticipate significant shifts in
-energy fluxes, rather than alterations in the overall structure of the
-Potter Cove food web, with strengthening of connections within
-compartments.
+S1), we expect a longer benthic food web (i.e., number of interactions
+connecting low and high-trophic levels), wider consumer trophic niches,
+meaning an increase in omnivory, and a more stable benthic food web as
+sea ice cover decreases and glaciers retreat due to global warming. As a
+net effect of climate change on the overall Potter Cove food web, we
+expect a significant shift in energy fluxes, rather than drastic
+alterations in the topological structure, affecting the transfer of
+energy from lower to higher trophic levels.
 
@@
 as demersal fish (Gutt 2001; Mintenbeck et al. 2012). While we do not
-anticipate large-scale topological changes in the mean food web
-attributes, local extinctions could lead to such changes, particularly
-affecting benthic species (Gutt and Piepenburg 2003). Given that the
-impacted species---whether individually like krill, or collectively like
-macrobenthos and notothenioids (e.g., \emph{P. antarcticum})---present a
-mid-trophic position, high population biomasses and high degree (Table
-S1), we hypothesize that significant shifts in energy fluxes will occur
-(Table 3). Additionally, the food web's low proportion of omnivores
-suggests reduced system resilience (Table 1), increasing the likelihood
-of regime changes (Gutt et al. 2015).
+anticipate large-scale topological changes affecting mean food web
+attributes, local extinctions may produce changes in the interactions,
+especially impacting benthic species (Gutt and Piepenburg 2003). Given
+that the impacted species---whether individually like krill, or
+collectively like macrobenthos and notothenioids (e.g., \emph{P.
+antarcticum})---present a mid-trophic position, high population
+biomasses and high degree (Table S1), we hypothesize that significant
+shifts in energy fluxes will occur (Table 3). Additionally, the food
+web's low proportion of omnivores suggests reduced system resilience
+(Table 1), increasing the likelihood of regime changes (Gutt et al.
+2015).
 
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2759}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2644}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2759}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1609}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3194}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
 \toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Study area}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Stressor}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Hypothesis on food web effects}
+\end{minipage} \\
+\midrule\noalign{}
 \endhead
@@
 \endlastfoot
-\multirow{2}{=}{\textbf{Study area}
-
-======================= \textbf{San Jorge Gulf}} &
-\multirow{2}{=}{\textbf{Stressor}
-
-======================} &
-\multicolumn{2}{>{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.4368} + 2\tabcolsep}@{}}{%
-\multirow{2}{=}{\textbf{Hypothesis on food web effects} \textbar{}
-=======================+ \textbar{}}} \\
- \\
+\textbf{San Jorge Gulf} & & \\
 & Fishery* & ↑ FW connectance
@@
 
-↓ functional diversity & \\
+↓ functional diversity \\
 & Sea warming & Shifts in FW topology
@@
 
-↑ functional diversity & \\
-\textbf{Beagle Channel} & & & \\
+↑ functional diversity \\
+\textbf{Beagle Channel} & & \\
 & Alien species & Shifts in FW topology
 
-↑ spread of perturbations & \\
-\textbf{Burdwood Bank} & & & \\
+↑ spread of perturbations \\
+\textbf{Burdwood Bank} & & \\
 & Fishery & Shifts in main energy fluxes
 
-↓ FW stability & \\
-\textbf{Scotia Sea} & & & \\
+↓ FW stability \\
+\textbf{Scotia Sea} & & \\
 & Sea warming & ↑ FW connectance
@@
 
-↑ spread of perturbation & \\
-\textbf{Potter Cove (Antarctica)} & & & \\
-& Sea warming & ↓ perturbation spreading & \\
-& Sea ice decline + glacial retreat & Differential impacts, by
-substrate: hard (HS) or soft (SS)
-
-↑ FW chain length \& ↑ trophic niches (HS)
-
-↑ FW fragility \& trophic cascades (SS) & \\
-\textbf{Weddell Sea (Antarctica)} & & & \\
+↑ spread of perturbation \\
+\textbf{Potter Cove (Antarctica)} & & \\
+& Sea warming & ↓ perturbation spreading \\
+& Sea ice decline + glacial retreat & ↑ FW chain length \& \textbar{} ↑
+trophic niches \textbar{} \\
+\textbf{Weddell Sea (Antarctica)} & & \\
 & Sea ice decline + iceberg scouring & Shifts in main energy fluxes
@@
 
-↓ resilience & \\
+↓ resilience \\
 \end{longtable}
@@
 Southern Ocean. Despite being qualitative, this is a first important
-step in synthesizing food webs and stressor effects on food webs for
-this region. These qualitative assessments must be complemented with
-further investigations that test their validity. To achieve this, we
-suggest using a combination of observational data such as reported
+step in synthesizing food webs and stressor effects on species and food
+webs for this region. These qualitative assessments must be complemented
+with further investigations that test their validity. To achieve this,
+we suggest using a combination of observational data such as reported
 biomass changes and historic records of sea temperature for the region
@@
 species and food web-level data, we suggest how warming effects may
-impact food web structure and functioning. Besides there is an important
+impact food web structure and functioning. Apart from an important
 amount of uncertainty, these qualitative predictions are intended to
@@
 doi:\href{https://doi.org/10.1038/s42003-021-01673-6}{10.1038/s42003-021-01673-6}.
+
+\bibitem[\citeproctext]{ref-Braeckman2019}
+Braeckman, U., Pasotti, F., Vázquez, S., Zacher, K., Hoffmann, R.,
+Elvert, M., Marchant, H., Buckner, C., Quartino, M.L., Mác Cormack, W.,
+Soetaert, K., Wenzhöfer, F., and Vanreusel, A. 2019. Degradation of
+macroalgal detritus in shallow coastal {Antarctic} sediments. Limnology
+and Oceanography \textbf{64}(4): 1423--1441.
+doi:\href{https://doi.org/10.1002/lno.11125}{10.1002/lno.11125}.
+
+\bibitem[\citeproctext]{ref-Braeckman2024}
+Braeckman, U., Soetaert, K., Pasotti, F., Quartino, M.L., Vanreusel, A.,
+Saravia, L.A., Schloss, I.R., and Van Oevelen, D. 2024. Glacial melt
+impacts carbon flows in an {Antarctic} benthic food web. Frontiers in
+Marine Science \textbf{11}.
+doi:\href{https://doi.org/10.3389/fmars.2024.1359597}{10.3389/fmars.2024.1359597}.
 
@@
 
-\bibitem[\citeproctext]{ref-Cordone2020}
-Cordone, G., Salinas, V., Marina, T.I., Doyle, S.R., Pasotti, F.,
-Saravia, L.A., and Momo, F.R. 2020. Green vs brown food web: {Effects}
-of habitat type on multidimensional stability proxies for a
-highly-resolved {Antarctic} food web. Food Webs \textbf{25}: e00166.
-doi:\href{https://doi.org/10.1016/j.fooweb.2020.e00166}{10.1016/j.fooweb.2020.e00166}.
-
 \bibitem[\citeproctext]{ref-Correa2008}
@@
 doi:\href{https://doi.org/10.1098/rspb.2015.2592}{10.1098/rspb.2015.2592}.
+
+\bibitem[\citeproctext]{ref-David2017}
+David, P., Thébault, E., Anneville, O., Duyck, P.-F., Chapuis, E., and
+Loeuille, N. 2017. Chapter {One} - {Impacts} of {Invasive Species} on
+{Food Webs}: {A Review} of {Empirical Data}. \emph{In} Advances in
+{Ecological Research}. \emph{Edited by} D.A. Bohan, A.J. Dumbrell, and
+F. Massol. Academic Press. pp. 1--60.
+doi:\href{https://doi.org/10.1016/bs.aecr.2016.10.001}{10.1016/bs.aecr.2016.10.001}.
 
@@
 
+\bibitem[\citeproctext]{ref-Rodriguez2024}
+Rodriguez, I.D., and Saravia, L.A. 2024. Potter {Cove}'s {Heavyweights}:
+{Estimation} of species' interaction strength of an {Antarctic} food
+web. EcoEvoRxiv. {[}accessed 18 April 2024{]}.
+
 \bibitem[\citeproctext]{ref-Rowlands2021}

### 2024-04-23 manuscript.Rmd
Submited version

@@
     keep_tex: yes
-  word_document: default
 bibliography: JAE_Review.bib

### 2024-06-08 manuscript - 8Jun.Rmd
Add M&M details

--- 2024-04-23 manuscript.Rmd
@@
 The aim of this review is threefold: 1) describe the complexity and structure of marine food webs along the Southwest Atlantic to Antarctic axis from a network perspective; 2) identify the ongoing global change-related stressors for each marine ecosystem containing the food webs; and 3) review proven food web changes and elaborate on a series of alternative hypotheses on how the identified stressors might affect food web features (energy flow, stability and topology), combining information on node- and network-level properties.
-To identify the main stressors, we performed an exploratory and configurative review instead of a systematic review [@Haddaway2015], because our objective was to formulate evidenced-based hypotheses rather than providing an exhaustive list of species-level stressors for each ecosystem.
+To identify the main stressors, we performed an exploratory and configurative review instead of a systematic review [@Haddaway2015], where we considered more than 200 peer-reviewed articles retrieved mainly from Google Scholar using keywords combining location (i.e., "San Jorge Gulf", "Beagle Channel", "Burdwood Bank", "Scotia Sea", "Weddell Sea", "Potter Cove") and stressors (i.e., "climate change", "global warming", "fishery", "microplastics", etc).
+We performed this type of review because our objective was to formulate evidenced-based hypotheses rather than providing an exhaustive list of species-level stressors for each ecosystem.
 Finally, we suggest which additional data and analyses are needed to gain insights into the stressors’ effects on food web properties in the Southwest Atlantic to Antarctic region.
@@
 Throughout this region, many studies address the ecology of predator-prey relationships but most of these studies are restricted to a few interacting species or certain components of the food web such as fish, crustaceans, and benthos (e.g., @Vinuesa2007, @Padovani2012, @Pasotti2015, @Riccialdelli2020, @Saunders2019, @Pasti2021, @Cordone2022).
-Only few studies consider the complexity of trophic interactions within highly resolved food webs containing hundreds of species, ranging from phytoplankton, zooplankton, benthos, fish, seabirds to whales (but see @Jacob2011, @Marina2018, @Funes2022, @Lopez-Lopez2022, @Rodriguez2022, @Marinainrev).
+Only few studies consider the complexity of trophic interactions within highly resolved food webs containing hundreds of species, ranging from phytoplankton, zooplankton, benthos, fish, seabirds to whales (but see @Jacob2011, @Marina2018, @Funes2022, @Lopez-Lopez2022, @Rodriguez2022, @Marina2024a).
 Neglecting this complexity might lead to a misunderstanding of the structure and functioning of the ecosystems and ultimately reduce the ability to predict ecosystem responses to perturbations [@Montoya2009].
@@
 
-In this review, we included six large marine areas in the Southern Hemisphere for which highly-resolved empirical food webs in terms of species diversity and trophic interactions have been previously described: (1) San Jorge Gulf (~45 - 47ºS, 65 - 68ºW) [@Funes2022], (2) Beagle Channel (~54ºS, 68ºW) [@Rodriguez2022], (3) Burdwood Bank (~54ºS, 59ºW) [@Marinainrev], (4) Scotia Sea (~48 - 58ºS, 50ºW) [@Lopez-Lopez2022], (5) Potter Cove (62ºS, 58ºW, Antarctica) [@Marina2018], and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica) [@Jacob2011; @Marina2024] (Figure 1).
+In this review, we included six large marine areas in the Southern Hemisphere for which highly-resolved empirical food webs in terms of species diversity and trophic interactions have been previously described: (1) San Jorge Gulf (~45 - 47ºS, 65 - 68ºW) [@Funes2022], (2) Beagle Channel (~54ºS, 68ºW) [@Rodriguez2022], (3) Burdwood Bank (~54ºS, 59ºW) [@Marina2024a], (4) Scotia Sea (~48 - 58ºS, 50ºW) [@Lopez-Lopez2022], (5) Potter Cove (62ºS, 58ºW, Antarctica) [@Marina2018], and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica) [@Jacob2011; @Marina2024] (Figure 1).
 The geographic locations of these marine biomes span from temperate Atlantic waters to Antarctic, and are exposed to global change stressors (e.g., sea warming, glacial retreat, fishery, pollution) [@Sage2020], of which some are locally more important, e.g., fisheries in the San Jorge Gulf or glacial retreat in the Antarctic.
@@
 most of the species have a relatively low number of interactions and few species concentrate most of them).
-Almost half of the consumers are omnivores (48%), and the network displays a small-world pattern [@Marinainrev] (Table 1).
+Almost half of the consumers are omnivores (48%), and the network displays a small-world pattern [@Marina2024a] (Table 1).
 This network pattern implies a rapid spread of a perturbation (e.g., contaminant, population fluctuation, local extinction) throughout the food web due to a short distance among species but, at the same time, a greater resistance caused by the confinement of perturbations mainly within subnetworks as a result of a high clustering coefficient [@Bornatowski2017; @Dormann2017].
@@
 
-Burdwood Bank         379         1788        0.01              2.99              2.52          0.49           @Marinainrev
+Burdwood Bank         379         1788        0.01              2.99              2.52          0.49           @Marina2024a
 

### 2024-06-10 manuscript.Rmd
Updated manuscript with minor revisions

@@
 Understanding how these networks respond to global change stressors is of increasing interest, especially along geographical gradients.
-This review summarizes potential stressor responses in marine food webs from the Southwest Atlantic to the Antarctic (45 - 78ºS), encompassing areas such as San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea, Potter Cove, and the Weddell Sea in Antarctica.
+This review summarizes potential stressor responses in marine food webs from the Southwest Atlantic to the Antarctic (45 - 78°S), encompassing areas such as San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea, Potter Cove, and the Weddell Sea in Antarctica.
 The objectives are: 1) to describe the structure of marine food webs along this latitudinal axis using a network approach; 2) to identify predominant global change-related stressors affecting each ecosystem; and 3) to summarize observed food web changes and hypothesize on stressor impacts.
@@
 
-Here we review for the first time stressor responses of marine food webs for areas located along a Southwest Atlantic to Antarctic gradient (45 - 78ºS, Figure 1).
+Here we review for the first time stressor responses of marine food webs for areas located along a Southwest Atlantic to Antarctic gradient (45 - 78°S, Figure 1).
 We considered proven and expected changes in food webs driven by global change-related stressors in selected areas along this large-scale latitudinal range.
 The aim of this review is threefold: 1) describe the complexity and structure of marine food webs along the Southwest Atlantic to Antarctic axis from a network perspective; 2) identify the ongoing global change-related stressors for each marine ecosystem containing the food webs; and 3) review proven food web changes and elaborate on a series of alternative hypotheses on how the identified stressors might affect food web features (energy flow, stability and topology), combining information on node- and network-level properties.
-To identify the main stressors, we performed an exploratory and configurative review instead of a systematic review [@Haddaway2015], because our objective was to formulate evidenced-based hypotheses rather than providing an exhaustive list of species-level stressors for each ecosystem.
+To identify the main stressors, we performed an exploratory and configurative review instead of a systematic review [@Haddaway2015], where we considered more than 200 peer-reviewed articles retrieved mainly from Google Scholar using keywords combining location ( "San Jorge Gulf", "Beagle Channel", "Burdwood Bank", "Scotia Sea", "Weddell Sea", "Potter Cove") and stressors ("acidification", "alien species", "climate change", "contamination", "fishery", "glacier retreat", "global warming", "ice scouring", "invasive species", "marine contaminant", "microplastics", "mercury", "pollution", "sea ice", "sea warming", "urban waste").
+Additionally, we specifically searched for publications by authors we know may have conducted related studies in the area.
+We performed this type of review because our objective was to formulate evidenced-based hypotheses rather than providing an exhaustive list of species-level stressors for each ecosystem.
 Finally, we suggest which additional data and analyses are needed to gain insights into the stressors’ effects on food web properties in the Southwest Atlantic to Antarctic region.
-
-________________
 
@@
 The Southwest and the Atlantic sectors of the Southern Ocean comprise one of the most biologically productive regions of the world's oceans [@Acha2004; @Latorre2023].
-The referred region extends from San Jorge Gulf (45ºS) in the Patagonian shelf to the Weddell Sea (78ºS) in the Southern Ocean and covers a well-connected oceanic area [@Matano2010; @Guihou2020].
+The referred region extends from San Jorge Gulf (45°S) in the Patagonian shelf to the Weddell Sea (78°S) in the Southern Ocean and covers a well-connected oceanic area [@Matano2010; @Guihou2020].
 
 Throughout this region, many studies address the ecology of predator-prey relationships but most of these studies are restricted to a few interacting species or certain components of the food web such as fish, crustaceans, and benthos (e.g., @Vinuesa2007, @Padovani2012, @Pasotti2015, @Riccialdelli2020, @Saunders2019, @Pasti2021, @Cordone2022).
-Only few studies consider the complexity of trophic interactions within highly resolved food webs containing hundreds of species, ranging from phytoplankton, zooplankton, benthos, fish, seabirds to whales (but see @Jacob2011, @Marina2018, @Funes2022, @Lopez-Lopez2022, @Rodriguez2022, @Marinainrev).
+Only few studies consider the complexity of trophic interactions within highly resolved food webs containing hundreds of species, ranging from phytoplankton, zooplankton, benthos, fish, seabirds to whales (but see @Jacob2011, @Marina2018, @Funes2022, @Lopez-Lopez2022, @Rodriguez2022, @Marina2024a).
 Neglecting this complexity might lead to a misunderstanding of the structure and functioning of the ecosystems and ultimately reduce the ability to predict ecosystem responses to perturbations [@Montoya2009].
@@
 
-In this review, we included six large marine areas in the Southern Hemisphere for which highly-resolved empirical food webs in terms of species diversity and trophic interactions have been previously described: (1) San Jorge Gulf (~45 - 47ºS, 65 - 68ºW) [@Funes2022], (2) Beagle Channel (~54ºS, 68ºW) [@Rodriguez2022], (3) Burdwood Bank (~54ºS, 59ºW) [@Marinainrev], (4) Scotia Sea (~48 - 58ºS, 50ºW) [@Lopez-Lopez2022], (5) Potter Cove (62ºS, 58ºW, Antarctica) [@Marina2018], and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica) [@Jacob2011; @Marina2024] (Figure 1).
+In this review, we included six large marine areas in the Southern Hemisphere for which highly-resolved empirical food webs in terms of species diversity and trophic interactions have been previously described: (1) San Jorge Gulf (~45 - 47°S, 65 - 68°W) [@Funes2022], (2) Beagle Channel (~54°S, 68°W) [@Rodriguez2022], (3) Burdwood Bank (~54°S, 59°W) [@Marina2024a], (4) Scotia Sea (~48 - 58°S, 50°W) [@Lopez-Lopez2022], (5) Potter Cove (62°S, 58°W, Antarctica) [@Marina2018], and (6) Weddell Sea (74 - 78°S, 30°W, Antarctica) [@Jacob2011; @Marina2024] (Figure 1).
 The geographic locations of these marine biomes span from temperate Atlantic waters to Antarctic, and are exposed to global change stressors (e.g., sea warming, glacial retreat, fishery, pollution) [@Sage2020], of which some are locally more important, e.g., fisheries in the San Jorge Gulf or glacial retreat in the Antarctic.
@@
 
-Located at a more southern latitude (~54ºS, 68ºW), the Beagle Channel (Figure 1) is an interoceanic passage at the southernmost tip of South America, spanning 240 km in length and 5 km in width (~1200 $\text{km}^2$), with a depth range of 0 - 140 m.
+Located at a more southern latitude (~54°S, 68°W), the Beagle Channel (Figure 1) is an interoceanic passage at the southernmost tip of South America, spanning 240 km in length and 5 km in width (~1200 $\text{km}^2$), with a depth range of 0 - 140 m.
 It features complex coastlines, varying bathymetry, a prevailing west-to-east circulation pattern, and a significant longitudinal gradient of glacial freshwater discharge [@Schloss2023].
@@
 
-The so-called Burdwood Bank ecosystem comprises Marine Protected Areas Namuncurá - Burdwood Bank I and II (~54ºS, 59ºW), meaning the shallow submarine plateau named Burdwood Bank with a 200 m isobath boundary, and a deep slope that reaches 4000 m in depth, respectively [@APN2022] (Figure 1).
-Physical features in the plateau are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC [@Acha2004].
+The so-called Burdwood Bank ecosystem comprises Marine Protected Areas Namuncurá - Burdwood Bank I and II (~54°S, 59°W), meaning the shallow submarine plateau named Burdwood Bank with a 200 m isobath boundary, and a deep slope that reaches 4000 m in depth, respectively [@APN2022] (Figure 1).
+Physical features in the plateau are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8°C [@Acha2004].
 The plateau is surrounded by steep flanks of up to 4000 m depth, protected by the Marine Protected Area Namuncurá - Burdwood Bank II (32,000 $\text{km}^2$).
@@
 
-The Scotia Sea is a deep-sea basin (~48 - 58ºS, 50ºW), delimited by the Drake Passage to the West and by the island complex of the Scotia Arc to the North, East, and South, with an approximate extension of 1.5 x 106 $\text{km}^2$ and a depth range of 0 - 3000 m [@Murphy2006] (Figure 1).
+The Scotia Sea is a deep-sea basin (~48 - 58°S, 50°W), delimited by the Drake Passage to the West and by the island complex of the Scotia Arc to the North, East, and South, with an approximate extension of 1.5 x 106 $\text{km}^2$ and a depth range of 0 - 3000 m [@Murphy2006] (Figure 1).
 Its oceanography is dominated by the Antarctic Circumpolar Current, which is spatially structured by frontal systems [@Whitworth1980].
@@
 
-Located between 74 and 78ºS, the high Antarctic Weddell Sea shelf spans approximately 450 km from East to West [@Jacob2011] (Figure 1).
+Located between 74 and 78°S, the high Antarctic Weddell Sea shelf spans approximately 450 km from East to West [@Jacob2011] (Figure 1).
 The water depth ranges from 200 to 500 m, with shallower regions being covered by continental ice that forms the coastline along the eastern and southern parts of the Weddell Sea.

### 2024-06-10 manuscript.tex
Updated manuscript with minor revisions

@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 summarizes potential stressor responses in marine food webs from the
-Southwest Atlantic to the Antarctic (45 - 78ºS), encompassing areas such
+Southwest Atlantic to the Antarctic (45 - 78°S), encompassing areas such
 as San Jorge Gulf, Beagle Channel, Burdwood Bank, Scotia Sea, Potter
@@
 for areas located along a Southwest Atlantic to Antarctic gradient (45 -
-78ºS, Figure 1). We considered proven and expected changes in food webs
+78°S, Figure 1). We considered proven and expected changes in food webs
 driven by global change-related stressors in selected areas along this
@@
 an exploratory and configurative review instead of a systematic review
-(Haddaway et al. 2015), because our objective was to formulate
+(Haddaway et al. 2015), where we considered more than 200 peer-reviewed 
+articles retrieved mainly from Google Scholar using keywords combining 
+location ( "San Jorge Gulf", "Beagle Channel", "Burdwood Bank", "Scotia Sea", 
+"Weddell Sea", "Potter Cove") and stressors ("acidification", "alien species", 
+"climate change", "contamination", "fishery", "glacier retreat", "global warming", 
+"ice scouring", "invasive species", "marine contaminant", "microplastics", "mercury", 
+"pollution", "sea ice", "sea warming", "urban waste"). Additionally, we 
+specifically searched for publications by authors we know may have conducted 
+related studies in the area. We performed this type of review because our 
+objective was to formulate
 evidenced-based hypotheses rather than providing an exhaustive list of
@@
 (Acha et al. 2004; Latorre et al. 2023). The referred region extends
-from San Jorge Gulf (45ºS) in the Patagonian shelf to the Weddell Sea
-(78ºS) in the Southern Ocean and covers a well-connected oceanic area
+from San Jorge Gulf (45°S) in the Patagonian shelf to the Weddell Sea
+(78°S) in the Southern Ocean and covers a well-connected oceanic area
 (Matano et al. 2010; Guihou et al. 2020).
@@
 Funes et al. (2022), López-López et al. (2022), Rodriguez et al. (2022),
-Marina et al. (in rev.)). Neglecting this complexity might lead to a
+Marina et al. (2024b)). Neglecting this complexity might lead to a
 misunderstanding of the structure and functioning of the ecosystems and
@@
 species diversity and trophic interactions have been previously
-described: (1) San Jorge Gulf (\textasciitilde45 - 47ºS, 65 - 68ºW)
-(Funes et al. 2022), (2) Beagle Channel (\textasciitilde54ºS, 68ºW)
-(Rodriguez et al. 2022), (3) Burdwood Bank (\textasciitilde54ºS, 59ºW)
-(Marina et al. in rev.), (4) Scotia Sea (\textasciitilde48 - 58ºS, 50ºW)
-(López-López et al. 2022), (5) Potter Cove (62ºS, 58ºW, Antarctica)
-(Marina et al. 2018), and (6) Weddell Sea (74 - 78ºS, 30ºW, Antarctica)
-(Jacob et al. 2011; Marina et al. 2024) (Figure 1). The geographic
+described: (1) San Jorge Gulf (\textasciitilde45 - 47°S, 65 - 68°W)
+(Funes et al. 2022), (2) Beagle Channel (\textasciitilde54°S, 68°W)
+(Rodriguez et al. 2022), (3) Burdwood Bank (\textasciitilde54°S, 59°W)
+(Marina et al. 2024b), (4) Scotia Sea (\textasciitilde48 - 58°S, 50°W)
+(López-López et al. 2022), (5) Potter Cove (62°S, 58°W, Antarctica)
+(Marina et al. 2018), and (6) Weddell Sea (74 - 78°S, 30°W, Antarctica)
+(Jacob et al. 2011; Marina et al. 2024a) (Figure 1). The geographic
 locations of these marine biomes span from temperate Atlantic waters to
@@
 
-Located at a more southern latitude (\textasciitilde54ºS, 68ºW), the
+Located at a more southern latitude (\textasciitilde54°S, 68°W), the
 Beagle Channel (Figure 1) is an interoceanic passage at the southernmost
@@
 The so-called Burdwood Bank ecosystem comprises Marine Protected Areas
-Namuncurá - Burdwood Bank I and II (\textasciitilde54ºS, 59ºW), meaning
+Namuncurá - Burdwood Bank I and II (\textasciitilde54°S, 59°W), meaning
 the shallow submarine plateau named Burdwood Bank with a 200 m isobath
@@
 features in the plateau are fairly stable, with salinity averaging 34
-all year round and temperature ranging between 4 and 8ºC (Acha et al.
+all year round and temperature ranging between 4 and 8°C (Acha et al.
 2004). The plateau is surrounded by steep flanks of up to 4000 m depth,
@@
 are omnivores (48\%), and the network displays a small-world pattern
-(Marina et al. in rev.) (Table 1). This network pattern implies a rapid
+(Marina et al. 2024b) (Table 1). This network pattern implies a rapid
 spread of a perturbation (e.g., contaminant, population fluctuation,
@@
 
-The Scotia Sea is a deep-sea basin (\textasciitilde48 - 58ºS, 50ºW),
+The Scotia Sea is a deep-sea basin (\textasciitilde48 - 58°S, 50°W),
 delimited by the Drake Passage to the West and by the island complex of
@@
 
-Located between 74 and 78ºS, the high Antarctic Weddell Sea shelf spans
+Located between 74 and 78°S, the high Antarctic Weddell Sea shelf spans
 approximately 450 km from East to West (Jacob et al. 2011) (Figure 1).
@@
 presence of numerous weak and few strong interactions (Marina et al.
-2024).
+2024a).
 
@@
 Burdwood Bank & 379 & 1788 & 0.01 & 2.99 & 2.52 & 0.49 & Marina et al.
-(in rev.) \\
+(2024b) \\
 Potter Cove & 110 & 649 & 0.05 & 2.33 & 2.22 & 0.46 & Marina et al.
@@
 \bibitem[\citeproctext]{ref-Marina2024}
-Marina, T.I., Saravia, L.A., and Kortsch, S. 2024. New insights into the
-{Weddell Sea} ecosystem applying a quantitative network approach. Ocean
-Science \textbf{20}(1): 141--153. Copernicus GmbH.
+Marina, T.I., Saravia, L.A., and Kortsch, S. 2024a. New insights into
+the {Weddell Sea} ecosystem applying a quantitative network approach.
+Ocean Science \textbf{20}(1): 141--153. Copernicus GmbH.
 doi:\href{https://doi.org/10.5194/os-20-141-2024}{10.5194/os-20-141-2024}.
 
-\bibitem[\citeproctext]{ref-Marinainrev}
+\bibitem[\citeproctext]{ref-Marina2024a}
 Marina, T.I., Schloss, I.R., Lovrich, G.A., Boy, C.C., Bruno, D.O.,
-Capitanio, F.L., Delpiani, S.M., Díaz de Astarloa, J.M., Fraysse, C.,
+Capitanio, F.L., Delpiani, S.M., Díaz De Astarloa, J.M., Fraysse, C.,
 García Alonso, V.A., Raya Rey, A., Schejter, L., Spinelli, M., Tatián,
-M., Urteaga, D., and Riccialdelli, L. in rev. The complex network of
-trophic interactions in a {Subantarctic} oceanic {Marine Protected
+M., Urteaga, D., and Riccialdelli, L. 2024b. The complex network of
+trophic interactions in a sub-{Antarctic} oceanic {Marine Protected
 Area}. Marine Ecology Progress Series.
+doi:\href{https://doi.org/10.3354/meps14600}{10.3354/meps14600}.
 

### 2024-06-11 manuscript.Rmd
Small modifications

@@
 The aim of this review is threefold: 1) describe the complexity and structure of marine food webs along the Southwest Atlantic to Antarctic axis from a network perspective; 2) identify the ongoing global change-related stressors for each marine ecosystem containing the food webs; and 3) review proven food web changes and elaborate on a series of alternative hypotheses on how the identified stressors might affect food web features (energy flow, stability and topology), combining information on node- and network-level properties.
-To identify the main stressors, we performed an exploratory and configurative review instead of a systematic review [@Haddaway2015], where we considered more than 200 peer-reviewed articles retrieved mainly from Google Scholar using keywords combining location ( "San Jorge Gulf", "Beagle Channel", "Burdwood Bank", "Scotia Sea", "Weddell Sea", "Potter Cove") and stressors ("acidification", "alien species", "climate change", "contamination", "fishery", "glacier retreat", "global warming", "ice scouring", "invasive species", "marine contaminant", "microplastics", "mercury", "pollution", "sea ice", "sea warming", "urban waste").
-Additionally, we specifically searched for publications by authors we know may have conducted related studies in the area.
+To identify the main stressors, we performed an exploratory and configurative review [@Haddaway2015], where we considered more than 200 peer-reviewed articles retrieved mainly from Google Scholar using keywords combining location ( "San Jorge Gulf", "Beagle Channel", "Burdwood Bank", "Scotia Sea", "Weddell Sea", "Potter Cove") and stressors ("acidification", "alien species", "climate change", "contamination", "fishery", "glacier retreat", "global warming", "ice scouring", "invasive species", "marine contaminant", "microplastics", "mercury", "pollution", "sea ice", "sea warming", "urban waste").
+Additionally, we specifically searched for publications by authors we know may have conducted related studies in the area including grey literature.
 We performed this type of review because our objective was to formulate evidenced-based hypotheses rather than providing an exhaustive list of species-level stressors for each ecosystem.

### 2024-06-11 manuscript.tex
Small modifications

@@
 network-level properties. To identify the main stressors, we performed
-an exploratory and configurative review instead of a systematic review
+an exploratory and configurative review 
 (Haddaway et al. 2015), where we considered more than 200 peer-reviewed 
@@
 specifically searched for publications by authors we know may have conducted 
-related studies in the area. We performed this type of review because our 
+related studies in the area including grey literature. We performed this type of review because our 
 objective was to formulate
